### 2017-01-24 archive/latex/annotated.tex
2017/01/24

\section{Class List}
Here are the classes, structs, unions and interfaces with brief descriptions\+:\begin{DoxyCompactList}
\item\contentsline{section}{\hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader$<$ value\+\_\+type $>$} \\*Main thread read multiple disk files simultaneously }{\pageref{classasync__multi__stream__reader}}{}
\item\contentsline{section}{\hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer$<$ value\+\_\+type $>$} \\*Multi-\/stream writer }{\pageref{classasync__multi__stream__writer}}{}
\item\contentsline{section}{\hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader$<$ value\+\_\+type $>$} \\*Read data from an external disk file using asynchronous stream }{\pageref{classasync__stream__reader}}{}
\item\contentsline{section}{\hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer$<$ value\+\_\+type $>$} \\*Write data into a disk file using an asynchronous stream }{\pageref{classasync__stream__writer}}{}
\item\contentsline{section}{\hyperlink{class_basic_i_o}{Basic\+IO} \\*Synchronous read operations }{\pageref{class_basic_i_o}}{}
\item\contentsline{section}{\hyperlink{struct_validate4_1_1_bkt_info}{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+Bkt\+Info} \\*Record L-\/type, S-\/type and L\+MS bucket sizes (no matter empty or non-\/empty) in SA \& L\+CP }{\pageref{struct_validate4_1_1_bkt_info}}{}
\item\contentsline{section}{\hyperlink{structbuffer}{buffer$<$ T $>$} \\*Read buffer }{\pageref{structbuffer}}{}
\item\contentsline{section}{\hyperlink{structbuffer__queue}{buffer\+\_\+queue$<$ buffer\+\_\+type $>$} \\*Queue of buffers }{\pageref{structbuffer__queue}}{}
\item\contentsline{section}{\hyperlink{structchoose__int__types}{choose\+\_\+int\+\_\+types$<$ P\+S $>$} \\*Template for choosing int/uint type according to pointer size }{\pageref{structchoose__int__types}}{}
\item\contentsline{section}{\hyperlink{structchoose__int__types_3_014_01_4}{choose\+\_\+int\+\_\+types$<$ 4 $>$} \\*PS = 4, int32/uint32 }{\pageref{structchoose__int__types_3_014_01_4}}{}
\item\contentsline{section}{\hyperlink{structchoose__int__types_3_018_01_4}{choose\+\_\+int\+\_\+types$<$ 8 $>$} \\*Pointer size = 8, 64-\/bit }{\pageref{structchoose__int__types_3_018_01_4}}{}
\item\contentsline{section}{\hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter$<$ tuple\+\_\+type, tuple\+\_\+comparator\+\_\+type $>$} \\*Template for sorter }{\pageref{struct_ex_tuple_sorter}}{}
\item\contentsline{section}{\hyperlink{struct_ex_vector}{Ex\+Vector$<$ value\+\_\+type $>$} \\*Template for vector }{\pageref{struct_ex_vector}}{}
\item\contentsline{section}{\hyperlink{struct_validate4_1_1_l_m_s_validate}{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+L\+M\+S\+Validate} \\*\hyperlink{class_validate}{Validate} S\+A\+\_\+\+L\+MS \& L\+C\+P\+\_\+\+L\+MS }{\pageref{struct_validate4_1_1_l_m_s_validate}}{}
\item\contentsline{section}{\hyperlink{struct_validate4_1_1_l_scan}{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+L\+Scan} \\*Scan SA \& L\+CP rightward to validate the S\+A-\/values of all the S-\/type suffixes and the L\+C\+P-\/values of them and their left neighbor in SA }{\pageref{struct_validate4_1_1_l_scan}}{}
\item\contentsline{section}{\hyperlink{classstd_1_1numeric__limits_3_01uint128_01_4}{std\+::numeric\+\_\+limits$<$ uint128 $>$} }{\pageref{classstd_1_1numeric__limits_3_01uint128_01_4}}{}
\item\contentsline{section}{\hyperlink{classstd_1_1numeric__limits_3_01uint40_01_4}{std\+::numeric\+\_\+limits$<$ uint40 $>$} }{\pageref{classstd_1_1numeric__limits_3_01uint40_01_4}}{}
\item\contentsline{section}{\hyperlink{structpair}{pair$<$ T1, T2 $>$} \\*Structure pair }{\pageref{structpair}}{}
\item\contentsline{section}{\hyperlink{struct_pair_less1st}{Pair\+Less1st$<$ pair\+\_\+type $>$} \\*Sort pair by 1st component in ascending order }{\pageref{struct_pair_less1st}}{}
\item\contentsline{section}{\hyperlink{struct_pair_less2nd}{Pair\+Less2nd$<$ pair\+\_\+type $>$} \\*Sort pair by 2nd component in ascending order }{\pageref{struct_pair_less2nd}}{}
\item\contentsline{section}{\hyperlink{structquadruple}{quadruple$<$ T1, T2, T3, T4 $>$} \\*Structure quadruple }{\pageref{structquadruple}}{}
\item\contentsline{section}{\hyperlink{struct_validate4_1_1_retrieve_pre}{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+Retrieve\+Pre} \\*Retrieve preceding items (pre\+\_\+ch \& pre\+\_\+t) for L-\/type, S-\/type and L\+MS suffixes }{\pageref{struct_validate4_1_1_retrieve_pre}}{}
\item\contentsline{section}{\hyperlink{struct_validate4_1_1_l_m_s_validate_1_1_r_interval}{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+L\+M\+S\+Validate\+::\+R\+Interval} \\*Store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, .. }{\pageref{struct_validate4_1_1_l_m_s_validate_1_1_r_interval}}{}
\item\contentsline{section}{\hyperlink{struct_validate_1_1_r_interval}{Validate$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::\+R\+Interval} \\*Store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, .. }{\pageref{struct_validate_1_1_r_interval}}{}
\item\contentsline{section}{\hyperlink{struct_validate2_1_1_r_interval}{Validate2$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\+R\+Interval} \\*Store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, .. }{\pageref{struct_validate2_1_1_r_interval}}{}
\item\contentsline{section}{\hyperlink{struct_validate3_1_1_r_interval}{Validate3$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\+R\+Interval} \\*Store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, .. }{\pageref{struct_validate3_1_1_r_interval}}{}
\item\contentsline{section}{\hyperlink{struct_validate4_1_1_r_m_q}{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+R\+MQ} \\*\hyperlink{struct_validate4_1_1_r_m_q}{R\+MQ} }{\pageref{struct_validate4_1_1_r_m_q}}{}
\item\contentsline{section}{\hyperlink{struct_validate4_1_1_r_scan}{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+R\+Scan} \\*Scan SA rightward to validate the S\+A-\/values of all the L-\/type suffixes and the L\+C\+P-\/values of them and their left neighbors in SA }{\pageref{struct_validate4_1_1_r_scan}}{}
\item\contentsline{section}{\hyperlink{class_test}{Test$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$} }{\pageref{class_test}}{}
\item\contentsline{section}{\hyperlink{structtriple}{triple$<$ T1, T2, T3 $>$} \\*Structure triple }{\pageref{structtriple}}{}
\item\contentsline{section}{\hyperlink{structtuple__great__comparator__1st}{tuple\+\_\+great\+\_\+comparator\+\_\+1st$<$ tuple\+\_\+type $>$} \\*Function object for comparing tuples by their first component in ascending order }{\pageref{structtuple__great__comparator__1st}}{}
\item\contentsline{section}{\hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st$<$ tuple\+\_\+type $>$} \\*Function object for comparing tuples by their first component in ascending order }{\pageref{structtuple__less__comparator__1st}}{}
\item\contentsline{section}{\hyperlink{structtuple__less__comparator__2nd}{tuple\+\_\+less\+\_\+comparator\+\_\+2nd$<$ tuple\+\_\+type $>$} \\*Function object for comparing tuples by their first two component in ascending order }{\pageref{structtuple__less__comparator__2nd}}{}
\item\contentsline{section}{\hyperlink{classuint128}{uint128} }{\pageref{classuint128}}{}
\item\contentsline{section}{\hyperlink{classuint40}{uint40} }{\pageref{classuint40}}{}
\item\contentsline{section}{\hyperlink{class_validate}{Validate$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$} \\*\hyperlink{class_validate}{Validate} suffix and L\+CP arrays using Karp-\/\+Rarbin finger-\/printing function }{\pageref{class_validate}}{}
\item\contentsline{section}{\hyperlink{class_validate2}{Validate2$<$ alphabet\+\_\+type, size\+\_\+type $>$} \\*Suffix and L\+CP array validater }{\pageref{class_validate2}}{}
\item\contentsline{section}{\hyperlink{class_validate3}{Validate3$<$ alphabet\+\_\+type, size\+\_\+type $>$} \\*\hyperlink{class_validate}{Validate} sa and lcp using Karp-\/\+Rabin fingerprinting function }{\pageref{class_validate3}}{}
\item\contentsline{section}{\hyperlink{class_validate4}{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$} \\*Vaildate SA and L\+CP following the induced-\/sorting principle }{\pageref{class_validate4}}{}
\end{DoxyCompactList}

### 2017-01-24 archive/latex/async__stream__reader_8h.tex
2017/01/24

\hypertarget{async__stream__reader_8h}{}\section{code/src/common/async\+\_\+stream\+\_\+reader.h File Reference}
\label{async__stream__reader_8h}\index{code/src/common/async\+\_\+stream\+\_\+reader.\+h@{code/src/common/async\+\_\+stream\+\_\+reader.\+h}}

read elements from disk file using asychronous I/O operations

{\ttfamily \#include \char`\"{}common.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}basicio.\+h\char`\"{}}\newline
{\ttfamily \#include $<$algorithm$>$}\newline
{\ttfamily \#include $<$condition\+\_\+variable$>$}\newline
{\ttfamily \#include $<$mutex$>$}\newline
{\ttfamily \#include $<$thread$>$}\newline
\subsection*{Classes}
\begin{DoxyCompactItemize}
\item 
struct \hyperlink{structbuffer}{buffer$<$ T $>$}
\begin{DoxyCompactList}\small\item\em read buffer \end{DoxyCompactList}\item 
struct \hyperlink{structbuffer__queue}{buffer\+\_\+queue$<$ buffer\+\_\+type $>$}
\begin{DoxyCompactList}\small\item\em queue of buffers \end{DoxyCompactList}\item 
class \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader$<$ value\+\_\+type $>$}
\begin{DoxyCompactList}\small\item\em read data from an external disk file using asynchronous stream \end{DoxyCompactList}\item 
class \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader$<$ value\+\_\+type $>$}
\begin{DoxyCompactList}\small\item\em main thread read multiple disk files simultaneously. \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
read elements from disk file using asychronous I/O operations

Copyright (c) 2016, Sun Yat-\/sen University, All rights reserved

\begin{DoxyAuthor}{Author}
Yi Wu 
\end{DoxyAuthor}
\begin{DoxyDate}{Date}
2016.\+12 
\end{DoxyDate}

### 2017-01-24 archive/latex/async__stream__writer_8h.tex
2017/01/24

\hypertarget{async__stream__writer_8h}{}\section{code/src/common/async\+\_\+stream\+\_\+writer.h File Reference}
\label{async__stream__writer_8h}\index{code/src/common/async\+\_\+stream\+\_\+writer.\+h@{code/src/common/async\+\_\+stream\+\_\+writer.\+h}}

write elements into disk file using asynchronous I/O operations.

{\ttfamily \#include \char`\"{}common/common.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}basicio.\+h\char`\"{}}\newline
{\ttfamily \#include $<$algorithm$>$}\newline
{\ttfamily \#include $<$condition\+\_\+variable$>$}\newline
{\ttfamily \#include $<$mutex$>$}\newline
{\ttfamily \#include $<$thread$>$}\newline
\subsection*{Classes}
\begin{DoxyCompactItemize}
\item 
struct \hyperlink{structbuffer}{buffer$<$ T $>$}
\begin{DoxyCompactList}\small\item\em read buffer \end{DoxyCompactList}\item 
struct \hyperlink{structbuffer__queue}{buffer\+\_\+queue$<$ buffer\+\_\+type $>$}
\begin{DoxyCompactList}\small\item\em queue of buffers \end{DoxyCompactList}\item 
class \hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer$<$ value\+\_\+type $>$}
\begin{DoxyCompactList}\small\item\em write data into a disk file using an asynchronous stream \end{DoxyCompactList}\item 
class \hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer$<$ value\+\_\+type $>$}
\begin{DoxyCompactList}\small\item\em multi-\/stream writer \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
write elements into disk file using asynchronous I/O operations.

Copyright (c) 2016, Sun Yat-\/sen University, All rights reserved

\begin{DoxyAuthor}{Author}
Yi Wu 
\end{DoxyAuthor}
\begin{DoxyDate}{Date}
2016.\+12 
\end{DoxyDate}

### 2017-01-24 archive/latex/basicio_8h.tex
2017/01/24

\hypertarget{basicio_8h}{}\section{code/src/common/basicio.h File Reference}
\label{basicio_8h}\index{code/src/common/basicio.\+h@{code/src/common/basicio.\+h}}

provide basic I/O interface for sequential read/write operations

\subsection*{Classes}
\begin{DoxyCompactItemize}
\item 
class \hyperlink{class_basic_i_o}{Basic\+IO}
\begin{DoxyCompactList}\small\item\em synchronous read operations \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
provide basic I/O interface for sequential read/write operations

Copyright (c) 2016, Sun Yat-\/sen University, All rights reserved

\begin{DoxyAuthor}{Author}
Yi Wu 
\end{DoxyAuthor}
\begin{DoxyDate}{Date}
2016.\+12 
\end{DoxyDate}

### 2017-01-24 archive/latex/class_basic_i_o.tex
2017/01/24

\hypertarget{class_basic_i_o}{}\section{Basic\+IO Class Reference}
\label{class_basic_i_o}\index{Basic\+IO@{Basic\+IO}}

synchronous read operations

{\ttfamily \#include $<$basicio.\+h$>$}

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
{\footnotesize template$<$typename value\+\_\+type $>$ }\\void \hyperlink{class_basic_i_o_a890e7521a5a2e33eae4d52ec77a196a5}{write\+\_\+to\+\_\+file} (const value\+\_\+type $\ast$\+\_\+src, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+cnt, std\+::\+F\+I\+LE $\ast$\+\_\+f)
\begin{DoxyCompactList}\small\item\em put data into a disk file specified by the descriptor \end{DoxyCompactList}\item 
{\footnotesize template$<$typename value\+\_\+type $>$ }\\void \hyperlink{class_basic_i_o_a1bcd7dbe1acd71bafa1b5d6d4fc32e9e}{write\+\_\+to\+\_\+file} (const value\+\_\+type $\ast$\+\_\+src, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+cnt, const std\+::string \&\+\_\+fn)
\begin{DoxyCompactList}\small\item\em put data into a disk file specified by the name, close the file after the operation. \end{DoxyCompactList}\item 
{\footnotesize template$<$typename value\+\_\+type $>$ }\\\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_basic_i_o_a5e1c1be36914e4749f4a4bd0cf1b53d0}{read\+\_\+from\+\_\+file} (value\+\_\+type $\ast$\+\_\+des, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+cnt, const std\+::\+F\+I\+LE $\ast$\+\_\+f)
\begin{DoxyCompactList}\small\item\em get data from a disk file specified by the descriptor \end{DoxyCompactList}\item 
{\footnotesize template$<$typename value\+\_\+type $>$ }\\\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_basic_i_o_a7e492b3c92dbb91e7f45cd5ed03365a3}{read\+\_\+from\+\_\+file} (value\+\_\+type $\ast$\+\_\+des, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+cnt, const std\+::string \&\+\_\+fn)
\begin{DoxyCompactList}\small\item\em read data from a disk file specified by the name, close the file after the operation. \end{DoxyCompactList}\item 
{\footnotesize template$<$typename value\+\_\+type $>$ }\\void \hyperlink{class_basic_i_o_a7aed99607484ece4b385e3fdced47e1c}{read\+\_\+at\+\_\+offset} (value\+\_\+type $\ast$\+\_\+des, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+offset, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+cnt, const std\+::\+F\+I\+LE $\ast$\+\_\+f)
\begin{DoxyCompactList}\small\item\em read data from a disk file, beginning at the specified offset \end{DoxyCompactList}\item 
{\footnotesize template$<$typename value\+\_\+type $>$ }\\void \hyperlink{class_basic_i_o_a934ed5d36b8a132b622c59c61b881bdd}{read\+\_\+at\+\_\+offset} (value\+\_\+type $\ast$\+\_\+des, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+offset, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+cnt, const std\+::string \&\+\_\+fn)
\begin{DoxyCompactList}\small\item\em read data from a disk file, beginning at the specified offset \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Static Public Member Functions}
\begin{DoxyCompactItemize}
\item 
static std\+::\+F\+I\+LE $\ast$ \hyperlink{class_basic_i_o_a0a548f83f6d4289239347e8fd2c93a32}{file\+\_\+open} (const std\+::string \+\_\+fn, const std\+::string \+\_\+mode)
\begin{DoxyCompactList}\small\item\em open file in specific mode \end{DoxyCompactList}\item 
static std\+::\+F\+I\+LE $\ast$ \hyperlink{class_basic_i_o_ad4ba62659302987f0bf22d5e4a705ab1}{file\+\_\+open\+\_\+nobuf} (const std\+::string \+\_\+fn, const std\+::string \+\_\+mode)
\begin{DoxyCompactList}\small\item\em open file in specific mode with nobuf option \end{DoxyCompactList}\item 
static \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_basic_i_o_a6cafa2bbf504906e3484bd1c1df10474}{file\+\_\+size} (const std\+::string \+\_\+fn)
\begin{DoxyCompactList}\small\item\em return file size in bytes \end{DoxyCompactList}\item 
static bool \hyperlink{class_basic_i_o_a875c4dd065101a3fe469222699a45708}{file\+\_\+exists} (const std\+::string \+\_\+fn)
\begin{DoxyCompactList}\small\item\em check if exists \end{DoxyCompactList}\item 
static void \hyperlink{class_basic_i_o_ad47c4d4b9845b01ad4ee0e81e726472c}{file\+\_\+delete} (const std\+::string \+\_\+fn)
\begin{DoxyCompactList}\small\item\em delete file \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
synchronous read operations

\subsection{Member Function Documentation}
\mbox{\Hypertarget{class_basic_i_o_ad47c4d4b9845b01ad4ee0e81e726472c}\label{class_basic_i_o_ad47c4d4b9845b01ad4ee0e81e726472c}} 
\index{Basic\+IO@{Basic\+IO}!file\+\_\+delete@{file\+\_\+delete}}
\index{file\+\_\+delete@{file\+\_\+delete}!Basic\+IO@{Basic\+IO}}
\subsubsection{\texorpdfstring{file\+\_\+delete()}{file\_delete()}}
{\footnotesize\ttfamily void Basic\+I\+O\+::file\+\_\+delete (\begin{DoxyParamCaption}\item[{const std\+::string}]{\+\_\+fn }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [static]}}

delete file

\begin{DoxyParams}{Parameters}
{\em \+\_\+fn} & filename \\
\hline
\end{DoxyParams}
\mbox{\Hypertarget{class_basic_i_o_a875c4dd065101a3fe469222699a45708}\label{class_basic_i_o_a875c4dd065101a3fe469222699a45708}} 
\index{Basic\+IO@{Basic\+IO}!file\+\_\+exists@{file\+\_\+exists}}
\index{file\+\_\+exists@{file\+\_\+exists}!Basic\+IO@{Basic\+IO}}
\subsubsection{\texorpdfstring{file\+\_\+exists()}{file\_exists()}}
{\footnotesize\ttfamily bool Basic\+I\+O\+::file\+\_\+exists (\begin{DoxyParamCaption}\item[{const std\+::string}]{\+\_\+fn }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [static]}}

check if exists

\begin{DoxyParams}{Parameters}
{\em \+\_\+fn} & filename \\
\hline
\end{DoxyParams}
\mbox{\Hypertarget{class_basic_i_o_a0a548f83f6d4289239347e8fd2c93a32}\label{class_basic_i_o_a0a548f83f6d4289239347e8fd2c93a32}} 
\index{Basic\+IO@{Basic\+IO}!file\+\_\+open@{file\+\_\+open}}
\index{file\+\_\+open@{file\+\_\+open}!Basic\+IO@{Basic\+IO}}
\subsubsection{\texorpdfstring{file\+\_\+open()}{file\_open()}}
{\footnotesize\ttfamily std\+::\+F\+I\+LE $\ast$ Basic\+I\+O\+::file\+\_\+open (\begin{DoxyParamCaption}\item[{const std\+::string}]{\+\_\+fn,  }\item[{const std\+::string}]{\+\_\+mode }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [static]}}

open file in specific mode

\begin{DoxyParams}{Parameters}
{\em \+\_\+fn} & filename \\
\hline
{\em \+\_\+mode} & mode \\
\hline
\end{DoxyParams}
\mbox{\Hypertarget{class_basic_i_o_ad4ba62659302987f0bf22d5e4a705ab1}\label{class_basic_i_o_ad4ba62659302987f0bf22d5e4a705ab1}} 
\index{Basic\+IO@{Basic\+IO}!file\+\_\+open\+\_\+nobuf@{file\+\_\+open\+\_\+nobuf}}
\index{file\+\_\+open\+\_\+nobuf@{file\+\_\+open\+\_\+nobuf}!Basic\+IO@{Basic\+IO}}
\subsubsection{\texorpdfstring{file\+\_\+open\+\_\+nobuf()}{file\_open\_nobuf()}}
{\footnotesize\ttfamily std\+::\+F\+I\+LE $\ast$ Basic\+I\+O\+::file\+\_\+open\+\_\+nobuf (\begin{DoxyParamCaption}\item[{const std\+::string}]{\+\_\+fn,  }\item[{const std\+::string}]{\+\_\+mode }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [static]}}

open file in specific mode with nobuf option

\begin{DoxyParams}{Parameters}
{\em \+\_\+fn} & filename \\
\hline
{\em \+\_\+mode} & mode \\
\hline
\end{DoxyParams}
\mbox{\Hypertarget{class_basic_i_o_a6cafa2bbf504906e3484bd1c1df10474}\label{class_basic_i_o_a6cafa2bbf504906e3484bd1c1df10474}} 
\index{Basic\+IO@{Basic\+IO}!file\+\_\+size@{file\+\_\+size}}
\index{file\+\_\+size@{file\+\_\+size}!Basic\+IO@{Basic\+IO}}
\subsubsection{\texorpdfstring{file\+\_\+size()}{file\_size()}}
{\footnotesize\ttfamily \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} Basic\+I\+O\+::file\+\_\+size (\begin{DoxyParamCaption}\item[{const std\+::string}]{\+\_\+fn }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [static]}}

return file size in bytes

\begin{DoxyParams}{Parameters}
{\em \+\_\+fn} & filename \\
\hline
\end{DoxyParams}
\mbox{\Hypertarget{class_basic_i_o_a7aed99607484ece4b385e3fdced47e1c}\label{class_basic_i_o_a7aed99607484ece4b385e3fdced47e1c}} 
\index{Basic\+IO@{Basic\+IO}!read\+\_\+at\+\_\+offset@{read\+\_\+at\+\_\+offset}}
\index{read\+\_\+at\+\_\+offset@{read\+\_\+at\+\_\+offset}!Basic\+IO@{Basic\+IO}}
\subsubsection{\texorpdfstring{read\+\_\+at\+\_\+offset()}{read\_at\_offset()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
void Basic\+I\+O\+::read\+\_\+at\+\_\+offset (\begin{DoxyParamCaption}\item[{value\+\_\+type $\ast$}]{\+\_\+des,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+offset,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+cnt,  }\item[{const std\+::\+F\+I\+LE $\ast$}]{\+\_\+f }\end{DoxyParamCaption})}

read data from a disk file, beginning at the specified offset

\begin{DoxyParams}{Parameters}
{\em \+\_\+des} & destination \\
\hline
{\em \+\_\+offset} & offset \\
\hline
{\em \+\_\+cnt} & number of elements \\
\hline
{\em \+\_\+f} & descriptor \\
\hline
\end{DoxyParams}
\mbox{\Hypertarget{class_basic_i_o_a934ed5d36b8a132b622c59c61b881bdd}\label{class_basic_i_o_a934ed5d36b8a132b622c59c61b881bdd}} 
\index{Basic\+IO@{Basic\+IO}!read\+\_\+at\+\_\+offset@{read\+\_\+at\+\_\+offset}}
\index{read\+\_\+at\+\_\+offset@{read\+\_\+at\+\_\+offset}!Basic\+IO@{Basic\+IO}}
\subsubsection{\texorpdfstring{read\+\_\+at\+\_\+offset()}{read\_at\_offset()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
void Basic\+I\+O\+::read\+\_\+at\+\_\+offset (\begin{DoxyParamCaption}\item[{value\+\_\+type $\ast$}]{\+\_\+des,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+offset,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+cnt,  }\item[{const std\+::string \&}]{\+\_\+fn }\end{DoxyParamCaption})}

read data from a disk file, beginning at the specified offset

\begin{DoxyParams}{Parameters}
{\em \+\_\+des} & destination \\
\hline
{\em \+\_\+offset} & offset \\
\hline
{\em \+\_\+cnt} & number of elements \\
\hline
{\em \+\_\+fn} & filename \\
\hline
\end{DoxyParams}
\mbox{\Hypertarget{class_basic_i_o_a5e1c1be36914e4749f4a4bd0cf1b53d0}\label{class_basic_i_o_a5e1c1be36914e4749f4a4bd0cf1b53d0}} 
\index{Basic\+IO@{Basic\+IO}!read\+\_\+from\+\_\+file@{read\+\_\+from\+\_\+file}}
\index{read\+\_\+from\+\_\+file@{read\+\_\+from\+\_\+file}!Basic\+IO@{Basic\+IO}}
\subsubsection{\texorpdfstring{read\+\_\+from\+\_\+file()}{read\_from\_file()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} Basic\+I\+O\+::read\+\_\+from\+\_\+file (\begin{DoxyParamCaption}\item[{value\+\_\+type $\ast$}]{\+\_\+des,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+cnt,  }\item[{const std\+::\+F\+I\+LE $\ast$}]{\+\_\+f }\end{DoxyParamCaption})}

get data from a disk file specified by the descriptor

\begin{DoxyParams}{Parameters}
{\em \+\_\+des} & destination \\
\hline
{\em \+\_\+cnt} & number of elements \\
\hline
{\em \+\_\+f} & descriptor \\
\hline
\end{DoxyParams}
\mbox{\Hypertarget{class_basic_i_o_a7e492b3c92dbb91e7f45cd5ed03365a3}\label{class_basic_i_o_a7e492b3c92dbb91e7f45cd5ed03365a3}} 
\index{Basic\+IO@{Basic\+IO}!read\+\_\+from\+\_\+file@{read\+\_\+from\+\_\+file}}
\index{read\+\_\+from\+\_\+file@{read\+\_\+from\+\_\+file}!Basic\+IO@{Basic\+IO}}
\subsubsection{\texorpdfstring{read\+\_\+from\+\_\+file()}{read\_from\_file()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} Basic\+I\+O\+::read\+\_\+from\+\_\+file (\begin{DoxyParamCaption}\item[{value\+\_\+type $\ast$}]{\+\_\+des,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+cnt,  }\item[{const std\+::string \&}]{\+\_\+fn }\end{DoxyParamCaption})}

read data from a disk file specified by the name, close the file after the operation.

\begin{DoxyParams}{Parameters}
{\em \+\_\+des} & destination \\
\hline
{\em \+\_\+cnt} & number of elements \\
\hline
{\em \+\_\+fn} & filename \\
\hline
\end{DoxyParams}
\mbox{\Hypertarget{class_basic_i_o_a890e7521a5a2e33eae4d52ec77a196a5}\label{class_basic_i_o_a890e7521a5a2e33eae4d52ec77a196a5}} 
\index{Basic\+IO@{Basic\+IO}!write\+\_\+to\+\_\+file@{write\+\_\+to\+\_\+file}}
\index{write\+\_\+to\+\_\+file@{write\+\_\+to\+\_\+file}!Basic\+IO@{Basic\+IO}}
\subsubsection{\texorpdfstring{write\+\_\+to\+\_\+file()}{write\_to\_file()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
void Basic\+I\+O\+::write\+\_\+to\+\_\+file (\begin{DoxyParamCaption}\item[{const value\+\_\+type $\ast$}]{\+\_\+src,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+cnt,  }\item[{std\+::\+F\+I\+LE $\ast$}]{\+\_\+f }\end{DoxyParamCaption})}

put data into a disk file specified by the descriptor

\begin{DoxyParams}{Parameters}
{\em \+\_\+src} & source \\
\hline
{\em \+\_\+cnt} & number of elements \\
\hline
{\em \+\_\+f} & descriptor \\
\hline
\end{DoxyParams}
\mbox{\Hypertarget{class_basic_i_o_a1bcd7dbe1acd71bafa1b5d6d4fc32e9e}\label{class_basic_i_o_a1bcd7dbe1acd71bafa1b5d6d4fc32e9e}} 
\index{Basic\+IO@{Basic\+IO}!write\+\_\+to\+\_\+file@{write\+\_\+to\+\_\+file}}
\index{write\+\_\+to\+\_\+file@{write\+\_\+to\+\_\+file}!Basic\+IO@{Basic\+IO}}
\subsubsection{\texorpdfstring{write\+\_\+to\+\_\+file()}{write\_to\_file()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
void Basic\+I\+O\+::write\+\_\+to\+\_\+file (\begin{DoxyParamCaption}\item[{const value\+\_\+type $\ast$}]{\+\_\+src,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+cnt,  }\item[{const std\+::string \&}]{\+\_\+fn }\end{DoxyParamCaption})}

put data into a disk file specified by the name, close the file after the operation.

\begin{DoxyParams}{Parameters}
{\em \+\_\+src} & source \\
\hline
{\em \+\_\+cnt} & number of elements \\
\hline
{\em \+\_\+fn} & filename \\
\hline
\end{DoxyParams}

The documentation for this class was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{basicio_8h}{basicio.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/class_test.tex
2017/01/24

\hypertarget{class_test}{}\section{Test$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$ Class Template Reference}
\label{class_test}\index{Test$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$@{Test$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$}}

{\ttfamily \#include $<$test.\+h$>$}

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{class_test_a9ca0652d8678a0c57e321fcc21f9ae39}{Test} (\hyperlink{class_test_aace52a5af52c5d5f457ec201881ab2ab}{alphabet\+\_\+vector\+\_\+type} $\ast$\+\_\+ex\+\_\+s, \hyperlink{class_test_a9290f9f05f2aac6555e7366cf214d186}{size\+\_\+vector\+\_\+type} $\ast$\+\_\+ex\+\_\+sa, \hyperlink{class_test_a9290f9f05f2aac6555e7366cf214d186}{size\+\_\+vector\+\_\+type} $\ast$\+\_\+ex\+\_\+lcp)
\begin{DoxyCompactList}\small\item\em ctor \end{DoxyCompactList}\item 
bool \hyperlink{class_test_ab5d1d239530c9b99ab1732e5d4008b87}{validate\+\_\+lms} (\hyperlink{class_test_a9290f9f05f2aac6555e7366cf214d186}{size\+\_\+vector\+\_\+type} $\ast$\+\_\+sa\+\_\+ex\+\_\+lms, \hyperlink{class_test_a9290f9f05f2aac6555e7366cf214d186}{size\+\_\+vector\+\_\+type} $\ast$\+\_\+lcp\+\_\+ex\+\_\+lms)
\begin{DoxyCompactList}\small\item\em validate S\+A\+\_\+\+L\+MS and L\+C\+P\+\_\+\+L\+MS \end{DoxyCompactList}\item 
bool \hyperlink{class_test_aed94eee4f2a73d02c0abbe448efe2095}{validate\+\_\+pre\+\_\+item} (\hyperlink{class_test_a1e7fba953871f5eee60eabf8b0e287b7}{triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$\+\_\+pre\+\_\+item\+\_\+of\+\_\+l\+\_\+sorter, \hyperlink{class_test_ad87ac75730f80ef0824f0c56ec7db12d}{triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$\+\_\+pre\+\_\+item\+\_\+of\+\_\+s\+\_\+sorter, \hyperlink{class_test_aa25f2080d593eb18d6e5e475d99bac17}{pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$\+\_\+pre\+\_\+item\+\_\+of\+\_\+lms\+\_\+sorter)
\begin{DoxyCompactList}\small\item\em vaildate preceding items \end{DoxyCompactList}\item 
\hyperlink{class_test_acafab99b8fa6756de9998d16fc9e33f4}{$\sim$\+Test} ()
\end{DoxyCompactItemize}
\subsection*{Private Types}
\begin{DoxyCompactItemize}
\item 
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$ alphabet\+\_\+type $>$\+::vector \hyperlink{class_test_aace52a5af52c5d5f457ec201881ab2ab}{alphabet\+\_\+vector\+\_\+type}
\item 
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$ size\+\_\+type $>$\+::vector \hyperlink{class_test_a9290f9f05f2aac6555e7366cf214d186}{size\+\_\+vector\+\_\+type}
\item 
typedef \hyperlink{structtriple}{triple}$<$ size\+\_\+type, \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8}, \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} $>$ \hyperlink{class_test_ae1d42342f4ec472a724f55af01c3c5ab}{triple2\+\_\+type}
\item 
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$ \hyperlink{class_test_ae1d42342f4ec472a724f55af01c3c5ab}{triple2\+\_\+type} $>$ \hyperlink{class_test_a8eb2bb639be9c46697c52f77d79703a8}{triple2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$ \hyperlink{class_test_ae1d42342f4ec472a724f55af01c3c5ab}{triple2\+\_\+type}, \hyperlink{class_test_a8eb2bb639be9c46697c52f77d79703a8}{triple2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type} $>$\+::sorter \hyperlink{class_test_a1e7fba953871f5eee60eabf8b0e287b7}{triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{structtuple__great__comparator__1st}{tuple\+\_\+great\+\_\+comparator\+\_\+1st}$<$ \hyperlink{class_test_ae1d42342f4ec472a724f55af01c3c5ab}{triple2\+\_\+type} $>$ \hyperlink{class_test_aeafbf94ce50f60c6c463e2e57a4d43a5}{triple2\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$ \hyperlink{class_test_ae1d42342f4ec472a724f55af01c3c5ab}{triple2\+\_\+type}, \hyperlink{class_test_aeafbf94ce50f60c6c463e2e57a4d43a5}{triple2\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type} $>$\+::sorter \hyperlink{class_test_ad87ac75730f80ef0824f0c56ec7db12d}{triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{structpair}{pair}$<$ size\+\_\+type, \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} $>$ \hyperlink{class_test_a9c312a6616c86eaf224d04d298f58ed4}{pair3\+\_\+type}
\item 
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$ \hyperlink{class_test_a9c312a6616c86eaf224d04d298f58ed4}{pair3\+\_\+type} $>$ \hyperlink{class_test_a5ebabea22d5111680c158fb28c7cc935}{pair3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$ \hyperlink{class_test_a9c312a6616c86eaf224d04d298f58ed4}{pair3\+\_\+type}, \hyperlink{class_test_a5ebabea22d5111680c158fb28c7cc935}{pair3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type} $>$\+::sorter \hyperlink{class_test_aa25f2080d593eb18d6e5e475d99bac17}{pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}
\end{DoxyCompactItemize}
\subsection*{Private Attributes}
\begin{DoxyCompactItemize}
\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_test_ac0031d768664e62b04aa14acaecdb354}{m\+\_\+len}
\item 
alphabet\+\_\+type $\ast$ \hyperlink{class_test_a2992148c8dda566ae4f4ebbdb26bdccd}{m\+\_\+s}
\item 
size\+\_\+type $\ast$ \hyperlink{class_test_a38956729bdb63c0bfe7760e827769309}{m\+\_\+sa}
\item 
size\+\_\+type $\ast$ \hyperlink{class_test_aba44b9a05184fb5f62f4901fd607da40}{m\+\_\+lcp}
\item 
\hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} $\ast$ \hyperlink{class_test_ad5db148e90886fc6524a1f07194df9a9}{m\+\_\+t}
\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_test_a3a2c92b2ace889d7c98d1188ee2542c5}{m\+\_\+lms\+\_\+num}
\item 
size\+\_\+type $\ast$ \hyperlink{class_test_a557862839f4ead2e08d12e7770340ded}{m\+\_\+sa\+\_\+lms}
\item 
size\+\_\+type $\ast$ \hyperlink{class_test_a94d43daa04ae5011cc46d8fd3dc8c83b}{m\+\_\+lcp\+\_\+lms}
\end{DoxyCompactItemize}

\subsection{Member Typedef Documentation}
\mbox{\Hypertarget{class_test_aace52a5af52c5d5f457ec201881ab2ab}\label{class_test_aace52a5af52c5d5f457ec201881ab2ab}} 
\index{Test@{Test}!alphabet\+\_\+vector\+\_\+type@{alphabet\+\_\+vector\+\_\+type}}
\index{alphabet\+\_\+vector\+\_\+type@{alphabet\+\_\+vector\+\_\+type}!Test@{Test}}
\subsubsection{\texorpdfstring{alphabet\+\_\+vector\+\_\+type}{alphabet\_vector\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$alphabet\+\_\+type$>$\+::vector \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_test_aace52a5af52c5d5f457ec201881ab2ab}{alphabet\+\_\+vector\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_test_a5ebabea22d5111680c158fb28c7cc935}\label{class_test_a5ebabea22d5111680c158fb28c7cc935}} 
\index{Test@{Test}!pair3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type@{pair3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}}
\index{pair3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type@{pair3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}!Test@{Test}}
\subsubsection{\texorpdfstring{pair3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}{pair3\_less\_comparator\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$\hyperlink{class_test_a9c312a6616c86eaf224d04d298f58ed4}{pair3\+\_\+type}$>$ \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_test_a5ebabea22d5111680c158fb28c7cc935}{pair3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_test_aa25f2080d593eb18d6e5e475d99bac17}\label{class_test_aa25f2080d593eb18d6e5e475d99bac17}} 
\index{Test@{Test}!pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type@{pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}}
\index{pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type@{pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}!Test@{Test}}
\subsubsection{\texorpdfstring{pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}{pair3\_less\_sorter\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$\hyperlink{class_test_a9c312a6616c86eaf224d04d298f58ed4}{pair3\+\_\+type}, \hyperlink{class_test_a5ebabea22d5111680c158fb28c7cc935}{pair3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}$>$\+::sorter \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_test_aa25f2080d593eb18d6e5e475d99bac17}{pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_test_a9c312a6616c86eaf224d04d298f58ed4}\label{class_test_a9c312a6616c86eaf224d04d298f58ed4}} 
\index{Test@{Test}!pair3\+\_\+type@{pair3\+\_\+type}}
\index{pair3\+\_\+type@{pair3\+\_\+type}!Test@{Test}}
\subsubsection{\texorpdfstring{pair3\+\_\+type}{pair3\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
typedef \hyperlink{structpair}{pair}$<$size\+\_\+type, \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8}$>$ \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_test_a9c312a6616c86eaf224d04d298f58ed4}{pair3\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_test_a9290f9f05f2aac6555e7366cf214d186}\label{class_test_a9290f9f05f2aac6555e7366cf214d186}} 
\index{Test@{Test}!size\+\_\+vector\+\_\+type@{size\+\_\+vector\+\_\+type}}
\index{size\+\_\+vector\+\_\+type@{size\+\_\+vector\+\_\+type}!Test@{Test}}
\subsubsection{\texorpdfstring{size\+\_\+vector\+\_\+type}{size\_vector\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$size\+\_\+type$>$\+::vector \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_test_a9290f9f05f2aac6555e7366cf214d186}{size\+\_\+vector\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_test_aeafbf94ce50f60c6c463e2e57a4d43a5}\label{class_test_aeafbf94ce50f60c6c463e2e57a4d43a5}} 
\index{Test@{Test}!triple2\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type@{triple2\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type}}
\index{triple2\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type@{triple2\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type}!Test@{Test}}
\subsubsection{\texorpdfstring{triple2\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type}{triple2\_great\_comparator\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
typedef \hyperlink{structtuple__great__comparator__1st}{tuple\+\_\+great\+\_\+comparator\+\_\+1st}$<$\hyperlink{class_test_ae1d42342f4ec472a724f55af01c3c5ab}{triple2\+\_\+type}$>$ \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_test_aeafbf94ce50f60c6c463e2e57a4d43a5}{triple2\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_test_ad87ac75730f80ef0824f0c56ec7db12d}\label{class_test_ad87ac75730f80ef0824f0c56ec7db12d}} 
\index{Test@{Test}!triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type@{triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type}}
\index{triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type@{triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type}!Test@{Test}}
\subsubsection{\texorpdfstring{triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type}{triple2\_great\_sorter\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$\hyperlink{class_test_ae1d42342f4ec472a724f55af01c3c5ab}{triple2\+\_\+type}, \hyperlink{class_test_aeafbf94ce50f60c6c463e2e57a4d43a5}{triple2\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type}$>$\+::sorter \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_test_ad87ac75730f80ef0824f0c56ec7db12d}{triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_test_a8eb2bb639be9c46697c52f77d79703a8}\label{class_test_a8eb2bb639be9c46697c52f77d79703a8}} 
\index{Test@{Test}!triple2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type@{triple2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}}
\index{triple2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type@{triple2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}!Test@{Test}}
\subsubsection{\texorpdfstring{triple2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}{triple2\_less\_comparator\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$\hyperlink{class_test_ae1d42342f4ec472a724f55af01c3c5ab}{triple2\+\_\+type}$>$ \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_test_a8eb2bb639be9c46697c52f77d79703a8}{triple2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_test_a1e7fba953871f5eee60eabf8b0e287b7}\label{class_test_a1e7fba953871f5eee60eabf8b0e287b7}} 
\index{Test@{Test}!triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type@{triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}}
\index{triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type@{triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}!Test@{Test}}
\subsubsection{\texorpdfstring{triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}{triple2\_less\_sorter\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$\hyperlink{class_test_ae1d42342f4ec472a724f55af01c3c5ab}{triple2\+\_\+type}, \hyperlink{class_test_a8eb2bb639be9c46697c52f77d79703a8}{triple2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}$>$\+::sorter \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_test_a1e7fba953871f5eee60eabf8b0e287b7}{triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_test_ae1d42342f4ec472a724f55af01c3c5ab}\label{class_test_ae1d42342f4ec472a724f55af01c3c5ab}} 
\index{Test@{Test}!triple2\+\_\+type@{triple2\+\_\+type}}
\index{triple2\+\_\+type@{triple2\+\_\+type}!Test@{Test}}
\subsubsection{\texorpdfstring{triple2\+\_\+type}{triple2\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
typedef \hyperlink{structtriple}{triple}$<$size\+\_\+type, \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8}, \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8}$>$ \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_test_ae1d42342f4ec472a724f55af01c3c5ab}{triple2\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{class_test_a9ca0652d8678a0c57e321fcc21f9ae39}\label{class_test_a9ca0652d8678a0c57e321fcc21f9ae39}} 
\index{Test@{Test}!Test@{Test}}
\index{Test@{Test}!Test@{Test}}
\subsubsection{\texorpdfstring{Test()}{Test()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
\hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_test}{Test} (\begin{DoxyParamCaption}\item[{\hyperlink{class_test_aace52a5af52c5d5f457ec201881ab2ab}{alphabet\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+ex\+\_\+s,  }\item[{\hyperlink{class_test_a9290f9f05f2aac6555e7366cf214d186}{size\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+ex\+\_\+sa,  }\item[{\hyperlink{class_test_a9290f9f05f2aac6555e7366cf214d186}{size\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+ex\+\_\+lcp }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

ctor

\mbox{\Hypertarget{class_test_acafab99b8fa6756de9998d16fc9e33f4}\label{class_test_acafab99b8fa6756de9998d16fc9e33f4}} 
\index{Test@{Test}!````~Test@{$\sim$\+Test}}
\index{````~Test@{$\sim$\+Test}!Test@{Test}}
\subsubsection{\texorpdfstring{$\sim$\+Test()}{~Test()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
\hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::$\sim$\hyperlink{class_test}{Test} (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

\subsection{Member Function Documentation}
\mbox{\Hypertarget{class_test_ab5d1d239530c9b99ab1732e5d4008b87}\label{class_test_ab5d1d239530c9b99ab1732e5d4008b87}} 
\index{Test@{Test}!validate\+\_\+lms@{validate\+\_\+lms}}
\index{validate\+\_\+lms@{validate\+\_\+lms}!Test@{Test}}
\subsubsection{\texorpdfstring{validate\+\_\+lms()}{validate\_lms()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
bool \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::validate\+\_\+lms (\begin{DoxyParamCaption}\item[{\hyperlink{class_test_a9290f9f05f2aac6555e7366cf214d186}{size\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+sa\+\_\+ex\+\_\+lms,  }\item[{\hyperlink{class_test_a9290f9f05f2aac6555e7366cf214d186}{size\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+lcp\+\_\+ex\+\_\+lms }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

validate S\+A\+\_\+\+L\+MS and L\+C\+P\+\_\+\+L\+MS

\mbox{\Hypertarget{class_test_aed94eee4f2a73d02c0abbe448efe2095}\label{class_test_aed94eee4f2a73d02c0abbe448efe2095}} 
\index{Test@{Test}!validate\+\_\+pre\+\_\+item@{validate\+\_\+pre\+\_\+item}}
\index{validate\+\_\+pre\+\_\+item@{validate\+\_\+pre\+\_\+item}!Test@{Test}}
\subsubsection{\texorpdfstring{validate\+\_\+pre\+\_\+item()}{validate\_pre\_item()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
bool \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::validate\+\_\+pre\+\_\+item (\begin{DoxyParamCaption}\item[{\hyperlink{class_test_a1e7fba953871f5eee60eabf8b0e287b7}{triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$}]{\+\_\+pre\+\_\+item\+\_\+of\+\_\+l\+\_\+sorter,  }\item[{\hyperlink{class_test_ad87ac75730f80ef0824f0c56ec7db12d}{triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$}]{\+\_\+pre\+\_\+item\+\_\+of\+\_\+s\+\_\+sorter,  }\item[{\hyperlink{class_test_aa25f2080d593eb18d6e5e475d99bac17}{pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$}]{\+\_\+pre\+\_\+item\+\_\+of\+\_\+lms\+\_\+sorter }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

vaildate preceding items

\subsection{Member Data Documentation}
\mbox{\Hypertarget{class_test_aba44b9a05184fb5f62f4901fd607da40}\label{class_test_aba44b9a05184fb5f62f4901fd607da40}} 
\index{Test@{Test}!m\+\_\+lcp@{m\+\_\+lcp}}
\index{m\+\_\+lcp@{m\+\_\+lcp}!Test@{Test}}
\subsubsection{\texorpdfstring{m\+\_\+lcp}{m\_lcp}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
size\+\_\+type$\ast$ \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::m\+\_\+lcp\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_test_a94d43daa04ae5011cc46d8fd3dc8c83b}\label{class_test_a94d43daa04ae5011cc46d8fd3dc8c83b}} 
\index{Test@{Test}!m\+\_\+lcp\+\_\+lms@{m\+\_\+lcp\+\_\+lms}}
\index{m\+\_\+lcp\+\_\+lms@{m\+\_\+lcp\+\_\+lms}!Test@{Test}}
\subsubsection{\texorpdfstring{m\+\_\+lcp\+\_\+lms}{m\_lcp\_lms}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
size\+\_\+type$\ast$ \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::m\+\_\+lcp\+\_\+lms\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_test_ac0031d768664e62b04aa14acaecdb354}\label{class_test_ac0031d768664e62b04aa14acaecdb354}} 
\index{Test@{Test}!m\+\_\+len@{m\+\_\+len}}
\index{m\+\_\+len@{m\+\_\+len}!Test@{Test}}
\subsubsection{\texorpdfstring{m\+\_\+len}{m\_len}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::m\+\_\+len\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_test_a3a2c92b2ace889d7c98d1188ee2542c5}\label{class_test_a3a2c92b2ace889d7c98d1188ee2542c5}} 
\index{Test@{Test}!m\+\_\+lms\+\_\+num@{m\+\_\+lms\+\_\+num}}
\index{m\+\_\+lms\+\_\+num@{m\+\_\+lms\+\_\+num}!Test@{Test}}
\subsubsection{\texorpdfstring{m\+\_\+lms\+\_\+num}{m\_lms\_num}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::m\+\_\+lms\+\_\+num\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_test_a2992148c8dda566ae4f4ebbdb26bdccd}\label{class_test_a2992148c8dda566ae4f4ebbdb26bdccd}} 
\index{Test@{Test}!m\+\_\+s@{m\+\_\+s}}
\index{m\+\_\+s@{m\+\_\+s}!Test@{Test}}
\subsubsection{\texorpdfstring{m\+\_\+s}{m\_s}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
alphabet\+\_\+type$\ast$ \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::m\+\_\+s\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_test_a38956729bdb63c0bfe7760e827769309}\label{class_test_a38956729bdb63c0bfe7760e827769309}} 
\index{Test@{Test}!m\+\_\+sa@{m\+\_\+sa}}
\index{m\+\_\+sa@{m\+\_\+sa}!Test@{Test}}
\subsubsection{\texorpdfstring{m\+\_\+sa}{m\_sa}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
size\+\_\+type$\ast$ \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::m\+\_\+sa\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_test_a557862839f4ead2e08d12e7770340ded}\label{class_test_a557862839f4ead2e08d12e7770340ded}} 
\index{Test@{Test}!m\+\_\+sa\+\_\+lms@{m\+\_\+sa\+\_\+lms}}
\index{m\+\_\+sa\+\_\+lms@{m\+\_\+sa\+\_\+lms}!Test@{Test}}
\subsubsection{\texorpdfstring{m\+\_\+sa\+\_\+lms}{m\_sa\_lms}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
size\+\_\+type$\ast$ \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::m\+\_\+sa\+\_\+lms\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_test_ad5db148e90886fc6524a1f07194df9a9}\label{class_test_ad5db148e90886fc6524a1f07194df9a9}} 
\index{Test@{Test}!m\+\_\+t@{m\+\_\+t}}
\index{m\+\_\+t@{m\+\_\+t}!Test@{Test}}
\subsubsection{\texorpdfstring{m\+\_\+t}{m\_t}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$ \\
\hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8}$\ast$ \hyperlink{class_test}{Test}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::m\+\_\+t\hspace{0.3cm}{\ttfamily [private]}}

The documentation for this class was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/\hyperlink{test_8h}{test.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/class_validate.tex
2017/01/24

\hypertarget{class_validate}{}\section{Validate$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$ Class Template Reference}
\label{class_validate}\index{Validate$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$@{Validate$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$}}

validate suffix and L\+CP arrays using Karp-\/\+Rarbin finger-\/printing function

{\ttfamily \#include $<$validate.\+h$>$}

\subsection*{Classes}
\begin{DoxyCompactItemize}
\item 
struct \hyperlink{struct_validate_1_1_r_interval}{R\+Interval}
\begin{DoxyCompactList}\small\item\em store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, ... \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{class_validate_a93b53c001ce92ccad38fe371e9df77b4}{Validate} (const std\+::string \&\+\_\+t\+\_\+fn, const std\+::string \&\+\_\+sa\+\_\+fn, const std\+::string \&\+\_\+lcp\+\_\+fn)
\begin{DoxyCompactList}\small\item\em constructor \end{DoxyCompactList}\item 
\hyperlink{class_validate_a991e319d335c6f666f0058be4f73fc97}{$\sim$\+Validate} ()
\begin{DoxyCompactList}\small\item\em destrcutor \end{DoxyCompactList}\item 
bool \hyperlink{class_validate_ab94f0feab53136b137c432332efa1ff3}{run} ()
\begin{DoxyCompactList}\small\item\em main program portal \end{DoxyCompactList}\item 
bool \hyperlink{class_validate_a3d560deb2bd3e2984f6f3b8b8b766904}{check\+\_\+block} (\hyperlink{tuples_8h_a80f1b898df1006722612d5ecf89cd4d7}{std\+::pair}$<$ size\+\_\+type, \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} $>$ $\ast$\+\_\+pair1\+\_\+block, \hyperlink{tuples_8h_a80f1b898df1006722612d5ecf89cd4d7}{std\+::pair}$<$ size\+\_\+type, \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} $>$ $\ast$\+\_\+pair2\+\_\+block, \hyperlink{tuples_8h_a80f1b898df1006722612d5ecf89cd4d7}{std\+::pair}$<$ size\+\_\+type, \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} $>$ $\ast$\+\_\+pair3\+\_\+block, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+item\+\_\+num, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+block\+\_\+id, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+block\+\_\+capacity, const bool \+\_\+is\+\_\+rightmost)
\begin{DoxyCompactList}\small\item\em check an sa/lcp block \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Private Types}
\begin{DoxyCompactItemize}
\item 
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$ alphabet\+\_\+type $>$\+::vector \hyperlink{class_validate_a0323dd6f1096806748299dfd4f644b69}{alphabet\+\_\+vector\+\_\+type}
\item 
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$ size\+\_\+type $>$\+::vector \hyperlink{class_validate_a3725fcfd4a55e4d8edc8b5d5955c081d}{size\+\_\+vector\+\_\+type}
\end{DoxyCompactItemize}
\subsection*{Private Attributes}
\begin{DoxyCompactItemize}
\item 
std\+::string \hyperlink{class_validate_a8038ca0a43b122fd9e08af72d7789611}{m\+\_\+t\+\_\+fn}
\begin{DoxyCompactList}\small\item\em file name of t array \end{DoxyCompactList}\item 
std\+::string \hyperlink{class_validate_aa7c887cf55845b0214e8db3af1076283}{m\+\_\+sa\+\_\+fn}
\begin{DoxyCompactList}\small\item\em file name of sa array \end{DoxyCompactList}\item 
std\+::string \hyperlink{class_validate_a8bbe1b0a3990ebae85d352bcce9da755}{m\+\_\+lcp\+\_\+fn}
\begin{DoxyCompactList}\small\item\em file name of lcp array \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate_a49a048e8046e03c3fbc7251bb9af87fd}{m\+\_\+len}
\begin{DoxyCompactList}\small\item\em length of input t/sa/lcp \end{DoxyCompactList}\item 
\hyperlink{struct_validate_1_1_r_interval}{R\+Interval} $\ast$ \hyperlink{class_validate_aaa32f94ddccccccd3d86897996c323cc}{m\+\_\+rinterval}
\item 
alphabet\+\_\+type \hyperlink{class_validate_abc933d4475a6b952888ee423c3228fc9}{m\+\_\+pre\+\_\+ch}
\item 
\hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} \hyperlink{class_validate_a767b5f07008091d4191201c07ad9a3cd}{m\+\_\+pre\+\_\+fp\+\_\+interval}
\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename alphabet\+\_\+type, typename size\+\_\+type, typename offset\+\_\+type$>$\newline
class Validate$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$}

validate suffix and L\+CP arrays using Karp-\/\+Rarbin finger-\/printing function

\subsection{Member Typedef Documentation}
\mbox{\Hypertarget{class_validate_a0323dd6f1096806748299dfd4f644b69}\label{class_validate_a0323dd6f1096806748299dfd4f644b69}} 
\index{Validate@{Validate}!alphabet\+\_\+vector\+\_\+type@{alphabet\+\_\+vector\+\_\+type}}
\index{alphabet\+\_\+vector\+\_\+type@{alphabet\+\_\+vector\+\_\+type}!Validate@{Validate}}
\subsubsection{\texorpdfstring{alphabet\+\_\+vector\+\_\+type}{alphabet\_vector\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type , typename offset\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$alphabet\+\_\+type$>$\+::vector \hyperlink{class_validate}{Validate}$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::\hyperlink{class_validate_a0323dd6f1096806748299dfd4f644b69}{alphabet\+\_\+vector\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate_a3725fcfd4a55e4d8edc8b5d5955c081d}\label{class_validate_a3725fcfd4a55e4d8edc8b5d5955c081d}} 
\index{Validate@{Validate}!size\+\_\+vector\+\_\+type@{size\+\_\+vector\+\_\+type}}
\index{size\+\_\+vector\+\_\+type@{size\+\_\+vector\+\_\+type}!Validate@{Validate}}
\subsubsection{\texorpdfstring{size\+\_\+vector\+\_\+type}{size\_vector\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type , typename offset\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$size\+\_\+type$>$\+::vector \hyperlink{class_validate}{Validate}$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::\hyperlink{class_validate_a3725fcfd4a55e4d8edc8b5d5955c081d}{size\+\_\+vector\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{class_validate_a93b53c001ce92ccad38fe371e9df77b4}\label{class_validate_a93b53c001ce92ccad38fe371e9df77b4}} 
\index{Validate@{Validate}!Validate@{Validate}}
\index{Validate@{Validate}!Validate@{Validate}}
\subsubsection{\texorpdfstring{Validate()}{Validate()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type , typename offset\+\_\+type $>$ \\
\hyperlink{class_validate}{Validate}$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::\hyperlink{class_validate}{Validate} (\begin{DoxyParamCaption}\item[{const std\+::string \&}]{\+\_\+t\+\_\+fn,  }\item[{const std\+::string \&}]{\+\_\+sa\+\_\+fn,  }\item[{const std\+::string \&}]{\+\_\+lcp\+\_\+fn }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor

\mbox{\Hypertarget{class_validate_a991e319d335c6f666f0058be4f73fc97}\label{class_validate_a991e319d335c6f666f0058be4f73fc97}} 
\index{Validate@{Validate}!````~Validate@{$\sim$\+Validate}}
\index{````~Validate@{$\sim$\+Validate}!Validate@{Validate}}
\subsubsection{\texorpdfstring{$\sim$\+Validate()}{~Validate()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type , typename offset\+\_\+type $>$ \\
\hyperlink{class_validate}{Validate}$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::$\sim$\hyperlink{class_validate}{Validate} (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

destrcutor

\subsection{Member Function Documentation}
\mbox{\Hypertarget{class_validate_a3d560deb2bd3e2984f6f3b8b8b766904}\label{class_validate_a3d560deb2bd3e2984f6f3b8b8b766904}} 
\index{Validate@{Validate}!check\+\_\+block@{check\+\_\+block}}
\index{check\+\_\+block@{check\+\_\+block}!Validate@{Validate}}
\subsubsection{\texorpdfstring{check\+\_\+block()}{check\_block()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type , typename offset\+\_\+type $>$ \\
bool \hyperlink{class_validate}{Validate}$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::check\+\_\+block (\begin{DoxyParamCaption}\item[{\hyperlink{tuples_8h_a80f1b898df1006722612d5ecf89cd4d7}{std\+::pair}$<$ size\+\_\+type, \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} $>$ $\ast$}]{\+\_\+pair1\+\_\+block,  }\item[{\hyperlink{tuples_8h_a80f1b898df1006722612d5ecf89cd4d7}{std\+::pair}$<$ size\+\_\+type, \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} $>$ $\ast$}]{\+\_\+pair2\+\_\+block,  }\item[{\hyperlink{tuples_8h_a80f1b898df1006722612d5ecf89cd4d7}{std\+::pair}$<$ size\+\_\+type, \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} $>$ $\ast$}]{\+\_\+pair3\+\_\+block,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+item\+\_\+num,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+block\+\_\+id,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+block\+\_\+capacity,  }\item[{const bool}]{\+\_\+is\+\_\+rightmost }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

check an sa/lcp block

\mbox{\Hypertarget{class_validate_ab94f0feab53136b137c432332efa1ff3}\label{class_validate_ab94f0feab53136b137c432332efa1ff3}} 
\index{Validate@{Validate}!run@{run}}
\index{run@{run}!Validate@{Validate}}
\subsubsection{\texorpdfstring{run()}{run()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type , typename offset\+\_\+type $>$ \\
bool \hyperlink{class_validate}{Validate}$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::run (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

main program portal

Parition sa and lcp into multiple block Tackle each piece individually.

\subsection{Member Data Documentation}
\mbox{\Hypertarget{class_validate_a8bbe1b0a3990ebae85d352bcce9da755}\label{class_validate_a8bbe1b0a3990ebae85d352bcce9da755}} 
\index{Validate@{Validate}!m\+\_\+lcp\+\_\+fn@{m\+\_\+lcp\+\_\+fn}}
\index{m\+\_\+lcp\+\_\+fn@{m\+\_\+lcp\+\_\+fn}!Validate@{Validate}}
\subsubsection{\texorpdfstring{m\+\_\+lcp\+\_\+fn}{m\_lcp\_fn}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type , typename offset\+\_\+type $>$ \\
std\+::string \hyperlink{class_validate}{Validate}$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::m\+\_\+lcp\+\_\+fn\hspace{0.3cm}{\ttfamily [private]}}

file name of lcp array

\mbox{\Hypertarget{class_validate_a49a048e8046e03c3fbc7251bb9af87fd}\label{class_validate_a49a048e8046e03c3fbc7251bb9af87fd}} 
\index{Validate@{Validate}!m\+\_\+len@{m\+\_\+len}}
\index{m\+\_\+len@{m\+\_\+len}!Validate@{Validate}}
\subsubsection{\texorpdfstring{m\+\_\+len}{m\_len}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type , typename offset\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate}{Validate}$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::m\+\_\+len\hspace{0.3cm}{\ttfamily [private]}}

length of input t/sa/lcp

\mbox{\Hypertarget{class_validate_abc933d4475a6b952888ee423c3228fc9}\label{class_validate_abc933d4475a6b952888ee423c3228fc9}} 
\index{Validate@{Validate}!m\+\_\+pre\+\_\+ch@{m\+\_\+pre\+\_\+ch}}
\index{m\+\_\+pre\+\_\+ch@{m\+\_\+pre\+\_\+ch}!Validate@{Validate}}
\subsubsection{\texorpdfstring{m\+\_\+pre\+\_\+ch}{m\_pre\_ch}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type , typename offset\+\_\+type $>$ \\
alphabet\+\_\+type \hyperlink{class_validate}{Validate}$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::m\+\_\+pre\+\_\+ch\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate_a767b5f07008091d4191201c07ad9a3cd}\label{class_validate_a767b5f07008091d4191201c07ad9a3cd}} 
\index{Validate@{Validate}!m\+\_\+pre\+\_\+fp\+\_\+interval@{m\+\_\+pre\+\_\+fp\+\_\+interval}}
\index{m\+\_\+pre\+\_\+fp\+\_\+interval@{m\+\_\+pre\+\_\+fp\+\_\+interval}!Validate@{Validate}}
\subsubsection{\texorpdfstring{m\+\_\+pre\+\_\+fp\+\_\+interval}{m\_pre\_fp\_interval}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type , typename offset\+\_\+type $>$ \\
\hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} \hyperlink{class_validate}{Validate}$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::m\+\_\+pre\+\_\+fp\+\_\+interval\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate_aaa32f94ddccccccd3d86897996c323cc}\label{class_validate_aaa32f94ddccccccd3d86897996c323cc}} 
\index{Validate@{Validate}!m\+\_\+rinterval@{m\+\_\+rinterval}}
\index{m\+\_\+rinterval@{m\+\_\+rinterval}!Validate@{Validate}}
\subsubsection{\texorpdfstring{m\+\_\+rinterval}{m\_rinterval}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type , typename offset\+\_\+type $>$ \\
\hyperlink{struct_validate_1_1_r_interval}{R\+Interval}$\ast$ \hyperlink{class_validate}{Validate}$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::m\+\_\+rinterval\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate_aa7c887cf55845b0214e8db3af1076283}\label{class_validate_aa7c887cf55845b0214e8db3af1076283}} 
\index{Validate@{Validate}!m\+\_\+sa\+\_\+fn@{m\+\_\+sa\+\_\+fn}}
\index{m\+\_\+sa\+\_\+fn@{m\+\_\+sa\+\_\+fn}!Validate@{Validate}}
\subsubsection{\texorpdfstring{m\+\_\+sa\+\_\+fn}{m\_sa\_fn}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type , typename offset\+\_\+type $>$ \\
std\+::string \hyperlink{class_validate}{Validate}$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::m\+\_\+sa\+\_\+fn\hspace{0.3cm}{\ttfamily [private]}}

file name of sa array

\mbox{\Hypertarget{class_validate_a8038ca0a43b122fd9e08af72d7789611}\label{class_validate_a8038ca0a43b122fd9e08af72d7789611}} 
\index{Validate@{Validate}!m\+\_\+t\+\_\+fn@{m\+\_\+t\+\_\+fn}}
\index{m\+\_\+t\+\_\+fn@{m\+\_\+t\+\_\+fn}!Validate@{Validate}}
\subsubsection{\texorpdfstring{m\+\_\+t\+\_\+fn}{m\_t\_fn}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type , typename offset\+\_\+type $>$ \\
std\+::string \hyperlink{class_validate}{Validate}$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::m\+\_\+t\+\_\+fn\hspace{0.3cm}{\ttfamily [private]}}

file name of t array

The documentation for this class was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/\hyperlink{validate_8h}{validate.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/class_validate2.tex
2017/01/24

\hypertarget{class_validate2}{}\section{Validate2$<$ alphabet\+\_\+type, size\+\_\+type $>$ Class Template Reference}
\label{class_validate2}\index{Validate2$<$ alphabet\+\_\+type, size\+\_\+type $>$@{Validate2$<$ alphabet\+\_\+type, size\+\_\+type $>$}}

a suffix and L\+CP array validater

{\ttfamily \#include $<$validate2.\+h$>$}

\subsection*{Classes}
\begin{DoxyCompactItemize}
\item 
struct \hyperlink{struct_validate2_1_1_r_interval}{R\+Interval}
\begin{DoxyCompactList}\small\item\em store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, ... \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{class_validate2_a003e523f9fb81a2d6a465d6cec444c1f}{Validate2} (const std\+::string \&\+\_\+t\+\_\+fn, const std\+::string \&\+\_\+sa\+\_\+fn, const std\+::string \&\+\_\+lcp\+\_\+fn)
\begin{DoxyCompactList}\small\item\em constructor \end{DoxyCompactList}\item 
bool \hyperlink{class_validate2_aa93abe8bbd0bbdaebd1b5a1c5a4c66df}{run} ()
\begin{DoxyCompactList}\small\item\em run the core part \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Private Types}
\begin{DoxyCompactItemize}
\item 
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$ size\+\_\+type $>$\+::vector \hyperlink{class_validate2_a8dab9b86f9c73419431821ebb68852c5}{size\+\_\+vector\+\_\+type}
\item 
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$ alphabet\+\_\+type $>$\+::vector \hyperlink{class_validate2_a351a2e7bbfdf9b87ecbb4f08cdbc1e64}{alphabet\+\_\+vector\+\_\+type}
\end{DoxyCompactItemize}
\subsection*{Private Attributes}
\begin{DoxyCompactItemize}
\item 
std\+::string \hyperlink{class_validate2_aefa1d9c5ac628be8be94f03668782e07}{m\+\_\+t\+\_\+fn}
\begin{DoxyCompactList}\small\item\em file name of input string \end{DoxyCompactList}\item 
std\+::string \hyperlink{class_validate2_a50d06103a2020809e3e6848732870df1}{m\+\_\+sa\+\_\+fn}
\begin{DoxyCompactList}\small\item\em file name of suffix array \end{DoxyCompactList}\item 
std\+::string \hyperlink{class_validate2_abe354af8e4d3c9d59fe1898ca9ee9b45}{m\+\_\+lcp\+\_\+fn}
\begin{DoxyCompactList}\small\item\em file name of lcp array \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate2_a64e02ffca40be106951a2325bc9d24e6}{m\+\_\+len}
\begin{DoxyCompactList}\small\item\em length of input string \end{DoxyCompactList}\item 
\hyperlink{struct_validate2_1_1_r_interval}{R\+Interval} $\ast$ \hyperlink{class_validate2_a1beb0a916dd1ad049b3b59f5058c5bb4}{m\+\_\+rinterval}
\begin{DoxyCompactList}\small\item\em pointer to an instance of \hyperlink{struct_validate2_1_1_r_interval}{R\+Interval} \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename alphabet\+\_\+type, typename size\+\_\+type$>$\newline
class Validate2$<$ alphabet\+\_\+type, size\+\_\+type $>$}

a suffix and L\+CP array validater

\subsection{Member Typedef Documentation}
\mbox{\Hypertarget{class_validate2_a351a2e7bbfdf9b87ecbb4f08cdbc1e64}\label{class_validate2_a351a2e7bbfdf9b87ecbb4f08cdbc1e64}} 
\index{Validate2@{Validate2}!alphabet\+\_\+vector\+\_\+type@{alphabet\+\_\+vector\+\_\+type}}
\index{alphabet\+\_\+vector\+\_\+type@{alphabet\+\_\+vector\+\_\+type}!Validate2@{Validate2}}
\subsubsection{\texorpdfstring{alphabet\+\_\+vector\+\_\+type}{alphabet\_vector\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$alphabet\+\_\+type$>$\+::vector \hyperlink{class_validate2}{Validate2}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate2_a351a2e7bbfdf9b87ecbb4f08cdbc1e64}{alphabet\+\_\+vector\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate2_a8dab9b86f9c73419431821ebb68852c5}\label{class_validate2_a8dab9b86f9c73419431821ebb68852c5}} 
\index{Validate2@{Validate2}!size\+\_\+vector\+\_\+type@{size\+\_\+vector\+\_\+type}}
\index{size\+\_\+vector\+\_\+type@{size\+\_\+vector\+\_\+type}!Validate2@{Validate2}}
\subsubsection{\texorpdfstring{size\+\_\+vector\+\_\+type}{size\_vector\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$size\+\_\+type$>$\+::vector \hyperlink{class_validate2}{Validate2}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate2_a8dab9b86f9c73419431821ebb68852c5}{size\+\_\+vector\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{class_validate2_a003e523f9fb81a2d6a465d6cec444c1f}\label{class_validate2_a003e523f9fb81a2d6a465d6cec444c1f}} 
\index{Validate2@{Validate2}!Validate2@{Validate2}}
\index{Validate2@{Validate2}!Validate2@{Validate2}}
\subsubsection{\texorpdfstring{Validate2()}{Validate2()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate2}{Validate2}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate2}{Validate2} (\begin{DoxyParamCaption}\item[{const std\+::string \&}]{\+\_\+t\+\_\+fn,  }\item[{const std\+::string \&}]{\+\_\+sa\+\_\+fn,  }\item[{const std\+::string \&}]{\+\_\+lcp\+\_\+fn }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor

\subsection{Member Function Documentation}
\mbox{\Hypertarget{class_validate2_aa93abe8bbd0bbdaebd1b5a1c5a4c66df}\label{class_validate2_aa93abe8bbd0bbdaebd1b5a1c5a4c66df}} 
\index{Validate2@{Validate2}!run@{run}}
\index{run@{run}!Validate2@{Validate2}}
\subsubsection{\texorpdfstring{run()}{run()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
bool \hyperlink{class_validate2}{Validate2}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::run (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

run the core part

\subsection{Member Data Documentation}
\mbox{\Hypertarget{class_validate2_abe354af8e4d3c9d59fe1898ca9ee9b45}\label{class_validate2_abe354af8e4d3c9d59fe1898ca9ee9b45}} 
\index{Validate2@{Validate2}!m\+\_\+lcp\+\_\+fn@{m\+\_\+lcp\+\_\+fn}}
\index{m\+\_\+lcp\+\_\+fn@{m\+\_\+lcp\+\_\+fn}!Validate2@{Validate2}}
\subsubsection{\texorpdfstring{m\+\_\+lcp\+\_\+fn}{m\_lcp\_fn}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
std\+::string \hyperlink{class_validate2}{Validate2}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::m\+\_\+lcp\+\_\+fn\hspace{0.3cm}{\ttfamily [private]}}

file name of lcp array

\mbox{\Hypertarget{class_validate2_a64e02ffca40be106951a2325bc9d24e6}\label{class_validate2_a64e02ffca40be106951a2325bc9d24e6}} 
\index{Validate2@{Validate2}!m\+\_\+len@{m\+\_\+len}}
\index{m\+\_\+len@{m\+\_\+len}!Validate2@{Validate2}}
\subsubsection{\texorpdfstring{m\+\_\+len}{m\_len}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate2}{Validate2}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::m\+\_\+len\hspace{0.3cm}{\ttfamily [private]}}

length of input string

\mbox{\Hypertarget{class_validate2_a1beb0a916dd1ad049b3b59f5058c5bb4}\label{class_validate2_a1beb0a916dd1ad049b3b59f5058c5bb4}} 
\index{Validate2@{Validate2}!m\+\_\+rinterval@{m\+\_\+rinterval}}
\index{m\+\_\+rinterval@{m\+\_\+rinterval}!Validate2@{Validate2}}
\subsubsection{\texorpdfstring{m\+\_\+rinterval}{m\_rinterval}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{struct_validate2_1_1_r_interval}{R\+Interval}$\ast$ \hyperlink{class_validate2}{Validate2}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::m\+\_\+rinterval\hspace{0.3cm}{\ttfamily [private]}}

pointer to an instance of \hyperlink{struct_validate2_1_1_r_interval}{R\+Interval}

\mbox{\Hypertarget{class_validate2_a50d06103a2020809e3e6848732870df1}\label{class_validate2_a50d06103a2020809e3e6848732870df1}} 
\index{Validate2@{Validate2}!m\+\_\+sa\+\_\+fn@{m\+\_\+sa\+\_\+fn}}
\index{m\+\_\+sa\+\_\+fn@{m\+\_\+sa\+\_\+fn}!Validate2@{Validate2}}
\subsubsection{\texorpdfstring{m\+\_\+sa\+\_\+fn}{m\_sa\_fn}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
std\+::string \hyperlink{class_validate2}{Validate2}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::m\+\_\+sa\+\_\+fn\hspace{0.3cm}{\ttfamily [private]}}

file name of suffix array

\mbox{\Hypertarget{class_validate2_aefa1d9c5ac628be8be94f03668782e07}\label{class_validate2_aefa1d9c5ac628be8be94f03668782e07}} 
\index{Validate2@{Validate2}!m\+\_\+t\+\_\+fn@{m\+\_\+t\+\_\+fn}}
\index{m\+\_\+t\+\_\+fn@{m\+\_\+t\+\_\+fn}!Validate2@{Validate2}}
\subsubsection{\texorpdfstring{m\+\_\+t\+\_\+fn}{m\_t\_fn}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
std\+::string \hyperlink{class_validate2}{Validate2}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::m\+\_\+t\+\_\+fn\hspace{0.3cm}{\ttfamily [private]}}

file name of input string

The documentation for this class was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/\hyperlink{validate2_8h}{validate2.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/class_validate3.tex
2017/01/24

\hypertarget{class_validate3}{}\section{Validate3$<$ alphabet\+\_\+type, size\+\_\+type $>$ Class Template Reference}
\label{class_validate3}\index{Validate3$<$ alphabet\+\_\+type, size\+\_\+type $>$@{Validate3$<$ alphabet\+\_\+type, size\+\_\+type $>$}}

validate sa and lcp using Karp-\/\+Rabin fingerprinting function

{\ttfamily \#include $<$validate3.\+h$>$}

\subsection*{Classes}
\begin{DoxyCompactItemize}
\item 
struct \hyperlink{struct_validate3_1_1_r_interval}{R\+Interval}
\begin{DoxyCompactList}\small\item\em store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, ... \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{class_validate3_ab0a59632c6e2b3bfdd0bf89483448d46}{Validate3} (const std\+::string \&\+\_\+t\+\_\+fn, const std\+::string \&\+\_\+sa\+\_\+fn, const std\+::string \&\+\_\+lcp\+\_\+fn)
\begin{DoxyCompactList}\small\item\em constructor \end{DoxyCompactList}\item 
bool \hyperlink{class_validate3_aaa21653a363d5adcc65b93ac34d22253}{run} ()
\begin{DoxyCompactList}\small\item\em core part of the program \end{DoxyCompactList}\item 
\hyperlink{class_validate3_a3a7778ec3337ed3baf9a7515cf0a94ad}{pair2\+\_\+sorter\+\_\+type} $\ast$ \hyperlink{class_validate3_ad41c23715467e5201ef2705d38d8f81d}{fetch\+\_\+fp} ()
\begin{DoxyCompactList}\small\item\em fetch fp\mbox{[}0, sa\mbox{[}i\mbox{]} -\/ 1\mbox{]} \end{DoxyCompactList}\item 
\hyperlink{class_validate3_ab3d4fd99ae8b2967f0b64b71a28efc66}{triple\+\_\+sorter\+\_\+type} $\ast$ \hyperlink{class_validate3_aeace570606a0320e2ad458145b7e16e3}{fetch\+\_\+fp\+\_\+ch\+\_\+cur} ()
\begin{DoxyCompactList}\small\item\em fetch fp\mbox{[}0, sa\mbox{[}i\mbox{]} + lcp\mbox{[}i\mbox{]} -\/ 1\mbox{]} and t\mbox{[}sa\mbox{[}i\mbox{]} + lcp\mbox{[}i\mbox{]}\mbox{]} \end{DoxyCompactList}\item 
\hyperlink{class_validate3_ab3d4fd99ae8b2967f0b64b71a28efc66}{triple\+\_\+sorter\+\_\+type} $\ast$ \hyperlink{class_validate3_abbf26d49c2f60ea8ecb3ba131f0a61ae}{fetch\+\_\+fp\+\_\+ch\+\_\+pre} ()
\begin{DoxyCompactList}\small\item\em fetch fp\mbox{[}0, sa\mbox{[}i -\/ 1\mbox{]} + lcp\mbox{[}i\mbox{]} -\/ 1\mbox{]} and t\mbox{[}sa\mbox{[}i -\/ 1\mbox{]} + lcp\mbox{[}i\mbox{]}\mbox{]} \end{DoxyCompactList}\item 
bool \hyperlink{class_validate3_ade475094c421af71da65620b706dec3f}{check} (\hyperlink{class_validate3_a3a7778ec3337ed3baf9a7515cf0a94ad}{pair2\+\_\+sorter\+\_\+type} $\ast$\+\_\+sorter1, \hyperlink{class_validate3_ab3d4fd99ae8b2967f0b64b71a28efc66}{triple\+\_\+sorter\+\_\+type} $\ast$\+\_\+sorter2, \hyperlink{class_validate3_ab3d4fd99ae8b2967f0b64b71a28efc66}{triple\+\_\+sorter\+\_\+type} $\ast$\+\_\+sorter3)
\begin{DoxyCompactList}\small\item\em compare range fingerprints and ending characters to check the result \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Private Types}
\begin{DoxyCompactItemize}
\item 
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$ alphabet\+\_\+type $>$\+::vector \hyperlink{class_validate3_a7a893a89f745710a34958b37717cb024}{alphabet\+\_\+vector\+\_\+type}
\item 
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$ size\+\_\+type $>$\+::vector \hyperlink{class_validate3_a9dcb1d691c20940089a7e6fbf1619069}{size\+\_\+vector\+\_\+type}
\item 
typedef \hyperlink{structpair}{pair}$<$ size\+\_\+type, size\+\_\+type $>$ \hyperlink{class_validate3_abecec0e807ea06aac66c60387611e78a}{pair1\+\_\+type}
\item 
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$ \hyperlink{class_validate3_abecec0e807ea06aac66c60387611e78a}{pair1\+\_\+type} $>$ \hyperlink{class_validate3_ace20fdc998ec6fb2c559aaf7413d464e}{pair1\+\_\+comparator\+\_\+type}
\item 
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$ \hyperlink{class_validate3_abecec0e807ea06aac66c60387611e78a}{pair1\+\_\+type}, \hyperlink{class_validate3_ace20fdc998ec6fb2c559aaf7413d464e}{pair1\+\_\+comparator\+\_\+type} $>$\+::sorter \hyperlink{class_validate3_a6b5f6c01fe108e6c572c52249bf37caa}{pair1\+\_\+sorter\+\_\+type}
\item 
typedef \hyperlink{structpair}{pair}$<$ size\+\_\+type, \hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} $>$ \hyperlink{class_validate3_aa5a02458227330cbaaf91b58684625f0}{pair2\+\_\+type}
\item 
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$ \hyperlink{class_validate3_aa5a02458227330cbaaf91b58684625f0}{pair2\+\_\+type} $>$ \hyperlink{class_validate3_a9a5316faa3c44f8f5743fec09cdea491}{pair2\+\_\+comparator\+\_\+type}
\item 
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$ \hyperlink{class_validate3_aa5a02458227330cbaaf91b58684625f0}{pair2\+\_\+type}, \hyperlink{class_validate3_a9a5316faa3c44f8f5743fec09cdea491}{pair2\+\_\+comparator\+\_\+type} $>$\+::sorter \hyperlink{class_validate3_a3a7778ec3337ed3baf9a7515cf0a94ad}{pair2\+\_\+sorter\+\_\+type}
\item 
typedef \hyperlink{structtriple}{triple}$<$ size\+\_\+type, \hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type}, \hyperlink{types_8h_aea9840dd402bd5d5201bef4633398cb3}{uint16} $>$ \hyperlink{class_validate3_a5f4a1e8af5876ec1bef35bd0c3068203}{triple\+\_\+type}
\item 
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$ \hyperlink{class_validate3_a5f4a1e8af5876ec1bef35bd0c3068203}{triple\+\_\+type} $>$ \hyperlink{class_validate3_a35d0df8691519c4413a99d0e5739be54}{triple\+\_\+comparator\+\_\+type}
\item 
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$ \hyperlink{class_validate3_a5f4a1e8af5876ec1bef35bd0c3068203}{triple\+\_\+type}, \hyperlink{class_validate3_a35d0df8691519c4413a99d0e5739be54}{triple\+\_\+comparator\+\_\+type} $>$\+::sorter \hyperlink{class_validate3_ab3d4fd99ae8b2967f0b64b71a28efc66}{triple\+\_\+sorter\+\_\+type}
\end{DoxyCompactItemize}
\subsection*{Private Attributes}
\begin{DoxyCompactItemize}
\item 
std\+::string \hyperlink{class_validate3_a6f754bab729d30bd1d600bee9b68c4c4}{m\+\_\+t\+\_\+fn}
\begin{DoxyCompactList}\small\item\em filename for intput string \end{DoxyCompactList}\item 
std\+::string \hyperlink{class_validate3_a2be6f4b53d68e4cecb67f40d73aec102}{m\+\_\+sa\+\_\+fn}
\begin{DoxyCompactList}\small\item\em filename for suffix array \end{DoxyCompactList}\item 
std\+::string \hyperlink{class_validate3_a9a5b2ec4499a2ce49c2697e5bc36c953}{m\+\_\+lcp\+\_\+fn}
\begin{DoxyCompactList}\small\item\em filename for L\+CP array \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate3_a20a6a7a05819b0830e92e78c13954921}{m\+\_\+len}
\item 
\hyperlink{struct_validate3_1_1_r_interval}{R\+Interval} $\ast$ \hyperlink{class_validate3_a70a0fb14cda49a88a90c2d426880adf0}{m\+\_\+rinterval}
\begin{DoxyCompactList}\small\item\em pointer to \hyperlink{struct_validate3_1_1_r_interval}{R\+Interval} object \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename alphabet\+\_\+type, typename size\+\_\+type$>$\newline
class Validate3$<$ alphabet\+\_\+type, size\+\_\+type $>$}

validate sa and lcp using Karp-\/\+Rabin fingerprinting function

type of elements in the input string and suffix/\+L\+CP array are specified by alphabet\+\_\+type and size\+\_\+type, respectively.

\subsection{Member Typedef Documentation}
\mbox{\Hypertarget{class_validate3_a7a893a89f745710a34958b37717cb024}\label{class_validate3_a7a893a89f745710a34958b37717cb024}} 
\index{Validate3@{Validate3}!alphabet\+\_\+vector\+\_\+type@{alphabet\+\_\+vector\+\_\+type}}
\index{alphabet\+\_\+vector\+\_\+type@{alphabet\+\_\+vector\+\_\+type}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{alphabet\+\_\+vector\+\_\+type}{alphabet\_vector\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$alphabet\+\_\+type$>$\+::vector \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate3_a7a893a89f745710a34958b37717cb024}{alphabet\+\_\+vector\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate3_ace20fdc998ec6fb2c559aaf7413d464e}\label{class_validate3_ace20fdc998ec6fb2c559aaf7413d464e}} 
\index{Validate3@{Validate3}!pair1\+\_\+comparator\+\_\+type@{pair1\+\_\+comparator\+\_\+type}}
\index{pair1\+\_\+comparator\+\_\+type@{pair1\+\_\+comparator\+\_\+type}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{pair1\+\_\+comparator\+\_\+type}{pair1\_comparator\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$\hyperlink{class_validate3_abecec0e807ea06aac66c60387611e78a}{pair1\+\_\+type}$>$ \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate3_ace20fdc998ec6fb2c559aaf7413d464e}{pair1\+\_\+comparator\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate3_a6b5f6c01fe108e6c572c52249bf37caa}\label{class_validate3_a6b5f6c01fe108e6c572c52249bf37caa}} 
\index{Validate3@{Validate3}!pair1\+\_\+sorter\+\_\+type@{pair1\+\_\+sorter\+\_\+type}}
\index{pair1\+\_\+sorter\+\_\+type@{pair1\+\_\+sorter\+\_\+type}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{pair1\+\_\+sorter\+\_\+type}{pair1\_sorter\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$\hyperlink{class_validate3_abecec0e807ea06aac66c60387611e78a}{pair1\+\_\+type}, \hyperlink{class_validate3_ace20fdc998ec6fb2c559aaf7413d464e}{pair1\+\_\+comparator\+\_\+type}$>$\+::sorter \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate3_a6b5f6c01fe108e6c572c52249bf37caa}{pair1\+\_\+sorter\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate3_abecec0e807ea06aac66c60387611e78a}\label{class_validate3_abecec0e807ea06aac66c60387611e78a}} 
\index{Validate3@{Validate3}!pair1\+\_\+type@{pair1\+\_\+type}}
\index{pair1\+\_\+type@{pair1\+\_\+type}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{pair1\+\_\+type}{pair1\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structpair}{pair}$<$size\+\_\+type, size\+\_\+type$>$ \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate3_abecec0e807ea06aac66c60387611e78a}{pair1\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate3_a9a5316faa3c44f8f5743fec09cdea491}\label{class_validate3_a9a5316faa3c44f8f5743fec09cdea491}} 
\index{Validate3@{Validate3}!pair2\+\_\+comparator\+\_\+type@{pair2\+\_\+comparator\+\_\+type}}
\index{pair2\+\_\+comparator\+\_\+type@{pair2\+\_\+comparator\+\_\+type}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{pair2\+\_\+comparator\+\_\+type}{pair2\_comparator\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$\hyperlink{class_validate3_aa5a02458227330cbaaf91b58684625f0}{pair2\+\_\+type}$>$ \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate3_a9a5316faa3c44f8f5743fec09cdea491}{pair2\+\_\+comparator\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate3_a3a7778ec3337ed3baf9a7515cf0a94ad}\label{class_validate3_a3a7778ec3337ed3baf9a7515cf0a94ad}} 
\index{Validate3@{Validate3}!pair2\+\_\+sorter\+\_\+type@{pair2\+\_\+sorter\+\_\+type}}
\index{pair2\+\_\+sorter\+\_\+type@{pair2\+\_\+sorter\+\_\+type}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{pair2\+\_\+sorter\+\_\+type}{pair2\_sorter\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$\hyperlink{class_validate3_aa5a02458227330cbaaf91b58684625f0}{pair2\+\_\+type}, \hyperlink{class_validate3_a9a5316faa3c44f8f5743fec09cdea491}{pair2\+\_\+comparator\+\_\+type}$>$\+::sorter \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate3_a3a7778ec3337ed3baf9a7515cf0a94ad}{pair2\+\_\+sorter\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate3_aa5a02458227330cbaaf91b58684625f0}\label{class_validate3_aa5a02458227330cbaaf91b58684625f0}} 
\index{Validate3@{Validate3}!pair2\+\_\+type@{pair2\+\_\+type}}
\index{pair2\+\_\+type@{pair2\+\_\+type}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{pair2\+\_\+type}{pair2\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structpair}{pair}$<$size\+\_\+type, \hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type}$>$ \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate3_aa5a02458227330cbaaf91b58684625f0}{pair2\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate3_a9dcb1d691c20940089a7e6fbf1619069}\label{class_validate3_a9dcb1d691c20940089a7e6fbf1619069}} 
\index{Validate3@{Validate3}!size\+\_\+vector\+\_\+type@{size\+\_\+vector\+\_\+type}}
\index{size\+\_\+vector\+\_\+type@{size\+\_\+vector\+\_\+type}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{size\+\_\+vector\+\_\+type}{size\_vector\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$size\+\_\+type$>$\+::vector \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate3_a9dcb1d691c20940089a7e6fbf1619069}{size\+\_\+vector\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate3_a35d0df8691519c4413a99d0e5739be54}\label{class_validate3_a35d0df8691519c4413a99d0e5739be54}} 
\index{Validate3@{Validate3}!triple\+\_\+comparator\+\_\+type@{triple\+\_\+comparator\+\_\+type}}
\index{triple\+\_\+comparator\+\_\+type@{triple\+\_\+comparator\+\_\+type}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{triple\+\_\+comparator\+\_\+type}{triple\_comparator\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$\hyperlink{class_validate3_a5f4a1e8af5876ec1bef35bd0c3068203}{triple\+\_\+type}$>$ \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate3_a35d0df8691519c4413a99d0e5739be54}{triple\+\_\+comparator\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate3_ab3d4fd99ae8b2967f0b64b71a28efc66}\label{class_validate3_ab3d4fd99ae8b2967f0b64b71a28efc66}} 
\index{Validate3@{Validate3}!triple\+\_\+sorter\+\_\+type@{triple\+\_\+sorter\+\_\+type}}
\index{triple\+\_\+sorter\+\_\+type@{triple\+\_\+sorter\+\_\+type}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{triple\+\_\+sorter\+\_\+type}{triple\_sorter\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$\hyperlink{class_validate3_a5f4a1e8af5876ec1bef35bd0c3068203}{triple\+\_\+type}, \hyperlink{class_validate3_a35d0df8691519c4413a99d0e5739be54}{triple\+\_\+comparator\+\_\+type}$>$\+::sorter \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate3_ab3d4fd99ae8b2967f0b64b71a28efc66}{triple\+\_\+sorter\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate3_a5f4a1e8af5876ec1bef35bd0c3068203}\label{class_validate3_a5f4a1e8af5876ec1bef35bd0c3068203}} 
\index{Validate3@{Validate3}!triple\+\_\+type@{triple\+\_\+type}}
\index{triple\+\_\+type@{triple\+\_\+type}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{triple\+\_\+type}{triple\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structtriple}{triple}$<$size\+\_\+type, \hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type}, \hyperlink{types_8h_aea9840dd402bd5d5201bef4633398cb3}{uint16}$>$ \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate3_a5f4a1e8af5876ec1bef35bd0c3068203}{triple\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{class_validate3_ab0a59632c6e2b3bfdd0bf89483448d46}\label{class_validate3_ab0a59632c6e2b3bfdd0bf89483448d46}} 
\index{Validate3@{Validate3}!Validate3@{Validate3}}
\index{Validate3@{Validate3}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{Validate3()}{Validate3()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate3}{Validate3} (\begin{DoxyParamCaption}\item[{const std\+::string \&}]{\+\_\+t\+\_\+fn,  }\item[{const std\+::string \&}]{\+\_\+sa\+\_\+fn,  }\item[{const std\+::string \&}]{\+\_\+lcp\+\_\+fn }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor

\begin{DoxyParams}{Parameters}
{\em \+\_\+t\+\_\+fn} & input string \\
\hline
{\em \+\_\+sa\+\_\+fn} & suffix array \\
\hline
{\em \+\_\+lcp\+\_\+fn} & lcp array \\
\hline
\end{DoxyParams}

\subsection{Member Function Documentation}
\mbox{\Hypertarget{class_validate3_ade475094c421af71da65620b706dec3f}\label{class_validate3_ade475094c421af71da65620b706dec3f}} 
\index{Validate3@{Validate3}!check@{check}}
\index{check@{check}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{check()}{check()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
bool \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::check (\begin{DoxyParamCaption}\item[{\hyperlink{class_validate3_a3a7778ec3337ed3baf9a7515cf0a94ad}{pair2\+\_\+sorter\+\_\+type} $\ast$}]{\+\_\+sorter1,  }\item[{\hyperlink{class_validate3_ab3d4fd99ae8b2967f0b64b71a28efc66}{triple\+\_\+sorter\+\_\+type} $\ast$}]{\+\_\+sorter2,  }\item[{\hyperlink{class_validate3_ab3d4fd99ae8b2967f0b64b71a28efc66}{triple\+\_\+sorter\+\_\+type} $\ast$}]{\+\_\+sorter3 }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

compare range fingerprints and ending characters to check the result

\mbox{\Hypertarget{class_validate3_ad41c23715467e5201ef2705d38d8f81d}\label{class_validate3_ad41c23715467e5201ef2705d38d8f81d}} 
\index{Validate3@{Validate3}!fetch\+\_\+fp@{fetch\+\_\+fp}}
\index{fetch\+\_\+fp@{fetch\+\_\+fp}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{fetch\+\_\+fp()}{fetch\_fp()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate3_a3a7778ec3337ed3baf9a7515cf0a94ad}{pair2\+\_\+sorter\+\_\+type}$\ast$ \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::fetch\+\_\+fp (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

fetch fp\mbox{[}0, sa\mbox{[}i\mbox{]} -\/ 1\mbox{]}

\mbox{\Hypertarget{class_validate3_aeace570606a0320e2ad458145b7e16e3}\label{class_validate3_aeace570606a0320e2ad458145b7e16e3}} 
\index{Validate3@{Validate3}!fetch\+\_\+fp\+\_\+ch\+\_\+cur@{fetch\+\_\+fp\+\_\+ch\+\_\+cur}}
\index{fetch\+\_\+fp\+\_\+ch\+\_\+cur@{fetch\+\_\+fp\+\_\+ch\+\_\+cur}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{fetch\+\_\+fp\+\_\+ch\+\_\+cur()}{fetch\_fp\_ch\_cur()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate3_ab3d4fd99ae8b2967f0b64b71a28efc66}{triple\+\_\+sorter\+\_\+type}$\ast$ \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::fetch\+\_\+fp\+\_\+ch\+\_\+cur (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

fetch fp\mbox{[}0, sa\mbox{[}i\mbox{]} + lcp\mbox{[}i\mbox{]} -\/ 1\mbox{]} and t\mbox{[}sa\mbox{[}i\mbox{]} + lcp\mbox{[}i\mbox{]}\mbox{]}

\mbox{\Hypertarget{class_validate3_abbf26d49c2f60ea8ecb3ba131f0a61ae}\label{class_validate3_abbf26d49c2f60ea8ecb3ba131f0a61ae}} 
\index{Validate3@{Validate3}!fetch\+\_\+fp\+\_\+ch\+\_\+pre@{fetch\+\_\+fp\+\_\+ch\+\_\+pre}}
\index{fetch\+\_\+fp\+\_\+ch\+\_\+pre@{fetch\+\_\+fp\+\_\+ch\+\_\+pre}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{fetch\+\_\+fp\+\_\+ch\+\_\+pre()}{fetch\_fp\_ch\_pre()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate3_ab3d4fd99ae8b2967f0b64b71a28efc66}{triple\+\_\+sorter\+\_\+type}$\ast$ \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::fetch\+\_\+fp\+\_\+ch\+\_\+pre (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

fetch fp\mbox{[}0, sa\mbox{[}i -\/ 1\mbox{]} + lcp\mbox{[}i\mbox{]} -\/ 1\mbox{]} and t\mbox{[}sa\mbox{[}i -\/ 1\mbox{]} + lcp\mbox{[}i\mbox{]}\mbox{]}

\mbox{\Hypertarget{class_validate3_aaa21653a363d5adcc65b93ac34d22253}\label{class_validate3_aaa21653a363d5adcc65b93ac34d22253}} 
\index{Validate3@{Validate3}!run@{run}}
\index{run@{run}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{run()}{run()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
bool \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::run (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

core part of the program

\subsection{Member Data Documentation}
\mbox{\Hypertarget{class_validate3_a9a5b2ec4499a2ce49c2697e5bc36c953}\label{class_validate3_a9a5b2ec4499a2ce49c2697e5bc36c953}} 
\index{Validate3@{Validate3}!m\+\_\+lcp\+\_\+fn@{m\+\_\+lcp\+\_\+fn}}
\index{m\+\_\+lcp\+\_\+fn@{m\+\_\+lcp\+\_\+fn}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{m\+\_\+lcp\+\_\+fn}{m\_lcp\_fn}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
std\+::string \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::m\+\_\+lcp\+\_\+fn\hspace{0.3cm}{\ttfamily [private]}}

filename for L\+CP array

\mbox{\Hypertarget{class_validate3_a20a6a7a05819b0830e92e78c13954921}\label{class_validate3_a20a6a7a05819b0830e92e78c13954921}} 
\index{Validate3@{Validate3}!m\+\_\+len@{m\+\_\+len}}
\index{m\+\_\+len@{m\+\_\+len}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{m\+\_\+len}{m\_len}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::m\+\_\+len\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate3_a70a0fb14cda49a88a90c2d426880adf0}\label{class_validate3_a70a0fb14cda49a88a90c2d426880adf0}} 
\index{Validate3@{Validate3}!m\+\_\+rinterval@{m\+\_\+rinterval}}
\index{m\+\_\+rinterval@{m\+\_\+rinterval}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{m\+\_\+rinterval}{m\_rinterval}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{struct_validate3_1_1_r_interval}{R\+Interval}$\ast$ \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::m\+\_\+rinterval\hspace{0.3cm}{\ttfamily [private]}}

pointer to \hyperlink{struct_validate3_1_1_r_interval}{R\+Interval} object

\mbox{\Hypertarget{class_validate3_a2be6f4b53d68e4cecb67f40d73aec102}\label{class_validate3_a2be6f4b53d68e4cecb67f40d73aec102}} 
\index{Validate3@{Validate3}!m\+\_\+sa\+\_\+fn@{m\+\_\+sa\+\_\+fn}}
\index{m\+\_\+sa\+\_\+fn@{m\+\_\+sa\+\_\+fn}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{m\+\_\+sa\+\_\+fn}{m\_sa\_fn}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
std\+::string \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::m\+\_\+sa\+\_\+fn\hspace{0.3cm}{\ttfamily [private]}}

filename for suffix array

\mbox{\Hypertarget{class_validate3_a6f754bab729d30bd1d600bee9b68c4c4}\label{class_validate3_a6f754bab729d30bd1d600bee9b68c4c4}} 
\index{Validate3@{Validate3}!m\+\_\+t\+\_\+fn@{m\+\_\+t\+\_\+fn}}
\index{m\+\_\+t\+\_\+fn@{m\+\_\+t\+\_\+fn}!Validate3@{Validate3}}
\subsubsection{\texorpdfstring{m\+\_\+t\+\_\+fn}{m\_t\_fn}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
std\+::string \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::m\+\_\+t\+\_\+fn\hspace{0.3cm}{\ttfamily [private]}}

filename for intput string

The documentation for this class was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/\hyperlink{validate3_8h}{validate3.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/class_validate4.tex
2017/01/24

\hypertarget{class_validate4}{}\section{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$ Class Template Reference}
\label{class_validate4}\index{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$@{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$}}

vaildate SA and L\+CP following the induced-\/sorting principle

{\ttfamily \#include $<$validate4.\+h$>$}

\subsection*{Classes}
\begin{DoxyCompactItemize}
\item 
struct \hyperlink{struct_validate4_1_1_bkt_info}{Bkt\+Info}
\begin{DoxyCompactList}\small\item\em record L-\/type, S-\/type and L\+MS bucket sizes (no matter empty or non-\/empty) in SA \& L\+CP \end{DoxyCompactList}\item 
struct \hyperlink{struct_validate4_1_1_l_m_s_validate}{L\+M\+S\+Validate}
\begin{DoxyCompactList}\small\item\em validate S\+A\+\_\+\+L\+MS \& L\+C\+P\+\_\+\+L\+MS \end{DoxyCompactList}\item 
struct \hyperlink{struct_validate4_1_1_l_scan}{L\+Scan}
\begin{DoxyCompactList}\small\item\em scan SA \& L\+CP rightward to validate the S\+A-\/values of all the S-\/type suffixes and the L\+C\+P-\/values of them and their left neighbor in SA. \end{DoxyCompactList}\item 
struct \hyperlink{struct_validate4_1_1_retrieve_pre}{Retrieve\+Pre}
\begin{DoxyCompactList}\small\item\em retrieve preceding items (pre\+\_\+ch \& pre\+\_\+t) for L-\/type, S-\/type and L\+MS suffixes \end{DoxyCompactList}\item 
struct \hyperlink{struct_validate4_1_1_r_m_q}{R\+MQ}
\begin{DoxyCompactList}\small\item\em \hyperlink{struct_validate4_1_1_r_m_q}{R\+MQ}. \end{DoxyCompactList}\item 
struct \hyperlink{struct_validate4_1_1_r_scan}{R\+Scan}
\begin{DoxyCompactList}\small\item\em scan SA rightward to validate the S\+A-\/values of all the L-\/type suffixes and the L\+C\+P-\/values of them and their left neighbors in SA. \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{class_validate4_aa1e9bf045b028c339da30db955857cb9}{Validate4} (const std\+::string \&\+\_\+t\+\_\+fn, const std\+::string \&\+\_\+sa\+\_\+fn, const std\+::string \&\+\_\+lcp\+\_\+fn)
\begin{DoxyCompactList}\small\item\em ctor \end{DoxyCompactList}\item 
bool \hyperlink{class_validate4_a6ec70437413135bc1a00c7c2310ece46}{run} ()
\item 
\hyperlink{class_validate4_a4098c3ea14d8a58ac6bf2aae8fa6071e}{$\sim$\+Validate4} ()
\end{DoxyCompactItemize}
\subsection*{Private Types}
\begin{DoxyCompactItemize}
\item 
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$ alphabet\+\_\+type $>$\+::vector \hyperlink{class_validate4_a49c80b3d101be19542a4341c2387603a}{alphabet\+\_\+vector\+\_\+type}
\item 
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$ size\+\_\+type $>$\+::vector \hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type}
\item 
typedef \hyperlink{structpair}{pair}$<$ size\+\_\+type, size\+\_\+type $>$ \hyperlink{class_validate4_aaa2fcb80a05115eb4ca02ab23df8827e}{pair1\+\_\+type}
\item 
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$ \hyperlink{class_validate4_aaa2fcb80a05115eb4ca02ab23df8827e}{pair1\+\_\+type} $>$ \hyperlink{class_validate4_af01005bf9ba711e95fc52fc41e323716}{pair1\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$ \hyperlink{class_validate4_aaa2fcb80a05115eb4ca02ab23df8827e}{pair1\+\_\+type}, \hyperlink{class_validate4_af01005bf9ba711e95fc52fc41e323716}{pair1\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type} $>$\+::sorter \hyperlink{class_validate4_a40b1f73557cfa4c0b26f56f5038a4c5c}{pair1\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{structtuple__great__comparator__1st}{tuple\+\_\+great\+\_\+comparator\+\_\+1st}$<$ \hyperlink{class_validate4_aaa2fcb80a05115eb4ca02ab23df8827e}{pair1\+\_\+type} $>$ \hyperlink{class_validate4_a3a6678b617cc9e0d65b36595cdd12a83}{pair1\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$ \hyperlink{class_validate4_aaa2fcb80a05115eb4ca02ab23df8827e}{pair1\+\_\+type}, \hyperlink{class_validate4_a3a6678b617cc9e0d65b36595cdd12a83}{pair1\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type} $>$\+::sorter \hyperlink{class_validate4_ac379442c631fdd03a2e64223cea2c911}{pair1\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{structtuple__less__comparator__2nd}{tuple\+\_\+less\+\_\+comparator\+\_\+2nd}$<$ \hyperlink{class_validate4_aaa2fcb80a05115eb4ca02ab23df8827e}{pair1\+\_\+type} $>$ \hyperlink{class_validate4_a67166f1b6f64e5d8887d9a5aa6072346}{pair1\+\_\+less\+\_\+comparator\+\_\+2nd\+\_\+type}
\item 
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$ \hyperlink{class_validate4_aaa2fcb80a05115eb4ca02ab23df8827e}{pair1\+\_\+type}, \hyperlink{class_validate4_a67166f1b6f64e5d8887d9a5aa6072346}{pair1\+\_\+less\+\_\+comparator\+\_\+2nd\+\_\+type} $>$\+::sorter \hyperlink{class_validate4_a65355c8a8ccca4870060305479e7748c}{pair1\+\_\+less\+\_\+sorter\+\_\+2nd\+\_\+type}
\item 
typedef \hyperlink{structpair}{pair}$<$ size\+\_\+type, \hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} $>$ \hyperlink{class_validate4_a655c0013e7d26a0653ab8f4f96145bad}{pair2\+\_\+type}
\item 
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$ \hyperlink{class_validate4_a655c0013e7d26a0653ab8f4f96145bad}{pair2\+\_\+type} $>$ \hyperlink{class_validate4_af39ac6db5faa77a64ab49a75f92337a3}{pair2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$ \hyperlink{class_validate4_a655c0013e7d26a0653ab8f4f96145bad}{pair2\+\_\+type}, \hyperlink{class_validate4_af39ac6db5faa77a64ab49a75f92337a3}{pair2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type} $>$\+::sorter \hyperlink{class_validate4_ad945003027abfd152a0e177d7541580d}{pair2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{structpair}{pair}$<$ size\+\_\+type, alphabet\+\_\+type $>$ \hyperlink{class_validate4_ac023757abc671597cf81dcc2d70b1ab1}{pair3\+\_\+type}
\item 
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$ \hyperlink{class_validate4_ac023757abc671597cf81dcc2d70b1ab1}{pair3\+\_\+type} $>$ \hyperlink{class_validate4_a12c8c95c3ef8bf9f3521b439454c5aa0}{pair3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$ \hyperlink{class_validate4_ac023757abc671597cf81dcc2d70b1ab1}{pair3\+\_\+type}, \hyperlink{class_validate4_a12c8c95c3ef8bf9f3521b439454c5aa0}{pair3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type} $>$\+::sorter \hyperlink{class_validate4_aff3135d55f749682df7e0f97c82a6769}{pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{structpair}{pair}$<$ alphabet\+\_\+type, \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} $>$ \hyperlink{class_validate4_a8ef701022ecc2f0ffc1eae0e71e0aaf7}{pair4\+\_\+type}
\item 
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$ \hyperlink{class_validate4_a8ef701022ecc2f0ffc1eae0e71e0aaf7}{pair4\+\_\+type} $>$\+::vector \hyperlink{class_validate4_a883822e6f1be0d67f71e1feb9729b1dc}{pair4\+\_\+vector\+\_\+type}
\item 
typedef \hyperlink{structtriple}{triple}$<$ size\+\_\+type, \hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type}, alphabet\+\_\+extension\+\_\+type $>$ \hyperlink{class_validate4_a8dd208bf04e6c5285cdacb9ac9532a67}{triple1\+\_\+type}
\item 
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$ \hyperlink{class_validate4_a8dd208bf04e6c5285cdacb9ac9532a67}{triple1\+\_\+type} $>$ \hyperlink{class_validate4_af07a5152d547f7fba2f93b78660b88ab}{triple1\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$ \hyperlink{class_validate4_a8dd208bf04e6c5285cdacb9ac9532a67}{triple1\+\_\+type}, \hyperlink{class_validate4_af07a5152d547f7fba2f93b78660b88ab}{triple1\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type} $>$\+::sorter \hyperlink{class_validate4_aa4a137d0ed68e95db5ebbe57544d80ed}{triple1\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{structtriple}{triple}$<$ size\+\_\+type, alphabet\+\_\+type, \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} $>$ \hyperlink{class_validate4_a1e1065b2bd86208beeec8aea6edd3ddd}{triple2\+\_\+type}
\item 
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$ \hyperlink{class_validate4_a1e1065b2bd86208beeec8aea6edd3ddd}{triple2\+\_\+type} $>$ \hyperlink{class_validate4_a83e9e52347608368b088892cabbdc8c5}{triple2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$ \hyperlink{class_validate4_a1e1065b2bd86208beeec8aea6edd3ddd}{triple2\+\_\+type}, \hyperlink{class_validate4_a83e9e52347608368b088892cabbdc8c5}{triple2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type} $>$\+::sorter \hyperlink{class_validate4_a4c1bcea817e34f96d95c99e0694bbfc8}{triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{structtuple__great__comparator__1st}{tuple\+\_\+great\+\_\+comparator\+\_\+1st}$<$ \hyperlink{class_validate4_a1e1065b2bd86208beeec8aea6edd3ddd}{triple2\+\_\+type} $>$ \hyperlink{class_validate4_a17f3f46281d706a75c002eed273aeaf8}{triple2\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$ \hyperlink{class_validate4_a1e1065b2bd86208beeec8aea6edd3ddd}{triple2\+\_\+type}, \hyperlink{class_validate4_a17f3f46281d706a75c002eed273aeaf8}{triple2\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type} $>$\+::sorter \hyperlink{class_validate4_aa35a0ebf404821377118043d536be262}{triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{structtriple}{triple}$<$ size\+\_\+type, \hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type}, alphabet\+\_\+extension\+\_\+type $>$ \hyperlink{class_validate4_a2bc9345c182543a419af47b6c8bd37d2}{triple3\+\_\+type}
\item 
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$ \hyperlink{class_validate4_a2bc9345c182543a419af47b6c8bd37d2}{triple3\+\_\+type} $>$ \hyperlink{class_validate4_a473516f742b15338b55ec169c794f7ca}{triple3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}
\item 
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$ \hyperlink{class_validate4_a2bc9345c182543a419af47b6c8bd37d2}{triple3\+\_\+type}, \hyperlink{class_validate4_a473516f742b15338b55ec169c794f7ca}{triple3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type} $>$\+::sorter \hyperlink{class_validate4_ac2e4bde5df51eeff18ef5591d76e63dc}{triple3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}
\end{DoxyCompactItemize}
\subsection*{Private Attributes}
\begin{DoxyCompactItemize}
\item 
\hyperlink{struct_validate4_1_1_bkt_info}{Bkt\+Info} \hyperlink{class_validate4_a4f79c420ccec4e83e536fae655fe7a11}{m\+\_\+bkt\+\_\+info}
\begin{DoxyCompactList}\small\item\em an instance of \hyperlink{struct_validate4_1_1_bkt_info}{Bkt\+Info}, collect information when validating S\+A\+\_\+\+L\+MS \& L\+C\+P\+\_\+\+L\+MS \end{DoxyCompactList}\item 
stxxl\+::syscall\+\_\+file $\ast$ \hyperlink{class_validate4_a63b517772b6359b72cf1c1a4ad5f14b5}{m\+\_\+t\+\_\+file}
\item 
stxxl\+::syscall\+\_\+file $\ast$ \hyperlink{class_validate4_a32bf87f5aa8dc5fda81440f23ce0cb45}{m\+\_\+sa\+\_\+file}
\item 
stxxl\+::syscall\+\_\+file $\ast$ \hyperlink{class_validate4_a04f44eed3b6ea4534076aff282adf037}{m\+\_\+lcp\+\_\+file}
\item 
\hyperlink{class_validate4_a49c80b3d101be19542a4341c2387603a}{alphabet\+\_\+vector\+\_\+type} $\ast$ \hyperlink{class_validate4_a421635668138c3d4cbe2b7c362d57006}{m\+\_\+t}
\item 
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$ \hyperlink{class_validate4_aa6e516f93f9b184ebf958a4c314588d5}{m\+\_\+sa}
\item 
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$ \hyperlink{class_validate4_a41b6536affab0d38c674648c9ee58959}{m\+\_\+lcp}
\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4_a4b57f273604a17a02e891b43bdd7f03e}{m\+\_\+len}
\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$\newline
class Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$}

vaildate SA and L\+CP following the induced-\/sorting principle

\begin{DoxyParams}{Parameters}
{\em alphabet\+\_\+type} & for elements in T \\
\hline
{\em alphabet\+\_\+extension\+\_\+type} & for instance, given alphabet\+\_\+type = uint8, we have alphbet\+\_\+extension\+\_\+type = uint16 \\
\hline
{\em size\+\_\+type} & for elements in S\+A/\+L\+CP \\
\hline
\end{DoxyParams}

\subsection{Member Typedef Documentation}
\mbox{\Hypertarget{class_validate4_a49c80b3d101be19542a4341c2387603a}\label{class_validate4_a49c80b3d101be19542a4341c2387603a}} 
\index{Validate4@{Validate4}!alphabet\+\_\+vector\+\_\+type@{alphabet\+\_\+vector\+\_\+type}}
\index{alphabet\+\_\+vector\+\_\+type@{alphabet\+\_\+vector\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{alphabet\+\_\+vector\+\_\+type}{alphabet\_vector\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$alphabet\+\_\+type$>$\+::vector \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_a49c80b3d101be19542a4341c2387603a}{alphabet\+\_\+vector\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a3a6678b617cc9e0d65b36595cdd12a83}\label{class_validate4_a3a6678b617cc9e0d65b36595cdd12a83}} 
\index{Validate4@{Validate4}!pair1\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type@{pair1\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type}}
\index{pair1\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type@{pair1\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{pair1\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type}{pair1\_great\_comparator\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structtuple__great__comparator__1st}{tuple\+\_\+great\+\_\+comparator\+\_\+1st}$<$\hyperlink{class_validate4_aaa2fcb80a05115eb4ca02ab23df8827e}{pair1\+\_\+type}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_a3a6678b617cc9e0d65b36595cdd12a83}{pair1\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_ac379442c631fdd03a2e64223cea2c911}\label{class_validate4_ac379442c631fdd03a2e64223cea2c911}} 
\index{Validate4@{Validate4}!pair1\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type@{pair1\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type}}
\index{pair1\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type@{pair1\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{pair1\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type}{pair1\_great\_sorter\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$\hyperlink{class_validate4_aaa2fcb80a05115eb4ca02ab23df8827e}{pair1\+\_\+type}, \hyperlink{class_validate4_a3a6678b617cc9e0d65b36595cdd12a83}{pair1\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type}$>$\+::sorter \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_ac379442c631fdd03a2e64223cea2c911}{pair1\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_af01005bf9ba711e95fc52fc41e323716}\label{class_validate4_af01005bf9ba711e95fc52fc41e323716}} 
\index{Validate4@{Validate4}!pair1\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type@{pair1\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}}
\index{pair1\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type@{pair1\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{pair1\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}{pair1\_less\_comparator\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$\hyperlink{class_validate4_aaa2fcb80a05115eb4ca02ab23df8827e}{pair1\+\_\+type}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_af01005bf9ba711e95fc52fc41e323716}{pair1\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a67166f1b6f64e5d8887d9a5aa6072346}\label{class_validate4_a67166f1b6f64e5d8887d9a5aa6072346}} 
\index{Validate4@{Validate4}!pair1\+\_\+less\+\_\+comparator\+\_\+2nd\+\_\+type@{pair1\+\_\+less\+\_\+comparator\+\_\+2nd\+\_\+type}}
\index{pair1\+\_\+less\+\_\+comparator\+\_\+2nd\+\_\+type@{pair1\+\_\+less\+\_\+comparator\+\_\+2nd\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{pair1\+\_\+less\+\_\+comparator\+\_\+2nd\+\_\+type}{pair1\_less\_comparator\_2nd\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structtuple__less__comparator__2nd}{tuple\+\_\+less\+\_\+comparator\+\_\+2nd}$<$\hyperlink{class_validate4_aaa2fcb80a05115eb4ca02ab23df8827e}{pair1\+\_\+type}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_a67166f1b6f64e5d8887d9a5aa6072346}{pair1\+\_\+less\+\_\+comparator\+\_\+2nd\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a40b1f73557cfa4c0b26f56f5038a4c5c}\label{class_validate4_a40b1f73557cfa4c0b26f56f5038a4c5c}} 
\index{Validate4@{Validate4}!pair1\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type@{pair1\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}}
\index{pair1\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type@{pair1\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{pair1\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}{pair1\_less\_sorter\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$\hyperlink{class_validate4_aaa2fcb80a05115eb4ca02ab23df8827e}{pair1\+\_\+type}, \hyperlink{class_validate4_af01005bf9ba711e95fc52fc41e323716}{pair1\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}$>$\+::sorter \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_a40b1f73557cfa4c0b26f56f5038a4c5c}{pair1\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a65355c8a8ccca4870060305479e7748c}\label{class_validate4_a65355c8a8ccca4870060305479e7748c}} 
\index{Validate4@{Validate4}!pair1\+\_\+less\+\_\+sorter\+\_\+2nd\+\_\+type@{pair1\+\_\+less\+\_\+sorter\+\_\+2nd\+\_\+type}}
\index{pair1\+\_\+less\+\_\+sorter\+\_\+2nd\+\_\+type@{pair1\+\_\+less\+\_\+sorter\+\_\+2nd\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{pair1\+\_\+less\+\_\+sorter\+\_\+2nd\+\_\+type}{pair1\_less\_sorter\_2nd\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$\hyperlink{class_validate4_aaa2fcb80a05115eb4ca02ab23df8827e}{pair1\+\_\+type}, \hyperlink{class_validate4_a67166f1b6f64e5d8887d9a5aa6072346}{pair1\+\_\+less\+\_\+comparator\+\_\+2nd\+\_\+type}$>$\+::sorter \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_a65355c8a8ccca4870060305479e7748c}{pair1\+\_\+less\+\_\+sorter\+\_\+2nd\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_aaa2fcb80a05115eb4ca02ab23df8827e}\label{class_validate4_aaa2fcb80a05115eb4ca02ab23df8827e}} 
\index{Validate4@{Validate4}!pair1\+\_\+type@{pair1\+\_\+type}}
\index{pair1\+\_\+type@{pair1\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{pair1\+\_\+type}{pair1\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structpair}{pair}$<$size\+\_\+type, size\+\_\+type$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_aaa2fcb80a05115eb4ca02ab23df8827e}{pair1\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_af39ac6db5faa77a64ab49a75f92337a3}\label{class_validate4_af39ac6db5faa77a64ab49a75f92337a3}} 
\index{Validate4@{Validate4}!pair2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type@{pair2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}}
\index{pair2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type@{pair2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{pair2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}{pair2\_less\_comparator\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$\hyperlink{class_validate4_a655c0013e7d26a0653ab8f4f96145bad}{pair2\+\_\+type}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_af39ac6db5faa77a64ab49a75f92337a3}{pair2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_ad945003027abfd152a0e177d7541580d}\label{class_validate4_ad945003027abfd152a0e177d7541580d}} 
\index{Validate4@{Validate4}!pair2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type@{pair2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}}
\index{pair2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type@{pair2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{pair2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}{pair2\_less\_sorter\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$\hyperlink{class_validate4_a655c0013e7d26a0653ab8f4f96145bad}{pair2\+\_\+type}, \hyperlink{class_validate4_af39ac6db5faa77a64ab49a75f92337a3}{pair2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}$>$\+::sorter \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_ad945003027abfd152a0e177d7541580d}{pair2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a655c0013e7d26a0653ab8f4f96145bad}\label{class_validate4_a655c0013e7d26a0653ab8f4f96145bad}} 
\index{Validate4@{Validate4}!pair2\+\_\+type@{pair2\+\_\+type}}
\index{pair2\+\_\+type@{pair2\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{pair2\+\_\+type}{pair2\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structpair}{pair}$<$size\+\_\+type, \hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_a655c0013e7d26a0653ab8f4f96145bad}{pair2\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a12c8c95c3ef8bf9f3521b439454c5aa0}\label{class_validate4_a12c8c95c3ef8bf9f3521b439454c5aa0}} 
\index{Validate4@{Validate4}!pair3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type@{pair3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}}
\index{pair3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type@{pair3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{pair3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}{pair3\_less\_comparator\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$\hyperlink{class_validate4_ac023757abc671597cf81dcc2d70b1ab1}{pair3\+\_\+type}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_a12c8c95c3ef8bf9f3521b439454c5aa0}{pair3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_aff3135d55f749682df7e0f97c82a6769}\label{class_validate4_aff3135d55f749682df7e0f97c82a6769}} 
\index{Validate4@{Validate4}!pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type@{pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}}
\index{pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type@{pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}{pair3\_less\_sorter\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$\hyperlink{class_validate4_ac023757abc671597cf81dcc2d70b1ab1}{pair3\+\_\+type}, \hyperlink{class_validate4_a12c8c95c3ef8bf9f3521b439454c5aa0}{pair3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}$>$\+::sorter \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_aff3135d55f749682df7e0f97c82a6769}{pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_ac023757abc671597cf81dcc2d70b1ab1}\label{class_validate4_ac023757abc671597cf81dcc2d70b1ab1}} 
\index{Validate4@{Validate4}!pair3\+\_\+type@{pair3\+\_\+type}}
\index{pair3\+\_\+type@{pair3\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{pair3\+\_\+type}{pair3\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structpair}{pair}$<$size\+\_\+type, alphabet\+\_\+type$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_ac023757abc671597cf81dcc2d70b1ab1}{pair3\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a8ef701022ecc2f0ffc1eae0e71e0aaf7}\label{class_validate4_a8ef701022ecc2f0ffc1eae0e71e0aaf7}} 
\index{Validate4@{Validate4}!pair4\+\_\+type@{pair4\+\_\+type}}
\index{pair4\+\_\+type@{pair4\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{pair4\+\_\+type}{pair4\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structpair}{pair}$<$alphabet\+\_\+type, \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_a8ef701022ecc2f0ffc1eae0e71e0aaf7}{pair4\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a883822e6f1be0d67f71e1feb9729b1dc}\label{class_validate4_a883822e6f1be0d67f71e1feb9729b1dc}} 
\index{Validate4@{Validate4}!pair4\+\_\+vector\+\_\+type@{pair4\+\_\+vector\+\_\+type}}
\index{pair4\+\_\+vector\+\_\+type@{pair4\+\_\+vector\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{pair4\+\_\+vector\+\_\+type}{pair4\_vector\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$\hyperlink{class_validate4_a8ef701022ecc2f0ffc1eae0e71e0aaf7}{pair4\+\_\+type}$>$\+::vector \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_a883822e6f1be0d67f71e1feb9729b1dc}{pair4\+\_\+vector\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a46ea31a0a4b23f583806792160421d15}\label{class_validate4_a46ea31a0a4b23f583806792160421d15}} 
\index{Validate4@{Validate4}!size\+\_\+vector\+\_\+type@{size\+\_\+vector\+\_\+type}}
\index{size\+\_\+vector\+\_\+type@{size\+\_\+vector\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{size\+\_\+vector\+\_\+type}{size\_vector\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_vector}{Ex\+Vector}$<$size\+\_\+type$>$\+::vector \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_af07a5152d547f7fba2f93b78660b88ab}\label{class_validate4_af07a5152d547f7fba2f93b78660b88ab}} 
\index{Validate4@{Validate4}!triple1\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type@{triple1\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}}
\index{triple1\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type@{triple1\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{triple1\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}{triple1\_less\_comparator\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$\hyperlink{class_validate4_a8dd208bf04e6c5285cdacb9ac9532a67}{triple1\+\_\+type}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_af07a5152d547f7fba2f93b78660b88ab}{triple1\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_aa4a137d0ed68e95db5ebbe57544d80ed}\label{class_validate4_aa4a137d0ed68e95db5ebbe57544d80ed}} 
\index{Validate4@{Validate4}!triple1\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type@{triple1\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}}
\index{triple1\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type@{triple1\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{triple1\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}{triple1\_less\_sorter\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$\hyperlink{class_validate4_a8dd208bf04e6c5285cdacb9ac9532a67}{triple1\+\_\+type}, \hyperlink{class_validate4_af07a5152d547f7fba2f93b78660b88ab}{triple1\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}$>$\+::sorter \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_aa4a137d0ed68e95db5ebbe57544d80ed}{triple1\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a8dd208bf04e6c5285cdacb9ac9532a67}\label{class_validate4_a8dd208bf04e6c5285cdacb9ac9532a67}} 
\index{Validate4@{Validate4}!triple1\+\_\+type@{triple1\+\_\+type}}
\index{triple1\+\_\+type@{triple1\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{triple1\+\_\+type}{triple1\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structtriple}{triple}$<$size\+\_\+type, \hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type}, alphabet\+\_\+extension\+\_\+type$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_a8dd208bf04e6c5285cdacb9ac9532a67}{triple1\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a17f3f46281d706a75c002eed273aeaf8}\label{class_validate4_a17f3f46281d706a75c002eed273aeaf8}} 
\index{Validate4@{Validate4}!triple2\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type@{triple2\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type}}
\index{triple2\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type@{triple2\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{triple2\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type}{triple2\_great\_comparator\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structtuple__great__comparator__1st}{tuple\+\_\+great\+\_\+comparator\+\_\+1st}$<$\hyperlink{class_validate4_a1e1065b2bd86208beeec8aea6edd3ddd}{triple2\+\_\+type}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_a17f3f46281d706a75c002eed273aeaf8}{triple2\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_aa35a0ebf404821377118043d536be262}\label{class_validate4_aa35a0ebf404821377118043d536be262}} 
\index{Validate4@{Validate4}!triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type@{triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type}}
\index{triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type@{triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type}{triple2\_great\_sorter\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$\hyperlink{class_validate4_a1e1065b2bd86208beeec8aea6edd3ddd}{triple2\+\_\+type}, \hyperlink{class_validate4_a17f3f46281d706a75c002eed273aeaf8}{triple2\+\_\+great\+\_\+comparator\+\_\+1st\+\_\+type}$>$\+::sorter \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_aa35a0ebf404821377118043d536be262}{triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a83e9e52347608368b088892cabbdc8c5}\label{class_validate4_a83e9e52347608368b088892cabbdc8c5}} 
\index{Validate4@{Validate4}!triple2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type@{triple2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}}
\index{triple2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type@{triple2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{triple2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}{triple2\_less\_comparator\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$\hyperlink{class_validate4_a1e1065b2bd86208beeec8aea6edd3ddd}{triple2\+\_\+type}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_a83e9e52347608368b088892cabbdc8c5}{triple2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a4c1bcea817e34f96d95c99e0694bbfc8}\label{class_validate4_a4c1bcea817e34f96d95c99e0694bbfc8}} 
\index{Validate4@{Validate4}!triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type@{triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}}
\index{triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type@{triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}{triple2\_less\_sorter\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$\hyperlink{class_validate4_a1e1065b2bd86208beeec8aea6edd3ddd}{triple2\+\_\+type}, \hyperlink{class_validate4_a83e9e52347608368b088892cabbdc8c5}{triple2\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}$>$\+::sorter \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_a4c1bcea817e34f96d95c99e0694bbfc8}{triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a1e1065b2bd86208beeec8aea6edd3ddd}\label{class_validate4_a1e1065b2bd86208beeec8aea6edd3ddd}} 
\index{Validate4@{Validate4}!triple2\+\_\+type@{triple2\+\_\+type}}
\index{triple2\+\_\+type@{triple2\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{triple2\+\_\+type}{triple2\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structtriple}{triple}$<$size\+\_\+type, alphabet\+\_\+type, \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_a1e1065b2bd86208beeec8aea6edd3ddd}{triple2\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a473516f742b15338b55ec169c794f7ca}\label{class_validate4_a473516f742b15338b55ec169c794f7ca}} 
\index{Validate4@{Validate4}!triple3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type@{triple3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}}
\index{triple3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type@{triple3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{triple3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}{triple3\_less\_comparator\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$\hyperlink{class_validate4_a2bc9345c182543a419af47b6c8bd37d2}{triple3\+\_\+type}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_a473516f742b15338b55ec169c794f7ca}{triple3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_ac2e4bde5df51eeff18ef5591d76e63dc}\label{class_validate4_ac2e4bde5df51eeff18ef5591d76e63dc}} 
\index{Validate4@{Validate4}!triple3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type@{triple3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}}
\index{triple3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type@{triple3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{triple3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}{triple3\_less\_sorter\_1st\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$\hyperlink{class_validate4_a2bc9345c182543a419af47b6c8bd37d2}{triple3\+\_\+type}, \hyperlink{class_validate4_a473516f742b15338b55ec169c794f7ca}{triple3\+\_\+less\+\_\+comparator\+\_\+1st\+\_\+type}$>$\+::sorter \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_ac2e4bde5df51eeff18ef5591d76e63dc}{triple3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a2bc9345c182543a419af47b6c8bd37d2}\label{class_validate4_a2bc9345c182543a419af47b6c8bd37d2}} 
\index{Validate4@{Validate4}!triple3\+\_\+type@{triple3\+\_\+type}}
\index{triple3\+\_\+type@{triple3\+\_\+type}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{triple3\+\_\+type}{triple3\_type}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
typedef \hyperlink{structtriple}{triple}$<$size\+\_\+type, \hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type}, alphabet\+\_\+extension\+\_\+type$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4_a2bc9345c182543a419af47b6c8bd37d2}{triple3\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{class_validate4_aa1e9bf045b028c339da30db955857cb9}\label{class_validate4_aa1e9bf045b028c339da30db955857cb9}} 
\index{Validate4@{Validate4}!Validate4@{Validate4}}
\index{Validate4@{Validate4}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{Validate4()}{Validate4()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\hyperlink{class_validate4}{Validate4} (\begin{DoxyParamCaption}\item[{const std\+::string \&}]{\+\_\+t\+\_\+fn,  }\item[{const std\+::string \&}]{\+\_\+sa\+\_\+fn,  }\item[{const std\+::string \&}]{\+\_\+lcp\+\_\+fn }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

ctor

\mbox{\Hypertarget{class_validate4_a4098c3ea14d8a58ac6bf2aae8fa6071e}\label{class_validate4_a4098c3ea14d8a58ac6bf2aae8fa6071e}} 
\index{Validate4@{Validate4}!````~Validate4@{$\sim$\+Validate4}}
\index{````~Validate4@{$\sim$\+Validate4}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{$\sim$\+Validate4()}{~Validate4()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::$\sim$\hyperlink{class_validate4}{Validate4} (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

\subsection{Member Function Documentation}
\mbox{\Hypertarget{class_validate4_a6ec70437413135bc1a00c7c2310ece46}\label{class_validate4_a6ec70437413135bc1a00c7c2310ece46}} 
\index{Validate4@{Validate4}!run@{run}}
\index{run@{run}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{run()}{run()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
bool \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::run (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

\subsection{Member Data Documentation}
\mbox{\Hypertarget{class_validate4_a4f79c420ccec4e83e536fae655fe7a11}\label{class_validate4_a4f79c420ccec4e83e536fae655fe7a11}} 
\index{Validate4@{Validate4}!m\+\_\+bkt\+\_\+info@{m\+\_\+bkt\+\_\+info}}
\index{m\+\_\+bkt\+\_\+info@{m\+\_\+bkt\+\_\+info}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{m\+\_\+bkt\+\_\+info}{m\_bkt\_info}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{struct_validate4_1_1_bkt_info}{Bkt\+Info} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::m\+\_\+bkt\+\_\+info\hspace{0.3cm}{\ttfamily [private]}}

an instance of \hyperlink{struct_validate4_1_1_bkt_info}{Bkt\+Info}, collect information when validating S\+A\+\_\+\+L\+MS \& L\+C\+P\+\_\+\+L\+MS

\mbox{\Hypertarget{class_validate4_a41b6536affab0d38c674648c9ee58959}\label{class_validate4_a41b6536affab0d38c674648c9ee58959}} 
\index{Validate4@{Validate4}!m\+\_\+lcp@{m\+\_\+lcp}}
\index{m\+\_\+lcp@{m\+\_\+lcp}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{m\+\_\+lcp}{m\_lcp}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::m\+\_\+lcp\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a04f44eed3b6ea4534076aff282adf037}\label{class_validate4_a04f44eed3b6ea4534076aff282adf037}} 
\index{Validate4@{Validate4}!m\+\_\+lcp\+\_\+file@{m\+\_\+lcp\+\_\+file}}
\index{m\+\_\+lcp\+\_\+file@{m\+\_\+lcp\+\_\+file}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{m\+\_\+lcp\+\_\+file}{m\_lcp\_file}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
stxxl\+::syscall\+\_\+file$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::m\+\_\+lcp\+\_\+file\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a4b57f273604a17a02e891b43bdd7f03e}\label{class_validate4_a4b57f273604a17a02e891b43bdd7f03e}} 
\index{Validate4@{Validate4}!m\+\_\+len@{m\+\_\+len}}
\index{m\+\_\+len@{m\+\_\+len}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{m\+\_\+len}{m\_len}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::m\+\_\+len\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_aa6e516f93f9b184ebf958a4c314588d5}\label{class_validate4_aa6e516f93f9b184ebf958a4c314588d5}} 
\index{Validate4@{Validate4}!m\+\_\+sa@{m\+\_\+sa}}
\index{m\+\_\+sa@{m\+\_\+sa}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{m\+\_\+sa}{m\_sa}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::m\+\_\+sa\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a32bf87f5aa8dc5fda81440f23ce0cb45}\label{class_validate4_a32bf87f5aa8dc5fda81440f23ce0cb45}} 
\index{Validate4@{Validate4}!m\+\_\+sa\+\_\+file@{m\+\_\+sa\+\_\+file}}
\index{m\+\_\+sa\+\_\+file@{m\+\_\+sa\+\_\+file}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{m\+\_\+sa\+\_\+file}{m\_sa\_file}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
stxxl\+::syscall\+\_\+file$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::m\+\_\+sa\+\_\+file\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a421635668138c3d4cbe2b7c362d57006}\label{class_validate4_a421635668138c3d4cbe2b7c362d57006}} 
\index{Validate4@{Validate4}!m\+\_\+t@{m\+\_\+t}}
\index{m\+\_\+t@{m\+\_\+t}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{m\+\_\+t}{m\_t}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_a49c80b3d101be19542a4341c2387603a}{alphabet\+\_\+vector\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::m\+\_\+t\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{class_validate4_a63b517772b6359b72cf1c1a4ad5f14b5}\label{class_validate4_a63b517772b6359b72cf1c1a4ad5f14b5}} 
\index{Validate4@{Validate4}!m\+\_\+t\+\_\+file@{m\+\_\+t\+\_\+file}}
\index{m\+\_\+t\+\_\+file@{m\+\_\+t\+\_\+file}!Validate4@{Validate4}}
\subsubsection{\texorpdfstring{m\+\_\+t\+\_\+file}{m\_t\_file}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
stxxl\+::syscall\+\_\+file$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::m\+\_\+t\+\_\+file\hspace{0.3cm}{\ttfamily [private]}}

The documentation for this class was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/\hyperlink{validate4_8h}{validate4.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/classasync__multi__stream__reader.tex
2017/01/24

\hypertarget{classasync__multi__stream__reader}{}\section{async\+\_\+multi\+\_\+stream\+\_\+reader$<$ value\+\_\+type $>$ Class Template Reference}
\label{classasync__multi__stream__reader}\index{async\+\_\+multi\+\_\+stream\+\_\+reader$<$ value\+\_\+type $>$@{async\+\_\+multi\+\_\+stream\+\_\+reader$<$ value\+\_\+type $>$}}

main thread read multiple disk files simultaneously.

{\ttfamily \#include $<$async\+\_\+stream\+\_\+reader.\+h$>$}

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{classasync__multi__stream__reader_af83e5faafb7612b51abc05e8edde52dd}{async\+\_\+multi\+\_\+stream\+\_\+reader} (const std\+::string \&\+\_\+fn\+\_\+prefix, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+filenum, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+mem\+\_\+avail=(8ul$<$$<$ 20), const uint64 \&\+\_\+bufnum=4ul)
\begin{DoxyCompactList}\small\item\em constructor \end{DoxyCompactList}\item 
value\+\_\+type \hyperlink{classasync__multi__stream__reader_ae47f5af3e9c0964be88975391631b3d4}{read} (const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+file\+\_\+idx)
\begin{DoxyCompactList}\small\item\em read an element \end{DoxyCompactList}\item 
void \hyperlink{classasync__multi__stream__reader_a1b4db036726c5b33edf9cdca1ccc24d9}{read} (const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+file\+\_\+idx, value\+\_\+type $\ast$\+\_\+des, \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \+\_\+num)
\begin{DoxyCompactList}\small\item\em read a sequence of elements \end{DoxyCompactList}\item 
void \hyperlink{classasync__multi__stream__reader_a620b5917c284dbdb6b1f93ea425b9c0e}{skip} (const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+file\+\_\+idx, \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \+\_\+num)
\begin{DoxyCompactList}\small\item\em skip a sequence of elements \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__multi__stream__reader_ab4ebef1c67d84d3581bc4ddaa0a1cc9b}{bytes\+\_\+read} ()
\begin{DoxyCompactList}\small\item\em report bytes read \end{DoxyCompactList}\item 
bool \hyperlink{classasync__multi__stream__reader_aec2bb44c72b149387343e53cf6e65f7d}{empty} (const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+file\+\_\+idx)
\begin{DoxyCompactList}\small\item\em check if the stream is empty (reach endofit) \end{DoxyCompactList}\item 
\hyperlink{classasync__multi__stream__reader_a1c178b1a22b1e8853bacd42c1e0c2303}{$\sim$async\+\_\+multi\+\_\+stream\+\_\+vbyte\+\_\+reader} ()
\begin{DoxyCompactList}\small\item\em destructor \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Private Types}
\begin{DoxyCompactItemize}
\item 
typedef \hyperlink{structbuffer}{buffer}$<$ value\+\_\+type $>$ \hyperlink{classasync__multi__stream__reader_ad58ad834dc6d741a12be1fb442b8e5d6}{buffer\+\_\+type}
\item 
typedef \hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ \hyperlink{classasync__multi__stream__reader_ad58ad834dc6d741a12be1fb442b8e5d6}{buffer\+\_\+type} $>$ \hyperlink{classasync__multi__stream__reader_a0bf4b801f7d874da5cbbe5c6504d0ecc}{buffer\+\_\+queue\+\_\+type}
\end{DoxyCompactItemize}
\subsection*{Private Member Functions}
\begin{DoxyCompactItemize}
\item 
void \hyperlink{classasync__multi__stream__reader_afae17e2365e9ed10f30d398a550caa89}{get\+\_\+full\+\_\+buffer} (const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+file\+\_\+idx)
\begin{DoxyCompactList}\small\item\em get a full buffer \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Static Private Member Functions}
\begin{DoxyCompactItemize}
\item 
{\footnotesize template$<$typename T $>$ }\\static void \hyperlink{classasync__multi__stream__reader_a6e68c1dfe4990e3320f6b03dbf400517}{io\+\_\+procedure} (\hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader} $\ast$\+\_\+caller, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+file\+\_\+idx)
\begin{DoxyCompactList}\small\item\em start an I/O thread for each disk file \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Private Attributes}
\begin{DoxyCompactItemize}
\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $\ast$ \hyperlink{classasync__multi__stream__reader_a6486d4f10a3caf9169018d2bb71c4fdc}{m\+\_\+bytes\+\_\+read}
\begin{DoxyCompactList}\small\item\em io statistics \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__multi__stream__reader_a4ddb169d2f5eff8499eef88ba091c566}{m\+\_\+bufsize}
\begin{DoxyCompactList}\small\item\em size of buffer \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__multi__stream__reader_a24bef59afd1ef00b27d54e00a5f1c39a}{m\+\_\+bufnum}
\begin{DoxyCompactList}\small\item\em number of buffers in a queue, orgained as an F\+I\+FO queue for each file \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__multi__stream__reader_aa8447afd5b6caafe60f2c69be4df23ff}{m\+\_\+filenum}
\begin{DoxyCompactList}\small\item\em number of files \end{DoxyCompactList}\item 
std\+::\+F\+I\+LE $\ast$$\ast$ \hyperlink{classasync__multi__stream__reader_a9e79f443dd594c3ea539aa97d3f8cb45}{m\+\_\+files}
\begin{DoxyCompactList}\small\item\em pointers to files \end{DoxyCompactList}\item 
\hyperlink{classasync__multi__stream__reader_a0bf4b801f7d874da5cbbe5c6504d0ecc}{buffer\+\_\+queue\+\_\+type} $\ast$$\ast$ \hyperlink{classasync__multi__stream__reader_a57291593ed44d4c1d2586a438bb4d0d6}{m\+\_\+full\+\_\+buffer\+\_\+queues}
\begin{DoxyCompactList}\small\item\em pointers to full buffer queues \end{DoxyCompactList}\item 
\hyperlink{classasync__multi__stream__reader_a0bf4b801f7d874da5cbbe5c6504d0ecc}{buffer\+\_\+queue\+\_\+type} $\ast$$\ast$ \hyperlink{classasync__multi__stream__reader_a955fea161fa853f416b372699af70b15}{m\+\_\+free\+\_\+buffer\+\_\+queues}
\begin{DoxyCompactList}\small\item\em pointers to free buffer queues \end{DoxyCompactList}\item 
std\+::thread $\ast$$\ast$ \hyperlink{classasync__multi__stream__reader_ae3ef39404dd6b7fbc2d8339d4e2c5748}{m\+\_\+io\+\_\+threads}
\begin{DoxyCompactList}\small\item\em pointers to I/O threads \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $\ast$ \hyperlink{classasync__multi__stream__reader_a47a94d5e9c912c3d448e8039cc650e64}{m\+\_\+items\+\_\+toread}
\begin{DoxyCompactList}\small\item\em items to read in each file \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $\ast$ \hyperlink{classasync__multi__stream__reader_acea48aa08da0c9e3065f6c8d00f65ef1}{m\+\_\+items\+\_\+read}
\begin{DoxyCompactList}\small\item\em items read in each file \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $\ast$ \hyperlink{classasync__multi__stream__reader_a42a6fa935ef4401a70e1ebfff9437d0d}{m\+\_\+cur\+\_\+buffer\+\_\+pos}
\begin{DoxyCompactList}\small\item\em position of next item to be read in current buffer for each file \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $\ast$ \hyperlink{classasync__multi__stream__reader_a7583fa561610fcc9f620d3ad5539e488}{m\+\_\+cur\+\_\+buffer\+\_\+filled}
\begin{DoxyCompactList}\small\item\em number of items in current buffer for each file \end{DoxyCompactList}\item 
\hyperlink{classasync__multi__stream__reader_ad58ad834dc6d741a12be1fb442b8e5d6}{buffer\+\_\+type} $\ast$$\ast$ \hyperlink{classasync__multi__stream__reader_aeedea79263b0e41a5fd3264b26aa39a8}{m\+\_\+cur\+\_\+buffer}
\begin{DoxyCompactList}\small\item\em pointer to current buffer for each file \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename value\+\_\+type$>$\newline
class async\+\_\+multi\+\_\+stream\+\_\+reader$<$ value\+\_\+type $>$}

main thread read multiple disk files simultaneously.

For the situation (such as mergesort), a set of buffers are established for each file and an I/O thread is created to continually load data into buffers for fast read by main thread.

\subsection{Member Typedef Documentation}
\mbox{\Hypertarget{classasync__multi__stream__reader_a0bf4b801f7d874da5cbbe5c6504d0ecc}\label{classasync__multi__stream__reader_a0bf4b801f7d874da5cbbe5c6504d0ecc}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!buffer\+\_\+queue\+\_\+type@{buffer\+\_\+queue\+\_\+type}}
\index{buffer\+\_\+queue\+\_\+type@{buffer\+\_\+queue\+\_\+type}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{buffer\+\_\+queue\+\_\+type}{buffer\_queue\_type}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
typedef \hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$\hyperlink{classasync__multi__stream__reader_ad58ad834dc6d741a12be1fb442b8e5d6}{buffer\+\_\+type}$>$ \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::\hyperlink{classasync__multi__stream__reader_a0bf4b801f7d874da5cbbe5c6504d0ecc}{buffer\+\_\+queue\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{classasync__multi__stream__reader_ad58ad834dc6d741a12be1fb442b8e5d6}\label{classasync__multi__stream__reader_ad58ad834dc6d741a12be1fb442b8e5d6}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!buffer\+\_\+type@{buffer\+\_\+type}}
\index{buffer\+\_\+type@{buffer\+\_\+type}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{buffer\+\_\+type}{buffer\_type}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
typedef \hyperlink{structbuffer}{buffer}$<$value\+\_\+type$>$ \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::\hyperlink{classasync__multi__stream__reader_ad58ad834dc6d741a12be1fb442b8e5d6}{buffer\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{classasync__multi__stream__reader_af83e5faafb7612b51abc05e8edde52dd}\label{classasync__multi__stream__reader_af83e5faafb7612b51abc05e8edde52dd}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{async\+\_\+multi\+\_\+stream\+\_\+reader()}{async\_multi\_stream\_reader()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::\hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader} (\begin{DoxyParamCaption}\item[{const std\+::string \&}]{\+\_\+fn\+\_\+prefix,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+filenum,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+mem\+\_\+avail = {\ttfamily (8ul~$<$$<$~20)},  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+bufnum = {\ttfamily 4ul} }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor

\mbox{\Hypertarget{classasync__multi__stream__reader_a1c178b1a22b1e8853bacd42c1e0c2303}\label{classasync__multi__stream__reader_a1c178b1a22b1e8853bacd42c1e0c2303}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!````~async\+\_\+multi\+\_\+stream\+\_\+vbyte\+\_\+reader@{$\sim$async\+\_\+multi\+\_\+stream\+\_\+vbyte\+\_\+reader}}
\index{````~async\+\_\+multi\+\_\+stream\+\_\+vbyte\+\_\+reader@{$\sim$async\+\_\+multi\+\_\+stream\+\_\+vbyte\+\_\+reader}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{$\sim$async\+\_\+multi\+\_\+stream\+\_\+vbyte\+\_\+reader()}{~async\_multi\_stream\_vbyte\_reader()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::$\sim$async\+\_\+multi\+\_\+stream\+\_\+vbyte\+\_\+reader (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

destructor

\subsection{Member Function Documentation}
\mbox{\Hypertarget{classasync__multi__stream__reader_ab4ebef1c67d84d3581bc4ddaa0a1cc9b}\label{classasync__multi__stream__reader_ab4ebef1c67d84d3581bc4ddaa0a1cc9b}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!bytes\+\_\+read@{bytes\+\_\+read}}
\index{bytes\+\_\+read@{bytes\+\_\+read}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{bytes\+\_\+read()}{bytes\_read()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::bytes\+\_\+read (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

report bytes read

\mbox{\Hypertarget{classasync__multi__stream__reader_aec2bb44c72b149387343e53cf6e65f7d}\label{classasync__multi__stream__reader_aec2bb44c72b149387343e53cf6e65f7d}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!empty@{empty}}
\index{empty@{empty}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{empty()}{empty()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
bool \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::empty (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+file\+\_\+idx }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

check if the stream is empty (reach endofit)

\mbox{\Hypertarget{classasync__multi__stream__reader_afae17e2365e9ed10f30d398a550caa89}\label{classasync__multi__stream__reader_afae17e2365e9ed10f30d398a550caa89}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!get\+\_\+full\+\_\+buffer@{get\+\_\+full\+\_\+buffer}}
\index{get\+\_\+full\+\_\+buffer@{get\+\_\+full\+\_\+buffer}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{get\+\_\+full\+\_\+buffer()}{get\_full\_buffer()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
void \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::get\+\_\+full\+\_\+buffer (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+file\+\_\+idx }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [private]}}

get a full buffer

\mbox{\Hypertarget{classasync__multi__stream__reader_a6e68c1dfe4990e3320f6b03dbf400517}\label{classasync__multi__stream__reader_a6e68c1dfe4990e3320f6b03dbf400517}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!io\+\_\+procedure@{io\+\_\+procedure}}
\index{io\+\_\+procedure@{io\+\_\+procedure}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{io\+\_\+procedure()}{io\_procedure()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
template$<$typename T $>$ \\
static void \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::io\+\_\+procedure (\begin{DoxyParamCaption}\item[{\hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$ $\ast$}]{\+\_\+caller,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+file\+\_\+idx }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [static]}, {\ttfamily [private]}}

start an I/O thread for each disk file

\begin{DoxyParams}{Parameters}
{\em \+\_\+caller} & handler managed by main thread \\
\hline
{\em \+\_\+file\+\_\+idx} & file index \\
\hline
\end{DoxyParams}
\mbox{\Hypertarget{classasync__multi__stream__reader_ae47f5af3e9c0964be88975391631b3d4}\label{classasync__multi__stream__reader_ae47f5af3e9c0964be88975391631b3d4}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!read@{read}}
\index{read@{read}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{read()}{read()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
value\+\_\+type \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::read (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+file\+\_\+idx }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

read an element

\begin{DoxyParams}{Parameters}
{\em \+\_\+file\+\_\+idx} & file index, start from 0 \\
\hline
\end{DoxyParams}
\begin{DoxyNote}{Note}
check if the stream is empty before calling the function 
\end{DoxyNote}
\mbox{\Hypertarget{classasync__multi__stream__reader_a1b4db036726c5b33edf9cdca1ccc24d9}\label{classasync__multi__stream__reader_a1b4db036726c5b33edf9cdca1ccc24d9}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!read@{read}}
\index{read@{read}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{read()}{read()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
void \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::read (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+file\+\_\+idx,  }\item[{value\+\_\+type $\ast$}]{\+\_\+des,  }\item[{\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}]{\+\_\+num }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

read a sequence of elements

\begin{DoxyParams}{Parameters}
{\em \+\_\+file\+\_\+idx} & file index \\
\hline
{\em \+\_\+des} & destination array \\
\hline
{\em \+\_\+num} & \+\_\+number of files to read \\
\hline
\end{DoxyParams}
\begin{DoxyNote}{Note}
check if the stream is empty before calling the function 
\end{DoxyNote}
\mbox{\Hypertarget{classasync__multi__stream__reader_a620b5917c284dbdb6b1f93ea425b9c0e}\label{classasync__multi__stream__reader_a620b5917c284dbdb6b1f93ea425b9c0e}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!skip@{skip}}
\index{skip@{skip}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{skip()}{skip()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
void \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::skip (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+file\+\_\+idx,  }\item[{\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}]{\+\_\+num }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

skip a sequence of elements

\begin{DoxyParams}{Parameters}
{\em \+\_\+file\+\_\+idx} & file index \\
\hline
{\em \+\_\+num} & number of elements to skip \\
\hline
\end{DoxyParams}
\begin{DoxyNote}{Note}
check if the stream is empty before calling the function 
\end{DoxyNote}

\subsection{Member Data Documentation}
\mbox{\Hypertarget{classasync__multi__stream__reader_a24bef59afd1ef00b27d54e00a5f1c39a}\label{classasync__multi__stream__reader_a24bef59afd1ef00b27d54e00a5f1c39a}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!m\+\_\+bufnum@{m\+\_\+bufnum}}
\index{m\+\_\+bufnum@{m\+\_\+bufnum}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+bufnum}{m\_bufnum}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+bufnum\hspace{0.3cm}{\ttfamily [private]}}

number of buffers in a queue, orgained as an F\+I\+FO queue for each file

\mbox{\Hypertarget{classasync__multi__stream__reader_a4ddb169d2f5eff8499eef88ba091c566}\label{classasync__multi__stream__reader_a4ddb169d2f5eff8499eef88ba091c566}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!m\+\_\+bufsize@{m\+\_\+bufsize}}
\index{m\+\_\+bufsize@{m\+\_\+bufsize}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+bufsize}{m\_bufsize}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+bufsize\hspace{0.3cm}{\ttfamily [private]}}

size of buffer

\mbox{\Hypertarget{classasync__multi__stream__reader_a6486d4f10a3caf9169018d2bb71c4fdc}\label{classasync__multi__stream__reader_a6486d4f10a3caf9169018d2bb71c4fdc}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!m\+\_\+bytes\+\_\+read@{m\+\_\+bytes\+\_\+read}}
\index{m\+\_\+bytes\+\_\+read@{m\+\_\+bytes\+\_\+read}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+bytes\+\_\+read}{m\_bytes\_read}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$\ast$ \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+bytes\+\_\+read\hspace{0.3cm}{\ttfamily [private]}}

io statistics

\mbox{\Hypertarget{classasync__multi__stream__reader_aeedea79263b0e41a5fd3264b26aa39a8}\label{classasync__multi__stream__reader_aeedea79263b0e41a5fd3264b26aa39a8}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!m\+\_\+cur\+\_\+buffer@{m\+\_\+cur\+\_\+buffer}}
\index{m\+\_\+cur\+\_\+buffer@{m\+\_\+cur\+\_\+buffer}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+cur\+\_\+buffer}{m\_cur\_buffer}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{classasync__multi__stream__reader_ad58ad834dc6d741a12be1fb442b8e5d6}{buffer\+\_\+type}$\ast$$\ast$ \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+cur\+\_\+buffer\hspace{0.3cm}{\ttfamily [private]}}

pointer to current buffer for each file

\mbox{\Hypertarget{classasync__multi__stream__reader_a7583fa561610fcc9f620d3ad5539e488}\label{classasync__multi__stream__reader_a7583fa561610fcc9f620d3ad5539e488}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!m\+\_\+cur\+\_\+buffer\+\_\+filled@{m\+\_\+cur\+\_\+buffer\+\_\+filled}}
\index{m\+\_\+cur\+\_\+buffer\+\_\+filled@{m\+\_\+cur\+\_\+buffer\+\_\+filled}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+cur\+\_\+buffer\+\_\+filled}{m\_cur\_buffer\_filled}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$\ast$ \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+cur\+\_\+buffer\+\_\+filled\hspace{0.3cm}{\ttfamily [private]}}

number of items in current buffer for each file

\mbox{\Hypertarget{classasync__multi__stream__reader_a42a6fa935ef4401a70e1ebfff9437d0d}\label{classasync__multi__stream__reader_a42a6fa935ef4401a70e1ebfff9437d0d}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!m\+\_\+cur\+\_\+buffer\+\_\+pos@{m\+\_\+cur\+\_\+buffer\+\_\+pos}}
\index{m\+\_\+cur\+\_\+buffer\+\_\+pos@{m\+\_\+cur\+\_\+buffer\+\_\+pos}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+cur\+\_\+buffer\+\_\+pos}{m\_cur\_buffer\_pos}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$\ast$ \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+cur\+\_\+buffer\+\_\+pos\hspace{0.3cm}{\ttfamily [private]}}

position of next item to be read in current buffer for each file

\mbox{\Hypertarget{classasync__multi__stream__reader_aa8447afd5b6caafe60f2c69be4df23ff}\label{classasync__multi__stream__reader_aa8447afd5b6caafe60f2c69be4df23ff}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!m\+\_\+filenum@{m\+\_\+filenum}}
\index{m\+\_\+filenum@{m\+\_\+filenum}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+filenum}{m\_filenum}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+filenum\hspace{0.3cm}{\ttfamily [private]}}

number of files

\mbox{\Hypertarget{classasync__multi__stream__reader_a9e79f443dd594c3ea539aa97d3f8cb45}\label{classasync__multi__stream__reader_a9e79f443dd594c3ea539aa97d3f8cb45}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!m\+\_\+files@{m\+\_\+files}}
\index{m\+\_\+files@{m\+\_\+files}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+files}{m\_files}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
std\+::\+F\+I\+LE$\ast$$\ast$ \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+files\hspace{0.3cm}{\ttfamily [private]}}

pointers to files

\mbox{\Hypertarget{classasync__multi__stream__reader_a955fea161fa853f416b372699af70b15}\label{classasync__multi__stream__reader_a955fea161fa853f416b372699af70b15}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!m\+\_\+free\+\_\+buffer\+\_\+queues@{m\+\_\+free\+\_\+buffer\+\_\+queues}}
\index{m\+\_\+free\+\_\+buffer\+\_\+queues@{m\+\_\+free\+\_\+buffer\+\_\+queues}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+free\+\_\+buffer\+\_\+queues}{m\_free\_buffer\_queues}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{classasync__multi__stream__reader_a0bf4b801f7d874da5cbbe5c6504d0ecc}{buffer\+\_\+queue\+\_\+type}$\ast$$\ast$ \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+free\+\_\+buffer\+\_\+queues\hspace{0.3cm}{\ttfamily [private]}}

pointers to free buffer queues

\mbox{\Hypertarget{classasync__multi__stream__reader_a57291593ed44d4c1d2586a438bb4d0d6}\label{classasync__multi__stream__reader_a57291593ed44d4c1d2586a438bb4d0d6}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!m\+\_\+full\+\_\+buffer\+\_\+queues@{m\+\_\+full\+\_\+buffer\+\_\+queues}}
\index{m\+\_\+full\+\_\+buffer\+\_\+queues@{m\+\_\+full\+\_\+buffer\+\_\+queues}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+full\+\_\+buffer\+\_\+queues}{m\_full\_buffer\_queues}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{classasync__multi__stream__reader_a0bf4b801f7d874da5cbbe5c6504d0ecc}{buffer\+\_\+queue\+\_\+type}$\ast$$\ast$ \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+full\+\_\+buffer\+\_\+queues\hspace{0.3cm}{\ttfamily [private]}}

pointers to full buffer queues

\mbox{\Hypertarget{classasync__multi__stream__reader_ae3ef39404dd6b7fbc2d8339d4e2c5748}\label{classasync__multi__stream__reader_ae3ef39404dd6b7fbc2d8339d4e2c5748}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!m\+\_\+io\+\_\+threads@{m\+\_\+io\+\_\+threads}}
\index{m\+\_\+io\+\_\+threads@{m\+\_\+io\+\_\+threads}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+io\+\_\+threads}{m\_io\_threads}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
std\+::thread$\ast$$\ast$ \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+io\+\_\+threads\hspace{0.3cm}{\ttfamily [private]}}

pointers to I/O threads

\mbox{\Hypertarget{classasync__multi__stream__reader_acea48aa08da0c9e3065f6c8d00f65ef1}\label{classasync__multi__stream__reader_acea48aa08da0c9e3065f6c8d00f65ef1}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!m\+\_\+items\+\_\+read@{m\+\_\+items\+\_\+read}}
\index{m\+\_\+items\+\_\+read@{m\+\_\+items\+\_\+read}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+items\+\_\+read}{m\_items\_read}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$\ast$ \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+items\+\_\+read\hspace{0.3cm}{\ttfamily [private]}}

items read in each file

\mbox{\Hypertarget{classasync__multi__stream__reader_a47a94d5e9c912c3d448e8039cc650e64}\label{classasync__multi__stream__reader_a47a94d5e9c912c3d448e8039cc650e64}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}!m\+\_\+items\+\_\+toread@{m\+\_\+items\+\_\+toread}}
\index{m\+\_\+items\+\_\+toread@{m\+\_\+items\+\_\+toread}!async\+\_\+multi\+\_\+stream\+\_\+reader@{async\+\_\+multi\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+items\+\_\+toread}{m\_items\_toread}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$\ast$ \hyperlink{classasync__multi__stream__reader}{async\+\_\+multi\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+items\+\_\+toread\hspace{0.3cm}{\ttfamily [private]}}

items to read in each file

The documentation for this class was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{async__stream__reader_8h}{async\+\_\+stream\+\_\+reader.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/classasync__multi__stream__writer.tex
2017/01/24

\hypertarget{classasync__multi__stream__writer}{}\section{async\+\_\+multi\+\_\+stream\+\_\+writer$<$ value\+\_\+type $>$ Class Template Reference}
\label{classasync__multi__stream__writer}\index{async\+\_\+multi\+\_\+stream\+\_\+writer$<$ value\+\_\+type $>$@{async\+\_\+multi\+\_\+stream\+\_\+writer$<$ value\+\_\+type $>$}}

multi-\/stream writer

{\ttfamily \#include $<$async\+\_\+stream\+\_\+writer.\+h$>$}

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{classasync__multi__stream__writer_a7f94653dac5ce376bea3b330942b59b3}{async\+\_\+multi\+\_\+stream\+\_\+writer} (const std\+::string \&\+\_\+fn\+\_\+prefix, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+filenum, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+mem\+\_\+avail=(8ul$<$$<$ 20), const uint64 \&\+\_\+bufnum=4ul)
\begin{DoxyCompactList}\small\item\em constructor \end{DoxyCompactList}\item 
void \hyperlink{classasync__multi__stream__writer_a0290b2d5fdf0368559eee905c09863e7}{write} (const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+file\+\_\+id, const value\+\_\+type \&\+\_\+item)
\begin{DoxyCompactList}\small\item\em write an item \end{DoxyCompactList}\item 
void \hyperlink{classasync__multi__stream__writer_af44e02f6c2eac01f1022b51105ea9cc0}{write} (const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+file\+\_\+id, const value\+\_\+type $\ast$\+\_\+src, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+num)
\begin{DoxyCompactList}\small\item\em write a sequence of items \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{std\+::uint64} \hyperlink{classasync__multi__stream__writer_a196cb6d52ef0d06c585f9e6bba4384b5}{bytes\+\_\+written} () const
\begin{DoxyCompactList}\small\item\em return performed I/O in bytes \end{DoxyCompactList}\item 
\hyperlink{classasync__multi__stream__writer_a26ace952cb25e9ec4a0839d0aafc5e5e}{$\sim$async\+\_\+multi\+\_\+stream\+\_\+writer} ()
\begin{DoxyCompactList}\small\item\em destructor \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Private Types}
\begin{DoxyCompactItemize}
\item 
typedef \hyperlink{structbuffer}{buffer}$<$ value\+\_\+type $>$ \hyperlink{classasync__multi__stream__writer_ae11c006e394241a9a5b003a30e8c8c92}{buffer\+\_\+type}
\item 
typedef \hyperlink{classasync__multi__stream__writer_a1ac00be81314a643563a45cafe6f8660}{buffer\+\_\+queue\+\_\+type}$<$ \hyperlink{classasync__multi__stream__writer_ae11c006e394241a9a5b003a30e8c8c92}{buffer\+\_\+type} $>$ \hyperlink{classasync__multi__stream__writer_a1ac00be81314a643563a45cafe6f8660}{buffer\+\_\+queue\+\_\+type}
\end{DoxyCompactItemize}
\subsection*{Private Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{classasync__multi__stream__writer_ae11c006e394241a9a5b003a30e8c8c92}{buffer\+\_\+type} $\ast$ \hyperlink{classasync__multi__stream__writer_a2598da84bf94a7576d3910e8fc16a18d}{get\+\_\+free\+\_\+buffer} (const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+file\+\_\+idx)
\begin{DoxyCompactList}\small\item\em get a free buffer from the queue \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Static Private Member Functions}
\begin{DoxyCompactItemize}
\item 
{\footnotesize template$<$typename T $>$ }\\static void \hyperlink{classasync__multi__stream__writer_ae0df727c7d673954c263e5b589a8f0c7}{io\+\_\+procedure} (\hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ T $>$ $\ast$\+\_\+caller, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+file\+\_\+idx)
\begin{DoxyCompactList}\small\item\em I/O thread that flush data into disk. \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Private Attributes}
\begin{DoxyCompactItemize}
\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $\ast$ \hyperlink{classasync__multi__stream__writer_a30c3a9ab1270eaff7fe8b2f1a98873b4}{m\+\_\+bytes\+\_\+written}
\begin{DoxyCompactList}\small\item\em I/O statistics. \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__multi__stream__writer_ae22c4cf2e0d2e00668294cfa3ab2c0f7}{m\+\_\+filenum}
\begin{DoxyCompactList}\small\item\em number of files \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__multi__stream__writer_af8bf043c48fb1ad0dfa3e0a562e0e891}{m\+\_\+bufsize}
\begin{DoxyCompactList}\small\item\em size of buffer \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__multi__stream__writer_a60bb0c6df357c9c9719527d812136ef3}{m\+\_\+bufnum}
\begin{DoxyCompactList}\small\item\em number of buffers in a buffer queue for each file \end{DoxyCompactList}\item 
std\+::\+F\+I\+LE $\ast$$\ast$ \hyperlink{classasync__multi__stream__writer_aa5b6be346293202ba59ff0d62f0a1196}{m\+\_\+files}
\begin{DoxyCompactList}\small\item\em handlers of files \end{DoxyCompactList}\item 
\hyperlink{classasync__multi__stream__writer_ae11c006e394241a9a5b003a30e8c8c92}{buffer\+\_\+type} $\ast$ \hyperlink{classasync__multi__stream__writer_af1f19cbe619c771f1786abc038146e72}{cur\+\_\+buffers}
\begin{DoxyCompactList}\small\item\em pointer to current buffer for each file \end{DoxyCompactList}\item 
\hyperlink{classasync__multi__stream__writer_a1ac00be81314a643563a45cafe6f8660}{buffer\+\_\+queue\+\_\+type} $\ast$$\ast$ \hyperlink{classasync__multi__stream__writer_a343172a30658146062d0388b442780f4}{m\+\_\+full\+\_\+buffer\+\_\+queues}
\begin{DoxyCompactList}\small\item\em full buffer queue \end{DoxyCompactList}\item 
\hyperlink{classasync__multi__stream__writer_a1ac00be81314a643563a45cafe6f8660}{buffer\+\_\+queue\+\_\+type} $\ast$$\ast$ \hyperlink{classasync__multi__stream__writer_a892131495e6b74180c6294fe0398301a}{m\+\_\+free\+\_\+buffer\+\_\+queues}
\begin{DoxyCompactList}\small\item\em free buffer queue \end{DoxyCompactList}\item 
std\+::thread $\ast$$\ast$ \hyperlink{classasync__multi__stream__writer_a6d7911a0a48ba0fe496b971cdb85369f}{m\+\_\+io\+\_\+threads}
\begin{DoxyCompactList}\small\item\em queue of io threads \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename value\+\_\+type$>$\newline
class async\+\_\+multi\+\_\+stream\+\_\+writer$<$ value\+\_\+type $>$}

multi-\/stream writer

Main thread write data to multiple files at the same time. For each file, create a set of buffer and an I/O thread to write data to disk by aysnchronous I/O operations.

\subsection{Member Typedef Documentation}
\mbox{\Hypertarget{classasync__multi__stream__writer_a1ac00be81314a643563a45cafe6f8660}\label{classasync__multi__stream__writer_a1ac00be81314a643563a45cafe6f8660}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!buffer\+\_\+queue\+\_\+type@{buffer\+\_\+queue\+\_\+type}}
\index{buffer\+\_\+queue\+\_\+type@{buffer\+\_\+queue\+\_\+type}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{buffer\+\_\+queue\+\_\+type}{buffer\_queue\_type}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
typedef \hyperlink{classasync__multi__stream__writer_a1ac00be81314a643563a45cafe6f8660}{buffer\+\_\+queue\+\_\+type}$<$\hyperlink{classasync__multi__stream__writer_ae11c006e394241a9a5b003a30e8c8c92}{buffer\+\_\+type}$>$ \hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::\hyperlink{classasync__multi__stream__writer_a1ac00be81314a643563a45cafe6f8660}{buffer\+\_\+queue\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{classasync__multi__stream__writer_ae11c006e394241a9a5b003a30e8c8c92}\label{classasync__multi__stream__writer_ae11c006e394241a9a5b003a30e8c8c92}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!buffer\+\_\+type@{buffer\+\_\+type}}
\index{buffer\+\_\+type@{buffer\+\_\+type}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{buffer\+\_\+type}{buffer\_type}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
typedef \hyperlink{structbuffer}{buffer}$<$value\+\_\+type$>$ \hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::\hyperlink{classasync__multi__stream__writer_ae11c006e394241a9a5b003a30e8c8c92}{buffer\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{classasync__multi__stream__writer_a7f94653dac5ce376bea3b330942b59b3}\label{classasync__multi__stream__writer_a7f94653dac5ce376bea3b330942b59b3}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{async\+\_\+multi\+\_\+stream\+\_\+writer()}{async\_multi\_stream\_writer()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::\hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer} (\begin{DoxyParamCaption}\item[{const std\+::string \&}]{\+\_\+fn\+\_\+prefix,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+filenum,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+mem\+\_\+avail = {\ttfamily (8ul~$<$$<$~20)},  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+bufnum = {\ttfamily 4ul} }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor

\mbox{\Hypertarget{classasync__multi__stream__writer_a26ace952cb25e9ec4a0839d0aafc5e5e}\label{classasync__multi__stream__writer_a26ace952cb25e9ec4a0839d0aafc5e5e}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!````~async\+\_\+multi\+\_\+stream\+\_\+writer@{$\sim$async\+\_\+multi\+\_\+stream\+\_\+writer}}
\index{````~async\+\_\+multi\+\_\+stream\+\_\+writer@{$\sim$async\+\_\+multi\+\_\+stream\+\_\+writer}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{$\sim$async\+\_\+multi\+\_\+stream\+\_\+writer()}{~async\_multi\_stream\_writer()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::$\sim$\hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer} (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

destructor

\subsection{Member Function Documentation}
\mbox{\Hypertarget{classasync__multi__stream__writer_a196cb6d52ef0d06c585f9e6bba4384b5}\label{classasync__multi__stream__writer_a196cb6d52ef0d06c585f9e6bba4384b5}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!bytes\+\_\+written@{bytes\+\_\+written}}
\index{bytes\+\_\+written@{bytes\+\_\+written}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{bytes\+\_\+written()}{bytes\_written()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{std\+::uint64} \hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::bytes\+\_\+written (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

return performed I/O in bytes

\mbox{\Hypertarget{classasync__multi__stream__writer_a2598da84bf94a7576d3910e8fc16a18d}\label{classasync__multi__stream__writer_a2598da84bf94a7576d3910e8fc16a18d}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!get\+\_\+free\+\_\+buffer@{get\+\_\+free\+\_\+buffer}}
\index{get\+\_\+free\+\_\+buffer@{get\+\_\+free\+\_\+buffer}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{get\+\_\+free\+\_\+buffer()}{get\_free\_buffer()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{classasync__multi__stream__writer_ae11c006e394241a9a5b003a30e8c8c92}{buffer\+\_\+type}$\ast$ \hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::get\+\_\+free\+\_\+buffer (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+file\+\_\+idx }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [private]}}

get a free buffer from the queue

\mbox{\Hypertarget{classasync__multi__stream__writer_ae0df727c7d673954c263e5b589a8f0c7}\label{classasync__multi__stream__writer_ae0df727c7d673954c263e5b589a8f0c7}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!io\+\_\+procedure@{io\+\_\+procedure}}
\index{io\+\_\+procedure@{io\+\_\+procedure}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{io\+\_\+procedure()}{io\_procedure()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
template$<$typename T $>$ \\
static void \hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::io\+\_\+procedure (\begin{DoxyParamCaption}\item[{\hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ T $>$ $\ast$}]{\+\_\+caller,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+file\+\_\+idx }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [static]}, {\ttfamily [private]}}

I/O thread that flush data into disk.

\mbox{\Hypertarget{classasync__multi__stream__writer_a0290b2d5fdf0368559eee905c09863e7}\label{classasync__multi__stream__writer_a0290b2d5fdf0368559eee905c09863e7}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!write@{write}}
\index{write@{write}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{write()}{write()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
void \hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::write (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+file\+\_\+id,  }\item[{const value\+\_\+type \&}]{\+\_\+item }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

write an item

\mbox{\Hypertarget{classasync__multi__stream__writer_af44e02f6c2eac01f1022b51105ea9cc0}\label{classasync__multi__stream__writer_af44e02f6c2eac01f1022b51105ea9cc0}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!write@{write}}
\index{write@{write}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{write()}{write()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
void \hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::write (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+file\+\_\+id,  }\item[{const value\+\_\+type $\ast$}]{\+\_\+src,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+num }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

write a sequence of items

\subsection{Member Data Documentation}
\mbox{\Hypertarget{classasync__multi__stream__writer_af1f19cbe619c771f1786abc038146e72}\label{classasync__multi__stream__writer_af1f19cbe619c771f1786abc038146e72}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!cur\+\_\+buffers@{cur\+\_\+buffers}}
\index{cur\+\_\+buffers@{cur\+\_\+buffers}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{cur\+\_\+buffers}{cur\_buffers}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{classasync__multi__stream__writer_ae11c006e394241a9a5b003a30e8c8c92}{buffer\+\_\+type}$\ast$ \hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::cur\+\_\+buffers\hspace{0.3cm}{\ttfamily [private]}}

pointer to current buffer for each file

\mbox{\Hypertarget{classasync__multi__stream__writer_a60bb0c6df357c9c9719527d812136ef3}\label{classasync__multi__stream__writer_a60bb0c6df357c9c9719527d812136ef3}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!m\+\_\+bufnum@{m\+\_\+bufnum}}
\index{m\+\_\+bufnum@{m\+\_\+bufnum}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{m\+\_\+bufnum}{m\_bufnum}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::m\+\_\+bufnum\hspace{0.3cm}{\ttfamily [private]}}

number of buffers in a buffer queue for each file

\mbox{\Hypertarget{classasync__multi__stream__writer_af8bf043c48fb1ad0dfa3e0a562e0e891}\label{classasync__multi__stream__writer_af8bf043c48fb1ad0dfa3e0a562e0e891}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!m\+\_\+bufsize@{m\+\_\+bufsize}}
\index{m\+\_\+bufsize@{m\+\_\+bufsize}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{m\+\_\+bufsize}{m\_bufsize}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::m\+\_\+bufsize\hspace{0.3cm}{\ttfamily [private]}}

size of buffer

\mbox{\Hypertarget{classasync__multi__stream__writer_a30c3a9ab1270eaff7fe8b2f1a98873b4}\label{classasync__multi__stream__writer_a30c3a9ab1270eaff7fe8b2f1a98873b4}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!m\+\_\+bytes\+\_\+written@{m\+\_\+bytes\+\_\+written}}
\index{m\+\_\+bytes\+\_\+written@{m\+\_\+bytes\+\_\+written}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{m\+\_\+bytes\+\_\+written}{m\_bytes\_written}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$\ast$ \hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::m\+\_\+bytes\+\_\+written\hspace{0.3cm}{\ttfamily [private]}}

I/O statistics.

\mbox{\Hypertarget{classasync__multi__stream__writer_ae22c4cf2e0d2e00668294cfa3ab2c0f7}\label{classasync__multi__stream__writer_ae22c4cf2e0d2e00668294cfa3ab2c0f7}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!m\+\_\+filenum@{m\+\_\+filenum}}
\index{m\+\_\+filenum@{m\+\_\+filenum}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{m\+\_\+filenum}{m\_filenum}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::m\+\_\+filenum\hspace{0.3cm}{\ttfamily [private]}}

number of files

\mbox{\Hypertarget{classasync__multi__stream__writer_aa5b6be346293202ba59ff0d62f0a1196}\label{classasync__multi__stream__writer_aa5b6be346293202ba59ff0d62f0a1196}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!m\+\_\+files@{m\+\_\+files}}
\index{m\+\_\+files@{m\+\_\+files}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{m\+\_\+files}{m\_files}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
std\+::\+F\+I\+LE$\ast$$\ast$ \hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::m\+\_\+files\hspace{0.3cm}{\ttfamily [private]}}

handlers of files

\mbox{\Hypertarget{classasync__multi__stream__writer_a892131495e6b74180c6294fe0398301a}\label{classasync__multi__stream__writer_a892131495e6b74180c6294fe0398301a}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!m\+\_\+free\+\_\+buffer\+\_\+queues@{m\+\_\+free\+\_\+buffer\+\_\+queues}}
\index{m\+\_\+free\+\_\+buffer\+\_\+queues@{m\+\_\+free\+\_\+buffer\+\_\+queues}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{m\+\_\+free\+\_\+buffer\+\_\+queues}{m\_free\_buffer\_queues}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{classasync__multi__stream__writer_a1ac00be81314a643563a45cafe6f8660}{buffer\+\_\+queue\+\_\+type}$\ast$$\ast$ \hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::m\+\_\+free\+\_\+buffer\+\_\+queues\hspace{0.3cm}{\ttfamily [private]}}

free buffer queue

\mbox{\Hypertarget{classasync__multi__stream__writer_a343172a30658146062d0388b442780f4}\label{classasync__multi__stream__writer_a343172a30658146062d0388b442780f4}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!m\+\_\+full\+\_\+buffer\+\_\+queues@{m\+\_\+full\+\_\+buffer\+\_\+queues}}
\index{m\+\_\+full\+\_\+buffer\+\_\+queues@{m\+\_\+full\+\_\+buffer\+\_\+queues}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{m\+\_\+full\+\_\+buffer\+\_\+queues}{m\_full\_buffer\_queues}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
\hyperlink{classasync__multi__stream__writer_a1ac00be81314a643563a45cafe6f8660}{buffer\+\_\+queue\+\_\+type}$\ast$$\ast$ \hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::m\+\_\+full\+\_\+buffer\+\_\+queues\hspace{0.3cm}{\ttfamily [private]}}

full buffer queue

\mbox{\Hypertarget{classasync__multi__stream__writer_a6d7911a0a48ba0fe496b971cdb85369f}\label{classasync__multi__stream__writer_a6d7911a0a48ba0fe496b971cdb85369f}} 
\index{async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}!m\+\_\+io\+\_\+threads@{m\+\_\+io\+\_\+threads}}
\index{m\+\_\+io\+\_\+threads@{m\+\_\+io\+\_\+threads}!async\+\_\+multi\+\_\+stream\+\_\+writer@{async\+\_\+multi\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{m\+\_\+io\+\_\+threads}{m\_io\_threads}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type $>$ \\
std\+::thread$\ast$$\ast$ \hyperlink{classasync__multi__stream__writer}{async\+\_\+multi\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::m\+\_\+io\+\_\+threads\hspace{0.3cm}{\ttfamily [private]}}

queue of io threads

The documentation for this class was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{async__stream__writer_8h}{async\+\_\+stream\+\_\+writer.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/classasync__stream__reader.tex
2017/01/24

\hypertarget{classasync__stream__reader}{}\section{async\+\_\+stream\+\_\+reader$<$ value\+\_\+type $>$ Class Template Reference}
\label{classasync__stream__reader}\index{async\+\_\+stream\+\_\+reader$<$ value\+\_\+type $>$@{async\+\_\+stream\+\_\+reader$<$ value\+\_\+type $>$}}

read data from an external disk file using asynchronous stream

{\ttfamily \#include $<$async\+\_\+stream\+\_\+reader.\+h$>$}

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
void \hyperlink{classasync__stream__reader_a15c2bd3c259b3a84de866c02dd6c7405}{get\+\_\+full\+\_\+buffer} ()
\begin{DoxyCompactList}\small\item\em get a full buffer \end{DoxyCompactList}\item 
\hyperlink{classasync__stream__reader_a02dc7a7adb24a552a265b30ba8544223}{async\+\_\+stream\+\_\+reader} (const std\+::string \&\+\_\+fn, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+avail\+\_\+mem=(8ul$<$$<$ 20), const uint64 \&\+\_\+bufnum=4ul)
\begin{DoxyCompactList}\small\item\em ctor, available buffer size is given, skip a number of bytes \end{DoxyCompactList}\item 
value\+\_\+type \hyperlink{classasync__stream__reader_abb382de67d33724ff4fea6714fc67ac8}{read} ()
\begin{DoxyCompactList}\small\item\em get next element in the stream \end{DoxyCompactList}\item 
void \hyperlink{classasync__stream__reader_ac441a02e7bb4708948552ce7ced4e9d4}{read} (value\+\_\+type $\ast$\+\_\+des, \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \+\_\+num)
\begin{DoxyCompactList}\small\item\em read a sequence of items in the stream \end{DoxyCompactList}\item 
void \hyperlink{classasync__stream__reader_a66bc0e20739b27b9c703be9254cdbe05}{skip} (\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \+\_\+num)
\begin{DoxyCompactList}\small\item\em skip a sequence of elements in the stream \end{DoxyCompactList}\item 
bool \hyperlink{classasync__stream__reader_accade2559119f3bed538d20f6eec4cfb}{empty} ()
\begin{DoxyCompactList}\small\item\em check if empty \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__stream__reader_a15f6c24ea5065855b1d5df69cc7e3e1a}{bytes\+\_\+read} () const
\begin{DoxyCompactList}\small\item\em get read bytes \end{DoxyCompactList}\item 
\hyperlink{classasync__stream__reader_acfbb53847f349372dd3bb0455d9dfaa9}{$\sim$async\+\_\+stream\+\_\+reader} ()
\begin{DoxyCompactList}\small\item\em destructor \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Private Types}
\begin{DoxyCompactItemize}
\item 
typedef \hyperlink{structbuffer}{buffer}$<$ value\+\_\+type $>$ \hyperlink{classasync__stream__reader_a48e2b7d24cfceba922a771e9c314b40c}{buffer\+\_\+type}
\item 
typedef \hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ value\+\_\+type $>$ \hyperlink{classasync__stream__reader_a5301e887b098a0ade898265ca6935d68}{buffer\+\_\+queue\+\_\+type}
\end{DoxyCompactItemize}
\subsection*{Static Private Member Functions}
\begin{DoxyCompactItemize}
\item 
{\footnotesize template$<$typename T $>$ }\\static void \hyperlink{classasync__stream__reader_aee14e37431d75f5a80831ce6c3632ea2}{io\+\_\+procedure} (\hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ T $>$ $\ast$\+\_\+caller)
\begin{DoxyCompactList}\small\item\em I/O procedure that load data into R\+AM using aysnchronous I/O operations. \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Private Attributes}
\begin{DoxyCompactItemize}
\item 
std\+::\+F\+I\+LE $\ast$ \hyperlink{classasync__stream__reader_ae071a19d938b35853aecdef137a3cfdb}{m\+\_\+file}
\begin{DoxyCompactList}\small\item\em file pointer \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__stream__reader_a5268366ca42bd2ef430e9e0817e9b274}{m\+\_\+bytes\+\_\+read}
\begin{DoxyCompactList}\small\item\em number of bytes already read \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__stream__reader_a8a1fa1966f7523fd4054e06cdd118234}{m\+\_\+cur\+\_\+buffer\+\_\+pos}
\begin{DoxyCompactList}\small\item\em pos of next element to be read in current buffer \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__stream__reader_a0414700ede611b3cbf26ef640c239709}{m\+\_\+cur\+\_\+buffer\+\_\+filled}
\begin{DoxyCompactList}\small\item\em number of elements in current buffer \end{DoxyCompactList}\item 
\hyperlink{classasync__stream__reader_a48e2b7d24cfceba922a771e9c314b40c}{buffer\+\_\+type} $\ast$ \hyperlink{classasync__stream__reader_a167103fd4cb153047682ec786d234f2f}{m\+\_\+cur\+\_\+buffer}
\begin{DoxyCompactList}\small\item\em pointer to current buffer \end{DoxyCompactList}\item 
std\+::thread $\ast$ \hyperlink{classasync__stream__reader_a50b44a356f5c742f20d7ea31bebc018e}{m\+\_\+io\+\_\+thread}
\begin{DoxyCompactList}\small\item\em io thread \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__stream__reader_acbf67b037e53db6a995079a8e9ffac57}{m\+\_\+items\+\_\+toread}
\begin{DoxyCompactList}\small\item\em number of items to read \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__stream__reader_a81e8aa844cad035565f9c194a0d3968b}{m\+\_\+items\+\_\+read}
\begin{DoxyCompactList}\small\item\em number of items read \end{DoxyCompactList}\item 
\hyperlink{classasync__stream__reader_a5301e887b098a0ade898265ca6935d68}{buffer\+\_\+queue\+\_\+type} $\ast$ \hyperlink{classasync__stream__reader_a15a955920c4b23bd70ef0b9e5aebf0df}{m\+\_\+free\+\_\+buffers}
\begin{DoxyCompactList}\small\item\em queue of free buffers \end{DoxyCompactList}\item 
\hyperlink{classasync__stream__reader_a5301e887b098a0ade898265ca6935d68}{buffer\+\_\+queue\+\_\+type} $\ast$ \hyperlink{classasync__stream__reader_a5713212cfddf2a29459e70a8d2852a44}{m\+\_\+full\+\_\+buffers}
\begin{DoxyCompactList}\small\item\em queue of full buffers \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename value\+\_\+type$>$\newline
class async\+\_\+stream\+\_\+reader$<$ value\+\_\+type $>$}

read data from an external disk file using asynchronous stream

I/O thread continually continually do the following steps\+: (1) retrieve a buffer from empty-\/buffer queue (2) load data into buffer (3) put buffer into full-\/buffer queue main thread read elements as following\+: if current buffer is not finished read, then read the next element; otherwise, put current buffer into empty-\/buffer queue and retrieve a buffer from full-\/buffer queue.

\subsection{Member Typedef Documentation}
\mbox{\Hypertarget{classasync__stream__reader_a5301e887b098a0ade898265ca6935d68}\label{classasync__stream__reader_a5301e887b098a0ade898265ca6935d68}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!buffer\+\_\+queue\+\_\+type@{buffer\+\_\+queue\+\_\+type}}
\index{buffer\+\_\+queue\+\_\+type@{buffer\+\_\+queue\+\_\+type}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{buffer\+\_\+queue\+\_\+type}{buffer\_queue\_type}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
typedef \hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$value\+\_\+type$>$ \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::\hyperlink{classasync__stream__reader_a5301e887b098a0ade898265ca6935d68}{buffer\+\_\+queue\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{classasync__stream__reader_a48e2b7d24cfceba922a771e9c314b40c}\label{classasync__stream__reader_a48e2b7d24cfceba922a771e9c314b40c}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!buffer\+\_\+type@{buffer\+\_\+type}}
\index{buffer\+\_\+type@{buffer\+\_\+type}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{buffer\+\_\+type}{buffer\_type}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
typedef \hyperlink{structbuffer}{buffer}$<$value\+\_\+type$>$ \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::\hyperlink{classasync__stream__reader_a48e2b7d24cfceba922a771e9c314b40c}{buffer\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{classasync__stream__reader_a02dc7a7adb24a552a265b30ba8544223}\label{classasync__stream__reader_a02dc7a7adb24a552a265b30ba8544223}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{async\+\_\+stream\+\_\+reader()}{async\_stream\_reader()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::\hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader} (\begin{DoxyParamCaption}\item[{const std\+::string \&}]{\+\_\+fn,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+avail\+\_\+mem = {\ttfamily (8ul~$<$$<$~20)},  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+bufnum = {\ttfamily 4ul} }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

ctor, available buffer size is given, skip a number of bytes

\begin{DoxyParams}{Parameters}
{\em \+\_\+fn} & filename \\
\hline
{\em \+\_\+avail\+\_\+mem} & available memory in bytes \\
\hline
{\em \+\_\+bufnum} & number of buffers \\
\hline
{\em \+\_\+skip\+\_\+bytes} & number of byts to skip \\
\hline
\end{DoxyParams}
\mbox{\Hypertarget{classasync__stream__reader_acfbb53847f349372dd3bb0455d9dfaa9}\label{classasync__stream__reader_acfbb53847f349372dd3bb0455d9dfaa9}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!````~async\+\_\+stream\+\_\+reader@{$\sim$async\+\_\+stream\+\_\+reader}}
\index{````~async\+\_\+stream\+\_\+reader@{$\sim$async\+\_\+stream\+\_\+reader}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{$\sim$async\+\_\+stream\+\_\+reader()}{~async\_stream\_reader()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::$\sim$\hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader} (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

destructor

\subsection{Member Function Documentation}
\mbox{\Hypertarget{classasync__stream__reader_a15f6c24ea5065855b1d5df69cc7e3e1a}\label{classasync__stream__reader_a15f6c24ea5065855b1d5df69cc7e3e1a}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!bytes\+\_\+read@{bytes\+\_\+read}}
\index{bytes\+\_\+read@{bytes\+\_\+read}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{bytes\+\_\+read()}{bytes\_read()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::bytes\+\_\+read (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

get read bytes

\mbox{\Hypertarget{classasync__stream__reader_accade2559119f3bed538d20f6eec4cfb}\label{classasync__stream__reader_accade2559119f3bed538d20f6eec4cfb}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!empty@{empty}}
\index{empty@{empty}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{empty()}{empty()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
bool \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::empty (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

check if empty

\mbox{\Hypertarget{classasync__stream__reader_a15c2bd3c259b3a84de866c02dd6c7405}\label{classasync__stream__reader_a15c2bd3c259b3a84de866c02dd6c7405}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!get\+\_\+full\+\_\+buffer@{get\+\_\+full\+\_\+buffer}}
\index{get\+\_\+full\+\_\+buffer@{get\+\_\+full\+\_\+buffer}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{get\+\_\+full\+\_\+buffer()}{get\_full\_buffer()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
void \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::get\+\_\+full\+\_\+buffer (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

get a full buffer

\mbox{\Hypertarget{classasync__stream__reader_aee14e37431d75f5a80831ce6c3632ea2}\label{classasync__stream__reader_aee14e37431d75f5a80831ce6c3632ea2}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!io\+\_\+procedure@{io\+\_\+procedure}}
\index{io\+\_\+procedure@{io\+\_\+procedure}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{io\+\_\+procedure()}{io\_procedure()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
template$<$typename T $>$ \\
static void \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::io\+\_\+procedure (\begin{DoxyParamCaption}\item[{\hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ T $>$ $\ast$}]{\+\_\+caller }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [static]}, {\ttfamily [private]}}

I/O procedure that load data into R\+AM using aysnchronous I/O operations.

\mbox{\Hypertarget{classasync__stream__reader_abb382de67d33724ff4fea6714fc67ac8}\label{classasync__stream__reader_abb382de67d33724ff4fea6714fc67ac8}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!read@{read}}
\index{read@{read}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{read()}{read()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
value\+\_\+type \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::read (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

get next element in the stream

\begin{DoxyNote}{Note}
check if empty before calling the function 
\end{DoxyNote}
\mbox{\Hypertarget{classasync__stream__reader_ac441a02e7bb4708948552ce7ced4e9d4}\label{classasync__stream__reader_ac441a02e7bb4708948552ce7ced4e9d4}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!read@{read}}
\index{read@{read}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{read()}{read()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
void \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::read (\begin{DoxyParamCaption}\item[{value\+\_\+type $\ast$}]{\+\_\+des,  }\item[{\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}]{\+\_\+num }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

read a sequence of items in the stream

\begin{DoxyParams}{Parameters}
{\em \+\_\+des} & target container \\
\hline
{\em \+\_\+num} & number of elements to be read \\
\hline
\end{DoxyParams}
\begin{DoxyNote}{Note}
check if empty before calling the function 
\end{DoxyNote}
\mbox{\Hypertarget{classasync__stream__reader_a66bc0e20739b27b9c703be9254cdbe05}\label{classasync__stream__reader_a66bc0e20739b27b9c703be9254cdbe05}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!skip@{skip}}
\index{skip@{skip}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{skip()}{skip()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
void \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::skip (\begin{DoxyParamCaption}\item[{\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}]{\+\_\+num }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

skip a sequence of elements in the stream

\begin{DoxyParams}{Parameters}
{\em \+\_\+num} & number of elements to be skipped \\
\hline
\end{DoxyParams}

\subsection{Member Data Documentation}
\mbox{\Hypertarget{classasync__stream__reader_a5268366ca42bd2ef430e9e0817e9b274}\label{classasync__stream__reader_a5268366ca42bd2ef430e9e0817e9b274}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!m\+\_\+bytes\+\_\+read@{m\+\_\+bytes\+\_\+read}}
\index{m\+\_\+bytes\+\_\+read@{m\+\_\+bytes\+\_\+read}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+bytes\+\_\+read}{m\_bytes\_read}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+bytes\+\_\+read\hspace{0.3cm}{\ttfamily [private]}}

number of bytes already read

\mbox{\Hypertarget{classasync__stream__reader_a167103fd4cb153047682ec786d234f2f}\label{classasync__stream__reader_a167103fd4cb153047682ec786d234f2f}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!m\+\_\+cur\+\_\+buffer@{m\+\_\+cur\+\_\+buffer}}
\index{m\+\_\+cur\+\_\+buffer@{m\+\_\+cur\+\_\+buffer}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+cur\+\_\+buffer}{m\_cur\_buffer}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{classasync__stream__reader_a48e2b7d24cfceba922a771e9c314b40c}{buffer\+\_\+type}$\ast$ \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+cur\+\_\+buffer\hspace{0.3cm}{\ttfamily [private]}}

pointer to current buffer

\mbox{\Hypertarget{classasync__stream__reader_a0414700ede611b3cbf26ef640c239709}\label{classasync__stream__reader_a0414700ede611b3cbf26ef640c239709}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!m\+\_\+cur\+\_\+buffer\+\_\+filled@{m\+\_\+cur\+\_\+buffer\+\_\+filled}}
\index{m\+\_\+cur\+\_\+buffer\+\_\+filled@{m\+\_\+cur\+\_\+buffer\+\_\+filled}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+cur\+\_\+buffer\+\_\+filled}{m\_cur\_buffer\_filled}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+cur\+\_\+buffer\+\_\+filled\hspace{0.3cm}{\ttfamily [private]}}

number of elements in current buffer

\mbox{\Hypertarget{classasync__stream__reader_a8a1fa1966f7523fd4054e06cdd118234}\label{classasync__stream__reader_a8a1fa1966f7523fd4054e06cdd118234}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!m\+\_\+cur\+\_\+buffer\+\_\+pos@{m\+\_\+cur\+\_\+buffer\+\_\+pos}}
\index{m\+\_\+cur\+\_\+buffer\+\_\+pos@{m\+\_\+cur\+\_\+buffer\+\_\+pos}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+cur\+\_\+buffer\+\_\+pos}{m\_cur\_buffer\_pos}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+cur\+\_\+buffer\+\_\+pos\hspace{0.3cm}{\ttfamily [private]}}

pos of next element to be read in current buffer

\mbox{\Hypertarget{classasync__stream__reader_ae071a19d938b35853aecdef137a3cfdb}\label{classasync__stream__reader_ae071a19d938b35853aecdef137a3cfdb}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!m\+\_\+file@{m\+\_\+file}}
\index{m\+\_\+file@{m\+\_\+file}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+file}{m\_file}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
std\+::\+F\+I\+LE$\ast$ \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+file\hspace{0.3cm}{\ttfamily [private]}}

file pointer

\mbox{\Hypertarget{classasync__stream__reader_a15a955920c4b23bd70ef0b9e5aebf0df}\label{classasync__stream__reader_a15a955920c4b23bd70ef0b9e5aebf0df}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!m\+\_\+free\+\_\+buffers@{m\+\_\+free\+\_\+buffers}}
\index{m\+\_\+free\+\_\+buffers@{m\+\_\+free\+\_\+buffers}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+free\+\_\+buffers}{m\_free\_buffers}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{classasync__stream__reader_a5301e887b098a0ade898265ca6935d68}{buffer\+\_\+queue\+\_\+type}$\ast$ \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+free\+\_\+buffers\hspace{0.3cm}{\ttfamily [private]}}

queue of free buffers

\mbox{\Hypertarget{classasync__stream__reader_a5713212cfddf2a29459e70a8d2852a44}\label{classasync__stream__reader_a5713212cfddf2a29459e70a8d2852a44}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!m\+\_\+full\+\_\+buffers@{m\+\_\+full\+\_\+buffers}}
\index{m\+\_\+full\+\_\+buffers@{m\+\_\+full\+\_\+buffers}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+full\+\_\+buffers}{m\_full\_buffers}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{classasync__stream__reader_a5301e887b098a0ade898265ca6935d68}{buffer\+\_\+queue\+\_\+type}$\ast$ \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+full\+\_\+buffers\hspace{0.3cm}{\ttfamily [private]}}

queue of full buffers

\mbox{\Hypertarget{classasync__stream__reader_a50b44a356f5c742f20d7ea31bebc018e}\label{classasync__stream__reader_a50b44a356f5c742f20d7ea31bebc018e}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!m\+\_\+io\+\_\+thread@{m\+\_\+io\+\_\+thread}}
\index{m\+\_\+io\+\_\+thread@{m\+\_\+io\+\_\+thread}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+io\+\_\+thread}{m\_io\_thread}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
std\+::thread$\ast$ \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+io\+\_\+thread\hspace{0.3cm}{\ttfamily [private]}}

io thread

\mbox{\Hypertarget{classasync__stream__reader_a81e8aa844cad035565f9c194a0d3968b}\label{classasync__stream__reader_a81e8aa844cad035565f9c194a0d3968b}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!m\+\_\+items\+\_\+read@{m\+\_\+items\+\_\+read}}
\index{m\+\_\+items\+\_\+read@{m\+\_\+items\+\_\+read}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+items\+\_\+read}{m\_items\_read}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+items\+\_\+read\hspace{0.3cm}{\ttfamily [private]}}

number of items read

\mbox{\Hypertarget{classasync__stream__reader_acbf67b037e53db6a995079a8e9ffac57}\label{classasync__stream__reader_acbf67b037e53db6a995079a8e9ffac57}} 
\index{async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}!m\+\_\+items\+\_\+toread@{m\+\_\+items\+\_\+toread}}
\index{m\+\_\+items\+\_\+toread@{m\+\_\+items\+\_\+toread}!async\+\_\+stream\+\_\+reader@{async\+\_\+stream\+\_\+reader}}
\subsubsection{\texorpdfstring{m\+\_\+items\+\_\+toread}{m\_items\_toread}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__stream__reader}{async\+\_\+stream\+\_\+reader}$<$ value\+\_\+type $>$\+::m\+\_\+items\+\_\+toread\hspace{0.3cm}{\ttfamily [private]}}

number of items to read

The documentation for this class was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{async__stream__reader_8h}{async\+\_\+stream\+\_\+reader.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/classasync__stream__writer.tex
2017/01/24

\hypertarget{classasync__stream__writer}{}\section{async\+\_\+stream\+\_\+writer$<$ value\+\_\+type $>$ Class Template Reference}
\label{classasync__stream__writer}\index{async\+\_\+stream\+\_\+writer$<$ value\+\_\+type $>$@{async\+\_\+stream\+\_\+writer$<$ value\+\_\+type $>$}}

write data into a disk file using an asynchronous stream

{\ttfamily \#include $<$async\+\_\+stream\+\_\+writer.\+h$>$}

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{classasync__stream__writer_a11b5cdf01df7a627d00c6e77be165702}{async\+\_\+stream\+\_\+writer} (const std\+::string \+\_\+fn, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+avail\+\_\+mem=(8ul$<$$<$ 20), const uint64 \&\+\_\+bufnum=4ul, const std\+::string \&\+\_\+mode=std\+::string(\char`\"{}w\char`\"{}))
\begin{DoxyCompactList}\small\item\em constructor \end{DoxyCompactList}\item 
void \hyperlink{classasync__stream__writer_afb36228f86866b4eb65343fd313754cc}{write} (const value\+\_\+type \&\+\_\+item)
\begin{DoxyCompactList}\small\item\em write an element into stream \end{DoxyCompactList}\item 
void \hyperlink{classasync__stream__writer_a95a073a12efffbb4d0f1417abef06ab3}{write} (const value\+\_\+type $\ast$\+\_\+src, \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \+\_\+num)
\begin{DoxyCompactList}\small\item\em write a sequence of items into the stream \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__stream__writer_a6fd98bbc41adf1cd51468ee490608d6e}{bytes\+\_\+written} () const
\begin{DoxyCompactList}\small\item\em collect I/O bytes \end{DoxyCompactList}\item 
\hyperlink{classasync__stream__writer_ac001ff454b249e4f71b4f92755017334}{$\sim$async\+\_\+stream\+\_\+writer} ()
\begin{DoxyCompactList}\small\item\em dtor \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Private Types}
\begin{DoxyCompactItemize}
\item 
typedef \hyperlink{structbuffer}{buffer}$<$ value\+\_\+type $>$ \hyperlink{classasync__stream__writer_a7e813664993581eab8d5fc6bcff2ce19}{buffer\+\_\+type}
\item 
typedef \hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ \hyperlink{classasync__stream__writer_a7e813664993581eab8d5fc6bcff2ce19}{buffer\+\_\+type} $>$ \hyperlink{classasync__stream__writer_a44dba276c5208314653dd887010e7161}{buffer\+\_\+queue\+\_\+type}
\end{DoxyCompactItemize}
\subsection*{Private Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{classasync__stream__writer_a7e813664993581eab8d5fc6bcff2ce19}{buffer\+\_\+type} $\ast$ \hyperlink{classasync__stream__writer_ad73941af15cf207e12376db3e2ffbfcd}{get\+\_\+free\+\_\+buffer} ()
\begin{DoxyCompactList}\small\item\em get a free buffer \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Static Private Member Functions}
\begin{DoxyCompactItemize}
\item 
{\footnotesize template$<$typename T $>$ }\\static void \hyperlink{classasync__stream__writer_a5fcc9c840654d18ba14668e43a3a0f31}{io\+\_\+procedure} (\hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ T $>$ $\ast$\+\_\+caller)
\begin{DoxyCompactList}\small\item\em I/O thread procedure. \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Private Attributes}
\begin{DoxyCompactItemize}
\item 
\hyperlink{classasync__stream__writer_a44dba276c5208314653dd887010e7161}{buffer\+\_\+queue\+\_\+type} $\ast$ \hyperlink{classasync__stream__writer_ad451ef8f2eb1c884b38cd10f387ac325}{m\+\_\+free\+\_\+buffers}
\begin{DoxyCompactList}\small\item\em empty-\/buffer queue \end{DoxyCompactList}\item 
\hyperlink{classasync__stream__writer_a44dba276c5208314653dd887010e7161}{buffer\+\_\+queue\+\_\+type} $\ast$ \hyperlink{classasync__stream__writer_a091edd8f3eab9d64c3bc3396d4fb7994}{m\+\_\+full\+\_\+buffers}
\begin{DoxyCompactList}\small\item\em full-\/buffer queue \end{DoxyCompactList}\item 
std\+::\+F\+I\+LE $\ast$ \hyperlink{classasync__stream__writer_ac8b191bccfc233007594d07c1bb228d4}{m\+\_\+file}
\begin{DoxyCompactList}\small\item\em file handler \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__stream__writer_a2e6bf4e33430ee652475dea9ce1ec7c5}{m\+\_\+bytes\+\_\+written}
\begin{DoxyCompactList}\small\item\em I/O statistics. \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__stream__writer_aea362e479496cec38f62cfe60402a390}{m\+\_\+bufsize}
\begin{DoxyCompactList}\small\item\em buffer size \end{DoxyCompactList}\item 
\hyperlink{classasync__stream__writer_a7e813664993581eab8d5fc6bcff2ce19}{buffer\+\_\+type} $\ast$ \hyperlink{classasync__stream__writer_aad27ed30f3cc0ac67c171894ff286871}{m\+\_\+cur\+\_\+buffer}
\begin{DoxyCompactList}\small\item\em pointer to current buffer \end{DoxyCompactList}\item 
std\+::thread $\ast$ \hyperlink{classasync__stream__writer_a4298b5c3a6950422907f0e59580386dd}{m\+\_\+io\+\_\+thread}
\begin{DoxyCompactList}\small\item\em pointer to I/O thread \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename value\+\_\+type$>$\newline
class async\+\_\+stream\+\_\+writer$<$ value\+\_\+type $>$}

write data into a disk file using an asynchronous stream

\subsection{Member Typedef Documentation}
\mbox{\Hypertarget{classasync__stream__writer_a44dba276c5208314653dd887010e7161}\label{classasync__stream__writer_a44dba276c5208314653dd887010e7161}} 
\index{async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}!buffer\+\_\+queue\+\_\+type@{buffer\+\_\+queue\+\_\+type}}
\index{buffer\+\_\+queue\+\_\+type@{buffer\+\_\+queue\+\_\+type}!async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{buffer\+\_\+queue\+\_\+type}{buffer\_queue\_type}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
typedef \hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$\hyperlink{classasync__stream__writer_a7e813664993581eab8d5fc6bcff2ce19}{buffer\+\_\+type}$>$ \hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::\hyperlink{classasync__stream__writer_a44dba276c5208314653dd887010e7161}{buffer\+\_\+queue\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{classasync__stream__writer_a7e813664993581eab8d5fc6bcff2ce19}\label{classasync__stream__writer_a7e813664993581eab8d5fc6bcff2ce19}} 
\index{async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}!buffer\+\_\+type@{buffer\+\_\+type}}
\index{buffer\+\_\+type@{buffer\+\_\+type}!async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{buffer\+\_\+type}{buffer\_type}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
typedef \hyperlink{structbuffer}{buffer}$<$value\+\_\+type$>$ \hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::\hyperlink{classasync__stream__writer_a7e813664993581eab8d5fc6bcff2ce19}{buffer\+\_\+type}\hspace{0.3cm}{\ttfamily [private]}}

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{classasync__stream__writer_a11b5cdf01df7a627d00c6e77be165702}\label{classasync__stream__writer_a11b5cdf01df7a627d00c6e77be165702}} 
\index{async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}!async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}}
\index{async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}!async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{async\+\_\+stream\+\_\+writer()}{async\_stream\_writer()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::\hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer} (\begin{DoxyParamCaption}\item[{const std\+::string}]{\+\_\+fn,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+avail\+\_\+mem = {\ttfamily (8ul~$<$$<$~20)},  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+bufnum = {\ttfamily 4ul},  }\item[{const std\+::string \&}]{\+\_\+mode = {\ttfamily std\+:\+:string(\char`\"{}w\char`\"{})} }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor

\mbox{\Hypertarget{classasync__stream__writer_ac001ff454b249e4f71b4f92755017334}\label{classasync__stream__writer_ac001ff454b249e4f71b4f92755017334}} 
\index{async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}!````~async\+\_\+stream\+\_\+writer@{$\sim$async\+\_\+stream\+\_\+writer}}
\index{````~async\+\_\+stream\+\_\+writer@{$\sim$async\+\_\+stream\+\_\+writer}!async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{$\sim$async\+\_\+stream\+\_\+writer()}{~async\_stream\_writer()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::$\sim$\hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer} (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

dtor

\subsection{Member Function Documentation}
\mbox{\Hypertarget{classasync__stream__writer_a6fd98bbc41adf1cd51468ee490608d6e}\label{classasync__stream__writer_a6fd98bbc41adf1cd51468ee490608d6e}} 
\index{async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}!bytes\+\_\+written@{bytes\+\_\+written}}
\index{bytes\+\_\+written@{bytes\+\_\+written}!async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{bytes\+\_\+written()}{bytes\_written()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::bytes\+\_\+written (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

collect I/O bytes

\mbox{\Hypertarget{classasync__stream__writer_ad73941af15cf207e12376db3e2ffbfcd}\label{classasync__stream__writer_ad73941af15cf207e12376db3e2ffbfcd}} 
\index{async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}!get\+\_\+free\+\_\+buffer@{get\+\_\+free\+\_\+buffer}}
\index{get\+\_\+free\+\_\+buffer@{get\+\_\+free\+\_\+buffer}!async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{get\+\_\+free\+\_\+buffer()}{get\_free\_buffer()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{classasync__stream__writer_a7e813664993581eab8d5fc6bcff2ce19}{buffer\+\_\+type}$\ast$ \hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::get\+\_\+free\+\_\+buffer (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [private]}}

get a free buffer

\begin{DoxyNote}{Note}
can always get an empty buffer 
\end{DoxyNote}
\mbox{\Hypertarget{classasync__stream__writer_a5fcc9c840654d18ba14668e43a3a0f31}\label{classasync__stream__writer_a5fcc9c840654d18ba14668e43a3a0f31}} 
\index{async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}!io\+\_\+procedure@{io\+\_\+procedure}}
\index{io\+\_\+procedure@{io\+\_\+procedure}!async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{io\+\_\+procedure()}{io\_procedure()}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
template$<$typename T $>$ \\
static void \hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::io\+\_\+procedure (\begin{DoxyParamCaption}\item[{\hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ T $>$ $\ast$}]{\+\_\+caller }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [static]}, {\ttfamily [private]}}

I/O thread procedure.

\mbox{\Hypertarget{classasync__stream__writer_afb36228f86866b4eb65343fd313754cc}\label{classasync__stream__writer_afb36228f86866b4eb65343fd313754cc}} 
\index{async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}!write@{write}}
\index{write@{write}!async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{write()}{write()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
void \hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::write (\begin{DoxyParamCaption}\item[{const value\+\_\+type \&}]{\+\_\+item }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

write an element into stream

\mbox{\Hypertarget{classasync__stream__writer_a95a073a12efffbb4d0f1417abef06ab3}\label{classasync__stream__writer_a95a073a12efffbb4d0f1417abef06ab3}} 
\index{async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}!write@{write}}
\index{write@{write}!async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{write()}{write()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
void \hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::write (\begin{DoxyParamCaption}\item[{const value\+\_\+type $\ast$}]{\+\_\+src,  }\item[{\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}]{\+\_\+num }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

write a sequence of items into the stream

\subsection{Member Data Documentation}
\mbox{\Hypertarget{classasync__stream__writer_aea362e479496cec38f62cfe60402a390}\label{classasync__stream__writer_aea362e479496cec38f62cfe60402a390}} 
\index{async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}!m\+\_\+bufsize@{m\+\_\+bufsize}}
\index{m\+\_\+bufsize@{m\+\_\+bufsize}!async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{m\+\_\+bufsize}{m\_bufsize}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::m\+\_\+bufsize\hspace{0.3cm}{\ttfamily [private]}}

buffer size

\mbox{\Hypertarget{classasync__stream__writer_a2e6bf4e33430ee652475dea9ce1ec7c5}\label{classasync__stream__writer_a2e6bf4e33430ee652475dea9ce1ec7c5}} 
\index{async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}!m\+\_\+bytes\+\_\+written@{m\+\_\+bytes\+\_\+written}}
\index{m\+\_\+bytes\+\_\+written@{m\+\_\+bytes\+\_\+written}!async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{m\+\_\+bytes\+\_\+written}{m\_bytes\_written}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::m\+\_\+bytes\+\_\+written\hspace{0.3cm}{\ttfamily [private]}}

I/O statistics.

\mbox{\Hypertarget{classasync__stream__writer_aad27ed30f3cc0ac67c171894ff286871}\label{classasync__stream__writer_aad27ed30f3cc0ac67c171894ff286871}} 
\index{async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}!m\+\_\+cur\+\_\+buffer@{m\+\_\+cur\+\_\+buffer}}
\index{m\+\_\+cur\+\_\+buffer@{m\+\_\+cur\+\_\+buffer}!async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{m\+\_\+cur\+\_\+buffer}{m\_cur\_buffer}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{classasync__stream__writer_a7e813664993581eab8d5fc6bcff2ce19}{buffer\+\_\+type}$\ast$ \hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::m\+\_\+cur\+\_\+buffer\hspace{0.3cm}{\ttfamily [private]}}

pointer to current buffer

\mbox{\Hypertarget{classasync__stream__writer_ac8b191bccfc233007594d07c1bb228d4}\label{classasync__stream__writer_ac8b191bccfc233007594d07c1bb228d4}} 
\index{async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}!m\+\_\+file@{m\+\_\+file}}
\index{m\+\_\+file@{m\+\_\+file}!async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{m\+\_\+file}{m\_file}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
std\+::\+F\+I\+LE$\ast$ \hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::m\+\_\+file\hspace{0.3cm}{\ttfamily [private]}}

file handler

\mbox{\Hypertarget{classasync__stream__writer_ad451ef8f2eb1c884b38cd10f387ac325}\label{classasync__stream__writer_ad451ef8f2eb1c884b38cd10f387ac325}} 
\index{async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}!m\+\_\+free\+\_\+buffers@{m\+\_\+free\+\_\+buffers}}
\index{m\+\_\+free\+\_\+buffers@{m\+\_\+free\+\_\+buffers}!async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{m\+\_\+free\+\_\+buffers}{m\_free\_buffers}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{classasync__stream__writer_a44dba276c5208314653dd887010e7161}{buffer\+\_\+queue\+\_\+type}$\ast$ \hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::m\+\_\+free\+\_\+buffers\hspace{0.3cm}{\ttfamily [private]}}

empty-\/buffer queue

\mbox{\Hypertarget{classasync__stream__writer_a091edd8f3eab9d64c3bc3396d4fb7994}\label{classasync__stream__writer_a091edd8f3eab9d64c3bc3396d4fb7994}} 
\index{async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}!m\+\_\+full\+\_\+buffers@{m\+\_\+full\+\_\+buffers}}
\index{m\+\_\+full\+\_\+buffers@{m\+\_\+full\+\_\+buffers}!async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{m\+\_\+full\+\_\+buffers}{m\_full\_buffers}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
\hyperlink{classasync__stream__writer_a44dba276c5208314653dd887010e7161}{buffer\+\_\+queue\+\_\+type}$\ast$ \hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::m\+\_\+full\+\_\+buffers\hspace{0.3cm}{\ttfamily [private]}}

full-\/buffer queue

\mbox{\Hypertarget{classasync__stream__writer_a4298b5c3a6950422907f0e59580386dd}\label{classasync__stream__writer_a4298b5c3a6950422907f0e59580386dd}} 
\index{async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}!m\+\_\+io\+\_\+thread@{m\+\_\+io\+\_\+thread}}
\index{m\+\_\+io\+\_\+thread@{m\+\_\+io\+\_\+thread}!async\+\_\+stream\+\_\+writer@{async\+\_\+stream\+\_\+writer}}
\subsubsection{\texorpdfstring{m\+\_\+io\+\_\+thread}{m\_io\_thread}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
std\+::thread$\ast$ \hyperlink{classasync__stream__writer}{async\+\_\+stream\+\_\+writer}$<$ value\+\_\+type $>$\+::m\+\_\+io\+\_\+thread\hspace{0.3cm}{\ttfamily [private]}}

pointer to I/O thread

The documentation for this class was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{async__stream__writer_8h}{async\+\_\+stream\+\_\+writer.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/classstd_1_1numeric__limits_3_01uint128_01_4.tex
2017/01/24

\hypertarget{classstd_1_1numeric__limits_3_01uint128_01_4}{}\section{std\+:\+:numeric\+\_\+limits$<$ uint128 $>$ Class Template Reference}
\label{classstd_1_1numeric__limits_3_01uint128_01_4}\index{std\+::numeric\+\_\+limits$<$ uint128 $>$@{std\+::numeric\+\_\+limits$<$ uint128 $>$}}

{\ttfamily \#include $<$types.\+h$>$}

\subsection*{Static Public Member Functions}
\begin{DoxyCompactItemize}
\item 
static \hyperlink{classuint128}{uint128} \hyperlink{classstd_1_1numeric__limits_3_01uint128_01_4_adef4934a87fb473dae963876142d84a9}{min} ()
\item 
static \hyperlink{classuint128}{uint128} \hyperlink{classstd_1_1numeric__limits_3_01uint128_01_4_a7093ce47008ca399ec2cd994099baa2a}{max} ()
\end{DoxyCompactItemize}

\subsection{Member Function Documentation}
\mbox{\Hypertarget{classstd_1_1numeric__limits_3_01uint128_01_4_a7093ce47008ca399ec2cd994099baa2a}\label{classstd_1_1numeric__limits_3_01uint128_01_4_a7093ce47008ca399ec2cd994099baa2a}} 
\index{std\+::numeric\+\_\+limits$<$ uint128 $>$@{std\+::numeric\+\_\+limits$<$ uint128 $>$}!max@{max}}
\index{max@{max}!std\+::numeric\+\_\+limits$<$ uint128 $>$@{std\+::numeric\+\_\+limits$<$ uint128 $>$}}
\subsubsection{\texorpdfstring{max()}{max()}}
{\footnotesize\ttfamily static \hyperlink{classuint128}{uint128} std\+::numeric\+\_\+limits$<$ \hyperlink{classuint128}{uint128} $>$\+::max (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [static]}}

\mbox{\Hypertarget{classstd_1_1numeric__limits_3_01uint128_01_4_adef4934a87fb473dae963876142d84a9}\label{classstd_1_1numeric__limits_3_01uint128_01_4_adef4934a87fb473dae963876142d84a9}} 
\index{std\+::numeric\+\_\+limits$<$ uint128 $>$@{std\+::numeric\+\_\+limits$<$ uint128 $>$}!min@{min}}
\index{min@{min}!std\+::numeric\+\_\+limits$<$ uint128 $>$@{std\+::numeric\+\_\+limits$<$ uint128 $>$}}
\subsubsection{\texorpdfstring{min()}{min()}}
{\footnotesize\ttfamily static \hyperlink{classuint128}{uint128} std\+::numeric\+\_\+limits$<$ \hyperlink{classuint128}{uint128} $>$\+::min (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [static]}}

The documentation for this class was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{types_8h}{types.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/classstd_1_1numeric__limits_3_01uint40_01_4.tex
2017/01/24

\hypertarget{classstd_1_1numeric__limits_3_01uint40_01_4}{}\section{std\+:\+:numeric\+\_\+limits$<$ uint40 $>$ Class Template Reference}
\label{classstd_1_1numeric__limits_3_01uint40_01_4}\index{std\+::numeric\+\_\+limits$<$ uint40 $>$@{std\+::numeric\+\_\+limits$<$ uint40 $>$}}

{\ttfamily \#include $<$types.\+h$>$}

\subsection*{Static Public Member Functions}
\begin{DoxyCompactItemize}
\item 
static \hyperlink{classuint40}{uint40} \hyperlink{classstd_1_1numeric__limits_3_01uint40_01_4_a42a1903dc50a04e31a067fef55745daf}{min} ()
\item 
static \hyperlink{classuint40}{uint40} \hyperlink{classstd_1_1numeric__limits_3_01uint40_01_4_a22582c529e203e9648b054d15bcb0564}{max} ()
\end{DoxyCompactItemize}

\subsection{Member Function Documentation}
\mbox{\Hypertarget{classstd_1_1numeric__limits_3_01uint40_01_4_a22582c529e203e9648b054d15bcb0564}\label{classstd_1_1numeric__limits_3_01uint40_01_4_a22582c529e203e9648b054d15bcb0564}} 
\index{std\+::numeric\+\_\+limits$<$ uint40 $>$@{std\+::numeric\+\_\+limits$<$ uint40 $>$}!max@{max}}
\index{max@{max}!std\+::numeric\+\_\+limits$<$ uint40 $>$@{std\+::numeric\+\_\+limits$<$ uint40 $>$}}
\subsubsection{\texorpdfstring{max()}{max()}}
{\footnotesize\ttfamily static \hyperlink{classuint40}{uint40} std\+::numeric\+\_\+limits$<$ \hyperlink{classuint40}{uint40} $>$\+::max (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [static]}}

\mbox{\Hypertarget{classstd_1_1numeric__limits_3_01uint40_01_4_a42a1903dc50a04e31a067fef55745daf}\label{classstd_1_1numeric__limits_3_01uint40_01_4_a42a1903dc50a04e31a067fef55745daf}} 
\index{std\+::numeric\+\_\+limits$<$ uint40 $>$@{std\+::numeric\+\_\+limits$<$ uint40 $>$}!min@{min}}
\index{min@{min}!std\+::numeric\+\_\+limits$<$ uint40 $>$@{std\+::numeric\+\_\+limits$<$ uint40 $>$}}
\subsubsection{\texorpdfstring{min()}{min()}}
{\footnotesize\ttfamily static \hyperlink{classuint40}{uint40} std\+::numeric\+\_\+limits$<$ \hyperlink{classuint40}{uint40} $>$\+::min (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [static]}}

The documentation for this class was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{types_8h}{types.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/classuint128.tex
2017/01/24

\hypertarget{classuint128}{}\section{uint128 Class Reference}
\label{classuint128}\index{uint128@{uint128}}

{\ttfamily \#include $<$types.\+h$>$}

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{classuint128_abe535f8ff596b02234d94ab4c8d40933}{uint128} ()
\begin{DoxyCompactList}\small\item\em default ctor \end{DoxyCompactList}\item 
\hyperlink{classuint128_a2b3acd15568d628cffb98f5c58f17ea9}{uint128} (const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+low, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+high)
\begin{DoxyCompactList}\small\item\em initialized from lower and higher parts \end{DoxyCompactList}\item 
\hyperlink{classuint128_a228d418fd9f623a4ee7120a7a53e0797}{uint128} (const \hyperlink{classuint128}{uint128} \&\+\_\+a)
\begin{DoxyCompactList}\small\item\em copy ctor \end{DoxyCompactList}\item 
\hyperlink{classuint128_a5820b53a7880e5caf28057ea8bddff4b}{uint128} (const \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} \&\+\_\+a)
\begin{DoxyCompactList}\small\item\em initialized from an unsigned int \end{DoxyCompactList}\item 
\hyperlink{classuint128_af1cf2b32a813dae00ec27cfae5fabf1a}{uint128} (const \hyperlink{types_8h_a3d594eb72953c94a18a03d929ebd9167}{int32} \&\+\_\+a)
\begin{DoxyCompactList}\small\item\em initialized from anint, a $>$= 0 \end{DoxyCompactList}\item 
\hyperlink{classuint128_a655c92ad28efbc6378c95510556475a7}{uint128} (const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+a)
\begin{DoxyCompactList}\small\item\em initialized from an unsigned long int \end{DoxyCompactList}\item 
void \hyperlink{classuint128_a09c291d8b7c8f1e2d3a4dd3a763408d9}{operator$<$$<$=} (const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \+\_\+bits)
\begin{DoxyCompactList}\small\item\em bitwise shift, \+\_\+bits bits leftward, self revision \end{DoxyCompactList}\item 
void \hyperlink{classuint128_a04bf2e2eb85e66ed7c722a8d5494b0a4}{operator$\vert$=} (const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \+\_\+ch)
\begin{DoxyCompactList}\small\item\em bitwise or \end{DoxyCompactList}\item 
\hyperlink{classuint128}{uint128} \hyperlink{classuint128_a24dc256af129ab352a5d52793dfbe514}{operator$<$$<$} (const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \+\_\+bits)
\begin{DoxyCompactList}\small\item\em biwise shift, \+\_\+bits bits leftward \end{DoxyCompactList}\item 
\hyperlink{classuint128}{uint128} \hyperlink{classuint128_a227d131e34d73974124c38cfbf0c6cc4}{operator\&} (const \hyperlink{classuint128}{uint128} \&\+\_\+b) const
\begin{DoxyCompactList}\small\item\em bitwise and \end{DoxyCompactList}\item 
bool \hyperlink{classuint128_a0f3b16aec08d80f999b17762b15ed0c5}{operator==} (const \hyperlink{classuint128}{uint128} \&b) const
\begin{DoxyCompactList}\small\item\em check equality \end{DoxyCompactList}\item 
bool \hyperlink{classuint128_a767bfa81f69c7884cbb9434c37435e50}{operator!=} (const \hyperlink{classuint128}{uint128} \&b) const
\begin{DoxyCompactList}\small\item\em check inequality \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classuint128_a597036514f1abbbc8626492230f3436f}{get\+\_\+high} () const
\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classuint128_adeb81ae4b8a8acbf46131e17ff7acc05}{get\+\_\+low} () const
\end{DoxyCompactItemize}
\subsection*{Static Public Member Functions}
\begin{DoxyCompactItemize}
\item 
static \hyperlink{classuint128}{uint128} \hyperlink{classuint128_a4d43d35f5576c480e4fc1cb63fbfaf78}{min} ()
\item 
static \hyperlink{classuint128}{uint128} \hyperlink{classuint128_a8fc47c78cb71d012c6208c150ca4cf3b}{max} ()
\end{DoxyCompactItemize}
\subsection*{Static Public Attributes}
\begin{DoxyCompactItemize}
\item 
static const size\+\_\+t \hyperlink{classuint128_a08388a396904d541e7e921f1f379b4a1}{digits} = 128
\begin{DoxyCompactList}\small\item\em number of digits/bits, 128 \end{DoxyCompactList}\item 
static const size\+\_\+t \hyperlink{classuint128_a8ddedda58a986c591392955033f74495}{bytes} = 16
\begin{DoxyCompactList}\small\item\em number of bytes, 16 \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Private Attributes}
\begin{DoxyCompactItemize}
\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classuint128_a439bdff9b7d8dd4bf99616bb07fc2a5e}{low}
\begin{DoxyCompactList}\small\item\em lower part, uint64 \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{classuint128_a9f8275501c9a4546f37fae8e85e3ec05}{high}
\begin{DoxyCompactList}\small\item\em higher part, uint64 \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Friends}
\begin{DoxyCompactItemize}
\item 
std\+::ostream \& \hyperlink{classuint128_a3981a0cf6398b930fa55fa5c5e802a65}{operator$<$$<$} (std\+::ostream \&\+\_\+os, const \hyperlink{classuint128}{uint128} \&\+\_\+a)
\end{DoxyCompactItemize}

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{classuint128_abe535f8ff596b02234d94ab4c8d40933}\label{classuint128_abe535f8ff596b02234d94ab4c8d40933}} 
\index{uint128@{uint128}!uint128@{uint128}}
\index{uint128@{uint128}!uint128@{uint128}}
\subsubsection{\texorpdfstring{uint128()}{uint128()}\hspace{0.1cm}{\footnotesize\ttfamily [1/6]}}
{\footnotesize\ttfamily uint128\+::uint128 (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

default ctor

\mbox{\Hypertarget{classuint128_a2b3acd15568d628cffb98f5c58f17ea9}\label{classuint128_a2b3acd15568d628cffb98f5c58f17ea9}} 
\index{uint128@{uint128}!uint128@{uint128}}
\index{uint128@{uint128}!uint128@{uint128}}
\subsubsection{\texorpdfstring{uint128()}{uint128()}\hspace{0.1cm}{\footnotesize\ttfamily [2/6]}}
{\footnotesize\ttfamily uint128\+::uint128 (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+low,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+high }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

initialized from lower and higher parts

\mbox{\Hypertarget{classuint128_a228d418fd9f623a4ee7120a7a53e0797}\label{classuint128_a228d418fd9f623a4ee7120a7a53e0797}} 
\index{uint128@{uint128}!uint128@{uint128}}
\index{uint128@{uint128}!uint128@{uint128}}
\subsubsection{\texorpdfstring{uint128()}{uint128()}\hspace{0.1cm}{\footnotesize\ttfamily [3/6]}}
{\footnotesize\ttfamily uint128\+::uint128 (\begin{DoxyParamCaption}\item[{const \hyperlink{classuint128}{uint128} \&}]{\+\_\+a }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

copy ctor

\mbox{\Hypertarget{classuint128_a5820b53a7880e5caf28057ea8bddff4b}\label{classuint128_a5820b53a7880e5caf28057ea8bddff4b}} 
\index{uint128@{uint128}!uint128@{uint128}}
\index{uint128@{uint128}!uint128@{uint128}}
\subsubsection{\texorpdfstring{uint128()}{uint128()}\hspace{0.1cm}{\footnotesize\ttfamily [4/6]}}
{\footnotesize\ttfamily uint128\+::uint128 (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} \&}]{\+\_\+a }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

initialized from an unsigned int

\mbox{\Hypertarget{classuint128_af1cf2b32a813dae00ec27cfae5fabf1a}\label{classuint128_af1cf2b32a813dae00ec27cfae5fabf1a}} 
\index{uint128@{uint128}!uint128@{uint128}}
\index{uint128@{uint128}!uint128@{uint128}}
\subsubsection{\texorpdfstring{uint128()}{uint128()}\hspace{0.1cm}{\footnotesize\ttfamily [5/6]}}
{\footnotesize\ttfamily uint128\+::uint128 (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a3d594eb72953c94a18a03d929ebd9167}{int32} \&}]{\+\_\+a }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

initialized from anint, a $>$= 0

\mbox{\Hypertarget{classuint128_a655c92ad28efbc6378c95510556475a7}\label{classuint128_a655c92ad28efbc6378c95510556475a7}} 
\index{uint128@{uint128}!uint128@{uint128}}
\index{uint128@{uint128}!uint128@{uint128}}
\subsubsection{\texorpdfstring{uint128()}{uint128()}\hspace{0.1cm}{\footnotesize\ttfamily [6/6]}}
{\footnotesize\ttfamily uint128\+::uint128 (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+a }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

initialized from an unsigned long int

\subsection{Member Function Documentation}
\mbox{\Hypertarget{classuint128_a597036514f1abbbc8626492230f3436f}\label{classuint128_a597036514f1abbbc8626492230f3436f}} 
\index{uint128@{uint128}!get\+\_\+high@{get\+\_\+high}}
\index{get\+\_\+high@{get\+\_\+high}!uint128@{uint128}}
\subsubsection{\texorpdfstring{get\+\_\+high()}{get\_high()}}
{\footnotesize\ttfamily \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} uint128\+::get\+\_\+high (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{classuint128_adeb81ae4b8a8acbf46131e17ff7acc05}\label{classuint128_adeb81ae4b8a8acbf46131e17ff7acc05}} 
\index{uint128@{uint128}!get\+\_\+low@{get\+\_\+low}}
\index{get\+\_\+low@{get\+\_\+low}!uint128@{uint128}}
\subsubsection{\texorpdfstring{get\+\_\+low()}{get\_low()}}
{\footnotesize\ttfamily \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} uint128\+::get\+\_\+low (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{classuint128_a8fc47c78cb71d012c6208c150ca4cf3b}\label{classuint128_a8fc47c78cb71d012c6208c150ca4cf3b}} 
\index{uint128@{uint128}!max@{max}}
\index{max@{max}!uint128@{uint128}}
\subsubsection{\texorpdfstring{max()}{max()}}
{\footnotesize\ttfamily static \hyperlink{classuint128}{uint128} uint128\+::max (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [static]}}

\mbox{\Hypertarget{classuint128_a4d43d35f5576c480e4fc1cb63fbfaf78}\label{classuint128_a4d43d35f5576c480e4fc1cb63fbfaf78}} 
\index{uint128@{uint128}!min@{min}}
\index{min@{min}!uint128@{uint128}}
\subsubsection{\texorpdfstring{min()}{min()}}
{\footnotesize\ttfamily static \hyperlink{classuint128}{uint128} uint128\+::min (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [static]}}

\mbox{\Hypertarget{classuint128_a767bfa81f69c7884cbb9434c37435e50}\label{classuint128_a767bfa81f69c7884cbb9434c37435e50}} 
\index{uint128@{uint128}!operator"!=@{operator"!=}}
\index{operator"!=@{operator"!=}!uint128@{uint128}}
\subsubsection{\texorpdfstring{operator"!=()}{operator!=()}}
{\footnotesize\ttfamily bool uint128\+::operator!= (\begin{DoxyParamCaption}\item[{const \hyperlink{classuint128}{uint128} \&}]{b }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

check inequality

\mbox{\Hypertarget{classuint128_a227d131e34d73974124c38cfbf0c6cc4}\label{classuint128_a227d131e34d73974124c38cfbf0c6cc4}} 
\index{uint128@{uint128}!operator\&@{operator\&}}
\index{operator\&@{operator\&}!uint128@{uint128}}
\subsubsection{\texorpdfstring{operator\&()}{operator\&()}}
{\footnotesize\ttfamily \hyperlink{classuint128}{uint128} uint128\+::operator \& (\begin{DoxyParamCaption}\item[{const \hyperlink{classuint128}{uint128} \&}]{\+\_\+b }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

bitwise and

\mbox{\Hypertarget{classuint128_a24dc256af129ab352a5d52793dfbe514}\label{classuint128_a24dc256af129ab352a5d52793dfbe514}} 
\index{uint128@{uint128}!operator$<$$<$@{operator$<$$<$}}
\index{operator$<$$<$@{operator$<$$<$}!uint128@{uint128}}
\subsubsection{\texorpdfstring{operator$<$$<$()}{operator<<()}}
{\footnotesize\ttfamily \hyperlink{classuint128}{uint128} uint128\+::operator$<$$<$ (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8}}]{\+\_\+bits }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

biwise shift, \+\_\+bits bits leftward

\mbox{\Hypertarget{classuint128_a09c291d8b7c8f1e2d3a4dd3a763408d9}\label{classuint128_a09c291d8b7c8f1e2d3a4dd3a763408d9}} 
\index{uint128@{uint128}!operator$<$$<$=@{operator$<$$<$=}}
\index{operator$<$$<$=@{operator$<$$<$=}!uint128@{uint128}}
\subsubsection{\texorpdfstring{operator$<$$<$=()}{operator<<=()}}
{\footnotesize\ttfamily void uint128\+::operator$<$$<$= (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8}}]{\+\_\+bits }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

bitwise shift, \+\_\+bits bits leftward, self revision

\mbox{\Hypertarget{classuint128_a0f3b16aec08d80f999b17762b15ed0c5}\label{classuint128_a0f3b16aec08d80f999b17762b15ed0c5}} 
\index{uint128@{uint128}!operator==@{operator==}}
\index{operator==@{operator==}!uint128@{uint128}}
\subsubsection{\texorpdfstring{operator==()}{operator==()}}
{\footnotesize\ttfamily bool uint128\+::operator== (\begin{DoxyParamCaption}\item[{const \hyperlink{classuint128}{uint128} \&}]{b }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

check equality

\mbox{\Hypertarget{classuint128_a04bf2e2eb85e66ed7c722a8d5494b0a4}\label{classuint128_a04bf2e2eb85e66ed7c722a8d5494b0a4}} 
\index{uint128@{uint128}!operator\texttt{"|}=@{operator\texttt{"|}=}}
\index{operator\texttt{"|}=@{operator\texttt{"|}=}!uint128@{uint128}}
\subsubsection{\texorpdfstring{operator\texttt{"|}=()}{operator|=()}}
{\footnotesize\ttfamily void uint128\+::operator$\vert$= (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8}}]{\+\_\+ch }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

bitwise or

\subsection{Friends And Related Function Documentation}
\mbox{\Hypertarget{classuint128_a3981a0cf6398b930fa55fa5c5e802a65}\label{classuint128_a3981a0cf6398b930fa55fa5c5e802a65}} 
\index{uint128@{uint128}!operator$<$$<$@{operator$<$$<$}}
\index{operator$<$$<$@{operator$<$$<$}!uint128@{uint128}}
\subsubsection{\texorpdfstring{operator$<$$<$}{operator<<}}
{\footnotesize\ttfamily std\+::ostream\& operator$<$$<$ (\begin{DoxyParamCaption}\item[{std\+::ostream \&}]{\+\_\+os,  }\item[{const \hyperlink{classuint128}{uint128} \&}]{\+\_\+a }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [friend]}}

\subsection{Member Data Documentation}
\mbox{\Hypertarget{classuint128_a8ddedda58a986c591392955033f74495}\label{classuint128_a8ddedda58a986c591392955033f74495}} 
\index{uint128@{uint128}!bytes@{bytes}}
\index{bytes@{bytes}!uint128@{uint128}}
\subsubsection{\texorpdfstring{bytes}{bytes}}
{\footnotesize\ttfamily const size\+\_\+t uint128\+::bytes = 16\hspace{0.3cm}{\ttfamily [static]}}

number of bytes, 16

\mbox{\Hypertarget{classuint128_a08388a396904d541e7e921f1f379b4a1}\label{classuint128_a08388a396904d541e7e921f1f379b4a1}} 
\index{uint128@{uint128}!digits@{digits}}
\index{digits@{digits}!uint128@{uint128}}
\subsubsection{\texorpdfstring{digits}{digits}}
{\footnotesize\ttfamily const size\+\_\+t uint128\+::digits = 128\hspace{0.3cm}{\ttfamily [static]}}

number of digits/bits, 128

\mbox{\Hypertarget{classuint128_a9f8275501c9a4546f37fae8e85e3ec05}\label{classuint128_a9f8275501c9a4546f37fae8e85e3ec05}} 
\index{uint128@{uint128}!high@{high}}
\index{high@{high}!uint128@{uint128}}
\subsubsection{\texorpdfstring{high}{high}}
{\footnotesize\ttfamily \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} uint128\+::high\hspace{0.3cm}{\ttfamily [private]}}

higher part, uint64

\mbox{\Hypertarget{classuint128_a439bdff9b7d8dd4bf99616bb07fc2a5e}\label{classuint128_a439bdff9b7d8dd4bf99616bb07fc2a5e}} 
\index{uint128@{uint128}!low@{low}}
\index{low@{low}!uint128@{uint128}}
\subsubsection{\texorpdfstring{low}{low}}
{\footnotesize\ttfamily \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} uint128\+::low\hspace{0.3cm}{\ttfamily [private]}}

lower part, uint64

The documentation for this class was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{types_8h}{types.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/classuint40.tex
2017/01/24

\hypertarget{classuint40}{}\section{uint40 Class Reference}
\label{classuint40}\index{uint40@{uint40}}

{\ttfamily \#include $<$types.\+h$>$}

\subsection*{Public Types}
\begin{DoxyCompactItemize}
\item 
typedef \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} \hyperlink{classuint40_a92fb8d876ca5cf77d4ed86dae0adc2f2}{low\+\_\+type}
\item 
typedef \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \hyperlink{classuint40_a58afcd6aeb1ea1e103b8e85eb6aefec4}{high\+\_\+type}
\end{DoxyCompactItemize}
\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{classuint40_a457b73a04d5f5b2833155af392aaac96}{uint40} ()
\item 
\hyperlink{classuint40_a06f45dcc09d7533278c5fefbf7085440}{uint40} (std\+::uint32\+\_\+t l, std\+::uint8\+\_\+t h)
\item 
\hyperlink{classuint40_ab359a2f13e4d14944ae6ba3245d71ef3}{uint40} (const \hyperlink{classuint40}{uint40} \&a)
\item 
\hyperlink{classuint40_ad4165899ffb9045026ba833e5b8bc347}{uint40} (const std\+::int32\+\_\+t \&a)
\item 
\hyperlink{classuint40_a18e730effdedf9cba7e5524e9aef2778}{uint40} (const std\+::uint32\+\_\+t \&a)
\item 
\hyperlink{classuint40_afde52c521f80c8d54ff9bf600fa12aee}{uint40} (const std\+::uint64\+\_\+t \&a)
\item 
\hyperlink{classuint40_a39ca6ed5905712c2fc9f0f8eefc16989}{uint40} (const std\+::int64\+\_\+t \&a)
\item 
void \hyperlink{classuint40_a4d8e0bfd4cb5f959d89d3966c10a28bc}{set\+\_\+high} (const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \&\+\_\+high)
\item 
void \hyperlink{classuint40_a451e74374aa8f180e94d341e18352d4c}{set\+\_\+low} (const \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} \&\+\_\+low)
\item 
void \hyperlink{classuint40_ab23ea17f6248ac0e7dbacbb71a96179b}{set} (const \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} \&\+\_\+low, const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \+\_\+high)
\item 
\hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} \hyperlink{classuint40_a0037fdf484bb069add9d9ee8c65dbc17}{get\+\_\+low} ()
\item 
\hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \hyperlink{classuint40_ac08ecc53d6ae5d245218a768c3ac105c}{get\+\_\+high} ()
\item 
\hyperlink{classuint40_afca52041b179c0002070c33e7dd101a9}{operator uint64\+\_\+t} () const
\item 
bool \hyperlink{classuint40_afa6fa84dfd61e527efa6e4457abc2d81}{operator==} (const \hyperlink{classuint40}{uint40} \&b) const
\item 
bool \hyperlink{classuint40_af17f2004231903079eb4e36b64c96180}{operator!=} (const \hyperlink{classuint40}{uint40} \&b) const
\end{DoxyCompactItemize}
\subsection*{Private Attributes}
\begin{DoxyCompactItemize}
\item 
\hyperlink{classuint40_a92fb8d876ca5cf77d4ed86dae0adc2f2}{low\+\_\+type} \hyperlink{classuint40_a216fde2e6997b39cb34b32daa869cef3}{low}
\item 
\hyperlink{classuint40_a58afcd6aeb1ea1e103b8e85eb6aefec4}{high\+\_\+type} \hyperlink{classuint40_a830b04aa389a4e72c446cc88de38b656}{high}
\end{DoxyCompactItemize}

\subsection{Member Typedef Documentation}
\mbox{\Hypertarget{classuint40_a58afcd6aeb1ea1e103b8e85eb6aefec4}\label{classuint40_a58afcd6aeb1ea1e103b8e85eb6aefec4}} 
\index{uint40@{uint40}!high\+\_\+type@{high\+\_\+type}}
\index{high\+\_\+type@{high\+\_\+type}!uint40@{uint40}}
\subsubsection{\texorpdfstring{high\+\_\+type}{high\_type}}
{\footnotesize\ttfamily typedef \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \hyperlink{classuint40_a58afcd6aeb1ea1e103b8e85eb6aefec4}{uint40\+::high\+\_\+type}}

\mbox{\Hypertarget{classuint40_a92fb8d876ca5cf77d4ed86dae0adc2f2}\label{classuint40_a92fb8d876ca5cf77d4ed86dae0adc2f2}} 
\index{uint40@{uint40}!low\+\_\+type@{low\+\_\+type}}
\index{low\+\_\+type@{low\+\_\+type}!uint40@{uint40}}
\subsubsection{\texorpdfstring{low\+\_\+type}{low\_type}}
{\footnotesize\ttfamily typedef \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} \hyperlink{classuint40_a92fb8d876ca5cf77d4ed86dae0adc2f2}{uint40\+::low\+\_\+type}}

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{classuint40_a457b73a04d5f5b2833155af392aaac96}\label{classuint40_a457b73a04d5f5b2833155af392aaac96}} 
\index{uint40@{uint40}!uint40@{uint40}}
\index{uint40@{uint40}!uint40@{uint40}}
\subsubsection{\texorpdfstring{uint40()}{uint40()}\hspace{0.1cm}{\footnotesize\ttfamily [1/7]}}
{\footnotesize\ttfamily uint40\+::uint40 (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{classuint40_a06f45dcc09d7533278c5fefbf7085440}\label{classuint40_a06f45dcc09d7533278c5fefbf7085440}} 
\index{uint40@{uint40}!uint40@{uint40}}
\index{uint40@{uint40}!uint40@{uint40}}
\subsubsection{\texorpdfstring{uint40()}{uint40()}\hspace{0.1cm}{\footnotesize\ttfamily [2/7]}}
{\footnotesize\ttfamily uint40\+::uint40 (\begin{DoxyParamCaption}\item[{std\+::uint32\+\_\+t}]{l,  }\item[{std\+::uint8\+\_\+t}]{h }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{classuint40_ab359a2f13e4d14944ae6ba3245d71ef3}\label{classuint40_ab359a2f13e4d14944ae6ba3245d71ef3}} 
\index{uint40@{uint40}!uint40@{uint40}}
\index{uint40@{uint40}!uint40@{uint40}}
\subsubsection{\texorpdfstring{uint40()}{uint40()}\hspace{0.1cm}{\footnotesize\ttfamily [3/7]}}
{\footnotesize\ttfamily uint40\+::uint40 (\begin{DoxyParamCaption}\item[{const \hyperlink{classuint40}{uint40} \&}]{a }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{classuint40_ad4165899ffb9045026ba833e5b8bc347}\label{classuint40_ad4165899ffb9045026ba833e5b8bc347}} 
\index{uint40@{uint40}!uint40@{uint40}}
\index{uint40@{uint40}!uint40@{uint40}}
\subsubsection{\texorpdfstring{uint40()}{uint40()}\hspace{0.1cm}{\footnotesize\ttfamily [4/7]}}
{\footnotesize\ttfamily uint40\+::uint40 (\begin{DoxyParamCaption}\item[{const std\+::int32\+\_\+t \&}]{a }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{classuint40_a18e730effdedf9cba7e5524e9aef2778}\label{classuint40_a18e730effdedf9cba7e5524e9aef2778}} 
\index{uint40@{uint40}!uint40@{uint40}}
\index{uint40@{uint40}!uint40@{uint40}}
\subsubsection{\texorpdfstring{uint40()}{uint40()}\hspace{0.1cm}{\footnotesize\ttfamily [5/7]}}
{\footnotesize\ttfamily uint40\+::uint40 (\begin{DoxyParamCaption}\item[{const std\+::uint32\+\_\+t \&}]{a }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{classuint40_afde52c521f80c8d54ff9bf600fa12aee}\label{classuint40_afde52c521f80c8d54ff9bf600fa12aee}} 
\index{uint40@{uint40}!uint40@{uint40}}
\index{uint40@{uint40}!uint40@{uint40}}
\subsubsection{\texorpdfstring{uint40()}{uint40()}\hspace{0.1cm}{\footnotesize\ttfamily [6/7]}}
{\footnotesize\ttfamily uint40\+::uint40 (\begin{DoxyParamCaption}\item[{const std\+::uint64\+\_\+t \&}]{a }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{classuint40_a39ca6ed5905712c2fc9f0f8eefc16989}\label{classuint40_a39ca6ed5905712c2fc9f0f8eefc16989}} 
\index{uint40@{uint40}!uint40@{uint40}}
\index{uint40@{uint40}!uint40@{uint40}}
\subsubsection{\texorpdfstring{uint40()}{uint40()}\hspace{0.1cm}{\footnotesize\ttfamily [7/7]}}
{\footnotesize\ttfamily uint40\+::uint40 (\begin{DoxyParamCaption}\item[{const std\+::int64\+\_\+t \&}]{a }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

\subsection{Member Function Documentation}
\mbox{\Hypertarget{classuint40_ac08ecc53d6ae5d245218a768c3ac105c}\label{classuint40_ac08ecc53d6ae5d245218a768c3ac105c}} 
\index{uint40@{uint40}!get\+\_\+high@{get\+\_\+high}}
\index{get\+\_\+high@{get\+\_\+high}!uint40@{uint40}}
\subsubsection{\texorpdfstring{get\+\_\+high()}{get\_high()}}
{\footnotesize\ttfamily \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} uint40\+::get\+\_\+high (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{classuint40_a0037fdf484bb069add9d9ee8c65dbc17}\label{classuint40_a0037fdf484bb069add9d9ee8c65dbc17}} 
\index{uint40@{uint40}!get\+\_\+low@{get\+\_\+low}}
\index{get\+\_\+low@{get\+\_\+low}!uint40@{uint40}}
\subsubsection{\texorpdfstring{get\+\_\+low()}{get\_low()}}
{\footnotesize\ttfamily \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} uint40\+::get\+\_\+low (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{classuint40_afca52041b179c0002070c33e7dd101a9}\label{classuint40_afca52041b179c0002070c33e7dd101a9}} 
\index{uint40@{uint40}!operator uint64\+\_\+t@{operator uint64\+\_\+t}}
\index{operator uint64\+\_\+t@{operator uint64\+\_\+t}!uint40@{uint40}}
\subsubsection{\texorpdfstring{operator uint64\+\_\+t()}{operator uint64\_t()}}
{\footnotesize\ttfamily uint40\+::operator uint64\+\_\+t (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{classuint40_af17f2004231903079eb4e36b64c96180}\label{classuint40_af17f2004231903079eb4e36b64c96180}} 
\index{uint40@{uint40}!operator"!=@{operator"!=}}
\index{operator"!=@{operator"!=}!uint40@{uint40}}
\subsubsection{\texorpdfstring{operator"!=()}{operator!=()}}
{\footnotesize\ttfamily bool uint40\+::operator!= (\begin{DoxyParamCaption}\item[{const \hyperlink{classuint40}{uint40} \&}]{b }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{classuint40_afa6fa84dfd61e527efa6e4457abc2d81}\label{classuint40_afa6fa84dfd61e527efa6e4457abc2d81}} 
\index{uint40@{uint40}!operator==@{operator==}}
\index{operator==@{operator==}!uint40@{uint40}}
\subsubsection{\texorpdfstring{operator==()}{operator==()}}
{\footnotesize\ttfamily bool uint40\+::operator== (\begin{DoxyParamCaption}\item[{const \hyperlink{classuint40}{uint40} \&}]{b }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{classuint40_ab23ea17f6248ac0e7dbacbb71a96179b}\label{classuint40_ab23ea17f6248ac0e7dbacbb71a96179b}} 
\index{uint40@{uint40}!set@{set}}
\index{set@{set}!uint40@{uint40}}
\subsubsection{\texorpdfstring{set()}{set()}}
{\footnotesize\ttfamily void uint40\+::set (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} \&}]{\+\_\+low,  }\item[{const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8}}]{\+\_\+high }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{classuint40_a4d8e0bfd4cb5f959d89d3966c10a28bc}\label{classuint40_a4d8e0bfd4cb5f959d89d3966c10a28bc}} 
\index{uint40@{uint40}!set\+\_\+high@{set\+\_\+high}}
\index{set\+\_\+high@{set\+\_\+high}!uint40@{uint40}}
\subsubsection{\texorpdfstring{set\+\_\+high()}{set\_high()}}
{\footnotesize\ttfamily void uint40\+::set\+\_\+high (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \&}]{\+\_\+high }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{classuint40_a451e74374aa8f180e94d341e18352d4c}\label{classuint40_a451e74374aa8f180e94d341e18352d4c}} 
\index{uint40@{uint40}!set\+\_\+low@{set\+\_\+low}}
\index{set\+\_\+low@{set\+\_\+low}!uint40@{uint40}}
\subsubsection{\texorpdfstring{set\+\_\+low()}{set\_low()}}
{\footnotesize\ttfamily void uint40\+::set\+\_\+low (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} \&}]{\+\_\+low }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

\subsection{Member Data Documentation}
\mbox{\Hypertarget{classuint40_a830b04aa389a4e72c446cc88de38b656}\label{classuint40_a830b04aa389a4e72c446cc88de38b656}} 
\index{uint40@{uint40}!high@{high}}
\index{high@{high}!uint40@{uint40}}
\subsubsection{\texorpdfstring{high}{high}}
{\footnotesize\ttfamily \hyperlink{classuint40_a58afcd6aeb1ea1e103b8e85eb6aefec4}{high\+\_\+type} uint40\+::high\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{classuint40_a216fde2e6997b39cb34b32daa869cef3}\label{classuint40_a216fde2e6997b39cb34b32daa869cef3}} 
\index{uint40@{uint40}!low@{low}}
\index{low@{low}!uint40@{uint40}}
\subsubsection{\texorpdfstring{low}{low}}
{\footnotesize\ttfamily \hyperlink{classuint40_a92fb8d876ca5cf77d4ed86dae0adc2f2}{low\+\_\+type} uint40\+::low\hspace{0.3cm}{\ttfamily [private]}}

The documentation for this class was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{types_8h}{types.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/common_8h.tex
2017/01/24

\hypertarget{common_8h}{}\section{code/src/common/common.h File Reference}
\label{common_8h}\index{code/src/common/common.\+h@{code/src/common/common.\+h}}

definition of macro, constant and alias for common use

{\ttfamily \#include \char`\"{}namespace.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}types.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}stxxl/bits/io/syscall\+\_\+file.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}stxxl/vector\char`\"{}}\newline
{\ttfamily \#include $<$string$>$}\newline
{\ttfamily \#include $<$climits$>$}\newline
{\ttfamily \#include $<$cassert$>$}\newline
{\ttfamily \#include $<$vector$>$}\newline
\subsection*{Typedefs}
\begin{DoxyCompactItemize}
\item 
using \hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} = \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32}
\item 
using \hyperlink{common_8h_a6f10cf5b333b34ed4bbf03429a74bcca}{fpb\+\_\+type} = \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}
\end{DoxyCompactItemize}
\subsection*{Variables}
\begin{DoxyCompactItemize}
\item 
static const size\+\_\+t \hyperlink{common_8h_a4b1a49a5378e8e0c9aca7501041c8d6d}{K\+\_\+512} = 512 $\ast$ 1024
\begin{DoxyCompactList}\small\item\em 512 K \end{DoxyCompactList}\item 
static const size\+\_\+t \hyperlink{common_8h_a260c3735667f0ab08a4c522a2e7bda23}{M\+\_\+512} = \hyperlink{common_8h_a4b1a49a5378e8e0c9aca7501041c8d6d}{K\+\_\+512} $\ast$ 1024
\begin{DoxyCompactList}\small\item\em 512 M \end{DoxyCompactList}\item 
static const \hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} \hyperlink{common_8h_aecfe9143b353556cb5a466f72c6a513c}{P} = 2047824239
\item 
static const \hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} \hyperlink{common_8h_a465886396cb5767ddce1163c14db7209}{R} = 1732327371
\item 
static const \hyperlink{types_8h_a948660ad4bbc6ed2c3e3262a30bac0ff}{uint\+\_\+type} \hyperlink{common_8h_ae891a1a9fb20d0711712f6e64864f8ed}{M\+A\+I\+N\+\_\+\+M\+E\+M\+\_\+\+A\+V\+A\+IL} = 3 $\ast$ 1024 $\ast$ 1024 $\ast$ 1024ull
\item 
static const \hyperlink{types_8h_a948660ad4bbc6ed2c3e3262a30bac0ff}{uint\+\_\+type} \hyperlink{common_8h_aff51988fecf5b6871480b3d91954df7d}{B\+U\+F\+F\+\_\+\+M\+E\+M\+\_\+\+A\+V\+A\+IL} = 8 $\ast$ 1024 $\ast$ 1024ull
\item 
static const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \hyperlink{common_8h_a12286339af3610eed714aba8e56125ea}{L\+\_\+\+T\+Y\+PE} = 0
\item 
static const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \hyperlink{common_8h_a726936e5500c7ab70b64cbc308774a97}{S\+\_\+\+T\+Y\+PE} = 1
\item 
static const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \hyperlink{common_8h_aceba1d712f3152d9ec9297ba5dd67f1b}{S\+E\+N\+T\+I\+N\+E\+L\+\_\+\+T\+Y\+PE} = 2
\end{DoxyCompactItemize}

\subsection{Detailed Description}
definition of macro, constant and alias for common use

Copyright (c) 2016, Sun Yat-\/sen University, All rights reserved

\begin{DoxyAuthor}{Author}
Yi Wu 
\end{DoxyAuthor}
\begin{DoxyDate}{Date}
2016.\+12 
\end{DoxyDate}

\subsection{Typedef Documentation}
\mbox{\Hypertarget{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}\label{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}} 
\index{common.\+h@{common.\+h}!fpa\+\_\+type@{fpa\+\_\+type}}
\index{fpa\+\_\+type@{fpa\+\_\+type}!common.\+h@{common.\+h}}
\subsubsection{\texorpdfstring{fpa\+\_\+type}{fpa\_type}}
{\footnotesize\ttfamily using \hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} =  \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32}}

\mbox{\Hypertarget{common_8h_a6f10cf5b333b34ed4bbf03429a74bcca}\label{common_8h_a6f10cf5b333b34ed4bbf03429a74bcca}} 
\index{common.\+h@{common.\+h}!fpb\+\_\+type@{fpb\+\_\+type}}
\index{fpb\+\_\+type@{fpb\+\_\+type}!common.\+h@{common.\+h}}
\subsubsection{\texorpdfstring{fpb\+\_\+type}{fpb\_type}}
{\footnotesize\ttfamily using \hyperlink{common_8h_a6f10cf5b333b34ed4bbf03429a74bcca}{fpb\+\_\+type} =  \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}

\subsection{Variable Documentation}
\mbox{\Hypertarget{common_8h_aff51988fecf5b6871480b3d91954df7d}\label{common_8h_aff51988fecf5b6871480b3d91954df7d}} 
\index{common.\+h@{common.\+h}!B\+U\+F\+F\+\_\+\+M\+E\+M\+\_\+\+A\+V\+A\+IL@{B\+U\+F\+F\+\_\+\+M\+E\+M\+\_\+\+A\+V\+A\+IL}}
\index{B\+U\+F\+F\+\_\+\+M\+E\+M\+\_\+\+A\+V\+A\+IL@{B\+U\+F\+F\+\_\+\+M\+E\+M\+\_\+\+A\+V\+A\+IL}!common.\+h@{common.\+h}}
\subsubsection{\texorpdfstring{B\+U\+F\+F\+\_\+\+M\+E\+M\+\_\+\+A\+V\+A\+IL}{BUFF\_MEM\_AVAIL}}
{\footnotesize\ttfamily const \hyperlink{types_8h_a948660ad4bbc6ed2c3e3262a30bac0ff}{uint\+\_\+type} B\+U\+F\+F\+\_\+\+M\+E\+M\+\_\+\+A\+V\+A\+IL = 8 $\ast$ 1024 $\ast$ 1024ull\hspace{0.3cm}{\ttfamily [static]}}

\mbox{\Hypertarget{common_8h_a4b1a49a5378e8e0c9aca7501041c8d6d}\label{common_8h_a4b1a49a5378e8e0c9aca7501041c8d6d}} 
\index{common.\+h@{common.\+h}!K\+\_\+512@{K\+\_\+512}}
\index{K\+\_\+512@{K\+\_\+512}!common.\+h@{common.\+h}}
\subsubsection{\texorpdfstring{K\+\_\+512}{K\_512}}
{\footnotesize\ttfamily const size\+\_\+t K\+\_\+512 = 512 $\ast$ 1024\hspace{0.3cm}{\ttfamily [static]}}

512 K

\mbox{\Hypertarget{common_8h_a12286339af3610eed714aba8e56125ea}\label{common_8h_a12286339af3610eed714aba8e56125ea}} 
\index{common.\+h@{common.\+h}!L\+\_\+\+T\+Y\+PE@{L\+\_\+\+T\+Y\+PE}}
\index{L\+\_\+\+T\+Y\+PE@{L\+\_\+\+T\+Y\+PE}!common.\+h@{common.\+h}}
\subsubsection{\texorpdfstring{L\+\_\+\+T\+Y\+PE}{L\_TYPE}}
{\footnotesize\ttfamily const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} L\+\_\+\+T\+Y\+PE = 0\hspace{0.3cm}{\ttfamily [static]}}

\mbox{\Hypertarget{common_8h_a260c3735667f0ab08a4c522a2e7bda23}\label{common_8h_a260c3735667f0ab08a4c522a2e7bda23}} 
\index{common.\+h@{common.\+h}!M\+\_\+512@{M\+\_\+512}}
\index{M\+\_\+512@{M\+\_\+512}!common.\+h@{common.\+h}}
\subsubsection{\texorpdfstring{M\+\_\+512}{M\_512}}
{\footnotesize\ttfamily const size\+\_\+t M\+\_\+512 = \hyperlink{common_8h_a4b1a49a5378e8e0c9aca7501041c8d6d}{K\+\_\+512} $\ast$ 1024\hspace{0.3cm}{\ttfamily [static]}}

512 M

\mbox{\Hypertarget{common_8h_ae891a1a9fb20d0711712f6e64864f8ed}\label{common_8h_ae891a1a9fb20d0711712f6e64864f8ed}} 
\index{common.\+h@{common.\+h}!M\+A\+I\+N\+\_\+\+M\+E\+M\+\_\+\+A\+V\+A\+IL@{M\+A\+I\+N\+\_\+\+M\+E\+M\+\_\+\+A\+V\+A\+IL}}
\index{M\+A\+I\+N\+\_\+\+M\+E\+M\+\_\+\+A\+V\+A\+IL@{M\+A\+I\+N\+\_\+\+M\+E\+M\+\_\+\+A\+V\+A\+IL}!common.\+h@{common.\+h}}
\subsubsection{\texorpdfstring{M\+A\+I\+N\+\_\+\+M\+E\+M\+\_\+\+A\+V\+A\+IL}{MAIN\_MEM\_AVAIL}}
{\footnotesize\ttfamily const \hyperlink{types_8h_a948660ad4bbc6ed2c3e3262a30bac0ff}{uint\+\_\+type} M\+A\+I\+N\+\_\+\+M\+E\+M\+\_\+\+A\+V\+A\+IL = 3 $\ast$ 1024 $\ast$ 1024 $\ast$ 1024ull\hspace{0.3cm}{\ttfamily [static]}}

\mbox{\Hypertarget{common_8h_aecfe9143b353556cb5a466f72c6a513c}\label{common_8h_aecfe9143b353556cb5a466f72c6a513c}} 
\index{common.\+h@{common.\+h}!P@{P}}
\index{P@{P}!common.\+h@{common.\+h}}
\subsubsection{\texorpdfstring{P}{P}}
{\footnotesize\ttfamily const \hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} P = 2047824239\hspace{0.3cm}{\ttfamily [static]}}

\mbox{\Hypertarget{common_8h_a465886396cb5767ddce1163c14db7209}\label{common_8h_a465886396cb5767ddce1163c14db7209}} 
\index{common.\+h@{common.\+h}!R@{R}}
\index{R@{R}!common.\+h@{common.\+h}}
\subsubsection{\texorpdfstring{R}{R}}
{\footnotesize\ttfamily const \hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} R = 1732327371\hspace{0.3cm}{\ttfamily [static]}}

\mbox{\Hypertarget{common_8h_a726936e5500c7ab70b64cbc308774a97}\label{common_8h_a726936e5500c7ab70b64cbc308774a97}} 
\index{common.\+h@{common.\+h}!S\+\_\+\+T\+Y\+PE@{S\+\_\+\+T\+Y\+PE}}
\index{S\+\_\+\+T\+Y\+PE@{S\+\_\+\+T\+Y\+PE}!common.\+h@{common.\+h}}
\subsubsection{\texorpdfstring{S\+\_\+\+T\+Y\+PE}{S\_TYPE}}
{\footnotesize\ttfamily const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} S\+\_\+\+T\+Y\+PE = 1\hspace{0.3cm}{\ttfamily [static]}}

\mbox{\Hypertarget{common_8h_aceba1d712f3152d9ec9297ba5dd67f1b}\label{common_8h_aceba1d712f3152d9ec9297ba5dd67f1b}} 
\index{common.\+h@{common.\+h}!S\+E\+N\+T\+I\+N\+E\+L\+\_\+\+T\+Y\+PE@{S\+E\+N\+T\+I\+N\+E\+L\+\_\+\+T\+Y\+PE}}
\index{S\+E\+N\+T\+I\+N\+E\+L\+\_\+\+T\+Y\+PE@{S\+E\+N\+T\+I\+N\+E\+L\+\_\+\+T\+Y\+PE}!common.\+h@{common.\+h}}
\subsubsection{\texorpdfstring{S\+E\+N\+T\+I\+N\+E\+L\+\_\+\+T\+Y\+PE}{SENTINEL\_TYPE}}
{\footnotesize\ttfamily const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} S\+E\+N\+T\+I\+N\+E\+L\+\_\+\+T\+Y\+PE = 2\hspace{0.3cm}{\ttfamily [static]}}

### 2017-01-24 archive/latex/dir_14807827589b339a04434892d1c1deae.tex
2017/01/24

\hypertarget{dir_14807827589b339a04434892d1c1deae}{}\section{code/src Directory Reference}
\label{dir_14807827589b339a04434892d1c1deae}\index{code/src Directory Reference@{code/src Directory Reference}}
\subsection*{Directories}
\begin{DoxyCompactItemize}
\item 
directory \hyperlink{dir_86633d98051024a4283a8055eb45f008}{common}
\end{DoxyCompactItemize}
\subsection*{Files}
\begin{DoxyCompactItemize}
\item 
file \hyperlink{test_8h}{test.\+h}
\item 
file \hyperlink{validate_8cpp}{validate.\+cpp}
\item 
file \hyperlink{validate_8h}{validate.\+h}
\begin{DoxyCompactList}\small\item\em first method for validating suffix and L\+CP arrays \end{DoxyCompactList}\item 
file \hyperlink{validate2_8cpp}{validate2.\+cpp}
\item 
file \hyperlink{validate2_8h}{validate2.\+h}
\begin{DoxyCompactList}\small\item\em validate sa and lcp using internal memory sorts and Karp-\/rabin finger-\/print function. \end{DoxyCompactList}\item 
file \hyperlink{validate3_8cpp}{validate3.\+cpp}
\item 
file \hyperlink{validate3_8h}{validate3.\+h}
\begin{DoxyCompactList}\small\item\em validate sa and lcp using external memory sorts and Karp-\/rabin finger-\/print function. \end{DoxyCompactList}\item 
file \hyperlink{validate4_8cpp}{validate4.\+cpp}
\item 
file \hyperlink{validate4_8h}{validate4.\+h}
\begin{DoxyCompactList}\small\item\em A two-\/phase validator for suffix and L\+CP arrays verification. \end{DoxyCompactList}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/dir_68267d1309a1af8e8297ef4c3efbcdba.tex
2017/01/24

--- 2017-01-24 archive/latex/dir_14807827589b339a04434892d1c1deae.tex
@@
-\hypertarget{dir_14807827589b339a04434892d1c1deae}{}\section{code/src Directory Reference}
-\label{dir_14807827589b339a04434892d1c1deae}\index{code/src Directory Reference@{code/src Directory Reference}}
+\hypertarget{dir_68267d1309a1af8e8297ef4c3efbcdba}{}\section{src Directory Reference}
+\label{dir_68267d1309a1af8e8297ef4c3efbcdba}\index{src Directory Reference@{src Directory Reference}}
 \subsection*{Directories}
@@
 \item 
-directory \hyperlink{dir_86633d98051024a4283a8055eb45f008}{common}
+directory \hyperlink{dir_fdedb0aba14d44ce9d99bc100e026e6a}{common}
 \end{DoxyCompactItemize}

### 2017-01-24 archive/latex/dir_86633d98051024a4283a8055eb45f008.tex
2017/01/24

\hypertarget{dir_86633d98051024a4283a8055eb45f008}{}\section{code/src/common Directory Reference}
\label{dir_86633d98051024a4283a8055eb45f008}\index{code/src/common Directory Reference@{code/src/common Directory Reference}}
\subsection*{Files}
\begin{DoxyCompactItemize}
\item 
file \hyperlink{async__stream__reader_8h}{async\+\_\+stream\+\_\+reader.\+h}
\begin{DoxyCompactList}\small\item\em read elements from disk file using asychronous I/O operations \end{DoxyCompactList}\item 
file \hyperlink{async__stream__writer_8h}{async\+\_\+stream\+\_\+writer.\+h}
\begin{DoxyCompactList}\small\item\em write elements into disk file using asynchronous I/O operations. \end{DoxyCompactList}\item 
file \hyperlink{basicio_8h}{basicio.\+h}
\begin{DoxyCompactList}\small\item\em provide basic I/O interface for sequential read/write operations \end{DoxyCompactList}\item 
file \hyperlink{common_8h}{common.\+h}
\begin{DoxyCompactList}\small\item\em definition of macro, constant and alias for common use \end{DoxyCompactList}\item 
file \hyperlink{namespace_8h}{namespace.\+h}
\item 
file \hyperlink{tuples_8h}{tuples.\+h}
\item 
file \hyperlink{types_8h}{types.\+h}
\begin{DoxyCompactList}\small\item\em definition of namespace \end{DoxyCompactList}\item 
file \hyperlink{widget_8h}{widget.\+h}
\begin{DoxyCompactList}\small\item\em sort elements in external memory \end{DoxyCompactList}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/dir_fdedb0aba14d44ce9d99bc100e026e6a.tex
2017/01/24

--- 2017-01-24 archive/latex/dir_86633d98051024a4283a8055eb45f008.tex
@@
-\hypertarget{dir_86633d98051024a4283a8055eb45f008}{}\section{code/src/common Directory Reference}
-\label{dir_86633d98051024a4283a8055eb45f008}\index{code/src/common Directory Reference@{code/src/common Directory Reference}}
+\hypertarget{dir_fdedb0aba14d44ce9d99bc100e026e6a}{}\section{src/common Directory Reference}
+\label{dir_fdedb0aba14d44ce9d99bc100e026e6a}\index{src/common Directory Reference@{src/common Directory Reference}}
 \subsection*{Files}

### 2017-01-24 archive/latex/files.tex
2017/01/24

\section{File List}
Here is a list of all files with brief descriptions\+:\begin{DoxyCompactList}
\item\contentsline{section}{code/src/\hyperlink{test_8h}{test.\+h} }{\pageref{test_8h}}{}
\item\contentsline{section}{code/src/\hyperlink{validate_8cpp}{validate.\+cpp} }{\pageref{validate_8cpp}}{}
\item\contentsline{section}{code/src/\hyperlink{validate_8h}{validate.\+h} \\*First method for validating suffix and L\+CP arrays }{\pageref{validate_8h}}{}
\item\contentsline{section}{code/src/\hyperlink{validate2_8cpp}{validate2.\+cpp} }{\pageref{validate2_8cpp}}{}
\item\contentsline{section}{code/src/\hyperlink{validate2_8h}{validate2.\+h} \\*\hyperlink{class_validate}{Validate} sa and lcp using internal memory sorts and Karp-\/rabin finger-\/print function }{\pageref{validate2_8h}}{}
\item\contentsline{section}{code/src/\hyperlink{validate3_8cpp}{validate3.\+cpp} }{\pageref{validate3_8cpp}}{}
\item\contentsline{section}{code/src/\hyperlink{validate3_8h}{validate3.\+h} \\*\hyperlink{class_validate}{Validate} sa and lcp using external memory sorts and Karp-\/rabin finger-\/print function }{\pageref{validate3_8h}}{}
\item\contentsline{section}{code/src/\hyperlink{validate4_8cpp}{validate4.\+cpp} }{\pageref{validate4_8cpp}}{}
\item\contentsline{section}{code/src/\hyperlink{validate4_8h}{validate4.\+h} \\*A two-\/phase validator for suffix and L\+CP arrays verification }{\pageref{validate4_8h}}{}
\item\contentsline{section}{code/src/common/\hyperlink{async__stream__reader_8h}{async\+\_\+stream\+\_\+reader.\+h} \\*Read elements from disk file using asychronous I/O operations }{\pageref{async__stream__reader_8h}}{}
\item\contentsline{section}{code/src/common/\hyperlink{async__stream__writer_8h}{async\+\_\+stream\+\_\+writer.\+h} \\*Write elements into disk file using asynchronous I/O operations }{\pageref{async__stream__writer_8h}}{}
\item\contentsline{section}{code/src/common/\hyperlink{basicio_8h}{basicio.\+h} \\*Provide basic I/O interface for sequential read/write operations }{\pageref{basicio_8h}}{}
\item\contentsline{section}{code/src/common/\hyperlink{common_8h}{common.\+h} \\*Definition of macro, constant and alias for common use }{\pageref{common_8h}}{}
\item\contentsline{section}{code/src/common/\hyperlink{namespace_8h}{namespace.\+h} }{\pageref{namespace_8h}}{}
\item\contentsline{section}{code/src/common/\hyperlink{tuples_8h}{tuples.\+h} }{\pageref{tuples_8h}}{}
\item\contentsline{section}{code/src/common/\hyperlink{types_8h}{types.\+h} \\*Definition of namespace }{\pageref{types_8h}}{}
\item\contentsline{section}{code/src/common/\hyperlink{widget_8h}{widget.\+h} \\*Sort elements in external memory }{\pageref{widget_8h}}{}
\item\contentsline{section}{code/test/\hyperlink{mytest1_8cpp}{mytest1.\+cpp} }{\pageref{mytest1_8cpp}}{}
\end{DoxyCompactList}

### 2017-01-24 archive/latex/index.tex
2017/01/24

\hypertarget{index_intro_sec}{}\section{Introduction}\label{index_intro_sec}
The implementations of two methods for validating massive SA and L\+CP arrays. The main files for Methods A and B\+: \hyperlink{validate3_8h}{validate3.\+h} \& \hyperlink{validate3_8cpp}{validate3.\+cpp} and \hyperlink{validate4_8h}{validate4.\+h} \& \hyperlink{validate4_8cpp}{validate4.\+cpp}, respectively.\hypertarget{index_copyright_sec}{}\section{Copyright}\label{index_copyright_sec}
Copyright 2017 by Yi Wu, Sun Yat-\/\+Sen university. Free to use, copy, modify or distribute the software.

### 2017-01-24 archive/latex/mytest1_8cpp.tex
2017/01/24

\hypertarget{mytest1_8cpp}{}\section{code/test/mytest1.cpp File Reference}
\label{mytest1_8cpp}\index{code/test/mytest1.\+cpp@{code/test/mytest1.\+cpp}}
\subsection*{Functions}
\begin{DoxyCompactItemize}
\item 
int \hyperlink{mytest1_8cpp_ae66f6b31b5ad750f1fe042a706a4e3d4}{main} ()
\end{DoxyCompactItemize}

\subsection{Function Documentation}
\mbox{\Hypertarget{mytest1_8cpp_ae66f6b31b5ad750f1fe042a706a4e3d4}\label{mytest1_8cpp_ae66f6b31b5ad750f1fe042a706a4e3d4}} 
\index{mytest1.\+cpp@{mytest1.\+cpp}!main@{main}}
\index{main@{main}!mytest1.\+cpp@{mytest1.\+cpp}}
\subsubsection{\texorpdfstring{main()}{main()}}
{\footnotesize\ttfamily int main (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})}

### 2017-01-24 archive/latex/namespace_8h.tex
2017/01/24

\hypertarget{namespace_8h}{}\section{code/src/common/namespace.h File Reference}
\label{namespace_8h}\index{code/src/common/namespace.\+h@{code/src/common/namespace.\+h}}
\subsection*{Macros}
\begin{DoxyCompactItemize}
\item 
\#define \hyperlink{namespace_8h_a9d80567b3813f4e453d1e9ec2ea08c8f}{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+C\+O\+R\+E\+\_\+\+B\+EG}~namespace core \{
\item 
\#define \hyperlink{namespace_8h_a867f010187a6a1158481891dfb51273f}{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+C\+O\+R\+E\+\_\+\+E\+ND}~\}
\item 
\#define \hyperlink{namespace_8h_a84670ad82c41e15277ca235f8616b59e}{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+U\+T\+I\+L\+I\+T\+Y\+\_\+\+B\+EG}~namespace utility \{
\item 
\#define \hyperlink{namespace_8h_afc10b2ddef8af94c352b9e2f24de67ca}{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+U\+T\+I\+L\+I\+T\+Y\+\_\+\+E\+ND}~\}
\end{DoxyCompactItemize}

\subsection{Macro Definition Documentation}
\mbox{\Hypertarget{namespace_8h_a9d80567b3813f4e453d1e9ec2ea08c8f}\label{namespace_8h_a9d80567b3813f4e453d1e9ec2ea08c8f}} 
\index{namespace.\+h@{namespace.\+h}!N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+C\+O\+R\+E\+\_\+\+B\+EG@{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+C\+O\+R\+E\+\_\+\+B\+EG}}
\index{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+C\+O\+R\+E\+\_\+\+B\+EG@{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+C\+O\+R\+E\+\_\+\+B\+EG}!namespace.\+h@{namespace.\+h}}
\subsubsection{\texorpdfstring{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+C\+O\+R\+E\+\_\+\+B\+EG}{NAMESPACE\_CORE\_BEG}}
{\footnotesize\ttfamily \#define N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+C\+O\+R\+E\+\_\+\+B\+EG~namespace core \{}

\mbox{\Hypertarget{namespace_8h_a867f010187a6a1158481891dfb51273f}\label{namespace_8h_a867f010187a6a1158481891dfb51273f}} 
\index{namespace.\+h@{namespace.\+h}!N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+C\+O\+R\+E\+\_\+\+E\+ND@{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+C\+O\+R\+E\+\_\+\+E\+ND}}
\index{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+C\+O\+R\+E\+\_\+\+E\+ND@{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+C\+O\+R\+E\+\_\+\+E\+ND}!namespace.\+h@{namespace.\+h}}
\subsubsection{\texorpdfstring{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+C\+O\+R\+E\+\_\+\+E\+ND}{NAMESPACE\_CORE\_END}}
{\footnotesize\ttfamily \#define N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+C\+O\+R\+E\+\_\+\+E\+ND~\}}

\mbox{\Hypertarget{namespace_8h_a84670ad82c41e15277ca235f8616b59e}\label{namespace_8h_a84670ad82c41e15277ca235f8616b59e}} 
\index{namespace.\+h@{namespace.\+h}!N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+U\+T\+I\+L\+I\+T\+Y\+\_\+\+B\+EG@{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+U\+T\+I\+L\+I\+T\+Y\+\_\+\+B\+EG}}
\index{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+U\+T\+I\+L\+I\+T\+Y\+\_\+\+B\+EG@{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+U\+T\+I\+L\+I\+T\+Y\+\_\+\+B\+EG}!namespace.\+h@{namespace.\+h}}
\subsubsection{\texorpdfstring{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+U\+T\+I\+L\+I\+T\+Y\+\_\+\+B\+EG}{NAMESPACE\_UTILITY\_BEG}}
{\footnotesize\ttfamily \#define N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+U\+T\+I\+L\+I\+T\+Y\+\_\+\+B\+EG~namespace utility \{}

\mbox{\Hypertarget{namespace_8h_afc10b2ddef8af94c352b9e2f24de67ca}\label{namespace_8h_afc10b2ddef8af94c352b9e2f24de67ca}} 
\index{namespace.\+h@{namespace.\+h}!N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+U\+T\+I\+L\+I\+T\+Y\+\_\+\+E\+ND@{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+U\+T\+I\+L\+I\+T\+Y\+\_\+\+E\+ND}}
\index{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+U\+T\+I\+L\+I\+T\+Y\+\_\+\+E\+ND@{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+U\+T\+I\+L\+I\+T\+Y\+\_\+\+E\+ND}!namespace.\+h@{namespace.\+h}}
\subsubsection{\texorpdfstring{N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+U\+T\+I\+L\+I\+T\+Y\+\_\+\+E\+ND}{NAMESPACE\_UTILITY\_END}}
{\footnotesize\ttfamily \#define N\+A\+M\+E\+S\+P\+A\+C\+E\+\_\+\+U\+T\+I\+L\+I\+T\+Y\+\_\+\+E\+ND~\}}

### 2017-01-24 archive/latex/namespacestd.tex
2017/01/24

\hypertarget{namespacestd}{}\section{std Namespace Reference}
\label{namespacestd}\index{std@{std}}
\subsection*{Classes}
\begin{DoxyCompactItemize}
\item 
class \hyperlink{classstd_1_1numeric__limits_3_01uint128_01_4}{numeric\+\_\+limits$<$ uint128 $>$}
\item 
class \hyperlink{classstd_1_1numeric__limits_3_01uint40_01_4}{numeric\+\_\+limits$<$ uint40 $>$}
\end{DoxyCompactItemize}
\subsection*{Variables}
\begin{DoxyCompactItemize}
\item 
class std\+::numeric\+\_\+limits$<$ \hyperlink{classuint40}{uint40} $>$ \hyperlink{namespacestd_ade73df0294cb697bb61d5edf0deac7d0}{\+\_\+\+\_\+attribute\+\_\+\+\_\+}
\end{DoxyCompactItemize}

\subsection{Variable Documentation}
\mbox{\Hypertarget{namespacestd_ade73df0294cb697bb61d5edf0deac7d0}\label{namespacestd_ade73df0294cb697bb61d5edf0deac7d0}} 
\index{std@{std}!\+\_\+\+\_\+attribute\+\_\+\+\_\+@{\+\_\+\+\_\+attribute\+\_\+\+\_\+}}
\index{\+\_\+\+\_\+attribute\+\_\+\+\_\+@{\+\_\+\+\_\+attribute\+\_\+\+\_\+}!std@{std}}
\subsubsection{\texorpdfstring{\+\_\+\+\_\+attribute\+\_\+\+\_\+}{\_\_attribute\_\_}}
{\footnotesize\ttfamily class std\+::numeric\+\_\+limits$<$ \hyperlink{classuint40}{uint40} $>$ std\+::\+\_\+\+\_\+attribute\+\_\+\+\_\+}

### 2017-01-24 archive/latex/struct_ex_tuple_sorter.tex
2017/01/24

\hypertarget{struct_ex_tuple_sorter}{}\section{Ex\+Tuple\+Sorter$<$ tuple\+\_\+type, tuple\+\_\+comparator\+\_\+type $>$ Struct Template Reference}
\label{struct_ex_tuple_sorter}\index{Ex\+Tuple\+Sorter$<$ tuple\+\_\+type, tuple\+\_\+comparator\+\_\+type $>$@{Ex\+Tuple\+Sorter$<$ tuple\+\_\+type, tuple\+\_\+comparator\+\_\+type $>$}}

template for sorter

{\ttfamily \#include $<$widget.\+h$>$}

\subsection*{Public Types}
\begin{DoxyCompactItemize}
\item 
typedef stxxl\+::sorter$<$ tuple\+\_\+type, tuple\+\_\+comparator\+\_\+type $>$ \hyperlink{struct_ex_tuple_sorter_adf836f2aaa3d62d311b66eccbf5543d5}{sorter}
\item 
typedef tuple\+\_\+comparator\+\_\+type \hyperlink{struct_ex_tuple_sorter_a876d6fabe768a68b9d730053a619298e}{comparator}
\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename tuple\+\_\+type, typename tuple\+\_\+comparator\+\_\+type$>$\newline
struct Ex\+Tuple\+Sorter$<$ tuple\+\_\+type, tuple\+\_\+comparator\+\_\+type $>$}

template for sorter

\subsection{Member Typedef Documentation}
\mbox{\Hypertarget{struct_ex_tuple_sorter_a876d6fabe768a68b9d730053a619298e}\label{struct_ex_tuple_sorter_a876d6fabe768a68b9d730053a619298e}} 
\index{Ex\+Tuple\+Sorter@{Ex\+Tuple\+Sorter}!comparator@{comparator}}
\index{comparator@{comparator}!Ex\+Tuple\+Sorter@{Ex\+Tuple\+Sorter}}
\subsubsection{\texorpdfstring{comparator}{comparator}}
{\footnotesize\ttfamily template$<$typename tuple\+\_\+type, typename tuple\+\_\+comparator\+\_\+type$>$ \\
typedef tuple\+\_\+comparator\+\_\+type \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$ tuple\+\_\+type, tuple\+\_\+comparator\+\_\+type $>$\+::\hyperlink{struct_ex_tuple_sorter_a876d6fabe768a68b9d730053a619298e}{comparator}}

\mbox{\Hypertarget{struct_ex_tuple_sorter_adf836f2aaa3d62d311b66eccbf5543d5}\label{struct_ex_tuple_sorter_adf836f2aaa3d62d311b66eccbf5543d5}} 
\index{Ex\+Tuple\+Sorter@{Ex\+Tuple\+Sorter}!sorter@{sorter}}
\index{sorter@{sorter}!Ex\+Tuple\+Sorter@{Ex\+Tuple\+Sorter}}
\subsubsection{\texorpdfstring{sorter}{sorter}}
{\footnotesize\ttfamily template$<$typename tuple\+\_\+type, typename tuple\+\_\+comparator\+\_\+type$>$ \\
typedef stxxl\+::sorter$<$tuple\+\_\+type, tuple\+\_\+comparator\+\_\+type$>$ \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter}$<$ tuple\+\_\+type, tuple\+\_\+comparator\+\_\+type $>$\+::\hyperlink{struct_ex_tuple_sorter_adf836f2aaa3d62d311b66eccbf5543d5}{sorter}}

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{widget_8h}{widget.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/struct_ex_vector.tex
2017/01/24

\hypertarget{struct_ex_vector}{}\section{Ex\+Vector$<$ value\+\_\+type $>$ Struct Template Reference}
\label{struct_ex_vector}\index{Ex\+Vector$<$ value\+\_\+type $>$@{Ex\+Vector$<$ value\+\_\+type $>$}}

template for vector

{\ttfamily \#include $<$widget.\+h$>$}

\subsection*{Public Types}
\begin{DoxyCompactItemize}
\item 
typedef stxxl\+::\+V\+E\+C\+T\+O\+R\+\_\+\+G\+E\+N\+E\+R\+A\+T\+OR$<$ value\+\_\+type, 8/sizeof(value\+\_\+type)+1, 2, \hyperlink{common_8h_a4b1a49a5378e8e0c9aca7501041c8d6d}{K\+\_\+512} $\ast$sizeof(value\+\_\+type)$>$\+::result \hyperlink{struct_ex_vector_aa45a4c6039859d71d03827b07d265287}{vector}
\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename value\+\_\+type$>$\newline
struct Ex\+Vector$<$ value\+\_\+type $>$}

template for vector

\subsection{Member Typedef Documentation}
\mbox{\Hypertarget{struct_ex_vector_aa45a4c6039859d71d03827b07d265287}\label{struct_ex_vector_aa45a4c6039859d71d03827b07d265287}} 
\index{Ex\+Vector@{Ex\+Vector}!vector@{vector}}
\index{vector@{vector}!Ex\+Vector@{Ex\+Vector}}
\subsubsection{\texorpdfstring{vector}{vector}}
{\footnotesize\ttfamily template$<$typename value\+\_\+type$>$ \\
typedef stxxl\+::\+V\+E\+C\+T\+O\+R\+\_\+\+G\+E\+N\+E\+R\+A\+T\+OR$<$value\+\_\+type, 8 / sizeof(value\+\_\+type) + 1, 2, \hyperlink{common_8h_a4b1a49a5378e8e0c9aca7501041c8d6d}{K\+\_\+512} $\ast$ sizeof(value\+\_\+type)$>$\+::result \hyperlink{struct_ex_vector}{Ex\+Vector}$<$ value\+\_\+type $>$\+::\hyperlink{struct_ex_vector_aa45a4c6039859d71d03827b07d265287}{vector}}

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{widget_8h}{widget.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/struct_pair_less1st.tex
2017/01/24

\hypertarget{struct_pair_less1st}{}\section{Pair\+Less1st$<$ pair\+\_\+type $>$ Struct Template Reference}
\label{struct_pair_less1st}\index{Pair\+Less1st$<$ pair\+\_\+type $>$@{Pair\+Less1st$<$ pair\+\_\+type $>$}}

sort pair by 1st component in ascending order

{\ttfamily \#include $<$widget.\+h$>$}

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
bool \hyperlink{struct_pair_less1st_a0c8e1c7ad75317672327e20bdafe56e3}{operator()} (const pair\+\_\+type \&\+\_\+a, const pair\+\_\+type \&\+\_\+b) const
\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename pair\+\_\+type$>$\newline
struct Pair\+Less1st$<$ pair\+\_\+type $>$}

sort pair by 1st component in ascending order

\subsection{Member Function Documentation}
\mbox{\Hypertarget{struct_pair_less1st_a0c8e1c7ad75317672327e20bdafe56e3}\label{struct_pair_less1st_a0c8e1c7ad75317672327e20bdafe56e3}} 
\index{Pair\+Less1st@{Pair\+Less1st}!operator()@{operator()}}
\index{operator()@{operator()}!Pair\+Less1st@{Pair\+Less1st}}
\subsubsection{\texorpdfstring{operator()()}{operator()()}}
{\footnotesize\ttfamily template$<$typename pair\+\_\+type $>$ \\
bool \hyperlink{struct_pair_less1st}{Pair\+Less1st}$<$ pair\+\_\+type $>$\+::operator() (\begin{DoxyParamCaption}\item[{const pair\+\_\+type \&}]{\+\_\+a,  }\item[{const pair\+\_\+type \&}]{\+\_\+b }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{widget_8h}{widget.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/struct_pair_less2nd.tex
2017/01/24

\hypertarget{struct_pair_less2nd}{}\section{Pair\+Less2nd$<$ pair\+\_\+type $>$ Struct Template Reference}
\label{struct_pair_less2nd}\index{Pair\+Less2nd$<$ pair\+\_\+type $>$@{Pair\+Less2nd$<$ pair\+\_\+type $>$}}

sort pair by 2nd component in ascending order

{\ttfamily \#include $<$widget.\+h$>$}

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
bool \hyperlink{struct_pair_less2nd_ab794f9af084ecf20527e87634b669f17}{operator()} (const pair\+\_\+type \&\+\_\+a, const pair\+\_\+type \&\+\_\+b) const
\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename pair\+\_\+type$>$\newline
struct Pair\+Less2nd$<$ pair\+\_\+type $>$}

sort pair by 2nd component in ascending order

\subsection{Member Function Documentation}
\mbox{\Hypertarget{struct_pair_less2nd_ab794f9af084ecf20527e87634b669f17}\label{struct_pair_less2nd_ab794f9af084ecf20527e87634b669f17}} 
\index{Pair\+Less2nd@{Pair\+Less2nd}!operator()@{operator()}}
\index{operator()@{operator()}!Pair\+Less2nd@{Pair\+Less2nd}}
\subsubsection{\texorpdfstring{operator()()}{operator()()}}
{\footnotesize\ttfamily template$<$typename pair\+\_\+type $>$ \\
bool \hyperlink{struct_pair_less2nd}{Pair\+Less2nd}$<$ pair\+\_\+type $>$\+::operator() (\begin{DoxyParamCaption}\item[{const pair\+\_\+type \&}]{\+\_\+a,  }\item[{const pair\+\_\+type \&}]{\+\_\+b }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{widget_8h}{widget.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/struct_validate2_1_1_r_interval.tex
2017/01/24

\hypertarget{struct_validate2_1_1_r_interval}{}\section{Validate2$<$ alphabet\+\_\+type, size\+\_\+type $>$\+:\+:R\+Interval Struct Reference}
\label{struct_validate2_1_1_r_interval}\index{Validate2$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\+R\+Interval@{Validate2$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\+R\+Interval}}

store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, ...

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{struct_validate2_1_1_r_interval_af2e88047192f7e9703b9faa2298cb5fc}{R\+Interval} (\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \+\_\+len)
\begin{DoxyCompactList}\small\item\em constructor \end{DoxyCompactList}\item 
\hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} \hyperlink{struct_validate2_1_1_r_interval_a84006809e4b3ef58bd7335d2f46a92b1}{compute} (\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \+\_\+interval)
\begin{DoxyCompactList}\small\item\em get fp\+Interval \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Public Attributes}
\begin{DoxyCompactItemize}
\item 
\hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} $\ast$ \hyperlink{struct_validate2_1_1_r_interval_aee05aa76b959338fd2d1c0833f2e35d7}{m\+\_\+data}
\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate2_1_1_r_interval_ace46ef0a61dad6c184579e23bfae12ce}{m\+\_\+num}
\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename alphabet\+\_\+type, typename size\+\_\+type$>$\newline
struct Validate2$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\+R\+Interval}

store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, ...

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{struct_validate2_1_1_r_interval_af2e88047192f7e9703b9faa2298cb5fc}\label{struct_validate2_1_1_r_interval_af2e88047192f7e9703b9faa2298cb5fc}} 
\index{Validate2\+::\+R\+Interval@{Validate2\+::\+R\+Interval}!R\+Interval@{R\+Interval}}
\index{R\+Interval@{R\+Interval}!Validate2\+::\+R\+Interval@{Validate2\+::\+R\+Interval}}
\subsubsection{\texorpdfstring{R\+Interval()}{RInterval()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate2}{Validate2}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::R\+Interval\+::\+R\+Interval (\begin{DoxyParamCaption}\item[{\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}]{\+\_\+len }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor

\subsection{Member Function Documentation}
\mbox{\Hypertarget{struct_validate2_1_1_r_interval_a84006809e4b3ef58bd7335d2f46a92b1}\label{struct_validate2_1_1_r_interval_a84006809e4b3ef58bd7335d2f46a92b1}} 
\index{Validate2\+::\+R\+Interval@{Validate2\+::\+R\+Interval}!compute@{compute}}
\index{compute@{compute}!Validate2\+::\+R\+Interval@{Validate2\+::\+R\+Interval}}
\subsubsection{\texorpdfstring{compute()}{compute()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} \hyperlink{class_validate2}{Validate2}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::R\+Interval\+::compute (\begin{DoxyParamCaption}\item[{\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}]{\+\_\+interval }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

get fp\+Interval

\subsection{Member Data Documentation}
\mbox{\Hypertarget{struct_validate2_1_1_r_interval_aee05aa76b959338fd2d1c0833f2e35d7}\label{struct_validate2_1_1_r_interval_aee05aa76b959338fd2d1c0833f2e35d7}} 
\index{Validate2\+::\+R\+Interval@{Validate2\+::\+R\+Interval}!m\+\_\+data@{m\+\_\+data}}
\index{m\+\_\+data@{m\+\_\+data}!Validate2\+::\+R\+Interval@{Validate2\+::\+R\+Interval}}
\subsubsection{\texorpdfstring{m\+\_\+data}{m\_data}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type}$\ast$ \hyperlink{class_validate2}{Validate2}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::R\+Interval\+::m\+\_\+data}

\mbox{\Hypertarget{struct_validate2_1_1_r_interval_ace46ef0a61dad6c184579e23bfae12ce}\label{struct_validate2_1_1_r_interval_ace46ef0a61dad6c184579e23bfae12ce}} 
\index{Validate2\+::\+R\+Interval@{Validate2\+::\+R\+Interval}!m\+\_\+num@{m\+\_\+num}}
\index{m\+\_\+num@{m\+\_\+num}!Validate2\+::\+R\+Interval@{Validate2\+::\+R\+Interval}}
\subsubsection{\texorpdfstring{m\+\_\+num}{m\_num}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate2}{Validate2}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::R\+Interval\+::m\+\_\+num}

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/\hyperlink{validate2_8h}{validate2.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/struct_validate3_1_1_r_interval.tex
2017/01/24

\hypertarget{struct_validate3_1_1_r_interval}{}\section{Validate3$<$ alphabet\+\_\+type, size\+\_\+type $>$\+:\+:R\+Interval Struct Reference}
\label{struct_validate3_1_1_r_interval}\index{Validate3$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\+R\+Interval@{Validate3$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\+R\+Interval}}

store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, ...

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{struct_validate3_1_1_r_interval_a6bed3e6ae2b969b4cc5f7466c95edba0}{R\+Interval} (\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \+\_\+len)
\begin{DoxyCompactList}\small\item\em constructor \end{DoxyCompactList}\item 
\hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} \hyperlink{struct_validate3_1_1_r_interval_a7f5178d27e49d60e23e2a45635d2b076}{compute} (\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \+\_\+interval)
\begin{DoxyCompactList}\small\item\em get fp\+Interval \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Public Attributes}
\begin{DoxyCompactItemize}
\item 
\hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} $\ast$ \hyperlink{struct_validate3_1_1_r_interval_a137b07cbcfdf9b356285f8389bb9bc76}{m\+\_\+data}
\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate3_1_1_r_interval_a7d49d9eae5b1e584d29ca795472ea921}{m\+\_\+num}
\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename alphabet\+\_\+type, typename size\+\_\+type$>$\newline
struct Validate3$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\+R\+Interval}

store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, ...

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{struct_validate3_1_1_r_interval_a6bed3e6ae2b969b4cc5f7466c95edba0}\label{struct_validate3_1_1_r_interval_a6bed3e6ae2b969b4cc5f7466c95edba0}} 
\index{Validate3\+::\+R\+Interval@{Validate3\+::\+R\+Interval}!R\+Interval@{R\+Interval}}
\index{R\+Interval@{R\+Interval}!Validate3\+::\+R\+Interval@{Validate3\+::\+R\+Interval}}
\subsubsection{\texorpdfstring{R\+Interval()}{RInterval()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::R\+Interval\+::\+R\+Interval (\begin{DoxyParamCaption}\item[{\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}]{\+\_\+len }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor

\subsection{Member Function Documentation}
\mbox{\Hypertarget{struct_validate3_1_1_r_interval_a7f5178d27e49d60e23e2a45635d2b076}\label{struct_validate3_1_1_r_interval_a7f5178d27e49d60e23e2a45635d2b076}} 
\index{Validate3\+::\+R\+Interval@{Validate3\+::\+R\+Interval}!compute@{compute}}
\index{compute@{compute}!Validate3\+::\+R\+Interval@{Validate3\+::\+R\+Interval}}
\subsubsection{\texorpdfstring{compute()}{compute()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::R\+Interval\+::compute (\begin{DoxyParamCaption}\item[{\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}]{\+\_\+interval }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

get fp\+Interval

\subsection{Member Data Documentation}
\mbox{\Hypertarget{struct_validate3_1_1_r_interval_a137b07cbcfdf9b356285f8389bb9bc76}\label{struct_validate3_1_1_r_interval_a137b07cbcfdf9b356285f8389bb9bc76}} 
\index{Validate3\+::\+R\+Interval@{Validate3\+::\+R\+Interval}!m\+\_\+data@{m\+\_\+data}}
\index{m\+\_\+data@{m\+\_\+data}!Validate3\+::\+R\+Interval@{Validate3\+::\+R\+Interval}}
\subsubsection{\texorpdfstring{m\+\_\+data}{m\_data}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type}$\ast$ \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::R\+Interval\+::m\+\_\+data}

\mbox{\Hypertarget{struct_validate3_1_1_r_interval_a7d49d9eae5b1e584d29ca795472ea921}\label{struct_validate3_1_1_r_interval_a7d49d9eae5b1e584d29ca795472ea921}} 
\index{Validate3\+::\+R\+Interval@{Validate3\+::\+R\+Interval}!m\+\_\+num@{m\+\_\+num}}
\index{m\+\_\+num@{m\+\_\+num}!Validate3\+::\+R\+Interval@{Validate3\+::\+R\+Interval}}
\subsubsection{\texorpdfstring{m\+\_\+num}{m\_num}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate3}{Validate3}$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::R\+Interval\+::m\+\_\+num}

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/\hyperlink{validate3_8h}{validate3.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/struct_validate4_1_1_bkt_info.tex
2017/01/24

\hypertarget{struct_validate4_1_1_bkt_info}{}\section{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+:\+:Bkt\+Info Struct Reference}
\label{struct_validate4_1_1_bkt_info}\index{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+Bkt\+Info@{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+Bkt\+Info}}

record L-\/type, S-\/type and L\+MS bucket sizes (no matter empty or non-\/empty) in SA \& L\+CP

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{struct_validate4_1_1_bkt_info_ac9e39b62bee276f6a9604bff588b6ecc}{Bkt\+Info} ()
\begin{DoxyCompactList}\small\item\em ctor \end{DoxyCompactList}\item 
void \hyperlink{struct_validate4_1_1_bkt_info_af55a2b8eee03bfe617ab34759b4ac007}{add\+\_\+l} (const alphabet\+\_\+type \+\_\+ch)
\begin{DoxyCompactList}\small\item\em count the number of L-\/type suffixes in the specified bucket \end{DoxyCompactList}\item 
void \hyperlink{struct_validate4_1_1_bkt_info_a9c11b8915349954523623d9e7b0a2c2a}{add\+\_\+s} (const alphabet\+\_\+type \+\_\+ch)
\begin{DoxyCompactList}\small\item\em count the number of S-\/type suffixes in the specified bucket \end{DoxyCompactList}\item 
void \hyperlink{struct_validate4_1_1_bkt_info_a5875efc6696925c0932f262174c2cc37}{add\+\_\+lms} (const alphabet\+\_\+type \+\_\+ch)
\begin{DoxyCompactList}\small\item\em count the number of L\+MS suffixes in the specified bucket \end{DoxyCompactList}\item 
void \hyperlink{struct_validate4_1_1_bkt_info_ac4fb0eabb194f773cd4ac5f6bcbbe969}{accumulate} ()
\begin{DoxyCompactList}\small\item\em collect the number of suffixes in the specified bucket \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate4_1_1_bkt_info_ae06c1968c2288d191f59214a0f10e7d7}{get\+\_\+l\+\_\+bkt\+\_\+size} (const alphabet\+\_\+type \+\_\+ch) const
\begin{DoxyCompactList}\small\item\em return the number of L-\/type suffixes in the specified bucket \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate4_1_1_bkt_info_a0c9a5615bab7f7c22d0d3f2de4b2621c}{get\+\_\+s\+\_\+bkt\+\_\+size} (const alphabet\+\_\+type \+\_\+ch) const
\begin{DoxyCompactList}\small\item\em return the number of S-\/type suffixes in the specified bucket \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate4_1_1_bkt_info_a0f7a940f516eefaae031ecd75c0fc971}{get\+\_\+lms\+\_\+bkt\+\_\+size} (const alphabet\+\_\+type \+\_\+ch) const
\begin{DoxyCompactList}\small\item\em return the number of L\+MS suffixes in the specified bucket \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate4_1_1_bkt_info_a22256d03bfca21336fa30f2ed9e12d51}{get\+\_\+bkt\+\_\+size} (const alphabet\+\_\+type \+\_\+ch) const
\begin{DoxyCompactList}\small\item\em return the number of suffixes in the specified bucket \end{DoxyCompactList}\item 
void \hyperlink{struct_validate4_1_1_bkt_info_ad8bc43e62d48c2f33fc6173f2a1d0840}{display} () const
\end{DoxyCompactItemize}
\subsection*{Public Attributes}
\begin{DoxyCompactItemize}
\item 
const alphabet\+\_\+type \hyperlink{struct_validate4_1_1_bkt_info_a1485e4eceab1832f682e1751d310d2b9}{ch\+\_\+max}
\begin{DoxyCompactList}\small\item\em maximum value for alphabet\+\_\+type \end{DoxyCompactList}\item 
std\+::vector$<$ \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $>$ \hyperlink{struct_validate4_1_1_bkt_info_a1659db6479f4667a77043e842b93f3fc}{m\+\_\+bkt\+\_\+size}
\begin{DoxyCompactList}\small\item\em bucket size \end{DoxyCompactList}\item 
std\+::vector$<$ \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $>$ \hyperlink{struct_validate4_1_1_bkt_info_a0b44f8a1a308a6fff54cb0d05dd63ec4}{m\+\_\+l\+\_\+bkt\+\_\+size}
\begin{DoxyCompactList}\small\item\em L-\/type bucket size. \end{DoxyCompactList}\item 
std\+::vector$<$ \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $>$ \hyperlink{struct_validate4_1_1_bkt_info_acf0b824764fc045b9f1ce0f1ed2863ad}{m\+\_\+s\+\_\+bkt\+\_\+size}
\begin{DoxyCompactList}\small\item\em S-\/type bucket size. \end{DoxyCompactList}\item 
std\+::vector$<$ \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $>$ \hyperlink{struct_validate4_1_1_bkt_info_ad615aafce19e6e86948b227ad517b3cd}{m\+\_\+lms\+\_\+bkt\+\_\+size}
\begin{DoxyCompactList}\small\item\em L\+MS bucket size, all the L\+MS suffixes are S-\/type suffixes. \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$\newline
struct Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+Bkt\+Info}

record L-\/type, S-\/type and L\+MS bucket sizes (no matter empty or non-\/empty) in SA \& L\+CP

Elements in SA \& L\+CP are naturally divided into multiple buckets and each bucket contains all the suffixes starting with an identical character. Each bucket can be further divided into two parts, whhere the left and right part separately contain the L-\/type and S-\/type suffixes, respectively. For description convenience, we denote the two part as L-\/type bucket and S-\/type bucket, respectively.

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_bkt_info_ac9e39b62bee276f6a9604bff588b6ecc}\label{struct_validate4_1_1_bkt_info_ac9e39b62bee276f6a9604bff588b6ecc}} 
\index{Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}!Bkt\+Info@{Bkt\+Info}}
\index{Bkt\+Info@{Bkt\+Info}!Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}}
\subsubsection{\texorpdfstring{Bkt\+Info()}{BktInfo()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::Bkt\+Info\+::\+Bkt\+Info (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

ctor

the number of buckets is ch\+\_\+max + 1, indexed by 0, 1, ..., ch\+\_\+max.

\subsection{Member Function Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_bkt_info_ac4fb0eabb194f773cd4ac5f6bcbbe969}\label{struct_validate4_1_1_bkt_info_ac4fb0eabb194f773cd4ac5f6bcbbe969}} 
\index{Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}!accumulate@{accumulate}}
\index{accumulate@{accumulate}!Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}}
\subsubsection{\texorpdfstring{accumulate()}{accumulate()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
void \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::Bkt\+Info\+::accumulate (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

collect the number of suffixes in the specified bucket

the number of suffixes in a bucket can be obtained by summing up the numbers of L-\/type and S-\/type suffixes. \mbox{\Hypertarget{struct_validate4_1_1_bkt_info_af55a2b8eee03bfe617ab34759b4ac007}\label{struct_validate4_1_1_bkt_info_af55a2b8eee03bfe617ab34759b4ac007}} 
\index{Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}!add\+\_\+l@{add\+\_\+l}}
\index{add\+\_\+l@{add\+\_\+l}!Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}}
\subsubsection{\texorpdfstring{add\+\_\+l()}{add\_l()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
void \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::Bkt\+Info\+::add\+\_\+l (\begin{DoxyParamCaption}\item[{const alphabet\+\_\+type}]{\+\_\+ch }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

count the number of L-\/type suffixes in the specified bucket

\mbox{\Hypertarget{struct_validate4_1_1_bkt_info_a5875efc6696925c0932f262174c2cc37}\label{struct_validate4_1_1_bkt_info_a5875efc6696925c0932f262174c2cc37}} 
\index{Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}!add\+\_\+lms@{add\+\_\+lms}}
\index{add\+\_\+lms@{add\+\_\+lms}!Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}}
\subsubsection{\texorpdfstring{add\+\_\+lms()}{add\_lms()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
void \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::Bkt\+Info\+::add\+\_\+lms (\begin{DoxyParamCaption}\item[{const alphabet\+\_\+type}]{\+\_\+ch }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

count the number of L\+MS suffixes in the specified bucket

\mbox{\Hypertarget{struct_validate4_1_1_bkt_info_a9c11b8915349954523623d9e7b0a2c2a}\label{struct_validate4_1_1_bkt_info_a9c11b8915349954523623d9e7b0a2c2a}} 
\index{Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}!add\+\_\+s@{add\+\_\+s}}
\index{add\+\_\+s@{add\+\_\+s}!Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}}
\subsubsection{\texorpdfstring{add\+\_\+s()}{add\_s()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
void \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::Bkt\+Info\+::add\+\_\+s (\begin{DoxyParamCaption}\item[{const alphabet\+\_\+type}]{\+\_\+ch }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

count the number of S-\/type suffixes in the specified bucket

\mbox{\Hypertarget{struct_validate4_1_1_bkt_info_ad8bc43e62d48c2f33fc6173f2a1d0840}\label{struct_validate4_1_1_bkt_info_ad8bc43e62d48c2f33fc6173f2a1d0840}} 
\index{Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}!display@{display}}
\index{display@{display}!Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}}
\subsubsection{\texorpdfstring{display()}{display()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
void \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::Bkt\+Info\+::display (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{struct_validate4_1_1_bkt_info_a22256d03bfca21336fa30f2ed9e12d51}\label{struct_validate4_1_1_bkt_info_a22256d03bfca21336fa30f2ed9e12d51}} 
\index{Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}!get\+\_\+bkt\+\_\+size@{get\+\_\+bkt\+\_\+size}}
\index{get\+\_\+bkt\+\_\+size@{get\+\_\+bkt\+\_\+size}!Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}}
\subsubsection{\texorpdfstring{get\+\_\+bkt\+\_\+size()}{get\_bkt\_size()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::Bkt\+Info\+::get\+\_\+bkt\+\_\+size (\begin{DoxyParamCaption}\item[{const alphabet\+\_\+type}]{\+\_\+ch }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

return the number of suffixes in the specified bucket

\mbox{\Hypertarget{struct_validate4_1_1_bkt_info_ae06c1968c2288d191f59214a0f10e7d7}\label{struct_validate4_1_1_bkt_info_ae06c1968c2288d191f59214a0f10e7d7}} 
\index{Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}!get\+\_\+l\+\_\+bkt\+\_\+size@{get\+\_\+l\+\_\+bkt\+\_\+size}}
\index{get\+\_\+l\+\_\+bkt\+\_\+size@{get\+\_\+l\+\_\+bkt\+\_\+size}!Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}}
\subsubsection{\texorpdfstring{get\+\_\+l\+\_\+bkt\+\_\+size()}{get\_l\_bkt\_size()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::Bkt\+Info\+::get\+\_\+l\+\_\+bkt\+\_\+size (\begin{DoxyParamCaption}\item[{const alphabet\+\_\+type}]{\+\_\+ch }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

return the number of L-\/type suffixes in the specified bucket

\mbox{\Hypertarget{struct_validate4_1_1_bkt_info_a0f7a940f516eefaae031ecd75c0fc971}\label{struct_validate4_1_1_bkt_info_a0f7a940f516eefaae031ecd75c0fc971}} 
\index{Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}!get\+\_\+lms\+\_\+bkt\+\_\+size@{get\+\_\+lms\+\_\+bkt\+\_\+size}}
\index{get\+\_\+lms\+\_\+bkt\+\_\+size@{get\+\_\+lms\+\_\+bkt\+\_\+size}!Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}}
\subsubsection{\texorpdfstring{get\+\_\+lms\+\_\+bkt\+\_\+size()}{get\_lms\_bkt\_size()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::Bkt\+Info\+::get\+\_\+lms\+\_\+bkt\+\_\+size (\begin{DoxyParamCaption}\item[{const alphabet\+\_\+type}]{\+\_\+ch }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

return the number of L\+MS suffixes in the specified bucket

\mbox{\Hypertarget{struct_validate4_1_1_bkt_info_a0c9a5615bab7f7c22d0d3f2de4b2621c}\label{struct_validate4_1_1_bkt_info_a0c9a5615bab7f7c22d0d3f2de4b2621c}} 
\index{Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}!get\+\_\+s\+\_\+bkt\+\_\+size@{get\+\_\+s\+\_\+bkt\+\_\+size}}
\index{get\+\_\+s\+\_\+bkt\+\_\+size@{get\+\_\+s\+\_\+bkt\+\_\+size}!Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}}
\subsubsection{\texorpdfstring{get\+\_\+s\+\_\+bkt\+\_\+size()}{get\_s\_bkt\_size()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::Bkt\+Info\+::get\+\_\+s\+\_\+bkt\+\_\+size (\begin{DoxyParamCaption}\item[{const alphabet\+\_\+type}]{\+\_\+ch }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

return the number of S-\/type suffixes in the specified bucket

\subsection{Member Data Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_bkt_info_a1485e4eceab1832f682e1751d310d2b9}\label{struct_validate4_1_1_bkt_info_a1485e4eceab1832f682e1751d310d2b9}} 
\index{Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}!ch\+\_\+max@{ch\+\_\+max}}
\index{ch\+\_\+max@{ch\+\_\+max}!Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}}
\subsubsection{\texorpdfstring{ch\+\_\+max}{ch\_max}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
const alphabet\+\_\+type \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::Bkt\+Info\+::ch\+\_\+max}

maximum value for alphabet\+\_\+type

\mbox{\Hypertarget{struct_validate4_1_1_bkt_info_a1659db6479f4667a77043e842b93f3fc}\label{struct_validate4_1_1_bkt_info_a1659db6479f4667a77043e842b93f3fc}} 
\index{Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}!m\+\_\+bkt\+\_\+size@{m\+\_\+bkt\+\_\+size}}
\index{m\+\_\+bkt\+\_\+size@{m\+\_\+bkt\+\_\+size}!Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}}
\subsubsection{\texorpdfstring{m\+\_\+bkt\+\_\+size}{m\_bkt\_size}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::Bkt\+Info\+::m\+\_\+bkt\+\_\+size}

bucket size

\mbox{\Hypertarget{struct_validate4_1_1_bkt_info_a0b44f8a1a308a6fff54cb0d05dd63ec4}\label{struct_validate4_1_1_bkt_info_a0b44f8a1a308a6fff54cb0d05dd63ec4}} 
\index{Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}!m\+\_\+l\+\_\+bkt\+\_\+size@{m\+\_\+l\+\_\+bkt\+\_\+size}}
\index{m\+\_\+l\+\_\+bkt\+\_\+size@{m\+\_\+l\+\_\+bkt\+\_\+size}!Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}}
\subsubsection{\texorpdfstring{m\+\_\+l\+\_\+bkt\+\_\+size}{m\_l\_bkt\_size}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::Bkt\+Info\+::m\+\_\+l\+\_\+bkt\+\_\+size}

L-\/type bucket size.

\mbox{\Hypertarget{struct_validate4_1_1_bkt_info_ad615aafce19e6e86948b227ad517b3cd}\label{struct_validate4_1_1_bkt_info_ad615aafce19e6e86948b227ad517b3cd}} 
\index{Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}!m\+\_\+lms\+\_\+bkt\+\_\+size@{m\+\_\+lms\+\_\+bkt\+\_\+size}}
\index{m\+\_\+lms\+\_\+bkt\+\_\+size@{m\+\_\+lms\+\_\+bkt\+\_\+size}!Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}}
\subsubsection{\texorpdfstring{m\+\_\+lms\+\_\+bkt\+\_\+size}{m\_lms\_bkt\_size}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::Bkt\+Info\+::m\+\_\+lms\+\_\+bkt\+\_\+size}

L\+MS bucket size, all the L\+MS suffixes are S-\/type suffixes.

\mbox{\Hypertarget{struct_validate4_1_1_bkt_info_acf0b824764fc045b9f1ce0f1ed2863ad}\label{struct_validate4_1_1_bkt_info_acf0b824764fc045b9f1ce0f1ed2863ad}} 
\index{Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}!m\+\_\+s\+\_\+bkt\+\_\+size@{m\+\_\+s\+\_\+bkt\+\_\+size}}
\index{m\+\_\+s\+\_\+bkt\+\_\+size@{m\+\_\+s\+\_\+bkt\+\_\+size}!Validate4\+::\+Bkt\+Info@{Validate4\+::\+Bkt\+Info}}
\subsubsection{\texorpdfstring{m\+\_\+s\+\_\+bkt\+\_\+size}{m\_s\_bkt\_size}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::Bkt\+Info\+::m\+\_\+s\+\_\+bkt\+\_\+size}

S-\/type bucket size.

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/\hyperlink{validate4_8h}{validate4.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/struct_validate4_1_1_l_m_s_validate.tex
2017/01/24

\hypertarget{struct_validate4_1_1_l_m_s_validate}{}\section{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+:\+:L\+M\+S\+Validate Struct Reference}
\label{struct_validate4_1_1_l_m_s_validate}\index{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+L\+M\+S\+Validate@{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+L\+M\+S\+Validate}}

validate S\+A\+\_\+\+L\+MS \& L\+C\+P\+\_\+\+L\+MS

\subsection*{Classes}
\begin{DoxyCompactItemize}
\item 
struct \hyperlink{struct_validate4_1_1_l_m_s_validate_1_1_r_interval}{R\+Interval}
\begin{DoxyCompactList}\small\item\em store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, ... \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{struct_validate4_1_1_l_m_s_validate_a93810bf60dc23710fb678ae863aaebec}{L\+M\+S\+Validate} (\hyperlink{class_validate4_a49c80b3d101be19542a4341c2387603a}{alphabet\+\_\+vector\+\_\+type} $\ast$\+\_\+t, \hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$\+\_\+sa, \hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$\+\_\+lcp)
\begin{DoxyCompactList}\small\item\em ctor \end{DoxyCompactList}\item 
void \hyperlink{struct_validate4_1_1_l_m_s_validate_afd7ee2100849c6c9bc493782d0c9aea3}{retrieve\+\_\+lms} ()
\begin{DoxyCompactList}\small\item\em retrive S\+A\+\_\+\+L\+MS and L\+C\+P\+\_\+\+L\+MS from SA and L\+CP \end{DoxyCompactList}\item 
\hyperlink{class_validate4_ad945003027abfd152a0e177d7541580d}{pair2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_l_m_s_validate_a0d6e08ffc57dfd088ff737ed01a566b2}{fetch\+\_\+fp} ()
\begin{DoxyCompactList}\small\item\em fetch fp\mbox{[}0, S\+A\+\_\+\+L\+MS\mbox{[}i\mbox{]} -\/ 1\mbox{]} \end{DoxyCompactList}\item 
\hyperlink{class_validate4_ac2e4bde5df51eeff18ef5591d76e63dc}{triple3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_l_m_s_validate_aa0d10da14dc1a8015967216e19eeb9af}{fetch\+\_\+fp\+\_\+ch\+\_\+cur} ()
\begin{DoxyCompactList}\small\item\em fetch fp\mbox{[}0, S\+A\+\_\+\+L\+MS\mbox{[}i\mbox{]} + L\+C\+P\+\_\+\+L\+MS\mbox{[}i\mbox{]} -\/ 1\mbox{]} and T\mbox{[}S\+A\+\_\+\+L\+MS\mbox{[}i\mbox{]} + L\+C\+P\+\_\+\+L\+MS\mbox{[}i\mbox{]}\mbox{]} \end{DoxyCompactList}\item 
\hyperlink{class_validate4_ac2e4bde5df51eeff18ef5591d76e63dc}{triple3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_l_m_s_validate_a4e998a01460cb1c68954282065ec7c86}{fetch\+\_\+fp\+\_\+ch\+\_\+pre} ()
\begin{DoxyCompactList}\small\item\em fetch fp\mbox{[}0, S\+A\+\_\+\+L\+MS\mbox{[}i\mbox{]} + L\+C\+P\+\_\+\+L\+MS\mbox{[}i + 1\mbox{]} -\/ 1\mbox{]} and T\mbox{[}S\+A\+\_\+\+L\+MS\mbox{[}i\mbox{]} + L\+C\+P\+\_\+\+L\+MS\mbox{[}i + 1\mbox{]}\mbox{]} \end{DoxyCompactList}\item 
bool \hyperlink{struct_validate4_1_1_l_m_s_validate_a906ef49f72b8a2baa0d7a2d196c4b62e}{check} (\hyperlink{class_validate4_ad945003027abfd152a0e177d7541580d}{pair2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$\+\_\+sorter1, \hyperlink{class_validate4_ac2e4bde5df51eeff18ef5591d76e63dc}{triple3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$\+\_\+sorter2, \hyperlink{class_validate4_ac2e4bde5df51eeff18ef5591d76e63dc}{triple3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$\+\_\+sorter3)
\begin{DoxyCompactList}\small\item\em check the result \end{DoxyCompactList}\item 
bool \hyperlink{struct_validate4_1_1_l_m_s_validate_ae154c8745df4a743f7f13dfbb6e0dd95}{run} ()
\begin{DoxyCompactList}\small\item\em core part \end{DoxyCompactList}\item 
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_l_m_s_validate_a31cdfa18f11ba39b3d9fbf08706913fc}{get\+\_\+sa\+\_\+lms} ()
\begin{DoxyCompactList}\small\item\em return m\+\_\+sa\+\_\+lms \end{DoxyCompactList}\item 
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_l_m_s_validate_aee1c58f6d4c6e4cfb99bde60f6d05323}{get\+\_\+lcp\+\_\+lms} ()
\begin{DoxyCompactList}\small\item\em return m\+\_\+lcp\+\_\+lms \end{DoxyCompactList}\item 
\hyperlink{struct_validate4_1_1_l_m_s_validate_adaf3ee4e530f37787e9ff8c9f2ac511b}{$\sim$\+L\+M\+S\+Validate} ()
\end{DoxyCompactItemize}
\subsection*{Private Attributes}
\begin{DoxyCompactItemize}
\item 
\hyperlink{class_validate4_a49c80b3d101be19542a4341c2387603a}{alphabet\+\_\+vector\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_l_m_s_validate_a01e3da98e0c54dad32ac5b0b083e0136}{m\+\_\+t}
\begin{DoxyCompactList}\small\item\em input string \end{DoxyCompactList}\item 
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_l_m_s_validate_ab1f06c75524fdc58a13bdc865c107a3b}{m\+\_\+sa}
\begin{DoxyCompactList}\small\item\em input suffix array \end{DoxyCompactList}\item 
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_l_m_s_validate_a1618db621ffc7cc9265df07c08b58b93}{m\+\_\+lcp}
\begin{DoxyCompactList}\small\item\em input L\+CP array \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate4_1_1_l_m_s_validate_a76364ef3c9b1168683dba0611b6e3114}{m\+\_\+len}
\begin{DoxyCompactList}\small\item\em length of input string \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate4_1_1_l_m_s_validate_a77706615d727c80929bca82cbfc6aa47}{m\+\_\+lms\+\_\+num}
\begin{DoxyCompactList}\small\item\em number of L\+MS suffixes \end{DoxyCompactList}\item 
\hyperlink{struct_validate4_1_1_l_m_s_validate_1_1_r_interval}{R\+Interval} $\ast$ \hyperlink{struct_validate4_1_1_l_m_s_validate_a51f4d2be526cb9a2793e793242922951}{m\+\_\+rinterval}
\begin{DoxyCompactList}\small\item\em pointer to an \hyperlink{struct_validate4_1_1_l_m_s_validate_1_1_r_interval}{R\+Interval} object \end{DoxyCompactList}\item 
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_l_m_s_validate_a789edc9840b1d8af636e4f07127ac333}{m\+\_\+sa\+\_\+lms}
\begin{DoxyCompactList}\small\item\em pointer to S\+A\+\_\+\+L\+MS \end{DoxyCompactList}\item 
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_l_m_s_validate_a6ce0f5fd88cd24e81c85faad0c1d64d5}{m\+\_\+lcp\+\_\+lms}
\begin{DoxyCompactList}\small\item\em pointer to L\+C\+P\+\_\+\+L\+MS \end{DoxyCompactList}\item 
const alphabet\+\_\+type \hyperlink{struct_validate4_1_1_l_m_s_validate_a3e640263256e534dcf3da45f50ef0645}{ch\+\_\+max}
\begin{DoxyCompactList}\small\item\em maximum value of alphabet type \end{DoxyCompactList}\item 
const size\+\_\+type \hyperlink{struct_validate4_1_1_l_m_s_validate_a8dce0e079545d3c4f2649614053cf5f1}{val\+\_\+max}
\begin{DoxyCompactList}\small\item\em maximum value of size type \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$\newline
struct Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+L\+M\+S\+Validate}

validate S\+A\+\_\+\+L\+MS \& L\+C\+P\+\_\+\+L\+MS

The Karp-\/\+Rabin fingerprinting function is exploited to validate the correctness of S\+A\+\_\+\+L\+MS \& L\+C\+P\+\_\+\+L\+MS.

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_a93810bf60dc23710fb678ae863aaebec}\label{struct_validate4_1_1_l_m_s_validate_a93810bf60dc23710fb678ae863aaebec}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!L\+M\+S\+Validate@{L\+M\+S\+Validate}}
\index{L\+M\+S\+Validate@{L\+M\+S\+Validate}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{L\+M\+S\+Validate()}{LMSValidate()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::\+L\+M\+S\+Validate (\begin{DoxyParamCaption}\item[{\hyperlink{class_validate4_a49c80b3d101be19542a4341c2387603a}{alphabet\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+t,  }\item[{\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+sa,  }\item[{\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+lcp }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

ctor

\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_adaf3ee4e530f37787e9ff8c9f2ac511b}\label{struct_validate4_1_1_l_m_s_validate_adaf3ee4e530f37787e9ff8c9f2ac511b}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!````~L\+M\+S\+Validate@{$\sim$\+L\+M\+S\+Validate}}
\index{````~L\+M\+S\+Validate@{$\sim$\+L\+M\+S\+Validate}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{$\sim$\+L\+M\+S\+Validate()}{~LMSValidate()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::$\sim$\+L\+M\+S\+Validate (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

\subsection{Member Function Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_a906ef49f72b8a2baa0d7a2d196c4b62e}\label{struct_validate4_1_1_l_m_s_validate_a906ef49f72b8a2baa0d7a2d196c4b62e}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!check@{check}}
\index{check@{check}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{check()}{check()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
bool \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::check (\begin{DoxyParamCaption}\item[{\hyperlink{class_validate4_ad945003027abfd152a0e177d7541580d}{pair2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$}]{\+\_\+sorter1,  }\item[{\hyperlink{class_validate4_ac2e4bde5df51eeff18ef5591d76e63dc}{triple3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$}]{\+\_\+sorter2,  }\item[{\hyperlink{class_validate4_ac2e4bde5df51eeff18ef5591d76e63dc}{triple3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$}]{\+\_\+sorter3 }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

check the result

\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_a0d6e08ffc57dfd088ff737ed01a566b2}\label{struct_validate4_1_1_l_m_s_validate_a0d6e08ffc57dfd088ff737ed01a566b2}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!fetch\+\_\+fp@{fetch\+\_\+fp}}
\index{fetch\+\_\+fp@{fetch\+\_\+fp}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{fetch\+\_\+fp()}{fetch\_fp()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_ad945003027abfd152a0e177d7541580d}{pair2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::fetch\+\_\+fp (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

fetch fp\mbox{[}0, S\+A\+\_\+\+L\+MS\mbox{[}i\mbox{]} -\/ 1\mbox{]}

\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_aa0d10da14dc1a8015967216e19eeb9af}\label{struct_validate4_1_1_l_m_s_validate_aa0d10da14dc1a8015967216e19eeb9af}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!fetch\+\_\+fp\+\_\+ch\+\_\+cur@{fetch\+\_\+fp\+\_\+ch\+\_\+cur}}
\index{fetch\+\_\+fp\+\_\+ch\+\_\+cur@{fetch\+\_\+fp\+\_\+ch\+\_\+cur}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{fetch\+\_\+fp\+\_\+ch\+\_\+cur()}{fetch\_fp\_ch\_cur()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_ac2e4bde5df51eeff18ef5591d76e63dc}{triple3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::fetch\+\_\+fp\+\_\+ch\+\_\+cur (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

fetch fp\mbox{[}0, S\+A\+\_\+\+L\+MS\mbox{[}i\mbox{]} + L\+C\+P\+\_\+\+L\+MS\mbox{[}i\mbox{]} -\/ 1\mbox{]} and T\mbox{[}S\+A\+\_\+\+L\+MS\mbox{[}i\mbox{]} + L\+C\+P\+\_\+\+L\+MS\mbox{[}i\mbox{]}\mbox{]}

\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_a4e998a01460cb1c68954282065ec7c86}\label{struct_validate4_1_1_l_m_s_validate_a4e998a01460cb1c68954282065ec7c86}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!fetch\+\_\+fp\+\_\+ch\+\_\+pre@{fetch\+\_\+fp\+\_\+ch\+\_\+pre}}
\index{fetch\+\_\+fp\+\_\+ch\+\_\+pre@{fetch\+\_\+fp\+\_\+ch\+\_\+pre}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{fetch\+\_\+fp\+\_\+ch\+\_\+pre()}{fetch\_fp\_ch\_pre()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_ac2e4bde5df51eeff18ef5591d76e63dc}{triple3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::fetch\+\_\+fp\+\_\+ch\+\_\+pre (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

fetch fp\mbox{[}0, S\+A\+\_\+\+L\+MS\mbox{[}i\mbox{]} + L\+C\+P\+\_\+\+L\+MS\mbox{[}i + 1\mbox{]} -\/ 1\mbox{]} and T\mbox{[}S\+A\+\_\+\+L\+MS\mbox{[}i\mbox{]} + L\+C\+P\+\_\+\+L\+MS\mbox{[}i + 1\mbox{]}\mbox{]}

\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_aee1c58f6d4c6e4cfb99bde60f6d05323}\label{struct_validate4_1_1_l_m_s_validate_aee1c58f6d4c6e4cfb99bde60f6d05323}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!get\+\_\+lcp\+\_\+lms@{get\+\_\+lcp\+\_\+lms}}
\index{get\+\_\+lcp\+\_\+lms@{get\+\_\+lcp\+\_\+lms}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{get\+\_\+lcp\+\_\+lms()}{get\_lcp\_lms()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::get\+\_\+lcp\+\_\+lms (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

return m\+\_\+lcp\+\_\+lms

\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_a31cdfa18f11ba39b3d9fbf08706913fc}\label{struct_validate4_1_1_l_m_s_validate_a31cdfa18f11ba39b3d9fbf08706913fc}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!get\+\_\+sa\+\_\+lms@{get\+\_\+sa\+\_\+lms}}
\index{get\+\_\+sa\+\_\+lms@{get\+\_\+sa\+\_\+lms}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{get\+\_\+sa\+\_\+lms()}{get\_sa\_lms()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::get\+\_\+sa\+\_\+lms (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

return m\+\_\+sa\+\_\+lms

\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_afd7ee2100849c6c9bc493782d0c9aea3}\label{struct_validate4_1_1_l_m_s_validate_afd7ee2100849c6c9bc493782d0c9aea3}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!retrieve\+\_\+lms@{retrieve\+\_\+lms}}
\index{retrieve\+\_\+lms@{retrieve\+\_\+lms}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{retrieve\+\_\+lms()}{retrieve\_lms()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
void \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::retrieve\+\_\+lms (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

retrive S\+A\+\_\+\+L\+MS and L\+C\+P\+\_\+\+L\+MS from SA and L\+CP

\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_ae154c8745df4a743f7f13dfbb6e0dd95}\label{struct_validate4_1_1_l_m_s_validate_ae154c8745df4a743f7f13dfbb6e0dd95}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!run@{run}}
\index{run@{run}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{run()}{run()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
bool \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::run (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

core part

\subsection{Member Data Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_a3e640263256e534dcf3da45f50ef0645}\label{struct_validate4_1_1_l_m_s_validate_a3e640263256e534dcf3da45f50ef0645}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!ch\+\_\+max@{ch\+\_\+max}}
\index{ch\+\_\+max@{ch\+\_\+max}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{ch\+\_\+max}{ch\_max}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
const alphabet\+\_\+type \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::ch\+\_\+max\hspace{0.3cm}{\ttfamily [private]}}

maximum value of alphabet type

\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_a1618db621ffc7cc9265df07c08b58b93}\label{struct_validate4_1_1_l_m_s_validate_a1618db621ffc7cc9265df07c08b58b93}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!m\+\_\+lcp@{m\+\_\+lcp}}
\index{m\+\_\+lcp@{m\+\_\+lcp}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{m\+\_\+lcp}{m\_lcp}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::m\+\_\+lcp\hspace{0.3cm}{\ttfamily [private]}}

input L\+CP array

\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_a6ce0f5fd88cd24e81c85faad0c1d64d5}\label{struct_validate4_1_1_l_m_s_validate_a6ce0f5fd88cd24e81c85faad0c1d64d5}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!m\+\_\+lcp\+\_\+lms@{m\+\_\+lcp\+\_\+lms}}
\index{m\+\_\+lcp\+\_\+lms@{m\+\_\+lcp\+\_\+lms}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{m\+\_\+lcp\+\_\+lms}{m\_lcp\_lms}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::m\+\_\+lcp\+\_\+lms\hspace{0.3cm}{\ttfamily [private]}}

pointer to L\+C\+P\+\_\+\+L\+MS

\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_a76364ef3c9b1168683dba0611b6e3114}\label{struct_validate4_1_1_l_m_s_validate_a76364ef3c9b1168683dba0611b6e3114}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!m\+\_\+len@{m\+\_\+len}}
\index{m\+\_\+len@{m\+\_\+len}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{m\+\_\+len}{m\_len}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::m\+\_\+len\hspace{0.3cm}{\ttfamily [private]}}

length of input string

\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_a77706615d727c80929bca82cbfc6aa47}\label{struct_validate4_1_1_l_m_s_validate_a77706615d727c80929bca82cbfc6aa47}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!m\+\_\+lms\+\_\+num@{m\+\_\+lms\+\_\+num}}
\index{m\+\_\+lms\+\_\+num@{m\+\_\+lms\+\_\+num}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{m\+\_\+lms\+\_\+num}{m\_lms\_num}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::m\+\_\+lms\+\_\+num\hspace{0.3cm}{\ttfamily [private]}}

number of L\+MS suffixes

\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_a51f4d2be526cb9a2793e793242922951}\label{struct_validate4_1_1_l_m_s_validate_a51f4d2be526cb9a2793e793242922951}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!m\+\_\+rinterval@{m\+\_\+rinterval}}
\index{m\+\_\+rinterval@{m\+\_\+rinterval}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{m\+\_\+rinterval}{m\_rinterval}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{struct_validate4_1_1_l_m_s_validate_1_1_r_interval}{R\+Interval}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::m\+\_\+rinterval\hspace{0.3cm}{\ttfamily [private]}}

pointer to an \hyperlink{struct_validate4_1_1_l_m_s_validate_1_1_r_interval}{R\+Interval} object

\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_ab1f06c75524fdc58a13bdc865c107a3b}\label{struct_validate4_1_1_l_m_s_validate_ab1f06c75524fdc58a13bdc865c107a3b}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!m\+\_\+sa@{m\+\_\+sa}}
\index{m\+\_\+sa@{m\+\_\+sa}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{m\+\_\+sa}{m\_sa}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::m\+\_\+sa\hspace{0.3cm}{\ttfamily [private]}}

input suffix array

\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_a789edc9840b1d8af636e4f07127ac333}\label{struct_validate4_1_1_l_m_s_validate_a789edc9840b1d8af636e4f07127ac333}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!m\+\_\+sa\+\_\+lms@{m\+\_\+sa\+\_\+lms}}
\index{m\+\_\+sa\+\_\+lms@{m\+\_\+sa\+\_\+lms}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{m\+\_\+sa\+\_\+lms}{m\_sa\_lms}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::m\+\_\+sa\+\_\+lms\hspace{0.3cm}{\ttfamily [private]}}

pointer to S\+A\+\_\+\+L\+MS

\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_a01e3da98e0c54dad32ac5b0b083e0136}\label{struct_validate4_1_1_l_m_s_validate_a01e3da98e0c54dad32ac5b0b083e0136}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!m\+\_\+t@{m\+\_\+t}}
\index{m\+\_\+t@{m\+\_\+t}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{m\+\_\+t}{m\_t}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_a49c80b3d101be19542a4341c2387603a}{alphabet\+\_\+vector\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::m\+\_\+t\hspace{0.3cm}{\ttfamily [private]}}

input string

\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_a8dce0e079545d3c4f2649614053cf5f1}\label{struct_validate4_1_1_l_m_s_validate_a8dce0e079545d3c4f2649614053cf5f1}} 
\index{Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}!val\+\_\+max@{val\+\_\+max}}
\index{val\+\_\+max@{val\+\_\+max}!Validate4\+::\+L\+M\+S\+Validate@{Validate4\+::\+L\+M\+S\+Validate}}
\subsubsection{\texorpdfstring{val\+\_\+max}{val\_max}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
const size\+\_\+type \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::val\+\_\+max\hspace{0.3cm}{\ttfamily [private]}}

maximum value of size type

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/\hyperlink{validate4_8h}{validate4.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/struct_validate4_1_1_l_m_s_validate_1_1_r_interval.tex
2017/01/24

\hypertarget{struct_validate4_1_1_l_m_s_validate_1_1_r_interval}{}\section{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+:\+:L\+M\+S\+Validate\+:\+:R\+Interval Struct Reference}
\label{struct_validate4_1_1_l_m_s_validate_1_1_r_interval}\index{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+L\+M\+S\+Validate\+::\+R\+Interval@{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+L\+M\+S\+Validate\+::\+R\+Interval}}

store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, ...

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{struct_validate4_1_1_l_m_s_validate_1_1_r_interval_ababcb7e5df16b2bd27a8b6285ccab230}{R\+Interval} (\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \+\_\+len)
\begin{DoxyCompactList}\small\item\em ctor \end{DoxyCompactList}\item 
\hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} \hyperlink{struct_validate4_1_1_l_m_s_validate_1_1_r_interval_a7c1aee0f298285e1eb0df8b3ab368036}{compute} (\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \+\_\+interval)
\begin{DoxyCompactList}\small\item\em get fp\+Interval \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Public Attributes}
\begin{DoxyCompactItemize}
\item 
\hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_l_m_s_validate_1_1_r_interval_ac666861e46f85b525452722ee93e6ff0}{m\+\_\+data}
\begin{DoxyCompactList}\small\item\em data load \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate4_1_1_l_m_s_validate_1_1_r_interval_ac1b3892751cdcfaa18b45203a247ffc5}{m\+\_\+num}
\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$\newline
struct Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+L\+M\+S\+Validate\+::\+R\+Interval}

store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, ...

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_1_1_r_interval_ababcb7e5df16b2bd27a8b6285ccab230}\label{struct_validate4_1_1_l_m_s_validate_1_1_r_interval_ababcb7e5df16b2bd27a8b6285ccab230}} 
\index{Validate4\+::\+L\+M\+S\+Validate\+::\+R\+Interval@{Validate4\+::\+L\+M\+S\+Validate\+::\+R\+Interval}!R\+Interval@{R\+Interval}}
\index{R\+Interval@{R\+Interval}!Validate4\+::\+L\+M\+S\+Validate\+::\+R\+Interval@{Validate4\+::\+L\+M\+S\+Validate\+::\+R\+Interval}}
\subsubsection{\texorpdfstring{R\+Interval()}{RInterval()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::\+R\+Interval\+::\+R\+Interval (\begin{DoxyParamCaption}\item[{\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}]{\+\_\+len }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

ctor

\subsection{Member Function Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_1_1_r_interval_a7c1aee0f298285e1eb0df8b3ab368036}\label{struct_validate4_1_1_l_m_s_validate_1_1_r_interval_a7c1aee0f298285e1eb0df8b3ab368036}} 
\index{Validate4\+::\+L\+M\+S\+Validate\+::\+R\+Interval@{Validate4\+::\+L\+M\+S\+Validate\+::\+R\+Interval}!compute@{compute}}
\index{compute@{compute}!Validate4\+::\+L\+M\+S\+Validate\+::\+R\+Interval@{Validate4\+::\+L\+M\+S\+Validate\+::\+R\+Interval}}
\subsubsection{\texorpdfstring{compute()}{compute()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::\+R\+Interval\+::compute (\begin{DoxyParamCaption}\item[{\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}]{\+\_\+interval }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

get fp\+Interval

\subsection{Member Data Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_1_1_r_interval_ac666861e46f85b525452722ee93e6ff0}\label{struct_validate4_1_1_l_m_s_validate_1_1_r_interval_ac666861e46f85b525452722ee93e6ff0}} 
\index{Validate4\+::\+L\+M\+S\+Validate\+::\+R\+Interval@{Validate4\+::\+L\+M\+S\+Validate\+::\+R\+Interval}!m\+\_\+data@{m\+\_\+data}}
\index{m\+\_\+data@{m\+\_\+data}!Validate4\+::\+L\+M\+S\+Validate\+::\+R\+Interval@{Validate4\+::\+L\+M\+S\+Validate\+::\+R\+Interval}}
\subsubsection{\texorpdfstring{m\+\_\+data}{m\_data}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::\+R\+Interval\+::m\+\_\+data}

data load

\mbox{\Hypertarget{struct_validate4_1_1_l_m_s_validate_1_1_r_interval_ac1b3892751cdcfaa18b45203a247ffc5}\label{struct_validate4_1_1_l_m_s_validate_1_1_r_interval_ac1b3892751cdcfaa18b45203a247ffc5}} 
\index{Validate4\+::\+L\+M\+S\+Validate\+::\+R\+Interval@{Validate4\+::\+L\+M\+S\+Validate\+::\+R\+Interval}!m\+\_\+num@{m\+\_\+num}}
\index{m\+\_\+num@{m\+\_\+num}!Validate4\+::\+L\+M\+S\+Validate\+::\+R\+Interval@{Validate4\+::\+L\+M\+S\+Validate\+::\+R\+Interval}}
\subsubsection{\texorpdfstring{m\+\_\+num}{m\_num}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+M\+S\+Validate\+::\+R\+Interval\+::m\+\_\+num}

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/\hyperlink{validate4_8h}{validate4.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/struct_validate4_1_1_l_scan.tex
2017/01/24

\hypertarget{struct_validate4_1_1_l_scan}{}\section{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+:\+:L\+Scan Struct Reference}
\label{struct_validate4_1_1_l_scan}\index{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+L\+Scan@{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+L\+Scan}}

scan SA \& L\+CP rightward to validate the S\+A-\/values of all the S-\/type suffixes and the L\+C\+P-\/values of them and their left neighbor in SA.

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{struct_validate4_1_1_l_scan_a8e95d99392cee99b081b8354d9a13757}{L\+Scan} (\hyperlink{struct_validate4_1_1_bkt_info}{Bkt\+Info} \&\+\_\+bkt\+\_\+info, \hyperlink{class_validate4_a49c80b3d101be19542a4341c2387603a}{alphabet\+\_\+vector\+\_\+type} $\ast$\+\_\+t, \hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$\+\_\+sa, \hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$\+\_\+lcp)
\begin{DoxyCompactList}\small\item\em ctor \end{DoxyCompactList}\item 
bool \hyperlink{struct_validate4_1_1_l_scan_a071826b788f5aadc92f87ad8cc986649}{s\+\_\+is\+\_\+empty} ()
\begin{DoxyCompactList}\small\item\em check if no more L\+MS to be scanned \end{DoxyCompactList}\item 
bool \hyperlink{struct_validate4_1_1_l_scan_a22b7a0b8c64f17da5a815ddaf8619ebb}{l\+\_\+is\+\_\+empty} ()
\begin{DoxyCompactList}\small\item\em check if no more L-\/type to be scanned \end{DoxyCompactList}\item 
bool \hyperlink{struct_validate4_1_1_l_scan_a9331f92d91cf67c38a3d6948a2190df8}{s\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty} ()
\begin{DoxyCompactList}\small\item\em check if no more S-\/type suffixes to be scanned in current bucket \end{DoxyCompactList}\item 
bool \hyperlink{struct_validate4_1_1_l_scan_ae76d58363b02ac96925becbbdbe02977}{l\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty} ()
\begin{DoxyCompactList}\small\item\em check if no more L-\/type suffixes to be scanned in current bucket \end{DoxyCompactList}\item 
void \hyperlink{struct_validate4_1_1_l_scan_aa570a8ac447950b6b0d9deae2e4cae63}{find\+\_\+next\+\_\+s\+\_\+bkt} ()
\begin{DoxyCompactList}\small\item\em find next non-\/empty S-\/bucket \end{DoxyCompactList}\item 
void \hyperlink{struct_validate4_1_1_l_scan_abd7e922317ee9d64d90853adba6a7634}{find\+\_\+next\+\_\+l\+\_\+bkt} ()
\begin{DoxyCompactList}\small\item\em find next non-\/empty L-\/bucket \end{DoxyCompactList}\item 
void \hyperlink{struct_validate4_1_1_l_scan_a4e402bf4909c1502337801bd56e22be2}{fetch\+\_\+s\+\_\+scanned} (size\+\_\+type \&\+\_\+sa\+\_\+value, size\+\_\+type \&\+\_\+lcp\+\_\+value)
\begin{DoxyCompactList}\small\item\em fetch the S\+A-\/value for currently scanned S-\/type suffix and the L\+C\+P-\/value of the suffix and its right neighbor in SA \end{DoxyCompactList}\item 
void \hyperlink{struct_validate4_1_1_l_scan_a1fabfd83060b51fdedd46b413da0f060}{fetch\+\_\+l\+\_\+scanned} (size\+\_\+type \&\+\_\+sa\+\_\+value, size\+\_\+type \&\+\_\+lcp\+\_\+value)
\begin{DoxyCompactList}\small\item\em fetch the S\+A-\/value for currently scanned L-\/type suffix and the L\+C\+P-\/value of the suffix and its right neighbor in SA \end{DoxyCompactList}\item 
void \hyperlink{struct_validate4_1_1_l_scan_a37796b2c2e404a1bdf1362e7b1794fee}{fetch\+\_\+s\+\_\+induced} (const alphabet\+\_\+type \+\_\+ch, size\+\_\+type \&\+\_\+sa\+\_\+value, size\+\_\+type \&\+\_\+lcp\+\_\+value)
\begin{DoxyCompactList}\small\item\em fetch the S\+A-\/value for currently induced S-\/type suffix and the L\+C\+P-\/value for the suffix and its right neighbor in SA \end{DoxyCompactList}\item 
alphabet\+\_\+type \hyperlink{struct_validate4_1_1_l_scan_a1be5f226a5053456897df328302764f3}{get\+\_\+s\+\_\+bkt\+\_\+ch} ()
\begin{DoxyCompactList}\small\item\em get ch for the S-\/type bucket currently being scanned \end{DoxyCompactList}\item 
alphabet\+\_\+type \hyperlink{struct_validate4_1_1_l_scan_ae986f4106e79412c60be8a88a9637f66}{get\+\_\+l\+\_\+bkt\+\_\+ch} ()
\begin{DoxyCompactList}\small\item\em get ch for the L\+MS bucket currently being scanned \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate4_1_1_l_scan_a9e88ab70a4b681b145bd79fa05d8f13d}{bruteforce\+\_\+compute\+\_\+lcp} (const size\+\_\+type \&\+\_\+pos1, const size\+\_\+type \&\+\_\+pos2)
\begin{DoxyCompactList}\small\item\em literally compare two suffixes pointed to by the starting positions \end{DoxyCompactList}\item 
\hyperlink{struct_validate4_1_1_l_scan_a1ac7b38fcbb0968d0683a0df18fedd9f}{$\sim$\+L\+Scan} ()
\begin{DoxyCompactList}\small\item\em dtor \end{DoxyCompactList}\item 
bool \hyperlink{struct_validate4_1_1_l_scan_ac923c1ac593c291db774594e8f51c9e5}{run} (\hyperlink{class_validate4_aa35a0ebf404821377118043d536be262}{triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$\+\_\+pre\+\_\+item\+\_\+of\+\_\+s\+\_\+sorter, \hyperlink{class_validate4_a883822e6f1be0d67f71e1feb9729b1dc}{pair4\+\_\+vector\+\_\+type} $\ast$\+\_\+pre\+\_\+item\+\_\+of\+\_\+l\+\_\+vector)
\begin{DoxyCompactList}\small\item\em induce and check the order of S-\/type suffixes and their L\+C\+P-\/values \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Private Attributes}
\begin{DoxyCompactItemize}
\item 
const alphabet\+\_\+type \hyperlink{struct_validate4_1_1_l_scan_a907234b2fa774b42e87050f0066e26b6}{ch\+\_\+max}
\begin{DoxyCompactList}\small\item\em maximum character \end{DoxyCompactList}\item 
\hyperlink{class_validate4_a49c80b3d101be19542a4341c2387603a}{alphabet\+\_\+vector\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_l_scan_a3f7a5fe6e603159503a161185eb38667}{m\+\_\+t}
\begin{DoxyCompactList}\small\item\em pointer to the input string \end{DoxyCompactList}\item 
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_l_scan_a38f7644fb0e19bc24c83cbcc04f1b01f}{m\+\_\+sa}
\begin{DoxyCompactList}\small\item\em pointer to the suffix array \end{DoxyCompactList}\item 
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_l_scan_af9ba74080cb7b3e0f685d29a4c78ab73}{m\+\_\+lcp}
\begin{DoxyCompactList}\small\item\em pointer to the L\+CP array \end{DoxyCompactList}\item 
std\+::vector$<$ \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $>$ \hyperlink{struct_validate4_1_1_l_scan_ad072911a65100e41a34b17ee6dc79cd4}{m\+\_\+s\+\_\+bkt\+\_\+toscan}
\begin{DoxyCompactList}\small\item\em number of S-\/type suffixes to be scanned in each bucket \end{DoxyCompactList}\item 
std\+::vector$<$ \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $>$ \hyperlink{struct_validate4_1_1_l_scan_a66ce5f59bcd37d47371f847769297b46}{m\+\_\+s\+\_\+bkt\+\_\+scanned}
\begin{DoxyCompactList}\small\item\em number of S-\/type suffixes scanned in each bucket \end{DoxyCompactList}\item 
std\+::vector$<$ \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $>$ \hyperlink{struct_validate4_1_1_l_scan_ad500f8ccaffab088a465a288f92fd4b2}{m\+\_\+l\+\_\+bkt\+\_\+toscan}
\begin{DoxyCompactList}\small\item\em number of L-\/type suffixes to be scanned in each bucket \end{DoxyCompactList}\item 
std\+::vector$<$ \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $>$ \hyperlink{struct_validate4_1_1_l_scan_a41c937ae175b97c22325458bcafeeb7e}{m\+\_\+l\+\_\+bkt\+\_\+scanned}
\begin{DoxyCompactList}\small\item\em numer of L-\/type suffixes scanned in each bucket \end{DoxyCompactList}\item 
std\+::vector$<$ \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $>$ \hyperlink{struct_validate4_1_1_l_scan_a3a342dcdec25a509df8f943c1e91b3b8}{m\+\_\+s\+\_\+bkt\+\_\+spos}
\begin{DoxyCompactList}\small\item\em indicate the starting position of each L-\/type bucket in SA (right boundary) \end{DoxyCompactList}\item 
std\+::vector$<$ \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $>$ \hyperlink{struct_validate4_1_1_l_scan_a82878f6289ad8c9ec7204de1e5a2e04c}{m\+\_\+l\+\_\+bkt\+\_\+spos}
\begin{DoxyCompactList}\small\item\em indicate the starting position of each S-\/type bucket in SA (right boundary) \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate4_1_1_l_scan_abaf348442b39a1a0447a382e1f66f13b}{m\+\_\+total\+\_\+s\+\_\+toscan}
\begin{DoxyCompactList}\small\item\em total number of S-\/type suffixes to be scanned \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate4_1_1_l_scan_a7b3fae11ba397c30d0f25f055e02cdf1}{m\+\_\+total\+\_\+s\+\_\+scanned}
\begin{DoxyCompactList}\small\item\em total number of S-\/type suffixes already scanned \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate4_1_1_l_scan_a400a5151679cb9c9da110cf565e81652}{m\+\_\+total\+\_\+l\+\_\+toscan}
\begin{DoxyCompactList}\small\item\em total number of L-\/type suffixes to be scanned \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate4_1_1_l_scan_aa9addcdfacecc8d69159683c9f694bef}{m\+\_\+total\+\_\+l\+\_\+scanned}
\begin{DoxyCompactList}\small\item\em total number of L-\/type suffixes already scanned \end{DoxyCompactList}\item 
alphabet\+\_\+type \hyperlink{struct_validate4_1_1_l_scan_ac765bc6e6817fbe71a7aacbd4e2811d9}{m\+\_\+cur\+\_\+s\+\_\+ch}
\begin{DoxyCompactList}\small\item\em S-\/type bucket currently being scanned. \end{DoxyCompactList}\item 
alphabet\+\_\+type \hyperlink{struct_validate4_1_1_l_scan_abf7d8f90883c943c08a007425c43c644}{m\+\_\+cur\+\_\+l\+\_\+ch}
\begin{DoxyCompactList}\small\item\em L-\/type bucket currently being scanned. \end{DoxyCompactList}\item 
size\+\_\+vector\+\_\+type\+::bufreader\+\_\+reverse\+\_\+type $\ast$ \hyperlink{struct_validate4_1_1_l_scan_aa424a1fcc802dbe8556953c1e8d07207}{m\+\_\+sa\+\_\+rev\+\_\+reader}
\begin{DoxyCompactList}\small\item\em for scan, point to the S\+A-\/value for currently scanned suffix (retrieve from SA, leftward) \end{DoxyCompactList}\item 
size\+\_\+vector\+\_\+type\+::bufreader\+\_\+reverse\+\_\+type $\ast$ \hyperlink{struct_validate4_1_1_l_scan_ad46060df61e67075c4dd51ef65b4fbe1}{m\+\_\+lcp\+\_\+rev\+\_\+reader}
\begin{DoxyCompactList}\small\item\em for scan, point to the L\+C\+P-\/value for currently scanned suffix and its right neighbor in SA (retrieve from L\+CP, leftward) \end{DoxyCompactList}\item 
std\+::vector$<$ typename size\+\_\+vector\+\_\+type\+::bufreader\+\_\+reverse\+\_\+type $\ast$ $>$ \hyperlink{struct_validate4_1_1_l_scan_a49a126aeb7f9b315fc49b0fc5da01cb2}{m\+\_\+sa\+\_\+s\+\_\+bkt\+\_\+rev\+\_\+reader}
\begin{DoxyCompactList}\small\item\em for induce, point to the S\+A-\/value for the S-\/type suffix to be induced in each bucket (retrievd from SA, leftward) \end{DoxyCompactList}\item 
std\+::vector$<$ typename size\+\_\+vector\+\_\+type\+::bufreader\+\_\+reverse\+\_\+type $\ast$ $>$ \hyperlink{struct_validate4_1_1_l_scan_a469303775a2ce2e5199df1cad4ba121b}{m\+\_\+lcp\+\_\+s\+\_\+bkt\+\_\+rev\+\_\+reader}
\begin{DoxyCompactList}\small\item\em for induce, point to the L\+C\+P-\/value for the S-\/type suffix to be induced in each bucket (retrieved from L\+CP, leftward) \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$\newline
struct Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+L\+Scan}

scan SA \& L\+CP rightward to validate the S\+A-\/values of all the S-\/type suffixes and the L\+C\+P-\/values of them and their left neighbor in SA.

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a8e95d99392cee99b081b8354d9a13757}\label{struct_validate4_1_1_l_scan_a8e95d99392cee99b081b8354d9a13757}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!L\+Scan@{L\+Scan}}
\index{L\+Scan@{L\+Scan}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{L\+Scan()}{LScan()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::\+L\+Scan (\begin{DoxyParamCaption}\item[{\hyperlink{struct_validate4_1_1_bkt_info}{Bkt\+Info} \&}]{\+\_\+bkt\+\_\+info,  }\item[{\hyperlink{class_validate4_a49c80b3d101be19542a4341c2387603a}{alphabet\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+t,  }\item[{\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+sa,  }\item[{\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+lcp }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

ctor

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a1ac7b38fcbb0968d0683a0df18fedd9f}\label{struct_validate4_1_1_l_scan_a1ac7b38fcbb0968d0683a0df18fedd9f}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!````~L\+Scan@{$\sim$\+L\+Scan}}
\index{````~L\+Scan@{$\sim$\+L\+Scan}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{$\sim$\+L\+Scan()}{~LScan()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::$\sim$\+L\+Scan (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

dtor

\subsection{Member Function Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a9e88ab70a4b681b145bd79fa05d8f13d}\label{struct_validate4_1_1_l_scan_a9e88ab70a4b681b145bd79fa05d8f13d}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!bruteforce\+\_\+compute\+\_\+lcp@{bruteforce\+\_\+compute\+\_\+lcp}}
\index{bruteforce\+\_\+compute\+\_\+lcp@{bruteforce\+\_\+compute\+\_\+lcp}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{bruteforce\+\_\+compute\+\_\+lcp()}{bruteforce\_compute\_lcp()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::bruteforce\+\_\+compute\+\_\+lcp (\begin{DoxyParamCaption}\item[{const size\+\_\+type \&}]{\+\_\+pos1,  }\item[{const size\+\_\+type \&}]{\+\_\+pos2 }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

literally compare two suffixes pointed to by the starting positions

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a1fabfd83060b51fdedd46b413da0f060}\label{struct_validate4_1_1_l_scan_a1fabfd83060b51fdedd46b413da0f060}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!fetch\+\_\+l\+\_\+scanned@{fetch\+\_\+l\+\_\+scanned}}
\index{fetch\+\_\+l\+\_\+scanned@{fetch\+\_\+l\+\_\+scanned}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{fetch\+\_\+l\+\_\+scanned()}{fetch\_l\_scanned()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
void \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::fetch\+\_\+l\+\_\+scanned (\begin{DoxyParamCaption}\item[{size\+\_\+type \&}]{\+\_\+sa\+\_\+value,  }\item[{size\+\_\+type \&}]{\+\_\+lcp\+\_\+value }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

fetch the S\+A-\/value for currently scanned L-\/type suffix and the L\+C\+P-\/value of the suffix and its right neighbor in SA

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a37796b2c2e404a1bdf1362e7b1794fee}\label{struct_validate4_1_1_l_scan_a37796b2c2e404a1bdf1362e7b1794fee}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!fetch\+\_\+s\+\_\+induced@{fetch\+\_\+s\+\_\+induced}}
\index{fetch\+\_\+s\+\_\+induced@{fetch\+\_\+s\+\_\+induced}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{fetch\+\_\+s\+\_\+induced()}{fetch\_s\_induced()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
void \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::fetch\+\_\+s\+\_\+induced (\begin{DoxyParamCaption}\item[{const alphabet\+\_\+type}]{\+\_\+ch,  }\item[{size\+\_\+type \&}]{\+\_\+sa\+\_\+value,  }\item[{size\+\_\+type \&}]{\+\_\+lcp\+\_\+value }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

fetch the S\+A-\/value for currently induced S-\/type suffix and the L\+C\+P-\/value for the suffix and its right neighbor in SA

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a4e402bf4909c1502337801bd56e22be2}\label{struct_validate4_1_1_l_scan_a4e402bf4909c1502337801bd56e22be2}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!fetch\+\_\+s\+\_\+scanned@{fetch\+\_\+s\+\_\+scanned}}
\index{fetch\+\_\+s\+\_\+scanned@{fetch\+\_\+s\+\_\+scanned}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{fetch\+\_\+s\+\_\+scanned()}{fetch\_s\_scanned()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
void \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::fetch\+\_\+s\+\_\+scanned (\begin{DoxyParamCaption}\item[{size\+\_\+type \&}]{\+\_\+sa\+\_\+value,  }\item[{size\+\_\+type \&}]{\+\_\+lcp\+\_\+value }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

fetch the S\+A-\/value for currently scanned S-\/type suffix and the L\+C\+P-\/value of the suffix and its right neighbor in SA

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_abd7e922317ee9d64d90853adba6a7634}\label{struct_validate4_1_1_l_scan_abd7e922317ee9d64d90853adba6a7634}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!find\+\_\+next\+\_\+l\+\_\+bkt@{find\+\_\+next\+\_\+l\+\_\+bkt}}
\index{find\+\_\+next\+\_\+l\+\_\+bkt@{find\+\_\+next\+\_\+l\+\_\+bkt}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{find\+\_\+next\+\_\+l\+\_\+bkt()}{find\_next\_l\_bkt()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
void \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::find\+\_\+next\+\_\+l\+\_\+bkt (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

find next non-\/empty L-\/bucket

\begin{DoxyNote}{Note}
guarantee there remains L-\/type suffixes to be scanned before calling the function 
\end{DoxyNote}
\mbox{\Hypertarget{struct_validate4_1_1_l_scan_aa570a8ac447950b6b0d9deae2e4cae63}\label{struct_validate4_1_1_l_scan_aa570a8ac447950b6b0d9deae2e4cae63}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!find\+\_\+next\+\_\+s\+\_\+bkt@{find\+\_\+next\+\_\+s\+\_\+bkt}}
\index{find\+\_\+next\+\_\+s\+\_\+bkt@{find\+\_\+next\+\_\+s\+\_\+bkt}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{find\+\_\+next\+\_\+s\+\_\+bkt()}{find\_next\_s\_bkt()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
void \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::find\+\_\+next\+\_\+s\+\_\+bkt (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

find next non-\/empty S-\/bucket

\begin{DoxyNote}{Note}
guarantee there remains S-\/type suffixes to be scanned before calling the function 
\end{DoxyNote}
\mbox{\Hypertarget{struct_validate4_1_1_l_scan_ae986f4106e79412c60be8a88a9637f66}\label{struct_validate4_1_1_l_scan_ae986f4106e79412c60be8a88a9637f66}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!get\+\_\+l\+\_\+bkt\+\_\+ch@{get\+\_\+l\+\_\+bkt\+\_\+ch}}
\index{get\+\_\+l\+\_\+bkt\+\_\+ch@{get\+\_\+l\+\_\+bkt\+\_\+ch}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{get\+\_\+l\+\_\+bkt\+\_\+ch()}{get\_l\_bkt\_ch()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
alphabet\+\_\+type \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::get\+\_\+l\+\_\+bkt\+\_\+ch (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

get ch for the L\+MS bucket currently being scanned

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a1be5f226a5053456897df328302764f3}\label{struct_validate4_1_1_l_scan_a1be5f226a5053456897df328302764f3}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!get\+\_\+s\+\_\+bkt\+\_\+ch@{get\+\_\+s\+\_\+bkt\+\_\+ch}}
\index{get\+\_\+s\+\_\+bkt\+\_\+ch@{get\+\_\+s\+\_\+bkt\+\_\+ch}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{get\+\_\+s\+\_\+bkt\+\_\+ch()}{get\_s\_bkt\_ch()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
alphabet\+\_\+type \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::get\+\_\+s\+\_\+bkt\+\_\+ch (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

get ch for the S-\/type bucket currently being scanned

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_ae76d58363b02ac96925becbbdbe02977}\label{struct_validate4_1_1_l_scan_ae76d58363b02ac96925becbbdbe02977}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!l\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty@{l\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty}}
\index{l\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty@{l\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{l\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty()}{l\_cur\_bkt\_is\_empty()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
bool \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::l\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

check if no more L-\/type suffixes to be scanned in current bucket

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a22b7a0b8c64f17da5a815ddaf8619ebb}\label{struct_validate4_1_1_l_scan_a22b7a0b8c64f17da5a815ddaf8619ebb}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!l\+\_\+is\+\_\+empty@{l\+\_\+is\+\_\+empty}}
\index{l\+\_\+is\+\_\+empty@{l\+\_\+is\+\_\+empty}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{l\+\_\+is\+\_\+empty()}{l\_is\_empty()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
bool \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::l\+\_\+is\+\_\+empty (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

check if no more L-\/type to be scanned

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_ac923c1ac593c291db774594e8f51c9e5}\label{struct_validate4_1_1_l_scan_ac923c1ac593c291db774594e8f51c9e5}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!run@{run}}
\index{run@{run}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{run()}{run()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
bool \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::run (\begin{DoxyParamCaption}\item[{\hyperlink{class_validate4_aa35a0ebf404821377118043d536be262}{triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$}]{\+\_\+pre\+\_\+item\+\_\+of\+\_\+s\+\_\+sorter,  }\item[{\hyperlink{class_validate4_a883822e6f1be0d67f71e1feb9729b1dc}{pair4\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+pre\+\_\+item\+\_\+of\+\_\+l\+\_\+vector }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

induce and check the order of S-\/type suffixes and their L\+C\+P-\/values

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a9331f92d91cf67c38a3d6948a2190df8}\label{struct_validate4_1_1_l_scan_a9331f92d91cf67c38a3d6948a2190df8}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!s\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty@{s\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty}}
\index{s\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty@{s\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{s\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty()}{s\_cur\_bkt\_is\_empty()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
bool \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::s\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

check if no more S-\/type suffixes to be scanned in current bucket

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a071826b788f5aadc92f87ad8cc986649}\label{struct_validate4_1_1_l_scan_a071826b788f5aadc92f87ad8cc986649}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!s\+\_\+is\+\_\+empty@{s\+\_\+is\+\_\+empty}}
\index{s\+\_\+is\+\_\+empty@{s\+\_\+is\+\_\+empty}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{s\+\_\+is\+\_\+empty()}{s\_is\_empty()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
bool \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::s\+\_\+is\+\_\+empty (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

check if no more L\+MS to be scanned

\subsection{Member Data Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a907234b2fa774b42e87050f0066e26b6}\label{struct_validate4_1_1_l_scan_a907234b2fa774b42e87050f0066e26b6}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!ch\+\_\+max@{ch\+\_\+max}}
\index{ch\+\_\+max@{ch\+\_\+max}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{ch\+\_\+max}{ch\_max}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
const alphabet\+\_\+type \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::ch\+\_\+max\hspace{0.3cm}{\ttfamily [private]}}

maximum character

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_abf7d8f90883c943c08a007425c43c644}\label{struct_validate4_1_1_l_scan_abf7d8f90883c943c08a007425c43c644}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+cur\+\_\+l\+\_\+ch@{m\+\_\+cur\+\_\+l\+\_\+ch}}
\index{m\+\_\+cur\+\_\+l\+\_\+ch@{m\+\_\+cur\+\_\+l\+\_\+ch}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+cur\+\_\+l\+\_\+ch}{m\_cur\_l\_ch}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
alphabet\+\_\+type \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+cur\+\_\+l\+\_\+ch\hspace{0.3cm}{\ttfamily [private]}}

L-\/type bucket currently being scanned.

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_ac765bc6e6817fbe71a7aacbd4e2811d9}\label{struct_validate4_1_1_l_scan_ac765bc6e6817fbe71a7aacbd4e2811d9}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+cur\+\_\+s\+\_\+ch@{m\+\_\+cur\+\_\+s\+\_\+ch}}
\index{m\+\_\+cur\+\_\+s\+\_\+ch@{m\+\_\+cur\+\_\+s\+\_\+ch}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+cur\+\_\+s\+\_\+ch}{m\_cur\_s\_ch}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
alphabet\+\_\+type \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+cur\+\_\+s\+\_\+ch\hspace{0.3cm}{\ttfamily [private]}}

S-\/type bucket currently being scanned.

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a41c937ae175b97c22325458bcafeeb7e}\label{struct_validate4_1_1_l_scan_a41c937ae175b97c22325458bcafeeb7e}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+l\+\_\+bkt\+\_\+scanned@{m\+\_\+l\+\_\+bkt\+\_\+scanned}}
\index{m\+\_\+l\+\_\+bkt\+\_\+scanned@{m\+\_\+l\+\_\+bkt\+\_\+scanned}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+l\+\_\+bkt\+\_\+scanned}{m\_l\_bkt\_scanned}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+l\+\_\+bkt\+\_\+scanned\hspace{0.3cm}{\ttfamily [private]}}

numer of L-\/type suffixes scanned in each bucket

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a82878f6289ad8c9ec7204de1e5a2e04c}\label{struct_validate4_1_1_l_scan_a82878f6289ad8c9ec7204de1e5a2e04c}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+l\+\_\+bkt\+\_\+spos@{m\+\_\+l\+\_\+bkt\+\_\+spos}}
\index{m\+\_\+l\+\_\+bkt\+\_\+spos@{m\+\_\+l\+\_\+bkt\+\_\+spos}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+l\+\_\+bkt\+\_\+spos}{m\_l\_bkt\_spos}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+l\+\_\+bkt\+\_\+spos\hspace{0.3cm}{\ttfamily [private]}}

indicate the starting position of each S-\/type bucket in SA (right boundary)

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_ad500f8ccaffab088a465a288f92fd4b2}\label{struct_validate4_1_1_l_scan_ad500f8ccaffab088a465a288f92fd4b2}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+l\+\_\+bkt\+\_\+toscan@{m\+\_\+l\+\_\+bkt\+\_\+toscan}}
\index{m\+\_\+l\+\_\+bkt\+\_\+toscan@{m\+\_\+l\+\_\+bkt\+\_\+toscan}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+l\+\_\+bkt\+\_\+toscan}{m\_l\_bkt\_toscan}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+l\+\_\+bkt\+\_\+toscan\hspace{0.3cm}{\ttfamily [private]}}

number of L-\/type suffixes to be scanned in each bucket

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_af9ba74080cb7b3e0f685d29a4c78ab73}\label{struct_validate4_1_1_l_scan_af9ba74080cb7b3e0f685d29a4c78ab73}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+lcp@{m\+\_\+lcp}}
\index{m\+\_\+lcp@{m\+\_\+lcp}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+lcp}{m\_lcp}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+lcp\hspace{0.3cm}{\ttfamily [private]}}

pointer to the L\+CP array

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_ad46060df61e67075c4dd51ef65b4fbe1}\label{struct_validate4_1_1_l_scan_ad46060df61e67075c4dd51ef65b4fbe1}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+lcp\+\_\+rev\+\_\+reader@{m\+\_\+lcp\+\_\+rev\+\_\+reader}}
\index{m\+\_\+lcp\+\_\+rev\+\_\+reader@{m\+\_\+lcp\+\_\+rev\+\_\+reader}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+lcp\+\_\+rev\+\_\+reader}{m\_lcp\_rev\_reader}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
size\+\_\+vector\+\_\+type\+::bufreader\+\_\+reverse\+\_\+type$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+lcp\+\_\+rev\+\_\+reader\hspace{0.3cm}{\ttfamily [private]}}

for scan, point to the L\+C\+P-\/value for currently scanned suffix and its right neighbor in SA (retrieve from L\+CP, leftward)

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a469303775a2ce2e5199df1cad4ba121b}\label{struct_validate4_1_1_l_scan_a469303775a2ce2e5199df1cad4ba121b}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+lcp\+\_\+s\+\_\+bkt\+\_\+rev\+\_\+reader@{m\+\_\+lcp\+\_\+s\+\_\+bkt\+\_\+rev\+\_\+reader}}
\index{m\+\_\+lcp\+\_\+s\+\_\+bkt\+\_\+rev\+\_\+reader@{m\+\_\+lcp\+\_\+s\+\_\+bkt\+\_\+rev\+\_\+reader}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+lcp\+\_\+s\+\_\+bkt\+\_\+rev\+\_\+reader}{m\_lcp\_s\_bkt\_rev\_reader}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$typename size\+\_\+vector\+\_\+type\+::bufreader\+\_\+reverse\+\_\+type$\ast$$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+lcp\+\_\+s\+\_\+bkt\+\_\+rev\+\_\+reader\hspace{0.3cm}{\ttfamily [private]}}

for induce, point to the L\+C\+P-\/value for the S-\/type suffix to be induced in each bucket (retrieved from L\+CP, leftward)

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a66ce5f59bcd37d47371f847769297b46}\label{struct_validate4_1_1_l_scan_a66ce5f59bcd37d47371f847769297b46}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+s\+\_\+bkt\+\_\+scanned@{m\+\_\+s\+\_\+bkt\+\_\+scanned}}
\index{m\+\_\+s\+\_\+bkt\+\_\+scanned@{m\+\_\+s\+\_\+bkt\+\_\+scanned}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+s\+\_\+bkt\+\_\+scanned}{m\_s\_bkt\_scanned}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+s\+\_\+bkt\+\_\+scanned\hspace{0.3cm}{\ttfamily [private]}}

number of S-\/type suffixes scanned in each bucket

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a3a342dcdec25a509df8f943c1e91b3b8}\label{struct_validate4_1_1_l_scan_a3a342dcdec25a509df8f943c1e91b3b8}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+s\+\_\+bkt\+\_\+spos@{m\+\_\+s\+\_\+bkt\+\_\+spos}}
\index{m\+\_\+s\+\_\+bkt\+\_\+spos@{m\+\_\+s\+\_\+bkt\+\_\+spos}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+s\+\_\+bkt\+\_\+spos}{m\_s\_bkt\_spos}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+s\+\_\+bkt\+\_\+spos\hspace{0.3cm}{\ttfamily [private]}}

indicate the starting position of each L-\/type bucket in SA (right boundary)

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_ad072911a65100e41a34b17ee6dc79cd4}\label{struct_validate4_1_1_l_scan_ad072911a65100e41a34b17ee6dc79cd4}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+s\+\_\+bkt\+\_\+toscan@{m\+\_\+s\+\_\+bkt\+\_\+toscan}}
\index{m\+\_\+s\+\_\+bkt\+\_\+toscan@{m\+\_\+s\+\_\+bkt\+\_\+toscan}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+s\+\_\+bkt\+\_\+toscan}{m\_s\_bkt\_toscan}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+s\+\_\+bkt\+\_\+toscan\hspace{0.3cm}{\ttfamily [private]}}

number of S-\/type suffixes to be scanned in each bucket

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a38f7644fb0e19bc24c83cbcc04f1b01f}\label{struct_validate4_1_1_l_scan_a38f7644fb0e19bc24c83cbcc04f1b01f}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+sa@{m\+\_\+sa}}
\index{m\+\_\+sa@{m\+\_\+sa}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+sa}{m\_sa}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+sa\hspace{0.3cm}{\ttfamily [private]}}

pointer to the suffix array

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_aa424a1fcc802dbe8556953c1e8d07207}\label{struct_validate4_1_1_l_scan_aa424a1fcc802dbe8556953c1e8d07207}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+sa\+\_\+rev\+\_\+reader@{m\+\_\+sa\+\_\+rev\+\_\+reader}}
\index{m\+\_\+sa\+\_\+rev\+\_\+reader@{m\+\_\+sa\+\_\+rev\+\_\+reader}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+sa\+\_\+rev\+\_\+reader}{m\_sa\_rev\_reader}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
size\+\_\+vector\+\_\+type\+::bufreader\+\_\+reverse\+\_\+type$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+sa\+\_\+rev\+\_\+reader\hspace{0.3cm}{\ttfamily [private]}}

for scan, point to the S\+A-\/value for currently scanned suffix (retrieve from SA, leftward)

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a49a126aeb7f9b315fc49b0fc5da01cb2}\label{struct_validate4_1_1_l_scan_a49a126aeb7f9b315fc49b0fc5da01cb2}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+sa\+\_\+s\+\_\+bkt\+\_\+rev\+\_\+reader@{m\+\_\+sa\+\_\+s\+\_\+bkt\+\_\+rev\+\_\+reader}}
\index{m\+\_\+sa\+\_\+s\+\_\+bkt\+\_\+rev\+\_\+reader@{m\+\_\+sa\+\_\+s\+\_\+bkt\+\_\+rev\+\_\+reader}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+sa\+\_\+s\+\_\+bkt\+\_\+rev\+\_\+reader}{m\_sa\_s\_bkt\_rev\_reader}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$typename size\+\_\+vector\+\_\+type\+::bufreader\+\_\+reverse\+\_\+type$\ast$$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+sa\+\_\+s\+\_\+bkt\+\_\+rev\+\_\+reader\hspace{0.3cm}{\ttfamily [private]}}

for induce, point to the S\+A-\/value for the S-\/type suffix to be induced in each bucket (retrievd from SA, leftward)

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a3f7a5fe6e603159503a161185eb38667}\label{struct_validate4_1_1_l_scan_a3f7a5fe6e603159503a161185eb38667}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+t@{m\+\_\+t}}
\index{m\+\_\+t@{m\+\_\+t}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+t}{m\_t}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_a49c80b3d101be19542a4341c2387603a}{alphabet\+\_\+vector\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+t\hspace{0.3cm}{\ttfamily [private]}}

pointer to the input string

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_aa9addcdfacecc8d69159683c9f694bef}\label{struct_validate4_1_1_l_scan_aa9addcdfacecc8d69159683c9f694bef}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+total\+\_\+l\+\_\+scanned@{m\+\_\+total\+\_\+l\+\_\+scanned}}
\index{m\+\_\+total\+\_\+l\+\_\+scanned@{m\+\_\+total\+\_\+l\+\_\+scanned}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+total\+\_\+l\+\_\+scanned}{m\_total\_l\_scanned}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+total\+\_\+l\+\_\+scanned\hspace{0.3cm}{\ttfamily [private]}}

total number of L-\/type suffixes already scanned

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a400a5151679cb9c9da110cf565e81652}\label{struct_validate4_1_1_l_scan_a400a5151679cb9c9da110cf565e81652}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+total\+\_\+l\+\_\+toscan@{m\+\_\+total\+\_\+l\+\_\+toscan}}
\index{m\+\_\+total\+\_\+l\+\_\+toscan@{m\+\_\+total\+\_\+l\+\_\+toscan}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+total\+\_\+l\+\_\+toscan}{m\_total\_l\_toscan}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+total\+\_\+l\+\_\+toscan\hspace{0.3cm}{\ttfamily [private]}}

total number of L-\/type suffixes to be scanned

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_a7b3fae11ba397c30d0f25f055e02cdf1}\label{struct_validate4_1_1_l_scan_a7b3fae11ba397c30d0f25f055e02cdf1}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+total\+\_\+s\+\_\+scanned@{m\+\_\+total\+\_\+s\+\_\+scanned}}
\index{m\+\_\+total\+\_\+s\+\_\+scanned@{m\+\_\+total\+\_\+s\+\_\+scanned}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+total\+\_\+s\+\_\+scanned}{m\_total\_s\_scanned}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+total\+\_\+s\+\_\+scanned\hspace{0.3cm}{\ttfamily [private]}}

total number of S-\/type suffixes already scanned

\mbox{\Hypertarget{struct_validate4_1_1_l_scan_abaf348442b39a1a0447a382e1f66f13b}\label{struct_validate4_1_1_l_scan_abaf348442b39a1a0447a382e1f66f13b}} 
\index{Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}!m\+\_\+total\+\_\+s\+\_\+toscan@{m\+\_\+total\+\_\+s\+\_\+toscan}}
\index{m\+\_\+total\+\_\+s\+\_\+toscan@{m\+\_\+total\+\_\+s\+\_\+toscan}!Validate4\+::\+L\+Scan@{Validate4\+::\+L\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+total\+\_\+s\+\_\+toscan}{m\_total\_s\_toscan}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::L\+Scan\+::m\+\_\+total\+\_\+s\+\_\+toscan\hspace{0.3cm}{\ttfamily [private]}}

total number of S-\/type suffixes to be scanned

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/\hyperlink{validate4_8h}{validate4.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/struct_validate4_1_1_r_m_q.tex
2017/01/24

\hypertarget{struct_validate4_1_1_r_m_q}{}\section{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+:\+:R\+MQ Struct Reference}
\label{struct_validate4_1_1_r_m_q}\index{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+R\+MQ@{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+R\+MQ}}

\hyperlink{struct_validate4_1_1_r_m_q}{R\+MQ}.

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{struct_validate4_1_1_r_m_q_a58a58fb442194bba96116dd76b361882}{R\+MQ} ()
\begin{DoxyCompactList}\small\item\em ctor \end{DoxyCompactList}\item 
size\+\_\+type \hyperlink{struct_validate4_1_1_r_m_q_a25c9ec1cab24c2ea2355b8ce828cf108}{get} (const alphabet\+\_\+type \+\_\+ch)
\begin{DoxyCompactList}\small\item\em getter \end{DoxyCompactList}\item 
void \hyperlink{struct_validate4_1_1_r_m_q_a51f01cfbe100d40fc976fd2e1e8b6d16}{update} (size\+\_\+type \+\_\+val)
\begin{DoxyCompactList}\small\item\em update \end{DoxyCompactList}\item 
void \hyperlink{struct_validate4_1_1_r_m_q_a8416e95d49b4b8c05cd814d78017d81f}{reset} (const alphabet\+\_\+type \+\_\+ch)
\begin{DoxyCompactList}\small\item\em reset the range minimum value to val\+\_\+max \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Private Attributes}
\begin{DoxyCompactItemize}
\item 
const alphabet\+\_\+type \hyperlink{struct_validate4_1_1_r_m_q_a0addfc5d1067fca9a97939554cb0cd70}{ch\+\_\+max}
\item 
const size\+\_\+type \hyperlink{struct_validate4_1_1_r_m_q_a45aa4f738281304a3f6bd5b9d78ef712}{val\+\_\+max}
\item 
std\+::vector$<$ size\+\_\+type $>$ \hyperlink{struct_validate4_1_1_r_m_q_abf525030d892825a6ef20c45eafaae2b}{m\+\_\+rmq}
\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$\newline
struct Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+R\+MQ}

\hyperlink{struct_validate4_1_1_r_m_q}{R\+MQ}.

Given SA\mbox{[}k\mbox{]} and SA\mbox{[}k + 1\mbox{]} respectively induced from SA\mbox{[}i\mbox{]} and SA\mbox{[}j\mbox{]}, the L\+C\+P-\/value of suf(\+S\+A\mbox{[}k\mbox{]}) and suf(SA\mbox{[}k + 1\mbox{]}) is determined by L\+CP\mbox{[}i + 1, j\mbox{]}. The response to the range-\/minimum query for L\+CP\mbox{[}i + 1, j\mbox{]} returns the minimum value among L\+CP\mbox{[}i + 1\mbox{]}, .., L\+CP\mbox{[}j -\/ 1\mbox{]}, L\+CP\mbox{[}j\mbox{]}.

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_r_m_q_a58a58fb442194bba96116dd76b361882}\label{struct_validate4_1_1_r_m_q_a58a58fb442194bba96116dd76b361882}} 
\index{Validate4\+::\+R\+MQ@{Validate4\+::\+R\+MQ}!R\+MQ@{R\+MQ}}
\index{R\+MQ@{R\+MQ}!Validate4\+::\+R\+MQ@{Validate4\+::\+R\+MQ}}
\subsubsection{\texorpdfstring{R\+M\+Q()}{RMQ()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+M\+Q\+::\+R\+MQ (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

ctor

\subsection{Member Function Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_r_m_q_a25c9ec1cab24c2ea2355b8ce828cf108}\label{struct_validate4_1_1_r_m_q_a25c9ec1cab24c2ea2355b8ce828cf108}} 
\index{Validate4\+::\+R\+MQ@{Validate4\+::\+R\+MQ}!get@{get}}
\index{get@{get}!Validate4\+::\+R\+MQ@{Validate4\+::\+R\+MQ}}
\subsubsection{\texorpdfstring{get()}{get()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
size\+\_\+type \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+M\+Q\+::get (\begin{DoxyParamCaption}\item[{const alphabet\+\_\+type}]{\+\_\+ch }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

getter

\mbox{\Hypertarget{struct_validate4_1_1_r_m_q_a8416e95d49b4b8c05cd814d78017d81f}\label{struct_validate4_1_1_r_m_q_a8416e95d49b4b8c05cd814d78017d81f}} 
\index{Validate4\+::\+R\+MQ@{Validate4\+::\+R\+MQ}!reset@{reset}}
\index{reset@{reset}!Validate4\+::\+R\+MQ@{Validate4\+::\+R\+MQ}}
\subsubsection{\texorpdfstring{reset()}{reset()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
void \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+M\+Q\+::reset (\begin{DoxyParamCaption}\item[{const alphabet\+\_\+type}]{\+\_\+ch }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

reset the range minimum value to val\+\_\+max

\mbox{\Hypertarget{struct_validate4_1_1_r_m_q_a51f01cfbe100d40fc976fd2e1e8b6d16}\label{struct_validate4_1_1_r_m_q_a51f01cfbe100d40fc976fd2e1e8b6d16}} 
\index{Validate4\+::\+R\+MQ@{Validate4\+::\+R\+MQ}!update@{update}}
\index{update@{update}!Validate4\+::\+R\+MQ@{Validate4\+::\+R\+MQ}}
\subsubsection{\texorpdfstring{update()}{update()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
void \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+M\+Q\+::update (\begin{DoxyParamCaption}\item[{size\+\_\+type}]{\+\_\+val }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

update

scan all the elements in m\+\_\+rmq, update m\+\_\+rmq\mbox{[}ch\mbox{]} as \+\_\+val if m\+\_\+rmq\mbox{[}ch\mbox{]} $>$ \+\_\+val.

\subsection{Member Data Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_r_m_q_a0addfc5d1067fca9a97939554cb0cd70}\label{struct_validate4_1_1_r_m_q_a0addfc5d1067fca9a97939554cb0cd70}} 
\index{Validate4\+::\+R\+MQ@{Validate4\+::\+R\+MQ}!ch\+\_\+max@{ch\+\_\+max}}
\index{ch\+\_\+max@{ch\+\_\+max}!Validate4\+::\+R\+MQ@{Validate4\+::\+R\+MQ}}
\subsubsection{\texorpdfstring{ch\+\_\+max}{ch\_max}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
const alphabet\+\_\+type \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+M\+Q\+::ch\+\_\+max\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{struct_validate4_1_1_r_m_q_abf525030d892825a6ef20c45eafaae2b}\label{struct_validate4_1_1_r_m_q_abf525030d892825a6ef20c45eafaae2b}} 
\index{Validate4\+::\+R\+MQ@{Validate4\+::\+R\+MQ}!m\+\_\+rmq@{m\+\_\+rmq}}
\index{m\+\_\+rmq@{m\+\_\+rmq}!Validate4\+::\+R\+MQ@{Validate4\+::\+R\+MQ}}
\subsubsection{\texorpdfstring{m\+\_\+rmq}{m\_rmq}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$size\+\_\+type$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+M\+Q\+::m\+\_\+rmq\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{struct_validate4_1_1_r_m_q_a45aa4f738281304a3f6bd5b9d78ef712}\label{struct_validate4_1_1_r_m_q_a45aa4f738281304a3f6bd5b9d78ef712}} 
\index{Validate4\+::\+R\+MQ@{Validate4\+::\+R\+MQ}!val\+\_\+max@{val\+\_\+max}}
\index{val\+\_\+max@{val\+\_\+max}!Validate4\+::\+R\+MQ@{Validate4\+::\+R\+MQ}}
\subsubsection{\texorpdfstring{val\+\_\+max}{val\_max}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
const size\+\_\+type \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+M\+Q\+::val\+\_\+max\hspace{0.3cm}{\ttfamily [private]}}

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/\hyperlink{validate4_8h}{validate4.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/struct_validate4_1_1_r_scan.tex
2017/01/24

\hypertarget{struct_validate4_1_1_r_scan}{}\section{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+:\+:R\+Scan Struct Reference}
\label{struct_validate4_1_1_r_scan}\index{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+R\+Scan@{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+R\+Scan}}

scan SA rightward to validate the S\+A-\/values of all the L-\/type suffixes and the L\+C\+P-\/values of them and their left neighbors in SA.

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{struct_validate4_1_1_r_scan_a278507de57d05bc31a364a632f3a38ab}{R\+Scan} (\hyperlink{struct_validate4_1_1_bkt_info}{Bkt\+Info} \&\+\_\+bkt\+\_\+info, \hyperlink{class_validate4_a49c80b3d101be19542a4341c2387603a}{alphabet\+\_\+vector\+\_\+type} $\ast$\+\_\+t, \hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$\+\_\+sa, \hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$\+\_\+lcp, \hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$\+\_\+sa\+\_\+lms, \hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$\+\_\+lcp\+\_\+lms)
\begin{DoxyCompactList}\small\item\em ctor \end{DoxyCompactList}\item 
bool \hyperlink{struct_validate4_1_1_r_scan_aee1dcbd2edf03def6f3b3954d5cf0871}{l\+\_\+is\+\_\+empty} ()
\begin{DoxyCompactList}\small\item\em check if no more L-\/type to be scanned \end{DoxyCompactList}\item 
bool \hyperlink{struct_validate4_1_1_r_scan_ad24066012dd9441ffab435ce3f02424e}{lms\+\_\+is\+\_\+empty} ()
\begin{DoxyCompactList}\small\item\em chec if no more L\+MS to be scanned \end{DoxyCompactList}\item 
bool \hyperlink{struct_validate4_1_1_r_scan_adf0c72967eddde6a6924472a16e92e95}{l\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty} ()
\begin{DoxyCompactList}\small\item\em check if no more L-\/type suffixes to be scanned in current bucket \end{DoxyCompactList}\item 
bool \hyperlink{struct_validate4_1_1_r_scan_a67647b0b0ef9df76bdcfa85547296a33}{lms\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty} ()
\begin{DoxyCompactList}\small\item\em check if no more L\+MS suffixes to be scanned in current bucket \end{DoxyCompactList}\item 
void \hyperlink{struct_validate4_1_1_r_scan_a32f26034048e070455cd9b1f56c95b89}{find\+\_\+next\+\_\+l\+\_\+bkt} ()
\begin{DoxyCompactList}\small\item\em find next non-\/empty L-\/bucket \end{DoxyCompactList}\item 
void \hyperlink{struct_validate4_1_1_r_scan_af8a20c45983e2d175f6bbc67dcbef719}{find\+\_\+next\+\_\+lms\+\_\+bkt} ()
\begin{DoxyCompactList}\small\item\em find next non-\/empty L\+MS bucket \end{DoxyCompactList}\item 
void \hyperlink{struct_validate4_1_1_r_scan_af88a27e36780a6b390bc0bd18c253429}{fetch\+\_\+l\+\_\+scanned} (size\+\_\+type \&\+\_\+sa\+\_\+value, size\+\_\+type \&\+\_\+lcp\+\_\+value)
\begin{DoxyCompactList}\small\item\em fetch the S\+A-\/value of currently scanned L-\/type suffix and the L\+C\+P-\/value of the suffix and its left neighbor in SA \end{DoxyCompactList}\item 
void \hyperlink{struct_validate4_1_1_r_scan_aaeb8ae64faa2ab76d7467586f3281d97}{fetch\+\_\+lms\+\_\+scanned} (size\+\_\+type \&\+\_\+sa\+\_\+value, size\+\_\+type \&\+\_\+lcp\+\_\+value)
\begin{DoxyCompactList}\small\item\em fetch the S\+A-\/value of currently scanned L\+MS suffix and the L\+C\+P-\/value of the suffix and its left neighbor in S\+A\+\_\+\+L\+MS \end{DoxyCompactList}\item 
void \hyperlink{struct_validate4_1_1_r_scan_aaa6c6e347bff1c6cb663771646c41826}{fetch\+\_\+l\+\_\+induced} (const alphabet\+\_\+type \+\_\+ch, size\+\_\+type \&\+\_\+sa\+\_\+value, size\+\_\+type \&\+\_\+lcp\+\_\+value)
\begin{DoxyCompactList}\small\item\em fetch the S\+A-\/value for currently induced L-\/type suffix and the L\+C\+P-\/value for the suffix and its left neighbor in SA \end{DoxyCompactList}\item 
alphabet\+\_\+type \hyperlink{struct_validate4_1_1_r_scan_a8d691af43c806d0e3279c0121abf6ed7}{get\+\_\+l\+\_\+bkt\+\_\+ch} ()
\begin{DoxyCompactList}\small\item\em return the initial character of suffixes in current scanned bucket \end{DoxyCompactList}\item 
alphabet\+\_\+type \hyperlink{struct_validate4_1_1_r_scan_ac53c6318e14f774d956baea8134b5937}{get\+\_\+lms\+\_\+bkt\+\_\+ch} ()
\begin{DoxyCompactList}\small\item\em return the initial character of suffixes in current scanned bucket \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate4_1_1_r_scan_adc3cb04c1da68e1ac8a544c1eaf7c00c}{bruteforce\+\_\+compute\+\_\+lcp} (const size\+\_\+type \&\+\_\+pos1, const size\+\_\+type \&\+\_\+pos2)
\begin{DoxyCompactList}\small\item\em literally compare two suffixes pointed to by the starting positions \end{DoxyCompactList}\item 
\hyperlink{struct_validate4_1_1_r_scan_a853d1a1bbc53a8b1cacf231c0f64bf8a}{$\sim$\+R\+Scan} ()
\begin{DoxyCompactList}\small\item\em de-\/ctor \end{DoxyCompactList}\item 
bool \hyperlink{struct_validate4_1_1_r_scan_a963da6ae9411fca7fb05701dd678161f}{run} (\hyperlink{class_validate4_a4c1bcea817e34f96d95c99e0694bbfc8}{triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$\+\_\+pre\+\_\+item\+\_\+of\+\_\+l\+\_\+sorter, \hyperlink{class_validate4_aff3135d55f749682df7e0f97c82a6769}{pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$\+\_\+pre\+\_\+item\+\_\+of\+\_\+lms\+\_\+sorter)
\begin{DoxyCompactList}\small\item\em induce and check the order of L-\/type suffixes and their L\+CP values \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Private Attributes}
\begin{DoxyCompactItemize}
\item 
const alphabet\+\_\+type \hyperlink{struct_validate4_1_1_r_scan_a3ff6f0be3fd0b25c66913d4d08b2e143}{ch\+\_\+max}
\begin{DoxyCompactList}\small\item\em maximum character \end{DoxyCompactList}\item 
\hyperlink{class_validate4_a49c80b3d101be19542a4341c2387603a}{alphabet\+\_\+vector\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_r_scan_a9d9ce16aa2eacc32f54cc88e8746a73a}{m\+\_\+t}
\begin{DoxyCompactList}\small\item\em pointer to input string \end{DoxyCompactList}\item 
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_r_scan_ab656e7db03298be8ce72f202e5aa5e77}{m\+\_\+sa}
\begin{DoxyCompactList}\small\item\em pointer to suffix array \end{DoxyCompactList}\item 
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_r_scan_a5521d8d0a72b169e07da61abd5463634}{m\+\_\+lcp}
\begin{DoxyCompactList}\small\item\em pointer to L\+CP array \end{DoxyCompactList}\item 
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_r_scan_a7427660483d5beb9bbf8e6a69c291c25}{m\+\_\+sa\+\_\+lms}
\begin{DoxyCompactList}\small\item\em pointer to S\+A\+\_\+\+L\+MS \end{DoxyCompactList}\item 
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$ \hyperlink{struct_validate4_1_1_r_scan_adf3e4856d77cd795d6b00b2355bd48bd}{m\+\_\+lcp\+\_\+lms}
\begin{DoxyCompactList}\small\item\em pointer to L\+C\+P\+\_\+\+L\+MS \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate4_1_1_r_scan_a4ba4d8371cdcc14a4a34b012ee27a7f8}{m\+\_\+len}
\begin{DoxyCompactList}\small\item\em number of elements in T/\+S\+A/\+L\+CP \end{DoxyCompactList}\item 
std\+::vector$<$ \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $>$ \hyperlink{struct_validate4_1_1_r_scan_a47335f1e738063b9ddc5ee00be052cfd}{m\+\_\+l\+\_\+bkt\+\_\+toscan}
\begin{DoxyCompactList}\small\item\em number of L-\/type suffixes to be scanned in each bucket \end{DoxyCompactList}\item 
std\+::vector$<$ \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $>$ \hyperlink{struct_validate4_1_1_r_scan_ace00679285e1e6082440d2485809f0cf}{m\+\_\+l\+\_\+bkt\+\_\+scanned}
\begin{DoxyCompactList}\small\item\em number of L-\/type suffixes scanned in each bucket \end{DoxyCompactList}\item 
std\+::vector$<$ \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $>$ \hyperlink{struct_validate4_1_1_r_scan_a9681af9f2bc82ec9202da5c967f36491}{m\+\_\+lms\+\_\+bkt\+\_\+toscan}
\begin{DoxyCompactList}\small\item\em number of L\+MS suffixes to be scanned in each bucket \end{DoxyCompactList}\item 
std\+::vector$<$ \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $>$ \hyperlink{struct_validate4_1_1_r_scan_ab56ecfb052c910af7ed356d5ad11be0b}{m\+\_\+lms\+\_\+bkt\+\_\+scanned}
\begin{DoxyCompactList}\small\item\em number of L\+MS suffixes scanned in each bucket \end{DoxyCompactList}\item 
std\+::vector$<$ \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} $>$ \hyperlink{struct_validate4_1_1_r_scan_ab9a643ec01afe4e6d3455ff025aeb612}{m\+\_\+l\+\_\+bkt\+\_\+spos}
\begin{DoxyCompactList}\small\item\em starting position of each L-\/type bucket in SA \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate4_1_1_r_scan_a4cc3c1365b0089fe9d7740fed39dd0a7}{m\+\_\+total\+\_\+l\+\_\+toscan}
\begin{DoxyCompactList}\small\item\em total number of L-\/type suffixes to be scanned \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate4_1_1_r_scan_ae0c9b8ab74cca6cebf6375cd772f1858}{m\+\_\+total\+\_\+l\+\_\+scanned}
\begin{DoxyCompactList}\small\item\em total number of L-\/type suffixes already scanned \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate4_1_1_r_scan_ae61305117585d96877b30800ea2479e4}{m\+\_\+total\+\_\+lms\+\_\+toscan}
\begin{DoxyCompactList}\small\item\em total number of L\+MS suffixes to be scanned \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate4_1_1_r_scan_a6451f758af2853be9d7aafc978001493}{m\+\_\+total\+\_\+lms\+\_\+scanned}
\begin{DoxyCompactList}\small\item\em total number of L\+MS suffixes already scanned \end{DoxyCompactList}\item 
alphabet\+\_\+type \hyperlink{struct_validate4_1_1_r_scan_a6ca7516c4fd64e5fe926636ac7197fda}{m\+\_\+cur\+\_\+l\+\_\+ch}
\begin{DoxyCompactList}\small\item\em L-\/type bucket currently being scanned. \end{DoxyCompactList}\item 
alphabet\+\_\+type \hyperlink{struct_validate4_1_1_r_scan_a8efbe937773c79d74f444e7f2c71fc8e}{m\+\_\+cur\+\_\+lms\+\_\+ch}
\begin{DoxyCompactList}\small\item\em L\+MS bucket currently being scanned. \end{DoxyCompactList}\item 
size\+\_\+vector\+\_\+type\+::bufreader\+\_\+type $\ast$ \hyperlink{struct_validate4_1_1_r_scan_a02e30a17efa641c20f6b979a21be9082}{m\+\_\+sa\+\_\+l\+\_\+reader}
\begin{DoxyCompactList}\small\item\em for scan, point to the S\+A-\/value for currently scanned L-\/type suffix (retrieve from SA) \end{DoxyCompactList}\item 
size\+\_\+vector\+\_\+type\+::bufreader\+\_\+type $\ast$ \hyperlink{struct_validate4_1_1_r_scan_a9aa4704ec4b22e0ecbec8c1c9687521d}{m\+\_\+lcp\+\_\+l\+\_\+reader}
\begin{DoxyCompactList}\small\item\em for scan, point to the L\+C\+P-\/value for currently scanned L-\/type suffix and its left neighbor in SA (retrieve from L\+CP) \end{DoxyCompactList}\item 
size\+\_\+vector\+\_\+type\+::bufreader\+\_\+type $\ast$ \hyperlink{struct_validate4_1_1_r_scan_a986bdf3f5bc40e0d41939f699ac68c2c}{m\+\_\+sa\+\_\+lms\+\_\+reader}
\begin{DoxyCompactList}\small\item\em for scan, point to the S\+A-\/value for currently scanned L\+MS suffix (retrieve from S\+A\+\_\+\+L\+MS) \end{DoxyCompactList}\item 
size\+\_\+vector\+\_\+type\+::bufreader\+\_\+type $\ast$ \hyperlink{struct_validate4_1_1_r_scan_aa712f18affa902ade5907584476a5003}{m\+\_\+lcp\+\_\+lms\+\_\+reader}
\begin{DoxyCompactList}\small\item\em for scan, point to the L\+C\+P-\/value for currently scanned L\+MS suffixes and the rightmost L\+MS one on its leftside (retrieve from L\+C\+P\+\_\+\+L\+MS) \end{DoxyCompactList}\item 
std\+::vector$<$ typename size\+\_\+vector\+\_\+type\+::bufreader\+\_\+type $\ast$ $>$ \hyperlink{struct_validate4_1_1_r_scan_adbffde97174383da7a58437bf76ab0fe}{m\+\_\+sa\+\_\+l\+\_\+bkt\+\_\+reader}
\item 
std\+::vector$<$ typename size\+\_\+vector\+\_\+type\+::bufreader\+\_\+type $\ast$ $>$ \hyperlink{struct_validate4_1_1_r_scan_a83351c07dee43e836114a49df9a0ec0a}{m\+\_\+lcp\+\_\+l\+\_\+bkt\+\_\+reader}
\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$\newline
struct Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+R\+Scan}

scan SA rightward to validate the S\+A-\/values of all the L-\/type suffixes and the L\+C\+P-\/values of them and their left neighbors in SA.

When scanning rightward, compute the L\+C\+P-\/value of currently scanned suffix and the last scanned one and validate the L\+C\+P-\/value of currently induced suffix and its left neighbor in SA.

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a278507de57d05bc31a364a632f3a38ab}\label{struct_validate4_1_1_r_scan_a278507de57d05bc31a364a632f3a38ab}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!R\+Scan@{R\+Scan}}
\index{R\+Scan@{R\+Scan}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{R\+Scan()}{RScan()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::\+R\+Scan (\begin{DoxyParamCaption}\item[{\hyperlink{struct_validate4_1_1_bkt_info}{Bkt\+Info} \&}]{\+\_\+bkt\+\_\+info,  }\item[{\hyperlink{class_validate4_a49c80b3d101be19542a4341c2387603a}{alphabet\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+t,  }\item[{\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+sa,  }\item[{\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+lcp,  }\item[{\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+sa\+\_\+lms,  }\item[{\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+lcp\+\_\+lms }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

ctor

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a853d1a1bbc53a8b1cacf231c0f64bf8a}\label{struct_validate4_1_1_r_scan_a853d1a1bbc53a8b1cacf231c0f64bf8a}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!````~R\+Scan@{$\sim$\+R\+Scan}}
\index{````~R\+Scan@{$\sim$\+R\+Scan}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{$\sim$\+R\+Scan()}{~RScan()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::$\sim$\+R\+Scan (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

de-\/ctor

\subsection{Member Function Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_r_scan_adc3cb04c1da68e1ac8a544c1eaf7c00c}\label{struct_validate4_1_1_r_scan_adc3cb04c1da68e1ac8a544c1eaf7c00c}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!bruteforce\+\_\+compute\+\_\+lcp@{bruteforce\+\_\+compute\+\_\+lcp}}
\index{bruteforce\+\_\+compute\+\_\+lcp@{bruteforce\+\_\+compute\+\_\+lcp}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{bruteforce\+\_\+compute\+\_\+lcp()}{bruteforce\_compute\_lcp()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::bruteforce\+\_\+compute\+\_\+lcp (\begin{DoxyParamCaption}\item[{const size\+\_\+type \&}]{\+\_\+pos1,  }\item[{const size\+\_\+type \&}]{\+\_\+pos2 }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

literally compare two suffixes pointed to by the starting positions

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_aaa6c6e347bff1c6cb663771646c41826}\label{struct_validate4_1_1_r_scan_aaa6c6e347bff1c6cb663771646c41826}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!fetch\+\_\+l\+\_\+induced@{fetch\+\_\+l\+\_\+induced}}
\index{fetch\+\_\+l\+\_\+induced@{fetch\+\_\+l\+\_\+induced}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{fetch\+\_\+l\+\_\+induced()}{fetch\_l\_induced()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
void \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::fetch\+\_\+l\+\_\+induced (\begin{DoxyParamCaption}\item[{const alphabet\+\_\+type}]{\+\_\+ch,  }\item[{size\+\_\+type \&}]{\+\_\+sa\+\_\+value,  }\item[{size\+\_\+type \&}]{\+\_\+lcp\+\_\+value }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

fetch the S\+A-\/value for currently induced L-\/type suffix and the L\+C\+P-\/value for the suffix and its left neighbor in SA

retrieve the values from SA and L\+CP \mbox{\Hypertarget{struct_validate4_1_1_r_scan_af88a27e36780a6b390bc0bd18c253429}\label{struct_validate4_1_1_r_scan_af88a27e36780a6b390bc0bd18c253429}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!fetch\+\_\+l\+\_\+scanned@{fetch\+\_\+l\+\_\+scanned}}
\index{fetch\+\_\+l\+\_\+scanned@{fetch\+\_\+l\+\_\+scanned}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{fetch\+\_\+l\+\_\+scanned()}{fetch\_l\_scanned()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
void \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::fetch\+\_\+l\+\_\+scanned (\begin{DoxyParamCaption}\item[{size\+\_\+type \&}]{\+\_\+sa\+\_\+value,  }\item[{size\+\_\+type \&}]{\+\_\+lcp\+\_\+value }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

fetch the S\+A-\/value of currently scanned L-\/type suffix and the L\+C\+P-\/value of the suffix and its left neighbor in SA

retrieve S\+A-\/value and L\+C\+P-\/value from SA and L\+CP \begin{DoxyNote}{Note}
before calling the function, check to determine there remains elements to read 
\end{DoxyNote}
\mbox{\Hypertarget{struct_validate4_1_1_r_scan_aaeb8ae64faa2ab76d7467586f3281d97}\label{struct_validate4_1_1_r_scan_aaeb8ae64faa2ab76d7467586f3281d97}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!fetch\+\_\+lms\+\_\+scanned@{fetch\+\_\+lms\+\_\+scanned}}
\index{fetch\+\_\+lms\+\_\+scanned@{fetch\+\_\+lms\+\_\+scanned}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{fetch\+\_\+lms\+\_\+scanned()}{fetch\_lms\_scanned()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
void \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::fetch\+\_\+lms\+\_\+scanned (\begin{DoxyParamCaption}\item[{size\+\_\+type \&}]{\+\_\+sa\+\_\+value,  }\item[{size\+\_\+type \&}]{\+\_\+lcp\+\_\+value }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

fetch the S\+A-\/value of currently scanned L\+MS suffix and the L\+C\+P-\/value of the suffix and its left neighbor in S\+A\+\_\+\+L\+MS

retrieve S\+A-\/value and L\+C\+P-\/value from S\+A\+\_\+\+L\+MS and L\+C\+P\+\_\+\+L\+MS \begin{DoxyNote}{Note}
before calling the function, check to determine there remains elements to read 
\end{DoxyNote}
\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a32f26034048e070455cd9b1f56c95b89}\label{struct_validate4_1_1_r_scan_a32f26034048e070455cd9b1f56c95b89}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!find\+\_\+next\+\_\+l\+\_\+bkt@{find\+\_\+next\+\_\+l\+\_\+bkt}}
\index{find\+\_\+next\+\_\+l\+\_\+bkt@{find\+\_\+next\+\_\+l\+\_\+bkt}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{find\+\_\+next\+\_\+l\+\_\+bkt()}{find\_next\_l\_bkt()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
void \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::find\+\_\+next\+\_\+l\+\_\+bkt (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

find next non-\/empty L-\/bucket

\begin{DoxyNote}{Note}
guarantee that there still exist L-\/type suffixes to be scanned before calling the function 
\end{DoxyNote}
\mbox{\Hypertarget{struct_validate4_1_1_r_scan_af8a20c45983e2d175f6bbc67dcbef719}\label{struct_validate4_1_1_r_scan_af8a20c45983e2d175f6bbc67dcbef719}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!find\+\_\+next\+\_\+lms\+\_\+bkt@{find\+\_\+next\+\_\+lms\+\_\+bkt}}
\index{find\+\_\+next\+\_\+lms\+\_\+bkt@{find\+\_\+next\+\_\+lms\+\_\+bkt}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{find\+\_\+next\+\_\+lms\+\_\+bkt()}{find\_next\_lms\_bkt()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
void \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::find\+\_\+next\+\_\+lms\+\_\+bkt (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

find next non-\/empty L\+MS bucket

\begin{DoxyNote}{Note}
guarantee that there still exist L\+MS suffixes to be scanned before calling the function 
\end{DoxyNote}
\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a8d691af43c806d0e3279c0121abf6ed7}\label{struct_validate4_1_1_r_scan_a8d691af43c806d0e3279c0121abf6ed7}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!get\+\_\+l\+\_\+bkt\+\_\+ch@{get\+\_\+l\+\_\+bkt\+\_\+ch}}
\index{get\+\_\+l\+\_\+bkt\+\_\+ch@{get\+\_\+l\+\_\+bkt\+\_\+ch}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{get\+\_\+l\+\_\+bkt\+\_\+ch()}{get\_l\_bkt\_ch()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
alphabet\+\_\+type \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::get\+\_\+l\+\_\+bkt\+\_\+ch (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

return the initial character of suffixes in current scanned bucket

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_ac53c6318e14f774d956baea8134b5937}\label{struct_validate4_1_1_r_scan_ac53c6318e14f774d956baea8134b5937}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!get\+\_\+lms\+\_\+bkt\+\_\+ch@{get\+\_\+lms\+\_\+bkt\+\_\+ch}}
\index{get\+\_\+lms\+\_\+bkt\+\_\+ch@{get\+\_\+lms\+\_\+bkt\+\_\+ch}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{get\+\_\+lms\+\_\+bkt\+\_\+ch()}{get\_lms\_bkt\_ch()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
alphabet\+\_\+type \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::get\+\_\+lms\+\_\+bkt\+\_\+ch (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

return the initial character of suffixes in current scanned bucket

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_adf0c72967eddde6a6924472a16e92e95}\label{struct_validate4_1_1_r_scan_adf0c72967eddde6a6924472a16e92e95}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!l\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty@{l\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty}}
\index{l\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty@{l\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{l\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty()}{l\_cur\_bkt\_is\_empty()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
bool \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::l\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

check if no more L-\/type suffixes to be scanned in current bucket

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_aee1dcbd2edf03def6f3b3954d5cf0871}\label{struct_validate4_1_1_r_scan_aee1dcbd2edf03def6f3b3954d5cf0871}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!l\+\_\+is\+\_\+empty@{l\+\_\+is\+\_\+empty}}
\index{l\+\_\+is\+\_\+empty@{l\+\_\+is\+\_\+empty}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{l\+\_\+is\+\_\+empty()}{l\_is\_empty()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
bool \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::l\+\_\+is\+\_\+empty (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

check if no more L-\/type to be scanned

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a67647b0b0ef9df76bdcfa85547296a33}\label{struct_validate4_1_1_r_scan_a67647b0b0ef9df76bdcfa85547296a33}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!lms\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty@{lms\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty}}
\index{lms\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty@{lms\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{lms\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty()}{lms\_cur\_bkt\_is\_empty()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
bool \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::lms\+\_\+cur\+\_\+bkt\+\_\+is\+\_\+empty (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

check if no more L\+MS suffixes to be scanned in current bucket

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_ad24066012dd9441ffab435ce3f02424e}\label{struct_validate4_1_1_r_scan_ad24066012dd9441ffab435ce3f02424e}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!lms\+\_\+is\+\_\+empty@{lms\+\_\+is\+\_\+empty}}
\index{lms\+\_\+is\+\_\+empty@{lms\+\_\+is\+\_\+empty}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{lms\+\_\+is\+\_\+empty()}{lms\_is\_empty()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
bool \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::lms\+\_\+is\+\_\+empty (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

chec if no more L\+MS to be scanned

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a963da6ae9411fca7fb05701dd678161f}\label{struct_validate4_1_1_r_scan_a963da6ae9411fca7fb05701dd678161f}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!run@{run}}
\index{run@{run}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{run()}{run()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
bool \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::run (\begin{DoxyParamCaption}\item[{\hyperlink{class_validate4_a4c1bcea817e34f96d95c99e0694bbfc8}{triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$}]{\+\_\+pre\+\_\+item\+\_\+of\+\_\+l\+\_\+sorter,  }\item[{\hyperlink{class_validate4_aff3135d55f749682df7e0f97c82a6769}{pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$}]{\+\_\+pre\+\_\+item\+\_\+of\+\_\+lms\+\_\+sorter }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

induce and check the order of L-\/type suffixes and their L\+CP values

The S\+A-\/value of currently scanned suffix (no matter L-\/type or L\+MS) can be directly retrieved from SA or S\+A\+\_\+\+L\+MS. The question is how to retrieve the L\+C\+P-\/value of the suffix and the last scanned one (may not be the neighbor in SA). case 1\+: if currently scanned suffix is L-\/type, then retrieve the L\+C\+P-\/value following one of the two sub-\/cases as below\+: sub-\/case (a)\+: if the suffix is the leftmost in the L-\/type bucket, then perform a literal comparison between the suffix and the last scanned one to obtain their L\+C\+P-\/value. sub-\/case (b)\+: otherwise, the last scanned is also the left neighbor in SA, retrieve the L\+C\+P-\/value from L\+CP. case 2\+: if currently scanned suffix is L\+MS, then retrieve the L\+C\+P-\/value following one of the two sub-\/cases as below\+: sub-\/case (a)\+: if the suffix is the leftmost in the L\+MS bucket and the last scanned is L-\/type, then perform a literal comparison between the suffix and the last scanned to obtain their L\+C\+P-\/value. sub-\/case (b)\+: otherwise, the last scanned is also the left neighbor in S\+A\+\_\+\+L\+MS, retrieve the L\+C\+P-\/value from L\+C\+P\+\_\+\+L\+MS. The S\+A-\/value of currently induced L-\/type suffix can be directly retrieved from SA or S\+A\+\_\+\+L\+MS. The question is how to retrieve the L\+C\+P-\/value of the suffix and the last induced. case 1\+: if currently induced suffix is the leftmost in the L-\/type bucket, then do nothing. case 2\+: otherwise, the L\+C\+P-\/value is 1 + R\+M\+Q\+\_\+\+V\+A\+L\+UE.

\subsection{Member Data Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a3ff6f0be3fd0b25c66913d4d08b2e143}\label{struct_validate4_1_1_r_scan_a3ff6f0be3fd0b25c66913d4d08b2e143}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!ch\+\_\+max@{ch\+\_\+max}}
\index{ch\+\_\+max@{ch\+\_\+max}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{ch\+\_\+max}{ch\_max}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
const alphabet\+\_\+type \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::ch\+\_\+max\hspace{0.3cm}{\ttfamily [private]}}

maximum character

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a6ca7516c4fd64e5fe926636ac7197fda}\label{struct_validate4_1_1_r_scan_a6ca7516c4fd64e5fe926636ac7197fda}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+cur\+\_\+l\+\_\+ch@{m\+\_\+cur\+\_\+l\+\_\+ch}}
\index{m\+\_\+cur\+\_\+l\+\_\+ch@{m\+\_\+cur\+\_\+l\+\_\+ch}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+cur\+\_\+l\+\_\+ch}{m\_cur\_l\_ch}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
alphabet\+\_\+type \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+cur\+\_\+l\+\_\+ch\hspace{0.3cm}{\ttfamily [private]}}

L-\/type bucket currently being scanned.

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a8efbe937773c79d74f444e7f2c71fc8e}\label{struct_validate4_1_1_r_scan_a8efbe937773c79d74f444e7f2c71fc8e}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+cur\+\_\+lms\+\_\+ch@{m\+\_\+cur\+\_\+lms\+\_\+ch}}
\index{m\+\_\+cur\+\_\+lms\+\_\+ch@{m\+\_\+cur\+\_\+lms\+\_\+ch}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+cur\+\_\+lms\+\_\+ch}{m\_cur\_lms\_ch}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
alphabet\+\_\+type \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+cur\+\_\+lms\+\_\+ch\hspace{0.3cm}{\ttfamily [private]}}

L\+MS bucket currently being scanned.

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_ace00679285e1e6082440d2485809f0cf}\label{struct_validate4_1_1_r_scan_ace00679285e1e6082440d2485809f0cf}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+l\+\_\+bkt\+\_\+scanned@{m\+\_\+l\+\_\+bkt\+\_\+scanned}}
\index{m\+\_\+l\+\_\+bkt\+\_\+scanned@{m\+\_\+l\+\_\+bkt\+\_\+scanned}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+l\+\_\+bkt\+\_\+scanned}{m\_l\_bkt\_scanned}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+l\+\_\+bkt\+\_\+scanned\hspace{0.3cm}{\ttfamily [private]}}

number of L-\/type suffixes scanned in each bucket

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_ab9a643ec01afe4e6d3455ff025aeb612}\label{struct_validate4_1_1_r_scan_ab9a643ec01afe4e6d3455ff025aeb612}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+l\+\_\+bkt\+\_\+spos@{m\+\_\+l\+\_\+bkt\+\_\+spos}}
\index{m\+\_\+l\+\_\+bkt\+\_\+spos@{m\+\_\+l\+\_\+bkt\+\_\+spos}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+l\+\_\+bkt\+\_\+spos}{m\_l\_bkt\_spos}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+l\+\_\+bkt\+\_\+spos\hspace{0.3cm}{\ttfamily [private]}}

starting position of each L-\/type bucket in SA

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a47335f1e738063b9ddc5ee00be052cfd}\label{struct_validate4_1_1_r_scan_a47335f1e738063b9ddc5ee00be052cfd}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+l\+\_\+bkt\+\_\+toscan@{m\+\_\+l\+\_\+bkt\+\_\+toscan}}
\index{m\+\_\+l\+\_\+bkt\+\_\+toscan@{m\+\_\+l\+\_\+bkt\+\_\+toscan}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+l\+\_\+bkt\+\_\+toscan}{m\_l\_bkt\_toscan}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+l\+\_\+bkt\+\_\+toscan\hspace{0.3cm}{\ttfamily [private]}}

number of L-\/type suffixes to be scanned in each bucket

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a5521d8d0a72b169e07da61abd5463634}\label{struct_validate4_1_1_r_scan_a5521d8d0a72b169e07da61abd5463634}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+lcp@{m\+\_\+lcp}}
\index{m\+\_\+lcp@{m\+\_\+lcp}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+lcp}{m\_lcp}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+lcp\hspace{0.3cm}{\ttfamily [private]}}

pointer to L\+CP array

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a83351c07dee43e836114a49df9a0ec0a}\label{struct_validate4_1_1_r_scan_a83351c07dee43e836114a49df9a0ec0a}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+lcp\+\_\+l\+\_\+bkt\+\_\+reader@{m\+\_\+lcp\+\_\+l\+\_\+bkt\+\_\+reader}}
\index{m\+\_\+lcp\+\_\+l\+\_\+bkt\+\_\+reader@{m\+\_\+lcp\+\_\+l\+\_\+bkt\+\_\+reader}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+lcp\+\_\+l\+\_\+bkt\+\_\+reader}{m\_lcp\_l\_bkt\_reader}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$typename size\+\_\+vector\+\_\+type\+::bufreader\+\_\+type$\ast$$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+lcp\+\_\+l\+\_\+bkt\+\_\+reader\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a9aa4704ec4b22e0ecbec8c1c9687521d}\label{struct_validate4_1_1_r_scan_a9aa4704ec4b22e0ecbec8c1c9687521d}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+lcp\+\_\+l\+\_\+reader@{m\+\_\+lcp\+\_\+l\+\_\+reader}}
\index{m\+\_\+lcp\+\_\+l\+\_\+reader@{m\+\_\+lcp\+\_\+l\+\_\+reader}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+lcp\+\_\+l\+\_\+reader}{m\_lcp\_l\_reader}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
size\+\_\+vector\+\_\+type\+::bufreader\+\_\+type$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+lcp\+\_\+l\+\_\+reader\hspace{0.3cm}{\ttfamily [private]}}

for scan, point to the L\+C\+P-\/value for currently scanned L-\/type suffix and its left neighbor in SA (retrieve from L\+CP)

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_adf3e4856d77cd795d6b00b2355bd48bd}\label{struct_validate4_1_1_r_scan_adf3e4856d77cd795d6b00b2355bd48bd}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+lcp\+\_\+lms@{m\+\_\+lcp\+\_\+lms}}
\index{m\+\_\+lcp\+\_\+lms@{m\+\_\+lcp\+\_\+lms}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+lcp\+\_\+lms}{m\_lcp\_lms}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+lcp\+\_\+lms\hspace{0.3cm}{\ttfamily [private]}}

pointer to L\+C\+P\+\_\+\+L\+MS

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_aa712f18affa902ade5907584476a5003}\label{struct_validate4_1_1_r_scan_aa712f18affa902ade5907584476a5003}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+lcp\+\_\+lms\+\_\+reader@{m\+\_\+lcp\+\_\+lms\+\_\+reader}}
\index{m\+\_\+lcp\+\_\+lms\+\_\+reader@{m\+\_\+lcp\+\_\+lms\+\_\+reader}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+lcp\+\_\+lms\+\_\+reader}{m\_lcp\_lms\_reader}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
size\+\_\+vector\+\_\+type\+::bufreader\+\_\+type$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+lcp\+\_\+lms\+\_\+reader\hspace{0.3cm}{\ttfamily [private]}}

for scan, point to the L\+C\+P-\/value for currently scanned L\+MS suffixes and the rightmost L\+MS one on its leftside (retrieve from L\+C\+P\+\_\+\+L\+MS)

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a4ba4d8371cdcc14a4a34b012ee27a7f8}\label{struct_validate4_1_1_r_scan_a4ba4d8371cdcc14a4a34b012ee27a7f8}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+len@{m\+\_\+len}}
\index{m\+\_\+len@{m\+\_\+len}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+len}{m\_len}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+len\hspace{0.3cm}{\ttfamily [private]}}

number of elements in T/\+S\+A/\+L\+CP

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_ab56ecfb052c910af7ed356d5ad11be0b}\label{struct_validate4_1_1_r_scan_ab56ecfb052c910af7ed356d5ad11be0b}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+lms\+\_\+bkt\+\_\+scanned@{m\+\_\+lms\+\_\+bkt\+\_\+scanned}}
\index{m\+\_\+lms\+\_\+bkt\+\_\+scanned@{m\+\_\+lms\+\_\+bkt\+\_\+scanned}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+lms\+\_\+bkt\+\_\+scanned}{m\_lms\_bkt\_scanned}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+lms\+\_\+bkt\+\_\+scanned\hspace{0.3cm}{\ttfamily [private]}}

number of L\+MS suffixes scanned in each bucket

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a9681af9f2bc82ec9202da5c967f36491}\label{struct_validate4_1_1_r_scan_a9681af9f2bc82ec9202da5c967f36491}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+lms\+\_\+bkt\+\_\+toscan@{m\+\_\+lms\+\_\+bkt\+\_\+toscan}}
\index{m\+\_\+lms\+\_\+bkt\+\_\+toscan@{m\+\_\+lms\+\_\+bkt\+\_\+toscan}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+lms\+\_\+bkt\+\_\+toscan}{m\_lms\_bkt\_toscan}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+lms\+\_\+bkt\+\_\+toscan\hspace{0.3cm}{\ttfamily [private]}}

number of L\+MS suffixes to be scanned in each bucket

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_ab656e7db03298be8ce72f202e5aa5e77}\label{struct_validate4_1_1_r_scan_ab656e7db03298be8ce72f202e5aa5e77}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+sa@{m\+\_\+sa}}
\index{m\+\_\+sa@{m\+\_\+sa}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+sa}{m\_sa}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+sa\hspace{0.3cm}{\ttfamily [private]}}

pointer to suffix array

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_adbffde97174383da7a58437bf76ab0fe}\label{struct_validate4_1_1_r_scan_adbffde97174383da7a58437bf76ab0fe}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+sa\+\_\+l\+\_\+bkt\+\_\+reader@{m\+\_\+sa\+\_\+l\+\_\+bkt\+\_\+reader}}
\index{m\+\_\+sa\+\_\+l\+\_\+bkt\+\_\+reader@{m\+\_\+sa\+\_\+l\+\_\+bkt\+\_\+reader}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+sa\+\_\+l\+\_\+bkt\+\_\+reader}{m\_sa\_l\_bkt\_reader}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
std\+::vector$<$typename size\+\_\+vector\+\_\+type\+::bufreader\+\_\+type$\ast$$>$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+sa\+\_\+l\+\_\+bkt\+\_\+reader\hspace{0.3cm}{\ttfamily [private]}}

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a02e30a17efa641c20f6b979a21be9082}\label{struct_validate4_1_1_r_scan_a02e30a17efa641c20f6b979a21be9082}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+sa\+\_\+l\+\_\+reader@{m\+\_\+sa\+\_\+l\+\_\+reader}}
\index{m\+\_\+sa\+\_\+l\+\_\+reader@{m\+\_\+sa\+\_\+l\+\_\+reader}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+sa\+\_\+l\+\_\+reader}{m\_sa\_l\_reader}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
size\+\_\+vector\+\_\+type\+::bufreader\+\_\+type$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+sa\+\_\+l\+\_\+reader\hspace{0.3cm}{\ttfamily [private]}}

for scan, point to the S\+A-\/value for currently scanned L-\/type suffix (retrieve from SA)

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a7427660483d5beb9bbf8e6a69c291c25}\label{struct_validate4_1_1_r_scan_a7427660483d5beb9bbf8e6a69c291c25}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+sa\+\_\+lms@{m\+\_\+sa\+\_\+lms}}
\index{m\+\_\+sa\+\_\+lms@{m\+\_\+sa\+\_\+lms}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+sa\+\_\+lms}{m\_sa\_lms}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+sa\+\_\+lms\hspace{0.3cm}{\ttfamily [private]}}

pointer to S\+A\+\_\+\+L\+MS

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a986bdf3f5bc40e0d41939f699ac68c2c}\label{struct_validate4_1_1_r_scan_a986bdf3f5bc40e0d41939f699ac68c2c}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+sa\+\_\+lms\+\_\+reader@{m\+\_\+sa\+\_\+lms\+\_\+reader}}
\index{m\+\_\+sa\+\_\+lms\+\_\+reader@{m\+\_\+sa\+\_\+lms\+\_\+reader}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+sa\+\_\+lms\+\_\+reader}{m\_sa\_lms\_reader}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
size\+\_\+vector\+\_\+type\+::bufreader\+\_\+type$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+sa\+\_\+lms\+\_\+reader\hspace{0.3cm}{\ttfamily [private]}}

for scan, point to the S\+A-\/value for currently scanned L\+MS suffix (retrieve from S\+A\+\_\+\+L\+MS)

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a9d9ce16aa2eacc32f54cc88e8746a73a}\label{struct_validate4_1_1_r_scan_a9d9ce16aa2eacc32f54cc88e8746a73a}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+t@{m\+\_\+t}}
\index{m\+\_\+t@{m\+\_\+t}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+t}{m\_t}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4_a49c80b3d101be19542a4341c2387603a}{alphabet\+\_\+vector\+\_\+type}$\ast$ \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+t\hspace{0.3cm}{\ttfamily [private]}}

pointer to input string

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_ae0c9b8ab74cca6cebf6375cd772f1858}\label{struct_validate4_1_1_r_scan_ae0c9b8ab74cca6cebf6375cd772f1858}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+total\+\_\+l\+\_\+scanned@{m\+\_\+total\+\_\+l\+\_\+scanned}}
\index{m\+\_\+total\+\_\+l\+\_\+scanned@{m\+\_\+total\+\_\+l\+\_\+scanned}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+total\+\_\+l\+\_\+scanned}{m\_total\_l\_scanned}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+total\+\_\+l\+\_\+scanned\hspace{0.3cm}{\ttfamily [private]}}

total number of L-\/type suffixes already scanned

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a4cc3c1365b0089fe9d7740fed39dd0a7}\label{struct_validate4_1_1_r_scan_a4cc3c1365b0089fe9d7740fed39dd0a7}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+total\+\_\+l\+\_\+toscan@{m\+\_\+total\+\_\+l\+\_\+toscan}}
\index{m\+\_\+total\+\_\+l\+\_\+toscan@{m\+\_\+total\+\_\+l\+\_\+toscan}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+total\+\_\+l\+\_\+toscan}{m\_total\_l\_toscan}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+total\+\_\+l\+\_\+toscan\hspace{0.3cm}{\ttfamily [private]}}

total number of L-\/type suffixes to be scanned

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_a6451f758af2853be9d7aafc978001493}\label{struct_validate4_1_1_r_scan_a6451f758af2853be9d7aafc978001493}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+total\+\_\+lms\+\_\+scanned@{m\+\_\+total\+\_\+lms\+\_\+scanned}}
\index{m\+\_\+total\+\_\+lms\+\_\+scanned@{m\+\_\+total\+\_\+lms\+\_\+scanned}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+total\+\_\+lms\+\_\+scanned}{m\_total\_lms\_scanned}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+total\+\_\+lms\+\_\+scanned\hspace{0.3cm}{\ttfamily [private]}}

total number of L\+MS suffixes already scanned

\mbox{\Hypertarget{struct_validate4_1_1_r_scan_ae61305117585d96877b30800ea2479e4}\label{struct_validate4_1_1_r_scan_ae61305117585d96877b30800ea2479e4}} 
\index{Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}!m\+\_\+total\+\_\+lms\+\_\+toscan@{m\+\_\+total\+\_\+lms\+\_\+toscan}}
\index{m\+\_\+total\+\_\+lms\+\_\+toscan@{m\+\_\+total\+\_\+lms\+\_\+toscan}!Validate4\+::\+R\+Scan@{Validate4\+::\+R\+Scan}}
\subsubsection{\texorpdfstring{m\+\_\+total\+\_\+lms\+\_\+toscan}{m\_total\_lms\_toscan}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::R\+Scan\+::m\+\_\+total\+\_\+lms\+\_\+toscan\hspace{0.3cm}{\ttfamily [private]}}

total number of L\+MS suffixes to be scanned

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/\hyperlink{validate4_8h}{validate4.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/struct_validate4_1_1_retrieve_pre.tex
2017/01/24

\hypertarget{struct_validate4_1_1_retrieve_pre}{}\section{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+:\+:Retrieve\+Pre Struct Reference}
\label{struct_validate4_1_1_retrieve_pre}\index{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+Retrieve\+Pre@{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+Retrieve\+Pre}}

retrieve preceding items (pre\+\_\+ch \& pre\+\_\+t) for L-\/type, S-\/type and L\+MS suffixes

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{struct_validate4_1_1_retrieve_pre_abd6dc10b410baedef42cc2261ca8f143}{Retrieve\+Pre} (\hyperlink{class_validate4_a49c80b3d101be19542a4341c2387603a}{alphabet\+\_\+vector\+\_\+type} $\ast$\+\_\+t, \hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$\+\_\+sa, \hyperlink{class_validate4_aff3135d55f749682df7e0f97c82a6769}{pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$\&\+\_\+pre\+\_\+item\+\_\+of\+\_\+lms\+\_\+sorter, \hyperlink{class_validate4_a4c1bcea817e34f96d95c99e0694bbfc8}{triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$\&\+\_\+pre\+\_\+item\+\_\+of\+\_\+l\+\_\+sorter, \hyperlink{class_validate4_aa35a0ebf404821377118043d536be262}{triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$\&\+\_\+pre\+\_\+item\+\_\+of\+\_\+s\+\_\+sorter, \hyperlink{struct_validate4_1_1_bkt_info}{Bkt\+Info} \&\+\_\+bkt\+\_\+info)
\begin{DoxyCompactList}\small\item\em ctor \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename alphabet\+\_\+type, typename alphabet\+\_\+extension\+\_\+type, typename size\+\_\+type$>$\newline
struct Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+Retrieve\+Pre}

retrieve preceding items (pre\+\_\+ch \& pre\+\_\+t) for L-\/type, S-\/type and L\+MS suffixes

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{struct_validate4_1_1_retrieve_pre_abd6dc10b410baedef42cc2261ca8f143}\label{struct_validate4_1_1_retrieve_pre_abd6dc10b410baedef42cc2261ca8f143}} 
\index{Validate4\+::\+Retrieve\+Pre@{Validate4\+::\+Retrieve\+Pre}!Retrieve\+Pre@{Retrieve\+Pre}}
\index{Retrieve\+Pre@{Retrieve\+Pre}!Validate4\+::\+Retrieve\+Pre@{Validate4\+::\+Retrieve\+Pre}}
\subsubsection{\texorpdfstring{Retrieve\+Pre()}{RetrievePre()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename alphabet\+\_\+extension\+\_\+type , typename size\+\_\+type $>$ \\
\hyperlink{class_validate4}{Validate4}$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::Retrieve\+Pre\+::\+Retrieve\+Pre (\begin{DoxyParamCaption}\item[{\hyperlink{class_validate4_a49c80b3d101be19542a4341c2387603a}{alphabet\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+t,  }\item[{\hyperlink{class_validate4_a46ea31a0a4b23f583806792160421d15}{size\+\_\+vector\+\_\+type} $\ast$}]{\+\_\+sa,  }\item[{\hyperlink{class_validate4_aff3135d55f749682df7e0f97c82a6769}{pair3\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$\&}]{\+\_\+pre\+\_\+item\+\_\+of\+\_\+lms\+\_\+sorter,  }\item[{\hyperlink{class_validate4_a4c1bcea817e34f96d95c99e0694bbfc8}{triple2\+\_\+less\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$\&}]{\+\_\+pre\+\_\+item\+\_\+of\+\_\+l\+\_\+sorter,  }\item[{\hyperlink{class_validate4_aa35a0ebf404821377118043d536be262}{triple2\+\_\+great\+\_\+sorter\+\_\+1st\+\_\+type} $\ast$\&}]{\+\_\+pre\+\_\+item\+\_\+of\+\_\+s\+\_\+sorter,  }\item[{\hyperlink{struct_validate4_1_1_bkt_info}{Bkt\+Info} \&}]{\+\_\+bkt\+\_\+info }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

ctor

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/\hyperlink{validate4_8h}{validate4.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/struct_validate_1_1_r_interval.tex
2017/01/24

\hypertarget{struct_validate_1_1_r_interval}{}\section{Validate$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+:\+:R\+Interval Struct Reference}
\label{struct_validate_1_1_r_interval}\index{Validate$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::\+R\+Interval@{Validate$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::\+R\+Interval}}

store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, ...

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{struct_validate_1_1_r_interval_ad4edd1de89ff283674249f14ad7ec3de}{R\+Interval} (\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \+\_\+len)
\begin{DoxyCompactList}\small\item\em constructor \end{DoxyCompactList}\item 
\hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} \hyperlink{struct_validate_1_1_r_interval_a15d2215c198eb022a01792b62cfad0ef}{compute} (\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \+\_\+interval)
\begin{DoxyCompactList}\small\item\em get fp\+Interval \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Public Attributes}
\begin{DoxyCompactItemize}
\item 
\hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} $\ast$ \hyperlink{struct_validate_1_1_r_interval_a163e4054b0e05de3538c1011a9f4c664}{m\+\_\+data}
\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{struct_validate_1_1_r_interval_ab24650a97073141c105fdb3db61ca902}{m\+\_\+num}
\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename alphabet\+\_\+type, typename size\+\_\+type, typename offset\+\_\+type$>$\newline
struct Validate$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::\+R\+Interval}

store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, ...

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{struct_validate_1_1_r_interval_ad4edd1de89ff283674249f14ad7ec3de}\label{struct_validate_1_1_r_interval_ad4edd1de89ff283674249f14ad7ec3de}} 
\index{Validate\+::\+R\+Interval@{Validate\+::\+R\+Interval}!R\+Interval@{R\+Interval}}
\index{R\+Interval@{R\+Interval}!Validate\+::\+R\+Interval@{Validate\+::\+R\+Interval}}
\subsubsection{\texorpdfstring{R\+Interval()}{RInterval()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type , typename offset\+\_\+type $>$ \\
\hyperlink{class_validate}{Validate}$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::R\+Interval\+::\+R\+Interval (\begin{DoxyParamCaption}\item[{\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}]{\+\_\+len }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor

\subsection{Member Function Documentation}
\mbox{\Hypertarget{struct_validate_1_1_r_interval_a15d2215c198eb022a01792b62cfad0ef}\label{struct_validate_1_1_r_interval_a15d2215c198eb022a01792b62cfad0ef}} 
\index{Validate\+::\+R\+Interval@{Validate\+::\+R\+Interval}!compute@{compute}}
\index{compute@{compute}!Validate\+::\+R\+Interval@{Validate\+::\+R\+Interval}}
\subsubsection{\texorpdfstring{compute()}{compute()}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type , typename offset\+\_\+type $>$ \\
\hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type} \hyperlink{class_validate}{Validate}$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::R\+Interval\+::compute (\begin{DoxyParamCaption}\item[{\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}]{\+\_\+interval }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

get fp\+Interval

\subsection{Member Data Documentation}
\mbox{\Hypertarget{struct_validate_1_1_r_interval_a163e4054b0e05de3538c1011a9f4c664}\label{struct_validate_1_1_r_interval_a163e4054b0e05de3538c1011a9f4c664}} 
\index{Validate\+::\+R\+Interval@{Validate\+::\+R\+Interval}!m\+\_\+data@{m\+\_\+data}}
\index{m\+\_\+data@{m\+\_\+data}!Validate\+::\+R\+Interval@{Validate\+::\+R\+Interval}}
\subsubsection{\texorpdfstring{m\+\_\+data}{m\_data}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type , typename offset\+\_\+type $>$ \\
\hyperlink{common_8h_a7fdaf8b9b3d2f6ae6b10597a8d3f96ee}{fpa\+\_\+type}$\ast$ \hyperlink{class_validate}{Validate}$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::R\+Interval\+::m\+\_\+data}

\mbox{\Hypertarget{struct_validate_1_1_r_interval_ab24650a97073141c105fdb3db61ca902}\label{struct_validate_1_1_r_interval_ab24650a97073141c105fdb3db61ca902}} 
\index{Validate\+::\+R\+Interval@{Validate\+::\+R\+Interval}!m\+\_\+num@{m\+\_\+num}}
\index{m\+\_\+num@{m\+\_\+num}!Validate\+::\+R\+Interval@{Validate\+::\+R\+Interval}}
\subsubsection{\texorpdfstring{m\+\_\+num}{m\_num}}
{\footnotesize\ttfamily template$<$typename alphabet\+\_\+type , typename size\+\_\+type , typename offset\+\_\+type $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{class_validate}{Validate}$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::R\+Interval\+::m\+\_\+num}

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/\hyperlink{validate_8h}{validate.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/structbuffer.tex
2017/01/24

\hypertarget{structbuffer}{}\section{buffer$<$ T $>$ Struct Template Reference}
\label{structbuffer}\index{buffer$<$ T $>$@{buffer$<$ T $>$}}

read buffer

{\ttfamily \#include $<$async\+\_\+stream\+\_\+reader.\+h$>$}

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{structbuffer_aefd0601854f94ec9c18c05986d218c16}{buffer} (\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \+\_\+size)
\begin{DoxyCompactList}\small\item\em constructor \end{DoxyCompactList}\item 
void \hyperlink{structbuffer_a2abf8fde8a3d6a1245f57d698e207b74}{read\+\_\+from\+\_\+file} (std\+::\+F\+I\+LE $\ast$\+\_\+f)
\begin{DoxyCompactList}\small\item\em read a data block from a disk file \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{structbuffer_a2b74a935bb50716bba0835781545803d}{size\+\_\+in\+\_\+bytes} () const
\begin{DoxyCompactList}\small\item\em total size of elements in buffer \end{DoxyCompactList}\item 
\hyperlink{structbuffer_accefc959744e463ae78a996a2f45f81a}{$\sim$buffer} ()
\begin{DoxyCompactList}\small\item\em dtor \end{DoxyCompactList}\item 
\hyperlink{structbuffer_aefd0601854f94ec9c18c05986d218c16}{buffer} (\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \+\_\+size)
\begin{DoxyCompactList}\small\item\em default ctor \end{DoxyCompactList}\item 
void \hyperlink{structbuffer_ac31d1516df0036a19bb3e58a4a2fac8a}{write\+\_\+to\+\_\+file} (std\+::\+F\+I\+LE $\ast$\+\_\+f)
\begin{DoxyCompactList}\small\item\em write to file \end{DoxyCompactList}\item 
\hyperlink{structbuffer_accefc959744e463ae78a996a2f45f81a}{$\sim$buffer} ()
\begin{DoxyCompactList}\small\item\em dtor \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{structbuffer_a2b74a935bb50716bba0835781545803d}{size\+\_\+in\+\_\+bytes} () const
\begin{DoxyCompactList}\small\item\em return occupied space (in bytes) in buffer \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{structbuffer_a877157a0ddb2aa0fa10c7273eece00cb}{free\+\_\+space} () const
\begin{DoxyCompactList}\small\item\em remaing space in the buffer \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Public Attributes}
\begin{DoxyCompactItemize}
\item 
T $\ast$ \hyperlink{structbuffer_a51dfd20b289c52f084b6d277c2e4745f}{m\+\_\+content}
\begin{DoxyCompactList}\small\item\em pointer to buffer payload \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{structbuffer_a120b15f6f771bc004c80d12eb881623f}{m\+\_\+size}
\begin{DoxyCompactList}\small\item\em size of buffer \end{DoxyCompactList}\item 
uiint64 \hyperlink{structbuffer_af3dc3d5097b6de42b637942b1b0cf8bc}{m\+\_\+filled}
\begin{DoxyCompactList}\small\item\em number of elements in buffer \end{DoxyCompactList}\item 
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{structbuffer_af5e119495e5a739d01f5d1d109aa39b6}{m\+\_\+filled}
\begin{DoxyCompactList}\small\item\em number of elements in buffer \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename T$>$\newline
struct buffer$<$ T $>$}

read buffer

buffer structure

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{structbuffer_aefd0601854f94ec9c18c05986d218c16}\label{structbuffer_aefd0601854f94ec9c18c05986d218c16}} 
\index{buffer@{buffer}!buffer@{buffer}}
\index{buffer@{buffer}!buffer@{buffer}}
\subsubsection{\texorpdfstring{buffer()}{buffer()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily template$<$typename T $>$ \\
\hyperlink{structbuffer}{buffer}$<$ T $>$\+::\hyperlink{structbuffer}{buffer} (\begin{DoxyParamCaption}\item[{\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}]{\+\_\+size }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor

\begin{DoxyParams}{Parameters}
{\em \+\_\+size} & size of buffer \\
\hline
\end{DoxyParams}
\mbox{\Hypertarget{structbuffer_accefc959744e463ae78a996a2f45f81a}\label{structbuffer_accefc959744e463ae78a996a2f45f81a}} 
\index{buffer@{buffer}!````~buffer@{$\sim$buffer}}
\index{````~buffer@{$\sim$buffer}!buffer@{buffer}}
\subsubsection{\texorpdfstring{$\sim$buffer()}{~buffer()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily template$<$typename T $>$ \\
\hyperlink{structbuffer}{buffer}$<$ T $>$\+::$\sim$\hyperlink{structbuffer}{buffer} (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

dtor

\mbox{\Hypertarget{structbuffer_aefd0601854f94ec9c18c05986d218c16}\label{structbuffer_aefd0601854f94ec9c18c05986d218c16}} 
\index{buffer@{buffer}!buffer@{buffer}}
\index{buffer@{buffer}!buffer@{buffer}}
\subsubsection{\texorpdfstring{buffer()}{buffer()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily template$<$typename T $>$ \\
\hyperlink{structbuffer}{buffer}$<$ T $>$\+::\hyperlink{structbuffer}{buffer} (\begin{DoxyParamCaption}\item[{\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}]{\+\_\+size }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

default ctor

\begin{DoxyParams}{Parameters}
{\em \+\_\+size} & buffer size \\
\hline
\end{DoxyParams}
\mbox{\Hypertarget{structbuffer_accefc959744e463ae78a996a2f45f81a}\label{structbuffer_accefc959744e463ae78a996a2f45f81a}} 
\index{buffer@{buffer}!````~buffer@{$\sim$buffer}}
\index{````~buffer@{$\sim$buffer}!buffer@{buffer}}
\subsubsection{\texorpdfstring{$\sim$buffer()}{~buffer()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily template$<$typename T $>$ \\
\hyperlink{structbuffer}{buffer}$<$ T $>$\+::$\sim$\hyperlink{structbuffer}{buffer} (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

dtor

\subsection{Member Function Documentation}
\mbox{\Hypertarget{structbuffer_a877157a0ddb2aa0fa10c7273eece00cb}\label{structbuffer_a877157a0ddb2aa0fa10c7273eece00cb}} 
\index{buffer@{buffer}!free\+\_\+space@{free\+\_\+space}}
\index{free\+\_\+space@{free\+\_\+space}!buffer@{buffer}}
\subsubsection{\texorpdfstring{free\+\_\+space()}{free\_space()}}
{\footnotesize\ttfamily template$<$typename T $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{structbuffer}{buffer}$<$ T $>$\+::free\+\_\+space (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

remaing space in the buffer

\mbox{\Hypertarget{structbuffer_a2abf8fde8a3d6a1245f57d698e207b74}\label{structbuffer_a2abf8fde8a3d6a1245f57d698e207b74}} 
\index{buffer@{buffer}!read\+\_\+from\+\_\+file@{read\+\_\+from\+\_\+file}}
\index{read\+\_\+from\+\_\+file@{read\+\_\+from\+\_\+file}!buffer@{buffer}}
\subsubsection{\texorpdfstring{read\+\_\+from\+\_\+file()}{read\_from\_file()}}
{\footnotesize\ttfamily template$<$typename T $>$ \\
void \hyperlink{structbuffer}{buffer}$<$ T $>$\+::read\+\_\+from\+\_\+file (\begin{DoxyParamCaption}\item[{std\+::\+F\+I\+LE $\ast$}]{\+\_\+f }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

read a data block from a disk file

\begin{DoxyParams}{Parameters}
{\em \+\_\+f} & file descriptor \\
\hline
\end{DoxyParams}
\mbox{\Hypertarget{structbuffer_a2b74a935bb50716bba0835781545803d}\label{structbuffer_a2b74a935bb50716bba0835781545803d}} 
\index{buffer@{buffer}!size\+\_\+in\+\_\+bytes@{size\+\_\+in\+\_\+bytes}}
\index{size\+\_\+in\+\_\+bytes@{size\+\_\+in\+\_\+bytes}!buffer@{buffer}}
\subsubsection{\texorpdfstring{size\+\_\+in\+\_\+bytes()}{size\_in\_bytes()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily template$<$typename T $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{structbuffer}{buffer}$<$ T $>$\+::size\+\_\+in\+\_\+bytes (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

total size of elements in buffer

\mbox{\Hypertarget{structbuffer_a2b74a935bb50716bba0835781545803d}\label{structbuffer_a2b74a935bb50716bba0835781545803d}} 
\index{buffer@{buffer}!size\+\_\+in\+\_\+bytes@{size\+\_\+in\+\_\+bytes}}
\index{size\+\_\+in\+\_\+bytes@{size\+\_\+in\+\_\+bytes}!buffer@{buffer}}
\subsubsection{\texorpdfstring{size\+\_\+in\+\_\+bytes()}{size\_in\_bytes()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily template$<$typename T $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{structbuffer}{buffer}$<$ T $>$\+::size\+\_\+in\+\_\+bytes (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

return occupied space (in bytes) in buffer

\mbox{\Hypertarget{structbuffer_ac31d1516df0036a19bb3e58a4a2fac8a}\label{structbuffer_ac31d1516df0036a19bb3e58a4a2fac8a}} 
\index{buffer@{buffer}!write\+\_\+to\+\_\+file@{write\+\_\+to\+\_\+file}}
\index{write\+\_\+to\+\_\+file@{write\+\_\+to\+\_\+file}!buffer@{buffer}}
\subsubsection{\texorpdfstring{write\+\_\+to\+\_\+file()}{write\_to\_file()}}
{\footnotesize\ttfamily template$<$typename T $>$ \\
void \hyperlink{structbuffer}{buffer}$<$ T $>$\+::write\+\_\+to\+\_\+file (\begin{DoxyParamCaption}\item[{std\+::\+F\+I\+LE $\ast$}]{\+\_\+f }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

write to file

\begin{DoxyParams}{Parameters}
{\em \+\_\+f} & file descriptor \\
\hline
\end{DoxyParams}

\subsection{Member Data Documentation}
\mbox{\Hypertarget{structbuffer_a51dfd20b289c52f084b6d277c2e4745f}\label{structbuffer_a51dfd20b289c52f084b6d277c2e4745f}} 
\index{buffer@{buffer}!m\+\_\+content@{m\+\_\+content}}
\index{m\+\_\+content@{m\+\_\+content}!buffer@{buffer}}
\subsubsection{\texorpdfstring{m\+\_\+content}{m\_content}}
{\footnotesize\ttfamily template$<$typename T $>$ \\
T $\ast$ \hyperlink{structbuffer}{buffer}$<$ T $>$\+::m\+\_\+content}

pointer to buffer payload

payload \mbox{\Hypertarget{structbuffer_af3dc3d5097b6de42b637942b1b0cf8bc}\label{structbuffer_af3dc3d5097b6de42b637942b1b0cf8bc}} 
\index{buffer@{buffer}!m\+\_\+filled@{m\+\_\+filled}}
\index{m\+\_\+filled@{m\+\_\+filled}!buffer@{buffer}}
\subsubsection{\texorpdfstring{m\+\_\+filled}{m\_filled}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily template$<$typename T $>$ \\
uiint64 \hyperlink{structbuffer}{buffer}$<$ T $>$\+::m\+\_\+filled}

number of elements in buffer

\mbox{\Hypertarget{structbuffer_af5e119495e5a739d01f5d1d109aa39b6}\label{structbuffer_af5e119495e5a739d01f5d1d109aa39b6}} 
\index{buffer@{buffer}!m\+\_\+filled@{m\+\_\+filled}}
\index{m\+\_\+filled@{m\+\_\+filled}!buffer@{buffer}}
\subsubsection{\texorpdfstring{m\+\_\+filled}{m\_filled}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily template$<$typename T $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{structbuffer}{buffer}$<$ T $>$\+::m\+\_\+filled}

number of elements in buffer

\mbox{\Hypertarget{structbuffer_a120b15f6f771bc004c80d12eb881623f}\label{structbuffer_a120b15f6f771bc004c80d12eb881623f}} 
\index{buffer@{buffer}!m\+\_\+size@{m\+\_\+size}}
\index{m\+\_\+size@{m\+\_\+size}!buffer@{buffer}}
\subsubsection{\texorpdfstring{m\+\_\+size}{m\_size}}
{\footnotesize\ttfamily template$<$typename T $>$ \\
\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \hyperlink{structbuffer}{buffer}$<$ T $>$\+::m\+\_\+size}

size of buffer

The documentation for this struct was generated from the following files\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{async__stream__reader_8h}{async\+\_\+stream\+\_\+reader.\+h}\item 
code/src/common/\hyperlink{async__stream__writer_8h}{async\+\_\+stream\+\_\+writer.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/structbuffer__queue.tex
2017/01/24

\hypertarget{structbuffer__queue}{}\section{buffer\+\_\+queue$<$ buffer\+\_\+type $>$ Struct Template Reference}
\label{structbuffer__queue}\index{buffer\+\_\+queue$<$ buffer\+\_\+type $>$@{buffer\+\_\+queue$<$ buffer\+\_\+type $>$}}

queue of buffers

{\ttfamily \#include $<$async\+\_\+stream\+\_\+reader.\+h$>$}

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{structbuffer__queue_acd123387742f7cc4e1e418e7864ca2a1}{buffer\+\_\+queue} (\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \+\_\+bufnum=0, \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \+\_\+bufsize=0)
\begin{DoxyCompactList}\small\item\em constructor \end{DoxyCompactList}\item 
\hyperlink{structbuffer__queue_a8dda78874230bead5795e510f315dc2c}{$\sim$buffer\+\_\+queue} ()
\begin{DoxyCompactList}\small\item\em destructor \end{DoxyCompactList}\item 
buffer\+\_\+type $\ast$ \hyperlink{structbuffer__queue_ab26cbb480e9a300a4a021f4be1bb2735}{pop} ()
\begin{DoxyCompactList}\small\item\em use resource, lock must be obtained before calling the function \end{DoxyCompactList}\item 
void \hyperlink{structbuffer__queue_a13c104db4054ca0cb59b5e0502267d55}{push} (buffer\+\_\+type $\ast$\+\_\+buf)
\begin{DoxyCompactList}\small\item\em recycle resource, lock must be obtained during the calling \end{DoxyCompactList}\item 
void \hyperlink{structbuffer__queue_a487335f8827c09d4d76d588e47d633ac}{send\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal} ()
\begin{DoxyCompactList}\small\item\em I/O thread send the signal when it reaches the endofbits. \end{DoxyCompactList}\item 
bool \hyperlink{structbuffer__queue_a5d618b9b6dd1f700db6f96182cc1ad15}{empty} () const
\begin{DoxyCompactList}\small\item\em check if queue is empty \end{DoxyCompactList}\item 
\hyperlink{structbuffer__queue_a4e972bf42989038b6ef7eda7a372d1c3}{buffer\+\_\+queue} (const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+bufnum=0, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+bufsize=0)
\begin{DoxyCompactList}\small\item\em a queue of write buffer \end{DoxyCompactList}\item 
\hyperlink{structbuffer__queue_a8dda78874230bead5795e510f315dc2c}{$\sim$buffer\+\_\+queue} ()
\begin{DoxyCompactList}\small\item\em dtor \end{DoxyCompactList}\item 
buffer\+\_\+type $\ast$ \hyperlink{structbuffer__queue_ab26cbb480e9a300a4a021f4be1bb2735}{pop} ()
\begin{DoxyCompactList}\small\item\em pop the front buffer in the queue \end{DoxyCompactList}\item 
void \hyperlink{structbuffer__queue_a13c104db4054ca0cb59b5e0502267d55}{push} (buffer\+\_\+type $\ast$\+\_\+buf)
\begin{DoxyCompactList}\small\item\em push a buffer \end{DoxyCompactList}\item 
void \hyperlink{structbuffer__queue_a487335f8827c09d4d76d588e47d633ac}{send\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal} ()
\begin{DoxyCompactList}\small\item\em stop writting \end{DoxyCompactList}\item 
bool \hyperlink{structbuffer__queue_a5d618b9b6dd1f700db6f96182cc1ad15}{empty} () const
\begin{DoxyCompactList}\small\item\em check if empty \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Public Attributes}
\begin{DoxyCompactItemize}
\item 
std\+::queue$<$ buffer\+\_\+type $\ast$ $>$ \hyperlink{structbuffer__queue_abac5a752d815ded66d3ab87b5b6649b6}{m\+\_\+queue}
\begin{DoxyCompactList}\small\item\em F\+I\+FO queue. \end{DoxyCompactList}\item 
std\+::condition\+\_\+variable \hyperlink{structbuffer__queue_a65f560d9b82c5154044243c21867a773}{m\+\_\+cv}
\begin{DoxyCompactList}\small\item\em condition variable for the queue \end{DoxyCompactList}\item 
std\+::mutex \hyperlink{structbuffer__queue_aa554ca5c5cccd9b58ddad9d25fa7f7e8}{m\+\_\+mutex}
\begin{DoxyCompactList}\small\item\em mutex for the queue \end{DoxyCompactList}\item 
bool \hyperlink{structbuffer__queue_abcecda21a70871516c9322a4b4f3c6bd}{m\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal}
\begin{DoxyCompactList}\small\item\em no more full buffer will be created \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename buffer\+\_\+type$>$\newline
struct buffer\+\_\+queue$<$ buffer\+\_\+type $>$}

queue of buffers

buffer queue

Buffers are orgainzed as a queue. Based on the producer-\/consumer mechanism, data are read into buffers and processed in the R\+AM.

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{structbuffer__queue_acd123387742f7cc4e1e418e7864ca2a1}\label{structbuffer__queue_acd123387742f7cc4e1e418e7864ca2a1}} 
\index{buffer\+\_\+queue@{buffer\+\_\+queue}!buffer\+\_\+queue@{buffer\+\_\+queue}}
\index{buffer\+\_\+queue@{buffer\+\_\+queue}!buffer\+\_\+queue@{buffer\+\_\+queue}}
\subsubsection{\texorpdfstring{buffer\+\_\+queue()}{buffer\_queue()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily template$<$typename buffer\+\_\+type $>$ \\
\hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ buffer\+\_\+type $>$\+::\hyperlink{structbuffer__queue}{buffer\+\_\+queue} (\begin{DoxyParamCaption}\item[{\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}]{\+\_\+bufnum = {\ttfamily 0},  }\item[{\hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}]{\+\_\+bufsize = {\ttfamily 0} }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor

\begin{DoxyParams}{Parameters}
{\em \+\_\+bufnum} & number of buffers in the queue \\
\hline
{\em \+\_\+bufsize} & size of each buffer \\
\hline
\end{DoxyParams}
\mbox{\Hypertarget{structbuffer__queue_a8dda78874230bead5795e510f315dc2c}\label{structbuffer__queue_a8dda78874230bead5795e510f315dc2c}} 
\index{buffer\+\_\+queue@{buffer\+\_\+queue}!````~buffer\+\_\+queue@{$\sim$buffer\+\_\+queue}}
\index{````~buffer\+\_\+queue@{$\sim$buffer\+\_\+queue}!buffer\+\_\+queue@{buffer\+\_\+queue}}
\subsubsection{\texorpdfstring{$\sim$buffer\+\_\+queue()}{~buffer\_queue()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily template$<$typename buffer\+\_\+type $>$ \\
\hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ buffer\+\_\+type $>$\+::$\sim$\hyperlink{structbuffer__queue}{buffer\+\_\+queue} (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

destructor

\mbox{\Hypertarget{structbuffer__queue_a4e972bf42989038b6ef7eda7a372d1c3}\label{structbuffer__queue_a4e972bf42989038b6ef7eda7a372d1c3}} 
\index{buffer\+\_\+queue@{buffer\+\_\+queue}!buffer\+\_\+queue@{buffer\+\_\+queue}}
\index{buffer\+\_\+queue@{buffer\+\_\+queue}!buffer\+\_\+queue@{buffer\+\_\+queue}}
\subsubsection{\texorpdfstring{buffer\+\_\+queue()}{buffer\_queue()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily template$<$typename buffer\+\_\+type $>$ \\
\hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ buffer\+\_\+type $>$\+::\hyperlink{structbuffer__queue}{buffer\+\_\+queue} (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+bufnum = {\ttfamily 0},  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+bufsize = {\ttfamily 0} }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

a queue of write buffer

\begin{DoxyParams}{Parameters}
{\em number} & of buffers \\
\hline
{\em size} & of each buffer \\
\hline
\end{DoxyParams}
\mbox{\Hypertarget{structbuffer__queue_a8dda78874230bead5795e510f315dc2c}\label{structbuffer__queue_a8dda78874230bead5795e510f315dc2c}} 
\index{buffer\+\_\+queue@{buffer\+\_\+queue}!````~buffer\+\_\+queue@{$\sim$buffer\+\_\+queue}}
\index{````~buffer\+\_\+queue@{$\sim$buffer\+\_\+queue}!buffer\+\_\+queue@{buffer\+\_\+queue}}
\subsubsection{\texorpdfstring{$\sim$buffer\+\_\+queue()}{~buffer\_queue()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily template$<$typename buffer\+\_\+type $>$ \\
\hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ buffer\+\_\+type $>$\+::$\sim$\hyperlink{structbuffer__queue}{buffer\+\_\+queue} (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

dtor

\subsection{Member Function Documentation}
\mbox{\Hypertarget{structbuffer__queue_a5d618b9b6dd1f700db6f96182cc1ad15}\label{structbuffer__queue_a5d618b9b6dd1f700db6f96182cc1ad15}} 
\index{buffer\+\_\+queue@{buffer\+\_\+queue}!empty@{empty}}
\index{empty@{empty}!buffer\+\_\+queue@{buffer\+\_\+queue}}
\subsubsection{\texorpdfstring{empty()}{empty()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily template$<$typename buffer\+\_\+type $>$ \\
bool \hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ buffer\+\_\+type $>$\+::empty (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

check if queue is empty

\mbox{\Hypertarget{structbuffer__queue_a5d618b9b6dd1f700db6f96182cc1ad15}\label{structbuffer__queue_a5d618b9b6dd1f700db6f96182cc1ad15}} 
\index{buffer\+\_\+queue@{buffer\+\_\+queue}!empty@{empty}}
\index{empty@{empty}!buffer\+\_\+queue@{buffer\+\_\+queue}}
\subsubsection{\texorpdfstring{empty()}{empty()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily template$<$typename buffer\+\_\+type $>$ \\
bool \hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ buffer\+\_\+type $>$\+::empty (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

check if empty

\mbox{\Hypertarget{structbuffer__queue_ab26cbb480e9a300a4a021f4be1bb2735}\label{structbuffer__queue_ab26cbb480e9a300a4a021f4be1bb2735}} 
\index{buffer\+\_\+queue@{buffer\+\_\+queue}!pop@{pop}}
\index{pop@{pop}!buffer\+\_\+queue@{buffer\+\_\+queue}}
\subsubsection{\texorpdfstring{pop()}{pop()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily template$<$typename buffer\+\_\+type $>$ \\
buffer\+\_\+type$\ast$ \hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ buffer\+\_\+type $>$\+::pop (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

use resource, lock must be obtained before calling the function

\mbox{\Hypertarget{structbuffer__queue_ab26cbb480e9a300a4a021f4be1bb2735}\label{structbuffer__queue_ab26cbb480e9a300a4a021f4be1bb2735}} 
\index{buffer\+\_\+queue@{buffer\+\_\+queue}!pop@{pop}}
\index{pop@{pop}!buffer\+\_\+queue@{buffer\+\_\+queue}}
\subsubsection{\texorpdfstring{pop()}{pop()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily template$<$typename buffer\+\_\+type $>$ \\
buffer\+\_\+type$\ast$ \hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ buffer\+\_\+type $>$\+::pop (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

pop the front buffer in the queue

\begin{DoxyNote}{Note}
lock is obtained before calling the function in the code 
\end{DoxyNote}
\mbox{\Hypertarget{structbuffer__queue_a13c104db4054ca0cb59b5e0502267d55}\label{structbuffer__queue_a13c104db4054ca0cb59b5e0502267d55}} 
\index{buffer\+\_\+queue@{buffer\+\_\+queue}!push@{push}}
\index{push@{push}!buffer\+\_\+queue@{buffer\+\_\+queue}}
\subsubsection{\texorpdfstring{push()}{push()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily template$<$typename buffer\+\_\+type $>$ \\
void \hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ buffer\+\_\+type $>$\+::push (\begin{DoxyParamCaption}\item[{buffer\+\_\+type $\ast$}]{\+\_\+buf }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

recycle resource, lock must be obtained during the calling

\mbox{\Hypertarget{structbuffer__queue_a13c104db4054ca0cb59b5e0502267d55}\label{structbuffer__queue_a13c104db4054ca0cb59b5e0502267d55}} 
\index{buffer\+\_\+queue@{buffer\+\_\+queue}!push@{push}}
\index{push@{push}!buffer\+\_\+queue@{buffer\+\_\+queue}}
\subsubsection{\texorpdfstring{push()}{push()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily template$<$typename buffer\+\_\+type $>$ \\
void \hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ buffer\+\_\+type $>$\+::push (\begin{DoxyParamCaption}\item[{buffer\+\_\+type $\ast$}]{\+\_\+buf }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

push a buffer

\begin{DoxyParams}{Parameters}
{\em ptr} & to buffer \\
\hline
\end{DoxyParams}
\begin{DoxyNote}{Note}
lock before pushing 
\end{DoxyNote}
\mbox{\Hypertarget{structbuffer__queue_a487335f8827c09d4d76d588e47d633ac}\label{structbuffer__queue_a487335f8827c09d4d76d588e47d633ac}} 
\index{buffer\+\_\+queue@{buffer\+\_\+queue}!send\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal@{send\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal}}
\index{send\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal@{send\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal}!buffer\+\_\+queue@{buffer\+\_\+queue}}
\subsubsection{\texorpdfstring{send\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal()}{send\_no\_more\_full\_buffer\_signal()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily template$<$typename buffer\+\_\+type $>$ \\
void \hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ buffer\+\_\+type $>$\+::send\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

I/O thread send the signal when it reaches the endofbits.

\mbox{\Hypertarget{structbuffer__queue_a487335f8827c09d4d76d588e47d633ac}\label{structbuffer__queue_a487335f8827c09d4d76d588e47d633ac}} 
\index{buffer\+\_\+queue@{buffer\+\_\+queue}!send\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal@{send\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal}}
\index{send\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal@{send\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal}!buffer\+\_\+queue@{buffer\+\_\+queue}}
\subsubsection{\texorpdfstring{send\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal()}{send\_no\_more\_full\_buffer\_signal()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily template$<$typename buffer\+\_\+type $>$ \\
void \hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ buffer\+\_\+type $>$\+::send\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

stop writting

\begin{DoxyNote}{Note}
lock before adapting 
\end{DoxyNote}

\subsection{Member Data Documentation}
\mbox{\Hypertarget{structbuffer__queue_a65f560d9b82c5154044243c21867a773}\label{structbuffer__queue_a65f560d9b82c5154044243c21867a773}} 
\index{buffer\+\_\+queue@{buffer\+\_\+queue}!m\+\_\+cv@{m\+\_\+cv}}
\index{m\+\_\+cv@{m\+\_\+cv}!buffer\+\_\+queue@{buffer\+\_\+queue}}
\subsubsection{\texorpdfstring{m\+\_\+cv}{m\_cv}}
{\footnotesize\ttfamily template$<$typename buffer\+\_\+type $>$ \\
std\+::condition\+\_\+variable \hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ buffer\+\_\+type $>$\+::m\+\_\+cv}

condition variable for the queue

condition variable \mbox{\Hypertarget{structbuffer__queue_aa554ca5c5cccd9b58ddad9d25fa7f7e8}\label{structbuffer__queue_aa554ca5c5cccd9b58ddad9d25fa7f7e8}} 
\index{buffer\+\_\+queue@{buffer\+\_\+queue}!m\+\_\+mutex@{m\+\_\+mutex}}
\index{m\+\_\+mutex@{m\+\_\+mutex}!buffer\+\_\+queue@{buffer\+\_\+queue}}
\subsubsection{\texorpdfstring{m\+\_\+mutex}{m\_mutex}}
{\footnotesize\ttfamily template$<$typename buffer\+\_\+type $>$ \\
std\+::mutex \hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ buffer\+\_\+type $>$\+::m\+\_\+mutex}

mutex for the queue

mutex \mbox{\Hypertarget{structbuffer__queue_abcecda21a70871516c9322a4b4f3c6bd}\label{structbuffer__queue_abcecda21a70871516c9322a4b4f3c6bd}} 
\index{buffer\+\_\+queue@{buffer\+\_\+queue}!m\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal@{m\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal}}
\index{m\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal@{m\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal}!buffer\+\_\+queue@{buffer\+\_\+queue}}
\subsubsection{\texorpdfstring{m\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal}{m\_no\_more\_full\_buffer\_signal}}
{\footnotesize\ttfamily template$<$typename buffer\+\_\+type $>$ \\
bool \hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ buffer\+\_\+type $>$\+::m\+\_\+no\+\_\+more\+\_\+full\+\_\+buffer\+\_\+signal}

no more full buffer will be created

main thread inform I/O thread \mbox{\Hypertarget{structbuffer__queue_abac5a752d815ded66d3ab87b5b6649b6}\label{structbuffer__queue_abac5a752d815ded66d3ab87b5b6649b6}} 
\index{buffer\+\_\+queue@{buffer\+\_\+queue}!m\+\_\+queue@{m\+\_\+queue}}
\index{m\+\_\+queue@{m\+\_\+queue}!buffer\+\_\+queue@{buffer\+\_\+queue}}
\subsubsection{\texorpdfstring{m\+\_\+queue}{m\_queue}}
{\footnotesize\ttfamily template$<$typename buffer\+\_\+type $>$ \\
std\+::queue$<$ buffer\+\_\+type $\ast$ $>$ \hyperlink{structbuffer__queue}{buffer\+\_\+queue}$<$ buffer\+\_\+type $>$\+::m\+\_\+queue}

F\+I\+FO queue.

buffer queue

The documentation for this struct was generated from the following files\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{async__stream__reader_8h}{async\+\_\+stream\+\_\+reader.\+h}\item 
code/src/common/\hyperlink{async__stream__writer_8h}{async\+\_\+stream\+\_\+writer.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/structchoose__int__types.tex
2017/01/24

\hypertarget{structchoose__int__types}{}\section{choose\+\_\+int\+\_\+types$<$ PS $>$ Struct Template Reference}
\label{structchoose__int__types}\index{choose\+\_\+int\+\_\+types$<$ P\+S $>$@{choose\+\_\+int\+\_\+types$<$ P\+S $>$}}

template for choosing int/uint type according to pointer size

{\ttfamily \#include $<$types.\+h$>$}

\subsection{Detailed Description}
\subsubsection*{template$<$int PS$>$\newline
struct choose\+\_\+int\+\_\+types$<$ P\+S $>$}

template for choosing int/uint type according to pointer size

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{types_8h}{types.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/structchoose__int__types_3_014_01_4.tex
2017/01/24

\hypertarget{structchoose__int__types_3_014_01_4}{}\section{choose\+\_\+int\+\_\+types$<$ 4 $>$ Struct Template Reference}
\label{structchoose__int__types_3_014_01_4}\index{choose\+\_\+int\+\_\+types$<$ 4 $>$@{choose\+\_\+int\+\_\+types$<$ 4 $>$}}

PS = 4, int32/uint32.

{\ttfamily \#include $<$types.\+h$>$}

\subsection*{Public Types}
\begin{DoxyCompactItemize}
\item 
using \hyperlink{structchoose__int__types_3_014_01_4_af6cc8894e99e97c539077c9e640ed478}{int\+\_\+type} = \hyperlink{types_8h_a3d594eb72953c94a18a03d929ebd9167}{int32}
\item 
using \hyperlink{structchoose__int__types_3_014_01_4_a3c2319206150de67a68544e265dabb29}{uint\+\_\+type} = \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32}
\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$$>$\newline
struct choose\+\_\+int\+\_\+types$<$ 4 $>$}

PS = 4, int32/uint32.

32-\/bit operating system, support 32-\/bit address space

\subsection{Member Typedef Documentation}
\mbox{\Hypertarget{structchoose__int__types_3_014_01_4_af6cc8894e99e97c539077c9e640ed478}\label{structchoose__int__types_3_014_01_4_af6cc8894e99e97c539077c9e640ed478}} 
\index{choose\+\_\+int\+\_\+types$<$ 4 $>$@{choose\+\_\+int\+\_\+types$<$ 4 $>$}!int\+\_\+type@{int\+\_\+type}}
\index{int\+\_\+type@{int\+\_\+type}!choose\+\_\+int\+\_\+types$<$ 4 $>$@{choose\+\_\+int\+\_\+types$<$ 4 $>$}}
\subsubsection{\texorpdfstring{int\+\_\+type}{int\_type}}
{\footnotesize\ttfamily using \hyperlink{structchoose__int__types}{choose\+\_\+int\+\_\+types}$<$ 4 $>$\+::\hyperlink{structchoose__int__types_3_014_01_4_af6cc8894e99e97c539077c9e640ed478}{int\+\_\+type} =  \hyperlink{types_8h_a3d594eb72953c94a18a03d929ebd9167}{int32}}

\mbox{\Hypertarget{structchoose__int__types_3_014_01_4_a3c2319206150de67a68544e265dabb29}\label{structchoose__int__types_3_014_01_4_a3c2319206150de67a68544e265dabb29}} 
\index{choose\+\_\+int\+\_\+types$<$ 4 $>$@{choose\+\_\+int\+\_\+types$<$ 4 $>$}!uint\+\_\+type@{uint\+\_\+type}}
\index{uint\+\_\+type@{uint\+\_\+type}!choose\+\_\+int\+\_\+types$<$ 4 $>$@{choose\+\_\+int\+\_\+types$<$ 4 $>$}}
\subsubsection{\texorpdfstring{uint\+\_\+type}{uint\_type}}
{\footnotesize\ttfamily using \hyperlink{structchoose__int__types}{choose\+\_\+int\+\_\+types}$<$ 4 $>$\+::\hyperlink{structchoose__int__types_3_014_01_4_a3c2319206150de67a68544e265dabb29}{uint\+\_\+type} =  \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32}}

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{types_8h}{types.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/structchoose__int__types_3_018_01_4.tex
2017/01/24

\hypertarget{structchoose__int__types_3_018_01_4}{}\section{choose\+\_\+int\+\_\+types$<$ 8 $>$ Struct Template Reference}
\label{structchoose__int__types_3_018_01_4}\index{choose\+\_\+int\+\_\+types$<$ 8 $>$@{choose\+\_\+int\+\_\+types$<$ 8 $>$}}

pointer size = 8, 64-\/bit

{\ttfamily \#include $<$types.\+h$>$}

\subsection*{Public Types}
\begin{DoxyCompactItemize}
\item 
using \hyperlink{structchoose__int__types_3_018_01_4_a4dde5a87f22a82a381bbae5f6d205d05}{int\+\_\+type} = \hyperlink{types_8h_a552928ab323811c9694f5b7c9f53d0fb}{int64}
\item 
using \hyperlink{structchoose__int__types_3_018_01_4_a4e70f94b235eba865f95080e668f666a}{uint\+\_\+type} = \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}
\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$$>$\newline
struct choose\+\_\+int\+\_\+types$<$ 8 $>$}

pointer size = 8, 64-\/bit

64-\/bit operating system, support 64-\/bit address space

\subsection{Member Typedef Documentation}
\mbox{\Hypertarget{structchoose__int__types_3_018_01_4_a4dde5a87f22a82a381bbae5f6d205d05}\label{structchoose__int__types_3_018_01_4_a4dde5a87f22a82a381bbae5f6d205d05}} 
\index{choose\+\_\+int\+\_\+types$<$ 8 $>$@{choose\+\_\+int\+\_\+types$<$ 8 $>$}!int\+\_\+type@{int\+\_\+type}}
\index{int\+\_\+type@{int\+\_\+type}!choose\+\_\+int\+\_\+types$<$ 8 $>$@{choose\+\_\+int\+\_\+types$<$ 8 $>$}}
\subsubsection{\texorpdfstring{int\+\_\+type}{int\_type}}
{\footnotesize\ttfamily using \hyperlink{structchoose__int__types}{choose\+\_\+int\+\_\+types}$<$ 8 $>$\+::\hyperlink{structchoose__int__types_3_018_01_4_a4dde5a87f22a82a381bbae5f6d205d05}{int\+\_\+type} =  \hyperlink{types_8h_a552928ab323811c9694f5b7c9f53d0fb}{int64}}

\mbox{\Hypertarget{structchoose__int__types_3_018_01_4_a4e70f94b235eba865f95080e668f666a}\label{structchoose__int__types_3_018_01_4_a4e70f94b235eba865f95080e668f666a}} 
\index{choose\+\_\+int\+\_\+types$<$ 8 $>$@{choose\+\_\+int\+\_\+types$<$ 8 $>$}!uint\+\_\+type@{uint\+\_\+type}}
\index{uint\+\_\+type@{uint\+\_\+type}!choose\+\_\+int\+\_\+types$<$ 8 $>$@{choose\+\_\+int\+\_\+types$<$ 8 $>$}}
\subsubsection{\texorpdfstring{uint\+\_\+type}{uint\_type}}
{\footnotesize\ttfamily using \hyperlink{structchoose__int__types}{choose\+\_\+int\+\_\+types}$<$ 8 $>$\+::\hyperlink{structchoose__int__types_3_018_01_4_a4e70f94b235eba865f95080e668f666a}{uint\+\_\+type} =  \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64}}

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{types_8h}{types.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/structpair.tex
2017/01/24

\hypertarget{structpair}{}\section{pair$<$ T1, T2 $>$ Struct Template Reference}
\label{structpair}\index{pair$<$ T1, T2 $>$@{pair$<$ T1, T2 $>$}}

structure pair

{\ttfamily \#include $<$tuples.\+h$>$}

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{structpair_a1dba17bb5c888d7ed8ce7b7c4acc52de}{pair} ()
\begin{DoxyCompactList}\small\item\em constructor, default \end{DoxyCompactList}\item 
\hyperlink{structpair_ab75f77e9a1f726301f66d3be6b1e184a}{pair} (const \hyperlink{structpair}{pair} \&\+\_\+item)
\begin{DoxyCompactList}\small\item\em constructor, copy \end{DoxyCompactList}\item 
\hyperlink{structpair_a5674a7a5327419692abe6160ae202859}{pair} (const T1 \&\+\_\+first, const T2 \&\+\_\+second)
\begin{DoxyCompactList}\small\item\em constructor, component \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Static Public Member Functions}
\begin{DoxyCompactItemize}
\item 
static \hyperlink{structpair}{pair} \& \hyperlink{structpair_abca1ec29c5040ce16bd3993e80d42923}{min\+\_\+value} ()
\begin{DoxyCompactList}\small\item\em min value \end{DoxyCompactList}\item 
static \hyperlink{structpair}{pair} \& \hyperlink{structpair_a89b59c46e545a619e96c7bd5d66a8ef6}{max\+\_\+value} ()
\begin{DoxyCompactList}\small\item\em max vlaue \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Public Attributes}
\begin{DoxyCompactItemize}
\item 
T1 \hyperlink{structpair_aed925258783c91efbc5432030709d54e}{first}
\item 
T2 \hyperlink{structpair_a63ae1bbd5a6ce6bd6167b5359fa7a01f}{second}
\end{DoxyCompactItemize}
\subsection*{Friends}
\begin{DoxyCompactItemize}
\item 
std\+::ostream \& \hyperlink{structpair_a9cd7ed0b2b2d0a6d5977137d9cf35a0c}{operator$<$$<$} (std\+::ostream \+\_\+os, const \hyperlink{structpair}{pair} \&\+\_\+item)
\begin{DoxyCompactList}\small\item\em output \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename T1, typename T2$>$\newline
struct pair$<$ T1, T2 $>$}

structure pair

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{structpair_a1dba17bb5c888d7ed8ce7b7c4acc52de}\label{structpair_a1dba17bb5c888d7ed8ce7b7c4acc52de}} 
\index{pair@{pair}!pair@{pair}}
\index{pair@{pair}!pair@{pair}}
\subsubsection{\texorpdfstring{pair()}{pair()}\hspace{0.1cm}{\footnotesize\ttfamily [1/3]}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 $>$ \\
\hyperlink{structpair}{pair}$<$ T1, T2 $>$\+::\hyperlink{structpair}{pair} (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor, default

\mbox{\Hypertarget{structpair_ab75f77e9a1f726301f66d3be6b1e184a}\label{structpair_ab75f77e9a1f726301f66d3be6b1e184a}} 
\index{pair@{pair}!pair@{pair}}
\index{pair@{pair}!pair@{pair}}
\subsubsection{\texorpdfstring{pair()}{pair()}\hspace{0.1cm}{\footnotesize\ttfamily [2/3]}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 $>$ \\
\hyperlink{structpair}{pair}$<$ T1, T2 $>$\+::\hyperlink{structpair}{pair} (\begin{DoxyParamCaption}\item[{const \hyperlink{structpair}{pair}$<$ T1, T2 $>$ \&}]{\+\_\+item }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor, copy

\mbox{\Hypertarget{structpair_a5674a7a5327419692abe6160ae202859}\label{structpair_a5674a7a5327419692abe6160ae202859}} 
\index{pair@{pair}!pair@{pair}}
\index{pair@{pair}!pair@{pair}}
\subsubsection{\texorpdfstring{pair()}{pair()}\hspace{0.1cm}{\footnotesize\ttfamily [3/3]}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 $>$ \\
\hyperlink{structpair}{pair}$<$ T1, T2 $>$\+::\hyperlink{structpair}{pair} (\begin{DoxyParamCaption}\item[{const T1 \&}]{\+\_\+first,  }\item[{const T2 \&}]{\+\_\+second }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor, component

\subsection{Member Function Documentation}
\mbox{\Hypertarget{structpair_a89b59c46e545a619e96c7bd5d66a8ef6}\label{structpair_a89b59c46e545a619e96c7bd5d66a8ef6}} 
\index{pair@{pair}!max\+\_\+value@{max\+\_\+value}}
\index{max\+\_\+value@{max\+\_\+value}!pair@{pair}}
\subsubsection{\texorpdfstring{max\+\_\+value()}{max\_value()}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 $>$ \\
static \hyperlink{structpair}{pair}\& \hyperlink{structpair}{pair}$<$ T1, T2 $>$\+::max\+\_\+value (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [static]}}

max vlaue

\mbox{\Hypertarget{structpair_abca1ec29c5040ce16bd3993e80d42923}\label{structpair_abca1ec29c5040ce16bd3993e80d42923}} 
\index{pair@{pair}!min\+\_\+value@{min\+\_\+value}}
\index{min\+\_\+value@{min\+\_\+value}!pair@{pair}}
\subsubsection{\texorpdfstring{min\+\_\+value()}{min\_value()}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 $>$ \\
static \hyperlink{structpair}{pair}\& \hyperlink{structpair}{pair}$<$ T1, T2 $>$\+::min\+\_\+value (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [static]}}

min value

\subsection{Friends And Related Function Documentation}
\mbox{\Hypertarget{structpair_a9cd7ed0b2b2d0a6d5977137d9cf35a0c}\label{structpair_a9cd7ed0b2b2d0a6d5977137d9cf35a0c}} 
\index{pair@{pair}!operator$<$$<$@{operator$<$$<$}}
\index{operator$<$$<$@{operator$<$$<$}!pair@{pair}}
\subsubsection{\texorpdfstring{operator$<$$<$}{operator<<}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 $>$ \\
std\+::ostream\& operator$<$$<$ (\begin{DoxyParamCaption}\item[{std\+::ostream}]{\+\_\+os,  }\item[{const \hyperlink{structpair}{pair}$<$ T1, T2 $>$ \&}]{\+\_\+item }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [friend]}}

output

\subsection{Member Data Documentation}
\mbox{\Hypertarget{structpair_aed925258783c91efbc5432030709d54e}\label{structpair_aed925258783c91efbc5432030709d54e}} 
\index{pair@{pair}!first@{first}}
\index{first@{first}!pair@{pair}}
\subsubsection{\texorpdfstring{first}{first}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 $>$ \\
T1 \hyperlink{structpair}{pair}$<$ T1, T2 $>$\+::first}

\mbox{\Hypertarget{structpair_a63ae1bbd5a6ce6bd6167b5359fa7a01f}\label{structpair_a63ae1bbd5a6ce6bd6167b5359fa7a01f}} 
\index{pair@{pair}!second@{second}}
\index{second@{second}!pair@{pair}}
\subsubsection{\texorpdfstring{second}{second}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 $>$ \\
T2 \hyperlink{structpair}{pair}$<$ T1, T2 $>$\+::second}

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{tuples_8h}{tuples.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/structquadruple.tex
2017/01/24

\hypertarget{structquadruple}{}\section{quadruple$<$ T1, T2, T3, T4 $>$ Struct Template Reference}
\label{structquadruple}\index{quadruple$<$ T1, T2, T3, T4 $>$@{quadruple$<$ T1, T2, T3, T4 $>$}}

structure quadruple

{\ttfamily \#include $<$tuples.\+h$>$}

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{structquadruple_ab4b318f9f20c5f861c0b7445bf806da8}{quadruple} ()
\begin{DoxyCompactList}\small\item\em constructor, default \end{DoxyCompactList}\item 
\hyperlink{structquadruple_a24c753a7c00f8325bf7f738815e89d06}{quadruple} (const \hyperlink{structquadruple}{quadruple} \&\+\_\+item)
\begin{DoxyCompactList}\small\item\em constructor, copy \end{DoxyCompactList}\item 
\hyperlink{structquadruple_a23034a914f2841aa59c833bb3923f1b6}{quadruple} (const T1 \&\+\_\+first, const T2 \&\+\_\+second, const T3 \&\+\_\+third, const T4 \&\+\_\+forth)
\begin{DoxyCompactList}\small\item\em constructor, component \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Static Public Member Functions}
\begin{DoxyCompactItemize}
\item 
static \hyperlink{structquadruple}{quadruple} \& \hyperlink{structquadruple_a97a2767881ac4cfb52513827b4f51588}{min\+\_\+value} ()
\begin{DoxyCompactList}\small\item\em min value \end{DoxyCompactList}\item 
static \hyperlink{structquadruple}{quadruple} \& \hyperlink{structquadruple_a1361dd9869f7323e5fc33ab07864e128}{max\+\_\+value} ()
\begin{DoxyCompactList}\small\item\em max value \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Public Attributes}
\begin{DoxyCompactItemize}
\item 
T1 \hyperlink{structquadruple_a45642eeda831800cd5c540037822ac65}{first}
\item 
T2 \hyperlink{structquadruple_aa93ca1ef60012d07903333d7b16bb32b}{second}
\item 
T3 \hyperlink{structquadruple_af1ada0ce5f85bbc7df2c5bfb113b442d}{third}
\item 
T4 \hyperlink{structquadruple_abab1a25fd1ed39d2605eaa9371de04ca}{forth}
\end{DoxyCompactItemize}
\subsection*{Friends}
\begin{DoxyCompactItemize}
\item 
std\+::ostream \& \hyperlink{structquadruple_af619be80f82068b7b05a8d943196f024}{operator$<$$<$} (std\+::ostream \+\_\+os, const \hyperlink{structquadruple}{quadruple} \&\+\_\+item)
\begin{DoxyCompactList}\small\item\em output \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename T1, typename T2, typename T3, typename T4$>$\newline
struct quadruple$<$ T1, T2, T3, T4 $>$}

structure quadruple

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{structquadruple_ab4b318f9f20c5f861c0b7445bf806da8}\label{structquadruple_ab4b318f9f20c5f861c0b7445bf806da8}} 
\index{quadruple@{quadruple}!quadruple@{quadruple}}
\index{quadruple@{quadruple}!quadruple@{quadruple}}
\subsubsection{\texorpdfstring{quadruple()}{quadruple()}\hspace{0.1cm}{\footnotesize\ttfamily [1/3]}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 , typename T4 $>$ \\
\hyperlink{structquadruple}{quadruple}$<$ T1, T2, T3, T4 $>$\+::\hyperlink{structquadruple}{quadruple} (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor, default

\mbox{\Hypertarget{structquadruple_a24c753a7c00f8325bf7f738815e89d06}\label{structquadruple_a24c753a7c00f8325bf7f738815e89d06}} 
\index{quadruple@{quadruple}!quadruple@{quadruple}}
\index{quadruple@{quadruple}!quadruple@{quadruple}}
\subsubsection{\texorpdfstring{quadruple()}{quadruple()}\hspace{0.1cm}{\footnotesize\ttfamily [2/3]}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 , typename T4 $>$ \\
\hyperlink{structquadruple}{quadruple}$<$ T1, T2, T3, T4 $>$\+::\hyperlink{structquadruple}{quadruple} (\begin{DoxyParamCaption}\item[{const \hyperlink{structquadruple}{quadruple}$<$ T1, T2, T3, T4 $>$ \&}]{\+\_\+item }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor, copy

\mbox{\Hypertarget{structquadruple_a23034a914f2841aa59c833bb3923f1b6}\label{structquadruple_a23034a914f2841aa59c833bb3923f1b6}} 
\index{quadruple@{quadruple}!quadruple@{quadruple}}
\index{quadruple@{quadruple}!quadruple@{quadruple}}
\subsubsection{\texorpdfstring{quadruple()}{quadruple()}\hspace{0.1cm}{\footnotesize\ttfamily [3/3]}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 , typename T4 $>$ \\
\hyperlink{structquadruple}{quadruple}$<$ T1, T2, T3, T4 $>$\+::\hyperlink{structquadruple}{quadruple} (\begin{DoxyParamCaption}\item[{const T1 \&}]{\+\_\+first,  }\item[{const T2 \&}]{\+\_\+second,  }\item[{const T3 \&}]{\+\_\+third,  }\item[{const T4 \&}]{\+\_\+forth }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor, component

\subsection{Member Function Documentation}
\mbox{\Hypertarget{structquadruple_a1361dd9869f7323e5fc33ab07864e128}\label{structquadruple_a1361dd9869f7323e5fc33ab07864e128}} 
\index{quadruple@{quadruple}!max\+\_\+value@{max\+\_\+value}}
\index{max\+\_\+value@{max\+\_\+value}!quadruple@{quadruple}}
\subsubsection{\texorpdfstring{max\+\_\+value()}{max\_value()}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 , typename T4 $>$ \\
static \hyperlink{structquadruple}{quadruple}\& \hyperlink{structquadruple}{quadruple}$<$ T1, T2, T3, T4 $>$\+::max\+\_\+value (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [static]}}

max value

\mbox{\Hypertarget{structquadruple_a97a2767881ac4cfb52513827b4f51588}\label{structquadruple_a97a2767881ac4cfb52513827b4f51588}} 
\index{quadruple@{quadruple}!min\+\_\+value@{min\+\_\+value}}
\index{min\+\_\+value@{min\+\_\+value}!quadruple@{quadruple}}
\subsubsection{\texorpdfstring{min\+\_\+value()}{min\_value()}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 , typename T4 $>$ \\
static \hyperlink{structquadruple}{quadruple}\& \hyperlink{structquadruple}{quadruple}$<$ T1, T2, T3, T4 $>$\+::min\+\_\+value (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [static]}}

min value

\subsection{Friends And Related Function Documentation}
\mbox{\Hypertarget{structquadruple_af619be80f82068b7b05a8d943196f024}\label{structquadruple_af619be80f82068b7b05a8d943196f024}} 
\index{quadruple@{quadruple}!operator$<$$<$@{operator$<$$<$}}
\index{operator$<$$<$@{operator$<$$<$}!quadruple@{quadruple}}
\subsubsection{\texorpdfstring{operator$<$$<$}{operator<<}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 , typename T4 $>$ \\
std\+::ostream\& operator$<$$<$ (\begin{DoxyParamCaption}\item[{std\+::ostream}]{\+\_\+os,  }\item[{const \hyperlink{structquadruple}{quadruple}$<$ T1, T2, T3, T4 $>$ \&}]{\+\_\+item }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [friend]}}

output

\subsection{Member Data Documentation}
\mbox{\Hypertarget{structquadruple_a45642eeda831800cd5c540037822ac65}\label{structquadruple_a45642eeda831800cd5c540037822ac65}} 
\index{quadruple@{quadruple}!first@{first}}
\index{first@{first}!quadruple@{quadruple}}
\subsubsection{\texorpdfstring{first}{first}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 , typename T4 $>$ \\
T1 \hyperlink{structquadruple}{quadruple}$<$ T1, T2, T3, T4 $>$\+::first}

\mbox{\Hypertarget{structquadruple_abab1a25fd1ed39d2605eaa9371de04ca}\label{structquadruple_abab1a25fd1ed39d2605eaa9371de04ca}} 
\index{quadruple@{quadruple}!forth@{forth}}
\index{forth@{forth}!quadruple@{quadruple}}
\subsubsection{\texorpdfstring{forth}{forth}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 , typename T4 $>$ \\
T4 \hyperlink{structquadruple}{quadruple}$<$ T1, T2, T3, T4 $>$\+::forth}

\mbox{\Hypertarget{structquadruple_aa93ca1ef60012d07903333d7b16bb32b}\label{structquadruple_aa93ca1ef60012d07903333d7b16bb32b}} 
\index{quadruple@{quadruple}!second@{second}}
\index{second@{second}!quadruple@{quadruple}}
\subsubsection{\texorpdfstring{second}{second}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 , typename T4 $>$ \\
T2 \hyperlink{structquadruple}{quadruple}$<$ T1, T2, T3, T4 $>$\+::second}

\mbox{\Hypertarget{structquadruple_af1ada0ce5f85bbc7df2c5bfb113b442d}\label{structquadruple_af1ada0ce5f85bbc7df2c5bfb113b442d}} 
\index{quadruple@{quadruple}!third@{third}}
\index{third@{third}!quadruple@{quadruple}}
\subsubsection{\texorpdfstring{third}{third}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 , typename T4 $>$ \\
T3 \hyperlink{structquadruple}{quadruple}$<$ T1, T2, T3, T4 $>$\+::third}

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{tuples_8h}{tuples.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/structtriple.tex
2017/01/24

\hypertarget{structtriple}{}\section{triple$<$ T1, T2, T3 $>$ Struct Template Reference}
\label{structtriple}\index{triple$<$ T1, T2, T3 $>$@{triple$<$ T1, T2, T3 $>$}}

structure triple

{\ttfamily \#include $<$tuples.\+h$>$}

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hyperlink{structtriple_a3bdf8136df773fff422b4cbb354cf749}{triple} ()
\begin{DoxyCompactList}\small\item\em constructor, default \end{DoxyCompactList}\item 
\hyperlink{structtriple_a88688d689a93bf4b8a25bc29728a53b5}{triple} (const \hyperlink{structtriple}{triple} \&\+\_\+item)
\begin{DoxyCompactList}\small\item\em constructor, copy \end{DoxyCompactList}\item 
\hyperlink{structtriple_ac34fdb8619fdc11fb442e2058d35d840}{triple} (const T1 \&\+\_\+first, const T2 \&\+\_\+second, const T3 \&\+\_\+third)
\begin{DoxyCompactList}\small\item\em constructor, component \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Static Public Member Functions}
\begin{DoxyCompactItemize}
\item 
static \hyperlink{structtriple}{triple} \& \hyperlink{structtriple_a91d8338063226b63eea74e56377a162b}{min\+\_\+value} ()
\begin{DoxyCompactList}\small\item\em min value \end{DoxyCompactList}\item 
static \hyperlink{structtriple}{triple} \& \hyperlink{structtriple_a73d954bee19bf6493205e794a6448e8f}{max\+\_\+value} ()
\begin{DoxyCompactList}\small\item\em max value \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Public Attributes}
\begin{DoxyCompactItemize}
\item 
T1 \hyperlink{structtriple_a6aa8508e6e6f859dda04f144f361c0d2}{first}
\item 
T2 \hyperlink{structtriple_a41050194c8c7984707c7ad13c96e8631}{second}
\item 
T3 \hyperlink{structtriple_a5675f08ea7996033edbcf7074404cdd8}{third}
\end{DoxyCompactItemize}
\subsection*{Friends}
\begin{DoxyCompactItemize}
\item 
std\+::ostream \& \hyperlink{structtriple_a213e2d21647f20d6287690438970f212}{operator$<$$<$} (std\+::ostream \+\_\+os, const \hyperlink{structtriple}{triple} \&\+\_\+item)
\begin{DoxyCompactList}\small\item\em output \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename T1, typename T2, typename T3$>$\newline
struct triple$<$ T1, T2, T3 $>$}

structure triple

\subsection{Constructor \& Destructor Documentation}
\mbox{\Hypertarget{structtriple_a3bdf8136df773fff422b4cbb354cf749}\label{structtriple_a3bdf8136df773fff422b4cbb354cf749}} 
\index{triple@{triple}!triple@{triple}}
\index{triple@{triple}!triple@{triple}}
\subsubsection{\texorpdfstring{triple()}{triple()}\hspace{0.1cm}{\footnotesize\ttfamily [1/3]}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 $>$ \\
\hyperlink{structtriple}{triple}$<$ T1, T2, T3 $>$\+::\hyperlink{structtriple}{triple} (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor, default

\mbox{\Hypertarget{structtriple_a88688d689a93bf4b8a25bc29728a53b5}\label{structtriple_a88688d689a93bf4b8a25bc29728a53b5}} 
\index{triple@{triple}!triple@{triple}}
\index{triple@{triple}!triple@{triple}}
\subsubsection{\texorpdfstring{triple()}{triple()}\hspace{0.1cm}{\footnotesize\ttfamily [2/3]}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 $>$ \\
\hyperlink{structtriple}{triple}$<$ T1, T2, T3 $>$\+::\hyperlink{structtriple}{triple} (\begin{DoxyParamCaption}\item[{const \hyperlink{structtriple}{triple}$<$ T1, T2, T3 $>$ \&}]{\+\_\+item }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor, copy

\mbox{\Hypertarget{structtriple_ac34fdb8619fdc11fb442e2058d35d840}\label{structtriple_ac34fdb8619fdc11fb442e2058d35d840}} 
\index{triple@{triple}!triple@{triple}}
\index{triple@{triple}!triple@{triple}}
\subsubsection{\texorpdfstring{triple()}{triple()}\hspace{0.1cm}{\footnotesize\ttfamily [3/3]}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 $>$ \\
\hyperlink{structtriple}{triple}$<$ T1, T2, T3 $>$\+::\hyperlink{structtriple}{triple} (\begin{DoxyParamCaption}\item[{const T1 \&}]{\+\_\+first,  }\item[{const T2 \&}]{\+\_\+second,  }\item[{const T3 \&}]{\+\_\+third }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}}

constructor, component

\subsection{Member Function Documentation}
\mbox{\Hypertarget{structtriple_a73d954bee19bf6493205e794a6448e8f}\label{structtriple_a73d954bee19bf6493205e794a6448e8f}} 
\index{triple@{triple}!max\+\_\+value@{max\+\_\+value}}
\index{max\+\_\+value@{max\+\_\+value}!triple@{triple}}
\subsubsection{\texorpdfstring{max\+\_\+value()}{max\_value()}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 $>$ \\
static \hyperlink{structtriple}{triple}\& \hyperlink{structtriple}{triple}$<$ T1, T2, T3 $>$\+::max\+\_\+value (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [static]}}

max value

\mbox{\Hypertarget{structtriple_a91d8338063226b63eea74e56377a162b}\label{structtriple_a91d8338063226b63eea74e56377a162b}} 
\index{triple@{triple}!min\+\_\+value@{min\+\_\+value}}
\index{min\+\_\+value@{min\+\_\+value}!triple@{triple}}
\subsubsection{\texorpdfstring{min\+\_\+value()}{min\_value()}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 $>$ \\
static \hyperlink{structtriple}{triple}\& \hyperlink{structtriple}{triple}$<$ T1, T2, T3 $>$\+::min\+\_\+value (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [inline]}, {\ttfamily [static]}}

min value

\subsection{Friends And Related Function Documentation}
\mbox{\Hypertarget{structtriple_a213e2d21647f20d6287690438970f212}\label{structtriple_a213e2d21647f20d6287690438970f212}} 
\index{triple@{triple}!operator$<$$<$@{operator$<$$<$}}
\index{operator$<$$<$@{operator$<$$<$}!triple@{triple}}
\subsubsection{\texorpdfstring{operator$<$$<$}{operator<<}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 $>$ \\
std\+::ostream\& operator$<$$<$ (\begin{DoxyParamCaption}\item[{std\+::ostream}]{\+\_\+os,  }\item[{const \hyperlink{structtriple}{triple}$<$ T1, T2, T3 $>$ \&}]{\+\_\+item }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [friend]}}

output

\subsection{Member Data Documentation}
\mbox{\Hypertarget{structtriple_a6aa8508e6e6f859dda04f144f361c0d2}\label{structtriple_a6aa8508e6e6f859dda04f144f361c0d2}} 
\index{triple@{triple}!first@{first}}
\index{first@{first}!triple@{triple}}
\subsubsection{\texorpdfstring{first}{first}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 $>$ \\
T1 \hyperlink{structtriple}{triple}$<$ T1, T2, T3 $>$\+::first}

\mbox{\Hypertarget{structtriple_a41050194c8c7984707c7ad13c96e8631}\label{structtriple_a41050194c8c7984707c7ad13c96e8631}} 
\index{triple@{triple}!second@{second}}
\index{second@{second}!triple@{triple}}
\subsubsection{\texorpdfstring{second}{second}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 $>$ \\
T2 \hyperlink{structtriple}{triple}$<$ T1, T2, T3 $>$\+::second}

\mbox{\Hypertarget{structtriple_a5675f08ea7996033edbcf7074404cdd8}\label{structtriple_a5675f08ea7996033edbcf7074404cdd8}} 
\index{triple@{triple}!third@{third}}
\index{third@{third}!triple@{triple}}
\subsubsection{\texorpdfstring{third}{third}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 $>$ \\
T3 \hyperlink{structtriple}{triple}$<$ T1, T2, T3 $>$\+::third}

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{tuples_8h}{tuples.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/structtuple__great__comparator__1st.tex
2017/01/24

\hypertarget{structtuple__great__comparator__1st}{}\section{tuple\+\_\+great\+\_\+comparator\+\_\+1st$<$ tuple\+\_\+type $>$ Struct Template Reference}
\label{structtuple__great__comparator__1st}\index{tuple\+\_\+great\+\_\+comparator\+\_\+1st$<$ tuple\+\_\+type $>$@{tuple\+\_\+great\+\_\+comparator\+\_\+1st$<$ tuple\+\_\+type $>$}}

function object for comparing tuples by their first component in ascending order

{\ttfamily \#include $<$widget.\+h$>$}

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
bool \hyperlink{structtuple__great__comparator__1st_ab62e5503d2af02a4f2383b54217659bb}{operator()} (const tuple\+\_\+type \&\+\_\+a, const tuple\+\_\+type \&\+\_\+b) const
\item 
tuple\+\_\+type \hyperlink{structtuple__great__comparator__1st_a92e31ba8514dbfb3a98e9bf9fdccaf31}{min\+\_\+value} () const
\begin{DoxyCompactList}\small\item\em min value \end{DoxyCompactList}\item 
tuple\+\_\+type \hyperlink{structtuple__great__comparator__1st_ace19155455686003f7a67d51d5bb799b}{max\+\_\+value} () const
\begin{DoxyCompactList}\small\item\em max value \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename tuple\+\_\+type$>$\newline
struct tuple\+\_\+great\+\_\+comparator\+\_\+1st$<$ tuple\+\_\+type $>$}

function object for comparing tuples by their first component in ascending order

\subsection{Member Function Documentation}
\mbox{\Hypertarget{structtuple__great__comparator__1st_ace19155455686003f7a67d51d5bb799b}\label{structtuple__great__comparator__1st_ace19155455686003f7a67d51d5bb799b}} 
\index{tuple\+\_\+great\+\_\+comparator\+\_\+1st@{tuple\+\_\+great\+\_\+comparator\+\_\+1st}!max\+\_\+value@{max\+\_\+value}}
\index{max\+\_\+value@{max\+\_\+value}!tuple\+\_\+great\+\_\+comparator\+\_\+1st@{tuple\+\_\+great\+\_\+comparator\+\_\+1st}}
\subsubsection{\texorpdfstring{max\+\_\+value()}{max\_value()}}
{\footnotesize\ttfamily template$<$typename tuple\+\_\+type $>$ \\
tuple\+\_\+type \hyperlink{structtuple__great__comparator__1st}{tuple\+\_\+great\+\_\+comparator\+\_\+1st}$<$ tuple\+\_\+type $>$\+::max\+\_\+value (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

max value

\mbox{\Hypertarget{structtuple__great__comparator__1st_a92e31ba8514dbfb3a98e9bf9fdccaf31}\label{structtuple__great__comparator__1st_a92e31ba8514dbfb3a98e9bf9fdccaf31}} 
\index{tuple\+\_\+great\+\_\+comparator\+\_\+1st@{tuple\+\_\+great\+\_\+comparator\+\_\+1st}!min\+\_\+value@{min\+\_\+value}}
\index{min\+\_\+value@{min\+\_\+value}!tuple\+\_\+great\+\_\+comparator\+\_\+1st@{tuple\+\_\+great\+\_\+comparator\+\_\+1st}}
\subsubsection{\texorpdfstring{min\+\_\+value()}{min\_value()}}
{\footnotesize\ttfamily template$<$typename tuple\+\_\+type $>$ \\
tuple\+\_\+type \hyperlink{structtuple__great__comparator__1st}{tuple\+\_\+great\+\_\+comparator\+\_\+1st}$<$ tuple\+\_\+type $>$\+::min\+\_\+value (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

min value

\mbox{\Hypertarget{structtuple__great__comparator__1st_ab62e5503d2af02a4f2383b54217659bb}\label{structtuple__great__comparator__1st_ab62e5503d2af02a4f2383b54217659bb}} 
\index{tuple\+\_\+great\+\_\+comparator\+\_\+1st@{tuple\+\_\+great\+\_\+comparator\+\_\+1st}!operator()@{operator()}}
\index{operator()@{operator()}!tuple\+\_\+great\+\_\+comparator\+\_\+1st@{tuple\+\_\+great\+\_\+comparator\+\_\+1st}}
\subsubsection{\texorpdfstring{operator()()}{operator()()}}
{\footnotesize\ttfamily template$<$typename tuple\+\_\+type $>$ \\
bool \hyperlink{structtuple__great__comparator__1st}{tuple\+\_\+great\+\_\+comparator\+\_\+1st}$<$ tuple\+\_\+type $>$\+::operator() (\begin{DoxyParamCaption}\item[{const tuple\+\_\+type \&}]{\+\_\+a,  }\item[{const tuple\+\_\+type \&}]{\+\_\+b }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{widget_8h}{widget.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/structtuple__less__comparator__1st.tex
2017/01/24

\hypertarget{structtuple__less__comparator__1st}{}\section{tuple\+\_\+less\+\_\+comparator\+\_\+1st$<$ tuple\+\_\+type $>$ Struct Template Reference}
\label{structtuple__less__comparator__1st}\index{tuple\+\_\+less\+\_\+comparator\+\_\+1st$<$ tuple\+\_\+type $>$@{tuple\+\_\+less\+\_\+comparator\+\_\+1st$<$ tuple\+\_\+type $>$}}

function object for comparing tuples by their first component in ascending order

{\ttfamily \#include $<$widget.\+h$>$}

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
bool \hyperlink{structtuple__less__comparator__1st_ad97f49eea57d8fec456d9d00a5126deb}{operator()} (const tuple\+\_\+type \&\+\_\+a, const tuple\+\_\+type \&\+\_\+b) const
\item 
tuple\+\_\+type \hyperlink{structtuple__less__comparator__1st_a1dc22790efdf3705634387a96a848d89}{min\+\_\+value} () const
\begin{DoxyCompactList}\small\item\em min value \end{DoxyCompactList}\item 
tuple\+\_\+type \hyperlink{structtuple__less__comparator__1st_ab43723d6ebd5e36767f98828e2df83a8}{max\+\_\+value} () const
\begin{DoxyCompactList}\small\item\em max value \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename tuple\+\_\+type$>$\newline
struct tuple\+\_\+less\+\_\+comparator\+\_\+1st$<$ tuple\+\_\+type $>$}

function object for comparing tuples by their first component in ascending order

\subsection{Member Function Documentation}
\mbox{\Hypertarget{structtuple__less__comparator__1st_ab43723d6ebd5e36767f98828e2df83a8}\label{structtuple__less__comparator__1st_ab43723d6ebd5e36767f98828e2df83a8}} 
\index{tuple\+\_\+less\+\_\+comparator\+\_\+1st@{tuple\+\_\+less\+\_\+comparator\+\_\+1st}!max\+\_\+value@{max\+\_\+value}}
\index{max\+\_\+value@{max\+\_\+value}!tuple\+\_\+less\+\_\+comparator\+\_\+1st@{tuple\+\_\+less\+\_\+comparator\+\_\+1st}}
\subsubsection{\texorpdfstring{max\+\_\+value()}{max\_value()}}
{\footnotesize\ttfamily template$<$typename tuple\+\_\+type $>$ \\
tuple\+\_\+type \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$ tuple\+\_\+type $>$\+::max\+\_\+value (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

max value

\mbox{\Hypertarget{structtuple__less__comparator__1st_a1dc22790efdf3705634387a96a848d89}\label{structtuple__less__comparator__1st_a1dc22790efdf3705634387a96a848d89}} 
\index{tuple\+\_\+less\+\_\+comparator\+\_\+1st@{tuple\+\_\+less\+\_\+comparator\+\_\+1st}!min\+\_\+value@{min\+\_\+value}}
\index{min\+\_\+value@{min\+\_\+value}!tuple\+\_\+less\+\_\+comparator\+\_\+1st@{tuple\+\_\+less\+\_\+comparator\+\_\+1st}}
\subsubsection{\texorpdfstring{min\+\_\+value()}{min\_value()}}
{\footnotesize\ttfamily template$<$typename tuple\+\_\+type $>$ \\
tuple\+\_\+type \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$ tuple\+\_\+type $>$\+::min\+\_\+value (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

min value

\mbox{\Hypertarget{structtuple__less__comparator__1st_ad97f49eea57d8fec456d9d00a5126deb}\label{structtuple__less__comparator__1st_ad97f49eea57d8fec456d9d00a5126deb}} 
\index{tuple\+\_\+less\+\_\+comparator\+\_\+1st@{tuple\+\_\+less\+\_\+comparator\+\_\+1st}!operator()@{operator()}}
\index{operator()@{operator()}!tuple\+\_\+less\+\_\+comparator\+\_\+1st@{tuple\+\_\+less\+\_\+comparator\+\_\+1st}}
\subsubsection{\texorpdfstring{operator()()}{operator()()}}
{\footnotesize\ttfamily template$<$typename tuple\+\_\+type $>$ \\
bool \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st}$<$ tuple\+\_\+type $>$\+::operator() (\begin{DoxyParamCaption}\item[{const tuple\+\_\+type \&}]{\+\_\+a,  }\item[{const tuple\+\_\+type \&}]{\+\_\+b }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{widget_8h}{widget.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/structtuple__less__comparator__2nd.tex
2017/01/24

\hypertarget{structtuple__less__comparator__2nd}{}\section{tuple\+\_\+less\+\_\+comparator\+\_\+2nd$<$ tuple\+\_\+type $>$ Struct Template Reference}
\label{structtuple__less__comparator__2nd}\index{tuple\+\_\+less\+\_\+comparator\+\_\+2nd$<$ tuple\+\_\+type $>$@{tuple\+\_\+less\+\_\+comparator\+\_\+2nd$<$ tuple\+\_\+type $>$}}

function object for comparing tuples by their first two component in ascending order

{\ttfamily \#include $<$widget.\+h$>$}

\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
bool \hyperlink{structtuple__less__comparator__2nd_a323236eaaac70cda8e4c7ccbfde17fc2}{operator()} (const tuple\+\_\+type \&\+\_\+a, const tuple\+\_\+type \&\+\_\+b) const
\item 
tuple\+\_\+type \hyperlink{structtuple__less__comparator__2nd_a9b508a5f80bfb71efd337db16683ec7a}{min\+\_\+value} () const
\begin{DoxyCompactList}\small\item\em min value \end{DoxyCompactList}\item 
tuple\+\_\+type \hyperlink{structtuple__less__comparator__2nd_aaf46814db637befeda6a9225723a59f6}{max\+\_\+value} () const
\begin{DoxyCompactList}\small\item\em max value \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$typename tuple\+\_\+type$>$\newline
struct tuple\+\_\+less\+\_\+comparator\+\_\+2nd$<$ tuple\+\_\+type $>$}

function object for comparing tuples by their first two component in ascending order

\subsection{Member Function Documentation}
\mbox{\Hypertarget{structtuple__less__comparator__2nd_aaf46814db637befeda6a9225723a59f6}\label{structtuple__less__comparator__2nd_aaf46814db637befeda6a9225723a59f6}} 
\index{tuple\+\_\+less\+\_\+comparator\+\_\+2nd@{tuple\+\_\+less\+\_\+comparator\+\_\+2nd}!max\+\_\+value@{max\+\_\+value}}
\index{max\+\_\+value@{max\+\_\+value}!tuple\+\_\+less\+\_\+comparator\+\_\+2nd@{tuple\+\_\+less\+\_\+comparator\+\_\+2nd}}
\subsubsection{\texorpdfstring{max\+\_\+value()}{max\_value()}}
{\footnotesize\ttfamily template$<$typename tuple\+\_\+type $>$ \\
tuple\+\_\+type \hyperlink{structtuple__less__comparator__2nd}{tuple\+\_\+less\+\_\+comparator\+\_\+2nd}$<$ tuple\+\_\+type $>$\+::max\+\_\+value (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

max value

\mbox{\Hypertarget{structtuple__less__comparator__2nd_a9b508a5f80bfb71efd337db16683ec7a}\label{structtuple__less__comparator__2nd_a9b508a5f80bfb71efd337db16683ec7a}} 
\index{tuple\+\_\+less\+\_\+comparator\+\_\+2nd@{tuple\+\_\+less\+\_\+comparator\+\_\+2nd}!min\+\_\+value@{min\+\_\+value}}
\index{min\+\_\+value@{min\+\_\+value}!tuple\+\_\+less\+\_\+comparator\+\_\+2nd@{tuple\+\_\+less\+\_\+comparator\+\_\+2nd}}
\subsubsection{\texorpdfstring{min\+\_\+value()}{min\_value()}}
{\footnotesize\ttfamily template$<$typename tuple\+\_\+type $>$ \\
tuple\+\_\+type \hyperlink{structtuple__less__comparator__2nd}{tuple\+\_\+less\+\_\+comparator\+\_\+2nd}$<$ tuple\+\_\+type $>$\+::min\+\_\+value (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

min value

\mbox{\Hypertarget{structtuple__less__comparator__2nd_a323236eaaac70cda8e4c7ccbfde17fc2}\label{structtuple__less__comparator__2nd_a323236eaaac70cda8e4c7ccbfde17fc2}} 
\index{tuple\+\_\+less\+\_\+comparator\+\_\+2nd@{tuple\+\_\+less\+\_\+comparator\+\_\+2nd}!operator()@{operator()}}
\index{operator()@{operator()}!tuple\+\_\+less\+\_\+comparator\+\_\+2nd@{tuple\+\_\+less\+\_\+comparator\+\_\+2nd}}
\subsubsection{\texorpdfstring{operator()()}{operator()()}}
{\footnotesize\ttfamily template$<$typename tuple\+\_\+type $>$ \\
bool \hyperlink{structtuple__less__comparator__2nd}{tuple\+\_\+less\+\_\+comparator\+\_\+2nd}$<$ tuple\+\_\+type $>$\+::operator() (\begin{DoxyParamCaption}\item[{const tuple\+\_\+type \&}]{\+\_\+a,  }\item[{const tuple\+\_\+type \&}]{\+\_\+b }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
code/src/common/\hyperlink{widget_8h}{widget.\+h}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/test_8h.tex
2017/01/24

\hypertarget{test_8h}{}\section{code/src/test.h File Reference}
\label{test_8h}\index{code/src/test.\+h@{code/src/test.\+h}}
{\ttfamily \#include \char`\"{}common/common.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}common/tuples.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}common/widget.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}common/basicio.\+h\char`\"{}}\newline
\subsection*{Classes}
\begin{DoxyCompactItemize}
\item 
class \hyperlink{class_test}{Test$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$}
\end{DoxyCompactItemize}
\subsection*{Macros}
\begin{DoxyCompactItemize}
\item 
\#define \hyperlink{test_8h_aa8de6ad987cfa13b647db341b8dcc510}{\+\_\+\+T\+E\+S\+T\+\_\+H}
\end{DoxyCompactItemize}

\subsection{Macro Definition Documentation}
\mbox{\Hypertarget{test_8h_aa8de6ad987cfa13b647db341b8dcc510}\label{test_8h_aa8de6ad987cfa13b647db341b8dcc510}} 
\index{test.\+h@{test.\+h}!\+\_\+\+T\+E\+S\+T\+\_\+H@{\+\_\+\+T\+E\+S\+T\+\_\+H}}
\index{\+\_\+\+T\+E\+S\+T\+\_\+H@{\+\_\+\+T\+E\+S\+T\+\_\+H}!test.\+h@{test.\+h}}
\subsubsection{\texorpdfstring{\+\_\+\+T\+E\+S\+T\+\_\+H}{\_TEST\_H}}
{\footnotesize\ttfamily \#define \+\_\+\+T\+E\+S\+T\+\_\+H}

### 2017-01-24 archive/latex/tuples_8h.tex
2017/01/24

\hypertarget{tuples_8h}{}\section{code/src/common/tuples.h File Reference}
\label{tuples_8h}\index{code/src/common/tuples.\+h@{code/src/common/tuples.\+h}}
\subsection*{Classes}
\begin{DoxyCompactItemize}
\item 
struct \hyperlink{structpair}{pair$<$ T1, T2 $>$}
\begin{DoxyCompactList}\small\item\em structure pair \end{DoxyCompactList}\item 
struct \hyperlink{structtriple}{triple$<$ T1, T2, T3 $>$}
\begin{DoxyCompactList}\small\item\em structure triple \end{DoxyCompactList}\item 
struct \hyperlink{structquadruple}{quadruple$<$ T1, T2, T3, T4 $>$}
\begin{DoxyCompactList}\small\item\em structure quadruple \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Functions}
\begin{DoxyCompactItemize}
\item 
{\footnotesize template$<$typename T1 , typename T2 $>$ }\\struct \hyperlink{structpair}{pair} \hyperlink{tuples_8h_a3287af29b6ef2cbe75f1caba87bdde63}{\+\_\+\+\_\+attribute\+\_\+\+\_\+} ((packed))
\item 
\hyperlink{tuples_8h_a861a18bf6751dab7e644b4c4858d3548}{pair} ()
\begin{DoxyCompactList}\small\item\em constructor, default \end{DoxyCompactList}\item 
\hyperlink{tuples_8h_ad95635b05637a43806af080d9ec581ba}{pair} (const \hyperlink{structpair}{pair} \&\+\_\+item)
\begin{DoxyCompactList}\small\item\em constructor, copy \end{DoxyCompactList}\item 
\hyperlink{tuples_8h_a80f1b898df1006722612d5ecf89cd4d7}{pair} (const T1 \&\+\_\+first, const T2 \&\+\_\+second)
\begin{DoxyCompactList}\small\item\em constructor, component \end{DoxyCompactList}\item 
static \hyperlink{structpair}{pair} \& \hyperlink{tuples_8h_ac8a41d1a11f39ac2d9916b2248d76d5d}{min\+\_\+value} ()
\begin{DoxyCompactList}\small\item\em min value \end{DoxyCompactList}\item 
static \hyperlink{structpair}{pair} \& \hyperlink{tuples_8h_abc17aed069c35187f4d6f8b05c506300}{max\+\_\+value} ()
\begin{DoxyCompactList}\small\item\em max vlaue \end{DoxyCompactList}\item 
std\+::ostream \& \hyperlink{tuples_8h_a068f246e1ab74655cd80c5d32b347a20}{operator$<$$<$} (std\+::ostream \+\_\+os, const \hyperlink{structpair}{pair} \&\+\_\+item)
\begin{DoxyCompactList}\small\item\em output \end{DoxyCompactList}\item 
{\footnotesize template$<$typename T1 , typename T2 , typename T3 $>$ }\\struct \hyperlink{structtriple}{triple} \hyperlink{tuples_8h_a61f5f588c8a34e43c27971a61e3a357d}{\+\_\+\+\_\+attribute\+\_\+\+\_\+} ((packed))
\item 
\hyperlink{tuples_8h_a72bccb6f22ab02a7f169a9d9b0671646}{triple} ()
\begin{DoxyCompactList}\small\item\em constructor, default \end{DoxyCompactList}\item 
\hyperlink{tuples_8h_a43fbd7271bb2ea578cbcc6b90491ef12}{triple} (const \hyperlink{structtriple}{triple} \&\+\_\+item)
\begin{DoxyCompactList}\small\item\em constructor, copy \end{DoxyCompactList}\item 
\hyperlink{tuples_8h_a2be7f6af3a54cfc97c55bc395576db62}{triple} (const T1 \&\+\_\+first, const T2 \&\+\_\+second, const T3 \&\+\_\+third)
\begin{DoxyCompactList}\small\item\em constructor, component \end{DoxyCompactList}\item 
std\+::ostream \& \hyperlink{tuples_8h_ae396d2c152e6415ae24b52df6cdfbe23}{operator$<$$<$} (std\+::ostream \+\_\+os, const \hyperlink{structtriple}{triple} \&\+\_\+item)
\begin{DoxyCompactList}\small\item\em output \end{DoxyCompactList}\item 
{\footnotesize template$<$typename T1 , typename T2 , typename T3 , typename T4 $>$ }\\struct \hyperlink{structquadruple}{quadruple} \hyperlink{tuples_8h_aa434f23135e2672ad8fe4ec768f3d88c}{\+\_\+\+\_\+attribute\+\_\+\+\_\+} ((packed))
\item 
\hyperlink{tuples_8h_abc5517aabc587ce4dbe5d5d5c51e926e}{quadruple} ()
\begin{DoxyCompactList}\small\item\em constructor, default \end{DoxyCompactList}\item 
\hyperlink{tuples_8h_ac6ecb9121ff7c7bc8f2bb354d86a7da9}{quadruple} (const \hyperlink{structquadruple}{quadruple} \&\+\_\+item)
\begin{DoxyCompactList}\small\item\em constructor, copy \end{DoxyCompactList}\item 
\hyperlink{tuples_8h_a275ae5ff396331c5f894cae5e717aafd}{quadruple} (const T1 \&\+\_\+first, const T2 \&\+\_\+second, const T3 \&\+\_\+third, const T4 \&\+\_\+forth)
\begin{DoxyCompactList}\small\item\em constructor, component \end{DoxyCompactList}\item 
std\+::ostream \& \hyperlink{tuples_8h_a5ab8584e7c3f4d217350802e27dd64da}{operator$<$$<$} (std\+::ostream \+\_\+os, const \hyperlink{structquadruple}{quadruple} \&\+\_\+item)
\begin{DoxyCompactList}\small\item\em output \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Variables}
\begin{DoxyCompactItemize}
\item 
T1 \hyperlink{tuples_8h_ae885a6822c40e26649c9dd8b476942f8}{first}
\item 
T2 \hyperlink{tuples_8h_a9a8a97f32d498c09c0f1f82c8a67bd6f}{second}
\item 
T3 \hyperlink{tuples_8h_ab02b336e2ad870f773affd07b0f68ef8}{third}
\item 
T4 \hyperlink{tuples_8h_a9c5c830dde97573ef7be2d18f35d61fd}{forth}
\end{DoxyCompactItemize}

\subsection{Function Documentation}
\mbox{\Hypertarget{tuples_8h_a3287af29b6ef2cbe75f1caba87bdde63}\label{tuples_8h_a3287af29b6ef2cbe75f1caba87bdde63}} 
\index{tuples.\+h@{tuples.\+h}!\+\_\+\+\_\+attribute\+\_\+\+\_\+@{\+\_\+\+\_\+attribute\+\_\+\+\_\+}}
\index{\+\_\+\+\_\+attribute\+\_\+\+\_\+@{\+\_\+\+\_\+attribute\+\_\+\+\_\+}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{\+\_\+\+\_\+attribute\+\_\+\+\_\+()}{\_\_attribute\_\_()}\hspace{0.1cm}{\footnotesize\ttfamily [1/3]}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 $>$ \\
struct \hyperlink{structpair}{pair} \+\_\+\+\_\+attribute\+\_\+\+\_\+ (\begin{DoxyParamCaption}\item[{(packed)}]{ }\end{DoxyParamCaption})}

\mbox{\Hypertarget{tuples_8h_a61f5f588c8a34e43c27971a61e3a357d}\label{tuples_8h_a61f5f588c8a34e43c27971a61e3a357d}} 
\index{tuples.\+h@{tuples.\+h}!\+\_\+\+\_\+attribute\+\_\+\+\_\+@{\+\_\+\+\_\+attribute\+\_\+\+\_\+}}
\index{\+\_\+\+\_\+attribute\+\_\+\+\_\+@{\+\_\+\+\_\+attribute\+\_\+\+\_\+}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{\+\_\+\+\_\+attribute\+\_\+\+\_\+()}{\_\_attribute\_\_()}\hspace{0.1cm}{\footnotesize\ttfamily [2/3]}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 $>$ \\
struct \hyperlink{structtriple}{triple} \+\_\+\+\_\+attribute\+\_\+\+\_\+ (\begin{DoxyParamCaption}\item[{(packed)}]{ }\end{DoxyParamCaption})}

\mbox{\Hypertarget{tuples_8h_aa434f23135e2672ad8fe4ec768f3d88c}\label{tuples_8h_aa434f23135e2672ad8fe4ec768f3d88c}} 
\index{tuples.\+h@{tuples.\+h}!\+\_\+\+\_\+attribute\+\_\+\+\_\+@{\+\_\+\+\_\+attribute\+\_\+\+\_\+}}
\index{\+\_\+\+\_\+attribute\+\_\+\+\_\+@{\+\_\+\+\_\+attribute\+\_\+\+\_\+}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{\+\_\+\+\_\+attribute\+\_\+\+\_\+()}{\_\_attribute\_\_()}\hspace{0.1cm}{\footnotesize\ttfamily [3/3]}}
{\footnotesize\ttfamily template$<$typename T1 , typename T2 , typename T3 , typename T4 $>$ \\
struct \hyperlink{structquadruple}{quadruple} \+\_\+\+\_\+attribute\+\_\+\+\_\+ (\begin{DoxyParamCaption}\item[{(packed)}]{ }\end{DoxyParamCaption})}

\mbox{\Hypertarget{tuples_8h_abc17aed069c35187f4d6f8b05c506300}\label{tuples_8h_abc17aed069c35187f4d6f8b05c506300}} 
\index{tuples.\+h@{tuples.\+h}!max\+\_\+value@{max\+\_\+value}}
\index{max\+\_\+value@{max\+\_\+value}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{max\+\_\+value()}{max\_value()}}
{\footnotesize\ttfamily static \hyperlink{structquadruple}{quadruple} \& max\+\_\+value (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [static]}}

max vlaue

max value \mbox{\Hypertarget{tuples_8h_ac8a41d1a11f39ac2d9916b2248d76d5d}\label{tuples_8h_ac8a41d1a11f39ac2d9916b2248d76d5d}} 
\index{tuples.\+h@{tuples.\+h}!min\+\_\+value@{min\+\_\+value}}
\index{min\+\_\+value@{min\+\_\+value}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{min\+\_\+value()}{min\_value()}}
{\footnotesize\ttfamily static \hyperlink{structquadruple}{quadruple} \& min\+\_\+value (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [static]}}

min value

\mbox{\Hypertarget{tuples_8h_a068f246e1ab74655cd80c5d32b347a20}\label{tuples_8h_a068f246e1ab74655cd80c5d32b347a20}} 
\index{tuples.\+h@{tuples.\+h}!operator$<$$<$@{operator$<$$<$}}
\index{operator$<$$<$@{operator$<$$<$}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{operator$<$$<$()}{operator<<()}\hspace{0.1cm}{\footnotesize\ttfamily [1/3]}}
{\footnotesize\ttfamily friend std\+::ostream\& \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::operator$<$$<$ (\begin{DoxyParamCaption}\item[{std\+::ostream}]{\+\_\+os,  }\item[{const \hyperlink{structpair}{pair} \&}]{\+\_\+item }\end{DoxyParamCaption})}

output

\mbox{\Hypertarget{tuples_8h_ae396d2c152e6415ae24b52df6cdfbe23}\label{tuples_8h_ae396d2c152e6415ae24b52df6cdfbe23}} 
\index{tuples.\+h@{tuples.\+h}!operator$<$$<$@{operator$<$$<$}}
\index{operator$<$$<$@{operator$<$$<$}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{operator$<$$<$()}{operator<<()}\hspace{0.1cm}{\footnotesize\ttfamily [2/3]}}
{\footnotesize\ttfamily friend std\+::ostream\& \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::operator$<$$<$ (\begin{DoxyParamCaption}\item[{std\+::ostream}]{\+\_\+os,  }\item[{const \hyperlink{structtriple}{triple} \&}]{\+\_\+item }\end{DoxyParamCaption})}

output

\mbox{\Hypertarget{tuples_8h_a5ab8584e7c3f4d217350802e27dd64da}\label{tuples_8h_a5ab8584e7c3f4d217350802e27dd64da}} 
\index{tuples.\+h@{tuples.\+h}!operator$<$$<$@{operator$<$$<$}}
\index{operator$<$$<$@{operator$<$$<$}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{operator$<$$<$()}{operator<<()}\hspace{0.1cm}{\footnotesize\ttfamily [3/3]}}
{\footnotesize\ttfamily friend std\+::ostream\& \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::operator$<$$<$ (\begin{DoxyParamCaption}\item[{std\+::ostream}]{\+\_\+os,  }\item[{const \hyperlink{structquadruple}{quadruple} \&}]{\+\_\+item }\end{DoxyParamCaption})}

output

\mbox{\Hypertarget{tuples_8h_a861a18bf6751dab7e644b4c4858d3548}\label{tuples_8h_a861a18bf6751dab7e644b4c4858d3548}} 
\index{tuples.\+h@{tuples.\+h}!pair@{pair}}
\index{pair@{pair}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{pair()}{pair()}\hspace{0.1cm}{\footnotesize\ttfamily [1/3]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::pair (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})}

constructor, default

\mbox{\Hypertarget{tuples_8h_ad95635b05637a43806af080d9ec581ba}\label{tuples_8h_ad95635b05637a43806af080d9ec581ba}} 
\index{tuples.\+h@{tuples.\+h}!pair@{pair}}
\index{pair@{pair}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{pair()}{pair()}\hspace{0.1cm}{\footnotesize\ttfamily [2/3]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::pair (\begin{DoxyParamCaption}\item[{const \hyperlink{structpair}{pair} \&}]{\+\_\+item }\end{DoxyParamCaption})}

constructor, copy

\mbox{\Hypertarget{tuples_8h_a80f1b898df1006722612d5ecf89cd4d7}\label{tuples_8h_a80f1b898df1006722612d5ecf89cd4d7}} 
\index{tuples.\+h@{tuples.\+h}!pair@{pair}}
\index{pair@{pair}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{pair()}{pair()}\hspace{0.1cm}{\footnotesize\ttfamily [3/3]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::pair (\begin{DoxyParamCaption}\item[{const T1 \&}]{\+\_\+first,  }\item[{const T2 \&}]{\+\_\+second }\end{DoxyParamCaption})}

constructor, component

\mbox{\Hypertarget{tuples_8h_abc5517aabc587ce4dbe5d5d5c51e926e}\label{tuples_8h_abc5517aabc587ce4dbe5d5d5c51e926e}} 
\index{tuples.\+h@{tuples.\+h}!quadruple@{quadruple}}
\index{quadruple@{quadruple}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{quadruple()}{quadruple()}\hspace{0.1cm}{\footnotesize\ttfamily [1/3]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::quadruple (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})}

constructor, default

\mbox{\Hypertarget{tuples_8h_ac6ecb9121ff7c7bc8f2bb354d86a7da9}\label{tuples_8h_ac6ecb9121ff7c7bc8f2bb354d86a7da9}} 
\index{tuples.\+h@{tuples.\+h}!quadruple@{quadruple}}
\index{quadruple@{quadruple}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{quadruple()}{quadruple()}\hspace{0.1cm}{\footnotesize\ttfamily [2/3]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::quadruple (\begin{DoxyParamCaption}\item[{const \hyperlink{structquadruple}{quadruple} \&}]{\+\_\+item }\end{DoxyParamCaption})}

constructor, copy

\mbox{\Hypertarget{tuples_8h_a275ae5ff396331c5f894cae5e717aafd}\label{tuples_8h_a275ae5ff396331c5f894cae5e717aafd}} 
\index{tuples.\+h@{tuples.\+h}!quadruple@{quadruple}}
\index{quadruple@{quadruple}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{quadruple()}{quadruple()}\hspace{0.1cm}{\footnotesize\ttfamily [3/3]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::quadruple (\begin{DoxyParamCaption}\item[{const T1 \&}]{\+\_\+first,  }\item[{const T2 \&}]{\+\_\+second,  }\item[{const T3 \&}]{\+\_\+third,  }\item[{const T4 \&}]{\+\_\+forth }\end{DoxyParamCaption})}

constructor, component

\mbox{\Hypertarget{tuples_8h_a72bccb6f22ab02a7f169a9d9b0671646}\label{tuples_8h_a72bccb6f22ab02a7f169a9d9b0671646}} 
\index{tuples.\+h@{tuples.\+h}!triple@{triple}}
\index{triple@{triple}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{triple()}{triple()}\hspace{0.1cm}{\footnotesize\ttfamily [1/3]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::triple (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})}

constructor, default

\mbox{\Hypertarget{tuples_8h_a43fbd7271bb2ea578cbcc6b90491ef12}\label{tuples_8h_a43fbd7271bb2ea578cbcc6b90491ef12}} 
\index{tuples.\+h@{tuples.\+h}!triple@{triple}}
\index{triple@{triple}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{triple()}{triple()}\hspace{0.1cm}{\footnotesize\ttfamily [2/3]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::triple (\begin{DoxyParamCaption}\item[{const \hyperlink{structtriple}{triple} \&}]{\+\_\+item }\end{DoxyParamCaption})}

constructor, copy

\mbox{\Hypertarget{tuples_8h_a2be7f6af3a54cfc97c55bc395576db62}\label{tuples_8h_a2be7f6af3a54cfc97c55bc395576db62}} 
\index{tuples.\+h@{tuples.\+h}!triple@{triple}}
\index{triple@{triple}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{triple()}{triple()}\hspace{0.1cm}{\footnotesize\ttfamily [3/3]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::triple (\begin{DoxyParamCaption}\item[{const T1 \&}]{\+\_\+first,  }\item[{const T2 \&}]{\+\_\+second,  }\item[{const T3 \&}]{\+\_\+third }\end{DoxyParamCaption})}

constructor, component

\subsection{Variable Documentation}
\mbox{\Hypertarget{tuples_8h_ae885a6822c40e26649c9dd8b476942f8}\label{tuples_8h_ae885a6822c40e26649c9dd8b476942f8}} 
\index{tuples.\+h@{tuples.\+h}!first@{first}}
\index{first@{first}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{first}{first}}
{\footnotesize\ttfamily T1 first}

\mbox{\Hypertarget{tuples_8h_a9c5c830dde97573ef7be2d18f35d61fd}\label{tuples_8h_a9c5c830dde97573ef7be2d18f35d61fd}} 
\index{tuples.\+h@{tuples.\+h}!forth@{forth}}
\index{forth@{forth}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{forth}{forth}}
{\footnotesize\ttfamily T4 forth}

\mbox{\Hypertarget{tuples_8h_a9a8a97f32d498c09c0f1f82c8a67bd6f}\label{tuples_8h_a9a8a97f32d498c09c0f1f82c8a67bd6f}} 
\index{tuples.\+h@{tuples.\+h}!second@{second}}
\index{second@{second}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{second}{second}}
{\footnotesize\ttfamily T2 second}

\mbox{\Hypertarget{tuples_8h_ab02b336e2ad870f773affd07b0f68ef8}\label{tuples_8h_ab02b336e2ad870f773affd07b0f68ef8}} 
\index{tuples.\+h@{tuples.\+h}!third@{third}}
\index{third@{third}!tuples.\+h@{tuples.\+h}}
\subsubsection{\texorpdfstring{third}{third}}
{\footnotesize\ttfamily T3 third}

### 2017-01-24 archive/latex/types_8h.tex
2017/01/24

\hypertarget{types_8h}{}\section{code/src/common/types.h File Reference}
\label{types_8h}\index{code/src/common/types.\+h@{code/src/common/types.\+h}}

definition of namespace

{\ttfamily \#include $<$iostream$>$}\newline
{\ttfamily \#include $<$limits$>$}\newline
{\ttfamily \#include $<$cstdint$>$}\newline
{\ttfamily \#include \char`\"{}stxxl/bits/common/uint\+\_\+types.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}namespace.\+h\char`\"{}}\newline
\subsection*{Classes}
\begin{DoxyCompactItemize}
\item 
struct \hyperlink{structchoose__int__types}{choose\+\_\+int\+\_\+types$<$ P\+S $>$}
\begin{DoxyCompactList}\small\item\em template for choosing int/uint type according to pointer size \end{DoxyCompactList}\item 
struct \hyperlink{structchoose__int__types_3_014_01_4}{choose\+\_\+int\+\_\+types$<$ 4 $>$}
\begin{DoxyCompactList}\small\item\em PS = 4, int32/uint32. \end{DoxyCompactList}\item 
struct \hyperlink{structchoose__int__types_3_018_01_4}{choose\+\_\+int\+\_\+types$<$ 8 $>$}
\begin{DoxyCompactList}\small\item\em pointer size = 8, 64-\/bit \end{DoxyCompactList}\item 
class \hyperlink{classuint40}{uint40}
\item 
class \hyperlink{classuint128}{uint128}
\item 
class \hyperlink{classstd_1_1numeric__limits_3_01uint40_01_4}{std\+::numeric\+\_\+limits$<$ uint40 $>$}
\item 
class \hyperlink{classstd_1_1numeric__limits_3_01uint128_01_4}{std\+::numeric\+\_\+limits$<$ uint128 $>$}
\end{DoxyCompactItemize}
\subsection*{Namespaces}
\begin{DoxyCompactItemize}
\item 
 \hyperlink{namespacestd}{std}
\end{DoxyCompactItemize}
\subsection*{Typedefs}
\begin{DoxyCompactItemize}
\item 
using \hyperlink{types_8h_abd106ada62607d216e5d94926d7ec378}{int8} = std\+::int8\+\_\+t
\item 
using \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} = std\+::uint8\+\_\+t
\item 
using \hyperlink{types_8h_ac2abd1926482d6e74d1a30ee2ea5d6f8}{int16} = std\+::int16\+\_\+t
\item 
using \hyperlink{types_8h_aea9840dd402bd5d5201bef4633398cb3}{uint16} = std\+::uint16\+\_\+t
\item 
using \hyperlink{types_8h_a3d594eb72953c94a18a03d929ebd9167}{int32} = std\+::int32\+\_\+t
\item 
using \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} = std\+::uint32\+\_\+t
\item 
using \hyperlink{types_8h_a552928ab323811c9694f5b7c9f53d0fb}{int64} = std\+::int64\+\_\+t
\item 
using \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} = std\+::uint64\+\_\+t
\item 
using \hyperlink{types_8h_a848058bb4f500afaf0f954ffa75d3e6b}{int\+\_\+type} = typename \hyperlink{structchoose__int__types}{choose\+\_\+int\+\_\+types}$<$ \hyperlink{types_8h_a06fc87d81c62e9abb8790b6e5713c55ba8cdfa64b8cdab0fc9fe0e5a9d0192a5c}{my\+\_\+pointer\+\_\+size} $>$\+::\hyperlink{types_8h_a848058bb4f500afaf0f954ffa75d3e6b}{int\+\_\+type}
\item 
using \hyperlink{types_8h_a948660ad4bbc6ed2c3e3262a30bac0ff}{uint\+\_\+type} = typename \hyperlink{structchoose__int__types}{choose\+\_\+int\+\_\+types}$<$ \hyperlink{types_8h_a06fc87d81c62e9abb8790b6e5713c55ba8cdfa64b8cdab0fc9fe0e5a9d0192a5c}{my\+\_\+pointer\+\_\+size} $>$\+::\hyperlink{types_8h_a948660ad4bbc6ed2c3e3262a30bac0ff}{uint\+\_\+type}
\item 
typedef \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} \hyperlink{types_8h_afb0e4a3c06d32e9372ba48a8ebe1861c}{low\+\_\+type}
\item 
typedef \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \hyperlink{types_8h_a3d1ab983bb49c4acd2478c5365ce2bbb}{high\+\_\+type}
\end{DoxyCompactItemize}
\subsection*{Enumerations}
\begin{DoxyCompactItemize}
\item 
enum \{ \hyperlink{types_8h_a06fc87d81c62e9abb8790b6e5713c55ba8cdfa64b8cdab0fc9fe0e5a9d0192a5c}{my\+\_\+pointer\+\_\+size} = sizeof(void$\ast$)
 \}
\end{DoxyCompactItemize}
\subsection*{Functions}
\begin{DoxyCompactItemize}
\item 
class \hyperlink{classuint40}{uint40} \hyperlink{types_8h_aa5073eed52429ca9c68cfeef8163dadb}{\+\_\+\+\_\+attribute\+\_\+\+\_\+} ((packed))
\item 
\hyperlink{types_8h_affa82c4225cfcd81baaccd829d3d1c0b}{uint40} ()
\item 
\hyperlink{types_8h_a4ba3483a239f25b1c755c75e19475edb}{uint40} (std\+::uint32\+\_\+t l, std\+::uint8\+\_\+t h)
\item 
\hyperlink{types_8h_a5e660390adddb6b4c8b4e041f0466e86}{uint40} (const \hyperlink{classuint40}{uint40} \&a)
\item 
\hyperlink{types_8h_aaf73c1c2f7134d2c727ccfbc94736b2d}{uint40} (const std\+::int32\+\_\+t \&a)
\item 
\hyperlink{types_8h_aeb67d0e1054914c055fd6340c46e9b86}{uint40} (const std\+::uint32\+\_\+t \&a)
\item 
\hyperlink{types_8h_ae19857f157c887383d1a7c165ce9519a}{uint40} (const std\+::uint64\+\_\+t \&a)
\item 
\hyperlink{types_8h_a42b38cde4ba7cf52ccc3ab60547e002a}{uint40} (const std\+::int64\+\_\+t \&a)
\item 
void \hyperlink{types_8h_a1bdb76cf7211909f821911726507fb30}{set\+\_\+high} (const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \&\+\_\+high)
\item 
void \hyperlink{types_8h_ac451e240aa7238b8cdd88c68a4b94c25}{set\+\_\+low} (const \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} \&\+\_\+low)
\item 
void \hyperlink{types_8h_a9805ad2d84465b3a1c4aa12235f922c4}{set} (const \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} \&\+\_\+low, const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \+\_\+high)
\item 
\hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} \hyperlink{types_8h_a3bac47f21d0c0a8e255bdd0b1dabd2f2}{get\+\_\+low} ()
\item 
\hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \hyperlink{types_8h_a20cad26639e8f866e2fcfd01b6e9d0d4}{get\+\_\+high} ()
\item 
\hyperlink{types_8h_a8c16775e7e2ad633aae492dd2552ef52}{operator uint64\+\_\+t} () const
\item 
bool \hyperlink{types_8h_a7ae67630ef1311127ca10f83158b9b87}{operator==} (const \hyperlink{classuint40}{uint40} \&b) const
\item 
bool \hyperlink{types_8h_affababd92753c4880d0c280bdb62633e}{operator!=} (const \hyperlink{classuint40}{uint40} \&b) const
\item 
\hyperlink{types_8h_ab620f7af906d024680c89ac9c99d5fae}{uint128} ()
\begin{DoxyCompactList}\small\item\em default ctor \end{DoxyCompactList}\item 
\hyperlink{types_8h_a38ef652b59a2ba178eff4646c7e5e008}{uint128} (const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+low, const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+high)
\begin{DoxyCompactList}\small\item\em initialized from lower and higher parts \end{DoxyCompactList}\item 
\hyperlink{types_8h_af7e6621517578e3fd6d7c26900edc6ef}{uint128} (const \hyperlink{classuint128}{uint128} \&\+\_\+a)
\begin{DoxyCompactList}\small\item\em copy ctor \end{DoxyCompactList}\item 
\hyperlink{types_8h_a5dc4f1787a04c99e251cd68bc631c7b3}{uint128} (const \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} \&\+\_\+a)
\begin{DoxyCompactList}\small\item\em initialized from an unsigned int \end{DoxyCompactList}\item 
\hyperlink{types_8h_a38af0db38b8983c09e453dbb2a423b35}{uint128} (const \hyperlink{types_8h_a3d594eb72953c94a18a03d929ebd9167}{int32} \&\+\_\+a)
\begin{DoxyCompactList}\small\item\em initialized from anint, a $>$= 0 \end{DoxyCompactList}\item 
\hyperlink{types_8h_ab68fd9ef279f5a248fe93b1206cbc559}{uint128} (const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&\+\_\+a)
\begin{DoxyCompactList}\small\item\em initialized from an unsigned long int \end{DoxyCompactList}\item 
void \hyperlink{types_8h_ad7a7fcf67e0961b6a8fb5116e0964081}{operator$<$$<$=} (const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \+\_\+bits)
\begin{DoxyCompactList}\small\item\em bitwise shift, \+\_\+bits bits leftward, self revision \end{DoxyCompactList}\item 
void \hyperlink{types_8h_aac289619282f098101aadadeb2cc4025}{operator$\vert$=} (const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \+\_\+ch)
\begin{DoxyCompactList}\small\item\em bitwise or \end{DoxyCompactList}\item 
\hyperlink{classuint128}{uint128} \hyperlink{types_8h_ac37ecdc1a86d796e924955bcd1db0312}{operator$<$$<$} (const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \+\_\+bits)
\begin{DoxyCompactList}\small\item\em biwise shift, \+\_\+bits bits leftward \end{DoxyCompactList}\item 
\hyperlink{classuint128}{uint128} \hyperlink{types_8h_a2ada254777d54d622dbeb7d45da92336}{operator\&} (const \hyperlink{classuint128}{uint128} \&\+\_\+b) const
\begin{DoxyCompactList}\small\item\em bitwise and \end{DoxyCompactList}\item 
bool \hyperlink{types_8h_a3af85699a8b10f425ac46a48ca949225}{operator==} (const \hyperlink{classuint128}{uint128} \&b) const
\begin{DoxyCompactList}\small\item\em check equality \end{DoxyCompactList}\item 
bool \hyperlink{types_8h_ab3a727e5eede21cf30765aa649eb6b9d}{operator!=} (const \hyperlink{classuint128}{uint128} \&b) const
\begin{DoxyCompactList}\small\item\em check inequality \end{DoxyCompactList}\item 
static \hyperlink{classuint128}{uint128} \hyperlink{types_8h_ac7d80e29baaa3f8e4eef22cdc851744a}{min} ()
\item 
static \hyperlink{classuint128}{uint128} \hyperlink{types_8h_add613a3d2d7eff426907064270db8215}{max} ()
\item 
std\+::ostream \& \hyperlink{types_8h_af5c7620c5c09b3c146557179b3a041e8}{operator$<$$<$} (std\+::ostream \&\+\_\+os, const \hyperlink{classuint128}{uint128} \&\+\_\+a)
\end{DoxyCompactItemize}
\subsection*{Variables}
\begin{DoxyCompactItemize}
\item 
enum  \{ ... \}  \hyperlink{types_8h_af03243776893bcf5923a8f446b8d851c}{\+\_\+\+\_\+attribute\+\_\+\+\_\+}
\item 
\hyperlink{types_8h_afb0e4a3c06d32e9372ba48a8ebe1861c}{low\+\_\+type} \hyperlink{types_8h_ade07039efd8c0cfca1f9cead48259d4d}{low}
\begin{DoxyCompactList}\small\item\em lower part, uint64 \end{DoxyCompactList}\item 
\hyperlink{types_8h_a3d1ab983bb49c4acd2478c5365ce2bbb}{high\+\_\+type} \hyperlink{types_8h_a558f35d10292a79de791071eb8088a8c}{high}
\begin{DoxyCompactList}\small\item\em higher part, uint64 \end{DoxyCompactList}\item 
static const size\+\_\+t \hyperlink{types_8h_af113dea6c24342761f00f6b36e99032e}{digits} = 128
\begin{DoxyCompactList}\small\item\em number of digits/bits, 128 \end{DoxyCompactList}\item 
static const size\+\_\+t \hyperlink{types_8h_ab09b9b43d1b1783c78e39783e382b3dd}{bytes} = 16
\begin{DoxyCompactList}\small\item\em number of bytes, 16 \end{DoxyCompactList}\item 
class std\+::numeric\+\_\+limits$<$ \hyperlink{classuint40}{uint40} $>$ \hyperlink{namespacestd_ade73df0294cb697bb61d5edf0deac7d0}{std\+::\+\_\+\+\_\+attribute\+\_\+\+\_\+}
\end{DoxyCompactItemize}

\subsection{Detailed Description}
definition of namespace

definition and alias of integer types

Copyright (c) 2016, Sun Yat-\/sen University, All rights reserved

\begin{DoxyAuthor}{Author}
Yi Wu 
\end{DoxyAuthor}
\begin{DoxyDate}{Date}
2016.\+12
\end{DoxyDate}
Copyright (c) 2016, Sun Yat-\/sen University, All rights reserved

Partly depends on \char`\"{}types.\+h\char`\"{} in S\+T\+X\+XL

\begin{DoxyAuthor}{Author}
Yi Wu 
\end{DoxyAuthor}
\begin{DoxyDate}{Date}
2016.\+12 
\end{DoxyDate}

\subsection{Typedef Documentation}
\mbox{\Hypertarget{types_8h_a3d1ab983bb49c4acd2478c5365ce2bbb}\label{types_8h_a3d1ab983bb49c4acd2478c5365ce2bbb}} 
\index{types.\+h@{types.\+h}!high\+\_\+type@{high\+\_\+type}}
\index{high\+\_\+type@{high\+\_\+type}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{high\+\_\+type}{high\_type}}
{\footnotesize\ttfamily typedef \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \hyperlink{types_8h_a3d1ab983bb49c4acd2478c5365ce2bbb}{high\+\_\+type}}

\mbox{\Hypertarget{types_8h_ac2abd1926482d6e74d1a30ee2ea5d6f8}\label{types_8h_ac2abd1926482d6e74d1a30ee2ea5d6f8}} 
\index{types.\+h@{types.\+h}!int16@{int16}}
\index{int16@{int16}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{int16}{int16}}
{\footnotesize\ttfamily using \hyperlink{types_8h_ac2abd1926482d6e74d1a30ee2ea5d6f8}{int16} =  std\+::int16\+\_\+t}

\mbox{\Hypertarget{types_8h_a3d594eb72953c94a18a03d929ebd9167}\label{types_8h_a3d594eb72953c94a18a03d929ebd9167}} 
\index{types.\+h@{types.\+h}!int32@{int32}}
\index{int32@{int32}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{int32}{int32}}
{\footnotesize\ttfamily using \hyperlink{types_8h_a3d594eb72953c94a18a03d929ebd9167}{int32} =  std\+::int32\+\_\+t}

\mbox{\Hypertarget{types_8h_a552928ab323811c9694f5b7c9f53d0fb}\label{types_8h_a552928ab323811c9694f5b7c9f53d0fb}} 
\index{types.\+h@{types.\+h}!int64@{int64}}
\index{int64@{int64}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{int64}{int64}}
{\footnotesize\ttfamily using \hyperlink{types_8h_a552928ab323811c9694f5b7c9f53d0fb}{int64} =  std\+::int64\+\_\+t}

\mbox{\Hypertarget{types_8h_abd106ada62607d216e5d94926d7ec378}\label{types_8h_abd106ada62607d216e5d94926d7ec378}} 
\index{types.\+h@{types.\+h}!int8@{int8}}
\index{int8@{int8}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{int8}{int8}}
{\footnotesize\ttfamily using \hyperlink{types_8h_abd106ada62607d216e5d94926d7ec378}{int8} =  std\+::int8\+\_\+t}

\mbox{\Hypertarget{types_8h_a848058bb4f500afaf0f954ffa75d3e6b}\label{types_8h_a848058bb4f500afaf0f954ffa75d3e6b}} 
\index{types.\+h@{types.\+h}!int\+\_\+type@{int\+\_\+type}}
\index{int\+\_\+type@{int\+\_\+type}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{int\+\_\+type}{int\_type}}
{\footnotesize\ttfamily using \hyperlink{types_8h_a848058bb4f500afaf0f954ffa75d3e6b}{int\+\_\+type} =  typename \hyperlink{structchoose__int__types}{choose\+\_\+int\+\_\+types}$<$\hyperlink{types_8h_a06fc87d81c62e9abb8790b6e5713c55ba8cdfa64b8cdab0fc9fe0e5a9d0192a5c}{my\+\_\+pointer\+\_\+size}$>$\+::\hyperlink{types_8h_a848058bb4f500afaf0f954ffa75d3e6b}{int\+\_\+type}}

\mbox{\Hypertarget{types_8h_afb0e4a3c06d32e9372ba48a8ebe1861c}\label{types_8h_afb0e4a3c06d32e9372ba48a8ebe1861c}} 
\index{types.\+h@{types.\+h}!low\+\_\+type@{low\+\_\+type}}
\index{low\+\_\+type@{low\+\_\+type}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{low\+\_\+type}{low\_type}}
{\footnotesize\ttfamily typedef \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} \hyperlink{types_8h_afb0e4a3c06d32e9372ba48a8ebe1861c}{low\+\_\+type}}

\mbox{\Hypertarget{types_8h_aea9840dd402bd5d5201bef4633398cb3}\label{types_8h_aea9840dd402bd5d5201bef4633398cb3}} 
\index{types.\+h@{types.\+h}!uint16@{uint16}}
\index{uint16@{uint16}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{uint16}{uint16}}
{\footnotesize\ttfamily using \hyperlink{types_8h_aea9840dd402bd5d5201bef4633398cb3}{uint16} =  std\+::uint16\+\_\+t}

\mbox{\Hypertarget{types_8h_a8f95e75e58492e87412191fabadd8ca8}\label{types_8h_a8f95e75e58492e87412191fabadd8ca8}} 
\index{types.\+h@{types.\+h}!uint32@{uint32}}
\index{uint32@{uint32}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{uint32}{uint32}}
{\footnotesize\ttfamily using \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} =  std\+::uint32\+\_\+t}

\mbox{\Hypertarget{types_8h_a60e8696a4678cd348e991a1f172e53f7}\label{types_8h_a60e8696a4678cd348e991a1f172e53f7}} 
\index{types.\+h@{types.\+h}!uint64@{uint64}}
\index{uint64@{uint64}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{uint64}{uint64}}
{\footnotesize\ttfamily using \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} =  std\+::uint64\+\_\+t}

\mbox{\Hypertarget{types_8h_a115946cb5fc5879545e9ccea096a6031}\label{types_8h_a115946cb5fc5879545e9ccea096a6031}} 
\index{types.\+h@{types.\+h}!uint8@{uint8}}
\index{uint8@{uint8}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{uint8}{uint8}}
{\footnotesize\ttfamily using \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} =  std\+::uint8\+\_\+t}

\mbox{\Hypertarget{types_8h_a948660ad4bbc6ed2c3e3262a30bac0ff}\label{types_8h_a948660ad4bbc6ed2c3e3262a30bac0ff}} 
\index{types.\+h@{types.\+h}!uint\+\_\+type@{uint\+\_\+type}}
\index{uint\+\_\+type@{uint\+\_\+type}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{uint\+\_\+type}{uint\_type}}
{\footnotesize\ttfamily using \hyperlink{types_8h_a948660ad4bbc6ed2c3e3262a30bac0ff}{uint\+\_\+type} =  typename \hyperlink{structchoose__int__types}{choose\+\_\+int\+\_\+types}$<$\hyperlink{types_8h_a06fc87d81c62e9abb8790b6e5713c55ba8cdfa64b8cdab0fc9fe0e5a9d0192a5c}{my\+\_\+pointer\+\_\+size}$>$\+::\hyperlink{types_8h_a948660ad4bbc6ed2c3e3262a30bac0ff}{uint\+\_\+type}}

\subsection{Enumeration Type Documentation}
\mbox{\Hypertarget{types_8h_a06fc87d81c62e9abb8790b6e5713c55b}\label{types_8h_a06fc87d81c62e9abb8790b6e5713c55b}} 
\subsubsection{\texorpdfstring{anonymous enum}{anonymous enum}}
{\footnotesize\ttfamily anonymous enum}

\begin{DoxyEnumFields}{Enumerator}
\raisebox{\heightof{T}}[0pt][0pt]{\index{my\+\_\+pointer\+\_\+size@{my\+\_\+pointer\+\_\+size}!types.\+h@{types.\+h}}\index{types.\+h@{types.\+h}!my\+\_\+pointer\+\_\+size@{my\+\_\+pointer\+\_\+size}}}\mbox{\Hypertarget{types_8h_a06fc87d81c62e9abb8790b6e5713c55ba8cdfa64b8cdab0fc9fe0e5a9d0192a5c}\label{types_8h_a06fc87d81c62e9abb8790b6e5713c55ba8cdfa64b8cdab0fc9fe0e5a9d0192a5c}} 
my\+\_\+pointer\+\_\+size&\\
\hline

\end{DoxyEnumFields}

\subsection{Function Documentation}
\mbox{\Hypertarget{types_8h_aa5073eed52429ca9c68cfeef8163dadb}\label{types_8h_aa5073eed52429ca9c68cfeef8163dadb}} 
\index{types.\+h@{types.\+h}!\+\_\+\+\_\+attribute\+\_\+\+\_\+@{\+\_\+\+\_\+attribute\+\_\+\+\_\+}}
\index{\+\_\+\+\_\+attribute\+\_\+\+\_\+@{\+\_\+\+\_\+attribute\+\_\+\+\_\+}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{\+\_\+\+\_\+attribute\+\_\+\+\_\+()}{\_\_attribute\_\_()}}
{\footnotesize\ttfamily class \hyperlink{classuint40}{uint40} \+\_\+\+\_\+attribute\+\_\+\+\_\+ (\begin{DoxyParamCaption}\item[{(packed)}]{ }\end{DoxyParamCaption})}

\mbox{\Hypertarget{types_8h_a20cad26639e8f866e2fcfd01b6e9d0d4}\label{types_8h_a20cad26639e8f866e2fcfd01b6e9d0d4}} 
\index{types.\+h@{types.\+h}!get\+\_\+high@{get\+\_\+high}}
\index{get\+\_\+high@{get\+\_\+high}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{get\+\_\+high()}{get\_high()}}
{\footnotesize\ttfamily \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} get\+\_\+high (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})}

\mbox{\Hypertarget{types_8h_a3bac47f21d0c0a8e255bdd0b1dabd2f2}\label{types_8h_a3bac47f21d0c0a8e255bdd0b1dabd2f2}} 
\index{types.\+h@{types.\+h}!get\+\_\+low@{get\+\_\+low}}
\index{get\+\_\+low@{get\+\_\+low}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{get\+\_\+low()}{get\_low()}}
{\footnotesize\ttfamily \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} get\+\_\+low (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})}

\mbox{\Hypertarget{types_8h_add613a3d2d7eff426907064270db8215}\label{types_8h_add613a3d2d7eff426907064270db8215}} 
\index{types.\+h@{types.\+h}!max@{max}}
\index{max@{max}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{max()}{max()}}
{\footnotesize\ttfamily static \hyperlink{classuint128}{uint128} \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::max (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [static]}}

\mbox{\Hypertarget{types_8h_ac7d80e29baaa3f8e4eef22cdc851744a}\label{types_8h_ac7d80e29baaa3f8e4eef22cdc851744a}} 
\index{types.\+h@{types.\+h}!min@{min}}
\index{min@{min}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{min()}{min()}}
{\footnotesize\ttfamily static \hyperlink{classuint128}{uint128} \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::min (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})\hspace{0.3cm}{\ttfamily [static]}}

\mbox{\Hypertarget{types_8h_a8c16775e7e2ad633aae492dd2552ef52}\label{types_8h_a8c16775e7e2ad633aae492dd2552ef52}} 
\index{types.\+h@{types.\+h}!operator uint64\+\_\+t@{operator uint64\+\_\+t}}
\index{operator uint64\+\_\+t@{operator uint64\+\_\+t}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{operator uint64\+\_\+t()}{operator uint64\_t()}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::operator uint64\+\_\+t (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{types_8h_affababd92753c4880d0c280bdb62633e}\label{types_8h_affababd92753c4880d0c280bdb62633e}} 
\index{types.\+h@{types.\+h}!operator"!=@{operator"!=}}
\index{operator"!=@{operator"!=}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{operator"!=()}{operator!=()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily bool \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::operator!= (\begin{DoxyParamCaption}\item[{const \hyperlink{classuint40}{uint40} \&}]{b }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{types_8h_ab3a727e5eede21cf30765aa649eb6b9d}\label{types_8h_ab3a727e5eede21cf30765aa649eb6b9d}} 
\index{types.\+h@{types.\+h}!operator"!=@{operator"!=}}
\index{operator"!=@{operator"!=}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{operator"!=()}{operator!=()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily bool \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::operator!= (\begin{DoxyParamCaption}\item[{const \hyperlink{classuint128}{uint128} \&}]{b }\end{DoxyParamCaption}) const}

check inequality

\mbox{\Hypertarget{types_8h_a2ada254777d54d622dbeb7d45da92336}\label{types_8h_a2ada254777d54d622dbeb7d45da92336}} 
\index{types.\+h@{types.\+h}!operator\&@{operator\&}}
\index{operator\&@{operator\&}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{operator\&()}{operator\&()}}
{\footnotesize\ttfamily \hyperlink{classuint128}{uint128} \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::operator \& (\begin{DoxyParamCaption}\item[{const \hyperlink{classuint128}{uint128} \&}]{\+\_\+b }\end{DoxyParamCaption}) const}

bitwise and

\mbox{\Hypertarget{types_8h_ac37ecdc1a86d796e924955bcd1db0312}\label{types_8h_ac37ecdc1a86d796e924955bcd1db0312}} 
\index{types.\+h@{types.\+h}!operator$<$$<$@{operator$<$$<$}}
\index{operator$<$$<$@{operator$<$$<$}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{operator$<$$<$()}{operator<<()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily \hyperlink{classuint128}{uint128} \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::operator$<$$<$ (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8}}]{\+\_\+bits }\end{DoxyParamCaption})}

biwise shift, \+\_\+bits bits leftward

\mbox{\Hypertarget{types_8h_af5c7620c5c09b3c146557179b3a041e8}\label{types_8h_af5c7620c5c09b3c146557179b3a041e8}} 
\index{types.\+h@{types.\+h}!operator$<$$<$@{operator$<$$<$}}
\index{operator$<$$<$@{operator$<$$<$}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{operator$<$$<$()}{operator<<()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily friend std\+::ostream\& \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::operator$<$$<$ (\begin{DoxyParamCaption}\item[{std\+::ostream \&}]{\+\_\+os,  }\item[{const \hyperlink{classuint128}{uint128} \&}]{\+\_\+a }\end{DoxyParamCaption})}

\mbox{\Hypertarget{types_8h_ad7a7fcf67e0961b6a8fb5116e0964081}\label{types_8h_ad7a7fcf67e0961b6a8fb5116e0964081}} 
\index{types.\+h@{types.\+h}!operator$<$$<$=@{operator$<$$<$=}}
\index{operator$<$$<$=@{operator$<$$<$=}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{operator$<$$<$=()}{operator<<=()}}
{\footnotesize\ttfamily void \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::operator$<$$<$= (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8}}]{\+\_\+bits }\end{DoxyParamCaption})}

bitwise shift, \+\_\+bits bits leftward, self revision

\mbox{\Hypertarget{types_8h_a7ae67630ef1311127ca10f83158b9b87}\label{types_8h_a7ae67630ef1311127ca10f83158b9b87}} 
\index{types.\+h@{types.\+h}!operator==@{operator==}}
\index{operator==@{operator==}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{operator==()}{operator==()}\hspace{0.1cm}{\footnotesize\ttfamily [1/2]}}
{\footnotesize\ttfamily bool \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::operator== (\begin{DoxyParamCaption}\item[{const \hyperlink{classuint40}{uint40} \&}]{b }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

\mbox{\Hypertarget{types_8h_a3af85699a8b10f425ac46a48ca949225}\label{types_8h_a3af85699a8b10f425ac46a48ca949225}} 
\index{types.\+h@{types.\+h}!operator==@{operator==}}
\index{operator==@{operator==}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{operator==()}{operator==()}\hspace{0.1cm}{\footnotesize\ttfamily [2/2]}}
{\footnotesize\ttfamily bool \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::operator== (\begin{DoxyParamCaption}\item[{const \hyperlink{classuint128}{uint128} \&}]{b }\end{DoxyParamCaption}) const}

check equality

\mbox{\Hypertarget{types_8h_aac289619282f098101aadadeb2cc4025}\label{types_8h_aac289619282f098101aadadeb2cc4025}} 
\index{types.\+h@{types.\+h}!operator\texttt{"|}=@{operator\texttt{"|}=}}
\index{operator\texttt{"|}=@{operator\texttt{"|}=}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{operator\texttt{"|}=()}{operator|=()}}
{\footnotesize\ttfamily void \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::operator$\vert$= (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8}}]{\+\_\+ch }\end{DoxyParamCaption})}

bitwise or

\mbox{\Hypertarget{types_8h_a9805ad2d84465b3a1c4aa12235f922c4}\label{types_8h_a9805ad2d84465b3a1c4aa12235f922c4}} 
\index{types.\+h@{types.\+h}!set@{set}}
\index{set@{set}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{set()}{set()}}
{\footnotesize\ttfamily void \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::set (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} \&}]{\+\_\+low,  }\item[{const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8}}]{\+\_\+high }\end{DoxyParamCaption})}

\mbox{\Hypertarget{types_8h_a1bdb76cf7211909f821911726507fb30}\label{types_8h_a1bdb76cf7211909f821911726507fb30}} 
\index{types.\+h@{types.\+h}!set\+\_\+high@{set\+\_\+high}}
\index{set\+\_\+high@{set\+\_\+high}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{set\+\_\+high()}{set\_high()}}
{\footnotesize\ttfamily void \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::set\+\_\+high (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a115946cb5fc5879545e9ccea096a6031}{uint8} \&}]{\+\_\+high }\end{DoxyParamCaption})}

\mbox{\Hypertarget{types_8h_ac451e240aa7238b8cdd88c68a4b94c25}\label{types_8h_ac451e240aa7238b8cdd88c68a4b94c25}} 
\index{types.\+h@{types.\+h}!set\+\_\+low@{set\+\_\+low}}
\index{set\+\_\+low@{set\+\_\+low}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{set\+\_\+low()}{set\_low()}}
{\footnotesize\ttfamily void \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::set\+\_\+low (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} \&}]{\+\_\+low }\end{DoxyParamCaption})}

\mbox{\Hypertarget{types_8h_ab620f7af906d024680c89ac9c99d5fae}\label{types_8h_ab620f7af906d024680c89ac9c99d5fae}} 
\index{types.\+h@{types.\+h}!uint128@{uint128}}
\index{uint128@{uint128}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{uint128()}{uint128()}\hspace{0.1cm}{\footnotesize\ttfamily [1/6]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::uint128 (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})}

default ctor

\mbox{\Hypertarget{types_8h_a38ef652b59a2ba178eff4646c7e5e008}\label{types_8h_a38ef652b59a2ba178eff4646c7e5e008}} 
\index{types.\+h@{types.\+h}!uint128@{uint128}}
\index{uint128@{uint128}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{uint128()}{uint128()}\hspace{0.1cm}{\footnotesize\ttfamily [2/6]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::uint128 (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+low,  }\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+high }\end{DoxyParamCaption})}

initialized from lower and higher parts

\mbox{\Hypertarget{types_8h_af7e6621517578e3fd6d7c26900edc6ef}\label{types_8h_af7e6621517578e3fd6d7c26900edc6ef}} 
\index{types.\+h@{types.\+h}!uint128@{uint128}}
\index{uint128@{uint128}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{uint128()}{uint128()}\hspace{0.1cm}{\footnotesize\ttfamily [3/6]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::uint128 (\begin{DoxyParamCaption}\item[{const \hyperlink{classuint128}{uint128} \&}]{\+\_\+a }\end{DoxyParamCaption})}

copy ctor

\mbox{\Hypertarget{types_8h_a5dc4f1787a04c99e251cd68bc631c7b3}\label{types_8h_a5dc4f1787a04c99e251cd68bc631c7b3}} 
\index{types.\+h@{types.\+h}!uint128@{uint128}}
\index{uint128@{uint128}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{uint128()}{uint128()}\hspace{0.1cm}{\footnotesize\ttfamily [4/6]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::uint128 (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a8f95e75e58492e87412191fabadd8ca8}{uint32} \&}]{\+\_\+a }\end{DoxyParamCaption})}

initialized from an unsigned int

\mbox{\Hypertarget{types_8h_a38af0db38b8983c09e453dbb2a423b35}\label{types_8h_a38af0db38b8983c09e453dbb2a423b35}} 
\index{types.\+h@{types.\+h}!uint128@{uint128}}
\index{uint128@{uint128}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{uint128()}{uint128()}\hspace{0.1cm}{\footnotesize\ttfamily [5/6]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::uint128 (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a3d594eb72953c94a18a03d929ebd9167}{int32} \&}]{\+\_\+a }\end{DoxyParamCaption})}

initialized from anint, a $>$= 0

\mbox{\Hypertarget{types_8h_ab68fd9ef279f5a248fe93b1206cbc559}\label{types_8h_ab68fd9ef279f5a248fe93b1206cbc559}} 
\index{types.\+h@{types.\+h}!uint128@{uint128}}
\index{uint128@{uint128}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{uint128()}{uint128()}\hspace{0.1cm}{\footnotesize\ttfamily [6/6]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::uint128 (\begin{DoxyParamCaption}\item[{const \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} \&}]{\+\_\+a }\end{DoxyParamCaption})}

initialized from an unsigned long int

\mbox{\Hypertarget{types_8h_affa82c4225cfcd81baaccd829d3d1c0b}\label{types_8h_affa82c4225cfcd81baaccd829d3d1c0b}} 
\index{types.\+h@{types.\+h}!uint40@{uint40}}
\index{uint40@{uint40}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{uint40()}{uint40()}\hspace{0.1cm}{\footnotesize\ttfamily [1/7]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::uint40 (\begin{DoxyParamCaption}{ }\end{DoxyParamCaption})}

\mbox{\Hypertarget{types_8h_a4ba3483a239f25b1c755c75e19475edb}\label{types_8h_a4ba3483a239f25b1c755c75e19475edb}} 
\index{types.\+h@{types.\+h}!uint40@{uint40}}
\index{uint40@{uint40}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{uint40()}{uint40()}\hspace{0.1cm}{\footnotesize\ttfamily [2/7]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::uint40 (\begin{DoxyParamCaption}\item[{std\+::uint32\+\_\+t}]{l,  }\item[{std\+::uint8\+\_\+t}]{h }\end{DoxyParamCaption})}

\mbox{\Hypertarget{types_8h_a5e660390adddb6b4c8b4e041f0466e86}\label{types_8h_a5e660390adddb6b4c8b4e041f0466e86}} 
\index{types.\+h@{types.\+h}!uint40@{uint40}}
\index{uint40@{uint40}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{uint40()}{uint40()}\hspace{0.1cm}{\footnotesize\ttfamily [3/7]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::uint40 (\begin{DoxyParamCaption}\item[{const \hyperlink{classuint40}{uint40} \&}]{a }\end{DoxyParamCaption})}

\mbox{\Hypertarget{types_8h_aaf73c1c2f7134d2c727ccfbc94736b2d}\label{types_8h_aaf73c1c2f7134d2c727ccfbc94736b2d}} 
\index{types.\+h@{types.\+h}!uint40@{uint40}}
\index{uint40@{uint40}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{uint40()}{uint40()}\hspace{0.1cm}{\footnotesize\ttfamily [4/7]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::uint40 (\begin{DoxyParamCaption}\item[{const std\+::int32\+\_\+t \&}]{a }\end{DoxyParamCaption})}

\mbox{\Hypertarget{types_8h_aeb67d0e1054914c055fd6340c46e9b86}\label{types_8h_aeb67d0e1054914c055fd6340c46e9b86}} 
\index{types.\+h@{types.\+h}!uint40@{uint40}}
\index{uint40@{uint40}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{uint40()}{uint40()}\hspace{0.1cm}{\footnotesize\ttfamily [5/7]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::uint40 (\begin{DoxyParamCaption}\item[{const std\+::uint32\+\_\+t \&}]{a }\end{DoxyParamCaption})}

\mbox{\Hypertarget{types_8h_ae19857f157c887383d1a7c165ce9519a}\label{types_8h_ae19857f157c887383d1a7c165ce9519a}} 
\index{types.\+h@{types.\+h}!uint40@{uint40}}
\index{uint40@{uint40}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{uint40()}{uint40()}\hspace{0.1cm}{\footnotesize\ttfamily [6/7]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::uint40 (\begin{DoxyParamCaption}\item[{const std\+::uint64\+\_\+t \&}]{a }\end{DoxyParamCaption})}

\mbox{\Hypertarget{types_8h_a42b38cde4ba7cf52ccc3ab60547e002a}\label{types_8h_a42b38cde4ba7cf52ccc3ab60547e002a}} 
\index{types.\+h@{types.\+h}!uint40@{uint40}}
\index{uint40@{uint40}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{uint40()}{uint40()}\hspace{0.1cm}{\footnotesize\ttfamily [7/7]}}
{\footnotesize\ttfamily \+\_\+\+\_\+attribute\+\_\+\+\_\+\+::uint40 (\begin{DoxyParamCaption}\item[{const std\+::int64\+\_\+t \&}]{a }\end{DoxyParamCaption})}

\subsection{Variable Documentation}
\mbox{\Hypertarget{types_8h_af03243776893bcf5923a8f446b8d851c}\label{types_8h_af03243776893bcf5923a8f446b8d851c}} 
\index{types.\+h@{types.\+h}!\+\_\+\+\_\+attribute\+\_\+\+\_\+@{\+\_\+\+\_\+attribute\+\_\+\+\_\+}}
\index{\+\_\+\+\_\+attribute\+\_\+\+\_\+@{\+\_\+\+\_\+attribute\+\_\+\+\_\+}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{\+\_\+\+\_\+attribute\+\_\+\+\_\+}{\_\_attribute\_\_}}
{\footnotesize\ttfamily class \hyperlink{classuint128}{uint128} \+\_\+\+\_\+attribute\+\_\+\+\_\+}

\mbox{\Hypertarget{types_8h_ab09b9b43d1b1783c78e39783e382b3dd}\label{types_8h_ab09b9b43d1b1783c78e39783e382b3dd}} 
\index{types.\+h@{types.\+h}!bytes@{bytes}}
\index{bytes@{bytes}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{bytes}{bytes}}
{\footnotesize\ttfamily const size\+\_\+t bytes = 16\hspace{0.3cm}{\ttfamily [static]}}

number of bytes, 16

\mbox{\Hypertarget{types_8h_af113dea6c24342761f00f6b36e99032e}\label{types_8h_af113dea6c24342761f00f6b36e99032e}} 
\index{types.\+h@{types.\+h}!digits@{digits}}
\index{digits@{digits}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{digits}{digits}}
{\footnotesize\ttfamily const size\+\_\+t digits = 128\hspace{0.3cm}{\ttfamily [static]}}

number of digits/bits, 128

\mbox{\Hypertarget{types_8h_a558f35d10292a79de791071eb8088a8c}\label{types_8h_a558f35d10292a79de791071eb8088a8c}} 
\index{types.\+h@{types.\+h}!high@{high}}
\index{high@{high}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{high}{high}}
{\footnotesize\ttfamily \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} high\hspace{0.3cm}{\ttfamily [private]}}

higher part, uint64

\mbox{\Hypertarget{types_8h_ade07039efd8c0cfca1f9cead48259d4d}\label{types_8h_ade07039efd8c0cfca1f9cead48259d4d}} 
\index{types.\+h@{types.\+h}!low@{low}}
\index{low@{low}!types.\+h@{types.\+h}}
\subsubsection{\texorpdfstring{low}{low}}
{\footnotesize\ttfamily \hyperlink{types_8h_a60e8696a4678cd348e991a1f172e53f7}{uint64} low\hspace{0.3cm}{\ttfamily [private]}}

lower part, uint64

### 2017-01-24 archive/latex/validate2_8cpp.tex
2017/01/24

\hypertarget{validate2_8cpp}{}\section{code/src/validate2.cpp File Reference}
\label{validate2_8cpp}\index{code/src/validate2.\+cpp@{code/src/validate2.\+cpp}}
{\ttfamily \#include \char`\"{}validate2.\+h\char`\"{}}\newline
\subsection*{Functions}
\begin{DoxyCompactItemize}
\item 
int \hyperlink{validate2_8cpp_a3c04138a5bfe5d72780bb7e82a18e627}{main} (int argc, char $\ast$$\ast$argv)
\end{DoxyCompactItemize}

\subsection{Function Documentation}
\mbox{\Hypertarget{validate2_8cpp_a3c04138a5bfe5d72780bb7e82a18e627}\label{validate2_8cpp_a3c04138a5bfe5d72780bb7e82a18e627}} 
\index{validate2.\+cpp@{validate2.\+cpp}!main@{main}}
\index{main@{main}!validate2.\+cpp@{validate2.\+cpp}}
\subsubsection{\texorpdfstring{main()}{main()}}
{\footnotesize\ttfamily int main (\begin{DoxyParamCaption}\item[{int}]{argc,  }\item[{char $\ast$$\ast$}]{argv }\end{DoxyParamCaption})}

### 2017-01-24 archive/latex/validate2_8h.tex
2017/01/24

\hypertarget{validate2_8h}{}\section{code/src/validate2.h File Reference}
\label{validate2_8h}\index{code/src/validate2.\+h@{code/src/validate2.\+h}}

validate sa and lcp using internal memory sorts and Karp-\/rabin finger-\/print function.

{\ttfamily \#include \char`\"{}common/common.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}common/tuples.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}common/widget.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}common/basicio.\+h\char`\"{}}\newline
\subsection*{Classes}
\begin{DoxyCompactItemize}
\item 
class \hyperlink{class_validate2}{Validate2$<$ alphabet\+\_\+type, size\+\_\+type $>$}
\begin{DoxyCompactList}\small\item\em a suffix and L\+CP array validater \end{DoxyCompactList}\item 
struct \hyperlink{struct_validate2_1_1_r_interval}{Validate2$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\+R\+Interval}
\begin{DoxyCompactList}\small\item\em store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, ... \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
validate sa and lcp using internal memory sorts and Karp-\/rabin finger-\/print function.

Copyright (c) 2016, Sun Yat-\/sen University, All rights reserved

\begin{DoxyNote}{Note}
The alphaber size of the input string is assumed to be O(1) or O(n).

This method requires multiple sequential scans for the input string. During each scan, all the fingerprints are computed by an iterative way. This has become the bottleneck to the system\textquotesingle{}s running time.
\end{DoxyNote}
\begin{DoxyAuthor}{Author}
Yi Wu 
\end{DoxyAuthor}
\begin{DoxyDate}{Date}
2016.\+12 
\end{DoxyDate}

### 2017-01-24 archive/latex/validate3_8cpp.tex
2017/01/24

\hypertarget{validate3_8cpp}{}\section{code/src/validate3.cpp File Reference}
\label{validate3_8cpp}\index{code/src/validate3.\+cpp@{code/src/validate3.\+cpp}}
{\ttfamily \#include \char`\"{}validate3.\+h\char`\"{}}\newline
\subsection*{Functions}
\begin{DoxyCompactItemize}
\item 
int \hyperlink{validate3_8cpp_a3c04138a5bfe5d72780bb7e82a18e627}{main} (int argc, char $\ast$$\ast$argv)
\end{DoxyCompactItemize}
\subsection*{Variables}
\begin{DoxyCompactItemize}
\item 
char $\ast$ \hyperlink{validate3_8cpp_a598d558168ea9fcc902baf4a3a42a5ea}{prog\+\_\+name}
\end{DoxyCompactItemize}

\subsection{Function Documentation}
\mbox{\Hypertarget{validate3_8cpp_a3c04138a5bfe5d72780bb7e82a18e627}\label{validate3_8cpp_a3c04138a5bfe5d72780bb7e82a18e627}} 
\index{validate3.\+cpp@{validate3.\+cpp}!main@{main}}
\index{main@{main}!validate3.\+cpp@{validate3.\+cpp}}
\subsubsection{\texorpdfstring{main()}{main()}}
{\footnotesize\ttfamily int main (\begin{DoxyParamCaption}\item[{int}]{argc,  }\item[{char $\ast$$\ast$}]{argv }\end{DoxyParamCaption})}

\subsection{Variable Documentation}
\mbox{\Hypertarget{validate3_8cpp_a598d558168ea9fcc902baf4a3a42a5ea}\label{validate3_8cpp_a598d558168ea9fcc902baf4a3a42a5ea}} 
\index{validate3.\+cpp@{validate3.\+cpp}!prog\+\_\+name@{prog\+\_\+name}}
\index{prog\+\_\+name@{prog\+\_\+name}!validate3.\+cpp@{validate3.\+cpp}}
\subsubsection{\texorpdfstring{prog\+\_\+name}{prog\_name}}
{\footnotesize\ttfamily char$\ast$ prog\+\_\+name}

### 2017-01-24 archive/latex/validate3_8h.tex
2017/01/24

\hypertarget{validate3_8h}{}\section{code/src/validate3.h File Reference}
\label{validate3_8h}\index{code/src/validate3.\+h@{code/src/validate3.\+h}}

validate sa and lcp using external memory sorts and Karp-\/rabin finger-\/print function.

{\ttfamily \#include \char`\"{}common/common.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}common/tuples.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}common/widget.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}common/basicio.\+h\char`\"{}}\newline
\subsection*{Classes}
\begin{DoxyCompactItemize}
\item 
class \hyperlink{class_validate3}{Validate3$<$ alphabet\+\_\+type, size\+\_\+type $>$}
\begin{DoxyCompactList}\small\item\em validate sa and lcp using Karp-\/\+Rabin fingerprinting function \end{DoxyCompactList}\item 
struct \hyperlink{struct_validate3_1_1_r_interval}{Validate3$<$ alphabet\+\_\+type, size\+\_\+type $>$\+::\+R\+Interval}
\begin{DoxyCompactList}\small\item\em store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, ... \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Macros}
\begin{DoxyCompactItemize}
\item 
\#define \hyperlink{validate3_8h_aed71fcd0df9f567ccbffeda93549cefc}{T\+E\+S\+T\+\_\+\+V\+A\+L\+I\+D\+A\+T\+E3}
\end{DoxyCompactItemize}

\subsection{Detailed Description}
validate sa and lcp using external memory sorts and Karp-\/rabin finger-\/print function.

Copyright (c) 2016, Sun Yat-\/sen University, All rights reserved

\begin{DoxyNote}{Note}
The alphaber size of the input string is assumed to be O(1) or O(n).

This is the first method reported in xxx.
\end{DoxyNote}
\begin{DoxyAuthor}{Author}
Yi Wu 
\end{DoxyAuthor}
\begin{DoxyDate}{Date}
2016.\+12 
\end{DoxyDate}

\subsection{Macro Definition Documentation}
\mbox{\Hypertarget{validate3_8h_aed71fcd0df9f567ccbffeda93549cefc}\label{validate3_8h_aed71fcd0df9f567ccbffeda93549cefc}} 
\index{validate3.\+h@{validate3.\+h}!T\+E\+S\+T\+\_\+\+V\+A\+L\+I\+D\+A\+T\+E3@{T\+E\+S\+T\+\_\+\+V\+A\+L\+I\+D\+A\+T\+E3}}
\index{T\+E\+S\+T\+\_\+\+V\+A\+L\+I\+D\+A\+T\+E3@{T\+E\+S\+T\+\_\+\+V\+A\+L\+I\+D\+A\+T\+E3}!validate3.\+h@{validate3.\+h}}
\subsubsection{\texorpdfstring{T\+E\+S\+T\+\_\+\+V\+A\+L\+I\+D\+A\+T\+E3}{TEST\_VALIDATE3}}
{\footnotesize\ttfamily \#define T\+E\+S\+T\+\_\+\+V\+A\+L\+I\+D\+A\+T\+E3}

### 2017-01-24 archive/latex/validate4_8cpp.tex
2017/01/24

\hypertarget{validate4_8cpp}{}\section{code/src/validate4.cpp File Reference}
\label{validate4_8cpp}\index{code/src/validate4.\+cpp@{code/src/validate4.\+cpp}}
{\ttfamily \#include \char`\"{}validate4.\+h\char`\"{}}\newline
\subsection*{Functions}
\begin{DoxyCompactItemize}
\item 
int \hyperlink{validate4_8cpp_a3c04138a5bfe5d72780bb7e82a18e627}{main} (int argc, char $\ast$$\ast$argv)
\end{DoxyCompactItemize}
\subsection*{Variables}
\begin{DoxyCompactItemize}
\item 
char $\ast$ \hyperlink{validate4_8cpp_a598d558168ea9fcc902baf4a3a42a5ea}{prog\+\_\+name}
\end{DoxyCompactItemize}

\subsection{Function Documentation}
\mbox{\Hypertarget{validate4_8cpp_a3c04138a5bfe5d72780bb7e82a18e627}\label{validate4_8cpp_a3c04138a5bfe5d72780bb7e82a18e627}} 
\index{validate4.\+cpp@{validate4.\+cpp}!main@{main}}
\index{main@{main}!validate4.\+cpp@{validate4.\+cpp}}
\subsubsection{\texorpdfstring{main()}{main()}}
{\footnotesize\ttfamily int main (\begin{DoxyParamCaption}\item[{int}]{argc,  }\item[{char $\ast$$\ast$}]{argv }\end{DoxyParamCaption})}

\subsection{Variable Documentation}
\mbox{\Hypertarget{validate4_8cpp_a598d558168ea9fcc902baf4a3a42a5ea}\label{validate4_8cpp_a598d558168ea9fcc902baf4a3a42a5ea}} 
\index{validate4.\+cpp@{validate4.\+cpp}!prog\+\_\+name@{prog\+\_\+name}}
\index{prog\+\_\+name@{prog\+\_\+name}!validate4.\+cpp@{validate4.\+cpp}}
\subsubsection{\texorpdfstring{prog\+\_\+name}{prog\_name}}
{\footnotesize\ttfamily char$\ast$ prog\+\_\+name}

### 2017-01-24 archive/latex/validate4_8h.tex
2017/01/24

\hypertarget{validate4_8h}{}\section{code/src/validate4.h File Reference}
\label{validate4_8h}\index{code/src/validate4.\+h@{code/src/validate4.\+h}}

A two-\/phase validator for suffix and L\+CP arrays verification.

{\ttfamily \#include \char`\"{}common/common.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}common/tuples.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}common/widget.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}common/basicio.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}test.\+h\char`\"{}}\newline
\subsection*{Classes}
\begin{DoxyCompactItemize}
\item 
class \hyperlink{class_validate4}{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$}
\begin{DoxyCompactList}\small\item\em vaildate SA and L\+CP following the induced-\/sorting principle \end{DoxyCompactList}\item 
struct \hyperlink{struct_validate4_1_1_bkt_info}{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+Bkt\+Info}
\begin{DoxyCompactList}\small\item\em record L-\/type, S-\/type and L\+MS bucket sizes (no matter empty or non-\/empty) in SA \& L\+CP \end{DoxyCompactList}\item 
struct \hyperlink{struct_validate4_1_1_l_m_s_validate}{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+L\+M\+S\+Validate}
\begin{DoxyCompactList}\small\item\em validate S\+A\+\_\+\+L\+MS \& L\+C\+P\+\_\+\+L\+MS \end{DoxyCompactList}\item 
struct \hyperlink{struct_validate4_1_1_l_m_s_validate_1_1_r_interval}{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+L\+M\+S\+Validate\+::\+R\+Interval}
\begin{DoxyCompactList}\small\item\em store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, ... \end{DoxyCompactList}\item 
struct \hyperlink{struct_validate4_1_1_retrieve_pre}{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+Retrieve\+Pre}
\begin{DoxyCompactList}\small\item\em retrieve preceding items (pre\+\_\+ch \& pre\+\_\+t) for L-\/type, S-\/type and L\+MS suffixes \end{DoxyCompactList}\item 
struct \hyperlink{struct_validate4_1_1_r_m_q}{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+R\+MQ}
\begin{DoxyCompactList}\small\item\em \hyperlink{struct_validate4_1_1_r_m_q}{R\+MQ}. \end{DoxyCompactList}\item 
struct \hyperlink{struct_validate4_1_1_r_scan}{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+R\+Scan}
\begin{DoxyCompactList}\small\item\em scan SA rightward to validate the S\+A-\/values of all the L-\/type suffixes and the L\+C\+P-\/values of them and their left neighbors in SA. \end{DoxyCompactList}\item 
struct \hyperlink{struct_validate4_1_1_l_scan}{Validate4$<$ alphabet\+\_\+type, alphabet\+\_\+extension\+\_\+type, size\+\_\+type $>$\+::\+L\+Scan}
\begin{DoxyCompactList}\small\item\em scan SA \& L\+CP rightward to validate the S\+A-\/values of all the S-\/type suffixes and the L\+C\+P-\/values of them and their left neighbor in SA. \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
A two-\/phase validator for suffix and L\+CP arrays verification.

Copyright (c) 2016, Sun Yat-\/sen University, All rights reserved

A Karp-\/\+Rabin method is employed to check S\+A\+\_\+\+L\+MS \& L\+C\+P\+\_\+\+L\+MS. This method is also applied to the verification for SA and L\+CP, where an implementation can be found in \hyperlink{validate3_8h}{validate3.\+h}/validate3.cpp When finished checking S\+A\+\_\+\+L\+MS \& L\+C\+P\+\_\+\+L\+MS, we validate SA \& L\+CP following the idea of the induced-\/sorting principle and R\+MQ.

\begin{DoxyNote}{Note}
The alphabet size of the input string is assumed to be constant.

A description (with more details) is available in our draft attached. 
\end{DoxyNote}
\begin{DoxyAuthor}{Author}
Yi Wu 
\end{DoxyAuthor}
\begin{DoxyDate}{Date}
2017.\+1 
\end{DoxyDate}

### 2017-01-24 archive/latex/validate_8cpp.tex
2017/01/24

\hypertarget{validate_8cpp}{}\section{code/src/validate.cpp File Reference}
\label{validate_8cpp}\index{code/src/validate.\+cpp@{code/src/validate.\+cpp}}
{\ttfamily \#include \char`\"{}validate.\+h\char`\"{}}\newline
\subsection*{Functions}
\begin{DoxyCompactItemize}
\item 
int \hyperlink{validate_8cpp_a3c04138a5bfe5d72780bb7e82a18e627}{main} (int argc, char $\ast$$\ast$argv)
\end{DoxyCompactItemize}
\subsection*{Variables}
\begin{DoxyCompactItemize}
\item 
char $\ast$ \hyperlink{validate_8cpp_a598d558168ea9fcc902baf4a3a42a5ea}{prog\+\_\+name}
\end{DoxyCompactItemize}

\subsection{Function Documentation}
\mbox{\Hypertarget{validate_8cpp_a3c04138a5bfe5d72780bb7e82a18e627}\label{validate_8cpp_a3c04138a5bfe5d72780bb7e82a18e627}} 
\index{validate.\+cpp@{validate.\+cpp}!main@{main}}
\index{main@{main}!validate.\+cpp@{validate.\+cpp}}
\subsubsection{\texorpdfstring{main()}{main()}}
{\footnotesize\ttfamily int main (\begin{DoxyParamCaption}\item[{int}]{argc,  }\item[{char $\ast$$\ast$}]{argv }\end{DoxyParamCaption})}

\subsection{Variable Documentation}
\mbox{\Hypertarget{validate_8cpp_a598d558168ea9fcc902baf4a3a42a5ea}\label{validate_8cpp_a598d558168ea9fcc902baf4a3a42a5ea}} 
\index{validate.\+cpp@{validate.\+cpp}!prog\+\_\+name@{prog\+\_\+name}}
\index{prog\+\_\+name@{prog\+\_\+name}!validate.\+cpp@{validate.\+cpp}}
\subsubsection{\texorpdfstring{prog\+\_\+name}{prog\_name}}
{\footnotesize\ttfamily char$\ast$ prog\+\_\+name}

### 2017-01-24 archive/latex/validate_8h.tex
2017/01/24

\hypertarget{validate_8h}{}\section{code/src/validate.h File Reference}
\label{validate_8h}\index{code/src/validate.\+h@{code/src/validate.\+h}}

first method for validating suffix and L\+CP arrays

{\ttfamily \#include \char`\"{}common/common.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}common/basicio.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}common/widget.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}stxxl/timer\char`\"{}}\newline
\subsection*{Classes}
\begin{DoxyCompactItemize}
\item 
class \hyperlink{class_validate}{Validate$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$}
\begin{DoxyCompactList}\small\item\em validate suffix and L\+CP arrays using Karp-\/\+Rarbin finger-\/printing function \end{DoxyCompactList}\item 
struct \hyperlink{struct_validate_1_1_r_interval}{Validate$<$ alphabet\+\_\+type, size\+\_\+type, offset\+\_\+type $>$\+::\+R\+Interval}
\begin{DoxyCompactList}\small\item\em store (R \% P)$^\wedge$1, (R \% P)$^\wedge$2, (R \% P)$^\wedge$4, ... \end{DoxyCompactList}\end{DoxyCompactItemize}
\subsection*{Macros}
\begin{DoxyCompactItemize}
\item 
\#define \hyperlink{validate_8h_a864a52c772f23a04bcef46a40c9efed4}{T\+E\+S\+T\+\_\+1}
\item 
\#define \hyperlink{validate_8h_a1cc15202a800a32df74352e452309c57}{S\+T\+A\+T\+I\+S\+T\+I\+C\+S\+\_\+\+C\+O\+L\+L\+E\+C\+T\+I\+ON}
\end{DoxyCompactItemize}

\subsection{Detailed Description}
first method for validating suffix and L\+CP arrays

Copyright (c) 2016, Sun Yat-\/sen University, All rights reserved

Given suffix and L\+CP arrays, validate their correctness using external memory sorts and Karp-\/\+Rabin Finger-\/printing function.

The alphabet of input string is assumed to be O(1) or O(n).

\begin{DoxyAuthor}{Author}
Yi Wu 
\end{DoxyAuthor}
\begin{DoxyDate}{Date}
2016.\+12 
\end{DoxyDate}

\subsection{Macro Definition Documentation}
\mbox{\Hypertarget{validate_8h_a1cc15202a800a32df74352e452309c57}\label{validate_8h_a1cc15202a800a32df74352e452309c57}} 
\index{validate.\+h@{validate.\+h}!S\+T\+A\+T\+I\+S\+T\+I\+C\+S\+\_\+\+C\+O\+L\+L\+E\+C\+T\+I\+ON@{S\+T\+A\+T\+I\+S\+T\+I\+C\+S\+\_\+\+C\+O\+L\+L\+E\+C\+T\+I\+ON}}
\index{S\+T\+A\+T\+I\+S\+T\+I\+C\+S\+\_\+\+C\+O\+L\+L\+E\+C\+T\+I\+ON@{S\+T\+A\+T\+I\+S\+T\+I\+C\+S\+\_\+\+C\+O\+L\+L\+E\+C\+T\+I\+ON}!validate.\+h@{validate.\+h}}
\subsubsection{\texorpdfstring{S\+T\+A\+T\+I\+S\+T\+I\+C\+S\+\_\+\+C\+O\+L\+L\+E\+C\+T\+I\+ON}{STATISTICS\_COLLECTION}}
{\footnotesize\ttfamily \#define S\+T\+A\+T\+I\+S\+T\+I\+C\+S\+\_\+\+C\+O\+L\+L\+E\+C\+T\+I\+ON}

\mbox{\Hypertarget{validate_8h_a864a52c772f23a04bcef46a40c9efed4}\label{validate_8h_a864a52c772f23a04bcef46a40c9efed4}} 
\index{validate.\+h@{validate.\+h}!T\+E\+S\+T\+\_\+1@{T\+E\+S\+T\+\_\+1}}
\index{T\+E\+S\+T\+\_\+1@{T\+E\+S\+T\+\_\+1}!validate.\+h@{validate.\+h}}
\subsubsection{\texorpdfstring{T\+E\+S\+T\+\_\+1}{TEST\_1}}
{\footnotesize\ttfamily \#define T\+E\+S\+T\+\_\+1}

### 2017-01-24 archive/latex/widget_8h.tex
2017/01/24

\hypertarget{widget_8h}{}\section{code/src/common/widget.h File Reference}
\label{widget_8h}\index{code/src/common/widget.\+h@{code/src/common/widget.\+h}}

sort elements in external memory

{\ttfamily \#include \char`\"{}common.\+h\char`\"{}}\newline
{\ttfamily \#include \char`\"{}stxxl/sorter\char`\"{}}\newline
\subsection*{Classes}
\begin{DoxyCompactItemize}
\item 
struct \hyperlink{struct_pair_less1st}{Pair\+Less1st$<$ pair\+\_\+type $>$}
\begin{DoxyCompactList}\small\item\em sort pair by 1st component in ascending order \end{DoxyCompactList}\item 
struct \hyperlink{struct_pair_less2nd}{Pair\+Less2nd$<$ pair\+\_\+type $>$}
\begin{DoxyCompactList}\small\item\em sort pair by 2nd component in ascending order \end{DoxyCompactList}\item 
struct \hyperlink{struct_ex_vector}{Ex\+Vector$<$ value\+\_\+type $>$}
\begin{DoxyCompactList}\small\item\em template for vector \end{DoxyCompactList}\item 
struct \hyperlink{structtuple__less__comparator__1st}{tuple\+\_\+less\+\_\+comparator\+\_\+1st$<$ tuple\+\_\+type $>$}
\begin{DoxyCompactList}\small\item\em function object for comparing tuples by their first component in ascending order \end{DoxyCompactList}\item 
struct \hyperlink{structtuple__great__comparator__1st}{tuple\+\_\+great\+\_\+comparator\+\_\+1st$<$ tuple\+\_\+type $>$}
\begin{DoxyCompactList}\small\item\em function object for comparing tuples by their first component in ascending order \end{DoxyCompactList}\item 
struct \hyperlink{structtuple__less__comparator__2nd}{tuple\+\_\+less\+\_\+comparator\+\_\+2nd$<$ tuple\+\_\+type $>$}
\begin{DoxyCompactList}\small\item\em function object for comparing tuples by their first two component in ascending order \end{DoxyCompactList}\item 
struct \hyperlink{struct_ex_tuple_sorter}{Ex\+Tuple\+Sorter$<$ tuple\+\_\+type, tuple\+\_\+comparator\+\_\+type $>$}
\begin{DoxyCompactList}\small\item\em template for sorter \end{DoxyCompactList}\end{DoxyCompactItemize}

\subsection{Detailed Description}
sort elements in external memory

Copyright (c) 2016, Sun Yat-\/sen University, All rights reserved

Input elements are grouped into multiple blocks. Elements in each block are sorted in R\+AM and the result is stored in external memory. The block-\/wise results are combined into a whole using a heap in R\+AM at last.

\begin{DoxyAuthor}{Author}
Yi Wu 
\end{DoxyAuthor}
\begin{DoxyDate}{Date}
2016.\+12 
\end{DoxyDate}

### 2017-01-24 draft/draft.tex
2017/01/24

% !TeX spellcheck = en_US

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{graphicx}
\usepackage[ruled, noend]{algorithm2e}
\usepackage{url}
\usepackage{epstopdf}
\usepackage{indentfirst}
\usepackage[tight,footnotesize]{subfigure}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{color}
\usepackage{enumerate}

\newtheorem{Formula}{Formula}
\newtheorem{Lemma}{Lemma}
\newtheorem{Corollary}{Corollary}
\newtheorem{Property}{Property}
\newtheorem{Rule}{Rule}

% *** CITATION PACKAGES ***
\ifCLASSOPTIONcompsoc
\usepackage[nocompress]{cite}
\else
\usepackage{cite}
\fi

\begin{document}

\title{Checking Big Suffix and LCP Arrays by Probabilistic Methods}

\author{
	Yi~Wu,
	Ge~Nong,
	Wai~Hong~Chan,
	Ling~Bo~Han% <-this % stops a space
	\IEEEcompsocitemizethanks{
		\IEEEcompsocthanksitem Y. Wu, G. Nong (corresponding author) and L.~B.~Han are with the Department of Computer Science, Sun Yat-sen University, Guangzhou 510275, China. E-mails: wu.yi.christian@gmail.com, issng@mail.sysu.edu.cn, hanlb@mail2.sysu.edu.cn.

		\IEEEcompsocthanksitem Wai Hong Chan (corresponding author) is with the Department of Mathematics and Information Technology, The Education University of Hong Kong, Hong Kong. E-mail: waihchan@ied.edu.hk.
}}% <-this % stops a space

\IEEEtitleabstractindextext{%
\begin{abstract}

	For full-text indexing of massive data, the suffix and LCP (longest common prefix) arrays have been recognized as the fundamental data structures and should be verified to ensure their correctness after construction. We propose in this paper two methods to probablisitically check the suffix and LCP arrays in external memory by using a Karp-Rabin fingerprinting function, in terms of that the checking result is wrong with only a negligible probability. The first method checks the lexical order and the LCP-value of two neighboring suffixes in the given suffix array by computing and comparing the fingerprints of their LCPs. The second method first applies the same technique to check a subset of the suffix and LCP arrays, and then checks the remaining when augmenting them from the verified part following the induced-sorting principle. The experimental results indicate that, xxx.

\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
	Suffix and LCP arrays, verification, Karp-Rabin fingerprinting function.
\end{IEEEkeywords}}

% make the title area
\maketitle

\IEEEdisplaynontitleabstractindextext

\IEEEpeerreviewmaketitle

\section{Introduction}\label{sec:introduction}

\subsection{Background} \label{sec:introduction:background}

Suffix and longest common prefix (LCP) arrays play an important role in various string processing tasks, such as data compression, pattern matching and genome assembly. In dozens of applications, these two data structures are combined to constitute a powerful full-text index for massive data, called enhanced suffix array~\cite{Abouelhodaa2004}, which is more space efficient than suffix tree and applicable to emulating any searching functionalities provided by the latter in the same time complexity. During the past decades, much effort has been put on the development of designing efficient suffix array construction algorithms~(SACAs). Specifically, the first internal-memory algorithm for building SA was introduced in~\cite{Manber1993}. From then on, a plethora of SACAs have been proposed on different computation models, e.g., internal memory~\cite{Karkkainen2003, Ko2003, Kim2003, Nong11}, external memory~\cite{Dementiev2008, Ferragina2012, Manzini2004, Bingmann12, Karkkainen2014, Nong14, Nong15} and shared memory models~\cite{Osipov2012, Deo2013, Wang2015, Karkkainen2015}. In respect of the design on LCP-array construction algorithms~(LACAs), the existing works can be classified into two categories, where the algorithms of the first category compute the suffix and LCP arrays in the same time~\cite{Fischer11, Bingmann12, Flick2015} and that of the second category take the suffix array (SA) and/or Burrows-Wheeler transform (BWT) as input to facilitate the computation~\cite{Kasai2001,Karkkainen2009, Fischer11, Puglisi2008, Puglisi2008, Deo2013, Karkkainen2016}.

While the study for efficient construction of suffix and LCP arrays is evolving, the programs implementing the proposed algorithms are commonly provided ``as is", with the purpose only for the performance evaluation experiemnts of the articles where they are reported. That is, these programms give no guarantee that they have correctly implemented the proposed algorithms. The programs for recently proprosed algorithms are becoming much more complicated than before, casuing more difficulties for program verifying and debugging\footnote{In our studies before, we have exprienced problems caused by bugs of the exisitng programs.}. As a common practice, a suffix or LCP array checker is also provided for verifying the correctness of a constructed array. For example, such a checker is provided in the software packages eSAIS \cite{xxx} (DC3, pScan and etc? more and better) for constructing suffix and/or LCP arrays. In addition to help avoid implementation bugs, a checker is also demanded for an array constructed by a probabilistic algorithm \cite{xxx}. In this case, the array is correct with a probability and hence must be verified by a checker to ensure its correctness.

As far as we know, the work presented in~\cite{Burkhardt2003} is the only SA checking method that can be found in the existing literature, and no efficient approach for the LCP-array verification has been reported yet. In particular, there is currently no reported solution that can check both the suffix and the LCP arrays in external memory. This motivates our work here to design efficient external memory algorithms for checking the suffix and LCP arrays of massive data.

\subsection{Contribution}\label{sec:introduction:contribution}

The contribution in this paper mainly includes two methods for checking the given suffix and LCP arrays in external memory, where both methods work for constant alphabets and the former can be also applied to integer ones.

In principle, the first method checks the lexical order and the LCP-value of two neighboring suffixes in the suffix array by literally comparing their characters in sequence. To reduce time complexity for the string comparison, we employ a Karp-Rabin fingerprinting function to transform each of the involved comparand into a single integer, called fingerprint, and compare the fingerprints instead to correctly check the equality of their prototypes with a negilible error probability. We will demonstrate that all the fingerprints in need can be calculated using linear time when scanning the input string. The experimental results indicate that the space efficiency remains invaraint with the increasing of input size, while both time and I/O consumptions grows linearly under the same circumstances.

The second method verifies the two arrays following the induced-sorting principle.

The second method verifies the two arrays following the induced-sorting principle, which was formerly proposed for building suffix and LCP arrays in both internal and external memory.

 This technique is also employed in the second method 
The second method is adapted from the induced-sorting principle.

The second method checks both suffix and LCP arrays based on the induced-sorting principle. The main idea is to first check a subset of the suffix and LCP arrays and then verify the inducing process to ensure the correctness of the final suffix and LCP arrays augmented from the subset. Different from the previous method, it can be also integrated into any algorithm for inducing suffix and LCP arrays to build and check the arrays simultaneously.

The remainder of this paper is organized as follows. We describe the proposed methods and algorithms in Sections~\ref{sec:method1} and~\ref{sec:method2}, then present the experimental results in Section~\ref{sec:experiment}, and give the conclusion in Section~\ref{sec:conclusion}.

{\color{red}

A suggested paper's framework:

1. The straightforward algorithm for computing and comparing the FPs of each pair of neighboring items in the LCP array, for checking both the SA and the LCP arrays.

The drawback is space consuming, to be overcome by the algorithms proposed in the rest of this article...

2. The method for building and checking simultaneously, for the suffix and LCP arrays constructed by induced sorting.

The principle of induced sorting is explained here.

The drawback is that it is applicable only for an array built by inducd sorting, to be overcome by further extending the idea to check any given array.

3. Extend the 2nd method to check any given suffix or LCP arrays.

4. Experiments

5. Conclusion
}

	\section{Method A} \label{sec:method1}

	\subsection{Notations} \label{sec:method1:notations}
	Given an input string $x[0, n)$ drawn from an alphabet $\Sigma$, we say $x[i, j]$ is a substring of $x$ that starts with $x[i]$ and ends with $x[j]$. Particularly, $x[i, j]$ is a suffix of $x$ if $j = n - 1$. For short, we denote $x[i, n)$ by ${\sf suf}(i)$.

	The suffix array of $x$, denoted by $sa$, is a permutation of $\{0, 1, \dots, n - 1\}$ such that ${\sf suf}(sa[i])$ is lexicographically greater than ${\sf suf}(sa[i - 1])$ for all $i \in [1, n)$.

	The LCP array of $x$, denoted by $lcp$, is composed of $n$ integers, where $lcp[0] = 0$ and $lcp[i]$ equals to the length of LCP of ${\sf suf}(sa[i])$ and ${\sf suf}(sa[i - 1])$ for all $i \in [1, n)$, i.e., the first $lcp[i]$ characters of ${\sf suf}(sa[i])$ and ${\sf suf}(sa[i - 1])$ are identical and the $(lcp[i]+1)$-th characters of two suffixes are different. For notation convenience, we refer the length of an LCP as LCP value or LCP length.

	\subsection{Main Idea} \label{sec:method1:idea}

	We first present in Lemma~\ref{lemma:1} the conditions that are sufficient and necessary for checking the suffix and LCP arrays. Specifically, condition (1) demonstrates that all the suffixes in $x$ are sorted in $sa$, while conditions (2)-(3) indicate that the order and the LCP value of any two neighboring suffixes in $sa$ are both correct.

	\begin{Lemma} \label{lemma:1}
		Both $sa[0, n)$ and $lcp[0, n)$ are correct if and only if the following conditions are satisfied, for all $i \in [1, n)$:
		\begin{enumerate}[(1)]
			\item
			$sa$ is a permutation of $\{0, 1, \dots, n - 1\}$.
			\item
			$x[sa[i], sa[i] + lcp[i] - 1] = x[sa[i - 1], sa[i - 1] + lcp[i] - 1]$.
			\item
			$x[sa[i] + lcp[i]] > x[sa[i - 1] + lcp[i]]$. 	
		\end{enumerate}
	\end{Lemma}

	\begin{IEEEproof}
		Both the sufficiency and necessity are immediately seen from the definition of suffix and LCP arrays.
	\end{IEEEproof}

	Obviously, we can generalize Lemma~\ref{lemma:1} to check any subset of $sa$ and $lcp$. Besides, given that $sa$ or $lcp$ is correct, this lemma can be used to check $lcp$ or $sa$ alone as well.

	For each pair of neighboring suffixes in $sa$, say ${\sf suf}(sa[i])$ and ${\sf suf}(sa[i + 1])$, it takes at worst $\mathcal{O}(n)$ time to perform a character-wise string comparison for checking their leftmost $lcp[i]$ characters. An alternative is to compare the two sequences of characters by their hash values in constant time. This can be done using a perfect hash function~(PHF) that maps two strings to an identical integer if and only if they are literally equal to each other. However, the cost of finding a PHF is non-negligible in practice, thus we prefer to use the Karp-Rabin fingerprinting function~\cite{Karp1987} for conducting the string-to-integer transformations mentioned above. Concretely, given a prime $L$ and an integer $\delta \in [1, L)$, the fingerprint of a substring $x[i, j]$, denoted by ${\sf fp}(i, j)$, can be calculated according to the following two formulas:

	\begin{Formula} \label{formula:1}
		${\sf fp}(0, i) = {\sf fp}(0, i - 1) \cdot {\delta} + x[i]\mod L$ for $i \ge 0$, or ${\sf fp}(0, i) = 0$ for $i < 0$.

	\end{Formula}

	\begin{Formula} \label{formula:2}
		${\sf fp}(i, j) = {\sf fp}(0, j) - {\sf fp}(0 ,i - 1) \cdot {\delta}^{j - i + 1}\mod L$.

	\end{Formula}

	Notice that two equal substrings always have a common fingerprint, but the inverse is not true. Fortunately, it has been proved that the probability of a false match can be reduced to a negligible level by setting $L$ properly~\cite{Karp1987}. This property is utilized in~\cite{Bille2013} to design a probabilistic algorithm for computing a sparse suffix array. Using the fingerprinting function, we have Corollary~\ref{corollary:1}.

	\begin{Corollary} \label{corollary:1}
		Both $sa[0, n)$ and $lcp[0, n)$ are correct with a high probability given the following conditions, for all $i \in [1, n)$:

		\begin{enumerate}[(1)]
			\item
			$sa$ is a permutation of $\{0, 1, \dots, n - 1\}$.

			\item
			${\sf fp}(sa[i], sa[i] + lcp[i] - 1) = {\sf fp}(sa[i - 1], sa[i - 1] + lcp[i] - 1)$.

			\item
			$x[sa[i] + lcp[i]] > x[sa[i - 1] + lcp[i]]$.
		\end{enumerate}

	\end{Corollary}

	\subsection{Algorithm} \label{sec:method1:algorithm}

	\begin{algorithm*}

		\SetAlgoNoLine

		\KwIn{$x$, $sa$, $lcp$}

		Step 1. Compute ${\sf fp}(sa[i], sa[i] + lcp[i] - 1)$ and retrieve $x[sa[i] + lcp[i]]$ for $i \in [1, n)$.

		Step 2. Compute ${\sf fp}(sa[i], sa[i] + lcp[i + 1] - 1)$ and retrieve $x[sa[i] + lcp[i + 1]]$ for $i \in [0, n - 1)$.

		Step 3. Check if ${\sf fp}(sa[i], sa[i] + lcp[i] - 1) = {\sf fp}(sa[i - 1], sa[i - 1] + lcp[i] - 1)$ and $x[sa[i] + lcp[i]] > x[sa[i - 1] + lcp[i]]$ for $i \in [1, n)$.

		\caption{The algorithm using Method A.}

		\label{alg:1}

	\end{algorithm*}

	We design Algorithm~\ref{alg:1} to check the conditions in Corollary~\ref{corollary:1}. This algorithm mainly consists of three steps and each step is explained detailedly in the following paragraphs.

	\vspace{1ex} \noindent {\bf Step 1.} The first step can be divided into three substeps:

	\begin{enumerate}

		\item [(1a)]
		Scan $sa$ and $lcp$ rightward with $i$ increasing from $1$ to $n - 1$. For each scanned $\langle sa[i], lcp[i] \rangle$, create an AITEM with $idx = i, pos = sa[i], lv = lcp[i]$. Sort the items by $pos$ in ascending order.

		\item [(1b)]
		Scan $x$ rightward with $p$ increasing from $0$ to $n - 1$. For each scanned $x[p]$, compute ${\sf fp}(0, p)$ and update all the AITEMs with $pos = p + 1$ by setting $fp = {\sf fp}(0, p)$ and $pos = pos + lv$. Sort the items by $pos$ in ascending order.

		\item [(1c)]
		Scan $x$ rightward with $p$ increasing from $0$ to $n - 1$. For each scanned $x[p]$, compute ${\sf fp}(0, p)$ and update all the AITEMs with $pos = p + 1$ by setting $fp = {\sf fp}(0, p) - fp \cdot {\delta}^{lv} \, mod \, L $ and $ch = x[p + 1]$. Sort the items by $idx$ in ascending order.

	\end{enumerate}

	An auxiliary data structure called AITEM is introduced to facilitate the computation of fingerprints, where each AITEM is a 5-tuple $\langle idx, pos, lv, ch, fp\rangle$ for a suffix. To enable fast calculation of ${\sf fp}(sa[i] - 1)/{\sf fp}(sa[i] + lcp[i] - 1)$ for all $i \in [1, n)$, step 2 first sorts the AITEMs by $pos$ and then sequentially retrieves ${\sf fp}(0, pos)$ for each item by iteratively computing $\{{\sf fp}(0, 0), {\sf fp}(0, 1), \dots, {\sf fp}(0, n - 1) \}$ according to Formula~\ref{formula:1}. Given that ${\sf fp}(sa[i] - 1)$ and ${\sf fp}(sa[i] + lcp[i] - 1)$ are already known, ${\sf fp}(sa[i], sa[i] + lcp[i] - 1)$ is obtained according to Formula~\ref{formula:2}.

	Notice that all the AITEMs are sorted by the starting positions of the corresponding suffixes in substep (1a). Thus, we check condition (1) of Corollary~\ref{corollary:1} during the time when sequentially accessing the items in substep (1b).

	\vspace{1ex} \noindent {\bf Step 2.} This step computes ${\sf fp}(sa[i], sa[i] + lcp[i + 1] - 1)$ for $i \in [0, n - 1)$ using the following three substeps:

	\begin{enumerate}

		\item [(2a)]
		Scan $sa$ and $lcp$ rightward with $i$ increasing from $0$ to $n - 2$. For each scanned $\langle sa[i], lcp[i + 1] \rangle$, create an AITEM with $idx = i, pos = sa[i], lv = lcp[i + 1]$. Sort the items by $pos$ in ascending order.

		\item [(2b)]
		Reuse step (1b) to update and sort AITEMs.

		\item [(2c)]
		Reuse step (1c) to update and sort AITEMs.

	\end{enumerate}

	The major difference between the first two steps lies in that, the field $lv$ of the AITEMs for ${\sf suf}(sa[i])$ are respectively set as $lcp[i]$ and $lcp[i + 1]$ in substeps (1a) and (2a).

	\vspace{1ex} \noindent {\bf Step 3.} Let $arrA$ and $arrB$ denote the arrays of AITEMs produced by steps 1 and 2, respectively. Scan $arrA$ and $arrB$ rightward with $i$ increasing from $0$ to $n - 2$. For each pair $\langle arrA[i], arrB[i]\rangle$, check if $arrA[i].fp = arrB[i].fp$ and $arrA[i].ch > arrB[i].ch$ to ensure the correctness of conditions (2)-(3) in Corollary~\ref{corollary:1}.

	\subsection{Substring Fingerprint} \label{sec:method1:fingerprint}

	Algorithm~\ref{alg:1} computes ${\sf fp}(i, j)$ from ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ according to Formula~\ref{formula:2}. Let $e$ denote $j - i + 1$, then the coefficient $(\delta^{e} \mod L)$ must be calculated quickly or it will become a performance bottleneck. One approach first decomposes $e$ into $k_1 \cdot m + k_2$ and then computes $\delta^{e}$ by multiplying $\delta^{k_1 \cdot m}$ and $\delta^{k_2}$, where $k_1, k_2$ are integers and $k_1 \in [0, \lceil \frac{n}{m} \rceil], k_2 \in [0, m)$. An alternative first decomposes $e$ into $\Sigma_{i = 0}^{\lceil \log2^n \rceil}{k_i \cdot 2^i}$ and then computes $\Pi_{i = 0}^{\lceil \log2^n \rceil}{\delta}^{k_i \cdot 2^i}$ to obtain $\delta^{e}$, where $k_i \in \{0, 1\}$. The first approach answers in ${O}(1)$ time and consumes $\mathcal{O}(m + \lceil \frac{n}{m} \rceil )$ space to maintain two lookup tables for storing $\{{\delta}^{0}, {\delta}^{m}, \dots, {\delta}^{\lceil \frac{n}{m} \rceil m}\}$ and $\{{\delta}^{0}, {\delta}^{1},\dots,{\delta}^{m - 1} \}$, respectively, while the second approach answers in $\mathcal{O}(\lceil \log2^n \rceil)$ time and consumes $\mathcal{O}(\lceil \log2^n \rceil)$ space to store $\{{\delta}^{1}, {\delta}^{2}, \dots, {\delta}^{2^{\lceil \log2^n \rceil}} \}$. For a better space performance, we adopt the second approach to compute the fingerprints in our implementation for the algorithm.

	\subsection{Analysis} \label{sec:method1:analysis}

	Algorithm~\ref{alg:1} performs multiple scans and sorts for fixed-size objects with integer keys.	Consider an external memory model with RAM size $M$, disk size $D$ and block size $B$, all are in words, then the time and I/O complexities for a scan are $\mathcal{O}(n)$ and $\mathcal{O}(n / B)$, respectively, while those for an integer sort are $\mathcal{O}(n\log_{M/ B}(n / B))$ and $\mathcal{O}((n / B)\log_{M / B}(n / B))$, respectively~\cite{Arge2013}. Besides, the algorithm reaches its peak disk use when sorting $n$ AITEMs in external memory during the second step. Given that each input character occupies $a$ words and each fingerprint occupies $b$ words, the space consumption for each sort is $(a + b + 3)n$ words.

	\subsection{Example} \label{sec:method1:example}

	\section{Method B} \label{sec:method2}

	As we will see from the experimental study in Section~\ref{sec:experiment}, Algorithm~\ref{alg:1} designed by Method A is quite space consuming, the peak disk use is 40 bytes per input character. This motivates us to design a lightweight checker that uses less space. In this section, we propose a method for checking the suffix and LCP arrays using the induced-sorting principle. The experimental results show that Algorithm~\ref{alg:3} designed by this method consumes about 40\% less space than Algorithm~\ref{alg:1} on real-world data.

	\subsection{Notations} \label{sec:algorithm2:notations}

	Assume $x[n - 1]$ is lexicographically the smallest character in $\Sigma$ and appears in $x[0, n)$ only once, we introduce the following notations and symbols for description clarity.

	{\em L-type/S-type/LMS character and suffix.} All the characters in $x$ are classified into three different types, namely L-type, S-type and LMS. In details, $x[i]$ is S-type if (1) $i = n - 1$ or (2) $x[i] < x[i + 1]$ or (3) $x[i] = x[i+1]$ and $x[i+1]$ is S-type; otherwise, $x[i]$ is L-type. In particular, if $x[i - 1]$ and $x[i]$ are respectively L-type and S-type, then $x[i]$ is LMS. Furthermore, ${\sf suf}(i)$ is L-type, S-type or LMS if $x[i]$ is L-type, S-type or LMS, respectively.

	{\em L-type/S-type/LMS substring.} Suppose $x[j]$ is LMS and no characters in $x[i + 1, j - 1]$ are LMS, then substring $x[i, j]$ is an L-type, S-type or LMS substring if $x[i]$ is L-type, S-type or LMS, respectively.

	{\em Suffix buckets.} Suffixes in $sa$ are naturally grouped into multiple buckets, where each bucket occupies a contiguous interval of $sa$ and contains all the suffixes with an identical heading character. Besides, a bucket can be further divided into two parts, where the left/right part is a subbucket containing only L-type/S-type suffixes. For short, we use ${\sf sa\_bkt}(c)$ to denote the bucket containing all the suffixes with a heading character $c$, and ${\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$ to denote the left/right subbucket in ${\sf sa\_bkt}(c)$.

	{\em LCP buckets.} Suppose ${\sf sa\_bkt}(c)$ is a suffix bucket ranging from $sa[i]$ to $sa[j]$, then $lcp[i, j]$ is the corresponding LCP bucket, denoted by ${\sf lcp\_bkt}(c)$, and it can be further divided into two subbuckets ${\sf lcp\_bkt_L}(c)$ and ${\sf lcp\_bkt_S}(c)$ according to ${\sf sa\_bkt_L}(c)$ and ${\sf sa\_bkt_S}(c)$.

	{\em Character repetition count.} Suppose $x[i] = x[i + 1] = \dots = x[j]$ and $x[j] \ne x[j + 1]$, then $j - i + 1$ is the number of successive repetitions for $x[i]$. Let ${\sf rep}(i)$ denote the value.

	{\em Inverse suffix array.} The inverse suffix array $isa$ satisfies that $isa[sa[i]] = i$ for $i \in [0, n)$.

	{\em Reduced string.} The reduced string $x_1$ records the names of LMS suffixes, where each name represents the relative order of the corresponding suffix among all the LMS ones.

	{\em Position array.} The position array $pa$ records the starting positions of LMS suffixes.

	{\em Type array.} The type array $t$ records the types of characters in $x$. Let $t[i] = 0$ or $1$ if $x[i]$ is L-type or S-type, respectively.

	In addition, we denote the suffix and LCP arrays of LMS suffixes by $sa_{\sf LMS}$ and $lcp_{\sf LMS}$.

	\subsection{An Overview of Inducing LCP Array} \label{sec:method2:overview}

	\begin{algorithm*}

		\SetAlgoNoLine

		\KwIn{$x$, $sa_1$, $lcp_1$}

		\KwOut{$sa$, $lcp$}

		S1. Compute $sa_{\sf LMS}$ and $lcp_{\sf LMS}$ from $sa_1$ and $lcp_1$, respectively.

		S2. Insert items of $sa_{\sf LMS}$ and $lcp_{\sf LMS}$ into $sa$ and $lcp$. \label{alg:2:step:1}

		S3. Induce L-type suffixes and LCP lengths.

		S4. Induce S-type suffixes and LCP lengths.

		\caption{The algorithm of the induction phase for an induced-sorting LACA.}

		\label{alg:2}

	\end{algorithm*}

	An induced-sorting SACA~(e.g.,~\cite{Nong11}) mainly consists of a reduction phase followed by an induction phase. In brief, it first sorts and names the LMS substrings to produce the reduced string $x_1$ during the reduction phase and then determines whether there exist two equal characters in $x_1$. If yes, then it recursively performs the reduction phase by replacing $x$ with $x_1$; otherwise, it computes $sa_1$ from $x_1$ and performs the induction phase to induce $sa$ from $sa_1$. The work presented in~\cite{Fischer11} shows that an induced-sorting SACA can be modified to design an LACA for constructing the suffix and LCP arrays simultaneously, which principle is explained here for readers to understand our method. Its main idea is to compute the LCP value of two suffixes placed at the neighboring positions in the same subbucket according to the following properties, where ${\sf suf}(sa[j])$ and ${\sf suf}(sa[k])$ are the suffixes from which induce ${\sf suf}(sa[i - 1])$ and ${\sf suf}(sa[i])$ during the induction phase.

	\begin{Property} \label{property:1}
		If $x[sa[i]] = x[sa[i - 1]]$, $t[sa[i]] = t[sa[i - 1]]$ and $x[sa[j]] \ne x[sa[k]]$, then $lcp[i] = 1$.

	\end{Property}

	\begin{Property} \label{property:2}
		If $x[sa[i]] = x[sa[i - 1]]$, $t[sa[i]] = t[sa[i - 1]]$ and $x[sa[j]] = x[sa[k]]$, then $lcp[i] = 1 + {\sf min}(lcp[j + 1], lcp[j + 2], \dots, lcp[k])$.

	\end{Property}

	Algorithm~\ref{alg:2} summarizes the main steps of the induction phase of the induced-sorting LACA in~\cite{Fischer11}. Suppose ${sa_{\sf LMS}}$ and $lcp_{\sf LMS}$ have been computed and their elements are inserted into the corresponding buckets in $sa$ and $lcp$, the last two steps of the algorithm are described below.

	\begin{enumerate}
		\item [S3.] Clear ${\sf sa\_bkt_L}(c)/{\sf lcp\_bkt_L}(c)$ for $c \in \Sigma$ in $sa/lcp$.
		\begin{enumerate}[(1)]
			\item
			Scan $sa$ rightward with $i$ increasing from $0$ to $n - 1$. For each scanned item $sa[i]$, insert $sa[i] - 1$ into the leftmost empty position of ${\sf sa\_bkt_L}(x[sa[i] - 1])$ if ${\sf t}[sa[i] - 1] = 0$.
			\item
			For each induced item placed in $sa[i]$: set $lcp[i] = 0$ if $x[sa[i]] \ne x[sa[i - 1]]$; otherwise, compute $lcp[i]$ following Properties~\ref{property:1}-\ref{property:2}.
		\end{enumerate}

		\item [S4.] Clear ${\sf sa\_bkt_S}(c)/{\sf lcp\_bkt_S}(c)$ for $c \in \Sigma$ in $sa/lcp$.
		\begin{enumerate}[(1)]
			\item
			Scan $sa$ leftward with $i$ decreasing from $n - 1$ to $0$. For each scanned item $sa[i]$, insert $sa[i] - 1$ into the rightmost empty position of ${\sf sa\_bkt_S}(x[sa[i] - 1])$ if ${\sf t}[sa[i] - 1] = 1$.
			\item
			For each induced item placed in $sa[i - 1]$: if $x[sa[i]] = x[sa[i - 1]]$ and $t[sa[i]] = t[sa[i - 1]]$, then compute $lcp[i]$ following Properties~\ref{property:1}-\ref{property:2}.
		\end{enumerate}

	\end{enumerate}

	There remain two special cases needing to be handled separately. When inducing L-type suffixes in S3, the LCP value of the rightmost L-type and the leftmost LMS suffixes in the same bucket, say ${\sf suf}(sa[i_1])$ and ${\sf suf}(sa[i_2])$, is equal to ${\sf min}({\sf rep}(sa[i_1]), {\sf rep}(sa[i_2]))$. Likewise, when inducing S-type suffixes in S4, the LCP value of the rightmost L-type and the leftmost S-type suffixes in the same bucket is computed following the same way. Notice that, ${\sf rep}(sa[i_1])/{\sf rep}(sa[i_2])$ is calculated by literally comparing the characters in the suffix from left to right. It is revealed in~\cite{Fischer11} that, a repetition interval cannot stride over two successive LMS substrings, thus all the involved comparisons can be done in overall linear running time.

	\subsection{Check LCP Array} \label{sec:method2:check_lcp}

	The inducing process of the LCP array in Section~\ref{sec:method2:overview} also constitutes the sufficient and neccessary conditions for a correct $lcp$ as stated below.

	\begin{Lemma}
		\label{lcp:correct}
		Given that $sa$ is correct, $lcp$ is correct if and only if:
		\begin{itemize}
			\item[(1)]
			$lcp_{\sf LMS}$ is correct.

			\item[(2)]
			$lcp[i]$ is equal to the value calculated by the inducing process in Section~\ref{sec:method2:overview}, for $i \in [0, n)$.

		\end{itemize}
	\end{Lemma}

	This lemma suggests a method to check an LCP array as follows.
	We address two cases: (1) given $lcp_{\sf LMS}$ and correct $sa$, to build and check $lcp$ simultaneously; (2) given $lcp$ and correct $sa$, to check $lcp$.

	Notice that the processes for inducing and checking $lcp$ are essentially the same in terms of that both utilize condition (2) in Lemma \ref{lcp:correct}, the only difference is that the former computes $lcp[i]$ using the condition but the latter checks if the condition is held for each given $lcp[i]$.

	\vspace{1ex} \noindent {\bf Case 1.} In the first case, we first check $lcp_{\sf LMS}$ by Method A, then induce and check $lcp$ from $lcp_{\sf LMS}$ simultaneously. The problem to be solved is that when an item is induced into a bucket, its corresponding item $lcp[i]$ to be compared is not known yet.
	Our solution for this is to integrate the processes of inducing and checking into a single one, by ensuring the sequence of items induced into a bucket in $lcp$ in the inducing process is identical to that later seen by the scanning process that is also the checking process.
	For each bucket, we increasingly compute the fingerprints of both sequences and check their equality during the whole process for inducing $lcp$.
	If the two fingerprints for each bucket are equal, then the condition (2) of Lemma~\ref{lcp:correct} will be seen by the checking process with a high probability.
	As a result, $lcp$ can be built and probabilistically checked in the same time using this method, for this we have Corollary~\ref{corollary:2}.

	\begin{Corollary} \label{corollary:2}
	Given that $sa$ is correct, then $lcp$ is correct with a high probability if and only if these conditions are satisfied for all $c \in \Sigma$:

		(1) $lcp_{\sf LMS}$ is correct.

		(2) The fingerprints of $lcp_{\sf L1}(c)$ and $lcp_{\sf L2}(c)$ are equal.

		(3) The fingerprints of $lcp_{\sf S2}(c)$ and $lcp_{\sf S2}(c)$ are equal.

	\end{Corollary}

	For each $c$, $lcp_{\sf L2}(c)/lcp_{\sf S2}(c)$ or $lcp_{\sf L1}(c)/lcp_{\sf S1}(c)$ records the sequences of items in ${\sf lcp\_bkt_L}(c)/{\sf lcp\_bkt_S}(c)$ in their order of being scanned or induced, respectively. We augment S3 and S4 of Algorithm~\ref{alg:2} to compute the fingerprints of these sequences as follows:

	\begin{enumerate}

		\item [S3'.] Initialize ${\sf fp}(lcp_{\sf L1}(c)) = 0$ and ${\sf fp}(lcp_{\sf L2}(c)) = 0$.

		\begin{enumerate} [(1)]

			\item For each scanned item $sa[i]$, update ${\sf fp}(lcp_{\sf L2}(c))$ by $lcp[i]$ if $x[sa[i]] = c$ and $t[sa[i]] = 0$.

			\item For each induced item placed in $sa[i]$, update ${\sf fp}(lcp_{\sf L1}(c))$ by $lv$ if $x[sa[i]] = c$, where $lv$ is the calculated LCP value.

		\end{enumerate}

		\item [S4'.] Initialize ${\sf fp}(lcp_{\sf S1}(c)) = 0$ and ${\sf fp}(lcp_{\sf S2}(c)) = 0$.

		\begin{enumerate}[(1)]

			\item  For each scanned item $sa[i]$, update ${\sf fp}(lcp_{\sf S2}(c))$ by $lcp[i]$ if $x[sa[i]] = x[sa[i - 1]] = c$ and $t[sa[i]] = t[sa[i - 1]] = 1$.

			\item For each induced item placed at $sa[i - 1]$, update $lcp_{\sf S1}(c)$ by $lv$ if $x[sa[i - 1]] = x[sa[i]] = c$ and $t[sa[i - 1]] = t[sa[i]] = 1$, where $lv$ is the calculated LCP value.

		\end{enumerate}

	\end{enumerate}

	We generalize Formula~\ref{formula:1} in Section~\ref{sec:method1:idea} to iteratively compute the fingerprint of each sequence in steps S3' and S4'. Specifically, when a new item $e$ is appended to a sequence, its fingerprint $fp$ is updated according to the formula $fp = fp \cdot \delta + e \mod L$.

	\vspace{1ex} \noindent {\bf Case 2.} In the second case, we first scan $lcp$ to compute $lcp_{\sf LMS}$ and check $lcp_{\sf LMS}$ by Method A, then induce and check the LCP array from $lcp_{\sf LMS}$ following the same idea of the first case. After that, we compare the given $lcp$ with the induced LCP array to ensure the correctness of the former.

	\subsection{Check Suffix Array} \label{sec:method2:check_sa}

	An induced-sorting SACA determines the order of two suffixes by comparing their heading characters and succeeding suffixes in $x$. In other words, Property~\ref{property:3} is held for any two suffixes placed in $sa[i]$ and $sa[j]$, where ${\sf suf}(sa[p])$ and ${\sf suf}(sa[q])$ are the two suffixes from which induce ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$ during the induction phase.

	\begin{Property} \label{property:3}
		If $(x[sa[i]], p) > (x[sa[j]], q)$, then $i > j$.

	\end{Property}

	As shown below, Property~\ref{property:3} can be used to constitute the sufficient and necessary conditions for a correct $sa$.

	\begin{Lemma} \label{lemma:3}
		$sa$ is correct if and only if:

		\begin{itemize}
			\item [(1)] $sa_{\sf LMS}$ is correct.

			\item [(2)] $i > j$ if $(x[sa[i]], p) > (x[sa[j]], q)$, for $i, j \in [0, n)$.

		\end{itemize}

	\end{Lemma}

	We use Lemma~\ref{lemma:3} to check a suffix array in two cases: (1) given $sa_{\sf LMS}$, to build and check $sa$ in the same time; (2) given $sa$, to check $sa$.

	\vspace{1ex} \noindent {\bf Case 1.} In the first case, we first check $sa_{\sf LMS}$ by using Method A, and then induce and check $sa$ from $sa_{\sf LMS}$ by comparing the fingerprint of the sequence of items induced into a bucket with that of the sequence of items scanned in the bucket. If the two fingerprints are equal for each bucket, then the condition (2) of Lemma~\ref{lemma:3} are satisfied with a high probability. Following the discussion, we have Corollary~\ref{corollary:3}.

	\begin{Corollary} \label{corollary:3}
		$sa$ is correct with a high probability if and only if these conditions are satisfied for all $c \in \Sigma$:

		(1) $sa_{\sf LMS}$ is correct.

		(2) The fingerprints of $sa_{\sf L1}(c)$ and $sa_{\sf L2}(c)$ are equal.

		(3) The fingerprints of $sa_{\sf S2}(c)$ and $sa_{\sf S2}(c)$ are equal.

	\end{Corollary}

	For each $c$, $sa_{\sf L2}(c)/sa_{\sf S2}(c)$ or $sa_{\sf L1}(c)/sa_{S1}(c)$ records the sequence of items in ${\sf sa\_bkt_L}/{\sf sa\_bkt_S}$ in their order of being scanned or induced, respectively. Similar to S3' and S4', we compute the fingerprints of these sequences by augmenting the last two steps of Algorithm~\ref{alg:2} as follows:

	\begin{enumerate}

		\item [S3''.] Initialize ${\sf fp}(sa_{\sf L1}(c)) = 0$ and ${\sf fp}(sa_{\sf L2}(c)) = 0$.

		\begin{enumerate} [(1)]

			\item For each scanned item $sa[i]$, update ${\sf fp}(sa_{\sf L2}(c))$ by $sa[i]$ if $x[sa[i]] = c$ and $t[sa[i]] = 0$.

			\item For each induced item, update ${\sf fp}(sa_{\sf L1}(c))$ by $sa[j] - 1$ if $x[sa[j] - 1] = c$, where $sa[j]$ is the starting position of the suffix from which induces the item.

		\end{enumerate}

		\item [S4''.] Initialize ${\sf fp}(sa_{\sf S1}(c)) = 0$ and ${\sf fp}(sa_{\sf S2}(c)) = 0$.

		\begin{enumerate}[(1)]

			\item For each scanned item $sa[i]$, update ${\sf fp}(sa_{\sf S2}(c))$ by $sa[i]$ if $x[sa[i]] = c$ and $t[sa[i]] = 1$.

			\item For each induced item, update ${\sf fp}(sa_{\sf S1}(c))$ by $sa[j] - 1$ if $x[sa[j] - 1] = c$, where $sa[j]$ is the starting position of the suffix from which induces the item.

		\end{enumerate}

	\end{enumerate}

		\vspace{1ex} \noindent {\bf Case 2.} In the second case, we first scan $sa$ to compute $sa_{\sf LMS}$ and check $sa_{\sf LMS}$ by using Method A, then induce and check the suffix array from $sa_{\sf LMS}$ following the same idea of the first case. Afterward, we compare the given $sa$ with the induced suffix array to ensure the correctness of the former.

	\subsection{Algorithms} \label{sec:method2:algorithm}

	We propose two external-memory algorithms based on the method described in Sections~\ref{sec:method2:check_lcp}-\ref{sec:method2:check_sa}. The first algorithm can build and check the suffix and LCP arrays simultaneously, while the second algorithm, called Algorithm~\ref{alg:3}, can check the two arrays after their construction.

	\subsubsection{Build and Check Simultaneously} \label{sec:method2:algorithm:sim}

	We adapt Algorithm~\ref{alg:2} to check the conditions of Corollaries~\ref{corollary:2}-\ref{corollary:3} when building the suffix and LCP arrays by an induced-sorting LACA.

	There are three places needed to be revised in Algorithm~\ref{alg:2}. The first place is to check $sa_{\sf LMS}$ and $lcp_{\sf LMS}$ using Algorithm~\ref{alg:1} after computing them in S1. The second place is to compute the fingerprints by adapting S3 and S4 of Algorithm~\ref{alg:2} as below:

	\begin{enumerate} [(1)]

		\item
		Augment S3 with S3' and S3'' to compute the fingerprints of ${\sf fp}(lcp_{\sf L1}(c)/lcp_{\sf L2}(c))$ and ${\sf fp}(sa_{\sf L1}(c)/sa_{\sf L2}(c))$ for all $c \in \Sigma$.

		\item
		Augment S4 with S4' and S4'' to compute the fingerprints of ${\sf fp}(lcp_{\sf S1}(c)/lcp_{\sf S2}(c))$ and ${\sf fp}(sa_{\sf S1}(c)/sa_{\sf S2}(c))$ for all $c \in \Sigma$.

	\end{enumerate}

	The third place is to compare the fingerprints after the inducing process.

	This algorithm can be applied to the external memory model if we extend Algorithm~\ref{alg:2} for inducing the suffix and LCP arrays using external memory by the method described in~\cite{Bingmann12}.

	\subsubsection{Build and Check Sequentially}

		Algorithm~\ref{alg:3} mainly consists of three steps. In the first step, it computes $sa_{\sf LMS}$ and $lcp_{\sf LMS}$ from $sa$ and $lcp$, and ensures their correctness by using Algorithm~\ref{alg:1}. In the second step, it checks the conditions of Corollaries~\ref{corollary:2}-\ref{corollary:3} to verify the suffix and LCP arrays induced from $sa_{\sf LMS}$ and $lcp_{\sf LMS}$. In the last step, it checks the given $sa$ and $lcp$ by comparing them with the induced suffix and LCP arrays. In what follows, we explain the algorithm step by step in more details for better understanding.

	\begin{algorithm}

		\SetAlgoNoLine

		\KwIn{$x$, $sa$, $lcp$}

		Step 1. Compute and check $sa_{\sf LMS}$ and $lcp_{\sf LMS}$.

		Step 2. Induce and check the suffix and LCP arrays from $sa_{\sf LMS}$ and $lcp_{\sf LMS}$.

		Step 3. Check $sa$ and $lcp$ by comparing them with the induced suffix and LCP arrays.

		\caption{The algorithm that performs verification after construction using Method B.}

		\label{alg:3}

	\end{algorithm}

	\vspace{1ex} \noindent {\bf Step 1.} This step computes $sa_{\sf LMS}$ and $lcp_{\sf LMS}$ from $sa$ and $lcp$ by the following three substeps:

	\begin{enumerate}
		\item [(1a)]
		Sort $i$ by $sa[i]$ for $i \in [0, n)$ to produce $isa$.

		\item [(1b)]
		Sort $\langle x[i - 1], t[i - 1], x[i], t[i], {\sf rep}(i) \rangle$ by $isa[i]$ for $i \in [0, n)$ to produce an array $arr$, where $arr[i]$ records $\langle x[sa[i] - 1], t[sa[i] - 1], x[sa[i]], t[sa[i]], {\sf rep}(sa[i]) \rangle$.

		\item [(1c)]
		Initialize $v=n$. Scan $sa$, $lcp$ and $arr$ rightward with $i$ increasing from $0$ to $n - 1$. For each scanned $\langle sa[i], lcp[i], arr[i] \rangle$: (1) if $lcp[i] < v$, then set $v = lcp[i]$; (2) if $t[sa[i] - 1] = 0$ and $t[sa[i]] = 1$, then append $sa[i]$ and $v$ to $sa_{\sf LMS}$ and $lcp_{\sf LMS}$, respectively, and reset $v = n$.

	\end{enumerate}

	As can be seen, step 1 determines whether or not a suffix is LMS by checking the types of its preceding and heading characters. To avoid random accesses to $x$ residing on disks, it first sorts the preceding and heading characters of suffixes by $isa$ to produce $arr$, and then scans $sa$, $lcp$ and $arr$ to identify all the LMS suffixes. During the process, for any two successively found LMS suffixes, say ${\sf suf}(sa[i_1])$ and ${\sf suf}(sa[i_2])$, the LCP length of them is calculated by tracing the minimum of $lcp[i_1 + 1, i_2]$. After that, $sa_{\sf LMS}$ and $lcp_{\sf LMS}$ are checked by using Algorithm~\ref{alg:1}.

	Notice that, when inducing in external memory, the heading characters of successively induced suffixes should be loaded into RAM by sequential I/O operations. For the purpose, the preceding characters calculated by substeps (1a)-(1b) are stored in external memory to facilitate the inducing process in step 2. Specifically, when scanning $arr$ in substep (1c), we distribute the elements of the array into $arr_{\sf L}, arr_{\sf S}$ and $arr_{\sf LMS}$ as following: append $arr[i]$ to $arr_{\sf L}$ or $arr_{\sf S}$ if $t[sa[i]] = 0$ or $1$, respectively, and append $arr[i]$ to $arr_{\sf LMS}$ if $t[sa[i] - 1] = 0$ and $t[sa[i]] = 1$.

	\vspace{1ex} \noindent {\bf Step 2.} This step employs two priority queues $PQ_{\sf L}$ and $PQ_{\sf S}$ to emulate the RAM-based inducing process in external memory, where each element of both priority queues is a 6-tuple $\langle ch, ty, ra, pos, lv, rp \rangle$ defined as below:

	\begin{itemize}

		\item $pos$: starting position of ${\sf suf}(pos)$.

		\item $ch$: heading character of ${\sf suf}(pos)$.

		\item $ty$: type of ${\sf suf}(pos)$.

		\item $ra$: rank of ${\sf suf}(pos)$.

		\item $lv$: LCP length of ${\sf suf}(pos)$ and its left or right neighbor in the induced SA.

		\item $rp$: ${\sf rep}(pos)$.	
	\end{itemize}

	At the very beginning, step 2 first scans $sa_{\sf LMS}$ and $lcp_{\sf LMS}$ to put the sorted LMS suffixes along with the corresponding LCP values into $PQ_{\sf L}$ with the sorting key $\langle ch, ty, ra\rangle$, then it pops the elements of $PQ_{\sf L}$ in ascending order to induce L-type suffixes. Specifically, for each visited element $e$, it retrieves the preceding character of ${\sf suf}(e.pos)$ from the leftmost unvisited element in $arr_{\sf L}$ or $arr_{\sf LMS}$ if $e.ty = 0$ or $1$, respectively. If the retrieved preceding character is L-type, then it computes the LCP length of ${\sf suf}(pos - 1)$ and its left neighbor in the induced SA, and puts the induced suffix along with the calculated LCP value into $PQ_{\sf L}$. Meanwhile, it puts ${\sf suf}(e.pos)$ into $PQ_{\sf S}$ if $e.ty = 0$.

	When $PQ_{\sf L}$ is empty, all the L-type suffixes are sorted in $PQ_{\sf S}$ with the sorting key $\langle ch, ty, ra\rangle$. Step 2 continues to pop the elements of $PQ_{\sf S}$ in descending order to induce S-type suffixes and their LCP values. For each visited element $e$, it retrieves the preceding character of ${\sf suf}(e.pos)$ from the rightmost unvisited element in $arr_{\sf L}$ or $arr_{\sf S}$ if $e.ty = 0$ or $1$, respectively. If the preceding character is S-type, then it calculates the LCP length of ${\sf suf}(e.pos - 1)$ and its right neighbor in the induced SA, and puts the induced suffix along with the calculated LCP value into $PQ_{\sf S}$. Meanwhile, it outputs $e.pos$ and $e.lv$ to build the suffix and LCP arrays.

	When $PQ_{\sf S}$ is empty, the construction of the suffix and LCP arrays is completed and the calculation of the required fingerprints is also finished. Then, step 2 compares the fingerprints to check the correctness of the induced suffix and LCP arrays.

	Notice that, we reuse a technique proposed in~\cite{Fischer11} to compute the LCP value of two neighboring suffixes in a subbucket according to Properties~\ref{property:1}-\ref{property:2}. Specifically, we record the heading characters and the LCP value of two suffixes from which most recently induce a suffix into ${\sf sa\_bkt}(c)$, for all $c \in \Sigma$. Given that $\Sigma$ is of a constant size, it takes overall $\mathcal{O}(n)$ time to keep the data structure up-to-date. Besides, for the rightmost L-type and the leftmost S-type/LMS suffixes in a bucket, we compare the repetition counts of their heading characters to compute the LCP length of them.

	\vspace{1ex} \noindent {\bf Step 3.} This step performs a scan on $sa$ and $lcp$ to compare the elements of them with those of the induced suffix and LCP arrays.

	\subsection{Analysis}

	Clearly, Algorithm~\ref{alg:3} can be implemented within sorting complexity in external memory. The space bottleneck of the algorithm occurs when inducing suffixes  during the second step. Suppose we respectively use $a$ and $b$ words to represent an input character and its type, then it takes at most $(3a + 3b)n$ words for storing $arr_{\sf L}, arr_{\sf S}$ and $arr_{\sf LMS}$ and $(4 + a + b)n$ words for sorting elements in $PQ_{\sf L}/PQ_{\sf S}$.

	\section{Experiments} \label{sec:experiment}

	We implement the prototypes of Algorithms~\ref{alg:1} and~\ref{alg:3} in external memory. Our programs for the algorithms are compiled by gcc/g++ 4.8.4 with -O3 options under ubuntu 14.04 64-bit operating system running on a desktop computer, which is equipped with an Intel Xeon E3-1220 V2 CPU, 4GiB RAM and 500GiB HD. The following metrics normalized by the input's size are investigated for performance evaluation on the real-world datasets listed in Table~\ref{tbl:1}:

	\begin{itemize}

		\item Running time: the running time in microseconds.

		\item Peak disk use: the peak use of external memory in bytes.

		\item I/O volume: the number of bytes read from and written to external memory.

	\end{itemize}

	%Table
	\renewcommand\arraystretch{1.3}
	\begin{table*}[!t]
		\caption{Corpus, $n$ in Gi, 1 byte per character}
		\label{tbl:1}
		\centering
		\begin{tabular}{|l|c|c|p{10cm}|}
			\hline
			Corpora & \multicolumn{1}{c|}{$n$} & \multicolumn{1}{c|}{$\|\Sigma\|$} & Description \\\hline
			enwiki & 8 & 256 & The 8-GiB prefix of an XML dump of English Wikipedia, available at \url{https://dumps.wikimedia.org/enwiki}, dated as 16/05/01. \\\hline	
			uniprot & 2.5 & 96 & UniProt Knowledgebase, available at \url{ftp://ftp.expasy.org/databases/.../complete}, dated as 16/05/11. \\\hline
			proteins & 1.1 & 27 & Swissprot database, available at \url{http://pizzachili.dcc.uchile.cl/texts/protein}, dated as 06/12/15. \\\hline
		\end{tabular}
	\end{table*}

	\subsection{Results}
	Some implementation choices in our programs are as follows. First, we use the second approach in Section~\ref{sec:method1:fingerprint} to facilitate the computation of fingerprints in Algorithm~\ref{alg:1}. Second, we employ the external-memory containers~(vector, sorter and priority queue) provided by the STXXL library~\cite{Dementiev2007} to perform scans and sorts on disks. Finally, we use a 32-bit integer to represent each fingerprint and a 40-bit integer to represent each element in the suffix/LCP arrays.

	For description convenience, we denote the programs for Algorithms~\ref{alg:1} and~\ref{alg:3} by ProgA and ProgB, respectively. As shown in Figure~\ref{fig:performance_analysis}, ProgA runs faster than ProgB on "enwiki", "uniprot" and "proteins" by about 20 percent. The speed gap between them is mainly due to the difference in their I/O efficiencies. Specifically, the I/O volume of ProgB is 190$n$ in average, while that of ProgA is kept at 155$n$ for different corpora. Notice that, although Algorithm~\ref{alg:3} reuses Algorithm~\ref{alg:1} to check $sa_{\sf LMS}$ and $lcp_{\sf LMS}$, the consumption for the verification of $sa_{\sf LMS}$ and $lcp_{\sf LMS}$ in ProgB is at most half of ProgA because the number of LMS suffixes is no more than $\frac{1}{2}n$. It can be also observed that both programs are insensitive to the input corpus in terms of the space requirement. In details, the peak disk uses of ProgA and ProgB are respectively 26$n$ and 40$n$ on the three corpora.

	We also investigate the performance trend of the two programs on the prefix of "enwiki" with the length varying on $\{1, 2, 4, 8\}$ GiB. Figure~\ref{fig:performance_analysis2} illustrates that, as the prefix length increases, a performance degradation occurs to ProgB in both time and I/O efficiencies, but the fluctuation of ProgA can be ignored.

	%figure
	\begin{figure}[htbp!]
		\centering
		\subfigure{
			\label{subfig:pdu_cmp}
			\includegraphics[width = 0.8\columnwidth]{pdu_cmp}
		}
		\hfil
		\subfigure{
			\label{subfig:iov_cmp}
			\includegraphics[width = 0.8\columnwidth]{io_cmp}
		}
		\hfil
		\subfigure{
			\label{subfig:ct_cmp}
			\includegraphics[width = 0.8\columnwidth]{ct_cmp}
		}
		\caption{Experimental results for various corpora.}
		\label{fig:performance_analysis}
	\end{figure}

	%figure
	\begin{figure}[htbp!]
		\centering
		\subfigure{
			\label{subfig:pdu_cmp2}
			\includegraphics[width = 0.8\columnwidth]{pdu_cmp2}
		}
		\hfil
		\subfigure{
			\label{subfig:iov_cmp2}
			\includegraphics[width = 0.8\columnwidth]{io_cmp2}
		}
		\hfil
		\subfigure{
			\label{subfig:ct_cmp2}
			\includegraphics[width = 0.8\columnwidth]{ct_cmp2}
		}
		\caption{Experimental results for prefixes of "enwiki".}
		\label{fig:performance_analysis2}
	\end{figure}

	\subsection{Discussions}

	It is identified that both programs heavily rely on the performance of the external memory sorter in use. A potential candidate for improving their speed is to adapt a GPU-based multi-way sorter~(e.g.,~\cite{Leischner2010, Davidson2012}) for sorting massive data using external memory. By the aid of these fast sorting algorithms, the throughputs of the programs are expected to nearly approach the I/O bandwidth. Besides, the first two steps of Algorithm~\ref{alg:1} are independent of each other and thus can be executed in parallel for acceleration. This technique can be also applied to check the suffix and LCP arrays of the LMS suffixes in Algorithm~\ref{alg:3}.

	Currently, for Algorithm~\ref{alg:3}, step 2 constitutes the space bottleneck. It is worthy of mentioning that this step produces a copy of the suffix and LCP array during the inducing and checking processes. Actually, given that $\Sigma$ is of a constant size and $sa/lcp$ are known already, we can simply scan the input $sa/lcp$ to perform the inducing process and compare each induced suffix/LCP value with that in the given $sa/lcp$ to perform the checking process, resulting in less space consumption. To the end, we must maintain a read pointer for each suffix/LCP bucket in $sa/lcp$ to scan elements in sequence.

	\section{Conclusions} \label{sec:conclusion}

	We present two probabilistic methods for checking the suffix and LCP arrays in external memory using the Karp-Rabin fingerprinting function. Both methods can be employed to verify the suffix and LCP arrays after their construction, while the second method can be also integrated into an induced-sorting LACA to perform construction and verification in the same time.

	We also design the algorithms for these two methods and implement the programs for performance evaluation. An experimental study is conducted to evaluate the time, space and I/O efficiencies.
	The results indicate that the program for the first method outperforms that for the second method in the running time and I/O volume by about 20 percent, while the peak disk use of the latter is about 26/40 = 0.65 as that of the former. There are still quite some opportunities to improve our algorithms and programs for better performance, for this our work has been undergoing.

	% Bibliography
	\bibliographystyle{IEEEtran}
	\bibliography{IEEEabrv,bibfile}

\end{document}

### 2017-01-24 archive/html/menudata.js

@@ -1,0 +1,114 @@
+var menudata={children:[
+{text:"Main Page",url:"index.html"},
+{text:"Namespaces",url:"namespaces.html",children:[
+{text:"Namespace List",url:"namespaces.html"},
+{text:"Namespace Members",url:"namespacemembers.html",children:[
+{text:"All",url:"namespacemembers.html"},
+{text:"Variables",url:"namespacemembers_vars.html"}]}]},
+{text:"Classes",url:"annotated.html",children:[
+{text:"Class List",url:"annotated.html"},
+{text:"Class Index",url:"classes.html"},
+{text:"Class Members",url:"functions.html",children:[
+{text:"All",url:"functions.html",children:[
+{text:"a",url:"functions.html#index_a"},
+{text:"b",url:"functions_b.html#index_b"},
+{text:"c",url:"functions_c.html#index_c"},
+{text:"d",url:"functions_d.html#index_d"},
+{text:"e",url:"functions_e.html#index_e"},
+{text:"f",url:"functions_f.html#index_f"},
+{text:"g",url:"functions_g.html#index_g"},
+{text:"h",url:"functions_h.html#index_h"},
+{text:"i",url:"functions_i.html#index_i"},
+{text:"l",url:"functions_l.html#index_l"},
+{text:"m",url:"functions_m.html#index_m"},
+{text:"o",url:"functions_o.html#index_o"},
+{text:"p",url:"functions_p.html#index_p"},
+{text:"q",url:"functions_q.html#index_q"},
+{text:"r",url:"functions_r.html#index_r"},
+{text:"s",url:"functions_s.html#index_s"},
+{text:"t",url:"functions_t.html#index_t"},
+{text:"u",url:"functions_u.html#index_u"},
+{text:"v",url:"functions_v.html#index_v"},
+{text:"w",url:"functions_w.html#index_w"},
+{text:"~",url:"functions_0x7e.html#index_0x7e"}]},
+{text:"Functions",url:"functions_func.html",children:[
+{text:"a",url:"functions_func.html#index_a"},
+{text:"b",url:"functions_func_b.html#index_b"},
+{text:"c",url:"functions_func_c.html#index_c"},
+{text:"d",url:"functions_func_d.html#index_d"},
+{text:"e",url:"functions_func_e.html#index_e"},
+{text:"f",url:"functions_func_f.html#index_f"},
+{text:"g",url:"functions_func_g.html#index_g"},
[…]

### 2017-01-24 archive/html/search/all_0.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['_5f_5fattribute_5f_5f',['__attribute__',['../types_8h.html#af03243776893bcf5923a8f446b8d851c',1,'__attribute__():&#160;types.h'],['../namespacestd.html#ade73df0294cb697bb61d5edf0deac7d0',1,'std::__attribute__()'],['../tuples_8h.html#a3287af29b6ef2cbe75f1caba87bdde63',1,'__attribute__((packed)):&#160;tuples.h'],['../tuples_8h.html#a61f5f588c8a34e43c27971a61e3a357d',1,'__attribute__((packed)):&#160;tuples.h'],['../tuples_8h.html#aa434f23135e2672ad8fe4ec768f3d88c',1,'__attribute__((packed)):&#160;tuples.h'],['../types_8h.html#aa5073eed52429ca9c68cfeef8163dadb',1,'__attribute__((packed)):&#160;types.h']]],
+  ['_5ftest_5fh',['_TEST_H',['../test_8h.html#aa8de6ad987cfa13b647db341b8dcc510',1,'test.h']]]
+];

### 2017-01-24 archive/html/search/all_1.js

@@ -1,0 +1,14 @@
+var searchData=
+[
+  ['accumulate',['accumulate',['../struct_validate4_1_1_bkt_info.html#ac4fb0eabb194f773cd4ac5f6bcbbe969',1,'Validate4::BktInfo']]],
+  ['add_5fl',['add_l',['../struct_validate4_1_1_bkt_info.html#af55a2b8eee03bfe617ab34759b4ac007',1,'Validate4::BktInfo']]],
+  ['add_5flms',['add_lms',['../struct_validate4_1_1_bkt_info.html#a5875efc6696925c0932f262174c2cc37',1,'Validate4::BktInfo']]],
+  ['add_5fs',['add_s',['../struct_validate4_1_1_bkt_info.html#a9c11b8915349954523623d9e7b0a2c2a',1,'Validate4::BktInfo']]],
+  ['alphabet_5fvector_5ftype',['alphabet_vector_type',['../class_test.html#aace52a5af52c5d5f457ec201881ab2ab',1,'Test::alphabet_vector_type()'],['../class_validate.html#a0323dd6f1096806748299dfd4f644b69',1,'Validate::alphabet_vector_type()'],['../class_validate2.html#a351a2e7bbfdf9b87ecbb4f08cdbc1e64',1,'Validate2::alphabet_vector_type()'],['../class_validate3.html#a7a893a89f745710a34958b37717cb024',1,'Validate3::alphabet_vector_type()'],['../class_validate4.html#a49c80b3d101be19542a4341c2387603a',1,'Validate4::alphabet_vector_type()']]],
+  ['async_5fmulti_5fstream_5freader',['async_multi_stream_reader',['../classasync__multi__stream__reader.html',1,'async_multi_stream_reader&lt; value_type &gt;'],['../classasync__multi__stream__reader.html#af83e5faafb7612b51abc05e8edde52dd',1,'async_multi_stream_reader::async_multi_stream_reader()']]],
+  ['async_5fmulti_5fstream_5fwriter',['async_multi_stream_writer',['../classasync__multi__stream__writer.html',1,'async_multi_stream_writer&lt; value_type &gt;'],['../classasync__multi__stream__writer.html#a7f94653dac5ce376bea3b330942b59b3',1,'async_multi_stream_writer::async_multi_stream_writer()']]],
[…]

### 2017-01-24 archive/html/search/all_10.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['quadruple',['quadruple',['../structquadruple.html',1,'quadruple&lt; T1, T2, T3, T4 &gt;'],['../structquadruple.html#ab4b318f9f20c5f861c0b7445bf806da8',1,'quadruple::quadruple()'],['../structquadruple.html#a24c753a7c00f8325bf7f738815e89d06',1,'quadruple::quadruple(const quadruple &amp;_item)'],['../structquadruple.html#a23034a914f2841aa59c833bb3923f1b6',1,'quadruple::quadruple(const T1 &amp;_first, const T2 &amp;_second, const T3 &amp;_third, const T4 &amp;_forth)'],['../tuples_8h.html#abc5517aabc587ce4dbe5d5d5c51e926e',1,'quadruple():&#160;tuples.h'],['../tuples_8h.html#ac6ecb9121ff7c7bc8f2bb354d86a7da9',1,'quadruple(const quadruple &amp;_item):&#160;tuples.h'],['../tuples_8h.html#a275ae5ff396331c5f894cae5e717aafd',1,'quadruple(const T1 &amp;_first, const T2 &amp;_second, const T3 &amp;_third, const T4 &amp;_forth):&#160;tuples.h']]]
+];

### 2017-01-24 archive/html/search/all_11.js

@@ -1,0 +1,15 @@
+var searchData=
+[
+  ['r',['R',['../common_8h.html#a465886396cb5767ddce1163c14db7209',1,'common.h']]],
+  ['read',['read',['../classasync__stream__reader.html#abb382de67d33724ff4fea6714fc67ac8',1,'async_stream_reader::read()'],['../classasync__stream__reader.html#ac441a02e7bb4708948552ce7ced4e9d4',1,'async_stream_reader::read(value_type *_des, uint64 _num)'],['../classasync__multi__stream__reader.html#ae47f5af3e9c0964be88975391631b3d4',1,'async_multi_stream_reader::read(const uint64 &amp;_file_idx)'],['../classasync__multi__stream__reader.html#a1b4db036726c5b33edf9cdca1ccc24d9',1,'async_multi_stream_reader::read(const uint64 &amp;_file_idx, value_type *_des, uint64 _num)']]],
+  ['read_5fat_5foffset',['read_at_offset',['../class_basic_i_o.html#a7aed99607484ece4b385e3fdced47e1c',1,'BasicIO::read_at_offset(value_type *_des, const uint64 &amp;_offset, const uint64 &amp;_cnt, const std::FILE *_f)'],['../class_basic_i_o.html#a934ed5d36b8a132b622c59c61b881bdd',1,'BasicIO::read_at_offset(value_type *_des, const uint64 &amp;_offset, const uint64 &amp;_cnt, const std::string &amp;_fn)']]],
+  ['read_5ffrom_5ffile',['read_from_file',['../structbuffer.html#a2abf8fde8a3d6a1245f57d698e207b74',1,'buffer::read_from_file()'],['../class_basic_i_o.html#a5e1c1be36914e4749f4a4bd0cf1b53d0',1,'BasicIO::read_from_file(value_type *_des, const uint64 &amp;_cnt, const std::FILE *_f)'],['../class_basic_i_o.html#a7e492b3c92dbb91e7f45cd5ed03365a3',1,'BasicIO::read_from_file(value_type *_des, const uint64 &amp;_cnt, const std::string &amp;_fn)']]],
+  ['readme_2emd',['readme.md',['../readme_8md.html',1,'']]],
+  ['reset',['reset',['../struct_validate4_1_1_r_m_q.html#a8416e95d49b4b8c05cd814d78017d81f',1,'Validate4::RMQ']]],
[…]

### 2017-01-24 archive/html/search/all_12.js

@@ -1,0 +1,18 @@
+var searchData=
+[
+  ['s_5fcur_5fbkt_5fis_5fempty',['s_cur_bkt_is_empty',['../struct_validate4_1_1_l_scan.html#a9331f92d91cf67c38a3d6948a2190df8',1,'Validate4::LScan']]],
+  ['s_5fis_5fempty',['s_is_empty',['../struct_validate4_1_1_l_scan.html#a071826b788f5aadc92f87ad8cc986649',1,'Validate4::LScan']]],
+  ['s_5ftype',['S_TYPE',['../common_8h.html#a726936e5500c7ab70b64cbc308774a97',1,'common.h']]],
+  ['second',['second',['../structpair.html#a63ae1bbd5a6ce6bd6167b5359fa7a01f',1,'pair::second()'],['../structtriple.html#a41050194c8c7984707c7ad13c96e8631',1,'triple::second()'],['../structquadruple.html#aa93ca1ef60012d07903333d7b16bb32b',1,'quadruple::second()'],['../tuples_8h.html#a9a8a97f32d498c09c0f1f82c8a67bd6f',1,'second():&#160;tuples.h']]],
+  ['send_5fno_5fmore_5ffull_5fbuffer_5fsignal',['send_no_more_full_buffer_signal',['../structbuffer__queue.html#a487335f8827c09d4d76d588e47d633ac',1,'buffer_queue::send_no_more_full_buffer_signal()'],['../structbuffer__queue.html#a487335f8827c09d4d76d588e47d633ac',1,'buffer_queue::send_no_more_full_buffer_signal()']]],
+  ['sentinel_5ftype',['SENTINEL_TYPE',['../common_8h.html#aceba1d712f3152d9ec9297ba5dd67f1b',1,'common.h']]],
+  ['set',['set',['../classuint40.html#ab23ea17f6248ac0e7dbacbb71a96179b',1,'uint40::set()'],['../types_8h.html#a9805ad2d84465b3a1c4aa12235f922c4',1,'set():&#160;types.h']]],
+  ['set_5fhigh',['set_high',['../classuint40.html#a4d8e0bfd4cb5f959d89d3966c10a28bc',1,'uint40::set_high()'],['../types_8h.html#a1bdb76cf7211909f821911726507fb30',1,'set_high():&#160;types.h']]],
[…]

### 2017-01-24 archive/html/search/all_13.js

@@ -1,0 +1,28 @@
+var searchData=
+[
+  ['test',['Test',['../class_test.html',1,'Test&lt; alphabet_type, alphabet_extension_type, size_type &gt;'],['../class_test.html#a9ca0652d8678a0c57e321fcc21f9ae39',1,'Test::Test()']]],
+  ['test_2eh',['test.h',['../test_8h.html',1,'']]],
+  ['test_5f1',['TEST_1',['../validate_8h.html#a864a52c772f23a04bcef46a40c9efed4',1,'validate.h']]],
+  ['test_5fvalidate3',['TEST_VALIDATE3',['../validate3_8h.html#aed71fcd0df9f567ccbffeda93549cefc',1,'validate3.h']]],
+  ['third',['third',['../structtriple.html#a5675f08ea7996033edbcf7074404cdd8',1,'triple::third()'],['../structquadruple.html#af1ada0ce5f85bbc7df2c5bfb113b442d',1,'quadruple::third()'],['../tuples_8h.html#ab02b336e2ad870f773affd07b0f68ef8',1,'third():&#160;tuples.h']]],
+  ['triple',['triple',['../structtriple.html',1,'triple&lt; T1, T2, T3 &gt;'],['../structtriple.html#a3bdf8136df773fff422b4cbb354cf749',1,'triple::triple()'],['../structtriple.html#a88688d689a93bf4b8a25bc29728a53b5',1,'triple::triple(const triple &amp;_item)'],['../structtriple.html#ac34fdb8619fdc11fb442e2058d35d840',1,'triple::triple(const T1 &amp;_first, const T2 &amp;_second, const T3 &amp;_third)'],['../tuples_8h.html#a72bccb6f22ab02a7f169a9d9b0671646',1,'triple():&#160;tuples.h'],['../tuples_8h.html#a43fbd7271bb2ea578cbcc6b90491ef12',1,'triple(const triple &amp;_item):&#160;tuples.h'],['../tuples_8h.html#a2be7f6af3a54cfc97c55bc395576db62',1,'triple(const T1 &amp;_first, const T2 &amp;_second, const T3 &amp;_third):&#160;tuples.h']]],
+  ['triple1_5fless_5fcomparator_5f1st_5ftype',['triple1_less_comparator_1st_type',['../class_validate4.html#af07a5152d547f7fba2f93b78660b88ab',1,'Validate4']]],
[…]

### 2017-01-24 archive/html/search/all_14.js

@@ -1,0 +1,11 @@
+var searchData=
+[
+  ['uint128',['uint128',['../classuint128.html',1,'uint128'],['../classuint128.html#abe535f8ff596b02234d94ab4c8d40933',1,'uint128::uint128()'],['../classuint128.html#a2b3acd15568d628cffb98f5c58f17ea9',1,'uint128::uint128(const uint64 &amp;_low, const uint64 &amp;_high)'],['../classuint128.html#a228d418fd9f623a4ee7120a7a53e0797',1,'uint128::uint128(const uint128 &amp;_a)'],['../classuint128.html#a5820b53a7880e5caf28057ea8bddff4b',1,'uint128::uint128(const uint32 &amp;_a)'],['../classuint128.html#af1cf2b32a813dae00ec27cfae5fabf1a',1,'uint128::uint128(const int32 &amp;_a)'],['../classuint128.html#a655c92ad28efbc6378c95510556475a7',1,'uint128::uint128(const uint64 &amp;_a)'],['../types_8h.html#ab620f7af906d024680c89ac9c99d5fae',1,'uint128():&#160;types.h'],['../types_8h.html#a38ef652b59a2ba178eff4646c7e5e008',1,'uint128(const uint64 &amp;_low, const uint64 &amp;_high):&#160;types.h'],['../types_8h.html#af7e6621517578e3fd6d7c26900edc6ef',1,'uint128(const uint128 &amp;_a):&#160;types.h'],['../types_8h.html#a5dc4f1787a04c99e251cd68bc631c7b3',1,'uint128(const uint32 &amp;_a):&#160;types.h'],['../types_8h.html#a38af0db38b8983c09e453dbb2a423b35',1,'uint128(const int32 &amp;_a):&#160;types.h'],['../types_8h.html#ab68fd9ef279f5a248fe93b1206cbc559',1,'uint128(const uint64 &amp;_a):&#160;types.h']]],
+  ['uint16',['uint16',['../types_8h.html#aea9840dd402bd5d5201bef4633398cb3',1,'types.h']]],
+  ['uint32',['uint32',['../types_8h.html#a8f95e75e58492e87412191fabadd8ca8',1,'types.h']]],
[…]

### 2017-01-24 archive/html/search/all_15.js

@@ -1,0 +1,19 @@
+var searchData=
+[
+  ['val_5fmax',['val_max',['../struct_validate4_1_1_l_m_s_validate.html#a8dce0e079545d3c4f2649614053cf5f1',1,'Validate4::LMSValidate::val_max()'],['../struct_validate4_1_1_r_m_q.html#a45aa4f738281304a3f6bd5b9d78ef712',1,'Validate4::RMQ::val_max()']]],
+  ['validate',['Validate',['../class_validate.html',1,'Validate&lt; alphabet_type, size_type, offset_type &gt;'],['../class_validate.html#a93b53c001ce92ccad38fe371e9df77b4',1,'Validate::Validate()']]],
+  ['validate_2ecpp',['validate.cpp',['../validate_8cpp.html',1,'']]],
+  ['validate_2eh',['validate.h',['../validate_8h.html',1,'']]],
+  ['validate2',['Validate2',['../class_validate2.html',1,'Validate2&lt; alphabet_type, size_type &gt;'],['../class_validate2.html#a003e523f9fb81a2d6a465d6cec444c1f',1,'Validate2::Validate2()']]],
+  ['validate2_2ecpp',['validate2.cpp',['../validate2_8cpp.html',1,'']]],
+  ['validate2_2eh',['validate2.h',['../validate2_8h.html',1,'']]],
+  ['validate3',['Validate3',['../class_validate3.html',1,'Validate3&lt; alphabet_type, size_type &gt;'],['../class_validate3.html#ab0a59632c6e2b3bfdd0bf89483448d46',1,'Validate3::Validate3()']]],
+  ['validate3_2ecpp',['validate3.cpp',['../validate3_8cpp.html',1,'']]],
+  ['validate3_2eh',['validate3.h',['../validate3_8h.html',1,'']]],
+  ['validate4',['Validate4',['../class_validate4.html',1,'Validate4&lt; alphabet_type, alphabet_extension_type, size_type &gt;'],['../class_validate4.html#aa1e9bf045b028c339da30db955857cb9',1,'Validate4::Validate4()']]],
+  ['validate4_2ecpp',['validate4.cpp',['../validate4_8cpp.html',1,'']]],
+  ['validate4_2eh',['validate4.h',['../validate4_8h.html',1,'']]],
+  ['validate_5flms',['validate_lms',['../class_test.html#ab5d1d239530c9b99ab1732e5d4008b87',1,'Test']]],
[…]

### 2017-01-24 archive/html/search/all_16.js

@@ -1,0 +1,6 @@
+var searchData=
+[
+  ['widget_2eh',['widget.h',['../widget_8h.html',1,'']]],
+  ['write',['write',['../classasync__stream__writer.html#afb36228f86866b4eb65343fd313754cc',1,'async_stream_writer::write(const value_type &amp;_item)'],['../classasync__stream__writer.html#a95a073a12efffbb4d0f1417abef06ab3',1,'async_stream_writer::write(const value_type *_src, uint64 _num)'],['../classasync__multi__stream__writer.html#a0290b2d5fdf0368559eee905c09863e7',1,'async_multi_stream_writer::write(const uint64 &amp;_file_id, const value_type &amp;_item)'],['../classasync__multi__stream__writer.html#af44e02f6c2eac01f1022b51105ea9cc0',1,'async_multi_stream_writer::write(const uint64 &amp;_file_id, const value_type *_src, const uint64 &amp;_num)']]],
+  ['write_5fto_5ffile',['write_to_file',['../structbuffer.html#ac31d1516df0036a19bb3e58a4a2fac8a',1,'buffer::write_to_file()'],['../class_basic_i_o.html#a890e7521a5a2e33eae4d52ec77a196a5',1,'BasicIO::write_to_file(const value_type *_src, const uint64 &amp;_cnt, std::FILE *_f)'],['../class_basic_i_o.html#a1bcd7dbe1acd71bafa1b5d6d4fc32e9e',1,'BasicIO::write_to_file(const value_type *_src, const uint64 &amp;_cnt, const std::string &amp;_fn)']]]
+];

### 2017-01-24 archive/html/search/all_17.js

@@ -1,0 +1,15 @@
+var searchData=
+[
+  ['_7easync_5fmulti_5fstream_5fvbyte_5freader',['~async_multi_stream_vbyte_reader',['../classasync__multi__stream__reader.html#a1c178b1a22b1e8853bacd42c1e0c2303',1,'async_multi_stream_reader']]],
+  ['_7easync_5fmulti_5fstream_5fwriter',['~async_multi_stream_writer',['../classasync__multi__stream__writer.html#a26ace952cb25e9ec4a0839d0aafc5e5e',1,'async_multi_stream_writer']]],
+  ['_7easync_5fstream_5freader',['~async_stream_reader',['../classasync__stream__reader.html#acfbb53847f349372dd3bb0455d9dfaa9',1,'async_stream_reader']]],
+  ['_7easync_5fstream_5fwriter',['~async_stream_writer',['../classasync__stream__writer.html#ac001ff454b249e4f71b4f92755017334',1,'async_stream_writer']]],
+  ['_7ebuffer',['~buffer',['../structbuffer.html#accefc959744e463ae78a996a2f45f81a',1,'buffer::~buffer()'],['../structbuffer.html#accefc959744e463ae78a996a2f45f81a',1,'buffer::~buffer()']]],
+  ['_7ebuffer_5fqueue',['~buffer_queue',['../structbuffer__queue.html#a8dda78874230bead5795e510f315dc2c',1,'buffer_queue::~buffer_queue()'],['../structbuffer__queue.html#a8dda78874230bead5795e510f315dc2c',1,'buffer_queue::~buffer_queue()']]],
+  ['_7elmsvalidate',['~LMSValidate',['../struct_validate4_1_1_l_m_s_validate.html#adaf3ee4e530f37787e9ff8c9f2ac511b',1,'Validate4::LMSValidate']]],
+  ['_7elscan',['~LScan',['../struct_validate4_1_1_l_scan.html#a1ac7b38fcbb0968d0683a0df18fedd9f',1,'Validate4::LScan']]],
+  ['_7erscan',['~RScan',['../struct_validate4_1_1_r_scan.html#a853d1a1bbc53a8b1cacf231c0f64bf8a',1,'Validate4::RScan']]],
+  ['_7etest',['~Test',['../class_test.html#acafab99b8fa6756de9998d16fc9e33f4',1,'Test']]],
[…]

### 2017-01-24 archive/html/search/all_2.js

@@ -1,0 +1,15 @@
+var searchData=
+[
+  ['basicio',['BasicIO',['../class_basic_i_o.html',1,'']]],
+  ['basicio_2eh',['basicio.h',['../basicio_8h.html',1,'']]],
+  ['bktinfo',['BktInfo',['../struct_validate4_1_1_bkt_info.html',1,'Validate4&lt; alphabet_type, alphabet_extension_type, size_type &gt;::BktInfo'],['../struct_validate4_1_1_bkt_info.html#ac9e39b62bee276f6a9604bff588b6ecc',1,'Validate4::BktInfo::BktInfo()']]],
+  ['bruteforce_5fcompute_5flcp',['bruteforce_compute_lcp',['../struct_validate4_1_1_r_scan.html#adc3cb04c1da68e1ac8a544c1eaf7c00c',1,'Validate4::RScan::bruteforce_compute_lcp()'],['../struct_validate4_1_1_l_scan.html#a9e88ab70a4b681b145bd79fa05d8f13d',1,'Validate4::LScan::bruteforce_compute_lcp()']]],
+  ['buff_5fmem_5favail',['BUFF_MEM_AVAIL',['../common_8h.html#aff51988fecf5b6871480b3d91954df7d',1,'common.h']]],
+  ['buffer',['buffer',['../structbuffer.html',1,'buffer&lt; T &gt;'],['../structbuffer.html#aefd0601854f94ec9c18c05986d218c16',1,'buffer::buffer(uint64 _size)'],['../structbuffer.html#aefd0601854f94ec9c18c05986d218c16',1,'buffer::buffer(uint64 _size)']]],
+  ['buffer_5fqueue',['buffer_queue',['../structbuffer__queue.html',1,'buffer_queue&lt; buffer_type &gt;'],['../structbuffer__queue.html#acd123387742f7cc4e1e418e7864ca2a1',1,'buffer_queue::buffer_queue(uint64 _bufnum=0, uint64 _bufsize=0)'],['../structbuffer__queue.html#a4e972bf42989038b6ef7eda7a372d1c3',1,'buffer_queue::buffer_queue(const uint64 &amp;_bufnum=0, const uint64 &amp;_bufsize=0)']]],
[…]

### 2017-01-24 archive/html/search/all_3.js

@@ -1,0 +1,13 @@
+var searchData=
+[
+  ['ch_5fmax',['ch_max',['../struct_validate4_1_1_bkt_info.html#a1485e4eceab1832f682e1751d310d2b9',1,'Validate4::BktInfo::ch_max()'],['../struct_validate4_1_1_l_m_s_validate.html#a3e640263256e534dcf3da45f50ef0645',1,'Validate4::LMSValidate::ch_max()'],['../struct_validate4_1_1_r_m_q.html#a0addfc5d1067fca9a97939554cb0cd70',1,'Validate4::RMQ::ch_max()'],['../struct_validate4_1_1_r_scan.html#a3ff6f0be3fd0b25c66913d4d08b2e143',1,'Validate4::RScan::ch_max()'],['../struct_validate4_1_1_l_scan.html#a907234b2fa774b42e87050f0066e26b6',1,'Validate4::LScan::ch_max()']]],
+  ['check',['check',['../class_validate3.html#ade475094c421af71da65620b706dec3f',1,'Validate3::check()'],['../struct_validate4_1_1_l_m_s_validate.html#a906ef49f72b8a2baa0d7a2d196c4b62e',1,'Validate4::LMSValidate::check()']]],
+  ['check_5fblock',['check_block',['../class_validate.html#a3d560deb2bd3e2984f6f3b8b8b766904',1,'Validate']]],
+  ['choose_5fint_5ftypes',['choose_int_types',['../structchoose__int__types.html',1,'']]],
+  ['choose_5fint_5ftypes_3c_204_20_3e',['choose_int_types&lt; 4 &gt;',['../structchoose__int__types_3_014_01_4.html',1,'']]],
+  ['choose_5fint_5ftypes_3c_208_20_3e',['choose_int_types&lt; 8 &gt;',['../structchoose__int__types_3_018_01_4.html',1,'']]],
+  ['common_2eh',['common.h',['../common_8h.html',1,'']]],
+  ['comparator',['comparator',['../struct_ex_tuple_sorter.html#a876d6fabe768a68b9d730053a619298e',1,'ExTupleSorter']]],
[…]

### 2017-01-24 archive/html/search/all_4.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['digits',['digits',['../classuint128.html#a08388a396904d541e7e921f1f379b4a1',1,'uint128::digits()'],['../types_8h.html#af113dea6c24342761f00f6b36e99032e',1,'digits():&#160;types.h']]],
+  ['display',['display',['../struct_validate4_1_1_bkt_info.html#ad8bc43e62d48c2f33fc6173f2a1d0840',1,'Validate4::BktInfo']]]
+];

### 2017-01-24 archive/html/search/all_5.js

@@ -1,0 +1,6 @@
+var searchData=
+[
+  ['empty',['empty',['../structbuffer__queue.html#a5d618b9b6dd1f700db6f96182cc1ad15',1,'buffer_queue::empty()'],['../classasync__stream__reader.html#accade2559119f3bed538d20f6eec4cfb',1,'async_stream_reader::empty()'],['../classasync__multi__stream__reader.html#aec2bb44c72b149387343e53cf6e65f7d',1,'async_multi_stream_reader::empty()'],['../structbuffer__queue.html#a5d618b9b6dd1f700db6f96182cc1ad15',1,'buffer_queue::empty()']]],
+  ['extuplesorter',['ExTupleSorter',['../struct_ex_tuple_sorter.html',1,'']]],
+  ['exvector',['ExVector',['../struct_ex_vector.html',1,'']]]
+];

### 2017-01-24 archive/html/search/all_6.js

@@ -1,0 +1,24 @@
+var searchData=
+[
+  ['fetch_5ffp',['fetch_fp',['../class_validate3.html#ad41c23715467e5201ef2705d38d8f81d',1,'Validate3::fetch_fp()'],['../struct_validate4_1_1_l_m_s_validate.html#a0d6e08ffc57dfd088ff737ed01a566b2',1,'Validate4::LMSValidate::fetch_fp()']]],
+  ['fetch_5ffp_5fch_5fcur',['fetch_fp_ch_cur',['../class_validate3.html#aeace570606a0320e2ad458145b7e16e3',1,'Validate3::fetch_fp_ch_cur()'],['../struct_validate4_1_1_l_m_s_validate.html#aa0d10da14dc1a8015967216e19eeb9af',1,'Validate4::LMSValidate::fetch_fp_ch_cur()']]],
+  ['fetch_5ffp_5fch_5fpre',['fetch_fp_ch_pre',['../class_validate3.html#abbf26d49c2f60ea8ecb3ba131f0a61ae',1,'Validate3::fetch_fp_ch_pre()'],['../struct_validate4_1_1_l_m_s_validate.html#a4e998a01460cb1c68954282065ec7c86',1,'Validate4::LMSValidate::fetch_fp_ch_pre()']]],
+  ['fetch_5fl_5finduced',['fetch_l_induced',['../struct_validate4_1_1_r_scan.html#aaa6c6e347bff1c6cb663771646c41826',1,'Validate4::RScan']]],
+  ['fetch_5fl_5fscanned',['fetch_l_scanned',['../struct_validate4_1_1_r_scan.html#af88a27e36780a6b390bc0bd18c253429',1,'Validate4::RScan::fetch_l_scanned()'],['../struct_validate4_1_1_l_scan.html#a1fabfd83060b51fdedd46b413da0f060',1,'Validate4::LScan::fetch_l_scanned()']]],
+  ['fetch_5flms_5fscanned',['fetch_lms_scanned',['../struct_validate4_1_1_r_scan.html#aaeb8ae64faa2ab76d7467586f3281d97',1,'Validate4::RScan']]],
+  ['fetch_5fs_5finduced',['fetch_s_induced',['../struct_validate4_1_1_l_scan.html#a37796b2c2e404a1bdf1362e7b1794fee',1,'Validate4::LScan']]],
[…]

### 2017-01-24 archive/html/search/all_7.js

@@ -1,0 +1,17 @@
+var searchData=
+[
+  ['get',['get',['../struct_validate4_1_1_r_m_q.html#a25c9ec1cab24c2ea2355b8ce828cf108',1,'Validate4::RMQ']]],
+  ['get_5fbkt_5fsize',['get_bkt_size',['../struct_validate4_1_1_bkt_info.html#a22256d03bfca21336fa30f2ed9e12d51',1,'Validate4::BktInfo']]],
+  ['get_5ffree_5fbuffer',['get_free_buffer',['../classasync__stream__writer.html#ad73941af15cf207e12376db3e2ffbfcd',1,'async_stream_writer::get_free_buffer()'],['../classasync__multi__stream__writer.html#a2598da84bf94a7576d3910e8fc16a18d',1,'async_multi_stream_writer::get_free_buffer()']]],
+  ['get_5ffull_5fbuffer',['get_full_buffer',['../classasync__stream__reader.html#a15c2bd3c259b3a84de866c02dd6c7405',1,'async_stream_reader::get_full_buffer()'],['../classasync__multi__stream__reader.html#afae17e2365e9ed10f30d398a550caa89',1,'async_multi_stream_reader::get_full_buffer()']]],
+  ['get_5fhigh',['get_high',['../classuint40.html#ac08ecc53d6ae5d245218a768c3ac105c',1,'uint40::get_high()'],['../classuint128.html#a597036514f1abbbc8626492230f3436f',1,'uint128::get_high()'],['../types_8h.html#a20cad26639e8f866e2fcfd01b6e9d0d4',1,'get_high():&#160;types.h']]],
+  ['get_5fl_5fbkt_5fch',['get_l_bkt_ch',['../struct_validate4_1_1_r_scan.html#a8d691af43c806d0e3279c0121abf6ed7',1,'Validate4::RScan::get_l_bkt_ch()'],['../struct_validate4_1_1_l_scan.html#ae986f4106e79412c60be8a88a9637f66',1,'Validate4::LScan::get_l_bkt_ch()']]],
+  ['get_5fl_5fbkt_5fsize',['get_l_bkt_size',['../struct_validate4_1_1_bkt_info.html#ae06c1968c2288d191f59214a0f10e7d7',1,'Validate4::BktInfo']]],
[…]

### 2017-01-24 archive/html/search/all_8.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['high',['high',['../classuint40.html#a830b04aa389a4e72c446cc88de38b656',1,'uint40::high()'],['../classuint128.html#a9f8275501c9a4546f37fae8e85e3ec05',1,'uint128::high()'],['../types_8h.html#a558f35d10292a79de791071eb8088a8c',1,'high():&#160;types.h']]],
+  ['high_5ftype',['high_type',['../classuint40.html#a58afcd6aeb1ea1e103b8e85eb6aefec4',1,'uint40::high_type()'],['../types_8h.html#a3d1ab983bb49c4acd2478c5365ce2bbb',1,'high_type():&#160;types.h']]]
+];

### 2017-01-24 archive/html/search/all_9.js

@@ -1,0 +1,9 @@
+var searchData=
+[
+  ['int16',['int16',['../types_8h.html#ac2abd1926482d6e74d1a30ee2ea5d6f8',1,'types.h']]],
+  ['int32',['int32',['../types_8h.html#a3d594eb72953c94a18a03d929ebd9167',1,'types.h']]],
+  ['int64',['int64',['../types_8h.html#a552928ab323811c9694f5b7c9f53d0fb',1,'types.h']]],
+  ['int8',['int8',['../types_8h.html#abd106ada62607d216e5d94926d7ec378',1,'types.h']]],
+  ['int_5ftype',['int_type',['../structchoose__int__types_3_014_01_4.html#af6cc8894e99e97c539077c9e640ed478',1,'choose_int_types&lt; 4 &gt;::int_type()'],['../structchoose__int__types_3_018_01_4.html#a4dde5a87f22a82a381bbae5f6d205d05',1,'choose_int_types&lt; 8 &gt;::int_type()'],['../types_8h.html#a848058bb4f500afaf0f954ffa75d3e6b',1,'int_type():&#160;types.h']]],
+  ['io_5fprocedure',['io_procedure',['../classasync__stream__reader.html#aee14e37431d75f5a80831ce6c3632ea2',1,'async_stream_reader::io_procedure()'],['../classasync__multi__stream__reader.html#a6e68c1dfe4990e3320f6b03dbf400517',1,'async_multi_stream_reader::io_procedure()'],['../classasync__stream__writer.html#a5fcc9c840654d18ba14668e43a3a0f31',1,'async_stream_writer::io_procedure()'],['../classasync__multi__stream__writer.html#ae0df727c7d673954c263e5b589a8f0c7',1,'async_multi_stream_writer::io_procedure()']]]
+];

### 2017-01-24 archive/html/search/all_b.js

@@ -1,0 +1,12 @@
+var searchData=
+[
+  ['l_5fcur_5fbkt_5fis_5fempty',['l_cur_bkt_is_empty',['../struct_validate4_1_1_r_scan.html#adf0c72967eddde6a6924472a16e92e95',1,'Validate4::RScan::l_cur_bkt_is_empty()'],['../struct_validate4_1_1_l_scan.html#ae76d58363b02ac96925becbbdbe02977',1,'Validate4::LScan::l_cur_bkt_is_empty()']]],
+  ['l_5fis_5fempty',['l_is_empty',['../struct_validate4_1_1_r_scan.html#aee1dcbd2edf03def6f3b3954d5cf0871',1,'Validate4::RScan::l_is_empty()'],['../struct_validate4_1_1_l_scan.html#a22b7a0b8c64f17da5a815ddaf8619ebb',1,'Validate4::LScan::l_is_empty()']]],
+  ['l_5ftype',['L_TYPE',['../common_8h.html#a12286339af3610eed714aba8e56125ea',1,'common.h']]],
+  ['lms_5fcur_5fbkt_5fis_5fempty',['lms_cur_bkt_is_empty',['../struct_validate4_1_1_r_scan.html#a67647b0b0ef9df76bdcfa85547296a33',1,'Validate4::RScan']]],
+  ['lms_5fis_5fempty',['lms_is_empty',['../struct_validate4_1_1_r_scan.html#ad24066012dd9441ffab435ce3f02424e',1,'Validate4::RScan']]],
+  ['lmsvalidate',['LMSValidate',['../struct_validate4_1_1_l_m_s_validate.html',1,'Validate4&lt; alphabet_type, alphabet_extension_type, size_type &gt;::LMSValidate'],['../struct_validate4_1_1_l_m_s_validate.html#a93810bf60dc23710fb678ae863aaebec',1,'Validate4::LMSValidate::LMSValidate()']]],
+  ['low',['low',['../classuint40.html#a216fde2e6997b39cb34b32daa869cef3',1,'uint40::low()'],['../classuint128.html#a439bdff9b7d8dd4bf99616bb07fc2a5e',1,'uint128::low()'],['../types_8h.html#ade07039efd8c0cfca1f9cead48259d4d',1,'low():&#160;types.h']]],
[…]

### 2017-01-24 archive/html/search/all_c.js

@@ -1,0 +1,90 @@
+var searchData=
+[
+  ['main_20page',['Main Page',['../index.html',1,'']]],
+  ['m_5f512',['M_512',['../common_8h.html#a260c3735667f0ab08a4c522a2e7bda23',1,'common.h']]],
+  ['m_5fbkt_5finfo',['m_bkt_info',['../class_validate4.html#a4f79c420ccec4e83e536fae655fe7a11',1,'Validate4']]],
+  ['m_5fbkt_5fsize',['m_bkt_size',['../struct_validate4_1_1_bkt_info.html#a1659db6479f4667a77043e842b93f3fc',1,'Validate4::BktInfo']]],
+  ['m_5fbufnum',['m_bufnum',['../classasync__multi__stream__reader.html#a24bef59afd1ef00b27d54e00a5f1c39a',1,'async_multi_stream_reader::m_bufnum()'],['../classasync__multi__stream__writer.html#a60bb0c6df357c9c9719527d812136ef3',1,'async_multi_stream_writer::m_bufnum()']]],
+  ['m_5fbufsize',['m_bufsize',['../classasync__multi__stream__reader.html#a4ddb169d2f5eff8499eef88ba091c566',1,'async_multi_stream_reader::m_bufsize()'],['../classasync__stream__writer.html#aea362e479496cec38f62cfe60402a390',1,'async_stream_writer::m_bufsize()'],['../classasync__multi__stream__writer.html#af8bf043c48fb1ad0dfa3e0a562e0e891',1,'async_multi_stream_writer::m_bufsize()']]],
+  ['m_5fbytes_5fread',['m_bytes_read',['../classasync__stream__reader.html#a5268366ca42bd2ef430e9e0817e9b274',1,'async_stream_reader::m_bytes_read()'],['../classasync__multi__stream__reader.html#a6486d4f10a3caf9169018d2bb71c4fdc',1,'async_multi_stream_reader::m_bytes_read()']]],
+  ['m_5fbytes_5fwritten',['m_bytes_written',['../classasync__stream__writer.html#a2e6bf4e33430ee652475dea9ce1ec7c5',1,'async_stream_writer::m_bytes_written()'],['../classasync__multi__stream__writer.html#a30c3a9ab1270eaff7fe8b2f1a98873b4',1,'async_multi_stream_writer::m_bytes_written()']]],
[…]

### 2017-01-24 archive/html/search/all_d.js

@@ -1,0 +1,10 @@
+var searchData=
+[
+  ['namespace_2eh',['namespace.h',['../namespace_8h.html',1,'']]],
+  ['namespace_5fcore_5fbeg',['NAMESPACE_CORE_BEG',['../namespace_8h.html#a9d80567b3813f4e453d1e9ec2ea08c8f',1,'namespace.h']]],
+  ['namespace_5fcore_5fend',['NAMESPACE_CORE_END',['../namespace_8h.html#a867f010187a6a1158481891dfb51273f',1,'namespace.h']]],
+  ['namespace_5futility_5fbeg',['NAMESPACE_UTILITY_BEG',['../namespace_8h.html#a84670ad82c41e15277ca235f8616b59e',1,'namespace.h']]],
+  ['namespace_5futility_5fend',['NAMESPACE_UTILITY_END',['../namespace_8h.html#afc10b2ddef8af94c352b9e2f24de67ca',1,'namespace.h']]],
+  ['numeric_5flimits_3c_20uint128_20_3e',['numeric_limits&lt; uint128 &gt;',['../classstd_1_1numeric__limits_3_01uint128_01_4.html',1,'std']]],
+  ['numeric_5flimits_3c_20uint40_20_3e',['numeric_limits&lt; uint40 &gt;',['../classstd_1_1numeric__limits_3_01uint40_01_4.html',1,'std']]]
+];

### 2017-01-24 archive/html/search/all_e.js

@@ -1,0 +1,11 @@
+var searchData=
+[
+  ['operator_20uint64_5ft',['operator uint64_t',['../classuint40.html#afca52041b179c0002070c33e7dd101a9',1,'uint40::operator uint64_t()'],['../types_8h.html#a8c16775e7e2ad633aae492dd2552ef52',1,'operator uint64_t():&#160;types.h']]],
+  ['operator_21_3d',['operator!=',['../classuint40.html#af17f2004231903079eb4e36b64c96180',1,'uint40::operator!=()'],['../classuint128.html#a767bfa81f69c7884cbb9434c37435e50',1,'uint128::operator!=()'],['../types_8h.html#affababd92753c4880d0c280bdb62633e',1,'operator!=(const uint40 &amp;b) const:&#160;types.h'],['../types_8h.html#ab3a727e5eede21cf30765aa649eb6b9d',1,'operator!=(const uint128 &amp;b) const:&#160;types.h']]],
+  ['operator_26',['operator&amp;',['../classuint128.html#a227d131e34d73974124c38cfbf0c6cc4',1,'uint128::operator&amp;()'],['../types_8h.html#a2ada254777d54d622dbeb7d45da92336',1,'operator&amp;():&#160;types.h']]],
+  ['operator_28_29',['operator()',['../struct_pair_less1st.html#a0c8e1c7ad75317672327e20bdafe56e3',1,'PairLess1st::operator()()'],['../struct_pair_less2nd.html#ab794f9af084ecf20527e87634b669f17',1,'PairLess2nd::operator()()'],['../structtuple__less__comparator__1st.html#ad97f49eea57d8fec456d9d00a5126deb',1,'tuple_less_comparator_1st::operator()()'],['../structtuple__great__comparator__1st.html#ab62e5503d2af02a4f2383b54217659bb',1,'tuple_great_comparator_1st::operator()()'],['../structtuple__less__comparator__2nd.html#a323236eaaac70cda8e4c7ccbfde17fc2',1,'tuple_less_comparator_2nd::operator()()']]],
[…]

### 2017-01-24 archive/html/search/all_f.js

@@ -1,0 +1,29 @@
+var searchData=
+[
+  ['p',['P',['../common_8h.html#aecfe9143b353556cb5a466f72c6a513c',1,'common.h']]],
+  ['pair',['pair',['../structpair.html',1,'pair&lt; T1, T2 &gt;'],['../structpair.html#a1dba17bb5c888d7ed8ce7b7c4acc52de',1,'pair::pair()'],['../structpair.html#ab75f77e9a1f726301f66d3be6b1e184a',1,'pair::pair(const pair &amp;_item)'],['../structpair.html#a5674a7a5327419692abe6160ae202859',1,'pair::pair(const T1 &amp;_first, const T2 &amp;_second)'],['../tuples_8h.html#a861a18bf6751dab7e644b4c4858d3548',1,'pair():&#160;tuples.h'],['../tuples_8h.html#ad95635b05637a43806af080d9ec581ba',1,'pair(const pair &amp;_item):&#160;tuples.h'],['../tuples_8h.html#a80f1b898df1006722612d5ecf89cd4d7',1,'pair(const T1 &amp;_first, const T2 &amp;_second):&#160;tuples.h']]],
+  ['pair1_5fcomparator_5ftype',['pair1_comparator_type',['../class_validate3.html#ace20fdc998ec6fb2c559aaf7413d464e',1,'Validate3']]],
+  ['pair1_5fgreat_5fcomparator_5f1st_5ftype',['pair1_great_comparator_1st_type',['../class_validate4.html#a3a6678b617cc9e0d65b36595cdd12a83',1,'Validate4']]],
+  ['pair1_5fgreat_5fsorter_5f1st_5ftype',['pair1_great_sorter_1st_type',['../class_validate4.html#ac379442c631fdd03a2e64223cea2c911',1,'Validate4']]],
+  ['pair1_5fless_5fcomparator_5f1st_5ftype',['pair1_less_comparator_1st_type',['../class_validate4.html#af01005bf9ba711e95fc52fc41e323716',1,'Validate4']]],
+  ['pair1_5fless_5fcomparator_5f2nd_5ftype',['pair1_less_comparator_2nd_type',['../class_validate4.html#a67166f1b6f64e5d8887d9a5aa6072346',1,'Validate4']]],
[…]

### 2017-01-24 archive/html/search/classes_0.js

@@ -1,0 +1,7 @@
+var searchData=
+[
+  ['async_5fmulti_5fstream_5freader',['async_multi_stream_reader',['../classasync__multi__stream__reader.html',1,'']]],
+  ['async_5fmulti_5fstream_5fwriter',['async_multi_stream_writer',['../classasync__multi__stream__writer.html',1,'']]],
+  ['async_5fstream_5freader',['async_stream_reader',['../classasync__stream__reader.html',1,'']]],
+  ['async_5fstream_5fwriter',['async_stream_writer',['../classasync__stream__writer.html',1,'']]]
+];

### 2017-01-24 archive/html/search/classes_1.js

@@ -1,0 +1,7 @@
+var searchData=
+[
+  ['basicio',['BasicIO',['../class_basic_i_o.html',1,'']]],
+  ['bktinfo',['BktInfo',['../struct_validate4_1_1_bkt_info.html',1,'Validate4']]],
+  ['buffer',['buffer',['../structbuffer.html',1,'']]],
+  ['buffer_5fqueue',['buffer_queue',['../structbuffer__queue.html',1,'']]]
+];

### 2017-01-24 archive/html/search/classes_2.js

@@ -1,0 +1,6 @@
+var searchData=
+[
+  ['choose_5fint_5ftypes',['choose_int_types',['../structchoose__int__types.html',1,'']]],
+  ['choose_5fint_5ftypes_3c_204_20_3e',['choose_int_types&lt; 4 &gt;',['../structchoose__int__types_3_014_01_4.html',1,'']]],
+  ['choose_5fint_5ftypes_3c_208_20_3e',['choose_int_types&lt; 8 &gt;',['../structchoose__int__types_3_018_01_4.html',1,'']]]
+];

### 2017-01-24 archive/html/search/classes_3.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['extuplesorter',['ExTupleSorter',['../struct_ex_tuple_sorter.html',1,'']]],
+  ['exvector',['ExVector',['../struct_ex_vector.html',1,'']]]
+];

### 2017-01-24 archive/html/search/classes_4.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['lmsvalidate',['LMSValidate',['../struct_validate4_1_1_l_m_s_validate.html',1,'Validate4']]],
+  ['lscan',['LScan',['../struct_validate4_1_1_l_scan.html',1,'Validate4']]]
+];

### 2017-01-24 archive/html/search/classes_5.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['numeric_5flimits_3c_20uint128_20_3e',['numeric_limits&lt; uint128 &gt;',['../classstd_1_1numeric__limits_3_01uint128_01_4.html',1,'std']]],
+  ['numeric_5flimits_3c_20uint40_20_3e',['numeric_limits&lt; uint40 &gt;',['../classstd_1_1numeric__limits_3_01uint40_01_4.html',1,'std']]]
+];

### 2017-01-24 archive/html/search/classes_6.js

@@ -1,0 +1,6 @@
+var searchData=
+[
+  ['pair',['pair',['../structpair.html',1,'']]],
+  ['pairless1st',['PairLess1st',['../struct_pair_less1st.html',1,'']]],
+  ['pairless2nd',['PairLess2nd',['../struct_pair_less2nd.html',1,'']]]
+];

### 2017-01-24 archive/html/search/classes_7.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['quadruple',['quadruple',['../structquadruple.html',1,'']]]
+];

### 2017-01-24 archive/html/search/classes_8.js

@@ -1,0 +1,7 @@
+var searchData=
+[
+  ['retrievepre',['RetrievePre',['../struct_validate4_1_1_retrieve_pre.html',1,'Validate4']]],
+  ['rinterval',['RInterval',['../struct_validate4_1_1_l_m_s_validate_1_1_r_interval.html',1,'Validate4&lt; alphabet_type, alphabet_extension_type, size_type &gt;::LMSValidate::RInterval'],['../struct_validate_1_1_r_interval.html',1,'Validate&lt; alphabet_type, size_type, offset_type &gt;::RInterval'],['../struct_validate2_1_1_r_interval.html',1,'Validate2&lt; alphabet_type, size_type &gt;::RInterval'],['../struct_validate3_1_1_r_interval.html',1,'Validate3&lt; alphabet_type, size_type &gt;::RInterval']]],
+  ['rmq',['RMQ',['../struct_validate4_1_1_r_m_q.html',1,'Validate4']]],
+  ['rscan',['RScan',['../struct_validate4_1_1_r_scan.html',1,'Validate4']]]
+];

### 2017-01-24 archive/html/search/classes_9.js

@@ -1,0 +1,8 @@
+var searchData=
+[
+  ['test',['Test',['../class_test.html',1,'']]],
+  ['triple',['triple',['../structtriple.html',1,'']]],
+  ['tuple_5fgreat_5fcomparator_5f1st',['tuple_great_comparator_1st',['../structtuple__great__comparator__1st.html',1,'']]],
+  ['tuple_5fless_5fcomparator_5f1st',['tuple_less_comparator_1st',['../structtuple__less__comparator__1st.html',1,'']]],
+  ['tuple_5fless_5fcomparator_5f2nd',['tuple_less_comparator_2nd',['../structtuple__less__comparator__2nd.html',1,'']]]
+];

### 2017-01-24 archive/html/search/classes_a.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['uint128',['uint128',['../classuint128.html',1,'']]],
+  ['uint40',['uint40',['../classuint40.html',1,'']]]
+];

### 2017-01-24 archive/html/search/classes_b.js

@@ -1,0 +1,7 @@
+var searchData=
+[
+  ['validate',['Validate',['../class_validate.html',1,'']]],
+  ['validate2',['Validate2',['../class_validate2.html',1,'']]],
+  ['validate3',['Validate3',['../class_validate3.html',1,'']]],
+  ['validate4',['Validate4',['../class_validate4.html',1,'']]]
+];

### 2017-01-24 archive/html/search/defines_0.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['_5ftest_5fh',['_TEST_H',['../test_8h.html#aa8de6ad987cfa13b647db341b8dcc510',1,'test.h']]]
+];

### 2017-01-24 archive/html/search/defines_1.js

@@ -1,0 +1,7 @@
+var searchData=
+[
+  ['namespace_5fcore_5fbeg',['NAMESPACE_CORE_BEG',['../namespace_8h.html#a9d80567b3813f4e453d1e9ec2ea08c8f',1,'namespace.h']]],
+  ['namespace_5fcore_5fend',['NAMESPACE_CORE_END',['../namespace_8h.html#a867f010187a6a1158481891dfb51273f',1,'namespace.h']]],
+  ['namespace_5futility_5fbeg',['NAMESPACE_UTILITY_BEG',['../namespace_8h.html#a84670ad82c41e15277ca235f8616b59e',1,'namespace.h']]],
+  ['namespace_5futility_5fend',['NAMESPACE_UTILITY_END',['../namespace_8h.html#afc10b2ddef8af94c352b9e2f24de67ca',1,'namespace.h']]]
+];

### 2017-01-24 archive/html/search/defines_2.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['statistics_5fcollection',['STATISTICS_COLLECTION',['../validate_8h.html#a1cc15202a800a32df74352e452309c57',1,'validate.h']]]
+];

### 2017-01-24 archive/html/search/defines_3.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['test_5f1',['TEST_1',['../validate_8h.html#a864a52c772f23a04bcef46a40c9efed4',1,'validate.h']]],
+  ['test_5fvalidate3',['TEST_VALIDATE3',['../validate3_8h.html#aed71fcd0df9f567ccbffeda93549cefc',1,'validate3.h']]]
+];

### 2017-01-24 archive/html/search/enumvalues_0.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['my_5fpointer_5fsize',['my_pointer_size',['../types_8h.html#a06fc87d81c62e9abb8790b6e5713c55ba8cdfa64b8cdab0fc9fe0e5a9d0192a5c',1,'types.h']]]
+];

### 2017-01-24 archive/html/search/files_0.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['async_5fstream_5freader_2eh',['async_stream_reader.h',['../async__stream__reader_8h.html',1,'']]],
+  ['async_5fstream_5fwriter_2eh',['async_stream_writer.h',['../async__stream__writer_8h.html',1,'']]]
+];

### 2017-01-24 archive/html/search/files_1.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['basicio_2eh',['basicio.h',['../basicio_8h.html',1,'']]]
+];

### 2017-01-24 archive/html/search/files_3.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['mytest1_2ecpp',['mytest1.cpp',['../mytest1_8cpp.html',1,'']]]
+];

### 2017-01-24 archive/html/search/files_4.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['namespace_2eh',['namespace.h',['../namespace_8h.html',1,'']]]
+];

### 2017-01-24 archive/html/search/files_6.js

@@ -1,0 +1,6 @@
+var searchData=
+[
+  ['test_2eh',['test.h',['../test_8h.html',1,'']]],
+  ['tuples_2eh',['tuples.h',['../tuples_8h.html',1,'']]],
+  ['types_2eh',['types.h',['../types_8h.html',1,'']]]
+];

### 2017-01-24 archive/html/search/files_7.js

@@ -1,0 +1,11 @@
+var searchData=
+[
+  ['validate_2ecpp',['validate.cpp',['../validate_8cpp.html',1,'']]],
+  ['validate_2eh',['validate.h',['../validate_8h.html',1,'']]],
+  ['validate2_2ecpp',['validate2.cpp',['../validate2_8cpp.html',1,'']]],
+  ['validate2_2eh',['validate2.h',['../validate2_8h.html',1,'']]],
+  ['validate3_2ecpp',['validate3.cpp',['../validate3_8cpp.html',1,'']]],
+  ['validate3_2eh',['validate3.h',['../validate3_8h.html',1,'']]],
+  ['validate4_2ecpp',['validate4.cpp',['../validate4_8cpp.html',1,'']]],
+  ['validate4_2eh',['validate4.h',['../validate4_8h.html',1,'']]]
+];

### 2017-01-24 archive/html/search/functions_0.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['_5f_5fattribute_5f_5f',['__attribute__',['../tuples_8h.html#a3287af29b6ef2cbe75f1caba87bdde63',1,'__attribute__((packed)):&#160;tuples.h'],['../tuples_8h.html#a61f5f588c8a34e43c27971a61e3a357d',1,'__attribute__((packed)):&#160;tuples.h'],['../tuples_8h.html#aa434f23135e2672ad8fe4ec768f3d88c',1,'__attribute__((packed)):&#160;tuples.h'],['../types_8h.html#aa5073eed52429ca9c68cfeef8163dadb',1,'__attribute__((packed)):&#160;types.h']]]
+];

### 2017-01-24 archive/html/search/functions_1.js

@@ -1,0 +1,11 @@
+var searchData=
+[
+  ['accumulate',['accumulate',['../struct_validate4_1_1_bkt_info.html#ac4fb0eabb194f773cd4ac5f6bcbbe969',1,'Validate4::BktInfo']]],
+  ['add_5fl',['add_l',['../struct_validate4_1_1_bkt_info.html#af55a2b8eee03bfe617ab34759b4ac007',1,'Validate4::BktInfo']]],
+  ['add_5flms',['add_lms',['../struct_validate4_1_1_bkt_info.html#a5875efc6696925c0932f262174c2cc37',1,'Validate4::BktInfo']]],
+  ['add_5fs',['add_s',['../struct_validate4_1_1_bkt_info.html#a9c11b8915349954523623d9e7b0a2c2a',1,'Validate4::BktInfo']]],
+  ['async_5fmulti_5fstream_5freader',['async_multi_stream_reader',['../classasync__multi__stream__reader.html#af83e5faafb7612b51abc05e8edde52dd',1,'async_multi_stream_reader']]],
+  ['async_5fmulti_5fstream_5fwriter',['async_multi_stream_writer',['../classasync__multi__stream__writer.html#a7f94653dac5ce376bea3b330942b59b3',1,'async_multi_stream_writer']]],
+  ['async_5fstream_5freader',['async_stream_reader',['../classasync__stream__reader.html#a02dc7a7adb24a552a265b30ba8544223',1,'async_stream_reader']]],
+  ['async_5fstream_5fwriter',['async_stream_writer',['../classasync__stream__writer.html#a11b5cdf01df7a627d00c6e77be165702',1,'async_stream_writer']]]
+];

### 2017-01-24 archive/html/search/functions_10.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['test',['Test',['../class_test.html#a9ca0652d8678a0c57e321fcc21f9ae39',1,'Test']]],
+  ['triple',['triple',['../structtriple.html#a3bdf8136df773fff422b4cbb354cf749',1,'triple::triple()'],['../structtriple.html#a88688d689a93bf4b8a25bc29728a53b5',1,'triple::triple(const triple &amp;_item)'],['../structtriple.html#ac34fdb8619fdc11fb442e2058d35d840',1,'triple::triple(const T1 &amp;_first, const T2 &amp;_second, const T3 &amp;_third)'],['../tuples_8h.html#a72bccb6f22ab02a7f169a9d9b0671646',1,'triple():&#160;tuples.h'],['../tuples_8h.html#a43fbd7271bb2ea578cbcc6b90491ef12',1,'triple(const triple &amp;_item):&#160;tuples.h'],['../tuples_8h.html#a2be7f6af3a54cfc97c55bc395576db62',1,'triple(const T1 &amp;_first, const T2 &amp;_second, const T3 &amp;_third):&#160;tuples.h']]]
+];

### 2017-01-24 archive/html/search/functions_11.js

@@ -1,0 +1,6 @@
+var searchData=
+[
+  ['uint128',['uint128',['../classuint128.html#abe535f8ff596b02234d94ab4c8d40933',1,'uint128::uint128()'],['../classuint128.html#a2b3acd15568d628cffb98f5c58f17ea9',1,'uint128::uint128(const uint64 &amp;_low, const uint64 &amp;_high)'],['../classuint128.html#a228d418fd9f623a4ee7120a7a53e0797',1,'uint128::uint128(const uint128 &amp;_a)'],['../classuint128.html#a5820b53a7880e5caf28057ea8bddff4b',1,'uint128::uint128(const uint32 &amp;_a)'],['../classuint128.html#af1cf2b32a813dae00ec27cfae5fabf1a',1,'uint128::uint128(const int32 &amp;_a)'],['../classuint128.html#a655c92ad28efbc6378c95510556475a7',1,'uint128::uint128(const uint64 &amp;_a)'],['../types_8h.html#ab620f7af906d024680c89ac9c99d5fae',1,'uint128():&#160;types.h'],['../types_8h.html#a38ef652b59a2ba178eff4646c7e5e008',1,'uint128(const uint64 &amp;_low, const uint64 &amp;_high):&#160;types.h'],['../types_8h.html#af7e6621517578e3fd6d7c26900edc6ef',1,'uint128(const uint128 &amp;_a):&#160;types.h'],['../types_8h.html#a5dc4f1787a04c99e251cd68bc631c7b3',1,'uint128(const uint32 &amp;_a):&#160;types.h'],['../types_8h.html#a38af0db38b8983c09e453dbb2a423b35',1,'uint128(const int32 &amp;_a):&#160;types.h'],['../types_8h.html#ab68fd9ef279f5a248fe93b1206cbc559',1,'uint128(const uint64 &amp;_a):&#160;types.h']]],
[…]

### 2017-01-24 archive/html/search/functions_12.js

@@ -1,0 +1,9 @@
+var searchData=
+[
+  ['validate',['Validate',['../class_validate.html#a93b53c001ce92ccad38fe371e9df77b4',1,'Validate']]],
+  ['validate2',['Validate2',['../class_validate2.html#a003e523f9fb81a2d6a465d6cec444c1f',1,'Validate2']]],
+  ['validate3',['Validate3',['../class_validate3.html#ab0a59632c6e2b3bfdd0bf89483448d46',1,'Validate3']]],
+  ['validate4',['Validate4',['../class_validate4.html#aa1e9bf045b028c339da30db955857cb9',1,'Validate4']]],
+  ['validate_5flms',['validate_lms',['../class_test.html#ab5d1d239530c9b99ab1732e5d4008b87',1,'Test']]],
+  ['validate_5fpre_5fitem',['validate_pre_item',['../class_test.html#aed94eee4f2a73d02c0abbe448efe2095',1,'Test']]]
+];

### 2017-01-24 archive/html/search/functions_13.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['write',['write',['../classasync__stream__writer.html#afb36228f86866b4eb65343fd313754cc',1,'async_stream_writer::write(const value_type &amp;_item)'],['../classasync__stream__writer.html#a95a073a12efffbb4d0f1417abef06ab3',1,'async_stream_writer::write(const value_type *_src, uint64 _num)'],['../classasync__multi__stream__writer.html#a0290b2d5fdf0368559eee905c09863e7',1,'async_multi_stream_writer::write(const uint64 &amp;_file_id, const value_type &amp;_item)'],['../classasync__multi__stream__writer.html#af44e02f6c2eac01f1022b51105ea9cc0',1,'async_multi_stream_writer::write(const uint64 &amp;_file_id, const value_type *_src, const uint64 &amp;_num)']]],
+  ['write_5fto_5ffile',['write_to_file',['../structbuffer.html#ac31d1516df0036a19bb3e58a4a2fac8a',1,'buffer::write_to_file()'],['../class_basic_i_o.html#a890e7521a5a2e33eae4d52ec77a196a5',1,'BasicIO::write_to_file(const value_type *_src, const uint64 &amp;_cnt, std::FILE *_f)'],['../class_basic_i_o.html#a1bcd7dbe1acd71bafa1b5d6d4fc32e9e',1,'BasicIO::write_to_file(const value_type *_src, const uint64 &amp;_cnt, const std::string &amp;_fn)']]]
+];

### 2017-01-24 archive/html/search/functions_2.js

@@ -1,0 +1,9 @@
+var searchData=
+[
+  ['bktinfo',['BktInfo',['../struct_validate4_1_1_bkt_info.html#ac9e39b62bee276f6a9604bff588b6ecc',1,'Validate4::BktInfo']]],
+  ['bruteforce_5fcompute_5flcp',['bruteforce_compute_lcp',['../struct_validate4_1_1_r_scan.html#adc3cb04c1da68e1ac8a544c1eaf7c00c',1,'Validate4::RScan::bruteforce_compute_lcp()'],['../struct_validate4_1_1_l_scan.html#a9e88ab70a4b681b145bd79fa05d8f13d',1,'Validate4::LScan::bruteforce_compute_lcp()']]],
+  ['buffer',['buffer',['../structbuffer.html#aefd0601854f94ec9c18c05986d218c16',1,'buffer::buffer(uint64 _size)'],['../structbuffer.html#aefd0601854f94ec9c18c05986d218c16',1,'buffer::buffer(uint64 _size)']]],
+  ['buffer_5fqueue',['buffer_queue',['../structbuffer__queue.html#acd123387742f7cc4e1e418e7864ca2a1',1,'buffer_queue::buffer_queue(uint64 _bufnum=0, uint64 _bufsize=0)'],['../structbuffer__queue.html#a4e972bf42989038b6ef7eda7a372d1c3',1,'buffer_queue::buffer_queue(const uint64 &amp;_bufnum=0, const uint64 &amp;_bufsize=0)']]],
+  ['bytes_5fread',['bytes_read',['../classasync__stream__reader.html#a15f6c24ea5065855b1d5df69cc7e3e1a',1,'async_stream_reader::bytes_read()'],['../classasync__multi__stream__reader.html#ab4ebef1c67d84d3581bc4ddaa0a1cc9b',1,'async_multi_stream_reader::bytes_read()']]],
+  ['bytes_5fwritten',['bytes_written',['../classasync__stream__writer.html#a6fd98bbc41adf1cd51468ee490608d6e',1,'async_stream_writer::bytes_written()'],['../classasync__multi__stream__writer.html#a196cb6d52ef0d06c585f9e6bba4384b5',1,'async_multi_stream_writer::bytes_written()']]]
+];

### 2017-01-24 archive/html/search/functions_3.js

@@ -1,0 +1,6 @@
+var searchData=
+[
+  ['check',['check',['../class_validate3.html#ade475094c421af71da65620b706dec3f',1,'Validate3::check()'],['../struct_validate4_1_1_l_m_s_validate.html#a906ef49f72b8a2baa0d7a2d196c4b62e',1,'Validate4::LMSValidate::check()']]],
+  ['check_5fblock',['check_block',['../class_validate.html#a3d560deb2bd3e2984f6f3b8b8b766904',1,'Validate']]],
+  ['compute',['compute',['../struct_validate_1_1_r_interval.html#a15d2215c198eb022a01792b62cfad0ef',1,'Validate::RInterval::compute()'],['../struct_validate2_1_1_r_interval.html#a84006809e4b3ef58bd7335d2f46a92b1',1,'Validate2::RInterval::compute()'],['../struct_validate3_1_1_r_interval.html#a7f5178d27e49d60e23e2a45635d2b076',1,'Validate3::RInterval::compute()'],['../struct_validate4_1_1_l_m_s_validate_1_1_r_interval.html#a7c1aee0f298285e1eb0df8b3ab368036',1,'Validate4::LMSValidate::RInterval::compute()']]]
+];

### 2017-01-24 archive/html/search/functions_4.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['display',['display',['../struct_validate4_1_1_bkt_info.html#ad8bc43e62d48c2f33fc6173f2a1d0840',1,'Validate4::BktInfo']]]
+];

### 2017-01-24 archive/html/search/functions_5.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['empty',['empty',['../structbuffer__queue.html#a5d618b9b6dd1f700db6f96182cc1ad15',1,'buffer_queue::empty()'],['../classasync__stream__reader.html#accade2559119f3bed538d20f6eec4cfb',1,'async_stream_reader::empty()'],['../classasync__multi__stream__reader.html#aec2bb44c72b149387343e53cf6e65f7d',1,'async_multi_stream_reader::empty()'],['../structbuffer__queue.html#a5d618b9b6dd1f700db6f96182cc1ad15',1,'buffer_queue::empty()']]]
+];

### 2017-01-24 archive/html/search/functions_6.js

@@ -1,0 +1,20 @@
+var searchData=
+[
+  ['fetch_5ffp',['fetch_fp',['../class_validate3.html#ad41c23715467e5201ef2705d38d8f81d',1,'Validate3::fetch_fp()'],['../struct_validate4_1_1_l_m_s_validate.html#a0d6e08ffc57dfd088ff737ed01a566b2',1,'Validate4::LMSValidate::fetch_fp()']]],
+  ['fetch_5ffp_5fch_5fcur',['fetch_fp_ch_cur',['../class_validate3.html#aeace570606a0320e2ad458145b7e16e3',1,'Validate3::fetch_fp_ch_cur()'],['../struct_validate4_1_1_l_m_s_validate.html#aa0d10da14dc1a8015967216e19eeb9af',1,'Validate4::LMSValidate::fetch_fp_ch_cur()']]],
+  ['fetch_5ffp_5fch_5fpre',['fetch_fp_ch_pre',['../class_validate3.html#abbf26d49c2f60ea8ecb3ba131f0a61ae',1,'Validate3::fetch_fp_ch_pre()'],['../struct_validate4_1_1_l_m_s_validate.html#a4e998a01460cb1c68954282065ec7c86',1,'Validate4::LMSValidate::fetch_fp_ch_pre()']]],
+  ['fetch_5fl_5finduced',['fetch_l_induced',['../struct_validate4_1_1_r_scan.html#aaa6c6e347bff1c6cb663771646c41826',1,'Validate4::RScan']]],
+  ['fetch_5fl_5fscanned',['fetch_l_scanned',['../struct_validate4_1_1_r_scan.html#af88a27e36780a6b390bc0bd18c253429',1,'Validate4::RScan::fetch_l_scanned()'],['../struct_validate4_1_1_l_scan.html#a1fabfd83060b51fdedd46b413da0f060',1,'Validate4::LScan::fetch_l_scanned()']]],
+  ['fetch_5flms_5fscanned',['fetch_lms_scanned',['../struct_validate4_1_1_r_scan.html#aaeb8ae64faa2ab76d7467586f3281d97',1,'Validate4::RScan']]],
+  ['fetch_5fs_5finduced',['fetch_s_induced',['../struct_validate4_1_1_l_scan.html#a37796b2c2e404a1bdf1362e7b1794fee',1,'Validate4::LScan']]],
[…]

### 2017-01-24 archive/html/search/functions_8.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['io_5fprocedure',['io_procedure',['../classasync__stream__reader.html#aee14e37431d75f5a80831ce6c3632ea2',1,'async_stream_reader::io_procedure()'],['../classasync__multi__stream__reader.html#a6e68c1dfe4990e3320f6b03dbf400517',1,'async_multi_stream_reader::io_procedure()'],['../classasync__stream__writer.html#a5fcc9c840654d18ba14668e43a3a0f31',1,'async_stream_writer::io_procedure()'],['../classasync__multi__stream__writer.html#ae0df727c7d673954c263e5b589a8f0c7',1,'async_multi_stream_writer::io_procedure()']]]
+];

### 2017-01-24 archive/html/search/functions_9.js

@@ -1,0 +1,9 @@
+var searchData=
+[
+  ['l_5fcur_5fbkt_5fis_5fempty',['l_cur_bkt_is_empty',['../struct_validate4_1_1_r_scan.html#adf0c72967eddde6a6924472a16e92e95',1,'Validate4::RScan::l_cur_bkt_is_empty()'],['../struct_validate4_1_1_l_scan.html#ae76d58363b02ac96925becbbdbe02977',1,'Validate4::LScan::l_cur_bkt_is_empty()']]],
+  ['l_5fis_5fempty',['l_is_empty',['../struct_validate4_1_1_r_scan.html#aee1dcbd2edf03def6f3b3954d5cf0871',1,'Validate4::RScan::l_is_empty()'],['../struct_validate4_1_1_l_scan.html#a22b7a0b8c64f17da5a815ddaf8619ebb',1,'Validate4::LScan::l_is_empty()']]],
+  ['lms_5fcur_5fbkt_5fis_5fempty',['lms_cur_bkt_is_empty',['../struct_validate4_1_1_r_scan.html#a67647b0b0ef9df76bdcfa85547296a33',1,'Validate4::RScan']]],
+  ['lms_5fis_5fempty',['lms_is_empty',['../struct_validate4_1_1_r_scan.html#ad24066012dd9441ffab435ce3f02424e',1,'Validate4::RScan']]],
+  ['lmsvalidate',['LMSValidate',['../struct_validate4_1_1_l_m_s_validate.html#a93810bf60dc23710fb678ae863aaebec',1,'Validate4::LMSValidate']]],
+  ['lscan',['LScan',['../struct_validate4_1_1_l_scan.html#a8e95d99392cee99b081b8354d9a13757',1,'Validate4::LScan']]]
+];

### 2017-01-24 archive/html/search/functions_a.js

@@ -1,0 +1,8 @@
+var searchData=
+[
+  ['main',['main',['../validate_8cpp.html#a3c04138a5bfe5d72780bb7e82a18e627',1,'main(int argc, char **argv):&#160;validate.cpp'],['../validate2_8cpp.html#a3c04138a5bfe5d72780bb7e82a18e627',1,'main(int argc, char **argv):&#160;validate2.cpp'],['../validate3_8cpp.html#a3c04138a5bfe5d72780bb7e82a18e627',1,'main(int argc, char **argv):&#160;validate3.cpp'],['../validate4_8cpp.html#a3c04138a5bfe5d72780bb7e82a18e627',1,'main(int argc, char **argv):&#160;validate4.cpp'],['../mytest1_8cpp.html#ae66f6b31b5ad750f1fe042a706a4e3d4',1,'main():&#160;mytest1.cpp']]],
+  ['max',['max',['../classuint128.html#a8fc47c78cb71d012c6208c150ca4cf3b',1,'uint128::max()'],['../classstd_1_1numeric__limits_3_01uint40_01_4.html#a22582c529e203e9648b054d15bcb0564',1,'std::numeric_limits&lt; uint40 &gt;::max()'],['../classstd_1_1numeric__limits_3_01uint128_01_4.html#a7093ce47008ca399ec2cd994099baa2a',1,'std::numeric_limits&lt; uint128 &gt;::max()'],['../types_8h.html#add613a3d2d7eff426907064270db8215',1,'max():&#160;types.h']]],
[…]

### 2017-01-24 archive/html/search/functions_b.js

@@ -1,0 +1,11 @@
+var searchData=
+[
+  ['operator_20uint64_5ft',['operator uint64_t',['../classuint40.html#afca52041b179c0002070c33e7dd101a9',1,'uint40::operator uint64_t()'],['../types_8h.html#a8c16775e7e2ad633aae492dd2552ef52',1,'operator uint64_t():&#160;types.h']]],
+  ['operator_21_3d',['operator!=',['../classuint40.html#af17f2004231903079eb4e36b64c96180',1,'uint40::operator!=()'],['../classuint128.html#a767bfa81f69c7884cbb9434c37435e50',1,'uint128::operator!=()'],['../types_8h.html#affababd92753c4880d0c280bdb62633e',1,'operator!=(const uint40 &amp;b) const:&#160;types.h'],['../types_8h.html#ab3a727e5eede21cf30765aa649eb6b9d',1,'operator!=(const uint128 &amp;b) const:&#160;types.h']]],
+  ['operator_26',['operator&amp;',['../classuint128.html#a227d131e34d73974124c38cfbf0c6cc4',1,'uint128::operator&amp;()'],['../types_8h.html#a2ada254777d54d622dbeb7d45da92336',1,'operator&amp;():&#160;types.h']]],
+  ['operator_28_29',['operator()',['../struct_pair_less1st.html#a0c8e1c7ad75317672327e20bdafe56e3',1,'PairLess1st::operator()()'],['../struct_pair_less2nd.html#ab794f9af084ecf20527e87634b669f17',1,'PairLess2nd::operator()()'],['../structtuple__less__comparator__1st.html#ad97f49eea57d8fec456d9d00a5126deb',1,'tuple_less_comparator_1st::operator()()'],['../structtuple__great__comparator__1st.html#ab62e5503d2af02a4f2383b54217659bb',1,'tuple_great_comparator_1st::operator()()'],['../structtuple__less__comparator__2nd.html#a323236eaaac70cda8e4c7ccbfde17fc2',1,'tuple_less_comparator_2nd::operator()()']]],
[…]

### 2017-01-24 archive/html/search/functions_c.js

@@ -1,0 +1,6 @@
+var searchData=
+[
+  ['pair',['pair',['../structpair.html#a1dba17bb5c888d7ed8ce7b7c4acc52de',1,'pair::pair()'],['../structpair.html#ab75f77e9a1f726301f66d3be6b1e184a',1,'pair::pair(const pair &amp;_item)'],['../structpair.html#a5674a7a5327419692abe6160ae202859',1,'pair::pair(const T1 &amp;_first, const T2 &amp;_second)'],['../tuples_8h.html#a861a18bf6751dab7e644b4c4858d3548',1,'pair():&#160;tuples.h'],['../tuples_8h.html#ad95635b05637a43806af080d9ec581ba',1,'pair(const pair &amp;_item):&#160;tuples.h'],['../tuples_8h.html#a80f1b898df1006722612d5ecf89cd4d7',1,'pair(const T1 &amp;_first, const T2 &amp;_second):&#160;tuples.h']]],
+  ['pop',['pop',['../structbuffer__queue.html#ab26cbb480e9a300a4a021f4be1bb2735',1,'buffer_queue::pop()'],['../structbuffer__queue.html#ab26cbb480e9a300a4a021f4be1bb2735',1,'buffer_queue::pop()']]],
+  ['push',['push',['../structbuffer__queue.html#a13c104db4054ca0cb59b5e0502267d55',1,'buffer_queue::push(buffer_type *_buf)'],['../structbuffer__queue.html#a13c104db4054ca0cb59b5e0502267d55',1,'buffer_queue::push(buffer_type *_buf)']]]
+];

### 2017-01-24 archive/html/search/functions_d.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['quadruple',['quadruple',['../structquadruple.html#ab4b318f9f20c5f861c0b7445bf806da8',1,'quadruple::quadruple()'],['../structquadruple.html#a24c753a7c00f8325bf7f738815e89d06',1,'quadruple::quadruple(const quadruple &amp;_item)'],['../structquadruple.html#a23034a914f2841aa59c833bb3923f1b6',1,'quadruple::quadruple(const T1 &amp;_first, const T2 &amp;_second, const T3 &amp;_third, const T4 &amp;_forth)'],['../tuples_8h.html#abc5517aabc587ce4dbe5d5d5c51e926e',1,'quadruple():&#160;tuples.h'],['../tuples_8h.html#ac6ecb9121ff7c7bc8f2bb354d86a7da9',1,'quadruple(const quadruple &amp;_item):&#160;tuples.h'],['../tuples_8h.html#a275ae5ff396331c5f894cae5e717aafd',1,'quadruple(const T1 &amp;_first, const T2 &amp;_second, const T3 &amp;_third, const T4 &amp;_forth):&#160;tuples.h']]]
+];

### 2017-01-24 archive/html/search/functions_e.js

@@ -1,0 +1,13 @@
+var searchData=
+[
+  ['read',['read',['../classasync__stream__reader.html#abb382de67d33724ff4fea6714fc67ac8',1,'async_stream_reader::read()'],['../classasync__stream__reader.html#ac441a02e7bb4708948552ce7ced4e9d4',1,'async_stream_reader::read(value_type *_des, uint64 _num)'],['../classasync__multi__stream__reader.html#ae47f5af3e9c0964be88975391631b3d4',1,'async_multi_stream_reader::read(const uint64 &amp;_file_idx)'],['../classasync__multi__stream__reader.html#a1b4db036726c5b33edf9cdca1ccc24d9',1,'async_multi_stream_reader::read(const uint64 &amp;_file_idx, value_type *_des, uint64 _num)']]],
+  ['read_5fat_5foffset',['read_at_offset',['../class_basic_i_o.html#a7aed99607484ece4b385e3fdced47e1c',1,'BasicIO::read_at_offset(value_type *_des, const uint64 &amp;_offset, const uint64 &amp;_cnt, const std::FILE *_f)'],['../class_basic_i_o.html#a934ed5d36b8a132b622c59c61b881bdd',1,'BasicIO::read_at_offset(value_type *_des, const uint64 &amp;_offset, const uint64 &amp;_cnt, const std::string &amp;_fn)']]],
+  ['read_5ffrom_5ffile',['read_from_file',['../structbuffer.html#a2abf8fde8a3d6a1245f57d698e207b74',1,'buffer::read_from_file()'],['../class_basic_i_o.html#a5e1c1be36914e4749f4a4bd0cf1b53d0',1,'BasicIO::read_from_file(value_type *_des, const uint64 &amp;_cnt, const std::FILE *_f)'],['../class_basic_i_o.html#a7e492b3c92dbb91e7f45cd5ed03365a3',1,'BasicIO::read_from_file(value_type *_des, const uint64 &amp;_cnt, const std::string &amp;_fn)']]],
+  ['reset',['reset',['../struct_validate4_1_1_r_m_q.html#a8416e95d49b4b8c05cd814d78017d81f',1,'Validate4::RMQ']]],
+  ['retrieve_5flms',['retrieve_lms',['../struct_validate4_1_1_l_m_s_validate.html#afd7ee2100849c6c9bc493782d0c9aea3',1,'Validate4::LMSValidate']]],
[…]

### 2017-01-24 archive/html/search/functions_f.js

@@ -1,0 +1,11 @@
+var searchData=
+[
+  ['s_5fcur_5fbkt_5fis_5fempty',['s_cur_bkt_is_empty',['../struct_validate4_1_1_l_scan.html#a9331f92d91cf67c38a3d6948a2190df8',1,'Validate4::LScan']]],
+  ['s_5fis_5fempty',['s_is_empty',['../struct_validate4_1_1_l_scan.html#a071826b788f5aadc92f87ad8cc986649',1,'Validate4::LScan']]],
+  ['send_5fno_5fmore_5ffull_5fbuffer_5fsignal',['send_no_more_full_buffer_signal',['../structbuffer__queue.html#a487335f8827c09d4d76d588e47d633ac',1,'buffer_queue::send_no_more_full_buffer_signal()'],['../structbuffer__queue.html#a487335f8827c09d4d76d588e47d633ac',1,'buffer_queue::send_no_more_full_buffer_signal()']]],
+  ['set',['set',['../classuint40.html#ab23ea17f6248ac0e7dbacbb71a96179b',1,'uint40::set()'],['../types_8h.html#a9805ad2d84465b3a1c4aa12235f922c4',1,'set():&#160;types.h']]],
+  ['set_5fhigh',['set_high',['../classuint40.html#a4d8e0bfd4cb5f959d89d3966c10a28bc',1,'uint40::set_high()'],['../types_8h.html#a1bdb76cf7211909f821911726507fb30',1,'set_high():&#160;types.h']]],
+  ['set_5flow',['set_low',['../classuint40.html#a451e74374aa8f180e94d341e18352d4c',1,'uint40::set_low()'],['../types_8h.html#ac451e240aa7238b8cdd88c68a4b94c25',1,'set_low():&#160;types.h']]],
+  ['size_5fin_5fbytes',['size_in_bytes',['../structbuffer.html#a2b74a935bb50716bba0835781545803d',1,'buffer::size_in_bytes() const'],['../structbuffer.html#a2b74a935bb50716bba0835781545803d',1,'buffer::size_in_bytes() const']]],
+  ['skip',['skip',['../classasync__stream__reader.html#a66bc0e20739b27b9c703be9254cdbe05',1,'async_stream_reader::skip()'],['../classasync__multi__stream__reader.html#a620b5917c284dbdb6b1f93ea425b9c0e',1,'async_multi_stream_reader::skip()']]]
+];

### 2017-01-24 archive/html/search/related_0.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['operator_3c_3c',['operator&lt;&lt;',['../structpair.html#a9cd7ed0b2b2d0a6d5977137d9cf35a0c',1,'pair::operator&lt;&lt;()'],['../structtriple.html#a213e2d21647f20d6287690438970f212',1,'triple::operator&lt;&lt;()'],['../structquadruple.html#af619be80f82068b7b05a8d943196f024',1,'quadruple::operator&lt;&lt;()'],['../classuint128.html#a3981a0cf6398b930fa55fa5c5e802a65',1,'uint128::operator&lt;&lt;()']]]
+];

### 2017-01-24 archive/html/search/searchdata.js

@@ -1,0 +1,45 @@
+var indexSectionsWithContent =
+{
+  0: "_abcdefghiklmnopqrstuvw~",
+  1: "abcelnpqrtuv",
+  2: "s",
+  3: "abcmnrtvw",
+  4: "_abcdefgilmopqrstuvw~",
+  5: "_bcdfhklmprstv",
+  6: "abcfhilpstuv",
+  7: "m",
+  8: "o",
+  9: "_nst",
+  10: "m"
+};
+
+var indexSectionNames =
+{
+  0: "all",
+  1: "classes",
+  2: "namespaces",
+  3: "files",
+  4: "functions",
+  5: "variables",
+  6: "typedefs",
+  7: "enumvalues",
+  8: "related",
+  9: "defines",
+  10: "pages"
+};
+
+var indexSectionLabels =
+{
+  0: "All",
+  1: "Classes",
+  2: "Namespaces",
+  3: "Files",
+  4: "Functions",
+  5: "Variables",
+  6: "Typedefs",
+  7: "Enumerator",
+  8: "Friends",
+  9: "Macros",
+  10: "Pages"
+};
+

### 2017-01-24 archive/html/search/typedefs_0.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['alphabet_5fvector_5ftype',['alphabet_vector_type',['../class_test.html#aace52a5af52c5d5f457ec201881ab2ab',1,'Test::alphabet_vector_type()'],['../class_validate.html#a0323dd6f1096806748299dfd4f644b69',1,'Validate::alphabet_vector_type()'],['../class_validate2.html#a351a2e7bbfdf9b87ecbb4f08cdbc1e64',1,'Validate2::alphabet_vector_type()'],['../class_validate3.html#a7a893a89f745710a34958b37717cb024',1,'Validate3::alphabet_vector_type()'],['../class_validate4.html#a49c80b3d101be19542a4341c2387603a',1,'Validate4::alphabet_vector_type()']]]
+];

### 2017-01-24 archive/html/search/typedefs_1.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['buffer_5fqueue_5ftype',['buffer_queue_type',['../classasync__stream__reader.html#a5301e887b098a0ade898265ca6935d68',1,'async_stream_reader::buffer_queue_type()'],['../classasync__multi__stream__reader.html#a0bf4b801f7d874da5cbbe5c6504d0ecc',1,'async_multi_stream_reader::buffer_queue_type()'],['../classasync__stream__writer.html#a44dba276c5208314653dd887010e7161',1,'async_stream_writer::buffer_queue_type()'],['../classasync__multi__stream__writer.html#a1ac00be81314a643563a45cafe6f8660',1,'async_multi_stream_writer::buffer_queue_type()']]],
+  ['buffer_5ftype',['buffer_type',['../classasync__stream__reader.html#a48e2b7d24cfceba922a771e9c314b40c',1,'async_stream_reader::buffer_type()'],['../classasync__multi__stream__reader.html#ad58ad834dc6d741a12be1fb442b8e5d6',1,'async_multi_stream_reader::buffer_type()'],['../classasync__stream__writer.html#a7e813664993581eab8d5fc6bcff2ce19',1,'async_stream_writer::buffer_type()'],['../classasync__multi__stream__writer.html#ae11c006e394241a9a5b003a30e8c8c92',1,'async_multi_stream_writer::buffer_type()']]]
+];

### 2017-01-24 archive/html/search/typedefs_2.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['comparator',['comparator',['../struct_ex_tuple_sorter.html#a876d6fabe768a68b9d730053a619298e',1,'ExTupleSorter']]]
+];

### 2017-01-24 archive/html/search/typedefs_3.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['fpa_5ftype',['fpa_type',['../common_8h.html#a7fdaf8b9b3d2f6ae6b10597a8d3f96ee',1,'common.h']]],
+  ['fpb_5ftype',['fpb_type',['../common_8h.html#a6f10cf5b333b34ed4bbf03429a74bcca',1,'common.h']]]
+];

### 2017-01-24 archive/html/search/typedefs_4.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['high_5ftype',['high_type',['../classuint40.html#a58afcd6aeb1ea1e103b8e85eb6aefec4',1,'uint40::high_type()'],['../types_8h.html#a3d1ab983bb49c4acd2478c5365ce2bbb',1,'high_type():&#160;types.h']]]
+];

### 2017-01-24 archive/html/search/typedefs_5.js

@@ -1,0 +1,8 @@
+var searchData=
+[
+  ['int16',['int16',['../types_8h.html#ac2abd1926482d6e74d1a30ee2ea5d6f8',1,'types.h']]],
+  ['int32',['int32',['../types_8h.html#a3d594eb72953c94a18a03d929ebd9167',1,'types.h']]],
+  ['int64',['int64',['../types_8h.html#a552928ab323811c9694f5b7c9f53d0fb',1,'types.h']]],
+  ['int8',['int8',['../types_8h.html#abd106ada62607d216e5d94926d7ec378',1,'types.h']]],
+  ['int_5ftype',['int_type',['../structchoose__int__types_3_014_01_4.html#af6cc8894e99e97c539077c9e640ed478',1,'choose_int_types&lt; 4 &gt;::int_type()'],['../structchoose__int__types_3_018_01_4.html#a4dde5a87f22a82a381bbae5f6d205d05',1,'choose_int_types&lt; 8 &gt;::int_type()'],['../types_8h.html#a848058bb4f500afaf0f954ffa75d3e6b',1,'int_type():&#160;types.h']]]
+];

### 2017-01-24 archive/html/search/typedefs_6.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['low_5ftype',['low_type',['../classuint40.html#a92fb8d876ca5cf77d4ed86dae0adc2f2',1,'uint40::low_type()'],['../types_8h.html#afb0e4a3c06d32e9372ba48a8ebe1861c',1,'low_type():&#160;types.h']]]
+];

### 2017-01-24 archive/html/search/typedefs_7.js

@@ -1,0 +1,22 @@
+var searchData=
+[
+  ['pair1_5fcomparator_5ftype',['pair1_comparator_type',['../class_validate3.html#ace20fdc998ec6fb2c559aaf7413d464e',1,'Validate3']]],
+  ['pair1_5fgreat_5fcomparator_5f1st_5ftype',['pair1_great_comparator_1st_type',['../class_validate4.html#a3a6678b617cc9e0d65b36595cdd12a83',1,'Validate4']]],
+  ['pair1_5fgreat_5fsorter_5f1st_5ftype',['pair1_great_sorter_1st_type',['../class_validate4.html#ac379442c631fdd03a2e64223cea2c911',1,'Validate4']]],
+  ['pair1_5fless_5fcomparator_5f1st_5ftype',['pair1_less_comparator_1st_type',['../class_validate4.html#af01005bf9ba711e95fc52fc41e323716',1,'Validate4']]],
+  ['pair1_5fless_5fcomparator_5f2nd_5ftype',['pair1_less_comparator_2nd_type',['../class_validate4.html#a67166f1b6f64e5d8887d9a5aa6072346',1,'Validate4']]],
+  ['pair1_5fless_5fsorter_5f1st_5ftype',['pair1_less_sorter_1st_type',['../class_validate4.html#a40b1f73557cfa4c0b26f56f5038a4c5c',1,'Validate4']]],
+  ['pair1_5fless_5fsorter_5f2nd_5ftype',['pair1_less_sorter_2nd_type',['../class_validate4.html#a65355c8a8ccca4870060305479e7748c',1,'Validate4']]],
+  ['pair1_5fsorter_5ftype',['pair1_sorter_type',['../class_validate3.html#a6b5f6c01fe108e6c572c52249bf37caa',1,'Validate3']]],
+  ['pair1_5ftype',['pair1_type',['../class_validate3.html#abecec0e807ea06aac66c60387611e78a',1,'Validate3::pair1_type()'],['../class_validate4.html#aaa2fcb80a05115eb4ca02ab23df8827e',1,'Validate4::pair1_type()']]],
+  ['pair2_5fcomparator_5ftype',['pair2_comparator_type',['../class_validate3.html#a9a5316faa3c44f8f5743fec09cdea491',1,'Validate3']]],
[…]

### 2017-01-24 archive/html/search/typedefs_8.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['size_5fvector_5ftype',['size_vector_type',['../class_test.html#a9290f9f05f2aac6555e7366cf214d186',1,'Test::size_vector_type()'],['../class_validate.html#a3725fcfd4a55e4d8edc8b5d5955c081d',1,'Validate::size_vector_type()'],['../class_validate2.html#a8dab9b86f9c73419431821ebb68852c5',1,'Validate2::size_vector_type()'],['../class_validate3.html#a9dcb1d691c20940089a7e6fbf1619069',1,'Validate3::size_vector_type()'],['../class_validate4.html#a46ea31a0a4b23f583806792160421d15',1,'Validate4::size_vector_type()']]],
+  ['sorter',['sorter',['../struct_ex_tuple_sorter.html#adf836f2aaa3d62d311b66eccbf5543d5',1,'ExTupleSorter']]]
+];

### 2017-01-24 archive/html/search/typedefs_9.js

@@ -1,0 +1,17 @@
+var searchData=
+[
+  ['triple1_5fless_5fcomparator_5f1st_5ftype',['triple1_less_comparator_1st_type',['../class_validate4.html#af07a5152d547f7fba2f93b78660b88ab',1,'Validate4']]],
+  ['triple1_5fless_5fsorter_5f1st_5ftype',['triple1_less_sorter_1st_type',['../class_validate4.html#aa4a137d0ed68e95db5ebbe57544d80ed',1,'Validate4']]],
+  ['triple1_5ftype',['triple1_type',['../class_validate4.html#a8dd208bf04e6c5285cdacb9ac9532a67',1,'Validate4']]],
+  ['triple2_5fgreat_5fcomparator_5f1st_5ftype',['triple2_great_comparator_1st_type',['../class_test.html#aeafbf94ce50f60c6c463e2e57a4d43a5',1,'Test::triple2_great_comparator_1st_type()'],['../class_validate4.html#a17f3f46281d706a75c002eed273aeaf8',1,'Validate4::triple2_great_comparator_1st_type()']]],
+  ['triple2_5fgreat_5fsorter_5f1st_5ftype',['triple2_great_sorter_1st_type',['../class_test.html#ad87ac75730f80ef0824f0c56ec7db12d',1,'Test::triple2_great_sorter_1st_type()'],['../class_validate4.html#aa35a0ebf404821377118043d536be262',1,'Validate4::triple2_great_sorter_1st_type()']]],
+  ['triple2_5fless_5fcomparator_5f1st_5ftype',['triple2_less_comparator_1st_type',['../class_test.html#a8eb2bb639be9c46697c52f77d79703a8',1,'Test::triple2_less_comparator_1st_type()'],['../class_validate4.html#a83e9e52347608368b088892cabbdc8c5',1,'Validate4::triple2_less_comparator_1st_type()']]],
+  ['triple2_5fless_5fsorter_5f1st_5ftype',['triple2_less_sorter_1st_type',['../class_test.html#a1e7fba953871f5eee60eabf8b0e287b7',1,'Test::triple2_less_sorter_1st_type()'],['../class_validate4.html#a4c1bcea817e34f96d95c99e0694bbfc8',1,'Validate4::triple2_less_sorter_1st_type()']]],
[…]

### 2017-01-24 archive/html/search/typedefs_a.js

@@ -1,0 +1,8 @@
+var searchData=
+[
+  ['uint16',['uint16',['../types_8h.html#aea9840dd402bd5d5201bef4633398cb3',1,'types.h']]],
+  ['uint32',['uint32',['../types_8h.html#a8f95e75e58492e87412191fabadd8ca8',1,'types.h']]],
+  ['uint64',['uint64',['../types_8h.html#a60e8696a4678cd348e991a1f172e53f7',1,'types.h']]],
+  ['uint8',['uint8',['../types_8h.html#a115946cb5fc5879545e9ccea096a6031',1,'types.h']]],
+  ['uint_5ftype',['uint_type',['../structchoose__int__types_3_014_01_4.html#a3c2319206150de67a68544e265dabb29',1,'choose_int_types&lt; 4 &gt;::uint_type()'],['../structchoose__int__types_3_018_01_4.html#a4e70f94b235eba865f95080e668f666a',1,'choose_int_types&lt; 8 &gt;::uint_type()'],['../types_8h.html#a948660ad4bbc6ed2c3e3262a30bac0ff',1,'uint_type():&#160;types.h']]]
+];

### 2017-01-24 archive/html/search/typedefs_b.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['vector',['vector',['../struct_ex_vector.html#aa45a4c6039859d71d03827b07d265287',1,'ExVector']]]
+];

### 2017-01-24 archive/html/search/variables_0.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['_5f_5fattribute_5f_5f',['__attribute__',['../types_8h.html#af03243776893bcf5923a8f446b8d851c',1,'__attribute__():&#160;types.h'],['../namespacestd.html#ade73df0294cb697bb61d5edf0deac7d0',1,'std::__attribute__()']]]
+];

### 2017-01-24 archive/html/search/variables_1.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['buff_5fmem_5favail',['BUFF_MEM_AVAIL',['../common_8h.html#aff51988fecf5b6871480b3d91954df7d',1,'common.h']]],
+  ['bytes',['bytes',['../classuint128.html#a8ddedda58a986c591392955033f74495',1,'uint128::bytes()'],['../types_8h.html#ab09b9b43d1b1783c78e39783e382b3dd',1,'bytes():&#160;types.h']]]
+];

### 2017-01-24 archive/html/search/variables_2.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['ch_5fmax',['ch_max',['../struct_validate4_1_1_bkt_info.html#a1485e4eceab1832f682e1751d310d2b9',1,'Validate4::BktInfo::ch_max()'],['../struct_validate4_1_1_l_m_s_validate.html#a3e640263256e534dcf3da45f50ef0645',1,'Validate4::LMSValidate::ch_max()'],['../struct_validate4_1_1_r_m_q.html#a0addfc5d1067fca9a97939554cb0cd70',1,'Validate4::RMQ::ch_max()'],['../struct_validate4_1_1_r_scan.html#a3ff6f0be3fd0b25c66913d4d08b2e143',1,'Validate4::RScan::ch_max()'],['../struct_validate4_1_1_l_scan.html#a907234b2fa774b42e87050f0066e26b6',1,'Validate4::LScan::ch_max()']]],
+  ['cur_5fbuffers',['cur_buffers',['../classasync__multi__stream__writer.html#af1f19cbe619c771f1786abc038146e72',1,'async_multi_stream_writer']]]
+];

### 2017-01-24 archive/html/search/variables_3.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['digits',['digits',['../classuint128.html#a08388a396904d541e7e921f1f379b4a1',1,'uint128::digits()'],['../types_8h.html#af113dea6c24342761f00f6b36e99032e',1,'digits():&#160;types.h']]]
+];

### 2017-01-24 archive/html/search/variables_4.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['first',['first',['../structpair.html#aed925258783c91efbc5432030709d54e',1,'pair::first()'],['../structtriple.html#a6aa8508e6e6f859dda04f144f361c0d2',1,'triple::first()'],['../structquadruple.html#a45642eeda831800cd5c540037822ac65',1,'quadruple::first()'],['../tuples_8h.html#ae885a6822c40e26649c9dd8b476942f8',1,'first():&#160;tuples.h']]],
+  ['forth',['forth',['../structquadruple.html#abab1a25fd1ed39d2605eaa9371de04ca',1,'quadruple::forth()'],['../tuples_8h.html#a9c5c830dde97573ef7be2d18f35d61fd',1,'forth():&#160;tuples.h']]]
+];

### 2017-01-24 archive/html/search/variables_5.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['high',['high',['../classuint40.html#a830b04aa389a4e72c446cc88de38b656',1,'uint40::high()'],['../classuint128.html#a9f8275501c9a4546f37fae8e85e3ec05',1,'uint128::high()'],['../types_8h.html#a558f35d10292a79de791071eb8088a8c',1,'high():&#160;types.h']]]
+];

### 2017-01-24 archive/html/search/variables_6.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['k_5f512',['K_512',['../common_8h.html#a4b1a49a5378e8e0c9aca7501041c8d6d',1,'common.h']]]
+];

### 2017-01-24 archive/html/search/variables_7.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['l_5ftype',['L_TYPE',['../common_8h.html#a12286339af3610eed714aba8e56125ea',1,'common.h']]],
+  ['low',['low',['../classuint40.html#a216fde2e6997b39cb34b32daa869cef3',1,'uint40::low()'],['../classuint128.html#a439bdff9b7d8dd4bf99616bb07fc2a5e',1,'uint128::low()'],['../types_8h.html#ade07039efd8c0cfca1f9cead48259d4d',1,'low():&#160;types.h']]]
+];

### 2017-01-24 archive/html/search/variables_8.js

@@ -1,0 +1,82 @@
+var searchData=
+[
+  ['m_5f512',['M_512',['../common_8h.html#a260c3735667f0ab08a4c522a2e7bda23',1,'common.h']]],
+  ['m_5fbkt_5finfo',['m_bkt_info',['../class_validate4.html#a4f79c420ccec4e83e536fae655fe7a11',1,'Validate4']]],
+  ['m_5fbkt_5fsize',['m_bkt_size',['../struct_validate4_1_1_bkt_info.html#a1659db6479f4667a77043e842b93f3fc',1,'Validate4::BktInfo']]],
+  ['m_5fbufnum',['m_bufnum',['../classasync__multi__stream__reader.html#a24bef59afd1ef00b27d54e00a5f1c39a',1,'async_multi_stream_reader::m_bufnum()'],['../classasync__multi__stream__writer.html#a60bb0c6df357c9c9719527d812136ef3',1,'async_multi_stream_writer::m_bufnum()']]],
+  ['m_5fbufsize',['m_bufsize',['../classasync__multi__stream__reader.html#a4ddb169d2f5eff8499eef88ba091c566',1,'async_multi_stream_reader::m_bufsize()'],['../classasync__stream__writer.html#aea362e479496cec38f62cfe60402a390',1,'async_stream_writer::m_bufsize()'],['../classasync__multi__stream__writer.html#af8bf043c48fb1ad0dfa3e0a562e0e891',1,'async_multi_stream_writer::m_bufsize()']]],
+  ['m_5fbytes_5fread',['m_bytes_read',['../classasync__stream__reader.html#a5268366ca42bd2ef430e9e0817e9b274',1,'async_stream_reader::m_bytes_read()'],['../classasync__multi__stream__reader.html#a6486d4f10a3caf9169018d2bb71c4fdc',1,'async_multi_stream_reader::m_bytes_read()']]],
+  ['m_5fbytes_5fwritten',['m_bytes_written',['../classasync__stream__writer.html#a2e6bf4e33430ee652475dea9ce1ec7c5',1,'async_stream_writer::m_bytes_written()'],['../classasync__multi__stream__writer.html#a30c3a9ab1270eaff7fe8b2f1a98873b4',1,'async_multi_stream_writer::m_bytes_written()']]],
[…]

### 2017-01-24 archive/html/search/variables_9.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['p',['P',['../common_8h.html#aecfe9143b353556cb5a466f72c6a513c',1,'common.h']]],
+  ['prog_5fname',['prog_name',['../validate_8cpp.html#a598d558168ea9fcc902baf4a3a42a5ea',1,'prog_name():&#160;validate.cpp'],['../validate3_8cpp.html#a598d558168ea9fcc902baf4a3a42a5ea',1,'prog_name():&#160;validate3.cpp'],['../validate4_8cpp.html#a598d558168ea9fcc902baf4a3a42a5ea',1,'prog_name():&#160;validate4.cpp']]]
+];

### 2017-01-24 archive/html/search/variables_a.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['r',['R',['../common_8h.html#a465886396cb5767ddce1163c14db7209',1,'common.h']]]
+];

### 2017-01-24 archive/html/search/variables_b.js

@@ -1,0 +1,6 @@
+var searchData=
+[
+  ['s_5ftype',['S_TYPE',['../common_8h.html#a726936e5500c7ab70b64cbc308774a97',1,'common.h']]],
+  ['second',['second',['../structpair.html#a63ae1bbd5a6ce6bd6167b5359fa7a01f',1,'pair::second()'],['../structtriple.html#a41050194c8c7984707c7ad13c96e8631',1,'triple::second()'],['../structquadruple.html#aa93ca1ef60012d07903333d7b16bb32b',1,'quadruple::second()'],['../tuples_8h.html#a9a8a97f32d498c09c0f1f82c8a67bd6f',1,'second():&#160;tuples.h']]],
+  ['sentinel_5ftype',['SENTINEL_TYPE',['../common_8h.html#aceba1d712f3152d9ec9297ba5dd67f1b',1,'common.h']]]
+];

### 2017-01-24 archive/html/search/variables_c.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['third',['third',['../structtriple.html#a5675f08ea7996033edbcf7074404cdd8',1,'triple::third()'],['../structquadruple.html#af1ada0ce5f85bbc7df2c5bfb113b442d',1,'quadruple::third()'],['../tuples_8h.html#ab02b336e2ad870f773affd07b0f68ef8',1,'third():&#160;tuples.h']]]
+];

### 2017-01-24 archive/html/search/variables_d.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['val_5fmax',['val_max',['../struct_validate4_1_1_l_m_s_validate.html#a8dce0e079545d3c4f2649614053cf5f1',1,'Validate4::LMSValidate::val_max()'],['../struct_validate4_1_1_r_m_q.html#a45aa4f738281304a3f6bd5b9d78ef712',1,'Validate4::RMQ::val_max()']]]
+];

### 2017-01-24 draft/draft.tex
2017/01/24

@@
 In principle, the first method checks the lexical order and the LCP-value of two neighboring suffixes in the suffix array by literally comparing their characters in sequence.
-To reduce time complexity for the string comparison, we employ a Karp-Rabin fingerprinting function to transform each of the involved comparand into a single integer, called fingerprint, and compare the fingerprints instead to correctly check the equality of their prototypes with a negilible error probability.
+To reduce time complexity for the string comparison, a Karp-Rabin fingerprinting function is employed to transform each involved comparand into a single integer, called fingerprint, and the fingerprints are compared to correctly check the equality of their prototypes with a negilible error probability.
 We will demonstrate that all the fingerprints in need can be calculated using linear time when scanning the input string.
-The experimental results indicate that the space efficiency remains invaraint with the increasing of input size, while both time and I/O consumptions grows linearly under the same circumstances.
-
-The second method verifies the two arrays following the induced-sorting principle.
+The experimental results indicate that both time and I/O consumptions grow linearly with the increasing input size while the space demand remains unchanged under the same circumstances.
 

### 2017-01-25 draft/draft.tex
2017/01/25

@@
 The first method checks the lexical order and the LCP-value of two neighboring suffixes in the given suffix array by computing and comparing the fingerprints of their LCPs.
-The second method first applies the same technique to check a subset of the suffix and LCP arrays, and then checks the remaining when augmenting them from the verified part following the induced-sorting principle.
-The experimental results indicate that, xxx.
+The second method first applies the fingerprinting technique to check a subset of the given suffix and LCP arrays, then it produces the whole arrays from the verified parts following the induced-sorting principle and compares the induced and input copies with each other for verification.
 
@@
 
-The contribution in this paper mainly includes two methods for checking the given suffix and LCP arrays in external memory, where both methods work for constant alphabets and the former can be also applied to integer ones.
+The contribution in this paper mainly includes two methods for checking the given suffix and LCP arrays in external memory.
 
-In principle, the first method checks the lexical order and the LCP-value of two neighboring suffixes in the suffix array by literally comparing their characters in sequence.
-To reduce time complexity for the string comparison, a Karp-Rabin fingerprinting function is employed to transform each involved comparand into a single integer, called fingerprint, and the fingerprints are compared to correctly check the equality of their prototypes with a negilible error probability.
-We will demonstrate that all the fingerprints in need can be calculated using linear time when scanning the input string.
-The experimental results indicate that both time and I/O consumptions grow linearly with the increasing input size while the space demand remains unchanged under the same circumstances.
+The main idea of the first method is to check the lexical order and the LCP-value of two neighboring suffixes in a suffix array by literally comparing their characters.
+To reduce time complexity for a comparison between two sequences of characters, a Karp-Rabin fingerprinting function is employed to transform each sequence into a single integer, called fingerprint, such that the equality of two sequences can be correctly checked with a negiligible error probability by comparing their fingerprints in constant time.
 
-The second method verifies the two arrays following the induced-sorting principle, which was formerly proposed for building suffix and LCP arrays in both internal and external memory.
-
- This technique is also employed in the second method 
-The second method is adapted from the induced-sorting principle.
-
-The second method checks both suffix and LCP arrays based on the induced-sorting principle.
-The main idea is to first check a subset of the suffix and LCP arrays and then verify the inducing process to ensure the correctness of the final suffix and LCP arrays augmented from the subset.
-Different from the previous method, it can be also integrated into any algorithm for inducing suffix and LCP arrays to build and check the arrays simultaneously.
+The second method first verifies a subset chosen from the given suffix and LCP arrays by using the fingerprinting technique adopted in the prior method.
+Then, it continues to produce the global suffix and LCP arrays from the verified subset following the induced sorting principle.
+Given that the inducing process is right, then the given suffix and LCP arrays are correct if they are identical to the induced counterparts.
 
 The remainder of this paper is organized as follows.
-We describe the proposed methods and algorithms in Sections~\ref{sec:method1} and~\ref{sec:method2}, then present the experimental results in Section~\ref{sec:experiment}, and give the conclusion in Section~\ref{sec:conclusion}.
-
-{\color{red}
-
-A suggested paper's framework:
-
-1. The straightforward algorithm for computing and comparing the FPs of each pair of neighboring items in the LCP array, for checking both the SA and the LCP arrays.
-
-The drawback is space consuming, to be overcome by the algorithms proposed in the rest of this article...
-
-2. The method for building and checking simultaneously, for the suffix and LCP arrays constructed by induced sorting.
-
-The principle of induced sorting is explained here.
-
-The drawback is that it is applicable only for an array built by inducd sorting, to be overcome by further extending the idea to check any given array.
-
-3. Extend the 2nd method to check any given suffix or LCP arrays.
-
-4. Experiments
-
-5. Conclusion
-}
+We first describe the proposed two checking methods in Sections~\ref{sec:method1} and~\ref{sec:method2}, then present the experimental results in Section~\ref{sec:experiment},and give the conclusion in Section~\ref{sec:conclusion}.
 
@@
 
-	\subsection{Notations} \label{sec:method1:notations}
-	Given an input string $x[0, n)$ drawn from an alphabet $\Sigma$, we say $x[i, j]$ is a substring of $x$ that starts with $x[i]$ and ends with $x[j]$.
-Particularly, $x[i, j]$ is a suffix of $x$ if $j = n - 1$.
-For short, we denote $x[i, n)$ by ${\sf suf}(i)$.
+\subsection{Preliminaries} \label{sec:method1:notations}
+
+Given an input string $x[0, n)$ drawn from an alphabet $\{\Sigma \cup \$\}$, we suppose $t
+
+suppose $\$$ to be smaller than any other characters and only appears in $x[n - 1]$.
+We denote by ${\sf sub}(i, j)$ a substring of $x$ starting from $x[i]$ to $x[j]$.
+Paricularly, if $j = n - 1$, we say ${\sf sub}(i, j)$ is a suffix of $x$ and represent it by ${\sf suf}(i)$ for the sake of description.
+The suffix array of $x$,
 

### 2017-01-27 draft/draft.tex
2017/01/27

@@
 
-The contribution in this paper mainly includes two methods for checking the given suffix and LCP arrays in external memory.
+Our contribution mainly includes two checking methods for the given suffix and LCP arrays in external memory.
 
-The main idea of the first method is to check the lexical order and the LCP-value of two neighboring suffixes in a suffix array by literally comparing their characters.
+The main idea of the first method is to test the lexical order and the LCP-value of two neighboring suffixes in a suffix array by literally comparing their characters.
 To reduce time complexity for a comparison between two sequences of characters, a Karp-Rabin fingerprinting function is employed to transform each sequence into a single integer, called fingerprint, such that the equality of two sequences can be correctly checked with a negiligible error probability by comparing their fingerprints in constant time.
 
-The second method first verifies a subset chosen from the given suffix and LCP arrays by using the fingerprinting technique adopted in the prior method.
-Then, it continues to produce the global suffix and LCP arrays from the verified subset following the induced sorting principle.
-Given that the inducing process is right, then the given suffix and LCP arrays are correct if they are identical to the induced counterparts.
+By using the same fingerprinting technique, the second method first verifies a subset chosen from the input arrays and then produces a copy of the suffix and LCP arrays from the verified subset following the induced sorting principle.
+Given that the inducing process is correct, the input arrays are considered to be right with a high probability if they are equal to the induced copies.
 
@@
 
-Given an input string $x[0, n)$ drawn from an alphabet $\{\Sigma \cup \$\}$, we suppose $t
+Given an input string $x$ drawn from an alphabet $\Sigma$, we assume that $x[n - 1] = \$$ and $\$ \in \Sigma$ is smaller than any other characters in $x$.
+The suffix array of $x$, denoted by $sa$, is a permutation of $\{0, 1, ..., n - 1\}$ such that ${\sf suf}(sa[i]) < {\sf suf}(sa[j])$ for all $0 \le i < j < n$, where ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$ are the suffixes starting with $x[sa[i]]$ and $x[sa[j]]$, respectively.
+Particularly, we say ${\sf suf}(sa[i])$ is a lexical neighbor of ${\sf suf}(sa[j])$ if $|i - j| = 1$.
+The LCP array of $x$, denoted by $lcp$, consists of $n$ integers, where $lcp[i]$ records the LCP-value of ${\sf suf}(sa[i])$ and its left neighbor in $sa$ for $i \in [1, n)$.
 
-suppose $\$$ to be smaller than any other characters and only appears in $x[n - 1]$.
-We denote by ${\sf sub}(i, j)$ a substring of $x$ starting from $x[i]$ to $x[j]$.
-Paricularly, if $j = n - 1$, we say ${\sf sub}(i, j)$ is a suffix of $x$ and represent it by ${\sf suf}(i)$ for the sake of description.
-The suffix array of $x$,
+\subsection{Idea} \label{sec:method1:idea}
 
-The suffix array of $x$, denoted by $sa$, is a permutation of $\{0, 1, \dots, n - 1\}$ such that ${\sf suf}(sa[i])$ is lexicographically greater than ${\sf suf}(sa[i - 1])$ for all $i \in [1, n)$.
-
-The LCP array of $x$, denoted by $lcp$, is composed of $n$ integers, where $lcp[0] = 0$ and $lcp[i]$ equals to the length of LCP of ${\sf suf}(sa[i])$ and ${\sf suf}(sa[i - 1])$ for all $i \in [1, n)$, i.e., the first $lcp[i]$ characters of ${\sf suf}(sa[i])$ and ${\sf suf}(sa[i - 1])$ are identical and the $(lcp[i]+1)$-th characters of two suffixes are different.
-For notation convenience, we refer the length of an LCP as LCP value or LCP length.
-
-	\subsection{Main Idea} \label{sec:method1:idea}
-
-	We first present in Lemma~\ref{lemma:1} the conditions that are sufficient and necessary for checking the suffix and LCP arrays.
-Specifically, condition (1) demonstrates that all the suffixes in $x$ are sorted in $sa$, while conditions (2)-(3) indicate that the order and the LCP value of any two neighboring suffixes in $sa$ are both correct.
+The lexical order and the LCP-value of two suffixes starting with $x[i]$ and $x[j]$ can be determined by literally comparing their characters rightward with $k$ increasing from $0$.
+Because all the suffixes differ in length and end with a common character, there must exist $k \in [0, n)$ such that $x[i, i + k) = x[j, j + k)$ and $x[i + k] \ne x[j + k]$.
+Lemma~\ref{lemma:1} indicates that this method can be also applied to checking suffix and LCP arrays, but it suffers from high time complexity as the two substrings indicated by the LCP-value for each pair of neighboring suffixes in $sa$ takes at most $\mathcal{O}(n)$ character-wise comparisons.
+An alternative is to exploit a perfect hash function~(PHF) to convert each substring into a single integer such that any two substrings have a common hash value if and only if they are literally equal to each other.
+Then, the equality of two substrings can be tested in constant time by comparing the corresponding hash values instead.
 
@@
 	Both the sufficiency and necessity are immediately seen from the definition of suffix and LCP arrays.
+Specifically, condition (1) demonstrates that all the suffixes in $x$ are sorted in $sa$, while conditions (2)-(3) indicate that the lexical order and the LCP-value of any two neighboring suffixes in $sa$ are both correct.
 \end{IEEEproof}
 
-	Obviously, we can generalize Lemma~\ref{lemma:1} to check any subset of $sa$ and $lcp$. Besides, given that $sa$ or $lcp$ is correct, this lemma can be used to check $lcp$ or $sa$ alone as well.
-
-	For each pair of neighboring suffixes in $sa$, say ${\sf suf}(sa[i])$ and ${\sf suf}(sa[i + 1])$, it takes at worst $\mathcal{O}(n)$ time to perform a character-wise string comparison for checking their leftmost $lcp[i]$ characters.
-An alternative is to compare the two sequences of characters by their hash values in constant time.
-This can be done using a perfect hash function~(PHF) that maps two strings to an identical integer if and only if they are literally equal to each other.
-However, the cost of finding a PHF is non-negligible in practice, thus we prefer to use the Karp-Rabin fingerprinting function~\cite{Karp1987} for conducting the string-to-integer transformations mentioned above.
-Concretely, given a prime $L$ and an integer $\delta \in [1, L)$, the fingerprint of a substring $x[i, j]$, denoted by ${\sf fp}(i, j)$, can be calculated according to the following two formulas:
+The key point here is how to efficiently compute the hash values for the involved substrings.
+Taking into account the high cost of finding a PHF for this requirement, we choose to use the Karp-Rabin fingerprinting function~\cite{Karp1987} for conducting these conversions, where all the substrings can be transformed into their integer forms, called fingerprints, by accessing characters of $x$ sequentially.
+Specifically, suppose $L$ is a prime and $\delta$ is randomly chosen from $[1, L)$, the fingerprint ${\sf fp}(i, j)$ of substring $x[i, j]$ can be calculated according to the three formulas below, where the first two are for computing ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ when scanning $x$ rightward and the last is for computing their difference.
+It is worthy of pointing out that two equal substrings always have a common fingerprint, but the inverse is not true.
+Fortunately, it has been proved that the probability of a false match can be reduced to a negligible level by setting $L$ to a large value~\cite{Karp1987}.
+This property is utilized in~\cite{Bille2013} to design a probabilistic algorithm for computing a sparse suffix array.
 
 \begin{Formula} \label{formula:1}
-		${\sf fp}(0, i) = {\sf fp}(0, i - 1) \cdot {\delta} + x[i]\mod L$ for $i \ge 0$, or ${\sf fp}(0, i) = 0$ for $i < 0$.
+	${\sf fp}(0, -1) = 0$.
 
@@
 \begin{Formula} \label{formula:2}	
+	${\sf fp}(0, i) = {\sf fp}(0, i - 1) \cdot {\delta} + x[i]\mod L$ for $i \ge 0$.
+
+\end{Formula}
+
+\begin{Formula} \label{formula:3}
 	${\sf fp}(i, j) = {\sf fp}(0, j) - {\sf fp}(0 ,i - 1) \cdot {\delta}^{j - i + 1}\mod L$.
@@
 
-	Notice that two equal substrings always have a common fingerprint, but the inverse is not true.
-Fortunately, it has been proved that the probability of a false match can be reduced to a negligible level by setting $L$ properly~\cite{Karp1987}.
-This property is utilized in~\cite{Bille2013} to design a probabilistic algorithm for computing a sparse suffix array.
-Using the fingerprinting function, we have Corollary~\ref{corollary:1}.
+The above discussion leads us to Corollary~\ref{corollary:1}.
+In the rest of this section, we will describe the algorithmic design and implementation of our first checking method based on this conclusion.
 
@@
 	\end{enumerate}
-
 \end{Corollary}

### 2017-02-01 draft/draft.tex
2017/02/01

@@
 
-Our contribution mainly includes two checking methods for the given suffix and LCP arrays in external memory.
+Our contribution includes two checking methods for the given suffix and LCP arrays in external memory.
 
@@
 The suffix array of $x$, denoted by $sa$, is a permutation of $\{0, 1, ..., n - 1\}$ such that ${\sf suf}(sa[i]) < {\sf suf}(sa[j])$ for all $0 \le i < j < n$, where ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$ are the suffixes starting with $x[sa[i]]$ and $x[sa[j]]$, respectively.
-Particularly, we say ${\sf suf}(sa[i])$ is a lexical neighbor of ${\sf suf}(sa[j])$ if $|i - j| = 1$.
+Particularly, ${\sf suf}(sa[i])$ is a lexical neighbor of ${\sf suf}(sa[j])$ if $|i - j| = 1$.
 The LCP array of $x$, denoted by $lcp$, consists of $n$ integers, where $lcp[i]$ records the LCP-value of ${\sf suf}(sa[i])$ and its left neighbor in $sa$ for $i \in [1, n)$.
@@
 
-The lexical order and the LCP-value of two suffixes starting with $x[i]$ and $x[j]$ can be determined by literally comparing their characters rightward with $k$ increasing from $0$.
+The lexical order and the LCP-value of ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$ can be determined by literally comparing their characters from left to right.
 Because all the suffixes differ in length and end with a common character, there must exist $k \in [0, n)$ such that $x[i, i + k) = x[j, j + k)$ and $x[i + k] \ne x[j + k]$.
-Lemma~\ref{lemma:1} indicates that this method can be also applied to checking suffix and LCP arrays, but it suffers from high time complexity as the two substrings indicated by the LCP-value for each pair of neighboring suffixes in $sa$ takes at most $\mathcal{O}(n)$ character-wise comparisons.
-An alternative is to exploit a perfect hash function~(PHF) to convert each substring into a single integer such that any two substrings have a common hash value if and only if they are literally equal to each other.
-Then, the equality of two substrings can be tested in constant time by comparing the corresponding hash values instead.
+According to Lemma~\ref{lemma:1}, this method can be also applied to checking suffix and LCP arrays, but it suffers from high time complexity as the two substrings indicated by the LCP-value for each pair of neighboring suffixes in $sa$ take at most $\mathcal{O}(n)$ character-wise comparisons.
 
@@
 
-The key point here is how to efficiently compute the hash values for the involved substrings.
-Taking into account the high cost of finding a PHF for this requirement, we choose to use the Karp-Rabin fingerprinting function~\cite{Karp1987} for conducting these conversions, where all the substrings can be transformed into their integer forms, called fingerprints, by accessing characters of $x$ sequentially.
-Specifically, suppose $L$ is a prime and $\delta$ is randomly chosen from $[1, L)$, the fingerprint ${\sf fp}(i, j)$ of substring $x[i, j]$ can be calculated according to the three formulas below, where the first two are for computing ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ when scanning $x$ rightward and the last is for computing their difference.
-It is worthy of pointing out that two equal substrings always have a common fingerprint, but the inverse is not true.
-Fortunately, it has been proved that the probability of a false match can be reduced to a negligible level by setting $L$ to a large value~\cite{Karp1987}.
-This property is utilized in~\cite{Bille2013} to design a probabilistic algorithm for computing a sparse suffix array.
+An alternative is to exploit a perfect hash function~(PHF) to convert each substring into a single integer such that any two substrings have a common hash value if and only if they are literally equal to each other.
+Hence, the equality of two substrings can be determined by comparing the corresponding hash values instead.
+The key point here is how to efficiently compute the hash values of $x[sa[i], sa[i] + lcp[i] - 1]$ and $x[sa[i - 1], sa[i - 1] + lcp[i] - 1]$ for all $i \in [1, n)$.
+Taking into account the high cost of finding a PHF to meet this requirement, we prefer using a Karp-Rabin fingerprinting function~\cite{Karp1987} to transform a substring into its integer form, called fingerprint.
+Specifically, suppose $L$ is a prime and $\delta$ is randomly chosen from $[1, L)$, the fingerprint ${\sf fp}(i, j)$ of a substring $x[i, j]$ can be calculated according to the formulas listed below: scan $x$ rightward and use Formulas~\ref{formula:1}-\ref{formula:2} to iteratively compute ${\sf fp}(0, k)$ for all $k \in [0, n)$, record ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ during the scan and subtract the former from the latter to obtain ${\sf fp}(i, j)$ following Formula~\ref{formula:3}.
 
@@
 
-The above discussion leads us to Corollary~\ref{corollary:1}.
-In the rest of this section, we will describe the algorithmic design and implementation of our first checking method based on this conclusion.
+It is worthy of pointing out that two equal substrings always share a common fingerprint, but the inverse is not true.
+Fortunately, it has been proved in~\cite{Karp1987} that the probability of a false match can be reduced to a negligible level by setting $L$ to a large value\footnote{This property is utilized in~\cite{Bille2013} to design a probabilistic algorithm for computing a sparse suffix array.
+}.
+This leads us to the following conclusion.
 
@@
 
+In the rest of this section, we describe the algorithm for checking the given suffix and LCP arrays using external memory based on this conclusion.
+
 \subsection{Algorithm} \label{sec:method1:algorithm}
+
+Following the discussion in Section~\ref{sec:method1:idea}, the conditions of Corollary~\ref{corollary:1} can be checked using $\mathcal{O}(n)$ time and space in random access models by the 2-step procedure below:
+
+\begin{itemize}
+	\item [S1.]
+	Scan $x$ rightward with $i$ increasing from $0$ to $n - 1$. For each scanned $x[i]$, iteratively compute ${\sf fp}(0, i)$ and set $fp[i] = {\sf fp}(0, i)$.
+
+	\item [S2.]
+	Scan $sa$ and $lcp$ rightward with $i$ increasing from $1$ to $n - 1$.
+For each scanned $sa[i]$ and $lcp[i]$, let $u = sa[i], v = lcp[i], w = sa[i - 1]$, then: (1) retrieve $fp[u - 1]$ and $fp[u + v - 1]$ from $fp$ to compute ${\sf fp}(u, u + v - 1)$; (2) retrieve $fp[w - 1]$ and $fp[w + v - 1]$ from $fp$ to compute ${\sf fp}(w, w + v - 1)$; (3) check if ${\sf fp}(u, u + v - 1) = {\sf fp}(w, w + v - 1)$ and $x[u + v] = x[w + v]$.
+
+\end{itemize}
+
+However, when running in external memory models,
+
+The algorithm  algorithm~\ref{alg:1} to check the suffix and LCP arrays in external memory. This algorithm mainly consists of three steps, where the first two steps
 
@@
 
-		\caption{The algorithm using Method A.}
+	\caption{The algorithmic framework for Method A.}
 

### 2017-02-02 draft/draft.tex
2017/02/02

@@
 Taking into account the high cost of finding a PHF to meet this requirement, we prefer using a Karp-Rabin fingerprinting function~\cite{Karp1987} to transform a substring into its integer form, called fingerprint.
-Specifically, suppose $L$ is a prime and $\delta$ is randomly chosen from $[1, L)$, the fingerprint ${\sf fp}(i, j)$ of a substring $x[i, j]$ can be calculated according to the formulas listed below: scan $x$ rightward and use Formulas~\ref{formula:1}-\ref{formula:2} to iteratively compute ${\sf fp}(0, k)$ for all $k \in [0, n)$, record ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ during the scan and subtract the former from the latter to obtain ${\sf fp}(i, j)$ following Formula~\ref{formula:3}.
+Specifically, suppose $L$ is a prime and $\delta$ is randomly chosen from $[1, L)$, the fingerprint ${\sf fp}(i, j)$ of a substring $x[i, j]$ can be calculated according to the three formulas listed below: scan $x$ rightward and use Formulas~\ref{formula:1}-\ref{formula:2} to iteratively compute ${\sf fp}(0, k)$ for all $k \in [0, n)$, record ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ during the scan and subtract the former from the latter to obtain ${\sf fp}(i, j)$ following Formula~\ref{formula:3}.
 
@@
 
-In the rest of this section, we describe the algorithm for checking the given suffix and LCP arrays using external memory based on this conclusion.
-
 \subsection{Algorithm} \label{sec:method1:algorithm}
 
-Following the discussion in Section~\ref{sec:method1:idea}, the conditions of Corollary~\ref{corollary:1} can be checked using $\mathcal{O}(n)$ time and space in random access models by the 2-step procedure below:
+Following the ideas in Section~\ref{sec:method1:idea}, we can check $sa$ and $lcp$ using the 3-step procedure below.
 
 \begin{itemize}
-	\item [S1.]
+	\item [S1]
 	Scan $x$ rightward with $i$ increasing from $0$ to $n - 1$. For each scanned $x[i]$, iteratively compute ${\sf fp}(0, i)$ and set $fp[i] = {\sf fp}(0, i)$.
 
-	\item [S2.]
+	\item [S2]
 	Scan $sa$ and $lcp$ rightward with $i$ increasing from $1$ to $n - 1$.
-For each scanned $sa[i]$ and $lcp[i]$, let $u = sa[i], v = lcp[i], w = sa[i - 1]$, then: (1) retrieve $fp[u - 1]$ and $fp[u + v - 1]$ from $fp$ to compute ${\sf fp}(u, u + v - 1)$; (2) retrieve $fp[w - 1]$ and $fp[w + v - 1]$ from $fp$ to compute ${\sf fp}(w, w + v - 1)$; (3) check if ${\sf fp}(u, u + v - 1) = {\sf fp}(w, w + v - 1)$ and $x[u + v] = x[w + v]$.
+For each scanned $sa[i]$ and $lcp[i]$, let $u = sa[i], v = lcp[i], w = sa[i - 1]$ and performs the following three substeps in sequence:
+
+	\begin{itemize}
+		\item [(a)] 
+		Retrieve $fp[u - 1]$ and $fp[u + v - 1]$ from $fp$ to compute ${\sf fp}(u, u + v - 1)$. Set $mk[u] = 1$.
+
+		\item [(b)] 
+		Retrieve $fp[w - 1]$ and $fp[w + v - 1]$ from $fp$ to compute ${\sf fp}(w, w + v - 1)$.
+
+		\item [(c)] 
+		Check if ${\sf fp}(u, u + v - 1) = {\sf fp}(w, w + v - 1)$ and $x[u + v] > x[w + v]$.
+	\end{itemize}
+
+	\item [S3] Set $mk[sa[0]] = 1$. Check if $mk[i] = 1$ for all $i \in [0, n)$.
 
@@
 
-However, when running in external memory models,
+Two zero-initialized arrays $fp$ and $mk$ are employed to faciliate the checking process, where the former is for storing the fingerprints of all the prefixes of $x$ and the latter is for indicating the existences of $\{0, 1, ..., n - 1\}$ in $sa$.
+This procedure consumes $\mathcal{O}(n)$ time and space when running in internal memory.
+However, if the input can not be wholly accommodated into RAM, it performs random I/O accesses frequently to visit $sa$ and $lcp$ in external memory during the execution of S2, leading to a large performance degradation.
 
-The algorithm  algorithm~\ref{alg:1} to check the suffix and LCP arrays in external memory. This algorithm mainly consists of three steps, where the first two steps
+In what follows, we describe an external-memory algorithm for checking the conditions of Corollary~\ref{corollary:1} in a disk-friendly way.
+As shown in Fig.~\ref{fig:xxx}, this algorithm mainly consists of three steps and each step is explained as following.
 
@@
 
-	Step 1. Compute ${\sf fp}(sa[i], sa[i] + lcp[i] - 1)$ and retrieve $x[sa[i] + lcp[i]]$ for $i \in [1, n)$.
+	Step 1. Sort $sa[i]$ by $i$ for all $i \in [0, n)$.
+
+	Step 2.
+
+	ompute ${\sf fp}(sa[i], sa[i] + lcp[i] - 1)$ and retrieve $x[sa[i] + lcp[i]]$ for $i \in [1, n)$.
 

### 2017-02-04 draft/draft.tex
2017/02/02

@@
 \usepackage{graphicx}
-\usepackage[ruled, noend]{algorithm2e}
+\usepackage[ruled, linesnumbered, noend]{algorithm2e}
 \usepackage{url}
@@
 
-Given an input string $x$ drawn from an alphabet $\Sigma$, we assume that $x[n - 1] = \$$ and $\$ \in \Sigma$ is smaller than any other characters in $x$.
-The suffix array of $x$, denoted by $sa$, is a permutation of $\{0, 1, ..., n - 1\}$ such that ${\sf suf}(sa[i]) < {\sf suf}(sa[j])$ for all $0 \le i < j < n$, where ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$ are the suffixes starting with $x[sa[i]]$ and $x[sa[j]]$, respectively.
-Particularly, ${\sf suf}(sa[i])$ is a lexical neighbor of ${\sf suf}(sa[j])$ if $|i - j| = 1$.
-The LCP array of $x$, denoted by $lcp$, consists of $n$ integers, where $lcp[i]$ records the LCP-value of ${\sf suf}(sa[i])$ and its left neighbor in $sa$ for $i \in [1, n)$.
+Given an input string $x[0, n)$ drawn from an alphabet $\Sigma$, the suffix array of $x$, denoted by $sa$, is a permutation of $\{0, 1, ..., n - 1\}$ such that ${\sf suf}(sa[i]) < {\sf suf}(sa[j])$ is satisfied for $0 \le i < j < n$, where ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$ are two suffixes starting with $x[sa[i]]$ and $x[sa[j]]$, respectively.
+Particularly, we say ${\sf suf}(sa[i - 1])$ and  ${\sf suf}(sa[i + 1])$ are the lexical neighbors of ${\sf suf}(sa[i])$ in $sa$.
+The LCP array of $x$, denoted by $lcp$, consists of $n$ integers, where $lcp[0]:=0$ and $lcp[i]$ records the LCP-value of ${\sf suf}(sa[i])$ and ${\sf suf}(sa[i - 1])$ for $i \in [1, n)$.
 
@@
 Because all the suffixes differ in length and end with a common character, there must exist $k \in [0, n)$ such that $x[i, i + k) = x[j, j + k)$ and $x[i + k] \ne x[j + k]$.
-According to Lemma~\ref{lemma:1}, this method can be also applied to checking suffix and LCP arrays, but it suffers from high time complexity as the two substrings indicated by the LCP-value for each pair of neighboring suffixes in $sa$ take at most $\mathcal{O}(n)$ character-wise comparisons.
+According to Lemma~\ref{lemma:1}, this method can be also applied to checking suffix and LCP arrays, but it suffers from high time complexity as the two substrings indicated by the LCP-value for each pair of neighboring suffixes in $sa$ take at worst $\mathcal{O}(n)$ character-wise comparisons.
 
@@
 Taking into account the high cost of finding a PHF to meet this requirement, we prefer using a Karp-Rabin fingerprinting function~\cite{Karp1987} to transform a substring into its integer form, called fingerprint.
-Specifically, suppose $L$ is a prime and $\delta$ is randomly chosen from $[1, L)$, the fingerprint ${\sf fp}(i, j)$ of a substring $x[i, j]$ can be calculated according to the three formulas listed below: scan $x$ rightward and use Formulas~\ref{formula:1}-\ref{formula:2} to iteratively compute ${\sf fp}(0, k)$ for all $k \in [0, n)$, record ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ during the scan and subtract the former from the latter to obtain ${\sf fp}(i, j)$ following Formula~\ref{formula:3}.
+Specifically, suppose $L$ is a prime and $\delta$ is randomly chosen from $[1, L)$, the fingerprint ${\sf fp}(i, j)$ of a substring $x[i, j]$ can be calculated by using Formulas~\ref{formula:1}-~\ref{formula:3} as following: scan $x$ rightward to iteratively compute ${\sf fp}(0, k)$ for all $k \in [0, n)$ according to Formulas~\ref{formula:1}-\ref{formula:2}, meanwhile, record ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ and subtract the former from the latter to obtain ${\sf fp}(i, j)$ according to Formula~\ref{formula:3}.
 
@@
 
-It is worthy of pointing out that two equal substrings always share a common fingerprint, but the inverse is not true.
+It is worthy of mentioning that two equal substrings always share a common fingerprint, but the inverse is not true.
 Fortunately, it has been proved in~\cite{Karp1987} that the probability of a false match can be reduced to a negligible level by setting $L$ to a large value\footnote{This property is utilized in~\cite{Bille2013} to design a probabilistic algorithm for computing a sparse suffix array.
@@
 
-Following the ideas in Section~\ref{sec:method1:idea}, we can check $sa$ and $lcp$ using the 3-step procedure below.
+Section~\ref{sec:method1:idea} indicates that we can perform verification for the given suffix and LCP arrays by testing the conditions of Corollary~\ref{corollary:1}.
+Based on this idea, we introduce below a linear algorithm for checking $sa$ and $lcp$ on random access models.
 
@@
 	\item [S2]
-	Scan $sa$ and $lcp$ rightward with $i$ increasing from $1$ to $n - 1$.
-For each scanned $sa[i]$ and $lcp[i]$, let $u = sa[i], v = lcp[i], w = sa[i - 1]$ and performs the following three substeps in sequence:
+	Scan $sa$ and $lcp$ rightward with $i$ increasing from $1$ to $n - 1$. For each scanned $sa[i]$ and $lcp[i]$, let $u = sa[i], v = lcp[i], w = sa[i - 1]$ and performs substeps (a)-(c) sequentially:
 
@@
 
-Two zero-initialized arrays $fp$ and $mk$ are employed to faciliate the checking process, where the former is for storing the fingerprints of all the prefixes of $x$ and the latter is for indicating the existences of $\{0, 1, ..., n - 1\}$ in $sa$.
-This procedure consumes $\mathcal{O}(n)$ time and space when running in internal memory.
-However, if the input can not be wholly accommodated into RAM, it performs random I/O accesses frequently to visit $sa$ and $lcp$ in external memory during the execution of S2, leading to a large performance degradation.
-
-In what follows, we describe an external-memory algorithm for checking the conditions of Corollary~\ref{corollary:1} in a disk-friendly way.
-As shown in Fig.~\ref{fig:xxx}, this algorithm mainly consists of three steps and each step is explained as following.
+Two zero-initialized arrays $fp$ and $mk$ are employed to faciliate the checking process, where the former is for storing the fingerprints of all the prefixes in $x$ and the latter is for checking the existence of $\{0, 1, ..., n - 1\}$ in $sa$.
+Clearly, this algorithm consumes $\mathcal{O}(n)$ time and space when running in internal memory.
+However, if the input can not be wholly accommodated into RAM, it may suffer from a performance degradation due to frequent random I/O operations for reading elements of $x$, $sa$ and $lcp$ from external memory during the execution of S2.
 
@@
 
-	\SetAlgoNoLine
+	\caption{The Algorithm for checking the conditions of Corollary~\ref{corollary:1}.}
+
+	\label{alg:1}
+
+	%\SetAlgoNoLine
 
@@
 
-	Step 1. Sort $sa[i]$ by $i$ for all $i \in [0, n)$.
+	$ST_1$ := $[(sa[i], i, null) | i \in [0, n)]$. \label{alg:1:a}
 
-	Step 2.
+	$ST_2$ := $[(sa[i] + lcp[i + 1], i, null, null) | i \in [0, n - 1)]$.
 
-	ompute ${\sf fp}(sa[i], sa[i] + lcp[i] - 1)$ and retrieve $x[sa[i] + lcp[i]]$ for $i \in [1, n)$.
+	$ST_3$ := $[(sa[i] + lcp[i], i, null, null) | i \in [1, n)]$.
 
-	Step 2. Compute ${\sf fp}(sa[i], sa[i] + lcp[i + 1] - 1)$ and retrieve $x[sa[i] + lcp[i + 1]]$ for $i \in [0, n - 1)$.
+	sort tuples in $ST_1$, $ST_2$ and $ST_3$ by 1st component. \label{alg:1:b}
 
-	Step 3. Check if ${\sf fp}(sa[i], sa[i] + lcp[i] - 1) = {\sf fp}(sa[i - 1], sa[i - 1] + lcp[i] - 1)$ and $x[sa[i] + lcp[i]] > x[sa[i - 1] + lcp[i]]$ for $i \in [1, n)$.
+	$fp := 0$  \label{alg:1:c}
 
-	\caption{The algorithmic framework for Method A.}
+	\For{$i \in [0, n]$}{
 
-	\label{alg:1}
+		\If{$ST_1.{\sf notEmpty}()$ {\sf and} $ST_1.{\sf top}().1st = i$}{~\label{alg:1:h}
+
+			$e := ST_1.{\sf top}()$, $ST_1.{\sf pop}()$, $e.3rd := fp$, $ST_1'.{\sf push}(e)$
+		}
+		\Else{
+
+			\Return false \hspace{5cm} // condition (1) is violated
+		}~\label{alg:1:i}
+
+		\While{$ST_2.{\sf notEmpty}()$ {\sf and} $ST_2.{\sf top}().1st = i$}{
+
+			$e := ST_2.{\sf top}()$, $ST_2.{\sf pop}()$, $e.3rd := fp$, $e.4th := x[i]$, $ST_2'.{\sf push}(e)$ 
+		}
+
+		\While{$ST_3.{\sf notEmpty}()$ {\sf and} $ST_3.{\sf top}().1st = i$}{
+
+			$e := ST_3.{\sf top}()$, $ST_3.{\sf pop}()$, $e.3rd := fp$, $e.4th := x[i]$, $ST_3'.{\sf push}(e)$ 
+		}
+
+		$fp := fp \cdot \delta + x[i] \! \mod \! P$
+	} \label{alg:1:d}
+
+	sort tuples in $ST_1$, $ST_2$ and $ST_3$ by 2nd component.  \label{alg:1:e}
+
+	\For {$i \in [1, n - 1)$}{  \label{alg:1:f}
+
+		$fp_1 := ST_1'.{\sf top}().3rd$, $ST_1'.{\sf pop}()$, $fp_2 := ST_2'.{\sf top}().3rd$, $ch_1 := ST_2'.{\sf top}().4th$, $ST_2'.{\sf pop}()$
+
+		$\hat{fp_1} = fp2 - fp1 \cdot \delta^{lcp[i]} \! \mod \! P$ \label{alg:1:j}
+
+	 	$fp_1 := ST_1'.{\sf top}().3rd$, $fp_3 := ST_2'.{\sf top}().3rd$, $ch_2 := ST_3'.{\sf top}().4th$, $ST_3'.{\sf pop}()$
+
+		$\hat{fp_2} = fp3 - fp1 \cdot \delta^{lcp[i]} \! \mod \! P$	\label{alg:1:k}
+
+		\If{$\hat{fp_1} \ne \hat{fp_2}$ {\sf or} $ch_1 \le ch_2$}{
+
+			\Return false \hspace{5cm} // condition (2) or (3) is violated
+		}	
+	} \label{alg:1:g}
+
+	\Return true
 
@@
 
-	We design Algorithm~\ref{alg:1} to check the conditions in Corollary~\ref{corollary:1}.
-This algorithm mainly consists of three steps and each step is explained detailedly in the following paragraphs.
-
-	\vspace{1ex} \noindent {\bf Step 1.} The first step can be divided into three substeps:
-
-	\begin{enumerate}
-
-		\item [(1a)]
-		Scan $sa$ and $lcp$ rightward with $i$ increasing from $1$ to $n - 1$.
-For each scanned $\langle sa[i], lcp[i] \rangle$, create an AITEM with $idx = i, pos = sa[i], lv = lcp[i]$.
-Sort the items by $pos$ in ascending order.
-
-		\item [(1b)]
-		Scan $x$ rightward with $p$ increasing from $0$ to $n - 1$.
-For each scanned $x[p]$, compute ${\sf fp}(0, p)$ and update all the AITEMs with $pos = p + 1$ by setting $fp = {\sf fp}(0, p)$ and $pos = pos + lv$.
-Sort the items by $pos$ in ascending order.
-
-		\item [(1c)]
-		Scan $x$ rightward with $p$ increasing from $0$ to $n - 1$.
-For each scanned $x[p]$, compute ${\sf fp}(0, p)$ and update all the AITEMs with $pos = p + 1$ by setting $fp = {\sf fp}(0, p) - fp \cdot {\delta}^{lv} \, mod \, L $ and $ch = x[p + 1]$.
-Sort the items by $idx$ in ascending order.
-
-	\end{enumerate}
-
-	An auxiliary data structure called AITEM is introduced to facilitate the computation of fingerprints, where each AITEM is a 5-tuple $\langle idx, pos, lv, ch, fp\rangle$ for a suffix.
-To enable fast calculation of ${\sf fp}(sa[i] - 1)/{\sf fp}(sa[i] + lcp[i] - 1)$ for all $i \in [1, n)$, step 2 first sorts the AITEMs by $pos$ and then sequentially retrieves ${\sf fp}(0, pos)$ for each item by iteratively computing $\{{\sf fp}(0, 0), {\sf fp}(0, 1), \dots, {\sf fp}(0, n - 1) \}$ according to Formula~\ref{formula:1}.
-Given that ${\sf fp}(sa[i] - 1)$ and ${\sf fp}(sa[i] + lcp[i] - 1)$ are already known, ${\sf fp}(sa[i], sa[i] + lcp[i] - 1)$ is obtained according to Formula~\ref{formula:2}.
-
-	Notice that all the AITEMs are sorted by the starting positions of the corresponding suffixes in substep (1a).
-Thus, we check condition (1) of Corollary~\ref{corollary:1} during the time when sequentially accessing the items in substep (1b).
-
-	\vspace{1ex} \noindent {\bf Step 2.} This step computes ${\sf fp}(sa[i], sa[i] + lcp[i + 1] - 1)$ for $i \in [0, n - 1)$ using the following three substeps:
-
-	\begin{enumerate}
-
-		\item [(2a)]
-		Scan $sa$ and $lcp$ rightward with $i$ increasing from $0$ to $n - 2$.
-For each scanned $\langle sa[i], lcp[i + 1] \rangle$, create an AITEM with $idx = i, pos = sa[i], lv = lcp[i + 1]$.
-Sort the items by $pos$ in ascending order.
-
-		\item [(2b)]
-		Reuse step (1b) to update and sort AITEMs.
-
-		\item [(2c)]
-		Reuse step (1c) to update and sort AITEMs.
-
-	\end{enumerate}
-
-	The major difference between the first two steps lies in that, the field $lv$ of the AITEMs for ${\sf suf}(sa[i])$ are respectively set as $lcp[i]$ and $lcp[i + 1]$ in substeps (1a) and (2a).
-
-	\vspace{1ex} \noindent {\bf Step 3.} Let $arrA$ and $arrB$ denote the arrays of AITEMs produced by steps 1 and 2, respectively.
-Scan $arrA$ and $arrB$ rightward with $i$ increasing from $0$ to $n - 2$.
-For each pair $\langle arrA[i], arrB[i]\rangle$, check if $arrA[i].fp = arrB[i].fp$ and $arrA[i].ch > arrB[i].ch$ to ensure the correctness of conditions (2)-(3) in Corollary~\ref{corollary:1}.
-
-	\subsection{Substring Fingerprint} \label{sec:method1:fingerprint}
-
-	Algorithm~\ref{alg:1} computes ${\sf fp}(i, j)$ from ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ according to Formula~\ref{formula:2}.
-Let $e$ denote $j - i + 1$, then the coefficient $(\delta^{e} \mod L)$ must be calculated quickly or it will become a performance bottleneck.
-One approach first decomposes $e$ into $k_1 \cdot m + k_2$ and then computes $\delta^{e}$ by multiplying $\delta^{k_1 \cdot m}$ and $\delta^{k_2}$, where $k_1, k_2$ are integers and $k_1 \in [0, \lceil \frac{n}{m} \rceil], k_2 \in [0, m)$.
-An alternative first decomposes $e$ into $\Sigma_{i = 0}^{\lceil \log2^n \rceil}{k_i \cdot 2^i}$ and then computes $\Pi_{i = 0}^{\lceil \log2^n \rceil}{\delta}^{k_i \cdot 2^i}$ to obtain $\delta^{e}$, where $k_i \in \{0, 1\}$.
-The first approach answers in ${O}(1)$ time and consumes $\mathcal{O}(m + \lceil \frac{n}{m} \rceil )$ space to maintain two lookup tables for storing $\{{\delta}^{0}, {\delta}^{m}, \dots, {\delta}^{\lceil \frac{n}{m} \rceil m}\}$ and $\{{\delta}^{0}, {\delta}^{1},\dots,{\delta}^{m - 1} \}$, respectively, while the second approach answers in $\mathcal{O}(\lceil \log2^n \rceil)$ time and consumes $\mathcal{O}(\lceil \log2^n \rceil)$ space to store $\{{\delta}^{1}, {\delta}^{2}, \dots, {\delta}^{2^{\lceil \log2^n \rceil}} \}$.
-For a better space performance, we adopt the second approach to compute the fingerprints in our implementation for the algorithm.
+We propose Algorithm~\ref{alg:1} to perform the checking process in an I/O friendly way, which conducts external-memory sorts to avoid random accesses to external disks. 
+At the very beginning, the algorithm first scans $sa$ and $lcp$ to produce $ST_1, ST_2, ST_3$ and sorts the tuples of them by 1st component in ascending order (lines~\ref{alg:1:a}-\ref{alg:1:b}). 
+Then, it computes the fingerprints of all the prefixes according to Formulas~\ref{formula:1}-\ref{formula:2} and assign them to the sorted tuples in lines~\ref{alg:1:c}-\ref{alg:1:d} as following: when finished computing ${\sf fp}(0, i - 1)$, extract each tuple $e$ with $e.1st = i$ from $ST_1, ST_2, ST_3$  and update them with ${\sf fp}(0, i - 1)$ and $x[i]$ (if required), where the tuples are forwarded to $ST_1', ST_2', ST_3'$ after updating and sorted back to their original order (line~\ref{alg:1:e}).
+During the process, we determine whether or not the 1st components of all the tuples in $ST_1$ consistute a permutation of $\{0, 1, ..., n - 1\}$ to test the first condition of Corollary~\ref{corollary:1} (lines~\ref{alg:1:h}-\ref{alg:1:i}).
+Finally, it repeatedly retrieves the top tuples from $ST_1', ST_2', ST_3'$ and applies Formulas~\ref{formula:3} to compute the fingerprints of two substrings specified by their 1st components for ensuring the satisfaction of conditions (2)-(3).
+A point to be explained here is how to compute $\delta^{lcp[i]}$ in lines~\ref{alg:1:j} and~\ref{alg:1:k}.
+Let $e := lcp[i]$, our method first decomposes $e$ into $\Sigma_{i = 0}^{\lceil \log2^n \rceil}{k_i \cdot 2^i}$ and then computes $\Pi_{i = 0}^{\lceil \log2^n \rceil}{\delta}^{k_i \cdot 2^i}$ to obtain $\delta^{e}$, where $k_i \in \{0, 1\}$.
+Following this way, the answer can be returned in $\mathcal{O}(\lceil \log2^n \rceil)$ time using $\mathcal{O}(\lceil \log2^n \rceil)$ space for storing $\{{\delta}^{1}, {\delta}^{2}, \dots, {\delta}^{2^{\lceil \log2^n \rceil}} \}$.
 
@@
 
-	Algorithm~\ref{alg:1} performs multiple scans and sorts for fixed-size objects with integer keys.	Consider an external memory model with RAM size $M$, disk size $D$ and block size $B$, all are in words, then the time and I/O complexities for a scan are $\mathcal{O}(n)$ and $\mathcal{O}(n / B)$, respectively, while those for an integer sort are $\mathcal{O}(n\log_{M/ B}(n / B))$ and $\mathcal{O}((n / B)\log_{M / B}(n / B))$, respectively~\cite{Arge2013}.
-Besides, the algorithm reaches its peak disk use when sorting $n$ AITEMs in external memory during the second step.
-Given that each input character occupies $a$ words and each fingerprint occupies $b$ words, the space consumption for each sort is $(a + b + 3)n$ words.
+Algorithm~\ref{alg:1} performs multiple scans and sorts for arrays of $n$ fixed-size tuples using external memory.
+Consider an external memory model with RAM size $M$, disk size $D$ and block size $B$, all are in words, then the time and I/O complexities for a scan are $\mathcal{O}(n)$ and $\mathcal{O}(n / B)$, respectively, while those for a sort with an integer key are $\mathcal{O}(n\log_{M/ B}(n / B))$ and $\mathcal{O}((n / B)\log_{M / B}(n / B))$, respectively~\cite{Arge2013}.
+Besides, the algorithm reaches its peak disk use when sorting tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}.
+An optimization for reducing maximum space requirements is to compute the fingeprints indicated by $ST_1, ST_2, ST_3$ separately.
+This will lead to a small increase in total I/O volume as it needs to compute $\{{\sf fp}(0, 0), {\sf fp}(0, 1), ..., {\sf fp}(0, n - 1)\}$ two more times.
 
@@
 
+We demonstrate in this part an example for better understanding. xxx.
+
 \section{Method B} \label{sec:method2}
 
-	As we will see from the experimental study in Section~\ref{sec:experiment}, Algorithm~\ref{alg:1} designed by Method A is quite space consuming, the peak disk use is 40 bytes per input character.
-This motivates us to design a lightweight checker that uses less space.
-In this section, we propose a method for checking the suffix and LCP arrays using the induced-sorting principle.
-The experimental results show that Algorithm~\ref{alg:3} designed by this method consumes about 40\% less space than Algorithm~\ref{alg:1} on real-world data.
+As will be seen from our experimental study in Section~\ref{sec:experiment}, Algorithm~\ref{alg:1} is quite space consuming, the peak disk use is 40 bytes per input character.
+This motivates us to design a lightweight checker using less space.
+In this section, we propose a method for checking the suffix and LCP arrays based on the induced-sorting principle.
+In comparison with Algorithm~\ref{alg:1}, the algorithm designed by this method only consumes about half space on real-world data sets.
 
-	\subsection{Notations} \label{sec:algorithm2:notations}
+\subsection{Preliminaries} \label{sec:algorithm2:preliminaries}
+
+The induced sorting principle was previously employed to design algorithms on building suffix and LCP arrays in internal and external memory.
+The basic idea is to induce lexical order and LCP-values of all the suffixes from those of a subset.
 

### 2017-02-06 draft/draft.tex
2017/02/06

@@
 more and better) for constructing suffix and/or LCP arrays.
-In addition to help avoid implementation bugs, a checker is also demanded for an array constructed by a probabilistic algorithm \cite{xxx}.
+In addition to help avoid implementation bugs, a checker is also demanded for an array constructed by a probabilistic algorithm \cite{Bille2013}.
 In this case, the array is correct with a probability and hence must be verified by a checker to ensure its correctness.
@@
 
+\SetKwProg{Fn}{Function}{}{}
+
 \begin{algorithm*}
@@
 	%\SetAlgoNoLine
-
-	\KwIn{$x$, $sa$, $lcp$}
+	\Fn{{\sf CheckByFP}($x$, $sa$, $lcp$, $n$)}{
 
@@
 			\If{$ST_1.{\sf notEmpty}()$ {\sf and} $ST_1.{\sf top}().1st = i$}{~\label{alg:1:h}
-
 				$e := ST_1.{\sf top}()$, $ST_1.{\sf pop}()$, $e.3rd := fp$, $ST_1'.{\sf push}(e)$
@@
 			\Else{
-
 				\Return false \hspace{5cm} // condition (1) is violated
 			}~\label{alg:1:i}
-
 			\While{$ST_2.{\sf notEmpty}()$ {\sf and} $ST_2.{\sf top}().1st = i$}{
@@
 		\Return true
-
+	}
 \end{algorithm*}
@@
 
-As will be seen from our experimental study in Section~\ref{sec:experiment}, Algorithm~\ref{alg:1} is quite space consuming, the peak disk use is 40 bytes per input character.
-This motivates us to design a lightweight checker using less space.
-In this section, we propose a method for checking the suffix and LCP arrays based on the induced-sorting principle.
-In comparison with Algorithm~\ref{alg:1}, the algorithm designed by this method only consumes about half space on real-world data sets.
+As will be seen from our experimental study in Section~\ref{sec:experiment}, Algorithm~\ref{alg:1} is quite space consuming, its peak disk use is 40 bytes per input character.
+In this section, we describe an alterative based on the induced-sorting principle, where the algorithm designed by this method only takes half space on real-world datasets in comparison with Algorithm~\ref{alg:1}.
 
-\subsection{Preliminaries} \label{sec:algorithm2:preliminaries}
+\subsection{Preliminaries} \label{sec:method2:preliminaries}
 
-The induced sorting principle was previously employed to design algorithms on building suffix and LCP arrays in internal and external memory.
-The basic idea is to induce lexical order and LCP-values of all the suffixes from those of a subset.
+Before our presentation, we first introduce some notations for description convenience.
 
-	Assume $x[n - 1]$ is lexicographically the smallest character in $\Sigma$ and appears in $x[0, n)$ only once, we introduce the following notations and symbols for description clarity.
+{\em L-type/S-type/LMS character and suffix.} All the characters in $x$ are classified into three types, namely L-, S- and S*-type.
+Detailedly, $x[i]$ is L-type if (1) $i = n - 1$ or (2) $x[i] > x[i + 1]$ or (3) $x[i] = x[i + 1]$ and $x[i + 1]$ is L-type; otherwise, $x[i]$ is S-type.
+Further, if $x[i]$ and $x[i + 1]$ are S- and L-type respectively, then $x[i]$ is also an S*-type character.
+Moreover, the type of a suffix is the same as that of its heading character.
 
-	{\em L-type/S-type/LMS character and suffix.} All the characters in $x$ are classified into three different types, namely L-type, S-type and LMS.
-In details, $x[i]$ is S-type if (1) $i = n - 1$ or (2) $x[i] < x[i + 1]$ or (3) $x[i] = x[i+1]$ and $x[i+1]$ is S-type; otherwise, $x[i]$ is L-type.
-In particular, if $x[i - 1]$ and $x[i]$ are respectively L-type and S-type, then $x[i]$ is LMS.
-Furthermore, ${\sf suf}(i)$ is L-type, S-type or LMS if $x[i]$ is L-type, S-type or LMS, respectively.
+{\em Buckets.} Suppose $sa$ is correct, then suffixes in $sa$ are naturally partitioned into multiple buckets and those with an identical heading character are grouped into one bucket occupying a contiguous interval.
+Further, a bucket can be divided into two parts, where the left and right part contain L- and S-type suffixes, respectively.
+For short, we use ${\sf sa\_bkt}(c)$ to denote the bucket storing suffixes starting with $c$ and ${\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$ to denote its left/right sub-bucket.
+Accordingly, $lcp$ can be decomposed into multiple buckets as well, where ${\sf lcp\_bkt}(c)/{\sf lcp\_bkt_L}(c)/{\sf lcp\_bkt_S}(c)$ store the LCP-values of suffixes in ${\sf sa\_bkt}(c)/{\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$ and their left lexical neighbors.
 
-	{\em L-type/S-type/LMS substring.} Suppose $x[j]$ is LMS and no characters in $x[i + 1, j - 1]$ are LMS, then substring $x[i, j]$ is an L-type, S-type or LMS substring if $x[i]$ is L-type, S-type or LMS, respectively.
+{\em $sa^*$ and $lcp^*$.} Suppose the total number of S*-type suffixes in $x$ is $n_1$, then $sa^*[0, n_1)$ and $lcp^*[0, n_1)$ indicate their lexical order and the LCP-values, where $x[sa^*[i]]$ is the heading character of the $(i + 1)$-th smallest S*-type suffix.
 
-	{\em Suffix buckets.} Suffixes in $sa$ are naturally grouped into multiple buckets, where each bucket occupies a contiguous interval of $sa$ and contains all the suffixes with an identical heading character.
-Besides, a bucket can be further divided into two parts, where the left/right part is a subbucket containing only L-type/S-type suffixes.
-For short, we use ${\sf sa\_bkt}(c)$ to denote the bucket containing all the suffixes with a heading character $c$, and ${\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$ to denote the left/right subbucket in ${\sf sa\_bkt}(c)$.
+\subsection{Idea} \label{sec:method2:idea}
 
-	{\em LCP buckets.} Suppose ${\sf sa\_bkt}(c)$ is a suffix bucket ranging from $sa[i]$ to $sa[j]$, then $lcp[i, j]$ is the corresponding LCP bucket, denoted by ${\sf lcp\_bkt}(c)$, and it can be further divided into two subbuckets ${\sf lcp\_bkt_L}(c)$ and ${\sf lcp\_bkt_S}(c)$ according to ${\sf sa\_bkt_L}(c)$ and ${\sf sa\_bkt_S}(c)$.
+The induced sorting~(IS) principle has been successfully used to design algorithms for building suffix and LCP arrays in both internal and external memory.
+These algorithms mainly consist of a reduction phase for computing $sa^*$ and $lcp^*$ followed by an induction phase for inducing $sa$ and $lcp$ from $sa^*$ and $lcp^*$.
+In other words, suppose $sa^*$ and $lcp^*$ are already known, we can directly compute the suffix and LCP arrays by calling the inducing process of an existing IS-based construction algorithm.
+This enlightens us to use the following conditions for verification:
 
-	{\em Character repetition count.} Suppose $x[i] = x[i + 1] = \dots = x[j]$ and $x[j] \ne x[j + 1]$, then $j - i + 1$ is the number of successive repetitions for $x[i]$.
-Let ${\sf rep}(i)$ denote the value.
+\begin{Lemma} \label{lemma:2}
+Both $sa[0, n)$ and $lcp[0, n)$ are correct if and only if the conditions below are satisfied:
 
-	{\em Inverse suffix array.} The inverse suffix array $isa$ satisfies that $isa[sa[i]] = i$ for $i \in [0, n)$.
+\begin{enumerate}[(1)]
+	\item
+	$sa^*$ and $lcp^*$ are both correct.
+	\item
+	$sa = sa'$ and $lcp = lcp'$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by calling the inducing procedure of an existing IS-based construction algorithm.
+\end{enumerate}
+\end{Lemma}
 
-	{\em Reduced string.} The reduced string $x_1$ records the names of LMS suffixes, where each name represents the relative order of the corresponding suffix among all the LMS ones.
+Similar to Section~\ref{sec:method1:idea}, we draw the conclusion in Corollary~\ref{corollary:2} by using the fingerprinting techinque to check condition (1) in Lemma~\ref{lemma:2}.
 
-	{\em Position array.} The position array $pa$ records the starting positions of LMS suffixes.
+\begin{Corollary} \label{corollary:2}
+Both $sa[0, n)$ and $lcp[0, n)$ are correct with a high probability given the following conditions, for $i \in [0, n)$, $j, k \in [1, n_1)$ and $j \ne k$:
 
-	{\em Type array.} The type array $t$ records the types of characters in $x$. Let $t[i] = 0$ or $1$ if $x[i]$ is L-type or S-type, respectively.
+\begin{enumerate}[(1)]
+	\item 
+	$sa^*[j] \ne sa^*[k]$. 
+	\item
+	${\sf fp}(sa^*[j], sa^*[j] + lcp^*[j] - 1) = {\sf fp}(sa^*[k - 1], sa^*[k - 1] + lcp^*[k] - 1)$.
+	\item
+	$x[sa^*[j] + lcp^*[j]] > x[sa^*[k - 1] + lcp^*[k]]$.
+	\item 
+	$sa[i] = sa'[i]$ and $lcp[i] = lcp'[i]$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by calling the inducing procedure of an existing IS-based construction algorithm.
+\end{enumerate}
 
-	In addition, we denote the suffix and LCP arrays of LMS suffixes by $sa_{\sf LMS}$ and $lcp_{\sf LMS}$.
+\end{Corollary}
+
+\subsection{Algorithm} \label{sec:method2:algorithm}
+
+The algorithm for checking Corollary~\ref{corollary:2} 	
+The following procedure can b
+For checking the conditions in \ref{corollary:2}, we
+
+\begin{algorithm*}
+
+	\caption{The Algorithm for checking $sa^*$ and $lcp^*$.}
+
+	\label{alg:2}
+
+	%\SetAlgoNoLine
+
+	\KwIn{$x$, $sa$, $lcp$, $n$}
+
+	$ST_1$ := $[(sa[i], i) | i \in [0, n)]$ \label{alg:2:a}
+
+	sort tuples in $ST_1$ by 1st component \label{alg:2:b}
+
+	$j := 0$
+
+	\For{$i \in (n, 0]$}{
+
+		$e := ST_1.{\sf top}()$, $ST_1.{\sf pop}()$
+
+		\If{$x[i]$ is S*-type}{
+
+			$e.1st := j$, $j := j + 1$, $ST_2.{\sf push}(e)$
+		}
+	}
+
+	sort tuples in $ST_2$ by 2nd component
+
+	$i := 0, j := 0, lcp_{min} := max\_val$ \hspace{1cm} // use $lcp_{min}$ to trace the LCP-value of two successive S*-type suffixes
+
+	\While{$ST_2.{\sf NotEmpty()}$}{
+
+		$e := ST_2.{\sf top}()$, $ST_2.{\sf pop}()$
+
+		\While {true} {
+
+			$i:= i + 1$, $lcp_{min} := {\sf min}(lcp_{min}, lcp[i])$
+
+			\If {$e.2nd = i$} {
+
+				$sa^*[j] := e.1st$, $lcp^*[j] := lcp_{min}$, $j := j + 1$
+
+				\textbf{break}
+			}
+		}
+
+		$lcp_{min} := max\_val$
+	}
+
+	CheckByFP\_Modified($x, sa^*, lcp^*, n_1$)
+
+\end{algorithm*}
+
+\end{document}
 
@@
 	As a result, $lcp$ can be built and probabilistically checked in the same time using this method, for this we have Corollary~\ref{corollary:2}.
-
-	\begin{Corollary} \label{corollary:2}
-	Given that $sa$ is correct, then $lcp$ is correct with a high probability if and only if these conditions are satisfied for all $c \in \Sigma$:
-
-		(1) $lcp_{\sf LMS}$ is correct.
-
-		(2) The fingerprints of $lcp_{\sf L1}(c)$ and $lcp_{\sf L2}(c)$ are equal.
-
-		(3) The fingerprints of $lcp_{\sf S2}(c)$ and $lcp_{\sf S2}(c)$ are equal.
-
-	\end{Corollary}
 

### 2017-02-07 draft/draft.tex
2017/02/07

@@
 \usepackage{graphicx}
-\usepackage[ruled, linesnumbered, noend]{algorithm2e}
+\usepackage[ruled, linesnumbered]{algorithm2e}
 \usepackage{url}
@@
 
-By using the same fingerprinting technique, the second method first verifies a subset chosen from the input arrays and then produces a copy of the suffix and LCP arrays from the verified subset following the induced sorting principle.
+By using the same fingerprinting technique, the second method first verifies a subset chosen from the input arrays and then produces a copy of the suffix and LCP arrays from the verified subset following the induced sorting~(IS) principle.
 Given that the inducing process is correct, the input arrays are considered to be right with a high probability if they are equal to the induced copies.
@@
 
-\begin{itemize}
+\begin{enumerate}
 	\item [S1]
@@
 
-	\begin{itemize}
-		\item [(a)] 
+	\begin{enumerate}[(a)]
+		\item 
 		Retrieve $fp[u - 1]$ and $fp[u + v - 1]$ from $fp$ to compute ${\sf fp}(u, u + v - 1)$. Set $mk[u] = 1$.
 
-		\item [(b)] 
+		\item 
 		Retrieve $fp[w - 1]$ and $fp[w + v - 1]$ from $fp$ to compute ${\sf fp}(w, w + v - 1)$.
 
-		\item [(c)] 
+		\item 
 		Check if ${\sf fp}(u, u + v - 1) = {\sf fp}(w, w + v - 1)$ and $x[u + v] > x[w + v]$.
-	\end{itemize}
+	\end{enumerate}
 
@@
 
-\end{itemize}
+\end{enumerate}
 
@@
 
-As will be seen from our experimental study in Section~\ref{sec:experiment}, Algorithm~\ref{alg:1} is quite space consuming, its peak disk use is 40 bytes per input character.
-In this section, we describe an alterative based on the induced-sorting principle, where the algorithm designed by this method only takes half space on real-world datasets in comparison with Algorithm~\ref{alg:1}.
+Our experimental study in Section~\ref{sec:experiment} shows that Algorithm~\ref{alg:1} is quite space consuming, its peak disk use is 40 bytes per input character.
+In this section, we describe an alternative based on the induced-sorting principle.
+Compared with Algorithm~\ref{alg:1}, the algorithm designed by this method only takes half space on real-world datasets.
 
@@
 
-{\em L-type/S-type/LMS character and suffix.} All the characters in $x$ are classified into three types, namely L-, S- and S*-type.
+{\em Character and suffix classification.} All the characters in $x$ are classified into three types, namely L-, S- and S*-type.
 Detailedly, $x[i]$ is L-type if (1) $i = n - 1$ or (2) $x[i] > x[i + 1]$ or (3) $x[i] = x[i + 1]$ and $x[i + 1]$ is L-type; otherwise, $x[i]$ is S-type.
@@
 
-{\em Buckets.} Suppose $sa$ is correct, then suffixes in $sa$ are naturally partitioned into multiple buckets and those with an identical heading character are grouped into one bucket occupying a contiguous interval.
+{\em Suffix and LCP buckets.} Suppose $sa$ is correct, then suffixes in $sa$ are naturally partitioned into multiple buckets and those with an identical heading character are grouped into one bucket occupying a contiguous interval.
 Further, a bucket can be divided into two parts, where the left and right part contain L- and S-type suffixes, respectively.
@@
 
-{\em $sa^*$ and $lcp^*$.} Suppose the total number of S*-type suffixes in $x$ is $n_1$, then $sa^*[0, n_1)$ and $lcp^*[0, n_1)$ indicate their lexical order and the LCP-values, where $x[sa^*[i]]$ is the heading character of the $(i + 1)$-th smallest S*-type suffix.
+{\em Suffix and LCP arrays for S*-type suffixes.} Suppose the number of S*-type suffixes in $x$ is $n_1$, $sa^*[0, n_1)$ and $lcp^*[0, n_1)$ indicate the lexical order and the LCP-values of these S*-type suffixes, where $x[sa^*[i]]$ is the heading character of the $(i + 1)$-th smallest S*-type suffix.
+
+{\em Type array.} The type array $t$ records the type of $x[i]$ in $t[i]$ for $i \in [0, n)$.
 
@@
 
-The induced sorting~(IS) principle has been successfully used to design algorithms for building suffix and LCP arrays in both internal and external memory.
+The induced sorting principle has been employed to design algorithms for constructing suffix and LCP arrays in both internal and external memory.
 These algorithms mainly consist of a reduction phase for computing $sa^*$ and $lcp^*$ followed by an induction phase for inducing $sa$ and $lcp$ from $sa^*$ and $lcp^*$.
-In other words, suppose $sa^*$ and $lcp^*$ are already known, we can directly compute the suffix and LCP arrays by calling the inducing process of an existing IS-based construction algorithm.
-This enlightens us to use the following conditions for verification:
+Suppose $sa^*$ and $lcp^*$ are already known, we can directly build the suffix and LCP arrays by calling the inducing process of an existing IS-based construction algorithm.
+This enlightens us to check the following conditions for verification:
 
@@
 	\item
-	$sa = sa'$ and $lcp = lcp'$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by calling the inducing procedure of an existing IS-based construction algorithm.
+	$sa = sa'$ and $lcp = lcp'$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by calling the inducing process of an existing IS-based construction algorithm.
 \end{enumerate}
@@
 
-Similar to Section~\ref{sec:method1:idea}, we draw the conclusion in Corollary~\ref{corollary:2} by using the fingerprinting techinque to check condition (1) in Lemma~\ref{lemma:2}.
+Following the same idea described in Section~\ref{sec:method1:idea}, we come to the conclusion in Corollary~\ref{corollary:2} by using the fingerprinting technique.
 
@@
 	\item
-	${\sf fp}(sa^*[j], sa^*[j] + lcp^*[j] - 1) = {\sf fp}(sa^*[k - 1], sa^*[k - 1] + lcp^*[k] - 1)$.
+	${\sf fp}(sa^*[j], sa^*[j] + lcp^*[j] - 1) = {\sf fp}(sa^*[j - 1], sa^*[j - 1] + lcp^*[j] - 1)$.
 	\item
-	$x[sa^*[j] + lcp^*[j]] > x[sa^*[k - 1] + lcp^*[k]]$.
+	$x[sa^*[j] + lcp^*[j]] > x[sa^*[j - 1] + lcp^*[j]]$.
 	\item 
-	$sa[i] = sa'[i]$ and $lcp[i] = lcp'[i]$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by calling the inducing procedure of an existing IS-based construction algorithm.
+	$sa[i] = sa'[i]$ and $lcp[i] = lcp'[i]$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by calling the inducing process of an existing IS-based construction algorithm.
 \end{enumerate}
@@
 \subsection{Algorithm} \label{sec:method2:algorithm}
-
-The algorithm for checking Corollary~\ref{corollary:2} 	
-The following procedure can b
-For checking the conditions in \ref{corollary:2}, we
+Algorithm~\ref{alg:2} checks the conditions in Corollary~\ref{corollary:2} using external memory, the details are shown as following.
+The first task of the algorithm is to retrieve $sa^*$ and $lcp^*$ from $sa$ and $lcp$.
+For the purpose, it creates a tuple for each suffix in $sa$ and sorts them by 1st component in descending order~(lines~\ref{alg:2:a}-\ref{alg:2:b}).
+After sorting, it scans $x$ leftward to find all the S*-type suffixes according to the definition in Section~\ref{sec:method2:preliminaries}~(lines~\ref{alg:2:c}-\ref{alg:2:d}).
+For each S*-type suffix, we pick the corresponding tuple from the top of $ST_1$ and forward the tuple to $ST_2$.
+Then, the algorithm sorts $ST_2$ by 2nd component in ascending order and scans the sorted tuples sequentially to produce $sa^*$ and $rank^*$, where $rank*$ is the compact form of $sa^*$.
+Meanwhile, we compute $lcp^*$ following the fact that the LCP-value of two suffixes in ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$ ($i < j$) is the minimum value among $\{lcp[i + 1], ..., lcp[j - 1], lcp[j]\}$~(lines~\ref{alg:2:g}-\ref{alg:2:h}).
+The next task is to check the correctness of $sa^*$ and $lcp^*$.
+This is accomplished in lines~\ref{alg:2:i}-\ref{alg:2:j} by reusing Algorithm~\ref{alg:1}.
+At last, we call the inducing process of an external-memory construction algorithm to generate $sa'$ and $lcp'$~(line~\ref{alg:2:k}), and compare the output with $sa$ and $lcp$ to determine the result in lines~\ref{alg:2:l}-\ref{alg:2:m}.
 
@@
 
-	\caption{The Algorithm for checking $sa^*$ and $lcp^*$.}
+	\caption{The Algorithm for checking the conditions of Corollary~\ref{corollary:2}.}
 
@@
 	%\SetAlgoNoLine
+	\Fn{{\sf CheckByIS}($x$, $sa$, $lcp$, $n$)}{
 
-	\KwIn{$x$, $sa$, $lcp$, $n$}
-
-	$ST_1$ := $[(sa[i], i) | i \in [0, n)]$ \label{alg:2:a}
+	$ST_1$ := $[(sa[i], i, null) | i \in [0, n)]$ \label{alg:2:a}
 
@@
 
-	$j := 0$
+	$r := 0$, $pos := -1$ \label{alg:2:c}
 
@@
 
-		\If{$x[i]$ is S*-type}{
+		\If{$x[i]$ is S*-type}{ \label{alg:2:e}
 
-			$e.1st := j$, $j := j + 1$, $ST_2.{\sf push}(e)$
-		}
+			\If{$pos \ge e.1st$}{
+
+				\Return false  \hspace{1cm} // condition (1) is violated
 			}
 
-	sort tuples in $ST_2$ by 2nd component
+			$e.3rd := r$, $r := r + 1$, $ST_2.{\sf push}(e)$, $pos := e.1st$
+		}\label{alg:2:f}
+	} \label{alg:2:d}
 
-	$i := 0, j := 0, lcp_{min} := max\_val$ \hspace{1cm} // use $lcp_{min}$ to trace the LCP-value of two successive S*-type suffixes
+	sort tuples in $ST_2$ by 2nd component \label{alg:2:g}
+
+	$i := 0$, $j := 0$, $lcp_{min} := max\_val$
 
@@
 
-			$i:= i + 1$, $lcp_{min} := {\sf min}(lcp_{min}, lcp[i])$
+			$lcp_{min} := {\sf min}(lcp_{min}, lcp[i])$
 
@@
 
-				$sa^*[j] := e.1st$, $lcp^*[j] := lcp_{min}$, $j := j + 1$
+				$sa^*[j] := e.1st$, $rank^*[j] := e.3rd$, $lcp^*[j] := lcp_{min}$, $j := j + 1$, $i:= i + 1$
 
@@
 			}
+
+			$i:= i + 1$
 		}
@@
 		$lcp_{min} := max\_val$
+	} \label{alg:2:h}
+
+	\If{${\sf CheckByFP}(x, rank^*, lcp^*, lcp^*.{\sf size}()) = false$}{  \label{alg:2:i}
+
+		\Return false;  \hspace{1cm} // conditions (2) or (3) is violated
+	}\label{alg:2:j}
+
+	$(sa', lcp') := {\sf InducingProcess}(x, sa^*, lcp^*)$ \label{alg:2:k}
+
+	\For{$i \in [0, n)$}{\label{alg:2:l}
+
+		\If{$sa[i] \ne sa'[i] || lcp[i] \ne lcp'[i]$}{
+
+			\Return false	// condition (4) is violated
 		}	
+	}\label{alg:2:m}
 
-	CheckByFP\_Modified($x, sa^*, lcp^*, n_1$)
-
+	\Return true
+}
 \end{algorithm*}
 
-\end{document}
+\subsection{Optimization} \label{sec:method2:optimization}
 
-	\subsection{An Overview of Inducing LCP Array} \label{sec:method2:overview}
-
-	\begin{algorithm*}
-
-		\SetAlgoNoLine
-
-		\KwIn{$x$, $sa_1$, $lcp_1$}
-
-		\KwOut{$sa$, $lcp$}
-
-		S1. Compute $sa_{\sf LMS}$ and $lcp_{\sf LMS}$ from $sa_1$ and $lcp_1$, respectively.
-
-		S2. Insert items of $sa_{\sf LMS}$ and $lcp_{\sf LMS}$ into $sa$ and $lcp$. \label{alg:2:step:1}
-
-		S3. Induce L-type suffixes and LCP lengths.
-
-		S4. Induce S-type suffixes and LCP lengths.
-
-		\caption{The algorithm of the induction phase for an induced-sorting LACA.}
-
-		\label{alg:2}
-
-	\end{algorithm*}
-
-	An induced-sorting SACA~(e.g.,~\cite{Nong11}) mainly consists of a reduction phase followed by an induction phase.
-In brief, it first sorts and names the LMS substrings to produce the reduced string $x_1$ during the reduction phase and then determines whether there exist two equal characters in $x_1$.
-If yes, then it recursively performs the reduction phase by replacing $x$ with $x_1$; otherwise, it computes $sa_1$ from $x_1$ and performs the induction phase to induce $sa$ from $sa_1$.
-The work presented in~\cite{Fischer11} shows that an induced-sorting SACA can be modified to design an LACA for constructing the suffix and LCP arrays simultaneously, which principle is explained here for readers to understand our method.
-Its main idea is to compute the LCP value of two suffixes placed at the neighboring positions in the same subbucket according to the following properties, where ${\sf suf}(sa[j])$ and ${\sf suf}(sa[k])$ are the suffixes from which induce ${\sf suf}(sa[i - 1])$ and ${\sf suf}(sa[i])$ during the induction phase.
-
-	\begin{Property} \label{property:1}
-		If $x[sa[i]] = x[sa[i - 1]]$, $t[sa[i]] = t[sa[i - 1]]$ and $x[sa[j]] \ne x[sa[k]]$, then $lcp[i] = 1$.
-
-	\end{Property}
-
-	\begin{Property} \label{property:2}
-		If $x[sa[i]] = x[sa[i - 1]]$, $t[sa[i]] = t[sa[i - 1]]$ and $x[sa[j]] = x[sa[k]]$, then $lcp[i] = 1 + {\sf min}(lcp[j + 1], lcp[j + 2], \dots, lcp[k])$.
-
-	\end{Property}
-
-	Algorithm~\ref{alg:2} summarizes the main steps of the induction phase of the induced-sorting LACA in~\cite{Fischer11}.
-Suppose ${sa_{\sf LMS}}$ and $lcp_{\sf LMS}$ have been computed and their elements are inserted into the corresponding buckets in $sa$ and $lcp$, the last two steps of the algorithm are described below.
+Remember that, Algorithm~\ref{alg:2} produces a copy of the suffix and LCP arrays during the inducing process.
+Actually, given that $\Sigma$ is of a constant size, we can simply scan $sa/lcp$ to induce and check suffixes/LCP arrays simultaneously without using extra space.
+The idea is that when a suffix/LCP-value is induced into a suffix/LCP bucket, we directly compare it with the corresponding value in $sa/lcp$.
+If the latter is equal to the induced one, then we believe it is correct.
+The key point here is how to retrieve elements from $sa/lcp$ quickly.
+This can be accomplished by sequential I/O operations if we maintain a file pointer together with a reading buffer for each suffix/LCP sub-bucket.
+For better understanding, we show more details of the optimized inducing and checking processes below, where $c \in [0, \Sigma)$.
 
 \begin{enumerate}
-		\item [S3.] Clear ${\sf sa\_bkt_L}(c)/{\sf lcp\_bkt_L}(c)$ for $c \in \Sigma$ in $sa/lcp$.
-		\begin{enumerate}[(1)]
-			\item
-			Scan $sa$ rightward with $i$ increasing from $0$ to $n - 1$.
-For each scanned item $sa[i]$, insert $sa[i] - 1$ into the leftmost empty position of ${\sf sa\_bkt_L}(x[sa[i] - 1])$ if ${\sf t}[sa[i] - 1] = 0$.
-			\item
-			For each induced item placed in $sa[i]$: set $lcp[i] = 0$ if $x[sa[i]] \ne x[sa[i - 1]]$; otherwise, compute $lcp[i]$ following Properties~\ref{property:1}-\ref{property:2}.
+	\item [S1] 
+	Let $lp1[c]$ and $lp2[c]$ point to the leftmost element of ${\sf sa\_bkt_L}(c)$ and ${\sf lcp\_bkt_L}(c)$, respectively.
+Induce L-type suffixes and their LCP-values.
+For each induced L-type suffix $p$ with a heading character $c_0$ and its LCP-value $q$: (1) check $p = lp1[c_0]$ and $q = lp2[c_0]$; (2) let $lp1[c_0]$ and $lp2[c_0]$ point to the next element on the right.
+	\item [S2] 
+	Let $sp1[c]$ and $sp2[c]$ point to the rightmost element of ${\sf sa\_bkt_S}(c)$ and ${\sf lcp\_bkt_S}(c)$, respectively.
+Induce S-type suffixes and their LCP-values.
+For each induced S-type suffix $p$ with a heading character $c_0$ and its LCP-value $q$: (1) check $p = sp1[c_0]$ and $q = sp2[c_0]$; (2) let $sp1[c_0]$ and $sp2[c_0]$ point to the next element on the left.
 \end{enumerate}
 
-		\item [S4.] Clear ${\sf sa\_bkt_S}(c)/{\sf lcp\_bkt_S}(c)$ for $c \in \Sigma$ in $sa/lcp$.
-		\begin{enumerate}[(1)]
-			\item
-			Scan $sa$ leftward with $i$ decreasing from $n - 1$ to $0$.
-For each scanned item $sa[i]$, insert $sa[i] - 1$ into the rightmost empty position of ${\sf sa\_bkt_S}(x[sa[i] - 1])$ if ${\sf t}[sa[i] - 1] = 1$.
-			\item
-			For each induced item placed in $sa[i - 1]$: if $x[sa[i]] = x[sa[i - 1]]$ and $t[sa[i]] = t[sa[i - 1]]$, then compute $lcp[i]$ following Properties~\ref{property:1}-\ref{property:2}.
-		\end{enumerate}
+\subsection{Analysis} \label{sec:method2:analysis}
 
-	\end{enumerate}
-
-	There remain two special cases needing to be handled separately.
-When inducing L-type suffixes in S3, the LCP value of the rightmost L-type and the leftmost LMS suffixes in the same bucket, say ${\sf suf}(sa[i_1])$ and ${\sf suf}(sa[i_2])$, is equal to ${\sf min}({\sf rep}(sa[i_1]), {\sf rep}(sa[i_2]))$.
-Likewise, when inducing S-type suffixes in S4, the LCP value of the rightmost L-type and the leftmost S-type suffixes in the same bucket is computed following the same way.
-Notice that, ${\sf rep}(sa[i_1])/{\sf rep}(sa[i_2])$ is calculated by literally comparing the characters in the suffix from left to right.
-It is revealed in~\cite{Fischer11} that, a repetition interval cannot stride over two successive LMS substrings, thus all the involved comparisons can be done in overall linear running time.
-
-	\subsection{Check LCP Array} \label{sec:method2:check_lcp}
-
-	The inducing process of the LCP array in Section~\ref{sec:method2:overview} also constitutes the sufficient and neccessary conditions for a correct $lcp$ as stated below.
-
-	\begin{Lemma}
-		\label{lcp:correct}
-		Given that $sa$ is correct, $lcp$ is correct if and only if:
-		\begin{itemize}
-			\item[(1)]
-			$lcp_{\sf LMS}$ is correct.
-
-			\item[(2)]
-			$lcp[i]$ is equal to the value calculated by the inducing process in Section~\ref{sec:method2:overview}, for $i \in [0, n)$.
-
-		\end{itemize}
-	\end{Lemma}
-
-	This lemma suggests a method to check an LCP array as follows.
-	We address two cases: (1) given $lcp_{\sf LMS}$ and correct $sa$, to build and check $lcp$ simultaneously; (2) given $lcp$ and correct $sa$, to check $lcp$.
-
-	Notice that the processes for inducing and checking $lcp$ are essentially the same in terms of that both utilize condition (2) in Lemma \ref{lcp:correct}, the only difference is that the former computes $lcp[i]$ using the condition but the latter checks if the condition is held for each given $lcp[i]$.
-
-	\vspace{1ex} \noindent {\bf Case 1.} In the first case, we first check $lcp_{\sf LMS}$ by Method A, then induce and check $lcp$ from $lcp_{\sf LMS}$ simultaneously.
-The problem to be solved is that when an item is induced into a bucket, its corresponding item $lcp[i]$ to be compared is not known yet.
-	Our solution for this is to integrate the processes of inducing and checking into a single one, by ensuring the sequence of items induced into a bucket in $lcp$ in the inducing process is identical to that later seen by the scanning process that is also the checking process.
-	For each bucket, we increasingly compute the fingerprints of both sequences and check their equality during the whole process for inducing $lcp$.
-	If the two fingerprints for each bucket are equal, then the condition (2) of Lemma~\ref{lcp:correct} will be seen by the checking process with a high probability.
-	As a result, $lcp$ can be built and probabilistically checked in the same time using this method, for this we have Corollary~\ref{corollary:2}.
-
-	For each $c$, $lcp_{\sf L2}(c)/lcp_{\sf S2}(c)$ or $lcp_{\sf L1}(c)/lcp_{\sf S1}(c)$ records the sequences of items in ${\sf lcp\_bkt_L}(c)/{\sf lcp\_bkt_S}(c)$ in their order of being scanned or induced, respectively.
-We augment S3 and S4 of Algorithm~\ref{alg:2} to compute the fingerprints of these sequences as follows:
-
-	\begin{enumerate}
-
-		\item [S3'.] Initialize ${\sf fp}(lcp_{\sf L1}(c)) = 0$ and ${\sf fp}(lcp_{\sf L2}(c)) = 0$.
-
-		\begin{enumerate} [(1)]
-
-			\item For each scanned item $sa[i]$, update ${\sf fp}(lcp_{\sf L2}(c))$ by $lcp[i]$ if $x[sa[i]] = c$ and $t[sa[i]] = 0$.
-
-			\item For each induced item placed in $sa[i]$, update ${\sf fp}(lcp_{\sf L1}(c))$ by $lv$ if $x[sa[i]] = c$, where $lv$ is the calculated LCP value.
-
-		\end{enumerate}
-
-		\item [S4'.] Initialize ${\sf fp}(lcp_{\sf S1}(c)) = 0$ and ${\sf fp}(lcp_{\sf S2}(c)) = 0$.
-
-		\begin{enumerate}[(1)]
-
-			\item  For each scanned item $sa[i]$, update ${\sf fp}(lcp_{\sf S2}(c))$ by $lcp[i]$ if $x[sa[i]] = x[sa[i - 1]] = c$ and $t[sa[i]] = t[sa[i - 1]] = 1$.
-
-			\item For each induced item placed at $sa[i - 1]$, update $lcp_{\sf S1}(c)$ by $lv$ if $x[sa[i - 1]] = x[sa[i]] = c$ and $t[sa[i - 1]] = t[sa[i]] = 1$, where $lv$ is the calculated LCP value.
-
-		\end{enumerate}
-
-	\end{enumerate}
-
-	We generalize Formula~\ref{formula:1} in Section~\ref{sec:method1:idea} to iteratively compute the fingerprint of each sequence in steps S3' and S4'.
-Specifically, when a new item $e$ is appended to a sequence, its fingerprint $fp$ is updated according to the formula $fp = fp \cdot \delta + e \mod L$.
-
-	\vspace{1ex} \noindent {\bf Case 2.} In the second case, we first scan $lcp$ to compute $lcp_{\sf LMS}$ and check $lcp_{\sf LMS}$ by Method A, then induce and check the LCP array from $lcp_{\sf LMS}$ following the same idea of the first case.
-After that, we compare the given $lcp$ with the induced LCP array to ensure the correctness of the former.
-
-	\subsection{Check Suffix Array} \label{sec:method2:check_sa}
-
-	An induced-sorting SACA determines the order of two suffixes by comparing their heading characters and succeeding suffixes in $x$.
-In other words, Property~\ref{property:3} is held for any two suffixes placed in $sa[i]$ and $sa[j]$, where ${\sf suf}(sa[p])$ and ${\sf suf}(sa[q])$ are the two suffixes from which induce ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$ during the induction phase.
-
-	\begin{Property} \label{property:3}
-		If $(x[sa[i]], p) > (x[sa[j]], q)$, then $i > j$.
-
-	\end{Property}
-
-	As shown below, Property~\ref{property:3} can be used to constitute the sufficient and necessary conditions for a correct $sa$.
-
-	\begin{Lemma} \label{lemma:3}
-		$sa$ is correct if and only if:
-
-		\begin{itemize}
-			\item [(1)] $sa_{\sf LMS}$ is correct.
-
-			\item [(2)] $i > j$ if $(x[sa[i]], p) > (x[sa[j]], q)$, for $i, j \in [0, n)$.
-
-		\end{itemize}
-
-	\end{Lemma}
-
-	We use Lemma~\ref{lemma:3} to check a suffix array in two cases: (1) given $sa_{\sf LMS}$, to build and check $sa$ in the same time; (2) given $sa$, to check $sa$.
-
-	\vspace{1ex} \noindent {\bf Case 1.} In the first case, we first check $sa_{\sf LMS}$ by using Method A, and then induce and check $sa$ from $sa_{\sf LMS}$ by comparing the fingerprint of the sequence of items induced into a bucket with that of the sequence of items scanned in the bucket.
-If the two fingerprints are equal for each bucket, then the condition (2) of Lemma~\ref{lemma:3} are satisfied with a high probability.
-Following the discussion, we have Corollary~\ref{corollary:3}.
-
-	\begin{Corollary} \label{corollary:3}
-		$sa$ is correct with a high probability if and only if these conditions are satisfied for all $c \in \Sigma$:
-
-		(1) $sa_{\sf LMS}$ is correct.
-
-		(2) The fingerprints of $sa_{\sf L1}(c)$ and $sa_{\sf L2}(c)$ are equal.
-
-		(3) The fingerprints of $sa_{\sf S2}(c)$ and $sa_{\sf S2}(c)$ are equal.
-
-	\end{Corollary}
-
-	For each $c$, $sa_{\sf L2}(c)/sa_{\sf S2}(c)$ or $sa_{\sf L1}(c)/sa_{S1}(c)$ records the sequence of items in ${\sf sa\_bkt_L}/{\sf sa\_bkt_S}$ in their order of being scanned or induced, respectively.
-Similar to S3' and S4', we compute the fingerprints of these sequences by augmenting the last two steps of Algorithm~\ref{alg:2} as follows:
-
-	\begin{enumerate}
-
-		\item [S3''.] Initialize ${\sf fp}(sa_{\sf L1}(c)) = 0$ and ${\sf fp}(sa_{\sf L2}(c)) = 0$.
-
-		\begin{enumerate} [(1)]
-
-			\item For each scanned item $sa[i]$, update ${\sf fp}(sa_{\sf L2}(c))$ by $sa[i]$ if $x[sa[i]] = c$ and $t[sa[i]] = 0$.
-
-			\item For each induced item, update ${\sf fp}(sa_{\sf L1}(c))$ by $sa[j] - 1$ if $x[sa[j] - 1] = c$, where $sa[j]$ is the starting position of the suffix from which induces the item.
-
-		\end{enumerate}
-
-		\item [S4''.] Initialize ${\sf fp}(sa_{\sf S1}(c)) = 0$ and ${\sf fp}(sa_{\sf S2}(c)) = 0$.
-
-		\begin{enumerate}[(1)]
-
-			\item For each scanned item $sa[i]$, update ${\sf fp}(sa_{\sf S2}(c))$ by $sa[i]$ if $x[sa[i]] = c$ and $t[sa[i]] = 1$.
-
-			\item For each induced item, update ${\sf fp}(sa_{\sf S1}(c))$ by $sa[j] - 1$ if $x[sa[j] - 1] = c$, where $sa[j]$ is the starting position of the suffix from which induces the item.
-
-		\end{enumerate}
-
-	\end{enumerate}
-
-		\vspace{1ex} \noindent {\bf Case 2.} In the second case, we first scan $sa$ to compute $sa_{\sf LMS}$ and check $sa_{\sf LMS}$ by using Method A, then induce and check the suffix array from $sa_{\sf LMS}$ following the same idea of the first case.
-Afterward, we compare the given $sa$ with the induced suffix array to ensure the correctness of the former.
-
-	\subsection{Algorithms} \label{sec:method2:algorithm}
-
-	We propose two external-memory algorithms based on the method described in Sections~\ref{sec:method2:check_lcp}-\ref{sec:method2:check_sa}.
-The first algorithm can build and check the suffix and LCP arrays simultaneously, while the second algorithm, called Algorithm~\ref{alg:3}, can check the two arrays after their construction.
-
-	\subsubsection{Build and Check Simultaneously} \label{sec:method2:algorithm:sim}
-
-	We adapt Algorithm~\ref{alg:2} to check the conditions of Corollaries~\ref{corollary:2}-\ref{corollary:3} when building the suffix and LCP arrays by an induced-sorting LACA.
-
-	There are three places needed to be revised in Algorithm~\ref{alg:2}.
-The first place is to check $sa_{\sf LMS}$ and $lcp_{\sf LMS}$ using Algorithm~\ref{alg:1} after computing them in S1.
-The second place is to compute the fingerprints by adapting S3 and S4 of Algorithm~\ref{alg:2} as below:
-
-	\begin{enumerate} [(1)]
-
-		\item
-		Augment S3 with S3' and S3'' to compute the fingerprints of ${\sf fp}(lcp_{\sf L1}(c)/lcp_{\sf L2}(c))$ and ${\sf fp}(sa_{\sf L1}(c)/sa_{\sf L2}(c))$ for all $c \in \Sigma$.
-
-		\item
-		Augment S4 with S4' and S4'' to compute the fingerprints of ${\sf fp}(lcp_{\sf S1}(c)/lcp_{\sf S2}(c))$ and ${\sf fp}(sa_{\sf S1}(c)/sa_{\sf S2}(c))$ for all $c \in \Sigma$.
-
-	\end{enumerate}
-
-	The third place is to compare the fingerprints after the inducing process.
-
-	This algorithm can be applied to the external memory model if we extend Algorithm~\ref{alg:2} for inducing the suffix and LCP arrays using external memory by the method described in~\cite{Bingmann12}.
-
-	\subsubsection{Build and Check Sequentially}
-
-		Algorithm~\ref{alg:3} mainly consists of three steps.
-In the first step, it computes $sa_{\sf LMS}$ and $lcp_{\sf LMS}$ from $sa$ and $lcp$, and ensures their correctness by using Algorithm~\ref{alg:1}.
-In the second step, it checks the conditions of Corollaries~\ref{corollary:2}-\ref{corollary:3} to verify the suffix and LCP arrays induced from $sa_{\sf LMS}$ and $lcp_{\sf LMS}$.
-In the last step, it checks the given $sa$ and $lcp$ by comparing them with the induced suffix and LCP arrays.
-In what follows, we explain the algorithm step by step in more details for better understanding.
-
-	\begin{algorithm}
-
-		\SetAlgoNoLine
-
-		\KwIn{$x$, $sa$, $lcp$}
-
-		Step 1. Compute and check $sa_{\sf LMS}$ and $lcp_{\sf LMS}$.
-
-		Step 2. Induce and check the suffix and LCP arrays from $sa_{\sf LMS}$ and $lcp_{\sf LMS}$.
-
-		Step 3. Check $sa$ and $lcp$ by comparing them with the induced suffix and LCP arrays.
-
-		\caption{The algorithm that performs verification after construction using Method B.}
-
-		\label{alg:3}
-
-	\end{algorithm}
-
-	\vspace{1ex} \noindent {\bf Step 1.} This step computes $sa_{\sf LMS}$ and $lcp_{\sf LMS}$ from $sa$ and $lcp$ by the following three substeps:
-
-	\begin{enumerate}
-		\item [(1a)]
-		Sort $i$ by $sa[i]$ for $i \in [0, n)$ to produce $isa$.
-
-		\item [(1b)]
-		Sort $\langle x[i - 1], t[i - 1], x[i], t[i], {\sf rep}(i) \rangle$ by $isa[i]$ for $i \in [0, n)$ to produce an array $arr$, where $arr[i]$ records $\langle x[sa[i] - 1], t[sa[i] - 1], x[sa[i]], t[sa[i]], {\sf rep}(sa[i]) \rangle$.
-
-		\item [(1c)]
-		Initialize $v=n$.
-Scan $sa$, $lcp$ and $arr$ rightward with $i$ increasing from $0$ to $n - 1$.
-For each scanned $\langle sa[i], lcp[i], arr[i] \rangle$: (1) if $lcp[i] < v$, then set $v = lcp[i]$; (2) if $t[sa[i] - 1] = 0$ and $t[sa[i]] = 1$, then append $sa[i]$ and $v$ to $sa_{\sf LMS}$ and $lcp_{\sf LMS}$, respectively, and reset $v = n$.
-
-	\end{enumerate}
-
-	As can be seen, step 1 determines whether or not a suffix is LMS by checking the types of its preceding and heading characters.
-To avoid random accesses to $x$ residing on disks, it first sorts the preceding and heading characters of suffixes by $isa$ to produce $arr$, and then scans $sa$, $lcp$ and $arr$ to identify all the LMS suffixes.
-During the process, for any two successively found LMS suffixes, say ${\sf suf}(sa[i_1])$ and ${\sf suf}(sa[i_2])$, the LCP length of them is calculated by tracing the minimum of $lcp[i_1 + 1, i_2]$.
-After that, $sa_{\sf LMS}$ and $lcp_{\sf LMS}$ are checked by using Algorithm~\ref{alg:1}.
-
-	Notice that, when inducing in external memory, the heading characters of successively induced suffixes should be loaded into RAM by sequential I/O operations.
-For the purpose, the preceding characters calculated by substeps (1a)-(1b) are stored in external memory to facilitate the inducing process in step 2.
-Specifically, when scanning $arr$ in substep (1c), we distribute the elements of the array into $arr_{\sf L}, arr_{\sf S}$ and $arr_{\sf LMS}$ as following: append $arr[i]$ to $arr_{\sf L}$ or $arr_{\sf S}$ if $t[sa[i]] = 0$ or $1$, respectively, and append $arr[i]$ to $arr_{\sf LMS}$ if $t[sa[i] - 1] = 0$ and $t[sa[i]] = 1$.
-
-	\vspace{1ex} \noindent {\bf Step 2.} This step employs two priority queues $PQ_{\sf L}$ and $PQ_{\sf S}$ to emulate the RAM-based inducing process in external memory, where each element of both priority queues is a 6-tuple $\langle ch, ty, ra, pos, lv, rp \rangle$ defined as below:
-
-	\begin{itemize}
-
-		\item $pos$: starting position of ${\sf suf}(pos)$.
-
-		\item $ch$: heading character of ${\sf suf}(pos)$.
-
-		\item $ty$: type of ${\sf suf}(pos)$.
-
-		\item $ra$: rank of ${\sf suf}(pos)$.
-
-		\item $lv$: LCP length of ${\sf suf}(pos)$ and its left or right neighbor in the induced SA.
-
-		\item $rp$: ${\sf rep}(pos)$.	
-	\end{itemize}
-
-	At the very beginning, step 2 first scans $sa_{\sf LMS}$ and $lcp_{\sf LMS}$ to put the sorted LMS suffixes along with the corresponding LCP values into $PQ_{\sf L}$ with the sorting key $\langle ch, ty, ra\rangle$, then it pops the elements of $PQ_{\sf L}$ in ascending order to induce L-type suffixes.
-Specifically, for each visited element $e$, it retrieves the preceding character of ${\sf suf}(e.pos)$ from the leftmost unvisited element in $arr_{\sf L}$ or $arr_{\sf LMS}$ if $e.ty = 0$ or $1$, respectively.
-If the retrieved preceding character is L-type, then it computes the LCP length of ${\sf suf}(pos - 1)$ and its left neighbor in the induced SA, and puts the induced suffix along with the calculated LCP value into $PQ_{\sf L}$.
-Meanwhile, it puts ${\sf suf}(e.pos)$ into $PQ_{\sf S}$ if $e.ty = 0$.
-
-	When $PQ_{\sf L}$ is empty, all the L-type suffixes are sorted in $PQ_{\sf S}$ with the sorting key $\langle ch, ty, ra\rangle$.
-Step 2 continues to pop the elements of $PQ_{\sf S}$ in descending order to induce S-type suffixes and their LCP values.
-For each visited element $e$, it retrieves the preceding character of ${\sf suf}(e.pos)$ from the rightmost unvisited element in $arr_{\sf L}$ or $arr_{\sf S}$ if $e.ty = 0$ or $1$, respectively.
-If the preceding character is S-type, then it calculates the LCP length of ${\sf suf}(e.pos - 1)$ and its right neighbor in the induced SA, and puts the induced suffix along with the calculated LCP value into $PQ_{\sf S}$.
-Meanwhile, it outputs $e.pos$ and $e.lv$ to build the suffix and LCP arrays.
-
-	When $PQ_{\sf S}$ is empty, the construction of the suffix and LCP arrays is completed and the calculation of the required fingerprints is also finished.
-Then, step 2 compares the fingerprints to check the correctness of the induced suffix and LCP arrays.
-
-	Notice that, we reuse a technique proposed in~\cite{Fischer11} to compute the LCP value of two neighboring suffixes in a subbucket according to Properties~\ref{property:1}-\ref{property:2}.
-Specifically, we record the heading characters and the LCP value of two suffixes from which most recently induce a suffix into ${\sf sa\_bkt}(c)$, for all $c \in \Sigma$.
-Given that $\Sigma$ is of a constant size, it takes overall $\mathcal{O}(n)$ time to keep the data structure up-to-date.
-Besides, for the rightmost L-type and the leftmost S-type/LMS suffixes in a bucket, we compare the repetition counts of their heading characters to compute the LCP length of them.
-
-	\vspace{1ex} \noindent {\bf Step 3.} This step performs a scan on $sa$ and $lcp$ to compare the elements of them with those of the induced suffix and LCP arrays.
-
-	\subsection{Analysis}
-
-	Clearly, Algorithm~\ref{alg:3} can be implemented within sorting complexity in external memory.
-The space bottleneck of the algorithm occurs when inducing suffixes  during the second step.
-Suppose we respectively use $a$ and $b$ words to represent an input character and its type, then it takes at most $(3a + 3b)n$ words for storing $arr_{\sf L}, arr_{\sf S}$ and $arr_{\sf LMS}$ and $(4 + a + b)n$ words for sorting elements in $PQ_{\sf L}/PQ_{\sf S}$.
+Both Algorithm~\ref{alg:2} can be implemented within sorting complexity.
+As will be shown in the next section, the space bottleneck of the algorithm occurs when inducing and checking the suffix and LCP arrays in lines~\ref{alg:2:i}-\ref{alg:2:m} due to the space demand for storing BWT.
+Besides, our implementation of the optimized version has a similar I/O performance to that of Algorithm~\ref{alg:1}, while the former takes only half space in comparison with the latter.
 

### 2017-02-09 draft/draft.tex
2017/02/09

@@
 As a common practice, a suffix or LCP array checker is also provided for verifying the correctness of a constructed array.
-For example, such a checker is provided in the software packages eSAIS \cite{xxx} (DC3, pScan and etc?
-more and better) for constructing suffix and/or LCP arrays.
-In addition to help avoid implementation bugs, a checker is also demanded for an array constructed by a probabilistic algorithm \cite{Bille2013}.
+For example, such a checker is provided in the software packages (like SA-IS~\cite{Nong11}, eSAIS~\cite{Bingmann12} and DC3~\cite{Dementiev08}) for constructing suffix and/or LCP arrays.
+In addition to help avoid implementation bugs, a checker is also demanded for an array constructed by a probabilistic algorithm~\cite{Bille2013}.
 In this case, the array is correct with a probability and hence must be verified by a checker to ensure its correctness.
@@
 		Check if ${\sf fp}(u, u + v - 1) = {\sf fp}(w, w + v - 1)$ and $x[u + v] > x[w + v]$.
+
+		\item 
+		Set $mk[sa[0]] = 1$. 
 	\end{enumerate}
 
-	\item [S3] Set $mk[sa[0]] = 1$. Check if $mk[i] = 1$ for all $i \in [0, n)$.
+	\item [S3] Check if $mk[i] = 1$ for all $i \in [0, n)$.
 
@@
 
-Two zero-initialized arrays $fp$ and $mk$ are employed to faciliate the checking process, where the former is for storing the fingerprints of all the prefixes in $x$ and the latter is for checking the existence of $\{0, 1, ..., n - 1\}$ in $sa$.
+Two zero-initialized arrays $fp$ and $mk$ are used to faciliate the checking process, where the former is for storing the fingerprints of all the prefixes in $x$ and the latter is for checking the existence of $\{0, 1, ..., n - 1\}$ in $sa$.
+Assume $L = 197$ and $\delta = 101$, we give a small example of S1-S2 in Fig.~\ref{fig:example} for better understanding.
 Clearly, this algorithm consumes $\mathcal{O}(n)$ time and space when running in internal memory.
 However, if the input can not be wholly accommodated into RAM, it may suffer from a performance degradation due to frequent random I/O operations for reading elements of $x$, $sa$ and $lcp$ from external memory during the execution of S2.
+
+\begin{figure*}
+	\centering
+	\label{fig:example}
+	\includegraphics[width = 0.8\textwidth]{example}
+	\caption{An Example for Checking the Suffix and LCP Arrays Using the Karp-Rabin Fingerprinting Functions}	
+\end{figure*}
 
@@
 
-\subsection{Analysis} \label{sec:method1:analysis}
+\subsection{Discussion} \label{sec:method1:discussion}
 
@@
 This will lead to a small increase in total I/O volume as it needs to compute $\{{\sf fp}(0, 0), {\sf fp}(0, 1), ..., {\sf fp}(0, n - 1)\}$ two more times.
-
-\subsection{Example} \label{sec:method1:example}
-
-We demonstrate in this part an example for better understanding. xxx.
 
@@
 
-		\If{$sa[i] \ne sa'[i] || lcp[i] \ne lcp'[i]$}{
+		\If{$sa[i] \ne sa'[i] \parallel lcp[i] \ne lcp'[i]$}{
 
@@
 
-Remember that, Algorithm~\ref{alg:2} produces a copy of the suffix and LCP arrays during the inducing process.
-Actually, given that $\Sigma$ is of a constant size, we can simply scan $sa/lcp$ to induce and check suffixes/LCP arrays simultaneously without using extra space.
-The idea is that when a suffix/LCP-value is induced into a suffix/LCP bucket, we directly compare it with the corresponding value in $sa/lcp$.
-If the latter is equal to the induced one, then we believe it is correct.
+Algorithm~\ref{alg:2} produces a copy of the suffix and LCP arrays during the inducing process.
+Actually, given that $\Sigma$ is of a constant size, we can simply scan $sa/lcp$ to induce and check the suffixes/LCP arrays simultaneously without using extra space.
+The idea is that when a suffix/LCP-value $v_1$ is induced into a suffix/LCP bucket, we directly compare it with the corresponding item $v_2$ in $sa/lcp$.
+If $v_1 = v_2$, then $v_2$ is correct and can be used to induce subsequent suffixes/LCP-values.
 The key point here is how to retrieve elements from $sa/lcp$ quickly.
-This can be accomplished by sequential I/O operations if we maintain a file pointer together with a reading buffer for each suffix/LCP sub-bucket.
-For better understanding, we show more details of the optimized inducing and checking processes below, where $c \in [0, \Sigma)$.
+This can be accomplished by conducting sequential I/O operations if we maintain a read pointer coupled with a buffer for each suffix/LCP sub-bucket.
+More details of the optimized inducing and checking processes as below, where $c \in [0, \Sigma)$ and $lp_1, lp_2, sp_1, sp_2$ are read pointer arrays for retrieving items from $sa/lcp$ buckets residing on disks.
 
@@
 	\item [S1] 
-	Let $lp1[c]$ and $lp2[c]$ point to the leftmost element of ${\sf sa\_bkt_L}(c)$ and ${\sf lcp\_bkt_L}(c)$, respectively.
-Induce L-type suffixes and their LCP-values.
-For each induced L-type suffix $p$ with a heading character $c_0$ and its LCP-value $q$: (1) check $p = lp1[c_0]$ and $q = lp2[c_0]$; (2) let $lp1[c_0]$ and $lp2[c_0]$ point to the next element on the right.
+	Let $lp_1[c]$ and $lp_2[c]$ point to the leftmost element of ${\sf sa\_bkt_L}(c)$ and ${\sf lcp\_bkt_L}(c)$ in $sa$ and $lcp$, respectively. 
 	\item [S2]
-	Let $sp1[c]$ and $sp2[c]$ point to the rightmost element of ${\sf sa\_bkt_S}(c)$ and ${\sf lcp\_bkt_S}(c)$, respectively.
-Induce S-type suffixes and their LCP-values.
-For each induced S-type suffix $p$ with a heading character $c_0$ and its LCP-value $q$: (1) check $p = sp1[c_0]$ and $q = sp2[c_0]$; (2) let $sp1[c_0]$ and $sp2[c_0]$ point to the next element on the left.
+	Induce L-type suffixes and their LCP-values following the induced sorting principle.
+Meanwhile, for each induced L-type suffix $p$ with a heading character $c_0$ and its LCP-value $q$: (1) check $p = lp_1[c_0]$ and $q = lp_2[c_0]$; (2) let $lp_1[c_0]$ and $lp_2[c_0]$ point to the right neighbor in the same $sa$ and $lcp$ sub-buckets.
+	\item [S3] 
+	Let $sp_1[c]$ and $sp_2[c]$ point to the rightmost element of ${\sf sa\_bkt_S}(c)$ and ${\sf lcp\_bkt_S}(c)$ in $sa$ and $lcp$, respectively. 
+	\item [S4]
+	Induce S-type suffixes and their LCP-values following the induced sorting principle.
+Meanwhile, for each induced S-type suffix $p$ with a heading character $c_0$ and its LCP-value $q$: (1) check $p = sp_1[c_0]$ and $q = sp_2[c_0]$; (2) let $sp_1[c_0]$ and $sp_2[c_0]$ point to the left neighbor in the same $sa$ and $lcp$ sub-buckets.
 \end{enumerate}
 
-\subsection{Analysis} \label{sec:method2:analysis}
+\subsection{Discussion} \label{sec:method2:discussion}
 
-Both Algorithm~\ref{alg:2} can be implemented within sorting complexity.
-As will be shown in the next section, the space bottleneck of the algorithm occurs when inducing and checking the suffix and LCP arrays in lines~\ref{alg:2:i}-\ref{alg:2:m} due to the space demand for storing BWT.
-Besides, our implementation of the optimized version has a similar I/O performance to that of Algorithm~\ref{alg:1}, while the former takes only half space in comparison with the latter.
+Both Algorithm~\ref{alg:2} and its optimized version can be implemented within sorting complexity.
+The space bottleneck occurs when inducing and checking the suffix and LCP arrays.
+This is because the existing IS-based construction algorithms store BWT to help retrieving preceding characters during the inducing process.
+We refer the interested readers to~\cite{Karkkainen2013} for more details.
 
@@
 
-	We implement the prototypes of Algorithms~\ref{alg:1} and~\ref{alg:3} in external memory.
-Our programs for the algorithms are compiled by gcc/g++ 4.8.4 with -O3 options under ubuntu 14.04 64-bit operating system running on a desktop computer, which is equipped with an Intel Xeon E3-1220 V2 CPU, 4GiB RAM and 500GiB HD.
-The following metrics normalized by the input's size are investigated for performance evaluation on the real-world datasets listed in Table~\ref{tbl:1}:
+\subsection{Setup} \label{sec:experiment:setup}
+
+The experimental platform is a work station equipped with an Intel Xeon E3-1220 V2 CPU, 4GiB RAM and 500GiB HD.
+To achieve high I/O efficiency, we implement the algorithms proposed in the previous sections using the external-memory containers provided by the STXXL library~\cite{Dementiev2007}.
+All the programs are compiled by gcc/g++ 4.8.4 with -O3 options under ubuntu 14.04 64-bit operating system.
+For performance analysis, we investigate on real-world datasets in Table~\ref{tbl:1} the following three metrics normalized by the size of input string:
 
@@
 
-		\item Running time: the running time in microseconds.
+	\item RT: running time, in nanoseconds. Measured using the Linux 'time' command.
 
-		\item Peak disk use: the peak use of external memory in bytes.
+	\item PDU: peak disk use of external memory, in bytes.
 
-		\item I/O volume: the number of bytes read from and written to external memory.
+	\item IOV: amount of data read from and write to external memory, in bytes.
 
@@
 
-	\subsection{Results}
-	Some implementation choices in our programs are as follows.
-First, we use the second approach in Section~\ref{sec:method1:fingerprint} to facilitate the computation of fingerprints in Algorithm~\ref{alg:1}.
-Second, we employ the external-memory containers~(vector, sorter and priority queue) provided by the STXXL library~\cite{Dementiev2007} to perform scans and sorts on disks.
-Finally, we use a 32-bit integer to represent each fingerprint and a 40-bit integer to represent each element in the suffix/LCP arrays.
+\subsection{Result} \label{sec:experiments:result}
 
-	For description convenience, we denote the programs for Algorithms~\ref{alg:1} and~\ref{alg:3} by ProgA and ProgB, respectively.
-As shown in Figure~\ref{fig:performance_analysis}, ProgA runs faster than ProgB on "enwiki", "uniprot" and "proteins" by about 20 percent.
+Fig.~\ref{fig:cmp1} demonstrates the performance comparison between the programs for Algorithms~\ref{alg:1} and~\ref{alg:2}. As depicted,
+
 The speed gap between them is mainly due to the difference in their I/O efficiencies.
@@
 
-	\subsection{Discussions}
+	\subsection{Discussion}
 
@@
 
-	We present two probabilistic methods for checking the suffix and LCP arrays in external memory using the Karp-Rabin fingerprinting function.
-Both methods can be employed to verify the suffix and LCP arrays after their construction, while the second method can be also integrated into an induced-sorting LACA to perform construction and verification in the same time.
-
-	We also design the algorithms for these two methods and implement the programs for performance evaluation. An experimental study is conducted to evaluate the time, space and I/O efficiencies.
-	The results indicate that the program for the first method outperforms that for the second method in the running time and I/O volume by about 20 percent, while the peak disk use of the latter is about 26/40 = 0.65 as that of the former.
-There are still quite some opportunities to improve our algorithms and programs for better performance, for this our work has been undergoing.
+In this article, we propose two methods for probablistically checking the give suffix and LCP arrays in external memory using a fingerprinting techinque.
+As observed from the experimental results, our program for the algorithm designed on Method A outperforms that for the algorithm designed on Method B in both running time and I/O volume by about 20 percent, while the peak disk use of the latter is about 26/40=0.65 as that of the former and can be further reduced to around 21n without a sacrifice in time and I/O performance.
 

### 2017-02-13 draft/draft.tex
2017/02/13

@@
 
-	For full-text indexing of massive data, the suffix and LCP (longest common prefix) arrays have been recognized as the fundamental data structures and should be verified to ensure their correctness after construction.
-We propose in this paper two methods to probablisitically check the suffix and LCP arrays in external memory by using a Karp-Rabin fingerprinting function, in terms of that the checking result is wrong with only a negligible probability.
-The first method checks the lexical order and the LCP-value of two neighboring suffixes in the given suffix array by computing and comparing the fingerprints of their LCPs.
-The second method first applies the fingerprinting technique to check a subset of the given suffix and LCP arrays, then it produces the whole arrays from the verified parts following the induced-sorting principle and compares the induced and input copies with each other for verification.
+For full-text indexing of massive data, the suffix and LCP (longest common prefix) arrays have been recognized as the fundamental data structures, and there are at least two needs in practice for checking their correctness, i.e.
+program debugging and verifying the arrays constructed by probabilistic algorithms.
+We propose in this paper two methods to check the suffix and LCP arrays in external memory by using a Karp-Rabin fingerprinting technique, where the checking result is wrong only with a negligible error probability.
+Our first method checks the lexicographical order and the LCP-value of two neighboring suffixes in the given suffix array by computing and comparing the fingerprints of their LCPs.
+This approach is also employed in the second method to verify a subset of the given suffix and LCP arrays, from which then a copy of the final suffix and LCP arrays is produced following the induced sorting principle and compared with the given one for verification.
 
@@
 \begin{IEEEkeywords}
-	Suffix and LCP arrays, verification, Karp-Rabin fingerprinting function.
+	Suffix and LCP arrays verification, Karp-Rabin fingerprinting technique, external memory.
 \end{IEEEkeywords}}
@@
 Suffix and longest common prefix (LCP) arrays play an important role in various string processing tasks, such as data compression, pattern matching and genome assembly.
-In dozens of applications, these two data structures are combined to constitute a powerful full-text index for massive data, called enhanced suffix array~\cite{Abouelhodaa2004}, which is more space efficient than suffix tree and applicable to emulating any searching functionalities provided by the latter in the same time complexity.
-During the past decades, much effort has been put on the development of designing efficient suffix array construction algorithms~(SACAs).
-Specifically, the first internal-memory algorithm for building SA was introduced in~\cite{Manber1993}.
-From then on, a plethora of SACAs have been proposed on different computation models, e.g., internal memory~\cite{Karkkainen2003, Ko2003, Kim2003, Nong11}, external memory~\cite{Dementiev2008, Ferragina2012, Manzini2004, Bingmann12, Karkkainen2014, Nong14, Nong15} and shared memory models~\cite{Osipov2012, Deo2013, Wang2015, Karkkainen2015}.
+Particularly, these two data structures constitute the core part of a powerful full-text index, called enhanced suffix array~\cite{Abouelhodaa2004}, which is more space efficient than suffix tree and applicable to emulating any searching functionalities provided by the latter in the same time complexity.
+The first algorithm for building SA in internal memory was presented in~\cite{Manber1993}.
+From then on, much effort has been put on the development of designing efficient SA construction algorithms~(SACAs) on different computation models, e.g., internal memory~\cite{Karkkainen2003, Ko2003, Kim2003, Nong11}, external memory~\cite{Dementiev2008, Ferragina2012, Manzini2004, Bingmann12, Karkkainen2014, Nong14, Nong15} and shared memory models~\cite{Osipov2012, Deo2013, Wang2015, Karkkainen2015}.
 In respect of the design on LCP-array construction algorithms~(LACAs), the existing works can be classified into two categories, where the algorithms of the first category compute the suffix and LCP arrays in the same time~\cite{Fischer11, Bingmann12, Flick2015} and that of the second category take the suffix array (SA) and/or Burrows-Wheeler transform (BWT) as input to facilitate the computation~\cite{Kasai2001,Karkkainen2009, Fischer11, Puglisi2008, Puglisi2008, Deo2013, Karkkainen2016}.
+Currently, the fastest algorithms of linear time and space complexity are based on induced sorting principle.
+However, some sub-linear algorithms reported recently achieved a better performance by exploiting the full use of computation resource in a multi-core environment.
 
+{\color{red} There are at least two needs in practice for checking the correctness of a suffix or LCP array, i.e. program debugging and verifying the array constructed by a probabilistic algorithm.}
 While the study for efficient construction of suffix and LCP arrays is evolving, the programs implementing the proposed algorithms are commonly provided ``as is", with the purpose only for the performance evaluation experiemnts of the articles where they are reported.
 That is, these programms give no guarantee that they have correctly implemented the proposed algorithms.
-The programs for recently proprosed algorithms are becoming much more complicated than before, casuing more difficulties for program verifying and debugging\footnote{In our studies before, we have exprienced problems caused by bugs of the exisitng programs.}.
+The programs for recently proprosed algorithms are becoming much more complicated than before, casuing {\color{red} challenges} for program verifying and debugging\footnote{In our studies before, we have exprienced problems caused by bugs of the exisitng programs.}.
 As a common practice, a suffix or LCP array checker is also provided for verifying the correctness of a constructed array.
@@
 
-In this article, we propose two methods for probablistically checking the give suffix and LCP arrays in external memory using a fingerprinting techinque.
-As observed from the experimental results, our program for the algorithm designed on Method A outperforms that for the algorithm designed on Method B in both running time and I/O volume by about 20 percent, while the peak disk use of the latter is about 26/40=0.65 as that of the former and can be further reduced to around 21n without a sacrifice in time and I/O performance.
+In this article, we propose two methods for probablistically checking the give suffix and LCP arrays using external memory.
+According to the experimental results, our program for Method A has a better performance than that for Method B with respect to the running time and I/O volume by about 20 percent, while the peak disk use of the latter is about 26/40=0.65 as that of the former and can be further reduced to around 21n without a sacrifice in the time and I/O effciency.
+We think these two methods could potentially be a xxxx .
 
@@
 \end{document}
+
+We are intended for ....
+
+put emphasis on
+
+with the same ease as when
+
+The biggest difference between two is that ...
+
+Toward the end, ...
+
+they are designed to be both easy to interpret on ... and easily traslated into ... (they are designed to be easily implemented in classic external memory models)
+
+Having a ... eliminates .... (random accesses), access ordering
+
+Not only are ..., but
+
+The fingerprints are calculated on the fly during the scan of x ...
+
+become so good that they are competitive with ...., and in some cases, even outperform them ...
+
+concurrent programming is needed to make sure ....
+
+designed to adapt to an evolving environment
+
+most importantly
+
+exchanges data between the computer presenting the applet and the computer serving it.
+
+carries out sophisticated calculations
+
+Presumably because
+
+make ... capable of ...
+
+greatly improve ... , it was still rather limited, though.
+
+additional performance improvements
+
+close the chapter with ...
+
+gain
+
+which pose ...
+
+integrate with
+
+In this chapter, we will ... how to ... and how to ...
+
+we prefer the comfort of an integrated development environment, ( prefer the low cost of fingerprinting techinques)
+
+space-hungry
+
+begin exploring ... by ...
+
+commnuicate the monmentous advances
+
+extremely simple
+
+check each number is present in the suffix array.
+
+go into much more greater details
+
+stand-alone algorithms for computing suffix arrays only and has been reused to
+
+invoke/call
+
+the mechanics of ...
+
+If you have done sth, then when you do sth, you end up with ...
+
+depend on the machine on which you will be running the java code ...
+
+alleviate
+
+The second method is invented to overcome the drawback of
+
+in place of
+
+as to/about
+
+as far as
+
+assign to a variable
+
+stated goals
+
+intermediate steps
+
+tied to the behavior of
+
+an assortment of
+
+following the footsteps of
+
+characters in the input string are processed from left to right
+
+in greater detail

### 2017-02-19 draft/draft.tex
2017/02/19

@@
 program debugging and verifying the arrays constructed by probabilistic algorithms.
-We propose in this paper two methods to check the suffix and LCP arrays in external memory by using a Karp-Rabin fingerprinting technique, where the checking result is wrong only with a negligible error probability.
-Our first method checks the lexicographical order and the LCP-value of two neighboring suffixes in the given suffix array by computing and comparing the fingerprints of their LCPs.
-This approach is also employed in the second method to verify a subset of the given suffix and LCP arrays, from which then a copy of the final suffix and LCP arrays is produced following the induced sorting principle and compared with the given one for verification.
+In this paper, we propose two methods to check the suffix and LCP arrays in external memory by using a Karp-Rabin fingerprinting technique, where the checking result is wrong only with a negligible error probability.
+The first method checks the lexicographical order and the LCP-value of two neighboring suffixes in the given suffix array by computing and comparing the fingerprints of their LCPs.
+This idea is also employed in the second method to verify a subset of the given suffix and LCP arrays, from which then a copy of the final suffix and LCP arrays is produced following the induced sorting principle and compared with the given arrays for verification.
 
@@
 Suffix and longest common prefix (LCP) arrays play an important role in various string processing tasks, such as data compression, pattern matching and genome assembly.
-Particularly, these two data structures constitute the core part of a powerful full-text index, called enhanced suffix array~\cite{Abouelhodaa2004}, which is more space efficient than suffix tree and applicable to emulating any searching functionalities provided by the latter in the same time complexity.
-The first algorithm for building SA in internal memory was presented in~\cite{Manber1993}.
-From then on, much effort has been put on the development of designing efficient SA construction algorithms~(SACAs) on different computation models, e.g., internal memory~\cite{Karkkainen2003, Ko2003, Kim2003, Nong11}, external memory~\cite{Dementiev2008, Ferragina2012, Manzini2004, Bingmann12, Karkkainen2014, Nong14, Nong15} and shared memory models~\cite{Osipov2012, Deo2013, Wang2015, Karkkainen2015}.
-In respect of the design on LCP-array construction algorithms~(LACAs), the existing works can be classified into two categories, where the algorithms of the first category compute the suffix and LCP arrays in the same time~\cite{Fischer11, Bingmann12, Flick2015} and that of the second category take the suffix array (SA) and/or Burrows-Wheeler transform (BWT) as input to facilitate the computation~\cite{Kasai2001,Karkkainen2009, Fischer11, Puglisi2008, Puglisi2008, Deo2013, Karkkainen2016}.
-Currently, the fastest algorithms of linear time and space complexity are based on induced sorting principle.
-However, some sub-linear algorithms reported recently achieved a better performance by exploiting the full use of computation resource in a multi-core environment.
+In many applications, these two data structures make up the core part of a powerful full-text index, called enhanced suffix array~\cite{Abouelhodaa2004}, which is more space efficient than a suffix tree and applicable to emulating any searching functionalities provided by the latter in the same time complexity.
+The first algorithm for building suffix array in internal memory was presented in~\cite{Manber1993}.
+From then on, much more effort has been put on designing efficient constructors for suffix array~(SA) on different memory models~\cite{Karkkainen2003, Ko2003, Kim2003, Nong11, Dementiev2008, Ferragina2012, Manzini2004, Bingmann12, Karkkainen2014, Nong14, Nong15}.
+In respect of the research on LCP-array construction algorithms, the existing works can be classified into two categories with regard to the input requirements, where the algorithms from the first category compute both suffix and LCP arrays at the same time with the original text only~\cite{Fischer11, Bingmann12, Flick2015} and those from the second category carry out the computation by taking SA and/or Burrows-Wheeler transform (BWT) as additional input~\cite{Kasai2001,Karkkainen2009, Fischer11, Puglisi2008, Puglisi2008, Deo2013}.
+Among all, the algorithms designed by the induced sorting~(IS) principle take linear time and space to run and outperform previous arts on both internal and external memory models~\cite{Nong11, Karkkainen2014}.
+Recently, there appear some novel works that are competitive with the IS-based ones and even achieve better performance when adequate computation resources are available.
+These algorithms can maximize their throughput by making use of the multi-core CPUs and/or GPUs in computers~\cite{Osipov2012, Deo2013, Wang2015, Karkkainen2015, Karkkainen2016}.
 
-{\color{red} There are at least two needs in practice for checking the correctness of a suffix or LCP array, i.e. program debugging and verifying the array constructed by a probabilistic algorithm.}
-While the study for efficient construction of suffix and LCP arrays is evolving, the programs implementing the proposed algorithms are commonly provided ``as is", with the purpose only for the performance evaluation experiemnts of the articles where they are reported.
-That is, these programms give no guarantee that they have correctly implemented the proposed algorithms.
-The programs for recently proprosed algorithms are becoming much more complicated than before, casuing {\color{red} challenges} for program verifying and debugging\footnote{In our studies before, we have exprienced problems caused by bugs of the exisitng programs.}.
-As a common practice, a suffix or LCP array checker is also provided for verifying the correctness of a constructed array.
-For example, such a checker is provided in the software packages (like SA-IS~\cite{Nong11}, eSAIS~\cite{Bingmann12} and DC3~\cite{Dementiev08}) for constructing suffix and/or LCP arrays.
+While the research on efficient construction of suffix and LCP arrays is evolving, the algorithms proposed recently are becoming more complicated than before.
+This reveals a need for program debugging because a program gives no guarantee that it has correctly implemented the underlying algorithm.
+As a common practice, a suffix or LCP checker is provided to check the correctness of a constructed array.
+For example, such a checker can be found in some software packages for SA-IS~\cite{Nong11}, eSAIS~\cite{Bingmann12}, DC3~\cite{Dementiev08} and so forth.
 In addition to help avoid implementation bugs, a checker is also demanded for an array constructed by a probabilistic algorithm~\cite{Bille2013}.
-In this case, the array is correct with a probability and hence must be verified by a checker to ensure its correctness.
-
-As far as we know, the work presented in~\cite{Burkhardt2003} is the only SA checking method that can be found in the existing literature, and no efficient approach for the LCP-array verification has been reported yet.
+In this case, the array is correctly constructed with a probability and hence must be verified by a checker to ensure its correctness.
+As far as we know, the work in~\cite{Burkhardt2003} describes the only SA checking method that can be found in the existing literature, and no efficient checking method for LCP array has been reported yet.
 In particular, there is currently no reported solution that can check both the suffix and the LCP arrays in external memory.
-This motivates our work here to design efficient external memory algorithms for checking the suffix and LCP arrays of massive data.
+This motivates our work here to design high-performance SA and LCP checkers for massive data.
 
@@
 
-Our contribution includes two checking methods for the given suffix and LCP arrays in external memory.
-
-The main idea of the first method is to test the lexical order and the LCP-value of two neighboring suffixes in a suffix array by literally comparing their characters.
-To reduce time complexity for a comparison between two sequences of characters, a Karp-Rabin fingerprinting function is employed to transform each sequence into a single integer, called fingerprint, such that the equality of two sequences can be correctly checked with a negiligible error probability by comparing their fingerprints in constant time.
-
-By using the same fingerprinting technique, the second method first verifies a subset chosen from the input arrays and then produces a copy of the suffix and LCP arrays from the verified subset following the induced sorting~(IS) principle.
-Given that the inducing process is correct, the input arrays are considered to be right with a high probability if they are equal to the induced copies.
+Our contribution mainly includes two methods to probablistically verify the given suffix and LCP arrays.
+Method A checks the lexical order and LCP-value of two neighboring suffixes in SA by literally comparing the characters of their LCPs in pairs.
+For reducing the time complexity of a comparison between two sequences of characters, we use a Karp-Rabin fingerprinting technique to convert each sequence into a single integer, called fingerprint, and compare the fingerprints instead to check equality of these sequences.
+The algorithm for this method involves multiple scans and sorts on sets of $\mathcal{O}(n)$ fixed-size items.
+When implemented in external memory, it suffers from a space bottleneck owing to the large disk volume taken by each sort.
+To overcome the drawback, Method B first employs the fingerprinting technique to check a subset selected from the given suffix and LCP arrays, then it reuses the inducing process of an IS-based algorithm to produce the final suffix and LCP arrays from the verified subset and literally compares them with the input arrays to ensure the correctness of the latter.
+Our experiments indicate that the peak disk use of the program for the algorithm designed by Method B is only half as that of the program for the algorithm designed by Method A.
 
 The remainder of this paper is organized as follows.
-We first describe the proposed two checking methods in Sections~\ref{sec:method1} and~\ref{sec:method2}, then present the experimental results in Section~\ref{sec:experiment},and give the conclusion in Section~\ref{sec:conclusion}.
+We first describe the checking methods and their algorithmic designs in Sections~\ref{sec:method1} and~\ref{sec:method2}, and then evaluate the performance of our programs for the algorithms of these methods in Section~\ref{sec:experiment}.
+Finally, we present the concluding remarks in Section~\ref{sec:conclusion}.
 
@@
 
-Given an input string $x[0, n)$ drawn from an alphabet $\Sigma$, the suffix array of $x$, denoted by $sa$, is a permutation of $\{0, 1, ..., n - 1\}$ such that ${\sf suf}(sa[i]) < {\sf suf}(sa[j])$ is satisfied for $0 \le i < j < n$, where ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$ are two suffixes starting with $x[sa[i]]$ and $x[sa[j]]$, respectively.
-Particularly, we say ${\sf suf}(sa[i - 1])$ and  ${\sf suf}(sa[i + 1])$ are the lexical neighbors of ${\sf suf}(sa[i])$ in $sa$.
-The LCP array of $x$, denoted by $lcp$, consists of $n$ integers, where $lcp[0]:=0$ and $lcp[i]$ records the LCP-value of ${\sf suf}(sa[i])$ and ${\sf suf}(sa[i - 1])$ for $i \in [1, n)$.
+Given a string $x[0, n)$ drawn from an alphabet $\Sigma$, the suffix array of $x$, denoted by $sa$, is a permutation of $\{0, 1, ..., n - 1\}$ such that ${\sf suf}(sa[i]) < {\sf suf}(sa[j])$ for $i, j \in [0, n)$ and $i < j$, where ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$ are two suffixes starting with $x[sa[i]]$ and $x[sa[j]]$, respectively.
+Particularly, we say ${\sf suf}(sa[j])$ is a lexical neighbor of ${\sf suf}(sa[i])$ if $|i - j| = 1$.
+The LCP array of $x$, denoted by $lcp$, consists of $n$ integers, where $lcp[0]=0$ and $lcp[i]$ records the LCP-value of ${\sf suf}(sa[i])$ and ${\sf suf}(sa[i - 1])$ for $i \in [1, n)$.
 
@@
 
-The lexical order and the LCP-value of ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$ can be determined by literally comparing their characters from left to right.
-Because all the suffixes differ in length and end with a common character, there must exist $k \in [0, n)$ such that $x[i, i + k) = x[j, j + k)$ and $x[i + k] \ne x[j + k]$.
-According to Lemma~\ref{lemma:1}, this method can be also applied to checking suffix and LCP arrays, but it suffers from high time complexity as the two substrings indicated by the LCP-value for each pair of neighboring suffixes in $sa$ take at worst $\mathcal{O}(n)$ character-wise comparisons.
+According to the definitions of $sa$ and $lcp$, we show in Lemma~\ref{lemma:1} the sufficient and necessary conditions for checking the given suffix and LCP arrays.
+Notice that the lexical order and the LCP-value of two suffixes in $x$ can be computed by literally comparing their characters from left to right.
+Because all the suffixes differ in length and end with a common character, there must exist $k \in [0, n)$ such that $x[i, i + k) = x[j, j + k)$ and $x[i + k] \ne x[j + k]$ for any $i, j \in [0, n)$ and $i \ne j$.
+This approach can be also applied to verifying the last two conditions in Lemma~\ref{lemma:1}, but it takes at worst $\mathcal{O}(n)$ character-wise comparisons for each pair of neighboring suffixes in $sa$ to compare the two substrings, that is the LCPs, indicated by their LCP-value.
 
@@
 An alternative is to exploit a perfect hash function~(PHF) to convert each substring into a single integer such that any two substrings have a common hash value if and only if they are literally equal to each other.
-Hence, the equality of two substrings can be determined by comparing the corresponding hash values instead.
-The key point here is how to efficiently compute the hash values of $x[sa[i], sa[i] + lcp[i] - 1]$ and $x[sa[i - 1], sa[i - 1] + lcp[i] - 1]$ for all $i \in [1, n)$.
-Taking into account the high cost of finding a PHF to meet this requirement, we prefer using a Karp-Rabin fingerprinting function~\cite{Karp1987} to transform a substring into its integer form, called fingerprint.
-Specifically, suppose $L$ is a prime and $\delta$ is randomly chosen from $[1, L)$, the fingerprint ${\sf fp}(i, j)$ of a substring $x[i, j]$ can be calculated by using Formulas~\ref{formula:1}-~\ref{formula:3} as following: scan $x$ rightward to iteratively compute ${\sf fp}(0, k)$ for all $k \in [0, n)$ according to Formulas~\ref{formula:1}-\ref{formula:2}, meanwhile, record ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ and subtract the former from the latter to obtain ${\sf fp}(i, j)$ according to Formula~\ref{formula:3}.
+This implies that we can compare the hash values instead to check equality of their corresponding substrings.
+The key point here is how to quickly calculate the hash values of $x[sa[i], sa[i] + lcp[i] - 1]$ and $x[sa[i - 1], sa[i - 1] + lcp[i] - 1]$ for all $i \in [1, n)$.
+Taking into consideration the high difficulty of finding a PHF to meet this requirement, we prefer using a Karp-Rabin fingerprinting function~\cite{Karp1987} to transform a substring into its integer form, called fingerprint.
+Specifically, suppose $L$ is a prime and $\delta$ is randomly chosen from $[1, L)$, the fingerprint ${\sf fp}(i, j)$ of a substring $x[i, j]$ can be calculated according to the formulas below as following: scan $x$ rightward to iteratively compute ${\sf fp}(0, k)$ for all $k \in [0, n)$ using Formulas~\ref{formula:1}-\ref{formula:2}, record ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ during the calculation and subtract the former from the latter to obtain ${\sf fp}(i, j)$ using Formula~\ref{formula:3}.
 
@@
 
-It is worthy of mentioning that two equal substrings always share a common fingerprint, but the inverse is not true.
+We point out that two equal substrings always share a common fingerprint, but the inverse is not true.
 Fortunately, it has been proved in~\cite{Karp1987} that the probability of a false match can be reduced to a negligible level by setting $L$ to a large value\footnote{This property is utilized in~\cite{Bille2013} to design a probabilistic algorithm for computing a sparse suffix array.
 }.
-This leads us to the following conclusion.
+This leads us to the conclusion in Corollary~\ref{corollary:1}.
 
@@
 
+We show in Fig.~\ref{fig:example} an example for better understanding.
+Assume $L = 197$ and $\delta = 101$, lines 4-8 compute ${\sf fp}(0, p)$ iteratively according to Formulas~\ref{formula:1}-\ref{formula:2}.
+These values are used to compute the fingerprints for the target substrings.
+Consider the leftmost pair of neighboring suffixes in $sa$, that is ${\sf suf}(sa[0])$ and ${\sf suf}(sa[1])$, the substrings indicated by their LCP-value are $x[sa[0], sa[0] + lcp[1] - 1]$ and $x[sa[1], sa[1] + lcp[1] - 1]$, respectively.
+According to Formula~\ref{formula:3}, ${\sf fp}(sa[0], sa[0] + lcp[1] - 1)$ is equal to the difference between ${\sf fp}(0, sa[0])$ and ${\sf fp}(0, sa[0] + lcp[1] + 1)$, which have been calculated beforehand.
+In lines 10-12, we obtain the fingerprints for these two substrings and find that they are equal to each other.
+
+\begin{figure*}
+	\centering
+	\label{fig:example}
+	\includegraphics[width = 0.8\textwidth]{example}
+	\caption{An Example for Computing the Fingerprints for the LCPs of the Neighboring Suffixes in SA.}	
+\end{figure*}
+
 \subsection{Algorithm} \label{sec:method1:algorithm}
 
-Section~\ref{sec:method1:idea} indicates that we can perform verification for the given suffix and LCP arrays by testing the conditions of Corollary~\ref{corollary:1}.
-Based on this idea, we introduce below a linear algorithm for checking $sa$ and $lcp$ on random access models.
+We first describe an algorithm for checking conditions in Corollary~\ref{corollary:1} on random access models, of which the core part is to check the lexical order and LCP-value for each pair of neighboring suffixes in $sa$ on-the-fly during the scan of $sa$ and $lcp$.
+This is done by using Formulas~\ref{formula:1}-\ref{formula:3} following our discussion in the previous subsection.
+As can be seen, two zero-initialized array, namely $fp$ and $mk$, are introduced to facilitate the checking process, where $fp$ is for storing the fingerprints of prefixes and $mk$ is for determining whether or not each number of $\{0, 1, ..., n - 1\}$ is present in $sa$.
 
@@
 	\item [S1]
-	Scan $x$ rightward with $i$ increasing from $0$ to $n - 1$. For each scanned $x[i]$, iteratively compute ${\sf fp}(0, i)$ and set $fp[i] = {\sf fp}(0, i)$.
+	Scan $x$ rightward with $i$ increasing from $0$ to $n - 1$. For each scanned $x[i]$, compute ${\sf fp}(0, i)$ and assign the value to $fp[i]$.
 
 	\item [S2]
-	Scan $sa$ and $lcp$ rightward with $i$ increasing from $1$ to $n - 1$. For each scanned $sa[i]$ and $lcp[i]$, let $u = sa[i], v = lcp[i], w = sa[i - 1]$ and performs substeps (a)-(c) sequentially:
+	Scan $sa$ and $lcp$ rightward with $i$ increasing from $1$ to $n - 1$. For each scanned $sa[i]$ and $lcp[i]$, let $u = sa[i], v = lcp[i], w = sa[i - 1]$ and perform substeps (a)-(c) in sequence:
 
@@
 		\item
-		Retrieve $fp[u - 1]$ and $fp[u + v - 1]$ from $fp$ to compute ${\sf fp}(u, u + v - 1)$. Set $mk[u] = 1$.
+		Retrieve $fp[u - 1]$ and $fp[u + v - 1]$ from $fp$ to compute ${\sf fp}(u, u + v - 1)$. Set $mk[u]$ to $1$.
 
@@
 
-Two zero-initialized arrays $fp$ and $mk$ are used to faciliate the checking process, where the former is for storing the fingerprints of all the prefixes in $x$ and the latter is for checking the existence of $\{0, 1, ..., n - 1\}$ in $sa$.
-Assume $L = 197$ and $\delta = 101$, we give a small example of S1-S2 in Fig.~\ref{fig:example} for better understanding.
-Clearly, this algorithm consumes $\mathcal{O}(n)$ time and space when running in internal memory.
-However, if the input can not be wholly accommodated into RAM, it may suffer from a performance degradation due to frequent random I/O operations for reading elements of $x$, $sa$ and $lcp$ from external memory during the execution of S2.
-
-\begin{figure*}
-	\centering
-	\label{fig:example}
-	\includegraphics[width = 0.8\textwidth]{example}
-	\caption{An Example for Checking the Suffix and LCP Arrays Using the Karp-Rabin Fingerprinting Functions}	
-\end{figure*}
+It is clear that the above algorithm consumes $\mathcal{O}(n)$ time and space when implemented in internal memory.
+However, if the two auxiliary arrays cannot be wholly accommodated into RAM during the execution of S2, it suffers from a performance degradation caused by frequent random accesses to disks.
+Assume that $x$, $sa$ and $lcp$ are stored in external memory, we design Algorithm~\ref{alg:1} for conducting these I/O operations in a disk-friendly way.
+The main idea is to first sort data in the order that they are visited and then access them by sequential reads and writes.
+To the end, our algorithm first scans $sa$ and $lcp$ to produce $ST_1, ST_2, ST_3$ and sorts their tuples by 1st component in ascending order at the very beginning (lines~\ref{alg:1:a}-\ref{alg:1:b}).
+Afterward, it iteratively computes the fingerprints of all the prefixes according to Formulas~\ref{formula:1}-\ref{formula:2} and assigns them to the sorted tuples as following (lines~\ref{alg:1:c}-\ref{alg:1:d}): when figuring out ${\sf fp}(0, i - 1)$, extract each tuple $e$ with $e.1st = i$ from $ST_1/ST_2/ST_3$, update $e$  with ${\sf fp}(0, i - 1)$, and then forward $e$ to $ST_1'/ST_2'/ST_3'$.
+Because the 1st component of the tuples in $ST_1$ constitute a copy of $sa$, the algorithm can check condition (1) in lines~\ref{alg:1:h}-\ref{alg:1:i} when scanning them in the sorted order.
+Finally, it sorts the updated tuples back to their original order (line~\ref{alg:1:e}) and visits them  sequentially to check conditions (2)-(3) following the same way of S2.
 
@@
 
-	\caption{The Algorithm for checking the conditions of Corollary~\ref{corollary:1}.}
+	\caption{The Algorithm Based on Corollary~\ref{corollary:1}.}
 
@@
 
-		$ST_1$ := $[(sa[i], i, null) | i \in [0, n)]$. \label{alg:1:a}
+		$ST_1$ := $[(sa[i], i, null) | i \in [0, n)]$ \label{alg:1:a}
 
-		$ST_2$ := $[(sa[i] + lcp[i + 1], i, null, null) | i \in [0, n - 1)]$.
+		$ST_2$ := $[(sa[i] + lcp[i + 1], i, null, null) | i \in [0, n - 1)]$
 
-		$ST_3$ := $[(sa[i] + lcp[i], i, null, null) | i \in [1, n)]$.
+		$ST_3$ := $[(sa[i] + lcp[i], i, null, null) | i \in [1, n)]$
 
-		sort tuples in $ST_1$, $ST_2$ and $ST_3$ by 1st component. \label{alg:1:b}
+		sort tuples in $ST_1$, $ST_2$ and $ST_3$ by 1st component \label{alg:1:b}
 
@@
 
-We propose Algorithm~\ref{alg:1} to perform the checking process in an I/O friendly way, which conducts external-memory sorts to avoid random accesses to external disks.
-At the very beginning, the algorithm first scans $sa$ and $lcp$ to produce $ST_1, ST_2, ST_3$ and sorts the tuples of them by 1st component in ascending order (lines~\ref{alg:1:a}-\ref{alg:1:b}).
-Then, it computes the fingerprints of all the prefixes according to Formulas~\ref{formula:1}-\ref{formula:2} and assign them to the sorted tuples in lines~\ref{alg:1:c}-\ref{alg:1:d} as following: when finished computing ${\sf fp}(0, i - 1)$, extract each tuple $e$ with $e.1st = i$ from $ST_1, ST_2, ST_3$  and update them with ${\sf fp}(0, i - 1)$ and $x[i]$ (if required), where the tuples are forwarded to $ST_1', ST_2', ST_3'$ after updating and sorted back to their original order (line~\ref{alg:1:e}).
-During the process, we determine whether or not the 1st components of all the tuples in $ST_1$ consistute a permutation of $\{0, 1, ..., n - 1\}$ to test the first condition of Corollary~\ref{corollary:1} (lines~\ref{alg:1:h}-\ref{alg:1:i}).
-Finally, it repeatedly retrieves the top tuples from $ST_1', ST_2', ST_3'$ and applies Formulas~\ref{formula:3} to compute the fingerprints of two substrings specified by their 1st components for ensuring the satisfaction of conditions (2)-(3).
-A point to be explained here is how to compute $\delta^{lcp[i]}$ in lines~\ref{alg:1:j} and~\ref{alg:1:k}.
-Let $e := lcp[i]$, our method first decomposes $e$ into $\Sigma_{i = 0}^{\lceil \log2^n \rceil}{k_i \cdot 2^i}$ and then computes $\Pi_{i = 0}^{\lceil \log2^n \rceil}{\delta}^{k_i \cdot 2^i}$ to obtain $\delta^{e}$, where $k_i \in \{0, 1\}$.
-Following this way, the answer can be returned in $\mathcal{O}(\lceil \log2^n \rceil)$ time using $\mathcal{O}(\lceil \log2^n \rceil)$ space for storing $\{{\delta}^{1}, {\delta}^{2}, \dots, {\delta}^{2^{\lceil \log2^n \rceil}} \}$.
+The last point to be mentioned here is how to obtain the value of $\delta^{lcp[i]}$ quickly when computing $\hat{fp_1}$ and $\hat{fp_2}$ in lines~\ref{alg:1:j} and~\ref{alg:1:k}.
+One method is to keep a lookup table in internal memory to store $\delta^{lcp[i]}$ for all $i \in [0, n)$.
+This method can answer the question in constant time, but it is space-consuming and
+impractical to use when the table is bigger than the memory bank capacity.
+We provide another method that returns the answer in $\mathcal{O}(\lceil \log2^n \rceil)$ time using $\mathcal{O}(\lceil \log2^n \rceil)$ internal memory space.
+Specifically, suppose $e$ is an integer from $[0, n)$, it can be decomposed into the form of $\Sigma_{i = 0}^{\lceil \log2^n \rceil}{k_i \cdot 2^i}$, where $k_0, k_1, ..., k_{\lceil \log2^n \rceil}$ are determined by performing at most $\lceil \log2^n \rceil$ divisions.
+Hence, we have $\delta^e = \Pi_{i = 0}^{\lceil \log2^n \rceil}{\delta}^{k_i \cdot 2^i}$ by replacing $e$ with its decomposition, where the expression on the right side of the equation can be easily computed with $\{{\delta}^{1}, {\delta}^{2}, \dots, {\delta}^{2^{\lceil \log2^n \rceil}} \}$ already known.
 
-\subsection{Discussion} \label{sec:method1:discussion}
+\subsection{Analysis} \label{sec:method1:analysis}
 
-Algorithm~\ref{alg:1} performs multiple scans and sorts for arrays of $n$ fixed-size tuples using external memory.
-Consider an external memory model with RAM size $M$, disk size $D$ and block size $B$, all are in words, then the time and I/O complexities for a scan are $\mathcal{O}(n)$ and $\mathcal{O}(n / B)$, respectively, while those for a sort with an integer key are $\mathcal{O}(n\log_{M/ B}(n / B))$ and $\mathcal{O}((n / B)\log_{M / B}(n / B))$, respectively~\cite{Arge2013}.
-Besides, the algorithm reaches its peak disk use when sorting tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}.
-An optimization for reducing maximum space requirements is to compute the fingeprints indicated by $ST_1, ST_2, ST_3$ separately.
-This will lead to a small increase in total I/O volume as it needs to compute $\{{\sf fp}(0, 0), {\sf fp}(0, 1), ..., {\sf fp}(0, n - 1)\}$ two more times.
+Algorithm~\ref{alg:1} is I/O-intensive, it performs multiple scans and sorts on the arrays of $\mathcal{O}(n)$ fixed-size tuples residing on disks.
+Given an external memory model with RAM size $M$, disk size $D$ and block size $B$, all are in words, the time and I/O complexities for each scan are $\mathcal{O}(n)$ and $\mathcal{O}(n / B)$, respectively, while those for each sort are $\mathcal{O}(n\log_{M/ B}(n / B))$ and $\mathcal{O}((n / B)\log_{M / B}(n / B))$, respectively~\cite{Arge2013}.
+This algorithm reaches its peak disk use when sorting tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}.
+A trick for reducing	the space requirements is to compute the fingerprints of prefixes specified in $ST_1$, $ST_2$ and $ST_3$, respectively.
+However, our experimental study in Section~\ref{sec:experiment} shows that Algorithm~\ref{alg:1} is still rather space hungry, its peak disk use is 40 bytes per input character.
+In the next section, we will describe an alternative checking method based on the induced-sorting principle.
+Compared with Algorithm~\ref{alg:1}, the program for our algorithm designed by this method only takes half space on real-world datasets.
 
@@
 
-Our experimental study in Section~\ref{sec:experiment} shows that Algorithm~\ref{alg:1} is quite space consuming, its peak disk use is 40 bytes per input character.
-In this section, we describe an alternative based on the induced-sorting principle.
-Compared with Algorithm~\ref{alg:1}, the algorithm designed by this method only takes half space on real-world datasets.
-
 \subsection{Preliminaries} \label{sec:method2:preliminaries}
 
-Before our presentation, we first introduce some notations for description convenience.
+We introduce some symbols and notations used in the following presentation.
 
 {\em Character and suffix classification.} All the characters in $x$ are classified into three types, namely L-, S- and S*-type.
-Detailedly, $x[i]$ is L-type if (1) $i = n - 1$ or (2) $x[i] > x[i + 1]$ or (3) $x[i] = x[i + 1]$ and $x[i + 1]$ is L-type; otherwise, $x[i]$ is S-type.
-Further, if $x[i]$ and $x[i + 1]$ are S- and L-type respectively, then $x[i]$ is also an S*-type character.
-Moreover, the type of a suffix is the same as that of its heading character.
+In detail, $x[i]$ is L-type if (1) $i = n - 1$ or (2) $x[i] > x[i + 1]$ or (3) $x[i] = x[i + 1]$ and $x[i + 1]$ is L-type; otherwise, $x[i]$ is S-type.
+Further, if $x[i]$ and $x[i + 1]$ are respectively S- and L-type, then $x[i]$ is also an S*-type character.
+Moreover, a suffix is L-, S- or S*-type if its heading character is L-, S-, or S*-type, respectively.
 
-{\em Suffix and LCP buckets.} Suppose $sa$ is correct, then suffixes in $sa$ are naturally partitioned into multiple buckets and those with an identical heading character are grouped into one bucket occupying a contiguous interval.
-Further, a bucket can be divided into two parts, where the left and right part contain L- and S-type suffixes, respectively.
-For short, we use ${\sf sa\_bkt}(c)$ to denote the bucket storing suffixes starting with $c$ and ${\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$ to denote its left/right sub-bucket.
-Accordingly, $lcp$ can be decomposed into multiple buckets as well, where ${\sf lcp\_bkt}(c)/{\sf lcp\_bkt_L}(c)/{\sf lcp\_bkt_S}(c)$ store the LCP-values of suffixes in ${\sf sa\_bkt}(c)/{\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$ and their left lexical neighbors.
+{\em Suffix and LCP buckets.} Suppose $sa$ is correct, all the suffixes in $sa$ are naturally partitioned into multiple buckets and those of a common heading character are grouped into a single bucket that occupies a contiguous interval in $sa$.
+Each bucket can be further divided into two sub-buckets, where the left and right parts only contain L- and S-type suffixes, respectively.
+For short, we use ${\sf sa\_bkt}(c)$ to denote the bucket storing suffixes starting with character $c$ and ${\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$ to denote its left/right sub-bucket.
+Accordingly, $lcp$ can be also split into multiple buckets, where ${\sf lcp\_bkt}(c)/{\sf lcp\_bkt_L}(c)/{\sf lcp\_bkt_S}(c)$ stores the LCP-values of suffixes in ${\sf sa\_bkt}(c)/{\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$.
 
-{\em Suffix and LCP arrays for S*-type suffixes.} Suppose the number of S*-type suffixes in $x$ is $n_1$, $sa^*[0, n_1)$ and $lcp^*[0, n_1)$ indicate the lexical order and the LCP-values of these S*-type suffixes, where $x[sa^*[i]]$ is the heading character of the $(i + 1)$-th smallest S*-type suffix.
-
-{\em Type array.} The type array $t$ records the type of $x[i]$ in $t[i]$ for $i \in [0, n)$.
+{\em Suffix and LCP arrays for S*-type suffixes.} Given that the number of S*-type suffixes is $n_1$, $sa^*[0, n_1)$ stores all the S*-type suffixes and arrange them in lexical order, while the $(i + 1)$-th item of $lcp^*[0, n_1)$ records the LCP-value of ${\sf suf}(sa^*[i])$ and ${\sf suf}(sa^*[i - 1])$.
 
@@
 
-The induced sorting principle has been employed to design algorithms for constructing suffix and LCP arrays in both internal and external memory.
-These algorithms mainly consist of a reduction phase for computing $sa^*$ and $lcp^*$ followed by an induction phase for inducing $sa$ and $lcp$ from $sa^*$ and $lcp^*$.
-Suppose $sa^*$ and $lcp^*$ are already known, we can directly build the suffix and LCP arrays by calling the inducing process of an existing IS-based construction algorithm.
-This enlightens us to check the following conditions for verification:
+The induced sorting principle has been employed to invent efficient algorithms for constructing suffix and LCP arrays on both internal and external memory models.
+These algorithms mainly consist of a reduction phase for computing $sa^*$ and $lcp^*$, followed by an induction phase for inducing $sa$ and $lcp$ from $sa^*$ and $lcp^*$.
+Given that $sa^*$ and $lcp^*$ are already known, we can directly construct the suffix and LCP arrays by calling the inducing process of any existing IS-based construction algorithm.
+This enlightens us to design a checker following Lemma~\ref{lemma:2}.
 
@@
 	\item
-	$sa = sa'$ and $lcp = lcp'$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by calling the inducing process of an existing IS-based construction algorithm.
+	$sa = sa'$ and $lcp = lcp'$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by calling the inducing process of any existing IS-based construction algorithm.
 \end{enumerate}
@@
 
-Following the same idea described in Section~\ref{sec:method1:idea}, we come to the conclusion in Corollary~\ref{corollary:2} by using the fingerprinting technique.
+Similar to Method A, we can employ the fingerprinting technique to probablistically check the correctness of $sa^*$ and $lcp^*$.
+Based on this idea, we describe in the subsequent paragraphs an external-memory algorithm for checking the conditions in Corollary~\ref{corollary:2}.
 
 \begin{Corollary} \label{corollary:2}
-Both $sa[0, n)$ and $lcp[0, n)$ are correct with a high probability given the following conditions, for $i \in [0, n)$, $j, k \in [1, n_1)$ and $j \ne k$:
+Both $sa[0, n)$ and $lcp[0, n)$ are correct with a high probability given the following conditions, for $i \in [0, n)$, $\{j, k\} \in [1, n_1)$ and $j \ne k$:
 
@@
 \subsection{Algorithm} \label{sec:method2:algorithm}
-Algorithm~\ref{alg:2} checks the conditions in Corollary~\ref{corollary:2} using external memory, the details are shown as following.
-The first task of the algorithm is to retrieve $sa^*$ and $lcp^*$ from $sa$ and $lcp$.
-For the purpose, it creates a tuple for each suffix in $sa$ and sorts them by 1st component in descending order~(lines~\ref{alg:2:a}-\ref{alg:2:b}).
-After sorting, it scans $x$ leftward to find all the S*-type suffixes according to the definition in Section~\ref{sec:method2:preliminaries}~(lines~\ref{alg:2:c}-\ref{alg:2:d}).
-For each S*-type suffix, we pick the corresponding tuple from the top of $ST_1$ and forward the tuple to $ST_2$.
-Then, the algorithm sorts $ST_2$ by 2nd component in ascending order and scans the sorted tuples sequentially to produce $sa^*$ and $rank^*$, where $rank*$ is the compact form of $sa^*$.
-Meanwhile, we compute $lcp^*$ following the fact that the LCP-value of two suffixes in ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$ ($i < j$) is the minimum value among $\{lcp[i + 1], ..., lcp[j - 1], lcp[j]\}$~(lines~\ref{alg:2:g}-\ref{alg:2:h}).
-The next task is to check the correctness of $sa^*$ and $lcp^*$.
-This is accomplished in lines~\ref{alg:2:i}-\ref{alg:2:j} by reusing Algorithm~\ref{alg:1}.
-At last, we call the inducing process of an external-memory construction algorithm to generate $sa'$ and $lcp'$~(line~\ref{alg:2:k}), and compare the output with $sa$ and $lcp$ to determine the result in lines~\ref{alg:2:l}-\ref{alg:2:m}.
+
+The first step of Algorithm~\ref{alg:2} is to compute and verify $sa^*$ and $lcp^*$.
+According to the definition, $sa^*$ can be produced by sequentially retrieving the S*-type suffixes from $sa$ while the LCP-value of two successive S*-type suffixes in $sa$, say ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$, is equal to the minimal of $\{lcp[i + 1], ..., lcp[j - 1], lcp[j]\}$.
+Hence, the proposed algorithm first sorts all the suffixes in $sa$ by their starting positions~(lines~\ref{alg:2:a}-\ref{alg:2:b}) and then scans $x$ only once to pick out the S*-type suffixes~(lines~\ref{alg:2:c}-\ref{alg:2:d}).
+After that, it puts these S*-type suffixes back in their lexical order and outputs them one by one to generate $sa^*$~(lines~\ref{alg:2:g}-\ref{alg:2:h}).
+Meanwhile, it calculates the LCP-value for each pair of neighboring suffixes in $sa^*$ by tracing the minimal over an interval of $lcp$ specified by the two suffixes.
+Notice that, we check condition (1) in Corollary~\ref{corollary:2} during the time when visiting the suffixes in position order (lines~\ref{alg:2:e}-\ref{alg:2:f}) and conditions (2)-(3) by calling Algorithm~\ref{alg:1} with $sa^*$ and $lcp^*$ as input.
+Suppose $sa^*$ and $lcp^*$ are both correct, then Algorithm~\ref{alg:1} invokes the inducing process of an existing construction algorithm to induce $sa'$ and $lcp'$, which are a copy of the final suffix and LCP arrays, from the two verified arrays~(line~\ref{alg:2:k}) and literally compares them with $sa$ and $lcp$ to complete the whole checking process~(lines~\ref{alg:2:l}-\ref{alg:2:m}).
 
@@
 
-	\caption{The Algorithm for checking the conditions of Corollary~\ref{corollary:2}.}
+	\caption{The Algorithm Based on Corollary~\ref{corollary:2}.}
 
@@
 
-	$r := 0$, $pos := -1$ \label{alg:2:c}
+	$pos := -1$ \label{alg:2:c}
 
@@
 
-			$e.3rd := r$, $r := r + 1$, $ST_2.{\sf push}(e)$, $pos := e.1st$
+			$ST_2.{\sf push}(e)$, $pos := e.1st$
 		}\label{alg:2:f}
@@
 
-				$sa^*[j] := e.1st$, $rank^*[j] := e.3rd$, $lcp^*[j] := lcp_{min}$, $j := j + 1$, $i:= i + 1$
+				$sa^*[j] := e.1st$, $lcp^*[j] := lcp_{min}$, $j := j + 1$, $i:= i + 1$
 
@@
 
-	\If{${\sf CheckByFP}(x, rank^*, lcp^*, lcp^*.{\sf size}()) = false$}{  \label{alg:2:i}
+	\If{${\sf CheckByFP}(x, sa^*, lcp^*, lcp^*.{\sf size}()) = false$}{  \label{alg:2:i}
 
@@
 
-\subsection{Optimization} \label{sec:method2:optimization}
-
-Algorithm~\ref{alg:2} produces a copy of the suffix and LCP arrays during the inducing process.
-Actually, given that $\Sigma$ is of a constant size, we can simply scan $sa/lcp$ to induce and check the suffixes/LCP arrays simultaneously without using extra space.
-The idea is that when a suffix/LCP-value $v_1$ is induced into a suffix/LCP bucket, we directly compare it with the corresponding item $v_2$ in $sa/lcp$.
-If $v_1 = v_2$, then $v_2$ is correct and can be used to induce subsequent suffixes/LCP-values.
-The key point here is how to retrieve elements from $sa/lcp$ quickly.
-This can be accomplished by conducting sequential I/O operations if we maintain a read pointer coupled with a buffer for each suffix/LCP sub-bucket.
-More details of the optimized inducing and checking processes as below, where $c \in [0, \Sigma)$ and $lp_1, lp_2, sp_1, sp_2$ are read pointer arrays for retrieving items from $sa/lcp$ buckets residing on disks.
+Assume that the alphabet $\Sigma$ is of a constant size, we can check $sa$ and $lcp$ without producing a copy of the final suffix and LCP arrays in Algorithm~\ref{alg:2}.
+The idea is to compare the induced suffix/LCP items with their corresponding items in $sa/lcp$ during the inducing process.
+Specifically, when a suffix/LCP item $v_1$ is induced into a bucket, we check if it is equal to the corresponding item $v_2$ in $sa/lcp$.
+If $v_1 = v_2$, then $v_2$ is correct and we can further use it to induce the lexical order and LCP-value of its preceding suffix later.
+The key point here is how to retrieve items from $sa/lcp$ quickly.
+This can be done by performing sequential I/O operations when we provide a read pointer together with a buffer for each suffix/LCP sub-bucket.
+We show more details of the adapted inducing process as below, where $c \in [0, \Sigma)$ and $lp_1/lp_2$ and $sp_1/sp_2$ are read pointer arrays for retrieving items from the L-type/S-type sub-buckets in $sa$ and $lcp$.
 
@@
 	\item [S1]
-	Let $lp_1[c]$ and $lp_2[c]$ point to the leftmost element of ${\sf sa\_bkt_L}(c)$ and ${\sf lcp\_bkt_L}(c)$ in $sa$ and $lcp$, respectively.
+	\begin{enumerate}[(a)]
+		\item 
+		Let $lp_1[c]$ and $lp_2[c]$ point to the leftmost items of ${\sf sa\_bkt_L}(c)$ and ${\sf lcp\_bkt_L}(c)$, respectively.
+		\item 
+		Scan $sa/lcp$ rightward to induce L-type suffixes and their LCP-values.
+For each induced suffix $p$ (with a heading character $c_0$) and its LCP-value $q$: (1) check if $p = lp_1[c_0]$ and $q = lp_2[c_0]$; (2) let $lp_1[c_0]$ and $lp_2[c_0]$ point to the next items on the right side.
+	\end{enumerate}
 	\item [S2]
-	Induce L-type suffixes and their LCP-values following the induced sorting principle.
-Meanwhile, for each induced L-type suffix $p$ with a heading character $c_0$ and its LCP-value $q$: (1) check $p = lp_1[c_0]$ and $q = lp_2[c_0]$; (2) let $lp_1[c_0]$ and $lp_2[c_0]$ point to the right neighbor in the same $sa$ and $lcp$ sub-buckets.
-	\item [S3]
-	Let $sp_1[c]$ and $sp_2[c]$ point to the rightmost element of ${\sf sa\_bkt_S}(c)$ and ${\sf lcp\_bkt_S}(c)$ in $sa$ and $lcp$, respectively.
-	\item [S4]
-	Induce S-type suffixes and their LCP-values following the induced sorting principle.
-Meanwhile, for each induced S-type suffix $p$ with a heading character $c_0$ and its LCP-value $q$: (1) check $p = sp_1[c_0]$ and $q = sp_2[c_0]$; (2) let $sp_1[c_0]$ and $sp_2[c_0]$ point to the left neighbor in the same $sa$ and $lcp$ sub-buckets.
+	\begin{enumerate}[(a)]
+		\item 	
+		Let $sp_1[c]$ and $sp_2[c]$ point to the rightmost items of ${\sf sa\_bkt_S}(c)$ and ${\sf lcp\_bkt_S}(c)$, respectively.
+		\item 	
+		Scan $sa/lcp$ leftward to induce S-type suffixes and their LCP-values.
+For each induced suffix $p$ (with a heading character $c_0$) and its LCP-value $q$: (1) check if $p = sp_1[c_0]$ and $q = sp_2[c_0]$; (2) let $sp_1[c_0]$ and $sp_2[c_0]$ point to the next items on the left side.
+	\end{enumerate}
 \end{enumerate}
 
-\subsection{Discussion} \label{sec:method2:discussion}
+\subsection{Analysis} \label{sec:method2:analysis}
 
-Both Algorithm~\ref{alg:2} and its optimized version can be implemented within sorting complexity.
-The space bottleneck occurs when inducing and checking the suffix and LCP arrays.
-This is because the existing IS-based construction algorithms store BWT to help retrieving preceding characters during the inducing process.
-We refer the interested readers to~\cite{Karkkainen2013} for more details.
+Algorithm~\ref{alg:2} mainly consists of two parts, where the first part for checking $sa^*$ and $lcp^*$ can be implemented within sorting complexity and the second part for checking $sa$ and $lcp$ can be implemented in linear time under the condition that $|\Sigma| = \mathcal{O}(1)$.
+As demonstrated in Section~\ref{alg:2}, the peak disk use of our program for Algorithm~\ref{alg:2} is around 20n and it has a similar performance compared to that for Algorithm~\ref{alg:1} in terms of time and I/O volume.
 
@@
 The experimental platform is a work station equipped with an Intel Xeon E3-1220 V2 CPU, 4GiB RAM and 500GiB HD.
-To achieve high I/O efficiency, we implement the algorithms proposed in the previous sections using the external-memory containers provided by the STXXL library~\cite{Dementiev2007}.
-All the programs are compiled by gcc/g++ 4.8.4 with -O3 options under ubuntu 14.04 64-bit operating system.
-For performance analysis, we investigate on real-world datasets in Table~\ref{tbl:1} the following three metrics normalized by the size of input string:
+To achieve high I/O efficiency, the algorithms proposed in the previous sections are implemented using the external-memory containers provided by the STXXL library~\cite{Dementiev2007}.
+Our programs are compiled by gcc/g++ 4.8.4 with -O3 options under ubuntu 14.04 64-bit operating system.
+For analysis, we evaluate the performance on real-world datasets listed in Table~\ref{tbl:1} by investigating the following three measurements normalized by the size of input string:
 

### 2017-02-25 draft/draft.tex
2017//02/25

@@
 From then on, much more effort has been put on designing efficient constructors for suffix array~(SA) on different memory models~\cite{Karkkainen2003, Ko2003, Kim2003, Nong11, Dementiev2008, Ferragina2012, Manzini2004, Bingmann12, Karkkainen2014, Nong14, Nong15}.
-In respect of the research on LCP-array construction algorithms, the existing works can be classified into two categories with regard to the input requirements, where the algorithms from the first category compute both suffix and LCP arrays at the same time with the original text only~\cite{Fischer11, Bingmann12, Flick2015} and those from the second category carry out the computation by taking SA and/or Burrows-Wheeler transform (BWT) as additional input~\cite{Kasai2001,Karkkainen2009, Fischer11, Puglisi2008, Puglisi2008, Deo2013}.
+In respect of the research on LCP array construction algorithms, the existing works can be classified into two categories with regard to their input requirements, where the algorithms from the first category compute both suffix and LCP arrays at the same time with the original text only~\cite{Fischer11, Bingmann12, Flick2015} and those from the second category carry out the computation by taking SA and/or Burrows-Wheeler transform (BWT) as additional input~\cite{Kasai2001,Karkkainen2009, Fischer11, Puglisi2008, Puglisi2008, Deo2013}.
 Among all, the algorithms designed by the induced sorting~(IS) principle take linear time and space to run and outperform previous arts on both internal and external memory models~\cite{Nong11, Karkkainen2014}.
-Recently, there appear some novel works that are competitive with the IS-based ones and even achieve better performance when adequate computation resources are available.
-These algorithms can maximize their throughput by making use of the multi-core CPUs and/or GPUs in computers~\cite{Osipov2012, Deo2013, Wang2015, Karkkainen2015, Karkkainen2016}.
+Recently, there appear some novel works that are competitive with the IS-based ones and can even achieve better performance when adequate computation resources are at hand.
+These algorithms are specific for parallel computation environments and capable of achieving high performance by fully using the available multi-core CPUs and/or GPUs~\cite{Osipov2012, Deo2013, Wang2015, Karkkainen2015, Karkkainen2016}.
 
@@
 For example, such a checker can be found in some software packages for SA-IS~\cite{Nong11}, eSAIS~\cite{Bingmann12}, DC3~\cite{Dementiev08} and so forth.
-In addition to help avoid implementation bugs, a checker is also demanded for an array constructed by a probabilistic algorithm~\cite{Bille2013}.
+In addition to help avoid implementation bugs, a checker is also demanded for an array constructed by a probabilistic algorithm~(e.g.~\cite{Bille2013}).
 In this case, the array is correctly constructed with a probability and hence must be verified by a checker to ensure its correctness.
 As far as we know, the work in~\cite{Burkhardt2003} describes the only SA checking method that can be found in the existing literature, and no efficient checking method for LCP array has been reported yet.
-In particular, there is currently no reported solution that can check both the suffix and the LCP arrays in external memory.
-This motivates our work here to design high-performance SA and LCP checkers for massive data.
+Particularly, there is currently no reported solution that can check both the suffix and the LCP arrays in external memory.
+This motivates our work here to design high-performance checkers for massive data.
 
@@
 Our contribution mainly includes two methods to probablistically verify the given suffix and LCP arrays.
-Method A checks the lexical order and LCP-value of two neighboring suffixes in SA by literally comparing the characters of their LCPs in pairs.
+Method A checks the lexical order and the LCP-value of two neighboring suffixes in SA by literally comparing the characters of their LCPs in pairs.
 For reducing the time complexity of a comparison between two sequences of characters, we use a Karp-Rabin fingerprinting technique to convert each sequence into a single integer, called fingerprint, and compare the fingerprints instead to check equality of these sequences.
-The algorithm for this method involves multiple scans and sorts on sets of $\mathcal{O}(n)$ fixed-size items.
+The algorithm for Method A involves multiple scans and sorts on sets of $\mathcal{O}(n)$ fixed-size items.
 When implemented in external memory, it suffers from a space bottleneck owing to the large disk volume taken by each sort.
@@
 The remainder of this paper is organized as follows.
-We first describe the checking methods and their algorithmic designs in Sections~\ref{sec:method1} and~\ref{sec:method2}, and then evaluate the performance of our programs for the algorithms of these methods in Section~\ref{sec:experiment}.
+We first describe the two methods and their algorithmic designs in Sections~\ref{sec:method1} and~\ref{sec:method2}, and then the evaluation of our programs for the algorithms designed by these methods in Section~\ref{sec:experiment}.
 Finally, we present the concluding remarks in Section~\ref{sec:conclusion}.
@@
 
-According to the definitions of $sa$ and $lcp$, we show in Lemma~\ref{lemma:1} the sufficient and necessary conditions for checking the given suffix and LCP arrays.
-Notice that the lexical order and the LCP-value of two suffixes in $x$ can be computed by literally comparing their characters from left to right.
+According to the above definitions, we show in Lemma~\ref{lemma:1} the sufficient and necessary conditions for checking suffix and LCP arrays.
+Notice that the lexical order and the LCP-value of any two suffixes in $x$ can be computed by literally comparing their characters from left to right.
 Because all the suffixes differ in length and end with a common character, there must exist $k \in [0, n)$ such that $x[i, i + k) = x[j, j + k)$ and $x[i + k] \ne x[j + k]$ for any $i, j \in [0, n)$ and $i \ne j$.
-This approach can be also applied to verifying the last two conditions in Lemma~\ref{lemma:1}, but it takes at worst $\mathcal{O}(n)$ character-wise comparisons for each pair of neighboring suffixes in $sa$ to compare the two substrings, that is the LCPs, indicated by their LCP-value.
+This approach can be also applied to verifying the last two conditions in Lemma~\ref{lemma:1}, but it takes at worst $\mathcal{O}(n)$ character-wise comparisons for each pair of neighboring suffixes in $sa$ to compare the two underlying substrings indicated by their LCP-value.
 
@@
 Taking into consideration the high difficulty of finding a PHF to meet this requirement, we prefer using a Karp-Rabin fingerprinting function~\cite{Karp1987} to transform a substring into its integer form, called fingerprint.
-Specifically, suppose $L$ is a prime and $\delta$ is randomly chosen from $[1, L)$, the fingerprint ${\sf fp}(i, j)$ of a substring $x[i, j]$ can be calculated according to the formulas below as following: scan $x$ rightward to iteratively compute ${\sf fp}(0, k)$ for all $k \in [0, n)$ using Formulas~\ref{formula:1}-\ref{formula:2}, record ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ during the calculation and subtract the former from the latter to obtain ${\sf fp}(i, j)$ using Formula~\ref{formula:3}.
+To be specific, suppose $L$ is a prime and $\delta$ is a number randomly chosen from $[1, L)$, the fingerprint ${\sf fp}(i, j)$ for a substring $x[i, j]$ can be calculated according to the formulas below as following: scan $x$ rightward to iteratively compute ${\sf fp}(0, k)$ for all $k \in [0, n)$ using Formulas~\ref{formula:1}-\ref{formula:2}, record ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ during the calculation and subtract the former from the latter to obtain ${\sf fp}(i, j)$ using Formula~\ref{formula:3}.
 
@@
 
-We show in Fig.~\ref{fig:example} an example for better understanding.
-Assume $L = 197$ and $\delta = 101$, lines 4-8 compute ${\sf fp}(0, p)$ iteratively according to Formulas~\ref{formula:1}-\ref{formula:2}.
-These values are used to compute the fingerprints for the target substrings.
+We close this part with an example in Fig.~\ref{fig:example} for a better understanding of computing and comparing fingerprints of substrings specified the LCP-values of neighboring suffixes in $sa$.
+Given that $L = 197$ and $\delta = 101$, lines 4-8 compute ${\sf fp}(0, p)$ iteratively according to Formulas~\ref{formula:1}-\ref{formula:2}.
+Then, lines 10-16 use these values to compute the fingerprints for target substrings.
 Consider the leftmost pair of neighboring suffixes in $sa$, that is ${\sf suf}(sa[0])$ and ${\sf suf}(sa[1])$, the substrings indicated by their LCP-value are $x[sa[0], sa[0] + lcp[1] - 1]$ and $x[sa[1], sa[1] + lcp[1] - 1]$, respectively.
-According to Formula~\ref{formula:3}, ${\sf fp}(sa[0], sa[0] + lcp[1] - 1)$ is equal to the difference between ${\sf fp}(0, sa[0])$ and ${\sf fp}(0, sa[0] + lcp[1] + 1)$, which have been calculated beforehand.
-In lines 10-12, we obtain the fingerprints for these two substrings and find that they are equal to each other.
+According to Formula~\ref{formula:3}, ${\sf fp}(sa[0], sa[0] + lcp[1] - 1)$ is equal to the difference between ${\sf fp}(0, sa[0] - 1)$ and ${\sf fp}(0, sa[0] + lcp[1] - 1)$, both of which have been calculated beforehand.
+Hence, we obtain the fingerprints for these two substrings in lines 10-12 and see that they are equal to each other.
 
-\begin{figure*}
+\begin{figure}
 	\centering
-	\label{fig:example}
-	\includegraphics[width = 0.8\textwidth]{example}
-	\caption{An Example for Computing the Fingerprints for the LCPs of the Neighboring Suffixes in SA.}	
-\end{figure*}
+
+	\includegraphics[width = 0.9\columnwidth]{example}
+	\caption{An Example for Computing and Comparing Fingerprints for Substrings Specifed by the LCP-Values of Neighboring Suffixes in SA. \label{fig:example}}	
+\end{figure}
 
@@
 
-We first describe an algorithm for checking conditions in Corollary~\ref{corollary:1} on random access models, of which the core part is to check the lexical order and LCP-value for each pair of neighboring suffixes in $sa$ on-the-fly during the scan of $sa$ and $lcp$.
+We describe an algorithm for checking the conditions in Corollary~\ref{corollary:1} on random access models, of which the core part is to check the lexical order and the LCP-value for each pair of neighboring suffixes in $sa$ on-the-fly during the scan of $sa$ and $lcp$.
 This is done by using Formulas~\ref{formula:1}-\ref{formula:3} following our discussion in the previous subsection.
-As can be seen, two zero-initialized array, namely $fp$ and $mk$, are introduced to facilitate the checking process, where $fp$ is for storing the fingerprints of prefixes and $mk$ is for determining whether or not each number of $\{0, 1, ..., n - 1\}$ is present in $sa$.
+Two zero-initialized array, namely $fp$ and $mk$, are introduced to facilitate the checking process, where $fp$ is for storing the fingerprints of all the prefixes in $x$ and $mk$ is for checking whether or not each number of $\{0, 1, ..., n - 1\}$ is present in $sa$.
 
@@
 Assume that $x$, $sa$ and $lcp$ are stored in external memory, we design Algorithm~\ref{alg:1} for conducting these I/O operations in a disk-friendly way.
-The main idea is to first sort data in the order that they are visited and then access them by sequential reads and writes.
-To the end, our algorithm first scans $sa$ and $lcp$ to produce $ST_1, ST_2, ST_3$ and sorts their tuples by 1st component in ascending order at the very beginning (lines~\ref{alg:1:a}-\ref{alg:1:b}).
+The main idea is to sort data in the order that they are visited and then access them by sequential reads and writes.
+For the purpose, Algorithm~\ref{alg:1} first scans $sa$ and $lcp$ to produce $ST_1, ST_2, ST_3$ and sorts their tuples by 1st component in ascending order at the very beginning (lines~\ref{alg:1:a}-\ref{alg:1:b}).
 Afterward, it iteratively computes the fingerprints of all the prefixes according to Formulas~\ref{formula:1}-\ref{formula:2} and assigns them to the sorted tuples as following (lines~\ref{alg:1:c}-\ref{alg:1:d}): when figuring out ${\sf fp}(0, i - 1)$, extract each tuple $e$ with $e.1st = i$ from $ST_1/ST_2/ST_3$, update $e$  with ${\sf fp}(0, i - 1)$, and then forward $e$ to $ST_1'/ST_2'/ST_3'$.
-Because the 1st component of the tuples in $ST_1$ constitute a copy of $sa$, the algorithm can check condition (1) in lines~\ref{alg:1:h}-\ref{alg:1:i} when scanning them in the sorted order.
-Finally, it sorts the updated tuples back to their original order (line~\ref{alg:1:e}) and visits them  sequentially to check conditions (2)-(3) following the same way of S2.
+Because the 1st components of the tuples in $ST_1$ constitute a copy of $sa$, the algorithm can check condition (1) in lines~\ref{alg:1:h}-\ref{alg:1:i} when scanning them in their sorted order.
+Finally, it sorts the updated tuples back to their original order~(line~\ref{alg:1:e}) and visits them  sequentially to check conditions (2)-(3) following the same way of S2~(lines~\ref{alg:1:f}-\ref{alg:1:g}).
 
@@
 
-		\For {$i \in [1, n - 1)$}{  \label{alg:1:f}
+		\For {$i \in [1, n)$}{  \label{alg:1:f}
 
@@
 This method can answer the question in constant time, but it is space-consuming and
-impractical to use when the table is bigger than the memory bank capacity.
+impractical to use if the table size exceeds the memory bank capacity.
 We provide another method that returns the answer in $\mathcal{O}(\lceil \log2^n \rceil)$ time using $\mathcal{O}(\lceil \log2^n \rceil)$ internal memory space.
-Specifically, suppose $e$ is an integer from $[0, n)$, it can be decomposed into the form of $\Sigma_{i = 0}^{\lceil \log2^n \rceil}{k_i \cdot 2^i}$, where $k_0, k_1, ..., k_{\lceil \log2^n \rceil}$ are determined by performing at most $\lceil \log2^n \rceil$ divisions.
-Hence, we have $\delta^e = \Pi_{i = 0}^{\lceil \log2^n \rceil}{\delta}^{k_i \cdot 2^i}$ by replacing $e$ with its decomposition, where the expression on the right side of the equation can be easily computed with $\{{\delta}^{1}, {\delta}^{2}, \dots, {\delta}^{2^{\lceil \log2^n \rceil}} \}$ already known.
+Specifically, suppose $e$ is an integer from $[0, n)$, it can be decomposed into the form of $\Sigma_{i = 0}^{\lceil \log2^n \rceil}{k_i \cdot 2^i}$, where $k_0, k_1, ..., k_{\lceil \log2^n \rceil}$ are computed by performing at most $\lceil \log2^n \rceil$ divisions.
+Thereby, we have $\delta^e = \Pi_{i = 0}^{\lceil \log2^n \rceil}{\delta}^{k_i \cdot 2^i}$ by replacing $e$ with its decomposition, where the expression on the right side of the equation can be easily computed with $\{{\delta}^{1}, {\delta}^{2}, \dots, {\delta}^{2^{\lceil \log2^n \rceil}} \}$ already known.
 
@@
 Given an external memory model with RAM size $M$, disk size $D$ and block size $B$, all are in words, the time and I/O complexities for each scan are $\mathcal{O}(n)$ and $\mathcal{O}(n / B)$, respectively, while those for each sort are $\mathcal{O}(n\log_{M/ B}(n / B))$ and $\mathcal{O}((n / B)\log_{M / B}(n / B))$, respectively~\cite{Arge2013}.
-This algorithm reaches its peak disk use when sorting tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}.
-A trick for reducing	the space requirements is to compute the fingerprints of prefixes specified in $ST_1$, $ST_2$ and $ST_3$, respectively.
-However, our experimental study in Section~\ref{sec:experiment} shows that Algorithm~\ref{alg:1} is still rather space hungry, its peak disk use is 40 bytes per input character.
-In the next section, we will describe an alternative checking method based on the induced-sorting principle.
-Compared with Algorithm~\ref{alg:1}, the program for our algorithm designed by this method only takes half space on real-world datasets.
+Clearly, this algorithm reaches its peak disk use when sorting tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}.
+The experimental study in Section~\ref{sec:experiment} indicatse that our program for Algorithm~\ref{alg:1} is rather space consuming, its peak disk use reaches 40 bytes per input character.
 
@@
 
-We introduce some symbols and notations used in the following presentation.
+In this part, we describe an alternative checking method based on the induced sorting principle.
+Compared with Algorithm~\ref{alg:1}, our program for the algorithm designed by this method only takes half space on real-world datasets.
+Before the presentation, we introduce some symbols and notations used in the following paragraphs.
 
@@
 In detail, $x[i]$ is L-type if (1) $i = n - 1$ or (2) $x[i] > x[i + 1]$ or (3) $x[i] = x[i + 1]$ and $x[i + 1]$ is L-type; otherwise, $x[i]$ is S-type.
-Further, if $x[i]$ and $x[i + 1]$ are respectively S- and L-type, then $x[i]$ is also an S*-type character.
+Further, if $x[i]$ and $x[i + 1]$ are separately S-type and L-type, then $x[i]$ is also an S*-type character.
 Moreover, a suffix is L-, S- or S*-type if its heading character is L-, S-, or S*-type, respectively.
@@
 
+{\em Type Array.} The array $t$ records in $t[i]$ the type information of $x[i]$, where $t[i] = 1$ or $0$ if $x[i]$ is S-type or L-type, respectively.
+
 \subsection{Idea} \label{sec:method2:idea}
 
-The induced sorting principle has been employed to invent efficient algorithms for constructing suffix and LCP arrays on both internal and external memory models.
-These algorithms mainly consist of a reduction phase for computing $sa^*$ and $lcp^*$, followed by an induction phase for inducing $sa$ and $lcp$ from $sa^*$ and $lcp^*$.
-Given that $sa^*$ and $lcp^*$ are already known, we can directly construct the suffix and LCP arrays by calling the inducing process of any existing IS-based construction algorithm.
-This enlightens us to design a checker following Lemma~\ref{lemma:2}.
+The induced sorting principle has been extensively used to design efficient algorithms for constructing the suffix and LCP arrays on internal and external memory models.
+An IS-based construction algorithm mainly consists of a reduction phase for computing $sa^*$ and $lcp^*$, followed by an induction phase for inducing $sa$ and $lcp$ from $sa^*$ and $lcp^*$~\footnote{In the interest of completeness, we give an overview of the induction phase in Appendix~\ref{sec:appendix}.}.
+Given that $sa^*$ and $lcp^*$ are already known, we can produce the final suffix and LCP arrays by calling the inducing process of an existing construction algorithm.
+This enlightens us to design a checker based on Lemma~\ref{lemma:2}.
 
@@
 Similar to Method A, we can employ the fingerprinting technique to probablistically check the correctness of $sa^*$ and $lcp^*$.
-Based on this idea, we describe in the subsequent paragraphs an external-memory algorithm for checking the conditions in Corollary~\ref{corollary:2}.
+Based on this idea, we describe in the next subsection an external-memory algorithm for checking the conditions in Corollary~\ref{corollary:2}.
 
@@
 The first step of Algorithm~\ref{alg:2} is to compute and verify $sa^*$ and $lcp^*$.
-According to the definition, $sa^*$ can be produced by sequentially retrieving the S*-type suffixes from $sa$ while the LCP-value of two successive S*-type suffixes in $sa$, say ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$, is equal to the minimal of $\{lcp[i + 1], ..., lcp[j - 1], lcp[j]\}$.
+According to their definitions, $sa^*$ can be produced by sequentially retrieving the S*-type suffixes from $sa$ and the LCP-value of two successive S*-type suffixes in $sa$, say ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$, is equal to the minimal of $\{lcp[i + 1], ..., lcp[j - 1], lcp[j]\}$.
 Hence, the proposed algorithm first sorts all the suffixes in $sa$ by their starting positions~(lines~\ref{alg:2:a}-\ref{alg:2:b}) and then scans $x$ only once to pick out the S*-type suffixes~(lines~\ref{alg:2:c}-\ref{alg:2:d}).
 After that, it puts these S*-type suffixes back in their lexical order and outputs them one by one to generate $sa^*$~(lines~\ref{alg:2:g}-\ref{alg:2:h}).
-Meanwhile, it calculates the LCP-value for each pair of neighboring suffixes in $sa^*$ by tracing the minimal over an interval of $lcp$ specified by the two suffixes.
+Meanwhile, it calculates the LCP-value for each pair of the neighboring suffixes in $sa^*$ by tracing the minimal over the $lcp$ interval indicated by the two suffixes.
 Notice that, we check condition (1) in Corollary~\ref{corollary:2} during the time when visiting the suffixes in position order (lines~\ref{alg:2:e}-\ref{alg:2:f}) and conditions (2)-(3) by calling Algorithm~\ref{alg:1} with $sa^*$ and $lcp^*$ as input.
-Suppose $sa^*$ and $lcp^*$ are both correct, then Algorithm~\ref{alg:1} invokes the inducing process of an existing construction algorithm to induce $sa'$ and $lcp'$, which are a copy of the final suffix and LCP arrays, from the two verified arrays~(line~\ref{alg:2:k}) and literally compares them with $sa$ and $lcp$ to complete the whole checking process~(lines~\ref{alg:2:l}-\ref{alg:2:m}).
+Suppose $sa^*$ and $lcp^*$ are both correct, then Algorithm~\ref{alg:2} invokes the inducing process of an existing construction algorithm to induce $sa'$ and $lcp'$, which are a copy of the final suffix and LCP arrays, from the two verified arrays~(line~\ref{alg:2:k}) and literally compares them with $sa$ and $lcp$ to complete the whole checking process~(lines~\ref{alg:2:l}-\ref{alg:2:m}).
 
-\begin{algorithm*}
+\begin{algorithm*}[!htbp]
 
@@
 Specifically, when a suffix/LCP item $v_1$ is induced into a bucket, we check if it is equal to the corresponding item $v_2$ in $sa/lcp$.
-If $v_1 = v_2$, then $v_2$ is correct and we can further use it to induce the lexical order and LCP-value of its preceding suffix later.
-The key point here is how to retrieve items from $sa/lcp$ quickly.
-This can be done by performing sequential I/O operations when we provide a read pointer together with a buffer for each suffix/LCP sub-bucket.
-We show more details of the adapted inducing process as below, where $c \in [0, \Sigma)$ and $lp_1/lp_2$ and $sp_1/sp_2$ are read pointer arrays for retrieving items from the L-type/S-type sub-buckets in $sa$ and $lcp$.
+If $v_1 = v_2$, then $v_2$ is correct and we further use this value to induce the remaining suffix/LCP items.
+The key point here is to retrieve items from $sa/lcp$ quickly.
+This can be done by conducting sequential I/O operations if we provide a read pointer together with a buffer for each suffix/LCP sub-bucket.
+We describe below more details of the adapted inducing process, where $lp_1/lp_2$ and $sp_1/sp_2$ are file pointer arrays for reading items from the sub-buckets of $sa$ and $lcp$.
 
@@
 		\item 
-		Let $lp_1[c]$ and $lp_2[c]$ point to the leftmost items of ${\sf sa\_bkt_L}(c)$ and ${\sf lcp\_bkt_L}(c)$, respectively.
+		Let $lp_1[c]$ and $lp_2[c]$ point to the leftmost items of ${\sf sa\_bkt_L}(c)$ and ${\sf lcp\_bkt_L}(c)$, for $c \in [0, \Sigma)$.
 		\item 
-		Scan $sa/lcp$ rightward to induce L-type suffixes and their LCP-values.
-For each induced suffix $p$ (with a heading character $c_0$) and its LCP-value $q$: (1) check if $p = lp_1[c_0]$ and $q = lp_2[c_0]$; (2) let $lp_1[c_0]$ and $lp_2[c_0]$ point to the next items on the right side.
+		Scan $sa$ and $lcp$ rightward to induce L-type suffixes and their LCP-values.
+For each induced suffix $p$ (with a heading character $c_0$) and its LCP-value $q$: (1) check if $p = lp_1[c_0]$ and $q = lp_2[c_0]$; (2) move $lp_1[c_0]$ and $lp_2[c_0]$ to the next items on the right.
 	\end{enumerate}
@@
 		\item 	
-		Let $sp_1[c]$ and $sp_2[c]$ point to the rightmost items of ${\sf sa\_bkt_S}(c)$ and ${\sf lcp\_bkt_S}(c)$, respectively.
+		Let $sp_1[c]$ and $sp_2[c]$ point to the rightmost items of ${\sf sa\_bkt_S}(c)$ and ${\sf lcp\_bkt_S}(c)$, for $c \in [0, \Sigma)$.
 		\item 	
-		Scan $sa/lcp$ leftward to induce S-type suffixes and their LCP-values.
-For each induced suffix $p$ (with a heading character $c_0$) and its LCP-value $q$: (1) check if $p = sp_1[c_0]$ and $q = sp_2[c_0]$; (2) let $sp_1[c_0]$ and $sp_2[c_0]$ point to the next items on the left side.
+		Scan $sa$ and $lcp$ leftward to induce S-type suffixes and their LCP-values.
+For each induced suffix $p$ (with a heading character $c_0$) and its LCP-value $q$: (1) check if $p = sp_1[c_0]$ and $q = sp_2[c_0]$; (2) move $sp_1[c_0]$ and $sp_2[c_0]$ to the next items on the left.
 	\end{enumerate}
@@
 
-Algorithm~\ref{alg:2} mainly consists of two parts, where the first part for checking $sa^*$ and $lcp^*$ can be implemented within sorting complexity and the second part for checking $sa$ and $lcp$ can be implemented in linear time under the condition that $|\Sigma| = \mathcal{O}(1)$.
-As demonstrated in Section~\ref{alg:2}, the peak disk use of our program for Algorithm~\ref{alg:2} is around 20n and it has a similar performance compared to that for Algorithm~\ref{alg:1} in terms of time and I/O volume.
+Algorithm~\ref{alg:2} mainly consists of two parts, where the first part for checking $sa^*$ and $lcp^*$ can be implemented within sorting complexity and the second part for checking $sa$ and $lcp$ can be implemented in linear time under the condition that $\|\Sigma\| = \mathcal{O}(1)$.
+As demonstrated in Section~\ref{alg:2}, the peak disk use of our program for Algorithm~\ref{alg:2} is around 21n and it has a better peformance than that for Algorithm~\ref{alg:1} in terms of time and I/O volume.
 
@@
 
-The experimental platform is a work station equipped with an Intel Xeon E3-1220 V2 CPU, 4GiB RAM and 500GiB HD.
-To achieve high I/O efficiency, the algorithms proposed in the previous sections are implemented using the external-memory containers provided by the STXXL library~\cite{Dementiev2007}.
-Our programs are compiled by gcc/g++ 4.8.4 with -O3 options under ubuntu 14.04 64-bit operating system.
-For analysis, we evaluate the performance on real-world datasets listed in Table~\ref{tbl:1} by investigating the following three measurements normalized by the size of input string:
+For implementation simplicity, our programs for the algorithms proposed in the previous sections use the external-memory containers provided by the STXXL library~\cite{Dementiev2007} to manage read/write operations on disks.
+We make a performance evaluation by running our programs on the real-world coropora listed in Table~\ref{tbl:1}, where three measurements normalized by the size of input string are investigated:
 
@@
 
-	\item RT: running time, in nanoseconds. Measured using the Linux 'time' command.
+	\item RT: running time, in microseconds.
 
@@
 \end{itemize}
+
+The experimental platform is a work station equipped with an Intel Xeon E3-1220 V2 CPU, 4GiB RAM and 500GiB HD.
+All the programs are compiled by gcc/g++ 4.8.4 with -O3 options under ubuntu 14.04 64-bit operating system.
+In what follows, we denote the programs for Algorithms~\ref{alg:1} and~\ref{alg:2} by "ProgA" and "ProgB", respectively.
 
@@
 
-Fig.~\ref{fig:cmp1} demonstrates the performance comparison between the programs for Algorithms~\ref{alg:1} and~\ref{alg:2}. As depicted,
+Fig.~\ref{fig:performance_analysis} illustrates the performance comparison of ProgA and ProgB on different datasets, where "enwiki\_8g" consists of the leftmost 8 Gi characters extracted from "enwiki".
+As depicted, ProgB runs slower than the latter by 20 percent.
+The speed gap between them is mainly due to the difference in their I/O performances.
+Specifically, the I/O volume of ProgB keeps at $155n$ for all the three datasets, while that of ProgA rises up to nearly $200n$ on average.
+Besides, the peak disk use of ProgB is about $26/40=0.65$ as ProgA.
+This can be explained as following.
+Recall that Algorithm~\ref{alg:2} invokes Algorithm~\ref{alg:1} to check the suffix and LCP arrays for the S*-type suffixes.
+Because at most one out of every two successive characters in the input string is S*-type, the consumption for checking the suffix and LCP arrays of S*-type suffixes in ProgB is expected to be half as that for checking the given arrays in ProgA.
+To make a deep insight, we collect in Table~\ref{tbl:2} the performance overhead of ProgB and ProgA when checking the suffix and LCP arrays of S*-type and all the suffixes, respectively.
+As can be observed, the mean ratio of the number of S*-type suffixes to the number of all the suffixes is around 0.30 for the datasets under investigation, while the mean ratios of time, space and I/O volume for checking $sa^*$ and $lcp^*$ to that for checking $sa$ and $lcp$ are 0.38, 0.57 and 0.60, respectively.
 
-The speed gap between them is mainly due to the difference in their I/O efficiencies.
-Specifically, the I/O volume of ProgB is 190$n$ in average, while that of ProgA is kept at 155$n$ for different corpora.
-Notice that, although Algorithm~\ref{alg:3} reuses Algorithm~\ref{alg:1} to check $sa_{\sf LMS}$ and $lcp_{\sf LMS}$, the consumption for the verification of $sa_{\sf LMS}$ and $lcp_{\sf LMS}$ in ProgB is at most half of ProgA because the number of LMS suffixes is no more than $\frac{1}{2}n$.
-It can be also observed that both programs are insensitive to the input corpus in terms of the space requirement.
-In details, the peak disk uses of ProgA and ProgB are respectively 26$n$ and 40$n$ on the three corpora.
-
-We also investigate the performance trend of the two programs on the prefix of "enwiki" with the length varying on $\{1, 2, 4, 8\}$ GiB.
-Figure~\ref{fig:performance_analysis2} illustrates that, as the prefix length increases, a performance degradation occurs to ProgB in both time and I/O efficiencies, but the fluctuation of ProgA can be ignored.
+The above phenomenon indicates that ProgB reaches its peak disk use when checking the final suffix and LCP arrays during the inducing process.
+For a further study, we adapt Algorithm~\ref{alg:2} by adopting the space optimization scheme discussed in Section~\ref{sec:method2:algorithm} and evaluate the tuned program, called ProgB+, in comparison with ProgA and ProgB.
+As shown in Fig.~\ref{fig:performance_analysis}, the maximum space requirement for ProgB+ is around 21n, which is much less than that of ProgB and only half as that of ProgA.
+In addition, progB+ outperforms its prototype with respect to time and I/O efficiency and it achieves a higher speed against ProgA when handling "proteins".
+We also investigate the performance trend of the three programs on the prefix of "enwiki" with the length varying in $\{1, 2, 4, 8\}$ GiB.
+In Figure~\ref{fig:performance_analysis2}, the maximum disk space for each program remains unchanged with different length of prefixes but the speed of them become slower as the prefix length increases.
+This is mainly caused by the performance degradation of the external memory sorter in our programs.
+As shown in Table~\ref{tbl:2}, ProgB+ keeps the I/O volume for checking $sa^*$ and $lcp^*$ around $90n$ when the prefix length of "enwiki" varies from $1$ to $8$ GiB, but their running time sharly rises from $1.05$ to $1.33$.
 
@@
 		\label{subfig:pdu_cmp}
-		\includegraphics[width = 0.8\columnwidth]{pdu_cmp}
+		\includegraphics[width = 0.95\columnwidth]{pdu_cmp}
 	}
@@
 		\label{subfig:iov_cmp}
-		\includegraphics[width = 0.8\columnwidth]{io_cmp}
+		\includegraphics[width = 0.95\columnwidth]{io_cmp}
 	}
@@
 		\label{subfig:ct_cmp}
-		\includegraphics[width = 0.8\columnwidth]{ct_cmp}
+		\includegraphics[width = 0.95\columnwidth]{ct_cmp}
 	}
-	\caption{Experimental results for various corpora.}
+	\caption{Performance of ProgA, ProgB and ProgB+ for different corpora.}
 	\label{fig:performance_analysis}
@@
 		\label{subfig:pdu_cmp2}
-		\includegraphics[width = 0.8\columnwidth]{pdu_cmp2}
+		\includegraphics[width = 0.95\columnwidth]{pdu_cmp2}
 	}
@@
 		\label{subfig:iov_cmp2}
-		\includegraphics[width = 0.8\columnwidth]{io_cmp2}
+		\includegraphics[width = 0.95\columnwidth]{io_cmp2}
 	}
@@
 		\label{subfig:ct_cmp2}
-		\includegraphics[width = 0.8\columnwidth]{ct_cmp2}
+		\includegraphics[width = 0.95\columnwidth]{ct_cmp2}
 	}
-	\caption{Experimental results for prefixes of "enwiki".}
+	\caption{Performance of ProgA, ProgB and ProgB+ for prefixes of "enwiki".}
 	\label{fig:performance_analysis2}
@@
 
-	\subsection{Discussion}
+%Table
+\renewcommand\arraystretch{1.3}
+\begin{table*}[!t]
+	\caption{Performance comparison between checking the suffix and LCP arrays of S*-type suffixes and that of all the suffixes}
+	\label{tbl:2}
+	\centering
+	\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|}
+		\hline
+		\multirow{2}{*}{dataset} & \multicolumn{3}{|c|}{\#} & \multicolumn{3}{|c|}{PDU} & \multicolumn{3}{|c|}{IOV} & \multicolumn{3}{|c|}{RT} \\\cline{2-13}
+						 & S*-type & all & ratio & S*-type & all & ratio & S*-type & all & ratio & S*-type & all & ratio \\\hline
+		enwiki\_1g & 329810376 & 1073741824 & 0.31 & 15.67 & 40 & 0.39 & 89.94 & 155 & 0.58 & 1.05 & 1.70 & 0.62 \\\hline
+		enwiki\_2g & 650901939 & 2147483648 & 0.30 & 15.41 & 40 & 0.39 & 89.18 & 155 & 0.58 & 1.22 & 1.85 & 0.66 \\\hline
+		enwiki\_4g & 1301327878 & 4294967296 & 0.30 & 15.45 & 40 & 0.39 & 89.14 & 155 & 0.58 & 1.19 & 1.89 & 0.63 \\\hline
+		enwiki\_8g & 2586471839 & 8589934592 & 0.30 & 15.35 & 40 & 0.38 & 88.80 & 155 & 0.57 & 1.33 & 2.14 & 0.62 \\\hline	
+		uniprot & 829262945 & 3028811776 & 0.27 & 13.94 & 40 & 0.35 & 83.80 & 155 & 0.54 & 1.04 & 2.26 & 0.46 \\\hline
+		proteins & 379092002 & 1184366592 & 0.32 & 16.21 & 40 & 0.41 & 92.29 & 155 & 0.60 & 1.14 & 1.85 & 0.62	\\\hline
+		mean & 1012811163 & 3189156522 & 0.30 & 15.34 & 40 & 0.38 & 88.86 & 155 & 0.57 & 1.16 & 1.95 & 0.60 \\\hline
+	\end{tabular}
+\end{table*}
 
-	It is identified that both programs heavily rely on the performance of the external memory sorter in use.
+%It is identified that both programs heavily rely on the performance of the external memory sorter in use.
 A potential candidate for improving their speed is to adapt a GPU-based multi-way sorter~(e.g.,~\cite{Leischner2010, Davidson2012}) for sorting massive data using external memory.
@@
 
-	Currently, for Algorithm~\ref{alg:3}, step 2 constitutes the space bottleneck.
+%Currently, for Algorithm~\ref{alg:3}, step 2 constitutes the space bottleneck.
 It is worthy of mentioning that this step produces a copy of the suffix and LCP array during the inducing and checking processes.
@@
 
+\subsection{Discussion} \label{sec:discussion}
+
+currently, the fastest  The fastest xxx
+
+There are still many ways to enhance the performance of our programs.
+Firstly, it is observed from Section~\ref{sec:experiment} that our programs suffer from a bottleneck when sorting massive data in external memory.
+For implementation simplicity, we currently employ the containers provided by the STXXL library to perform the sorting task.
+Benefiting from the high-performance radixsort in GPUs, it is potential to design a specific sorter to speed up the sorting process in our programs.
+Secondly, Method B checks the suffix and LCP arrays following the induced sorting principle.
+Unfortunately, the existing IS-based construction algorithms are not capable of fully use the available computation resources.
+At the time of writing this paper, the authors are dedicated to designing IS-based parallel algorithms capable of running in the context of multi-core CPU and/or GPU computation environments.
+This research may also improve the implementation design of our checking algorithms.
+
 \section{Conclusions} \label{sec:conclusion}
 
-In this article, we propose two methods for probablistically checking the give suffix and LCP arrays using external memory.
-According to the experimental results, our program for Method A has a better performance than that for Method B with respect to the running time and I/O volume by about 20 percent, while the peak disk use of the latter is about 26/40=0.65 as that of the former and can be further reduced to around 21n without a sacrifice in the time and I/O effciency.
-We think these two methods could potentially be a xxxx .
+In this paper, we propose two methods for probablistically checking the given suffix and LCP arrays in external memory.
+As observed from the experiments, our programs for the algorithms designed by Methods A and B have a better performance than eSAIS in terms of time, space and I/O volume.
+Besides, ProgA runs faster than ProgB on various real-world datasets, but the peak disk use of the latter is smaller and can be further reduced to half as that of the former without a sacrifice in time and I/O efficiency.
+
+\appendices
+\section{Overview on the Induction Phase} \label{sec:appendix}
+
+The lexical order of two suffixes starting with $x[i]$ and $x[j]$ can be determined by sequentially comparing their characters until finding a position $k$ such that $x[i, i + k) = x[j, j + k)$ and $x[i + k] \ne x[j + k]$.
+In other words, we have ${\sf suf}(i) < {\sf suf}(j)$ if (1) $x[i] < x[j]$~$(k = 0)$ or (2) $x[i] = x[j]$ and ${\sf suf}(i + 1) < {\sf suf}(j + 1)$~$(k > 0)$; otherwise, ${\sf suf}(i) > {\sf suf}(j)$.
+This rule is used by the IS-based SA construction algorithms to sort suffixes during the induction phase:
+
+\begin{enumerate}[S1]
+	\item 
+	Clear S-type sub-buckets in $sa$. Scan $sa^*$ leftward and insert each element into current rightmost empty position in the corresponding S-type sub-bucket.
+
+	\item 
+	Clear L-type sub-buckets in $sa$ and insert $n - 1$ into the leftmost position in ${\sf sa\_bkt_L}(x[n - 1])$.
+Scan $sa$ rightward with $i$ increasing from $0$ to $n - 1$.
+For each scanned non-empty $sa[i]$ with $t[sa[i] - 1] = 0$, insert $sa[i] - 1$ into current leftmost empty position in ${\sf sa\_bkt_L}(x[sa[i] - 1])$.
+
+	\item
+	Clear S-type sub-buckets in $sa$.
+Scan $sa$ leftward with $i$ decreasing from $n - 1$ to $0$.
+For each scanned non-empty $sa[i]$ with $t[sa[i] - 1] = 1$, insert $sa[i] - 1$ into current rightmost empty position in ${\sf sa\_bkt_S}(x[sa[i] - 1])$.
+
+\end{enumerate}
+
+In brief, assume $sa^*$ is already known, S1 inserts all the S*-type suffixes into $sa$ in their lexical order.
+Then, S2-S3 induce the order of L-type and S-type suffixes from those already sorted in $sa$, respectively, where the relative order of two suffixes induced into the same sub-bucket matches their insertion order according to the rule stated above.
+To be more specific, we show in Fig.~\ref{fig:example2} a running example of the induction phase.
+
+As depicted, the input string $x$ contains 6 S*-type suffixes sorted in line 3.
+When finished inserting the S*-type suffixes in lines 5-6, we first find the head of each L-type sub-bucket (marked by the symbol $\wedge$) and insert ${\sf suf}(13)$ into $sa$.
+Notice that ${\sf suf}(13)$ consists of only one character, it must be the smallest L-type suffixes starting with $1$.
+Thus, we put ${\sf suf}(13)$ into the leftmost position in ${\sf sa\_bkt_L}(1)$ in line 8.
+Then, we scan $sa$ from left to right for inducing the order of all the L-type suffixes.
+In lines 10-11, when visiting $sa[0] = 13$ (marked by the symbol $@$), we check the type array $t$ to find $x[12] = 2$ is L-type and hence insert ${\sf suf}(12)$ into current leftmost empty position in $sa\_bkt_L(2)$.
+Similarly, in lines 12-13, we visit the next scanned item $sa[1] = 11$ and see that $t[10] = 0$, thus we place ${\sf suf}(10)$ into the current head of $sa\_bkt_L(3)$.
+Following this way, we get all the L-type suffixes sorted in $sa$.
+After that, we first find the end of each S-type sub-bucket in lines 25-26 and scan $sa$ leftward for inducing the order of all the S-type suffixes in lines 27-40.
+When visiting $sa[13] = 2$, we see $x[1]$ is S-type and thus put ${\sf suf}(1)$ into current rightmost empty position in $sa\_bkt_S(1)$.
+Then, at $sa[12] = 8$, we see $x[7] = 1$ is S-type and thus put ${\sf suf}(7)$ into current rightmost empty position in $sa\_bkt_S(1)$.
+To repeat scanning $sa$ in this way, we get all the S-type suffixes sorted in $sa$.
+
+The work presented in~\cite{Fischer11} describes how to compute the LCP array during the execution of S2-S3.
+Given two suffixes placed at the neighboring positions in $sa$, their LCP-value can be computed according to one of the following two cases with regard to whether or not they are inserted into the same sub-bucket: if yes, then the LCP-value of them is one greater than that of the two suffixes from which inducing them; otherwise, the LCP-value of them is equal to zero.
+In this way, we can determine $lcp[i]$ immediately after the computation of $sa[i]$.
+The problem here is how to obtain the LCP-value of these inducing suffixes, which is modeled as a range minimum query in~\cite{Fischer11} and can be easily answered within $\mathcal{O}(1)$ time using $\mathcal{O}(\|\Sigma\|)$ space.
+To be specific, when scanning from $sa[0]$ to $sa[5]$ in lines 10-21 of Fig.~\ref{fig:example2}, we induce ${\sf suf}(12)$ and ${\sf suf}(6)$ into the neighboring positions in ${\sf sa\_bkt_L(2)}$.
+During the scan, if we keep recording the minimal of $lcp(0, 5]$ in a variable, then we can obtain the LCP-value of the inducing suffixes ${\sf suf}(13)$ and ${\sf suf}(5)$ from the variable when inducing ${\sf suf}(6)$ into $sa$.
+
+\begin{figure}
+	\centering
+	\includegraphics[width = 0.9\columnwidth]{example2}
+
+	\caption{An Example for Computing the suffix and LCP arrays during the Induction Phase. \label{fig:example2}}	
+\end{figure}
 
@@
 in greater detail
+
+in the  order received
+
+build up a whole new thing from scratch
+
+In the interest of completeness, we briefly discuss the date and time formatting options of the printf method
+
+immediately follow
+
+preceding statement
+
+tuned version
+
+hang on to the object
+
+track down
+
+invisible to the remainder of the program
+
+put it another way

### 2017-03-01 draft/draft.tex
2017/03/01

@@
 From then on, much more effort has been put on designing efficient constructors for suffix array~(SA) on different memory models~\cite{Karkkainen2003, Ko2003, Kim2003, Nong11, Dementiev2008, Ferragina2012, Manzini2004, Bingmann12, Karkkainen2014, Nong14, Nong15}.
-In respect of the research on LCP array construction algorithms, the existing works can be classified into two categories with regard to their input requirements, where the algorithms from the first category compute both suffix and LCP arrays at the same time with the original text only~\cite{Fischer11, Bingmann12, Flick2015} and those from the second category carry out the computation by taking SA and/or Burrows-Wheeler transform (BWT) as additional input~\cite{Kasai2001,Karkkainen2009, Fischer11, Puglisi2008, Puglisi2008, Deo2013}.
+In respect of the research on LCP array construction algorithms, the existing works can be classified into two categories with regard to their input requirements, where the algorithms from the first category compute both suffix and LCP arrays at the same time with the original text only~\cite{Fischer11, Bingmann12, Flick2015} and those from the second category carry out the computation by taking SA and/or Burrows-Wheeler transform (BWT) as additional input~\cite{Kasai2001,Karkkainen2009, Fischer11, Puglisi2008, Deo2013}.
 Among all, the algorithms designed by the induced sorting~(IS) principle take linear time and space to run and outperform previous arts on both internal and external memory models~\cite{Nong11, Karkkainen2014}.
@@
 
-Our contribution mainly includes two methods to probablistically verify the given suffix and LCP arrays.
+Our contribution mainly includes two methods to probabilistically verify the given suffix and LCP arrays.
 Method A checks the lexical order and the LCP-value of two neighboring suffixes in SA by literally comparing the characters of their LCPs in pairs.
@@
 When implemented in external memory, it suffers from a space bottleneck owing to the large disk volume taken by each sort.
-To overcome the drawback, Method B first employs the fingerprinting technique to check a subset selected from the given suffix and LCP arrays, then it reuses the inducing process of an IS-based algorithm to produce the final suffix and LCP arrays from the verified subset and literally compares them with the input arrays to ensure the correctness of the latter.
+To overcome the drawback, Method B first employs the fingerprinting technique to check a subset selected from the given suffix and LCP arrays, then it reuses the inducing process of an IS-based construction algorithm to produce the final suffix and LCP arrays from the verified subset and literally compares them with the input arrays to ensure the correctness of the latter.
 Our experiments indicate that the peak disk use of the program for the algorithm designed by Method B is only half as that of the program for the algorithm designed by Method A.
@@
 
-We close this part with an example in Fig.~\ref{fig:example} for a better understanding of computing and comparing fingerprints of substrings specified the LCP-values of neighboring suffixes in $sa$.
+We close this part with an example in Fig.~\ref{fig:example} for a better understanding of computing and comparing the fingerprints of the substrings specified the LCP-values of lexical neighbors.
 Given that $L = 197$ and $\delta = 101$, lines 4-8 compute ${\sf fp}(0, p)$ iteratively according to Formulas~\ref{formula:1}-\ref{formula:2}.
@@
 Assume that $x$, $sa$ and $lcp$ are stored in external memory, we design Algorithm~\ref{alg:1} for conducting these I/O operations in a disk-friendly way.
-The main idea is to sort data in the order that they are visited and then access them by sequential reads and writes.
+The main idea is to sort data in the order that they are visited and then access them by sequential reads.
 For the purpose, Algorithm~\ref{alg:1} first scans $sa$ and $lcp$ to produce $ST_1, ST_2, ST_3$ and sorts their tuples by 1st component in ascending order at the very beginning (lines~\ref{alg:1:a}-\ref{alg:1:b}).
 Afterward, it iteratively computes the fingerprints of all the prefixes according to Formulas~\ref{formula:1}-\ref{formula:2} and assigns them to the sorted tuples as following (lines~\ref{alg:1:c}-\ref{alg:1:d}): when figuring out ${\sf fp}(0, i - 1)$, extract each tuple $e$ with $e.1st = i$ from $ST_1/ST_2/ST_3$, update $e$  with ${\sf fp}(0, i - 1)$, and then forward $e$ to $ST_1'/ST_2'/ST_3'$.
-Because the 1st components of the tuples in $ST_1$ constitute a copy of $sa$, the algorithm can check condition (1) in lines~\ref{alg:1:h}-\ref{alg:1:i} when scanning them in their sorted order.
+Because the 1st components of the tuples in $ST_1$ constitute a copy of $sa$, the algorithm can check condition (1) when scanning these tuples in their sorted order.
 Finally, it sorts the updated tuples back to their original order~(line~\ref{alg:1:e}) and visits them  sequentially to check conditions (2)-(3) following the same way of S2~(lines~\ref{alg:1:f}-\ref{alg:1:g}).
@@
 
-		sort tuples in $ST_1$, $ST_2$ and $ST_3$ by 2nd component.  \label{alg:1:e}
+		sort tuples in $ST_1'$, $ST_2'$ and $ST_3'$ by 2nd component.  \label{alg:1:e}
 
@@
 
-			$\hat{fp_1} = fp2 - fp1 \cdot \delta^{lcp[i]} \! \mod \! P$ \label{alg:1:j}
+			$\hat{fp_1} = fp_2 - fp_1 \cdot \delta^{lcp[i]} \! \mod \! P$ \label{alg:1:j}
 
-		 	$fp_1 := ST_1'.{\sf top}().3rd$, $fp_3 := ST_2'.{\sf top}().3rd$, $ch_2 := ST_3'.{\sf top}().4th$, $ST_3'.{\sf pop}()$
+		 	$fp_1 := ST_1'.{\sf top}().3rd$, $fp_3 := ST_3'.{\sf top}().3rd$, $ch_2 := ST_3'.{\sf top}().4th$, $ST_3'.{\sf pop}()$
 
-			$\hat{fp_2} = fp3 - fp1 \cdot \delta^{lcp[i]} \! \mod \! P$	\label{alg:1:k}
+			$\hat{fp_2} = fp_3 - fp_1 \cdot \delta^{lcp[i]} \! \mod \! P$	\label{alg:1:k}
 
@@
 This method can answer the question in constant time, but it is space-consuming and
-impractical to use if the table size exceeds the memory bank capacity.
+impractical to use if the table size exceeds the capacity of memory bank.
 We provide another method that returns the answer in $\mathcal{O}(\lceil \log2^n \rceil)$ time using $\mathcal{O}(\lceil \log2^n \rceil)$ internal memory space.
-Specifically, suppose $e$ is an integer from $[0, n)$, it can be decomposed into the form of $\Sigma_{i = 0}^{\lceil \log2^n \rceil}{k_i \cdot 2^i}$, where $k_0, k_1, ..., k_{\lceil \log2^n \rceil}$ are computed by performing at most $\lceil \log2^n \rceil$ divisions.
+Specifically, suppose $e$ is an integer from $[0, n)$, it can be broken down into the form of $\Sigma_{i = 0}^{\lceil \log2^n \rceil}{k_i \cdot 2^i}$ by performing at most $\lceil \log2^n \rceil$ divisions, where $k_0, k_1, ..., k_{\lceil \log2^n \rceil}$ are integers from $\{0, 1\}$ .
 Thereby, we have $\delta^e = \Pi_{i = 0}^{\lceil \log2^n \rceil}{\delta}^{k_i \cdot 2^i}$ by replacing $e$ with its decomposition, where the expression on the right side of the equation can be easily computed with $\{{\delta}^{1}, {\delta}^{2}, \dots, {\delta}^{2^{\lceil \log2^n \rceil}} \}$ already known.
@@
 Clearly, this algorithm reaches its peak disk use when sorting tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}.
-The experimental study in Section~\ref{sec:experiment} indicatse that our program for Algorithm~\ref{alg:1} is rather space consuming, its peak disk use reaches 40 bytes per input character.
+The experimental study in Section~\ref{sec:experiment} indicates that our program for Algorithm~\ref{alg:1} is rather space consuming, its peak disk use reaches 40 bytes per input character.
 
@@
 In detail, $x[i]$ is L-type if (1) $i = n - 1$ or (2) $x[i] > x[i + 1]$ or (3) $x[i] = x[i + 1]$ and $x[i + 1]$ is L-type; otherwise, $x[i]$ is S-type.
-Further, if $x[i]$ and $x[i + 1]$ are separately S-type and L-type, then $x[i]$ is also an S*-type character.
+Further, if $x[i]$ and $x[i + 1]$ are separately L-type and S-type, then $x[i + 1]$ is also an S*-type character.
 Moreover, a suffix is L-, S- or S*-type if its heading character is L-, S-, or S*-type, respectively.
@@
 
-Similar to Method A, we can employ the fingerprinting technique to probablistically check the correctness of $sa^*$ and $lcp^*$.
+Similar to Method A, we can employ the fingerprinting technique to probabilistically check the correctness of $sa^*$ and $lcp^*$.
 Based on this idea, we describe in the next subsection an external-memory algorithm for checking the conditions in Corollary~\ref{corollary:2}.
@@
 Notice that, we check condition (1) in Corollary~\ref{corollary:2} during the time when visiting the suffixes in position order (lines~\ref{alg:2:e}-\ref{alg:2:f}) and conditions (2)-(3) by calling Algorithm~\ref{alg:1} with $sa^*$ and $lcp^*$ as input.
-Suppose $sa^*$ and $lcp^*$ are both correct, then Algorithm~\ref{alg:2} invokes the inducing process of an existing construction algorithm to induce $sa'$ and $lcp'$, which are a copy of the final suffix and LCP arrays, from the two verified arrays~(line~\ref{alg:2:k}) and literally compares them with $sa$ and $lcp$ to complete the whole checking process~(lines~\ref{alg:2:l}-\ref{alg:2:m}).
+Suppose $sa^*$ and $lcp^*$ are both correct, then Algorithm~\ref{alg:2} invokes the inducing process of an existing IS-based construction algorithm to induce $sa'$ and $lcp'$, which are a copy of the final suffix and LCP arrays, from the two verified arrays~(line~\ref{alg:2:k}) and literally compares them with $sa$ and $lcp$ to complete the whole checking process~(lines~\ref{alg:2:l}-\ref{alg:2:m}).
 
@@
 Algorithm~\ref{alg:2} mainly consists of two parts, where the first part for checking $sa^*$ and $lcp^*$ can be implemented within sorting complexity and the second part for checking $sa$ and $lcp$ can be implemented in linear time under the condition that $\|\Sigma\| = \mathcal{O}(1)$.
-As demonstrated in Section~\ref{alg:2}, the peak disk use of our program for Algorithm~\ref{alg:2} is around 21n and it has a better peformance than that for Algorithm~\ref{alg:1} in terms of time and I/O volume.
+As will be seen from Section~\ref{sec:experiment}, the peak disk use of our program for Algorithm~\ref{alg:2} is around $21n$, while it has a better performance than that for Algorithm~\ref{alg:1} in terms of time and I/O volume.
 
@@
 For implementation simplicity, our programs for the algorithms proposed in the previous sections use the external-memory containers provided by the STXXL library~\cite{Dementiev2007} to manage read/write operations on disks.
-We make a performance evaluation by running our programs on the real-world coropora listed in Table~\ref{tbl:1}, where three measurements normalized by the size of input string are investigated:
+We make a performance evaluation by running our programs on the real-world corpora listed in Table~\ref{tbl:1}, where three measurements normalized by the size of input string are investigated:
 
@@
 
-The experimental platform is a work station equipped with an Intel Xeon E3-1220 V2 CPU, 4GiB RAM and 500GiB HD.
+The experimental platform is a work station equipped with an Intel Xeon E3-1220 V2 CPU, 4 GiB RAM and 2 TiB HD.
 All the programs are compiled by gcc/g++ 4.8.4 with -O3 options under ubuntu 14.04 64-bit operating system.
@@
 \renewcommand\arraystretch{1.3}
-\begin{table*}[!t]
-	\caption{Corpus, $n$ in Gi, 1 byte per character}
+\begin{table}[!t]
+	\caption{Corpus, $n$ in Gi, 1 byte per character.}
 	\label{tbl:1}
 	\centering
-	\begin{tabular}{|l|c|c|p{10cm}|}
+	\begin{tabular}{|l|c|c|p{5cm}|}
 		\hline
@@
 	\end{tabular}
-\end{table*}
+\end{table}
 
-\subsection{Result} \label{sec:experiments:result}
+\subsection{Result} \label{sec:experiments:results}
 
 Fig.~\ref{fig:performance_analysis} illustrates the performance comparison of ProgA and ProgB on different datasets, where "enwiki\_8g" consists of the leftmost 8 Gi characters extracted from "enwiki".
-As depicted, ProgB runs slower than the latter by 20 percent.
+As depicted, ProgB runs slower than ProgA by around 20 percent.
 The speed gap between them is mainly due to the difference in their I/O performances.
@@
 The above phenomenon indicates that ProgB reaches its peak disk use when checking the final suffix and LCP arrays during the inducing process.
-For a further study, we adapt Algorithm~\ref{alg:2} by adopting the space optimization scheme discussed in Section~\ref{sec:method2:algorithm} and evaluate the tuned program, called ProgB+, in comparison with ProgA and ProgB.
-As shown in Fig.~\ref{fig:performance_analysis}, the maximum space requirement for ProgB+ is around 21n, which is much less than that of ProgB and only half as that of ProgA.
+By adopting the space optimization scheme introduced in Section~\ref{sec:method2:algorithm}, we adapt Algorithm~\ref{alg:2} and evaluate the tuned version of ProgB, called ProgB+, in comparison with ProgA and ProgB.
+Fig.~\ref{fig:performance_analysis} shows that the maximum space requirement for ProgB+ is about $21n$, which is much less than that of ProgB and even only half as that of ProgA.
 In addition, progB+ outperforms its prototype with respect to time and I/O efficiency and it achieves a higher speed against ProgA when handling "proteins".
 We also investigate the performance trend of the three programs on the prefix of "enwiki" with the length varying in $\{1, 2, 4, 8\}$ GiB.
-In Figure~\ref{fig:performance_analysis2}, the maximum disk space for each program remains unchanged with different length of prefixes but the speed of them become slower as the prefix length increases.
-This is mainly caused by the performance degradation of the external memory sorter in our programs.
-As shown in Table~\ref{tbl:2}, ProgB+ keeps the I/O volume for checking $sa^*$ and $lcp^*$ around $90n$ when the prefix length of "enwiki" varies from $1$ to $8$ GiB, but their running time sharly rises from $1.05$ to $1.33$.
+In Figure~\ref{fig:performance_analysis2}, the peak disk use for each program remains unchanged, but their speed become slower as the prefix length increases due to the performance degradation of the external memory sorter exploited in our programs.
+As we can see from Table~\ref{tbl:2}, ProgB+ keeps the I/O volume around $90n$ with the prefix length of "enwiki" varying from $1$ to $8$ GiB, while its running time rises from $1.05$ to $1.33$.
 
 %figure
-\begin{figure}[htbp!]
+\begin{figure}
 	\centering
@@
 		\label{subfig:pdu_cmp}
-		\includegraphics[width = 0.95\columnwidth]{pdu_cmp}
+		\includegraphics[width = 0.9\columnwidth]{pdu_cmp}
 	}
@@
 		\label{subfig:iov_cmp}
-		\includegraphics[width = 0.95\columnwidth]{io_cmp}
+		\includegraphics[width = 0.9\columnwidth]{io_cmp}
 	}
@@
 		\label{subfig:ct_cmp}
-		\includegraphics[width = 0.95\columnwidth]{ct_cmp}
+		\includegraphics[width = 0.9\columnwidth]{ct_cmp}
 	}
@@
 		\label{subfig:pdu_cmp2}
-		\includegraphics[width = 0.95\columnwidth]{pdu_cmp2}
+		\includegraphics[width = 0.9\columnwidth]{pdu_cmp2}
 	}
@@
 		\label{subfig:iov_cmp2}
-		\includegraphics[width = 0.95\columnwidth]{io_cmp2}
+		\includegraphics[width = 0.9\columnwidth]{io_cmp2}
 	}
@@
 		\label{subfig:ct_cmp2}
-		\includegraphics[width = 0.95\columnwidth]{ct_cmp2}
+		\includegraphics[width = 0.9\columnwidth]{ct_cmp2}
 	}
@@
 \renewcommand\arraystretch{1.3}
-\begin{table*}[!t]
-	\caption{Performance comparison between checking the suffix and LCP arrays of S*-type suffixes and that of all the suffixes}
+\begin{table*}
+	\caption{A performance comparison of checking the suffix and LCP arrays of S*-type suffixes to checking that of all the suffixes.}
 	\label{tbl:2}
@@
 		\hline
-		\multirow{2}{*}{dataset} & \multicolumn{3}{|c|}{\#} & \multicolumn{3}{|c|}{PDU} & \multicolumn{3}{|c|}{IOV} & \multicolumn{3}{|c|}{RT} \\\cline{2-13}
+		\multirow{2}{*}{dataset} & \multicolumn{3}{|c|}{number of suffixes} & \multicolumn{3}{|c|}{PDU} & \multicolumn{3}{|c|}{IOV} & \multicolumn{3}{|c|}{RT} \\\cline{2-13}
 						 & S*-type & all & ratio & S*-type & all & ratio & S*-type & all & ratio & S*-type & all & ratio \\\hline
@@
 
-\subsection{Discussion} \label{sec:discussion}
+The next experiment is to compare our programs with that of two solutions for building the suffix and LCP arrays as below, where either of them combines an existing suffix sorter with an LCP builder.
 
-currently, the fastest  The fastest xxx
+\begin{enumerate} [solut{i}on 1]
+	\item Use eSAIS for building SA and the sequential version of Sparse-$\phi$~\cite{Karkkainen2016} for building LCP array.
 
-There are still many ways to enhance the performance of our programs.
-Firstly, it is observed from Section~\ref{sec:experiment} that our programs suffer from a bottleneck when sorting massive data in external memory.
-For implementation simplicity, we currently employ the containers provided by the STXXL library to perform the sorting task.
-Benefiting from the high-performance radixsort in GPUs, it is potential to design a specific sorter to speed up the sorting process in our programs.
-Secondly, Method B checks the suffix and LCP arrays following the induced sorting principle.
-Unfortunately, the existing IS-based construction algorithms are not capable of fully use the available computation resources.
-At the time of writing this paper, the authors are dedicated to designing IS-based parallel algorithms capable of running in the context of multi-core CPU and/or GPU computation environments.
-This research may also improve the implementation design of our checking algorithms.
+	\item Use pSAscan~\cite{Karkkainen2015} for building SA and the parallel version of Sparse-$\phi$ for building LCP array.
+\end{enumerate}
+
+ We select eSAIS and pSAscan because they are currently the fastest sequential and parallel algorithms for SA construction.
+Also, Sparse-$\phi$ is the fastest algorithm for LCP array construction ever reported.
+A runtime breakdown of the programs for these solutions on the prefixes of "enwiki" is given in Table~\ref{tbl:3}.
+As can be seen, solution 2 is about two times faster than solution 1 and twice as fast as ProgA, which is mainly owing to the high speed of pSAscan.
+Notice that both eSAIS and the proposed checking algorithms can achieve optimal time and I/O complexity in external memory, but pSAscan and Sparse-$\phi$ are not theoretically optimal and thus have a limitation to their scalability.
+As reported in~\cite{Karkkainen2015}, when the length of input string is considerably greater than the size of internal memory, eSAIS is more quickly and I/O efficient than pSAScan.
+We can see from the same table that an increase in the time overhead occurs to pSAscan when handling the prefix containing 8 Gi characters.
+
+%Table
+\renewcommand\arraystretch{1.3}
+\begin{table*}[h]
+	\caption{A runtime comparison between the programs for the two solutions and the proposed algorithms.}
+	\label{tbl:3}
+	\centering
+	\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+		\hline
+		\multirow{2}{*}{dataset} & \multicolumn{3}{|c|}{solution 1} & \multicolumn{3}{c|}{solution 2} & \multirow{2}{*}{ProgA} & \multirow{2}{*}{ProgB+} \\\cline{2-7}
+		 & eSAIS & sequential sparse-$\phi$ & total & pSAscan & parallel sparse-$\phi$ & total & & \\\hline
+		enwiki\_1g & 2.21 & 0.61 & 2.82 & 0.39 & 0.59 & 0.98 & 1.70 & 2.54 \\\hline
+		enwiki\_2g & 2.63 & 0.53 & 3.16 & 0.47 & 0.53 & 1.00 & 1.84 & 2.51 \\\hline
+		enwiki\_4g & 2.90 & 0.63 & 3.53 & 0.59 & 0.40 & 0.99 & 1.89 & 2.56 \\\hline
+		enwiki\_8g & 3.02 & 0.63 & 3.65 & 0.83 & 0.45 & 1.28 & 2.13 & 2.79 \\\hline
+	\end{tabular}
+\end{table*}
+
+\subsection{Discussion}
+
+There are still several ways to enhance the performance of our programs.
+Firstly, it was observed that our programs suffer from a bottleneck when sorting massive data in external memory.
+For implementation simplicity, we currently use the container provided by the STXXL library to perform the sorting task without designing a specific sorter.
+It is possible to speed up the sorting process by means of the high-performance radix-sort algorithms proposed on GPU-based computation platforms.
+Secondly, Method B checks the suffix and LCP arrays using the induced sorting principle.
+Unfortunately, the existing IS-based suffix/LCP array construction algorithms are not capable of fully using the available computation resources.
+At the time of writing this paper, the authors are making research on designing IS-based algorithms for running in the context of parallel environments.
+This work may also improve the implementation design of Algorithm~\ref{alg:2}.
+
+Method A has a higher versatility compared to the existing construction algorithms, it can be employed to check any set containing one or multiple pairs of lexicographically neighboring or non-neighboring suffixes.
+This feature can be applied to various scenarios.
+For example, sometimes the consistency of a suffix/LCP array may be broken due to hardware malfunctions or human errors.
+If the backup of the corrupted data is not available and it is too time-consuming to rebuild the whole array, then we can locate the bad areas quickly by using a generalized version of Algorithm~\ref{alg:1} and restore the partial SA for each area by calling a sparse SA construction algorithm.
+Another example is to check the correctness of a sparse SA.
+Because the number of suffixes in the sparse SA is commonly much smaller than the number of suffixes in the SA, it is expected that a substantial improvement in time, space and I/O volume can be achieved when performing verification using the proposed algorithms.
 
@@
 
-In this paper, we propose two methods for probablistically checking the given suffix and LCP arrays in external memory.
-As observed from the experiments, our programs for the algorithms designed by Methods A and B have a better performance than eSAIS in terms of time, space and I/O volume.
-Besides, ProgA runs faster than ProgB on various real-world datasets, but the peak disk use of the latter is smaller and can be further reduced to half as that of the former without a sacrifice in time and I/O efficiency.
+In this paper, we propose two methods for probabilistically checking the given suffix and LCP arrays.
+Theoretically, the external-memory algorithms designed by these methods can achieve better time and I/O complexities compared to the existing fastest construction algorithms.
+Our experimental results indicate that the programs for Algorithm~\ref{alg:2} designed by Method B run slower than that for Algorithm~\ref{alg:1} designed by Method A, but they are more efficient than the latter in terms of time and I/O volume.
+As discussed in Section~\ref{sec:experiment}, there are still several ways of enhancing the performance of our programs.
+For future work, we attempt to redesign the sorting and inducing process in our implementations to make them competitive with the state-of-the-art parallel construction algorithms.
+
+From our perspective, a checker should be not only fast but also versatile.
+As a common practice, we usually check an array derived from a builder by literally comparing it with the one produced by another builder.
+However, this is not feasible in all the cases, because, for example, an algorithm for constructing infinite-order array can not be directly used to check a finite-order array and vise versa.
+On the contrary, our first method can be generalized to check the correctness of the lexical order and the LCP values of one or multiple pairs of suffixes starting at any positions of input string.
+This makes it possible to trivially adapt Algorithm~\ref{alg:1} for verifying a sparse or finite-order SA together with the corresponding LCP array.
 
@@
 
-The lexical order of two suffixes starting with $x[i]$ and $x[j]$ can be determined by sequentially comparing their characters until finding a position $k$ such that $x[i, i + k) = x[j, j + k)$ and $x[i + k] \ne x[j + k]$.
+Recall that the lexical order of two suffixes starting with $x[i]$ and $x[j]$ can be determined by sequentially comparing their characters until finding a position $k$ such that $x[i, i + k) = x[j, j + k)$ and $x[i + k] \ne x[j + k]$.
 In other words, we have ${\sf suf}(i) < {\sf suf}(j)$ if (1) $x[i] < x[j]$~$(k = 0)$ or (2) $x[i] = x[j]$ and ${\sf suf}(i + 1) < {\sf suf}(j + 1)$~$(k > 0)$; otherwise, ${\sf suf}(i) > {\sf suf}(j)$.
@@
 Then, we scan $sa$ from left to right for inducing the order of all the L-type suffixes.
-In lines 10-11, when visiting $sa[0] = 13$ (marked by the symbol $@$), we check the type array $t$ to find $x[12] = 2$ is L-type and hence insert ${\sf suf}(12)$ into current leftmost empty position in $sa\_bkt_L(2)$.
-Similarly, in lines 12-13, we visit the next scanned item $sa[1] = 11$ and see that $t[10] = 0$, thus we place ${\sf suf}(10)$ into the current head of $sa\_bkt_L(3)$.
+In lines 10-11, when visiting $sa[0] = 13$ (marked by the symbol $@$), we check the type array $t$ to find $x[12] = 2$ is L-type and hence insert ${\sf suf}(12)$ into current leftmost empty position in ${\sf sa\_bkt_L}(2)$.
+Similarly, in lines 12-13, we visit the next scanned item $sa[1] = 11$ and see that $t[10] = 0$, thus we place ${\sf suf}(10)$ into the current head of ${\sf sa\_bkt_L}(3)$.
 Following this way, we get all the L-type suffixes sorted in $sa$.
 After that, we first find the end of each S-type sub-bucket in lines 25-26 and scan $sa$ leftward for inducing the order of all the S-type suffixes in lines 27-40.
-When visiting $sa[13] = 2$, we see $x[1]$ is S-type and thus put ${\sf suf}(1)$ into current rightmost empty position in $sa\_bkt_S(1)$.
-Then, at $sa[12] = 8$, we see $x[7] = 1$ is S-type and thus put ${\sf suf}(7)$ into current rightmost empty position in $sa\_bkt_S(1)$.
+When visiting $sa[13] = 2$, we see $x[1]$ is S-type and thus put ${\sf suf}(1)$ into current rightmost empty position in ${\sf sa\_bkt_S}(1)$.
+Then, at $sa[12] = 8$, we see $x[7] = 1$ is S-type and thus put ${\sf suf}(7)$ into current rightmost empty position in ${\sf sa\_bkt_S}(1)$.
 To repeat scanning $sa$ in this way, we get all the S-type suffixes sorted in $sa$.
@@
 To be specific, when scanning from $sa[0]$ to $sa[5]$ in lines 10-21 of Fig.~\ref{fig:example2}, we induce ${\sf suf}(12)$ and ${\sf suf}(6)$ into the neighboring positions in ${\sf sa\_bkt_L(2)}$.
-During the scan, if we keep recording the minimal of $lcp(0, 5]$ in a variable, then we can obtain the LCP-value of the inducing suffixes ${\sf suf}(13)$ and ${\sf suf}(5)$ from the variable when inducing ${\sf suf}(6)$ into $sa$.
+During the scan, if we keep recording the minimal of $lcp(0, 5]$ in a variable, then we can obtain the LCP-value of the inducing suffixes ${\sf suf}(13)$ and ${\sf suf}(5)$ from this variable when putting ${\sf suf}(6)$ into $sa$.
 

### 2017-03-14 draft/draft.tex
2017/03/14

@@
 
-For full-text indexing of massive data, the suffix and LCP (longest common prefix) arrays have been recognized as the fundamental data structures, and there are at least two needs in practice for checking their correctness, i.e.
+For full-text indexing of massive data, the suffix and LCP (longest common prefix) arrays have been recognized as fundamental data structures, and there are at least two needs in practice for checking their correctness, i.e.
 program debugging and verifying the arrays constructed by probabilistic algorithms.
-In this paper, we propose two methods to check the suffix and LCP arrays in external memory by using a Karp-Rabin fingerprinting technique, where the checking result is wrong only with a negligible error probability.
-The first method checks the lexicographical order and the LCP-value of two neighboring suffixes in the given suffix array by computing and comparing the fingerprints of their LCPs.
-This idea is also employed in the second method to verify a subset of the given suffix and LCP arrays, from which then a copy of the final suffix and LCP arrays is produced following the induced sorting principle and compared with the given arrays for verification.
+In this paper, we propose two probabilistic methods to check the suffix and LCP arrays of constant or integer alphabets in external memory by using a Karp-Rabin fingerprinting technique, where the checking result is wrong only with a negligible error probability.
+The first method checks the lexicographical order and the LCP-value of two suffixes by computing and comparing the fingerprints of their LCPs.
+This method is rather general in terms of that it can verify any full or sparse suffix/LCP array of any order.
+The second method is more space efficient, it first employs the fingerprinting technique to verify a subset of the given suffix and LCP arrays, from which then a copy of the suffix and LCP arrays is produced using the induced sorting principle and compared with the given arrays for verification, where the copy of the induced suffix and LCP arrays can be removed for constant alphabets.
 
@@
 \begin{IEEEkeywords}
-	Suffix and LCP arrays verification, Karp-Rabin fingerprinting technique, external memory.
+	Suffix and LCP arrays, verification, Karp-Rabin fingerprinting, external memory.
 \end{IEEEkeywords}}
@@
 Suffix and longest common prefix (LCP) arrays play an important role in various string processing tasks, such as data compression, pattern matching and genome assembly.
-In many applications, these two data structures make up the core part of a powerful full-text index, called enhanced suffix array~\cite{Abouelhodaa2004}, which is more space efficient than a suffix tree and applicable to emulating any searching functionalities provided by the latter in the same time complexity.
-The first algorithm for building suffix array in internal memory was presented in~\cite{Manber1993}.
-From then on, much more effort has been put on designing efficient constructors for suffix array~(SA) on different memory models~\cite{Karkkainen2003, Ko2003, Kim2003, Nong11, Dementiev2008, Ferragina2012, Manzini2004, Bingmann12, Karkkainen2014, Nong14, Nong15}.
-In respect of the research on LCP array construction algorithms, the existing works can be classified into two categories with regard to their input requirements, where the algorithms from the first category compute both suffix and LCP arrays at the same time with the original text only~\cite{Fischer11, Bingmann12, Flick2015} and those from the second category carry out the computation by taking SA and/or Burrows-Wheeler transform (BWT) as additional input~\cite{Kasai2001,Karkkainen2009, Fischer11, Puglisi2008, Deo2013}.
-Among all, the algorithms designed by the induced sorting~(IS) principle take linear time and space to run and outperform previous arts on both internal and external memory models~\cite{Nong11, Karkkainen2014}.
-Recently, there appear some novel works that are competitive with the IS-based ones and can even achieve better performance when adequate computation resources are at hand.
-These algorithms are specific for parallel computation environments and capable of achieving high performance by fully using the available multi-core CPUs and/or GPUs~\cite{Osipov2012, Deo2013, Wang2015, Karkkainen2015, Karkkainen2016}.
+In many applications, these two data structures make up the core part of a powerful full-text index, called enhanced suffix array~\cite{Abouelhodaa2004}, which is more space efficient than a suffix tree and applicable to emulating most searching functionalities provided by the latter in the same time complexity.
+The first algorithm for building suffix array~(SA) in internal memory was presented in~\cite{Manber1993}.
+From then on, much more effort has been put on designing efficient constructors for suffix array on different computation models~\cite{Karkkainen2003, Ko2003, Kim2003, Nong11, Dementiev2008, Ferragina2012, Manzini2004, Bingmann12, Karkkainen2014, Nong14, Nong15}.
+In respect of the research on LCP array construction algorithms, the existing works can be classified into two categories with regard to their input requirements, where the algorithms from the first category compute both suffix and LCP arrays at the same time with the original text only~\cite{Fischer11, Bingmann12, Flick2015}, and those from the second category carry out the computation by taking SA and/or Burrows-Wheeler transform (BWT) as additional inputs~\cite{Kasai2001,Karkkainen2009, Fischer11, Puglisi2008, Deo2013}.
+So far, the algorithms designed by the induced sorting~(IS) principle take linear time and space to run and get the best results on both internal and external memory~\cite{Nong11, Karkkainen2014, Karkkainen2017}.
+In addition to the sequential algorithms, there are also parallel algorithms proposed to achieve high performance by fully using the available multi-core CPUs and/or GPUs~\cite{Osipov2012, Deo2013, Wang2015, Karkkainen2015, Karkkainen2016}.
 
-While the research on efficient construction of suffix and LCP arrays is evolving, the algorithms proposed recently are becoming more complicated than before.
-This reveals a need for program debugging because a program gives no guarantee that it has correctly implemented the underlying algorithm.
+While the research on efficient construction of suffix and LCP arrays keeps evolving, the algorithms proposed recently are becoming more complicated than before.
+Currently, the open source programs for the state-of-the-art algorithms are provided "as-is" for demonstration and experiment purpose only, giving no guarantee that they have correctly implemented the algorithms.
 As a common practice, a suffix or LCP checker is provided to check the correctness of a constructed array.
-For example, such a checker can be found in some software packages for SA-IS~\cite{Nong11}, eSAIS~\cite{Bingmann12}, DC3~\cite{Dementiev08} and so forth.
+For example, such a checker can be found in some software packages for DC3~\cite{Dementiev08}, SA-IS~\cite{Nong11}, eSAIS~\cite{Bingmann12} and so forth.
 In addition to help avoid implementation bugs, a checker is also demanded for an array constructed by a probabilistic algorithm~(e.g.~\cite{Bille2013}).
@@
 Particularly, there is currently no reported solution that can check both the suffix and the LCP arrays in external memory.
-This motivates our work here to design high-performance checkers for massive data.
+This motivates our work here to design efficient checkers for big suffix and LCP arrays in external memory.
 
@@
 
-Our contribution mainly includes two methods to probabilistically verify the given suffix and LCP arrays.
-Method A checks the lexical order and the LCP-value of two neighboring suffixes in SA by literally comparing the characters of their LCPs in pairs.
-For reducing the time complexity of a comparison between two sequences of characters, we use a Karp-Rabin fingerprinting technique to convert each sequence into a single integer, called fingerprint, and compare the fingerprints instead to check equality of these sequences.
+Our contribution comprises two methods to probabilistically verify any given suffix and LCP arrays.
+In principle, Method A checks the lexical order and the LCP-value of two neighboring suffixes in the suffix array by literally comparing the characters of their LCPs.
+For reducing the time complexity of a comparison between two sequences of characters, we use a Karp-Rabin fingerprinting technique to convert each sequence into a single integer, called fingerprint, and compare the fingerprints instead to check the equality of two sequences.
 The algorithm for Method A involves multiple scans and sorts on sets of $\mathcal{O}(n)$ fixed-size items.
-When implemented in external memory, it suffers from a space bottleneck owing to the large disk volume taken by each sort.
-To overcome the drawback, Method B first employs the fingerprinting technique to check a subset selected from the given suffix and LCP arrays, then it reuses the inducing process of an IS-based construction algorithm to produce the final suffix and LCP arrays from the verified subset and literally compares them with the input arrays to ensure the correctness of the latter.
-Our experiments indicate that the peak disk use of the program for the algorithm designed by Method B is only half as that of the program for the algorithm designed by Method A.
+Its implementation in external memory suffers from a space bottleneck due to the large disk volume taken by each sort.
+To overcome this drawback, Method B first employs the fingerprinting technique to check a subset selected from the given suffix and LCP arrays, then it reuses the inducing process of the IS-based construction algorithm SA-IS \cite{Nong11} to produce the final suffix and LCP arrays from the verified subset and literally compares them with the input arrays to ensure the correctness of the latter.
+Our experiments indicate that the peak disk use of the programs for Algorithm~\ref{alg:2} designed by Method B is only about half as that of the program for Algorithm~\ref{alg:1} designed by Method A.
 
 The remainder of this paper is organized as follows.
-We first describe the two methods and their algorithmic designs in Sections~\ref{sec:method1} and~\ref{sec:method2}, and then the evaluation of our programs for the algorithms designed by these methods in Section~\ref{sec:experiment}.
-Finally, we present the concluding remarks in Section~\ref{sec:conclusion}.
+Sections~\ref{sec:method1} and~\ref{sec:method2} describe the two methods and their algorithmic designs.
+Section~\ref{sec:experiment} conducts an experimental study for performance evaluation of our programs for these algorithms.
+Section~\ref{sec:conclusion} gives some concluding remarks.
 
@@
 
-Given a string $x[0, n)$ drawn from an alphabet $\Sigma$, the suffix array of $x$, denoted by $sa$, is a permutation of $\{0, 1, ..., n - 1\}$ such that ${\sf suf}(sa[i]) < {\sf suf}(sa[j])$ for $i, j \in [0, n)$ and $i < j$, where ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$ are two suffixes starting with $x[sa[i]]$ and $x[sa[j]]$, respectively.
+Given a string $x[0, n-1]$ drawn from a constant or integer alphabet $\Sigma$ of size $O(1)$ or $O(n)$, respectively, the suffix array of $x$, denoted by $sa$, is a permutation of $\{0, 1, ..., n - 1\}$ such that ${\sf suf}(sa[i]) < {\sf suf}(sa[j])$ for $i, j \in [0, n)$ and $i < j$, where ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$ are two suffixes starting with $x[sa[i]]$ and $x[sa[j]]$, respectively.
 Particularly, we say ${\sf suf}(sa[j])$ is a lexical neighbor of ${\sf suf}(sa[i])$ if $|i - j| = 1$.
@@
 
-According to the above definitions, we show in Lemma~\ref{lemma:1} the sufficient and necessary conditions for checking suffix and LCP arrays.
-Notice that the lexical order and the LCP-value of any two suffixes in $x$ can be computed by literally comparing their characters from left to right.
-Because all the suffixes differ in length and end with a common character, there must exist $k \in [0, n)$ such that $x[i, i + k) = x[j, j + k)$ and $x[i + k] \ne x[j + k]$ for any $i, j \in [0, n)$ and $i \ne j$.
-This approach can be also applied to verifying the last two conditions in Lemma~\ref{lemma:1}, but it takes at worst $\mathcal{O}(n)$ character-wise comparisons for each pair of neighboring suffixes in $sa$ to compare the two underlying substrings indicated by their LCP-value.
+According to the above definitions, we give in Lemma~\ref{lemma:1} the sufficient and necessary conditions for checking suffix and LCP arrays.
+Notice that the lexical order and the LCP-value of any two suffixes in $x$ can be computed by literally comparing their characters rightward.
+For convenience, we append a virtual character to $x$ and assume it to be lexicographically smaller than any characters in $\Sigma$.
+Because all the suffixes differ in length and end with the virtual character, any two suffixes are different.
 
@@
 
-An alternative is to exploit a perfect hash function~(PHF) to convert each substring into a single integer such that any two substrings have a common hash value if and only if they are literally equal to each other.
-This implies that we can compare the hash values instead to check equality of their corresponding substrings.
-The key point here is how to quickly calculate the hash values of $x[sa[i], sa[i] + lcp[i] - 1]$ and $x[sa[i - 1], sa[i - 1] + lcp[i] - 1]$ for all $i \in [1, n)$.
-Taking into consideration the high difficulty of finding a PHF to meet this requirement, we prefer using a Karp-Rabin fingerprinting function~\cite{Karp1987} to transform a substring into its integer form, called fingerprint.
-To be specific, suppose $L$ is a prime and $\delta$ is a number randomly chosen from $[1, L)$, the fingerprint ${\sf fp}(i, j)$ for a substring $x[i, j]$ can be calculated according to the formulas below as following: scan $x$ rightward to iteratively compute ${\sf fp}(0, k)$ for all $k \in [0, n)$ using Formulas~\ref{formula:1}-\ref{formula:2}, record ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ during the calculation and subtract the former from the latter to obtain ${\sf fp}(i, j)$ using Formula~\ref{formula:3}.
+If we directly compare the characters of two suffixes, the worst case time is $O(n)$.
+An alternative is to exploit a perfect hash function to convert each substring into a single integer such that any two substrings have a common hash value if and only if they are literally equal to each other, hence we can compare the hash values of two substrings instead to check their equality.
+Taking into account the high difficulty of finding such a perfect hash function to meet this requirement, we prefer using a Karp-Rabin fingerprinting function~\cite{Karp1987} to transform a substring into an integer called fingerprint.
+To be specific, suppose $L$ is a prime and $\delta$ is a number randomly chosen from $[1, L)$, the fingerprint ${\sf fp}(i, j)$ for a substring $x[i, j]$ can be iteratively calculated according to the formulas below as follows: scan $x$ rightward to iteratively compute ${\sf fp}(0, k)$ for all $k \in [0, n)$ using Formulas~\ref{formula:1}-\ref{formula:2}, record ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ during the calculation and subtract the former from the latter to obtain ${\sf fp}(i, j)$ using Formula~\ref{formula:3}.
 
@@
 
-We point out that two equal substrings always share a common fingerprint, but the inverse is not true.
-Fortunately, it has been proved in~\cite{Karp1987} that the probability of a false match can be reduced to a negligible level by setting $L$ to a large value\footnote{This property is utilized in~\cite{Bille2013} to design a probabilistic algorithm for computing a sparse suffix array.
-}.
-This leads us to the conclusion in Corollary~\ref{corollary:1}.
+Notice that two equal substrings always share a common fingerprint, but the inverse is not true.
+It has been proved in~\cite{Karp1987} that the probability of a false match can be reduced to a negligible level by setting $L$ to a large value\footnote{This property is utilized in~\cite{Bille2013} to design a probabilistic algorithm for computing a sparse suffix array.}.
+Hence, we have:
 
@@
 
-We close this part with an example in Fig.~\ref{fig:example} for a better understanding of computing and comparing the fingerprints of the substrings specified the LCP-values of lexical neighbors.
+Fig.~\ref{fig:example} gives an illustrating example for utilizing Corollary~\ref{corollary:1} to check the input suffix and LCP arrays.
 Given that $L = 197$ and $\delta = 101$, lines 4-8 compute ${\sf fp}(0, p)$ iteratively according to Formulas~\ref{formula:1}-\ref{formula:2}.
-Then, lines 10-16 use these values to compute the fingerprints for target substrings.
-Consider the leftmost pair of neighboring suffixes in $sa$, that is ${\sf suf}(sa[0])$ and ${\sf suf}(sa[1])$, the substrings indicated by their LCP-value are $x[sa[0], sa[0] + lcp[1] - 1]$ and $x[sa[1], sa[1] + lcp[1] - 1]$, respectively.
+Then, lines 10-16 use these values to compute the fingerprints for all the target substrings.
+In more detail, consider the leftmost pair of neighboring suffixes in $sa$, that is ${\sf suf}(sa[0])$ and ${\sf suf}(sa[1])$, the substrings indicated by their LCP-value are $x[sa[0], sa[0] + lcp[1] - 1]$ and $x[sa[1], sa[1] + lcp[1] - 1]$, respectively.
 According to Formula~\ref{formula:3}, ${\sf fp}(sa[0], sa[0] + lcp[1] - 1)$ is equal to the difference between ${\sf fp}(0, sa[0] - 1)$ and ${\sf fp}(0, sa[0] + lcp[1] - 1)$, both of which have been calculated beforehand.
+Following the same way, ${\sf fp}(sa[1], sa[1] + lcp[1] - 1)$ is computed by reducing ${\sf fp}(0, sa[1] - 1)$ from ${\sf fp}(0, sa[1] + lcp[1] - 1)$.
 Hence, we obtain the fingerprints for these two substrings in lines 10-12 and see that they are equal to each other.
@@
 	\includegraphics[width = 0.9\columnwidth]{example}
-	\caption{An Example for Computing and Comparing Fingerprints for Substrings Specifed by the LCP-Values of Neighboring Suffixes in SA. \label{fig:example}}	
+	\caption{An example for computing and comparing fingerprints for substrings specifed by the LCP-Values of neighboring suffixes in the suffix array. \label{fig:example}}	
 \end{figure}
@@
 Assume that $x$, $sa$ and $lcp$ are stored in external memory, we design Algorithm~\ref{alg:1} for conducting these I/O operations in a disk-friendly way.
-The main idea is to sort data in the order that they are visited and then access them by sequential reads.
+The main idea is to first sort data in their access order and then visit them by sequential reads.
 For the purpose, Algorithm~\ref{alg:1} first scans $sa$ and $lcp$ to produce $ST_1, ST_2, ST_3$ and sorts their tuples by 1st component in ascending order at the very beginning (lines~\ref{alg:1:a}-\ref{alg:1:b}).
 Afterward, it iteratively computes the fingerprints of all the prefixes according to Formulas~\ref{formula:1}-\ref{formula:2} and assigns them to the sorted tuples as following (lines~\ref{alg:1:c}-\ref{alg:1:d}): when figuring out ${\sf fp}(0, i - 1)$, extract each tuple $e$ with $e.1st = i$ from $ST_1/ST_2/ST_3$, update $e$  with ${\sf fp}(0, i - 1)$, and then forward $e$ to $ST_1'/ST_2'/ST_3'$.
-Because the 1st components of the tuples in $ST_1$ constitute a copy of $sa$, the algorithm can check condition (1) when scanning these tuples in their sorted order.
+Because the 1st components of the tuples in $ST_1$ constitute a copy of $sa$, the algorithm checks condition (1) when scanning these tuples in their sorted order.
 Finally, it sorts the updated tuples back to their original order~(line~\ref{alg:1:e}) and visits them  sequentially to check conditions (2)-(3) following the same way of S2~(lines~\ref{alg:1:f}-\ref{alg:1:g}).
@@
 
-			$fp := fp \cdot \delta + x[i] \! \mod \! P$
+			$fp := fp \cdot \delta + x[i] \! \mod \! P$ \hspace{5cm} // $x[n]$ is the virtual character
 		} \label{alg:1:d}
@@
 
-			\If{$\hat{fp_1} \ne \hat{fp_2}$ {\sf or} $ch_1 \le ch_2$}{
+			\If{$\hat{fp_1} \ne \hat{fp_2}$ {\sf or} $ch_1 \ge ch_2$}{
 
@@
 One method is to keep a lookup table in internal memory to store $\delta^{lcp[i]}$ for all $i \in [0, n)$.
-This method can answer the question in constant time, but it is space-consuming and
-impractical to use if the table size exceeds the capacity of memory bank.
-We provide another method that returns the answer in $\mathcal{O}(\lceil \log2^n \rceil)$ time using $\mathcal{O}(\lceil \log2^n \rceil)$ internal memory space.
-Specifically, suppose $e$ is an integer from $[0, n)$, it can be broken down into the form of $\Sigma_{i = 0}^{\lceil \log2^n \rceil}{k_i \cdot 2^i}$ by performing at most $\lceil \log2^n \rceil$ divisions, where $k_0, k_1, ..., k_{\lceil \log2^n \rceil}$ are integers from $\{0, 1\}$ .
-Thereby, we have $\delta^e = \Pi_{i = 0}^{\lceil \log2^n \rceil}{\delta}^{k_i \cdot 2^i}$ by replacing $e$ with its decomposition, where the expression on the right side of the equation can be easily computed with $\{{\delta}^{1}, {\delta}^{2}, \dots, {\delta}^{2^{\lceil \log2^n \rceil}} \}$ already known.
+This can answer the question in constant time, but it is impractical if the table is larger than the available memory size.
+Notice that the LCP of any two suffixes is smaller than $n$, thus we can return the answer in $\mathcal{O}(\lceil \log_2{n} \rceil)$ time using $\mathcal{O}(\lceil \log_2{n} \rceil)$ internal memory space based on the following idea.
+Suppose $e$ is an integer from $[0, n)$, it can be broken down into the form of $\Sigma_{i = 0}^{\lceil \log_2{n} \rceil}{k_i \cdot 2^i}$ by performing at most $\lceil \log_2{n} \rceil$ divisions, where $k_0, k_1, ..., k_{\lceil \log_2{n} \rceil}$ are integers from $\{0, 1\}$ .
+Thereby, we have $\delta^e = \Pi_{i = 0}^{\lceil \log_2{n} \rceil}{\delta}^{k_i \cdot 2^i}$ by replacing $e$ with its decomposition, where the expression on the right side of the equation can be easily computed with $\{{\delta}^{1}, {\delta}^{2}, \dots, {\delta}^{2^{\lceil \log_2{n} \rceil}} \}$ already known.
 
@@
 
-Algorithm~\ref{alg:1} is I/O-intensive, it performs multiple scans and sorts on the arrays of $\mathcal{O}(n)$ fixed-size tuples residing on disks.
+Algorithm~\ref{alg:1} performs multiple scans and sorts on the arrays of $\mathcal{O}(n)$ fixed-size tuples residing on disks.
 Given an external memory model with RAM size $M$, disk size $D$ and block size $B$, all are in words, the time and I/O complexities for each scan are $\mathcal{O}(n)$ and $\mathcal{O}(n / B)$, respectively, while those for each sort are $\mathcal{O}(n\log_{M/ B}(n / B))$ and $\mathcal{O}((n / B)\log_{M / B}(n / B))$, respectively~\cite{Arge2013}.
-Clearly, this algorithm reaches its peak disk use when sorting tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}.
-The experimental study in Section~\ref{sec:experiment} indicates that our program for Algorithm~\ref{alg:1} is rather space consuming, its peak disk use reaches 40 bytes per input character.
+Algorithm~\ref{alg:1} reaches its peak disk use when sorting tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}.
+Suppose the input string and the suffix/LCP array are encoded using $\alpha$- and $\beta$-byte integers, respectively, and each fingerprint is represented by a $\gamma$-byte integer, it takes $(2 \cdot (2 \cdot \alpha + \beta)) \cdot n$ space for sorting $ST_1/ST_1'$ and $(2 \cdot (2 \cdot \alpha + \beta + \gamma)) \cdot n$ for sorting $ST_2/ST_2'$ and $ST_3/ST_3'$.
+To save disk space, our program implementing the algorithm sorts $ST_1/ST_1'$, $ST_2/ST_2'$ and $ST_3/ST_3'$ separately and performs a single scan over $x$ for each of them to obtain the target fingerprints, resulting in smaller space requirement but larger running time.
+The experimental study in Section~\ref{sec:experiment} indicates that this program is still space consuming, its peak disk use is 40 bytes per input character.
 
@@
 In this part, we describe an alternative checking method based on the induced sorting principle.
-Compared with Algorithm~\ref{alg:1}, our program for the algorithm designed by this method only takes half space on real-world datasets.
+Compared with Algorithm~\ref{alg:1}, our programs for Algorithm~\ref{alg:2} designed by this method take around half disk space on real-world datasets.
 Before the presentation, we introduce some symbols and notations used in the following paragraphs.
@@
 {\em Suffix and LCP buckets.} Suppose $sa$ is correct, all the suffixes in $sa$ are naturally partitioned into multiple buckets and those of a common heading character are grouped into a single bucket that occupies a contiguous interval in $sa$.
-Each bucket can be further divided into two sub-buckets, where the left and right parts only contain L- and S-type suffixes, respectively.
+Each bucket can be further divided into two sub-buckets, where the left and the right parts only contain L- and S-type suffixes, respectively.
 For short, we use ${\sf sa\_bkt}(c)$ to denote the bucket storing suffixes starting with character $c$ and ${\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$ to denote its left/right sub-bucket.
@@
 
-{\em Suffix and LCP arrays for S*-type suffixes.} Given that the number of S*-type suffixes is $n_1$, $sa^*[0, n_1)$ stores all the S*-type suffixes and arrange them in lexical order, while the $(i + 1)$-th item of $lcp^*[0, n_1)$ records the LCP-value of ${\sf suf}(sa^*[i])$ and ${\sf suf}(sa^*[i - 1])$.
+{\em Suffix and LCP arrays for S*-type suffixes.} Given that the number of S*-type suffixes is $n_1$, $sa^*[0, n_1)$ stores all the S*-type suffixes arranged in lexical order, while $lcp^*[0] = 0$ and $lcp^*[i]$ records the LCP-value of ${\sf suf}(sa^*[i])$ and ${\sf suf}(sa^*[i - 1])$ for $i \in [1, n_1)$.
 
@@
 An IS-based construction algorithm mainly consists of a reduction phase for computing $sa^*$ and $lcp^*$, followed by an induction phase for inducing $sa$ and $lcp$ from $sa^*$ and $lcp^*$~\footnote{In the interest of completeness, we give an overview of the induction phase in Appendix~\ref{sec:appendix}.}.
-Given that $sa^*$ and $lcp^*$ are already known, we can produce the final suffix and LCP arrays by calling the inducing process of an existing construction algorithm.
+Given that $sa^*$ and $lcp^*$ are already known, we can produce the final suffix and LCP arrays by calling the inducing process of an existing IS-based construction algorithm.
 This enlightens us to design a checker based on Lemma~\ref{lemma:2}.
@@
 	\item
-	$sa = sa'$ and $lcp = lcp'$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by calling the inducing process of any existing IS-based construction algorithm.
+	$sa = sa'$ and $lcp = lcp'$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by the IS method.
 \end{enumerate}
@@
 
-Similar to Method A, we can employ the fingerprinting technique to probabilistically check the correctness of $sa^*$ and $lcp^*$.
-Based on this idea, we describe in the next subsection an external-memory algorithm for checking the conditions in Corollary~\ref{corollary:2}.
+Similar to Method A, the fingerprinting technique can be employed to probabilistically check the correctness of $sa^*$ and $lcp^*$.
+An external-memory algorithm for checking the conditions in Corollary~\ref{corollary:2} is given in the next subsection.
 
 \begin{Corollary} \label{corollary:2}
-Both $sa[0, n)$ and $lcp[0, n)$ are correct with a high probability given the following conditions, for $i \in [0, n)$, $\{j, k\} \in [1, n_1)$ and $j \ne k$:
-
+Both $sa[0, n)$ and $lcp[0, n)$ are correct with a high probability given the following conditions, for all $i \in [1, n_1)$ and $j \in [0, n)$:
 \begin{enumerate}[(1)]
 	\item
-	$sa^*[j] \ne sa^*[k]$.
+	$x[sa^*[i]]$ is S*-type, and $sa^*[i] \ne sa^*[k]$ for all $k \in [0, n_1)$ and $k \ne i$.
 	\item
-	${\sf fp}(sa^*[j], sa^*[j] + lcp^*[j] - 1) = {\sf fp}(sa^*[j - 1], sa^*[j - 1] + lcp^*[j] - 1)$.
+	${\sf fp}(sa^*[i], sa^*[i] + lcp^*[i] - 1) = {\sf fp}(sa^*[i - 1], sa^*[i - 1] + lcp^*[i] - 1)$.
 	\item
-	$x[sa^*[j] + lcp^*[j]] > x[sa^*[j - 1] + lcp^*[j]]$.
+	$x[sa^*[i] + lcp^*[i]] > x[sa^*[i - 1] + lcp^*[i]]$.
 	\item
-	$sa[i] = sa'[i]$ and $lcp[i] = lcp'[i]$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by calling the inducing process of an existing IS-based construction algorithm.
+	$sa[j] = sa'[j]$ and $lcp[j] = lcp'[j]$ for $j \in [0, n)$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by the IS method.
 \end{enumerate}
-
 \end{Corollary}
@@
 
-	sort tuples in $ST_2$ by 2nd component \label{alg:2:g}
+	sort tuples in $ST_2$ by the 2nd component \label{alg:2:g}
 
@@
 
-	\If{${\sf CheckByFP}(x, sa^*, lcp^*, lcp^*.{\sf size}()) = false$}{  \label{alg:2:i}
+	\If{${\sf CheckByFP}(x, sa^*, lcp^*, n_1) = false$}{  \label{alg:2:i}
 
-		\Return false;  \hspace{1cm} // conditions (2) or (3) is violated
+		\Return false \hspace{1cm} // conditions (2) or (3) is violated
 	}\label{alg:2:j}
@@
 
-			\Return false	// condition (4) is violated
+			\Return false \hspace{1cm}	// condition (4) is violated
 		}	
@@
 
-Assume that the alphabet $\Sigma$ is of a constant size, we can check $sa$ and $lcp$ without producing a copy of the final suffix and LCP arrays in Algorithm~\ref{alg:2}.
-The idea is to compare the induced suffix/LCP items with their corresponding items in $sa/lcp$ during the inducing process.
+{\bf Assume that the alphabet $\Sigma$ is of a constant size, we can check $sa$ and $lcp$ without producing a copy of the final suffix and LCP arrays in Algorithm~\ref{alg:2}.} The idea is to compare the induced suffix/LCP items with their corresponding items in $sa/lcp$ during the inducing process.
 Specifically, when a suffix/LCP item $v_1$ is induced into a bucket, we check if it is equal to the corresponding item $v_2$ in $sa/lcp$.
 If $v_1 = v_2$, then $v_2$ is correct and we further use this value to induce the remaining suffix/LCP items.
-The key point here is to retrieve items from $sa/lcp$ quickly.
+The key point here is to retrieve items of $sa/lcp$ from external storage as fast as possible.
 This can be done by conducting sequential I/O operations if we provide a read pointer together with a buffer for each suffix/LCP sub-bucket.
@@
 
-Algorithm~\ref{alg:2} mainly consists of two parts, where the first part for checking $sa^*$ and $lcp^*$ can be implemented within sorting complexity and the second part for checking $sa$ and $lcp$ can be implemented in linear time under the condition that $\|\Sigma\| = \mathcal{O}(1)$.
-As will be seen from Section~\ref{sec:experiment}, the peak disk use of our program for Algorithm~\ref{alg:2} is around $21n$, while it has a better performance than that for Algorithm~\ref{alg:1} in terms of time and I/O volume.
+Algorithm~\ref{alg:2} mainly consists of two parts, where the first part for checking $sa^*$ and $lcp^*$ can be done within sorting time and the second part for checking $sa$ and $lcp$ can be done in linear time.
+Clearly, the space complexity of part one is dependent upon the number of S*-type suffixes.
+As will be seen from Section~\ref{sec:experiment}, the programs for Algorithm~\ref{alg:2} take around $15n$ to check $sa^*$ and $lcp^*$, which is about one-third as that for Algorithm~\ref{alg:1} to check $sa$ and $lcp$.
+This corresponds to the ratio of S*-type suffixes to all in the real-world datasets.
+From our experiments, these programs take more disk space during the execution of inducing process, their peak disk use is about half as that for Algorithm~\ref{alg:1}.
 
@@
 For implementation simplicity, our programs for the algorithms proposed in the previous sections use the external-memory containers provided by the STXXL library~\cite{Dementiev2007} to manage read/write operations on disks.
-We make a performance evaluation by running our programs on the real-world corpora listed in Table~\ref{tbl:1}, where three measurements normalized by the size of input string are investigated:
+We make a performance evaluation by running them on the real-world corpora listed in Table~\ref{tbl:1}, where three measures normalized by the size of input string are investigated:
 
@@
 
-	\item IOV: amount of data read from and write to external memory, in bytes.
+	\item IOV: amount of data read from and write to external memory, in bytes. Each element of the suffix and LCP arrays takes 5 bytes.
 
@@
 
-The experimental platform is a work station equipped with an Intel Xeon E3-1220 V2 CPU, 4 GiB RAM and 2 TiB HD.
-All the programs are compiled by gcc/g++ 4.8.4 with -O3 options under ubuntu 14.04 64-bit operating system.
-In what follows, we denote the programs for Algorithms~\ref{alg:1} and~\ref{alg:2} by "ProgA" and "ProgB", respectively.
+The experimental platform is a server equipped with an Intel Core i3-550 CPU, 4 GiB RAM and 2 TiB HD.
+All the programs are compiled by gcc/g++ 4.8.4 with -O3 options on ubuntu 14.04 64-bit operating system and each program is allowed to use 3 GiB RAM.
+For denotation convenience, we use "ProgA" and "ProgB" to represent the programs for Algorithms~\ref{alg:1} and~\ref{alg:2}, respectively.
 
@@
 \renewcommand\arraystretch{1.3}
-\begin{table}[!t]
+\begin{table}[!htbp]
 	\caption{Corpus, $n$ in Gi, 1 byte per character.}
@@
 	\centering
-	\begin{tabular}{|l|c|c|p{5cm}|}
+	\begin{tabular}{|l|c|c|p{5.2cm}|}
 		\hline
-		Corpora & \multicolumn{1}{c|}{$n$} & \multicolumn{1}{c|}{$\|\Sigma\|$} & Description \\\hline
-		enwiki & 8 & 256 & The 8-GiB prefix of an XML dump of English Wikipedia, available at \url{https://dumps.wikimedia.org/enwiki}, dated as 16/05/01. \\\hline	
-		uniprot & 2.5 & 96 & UniProt Knowledgebase, available at \url{ftp://ftp.expasy.org/databases/.../complete}, dated as 16/05/11. \\\hline
-		proteins & 1.1 & 27 & Swissprot database, available at \url{http://pizzachili.dcc.uchile.cl/texts/protein}, dated as 06/12/15. \\\hline
+		Corpora & \multicolumn{1}{c|}{$\|\Sigma\|$} & $n$ & Description \\\hline
+		enwiki & 256 & 74.7 & An XML dump of English Wikipedia, available at \url{https://dumps.wikimedia.org/enwiki}, dated as 16/05/01. \\\hline	
+		uniprot & 96 & 2.5 & UniProt Knowledgebase, available at \url{ftp://ftp.expasy.org/databases/uniprot/current_release/knowledgebase/complete/}, dated as 16/05/11. \\\hline
+		proteins & 27 & 1.1 & Swissprot database, available at \url{http://pizzachili.dcc.uchile.cl/texts/protein}, dated as 06/12/15. \\\hline
 	\end{tabular}
@@
 
-\subsection{Result} \label{sec:experiments:results}
+\subsection{Results} \label{sec:experiments:results}
 
-Fig.~\ref{fig:performance_analysis} illustrates the performance comparison of ProgA and ProgB on different datasets, where "enwiki\_8g" consists of the leftmost 8 Gi characters extracted from "enwiki".
-As depicted, ProgB runs slower than ProgA by around 20 percent.
-The speed gap between them is mainly due to the difference in their I/O performances.
-Specifically, the I/O volume of ProgB keeps at $155n$ for all the three datasets, while that of ProgA rises up to nearly $200n$ on average.
+Fig.~\ref{fig:performance_analysis} illustrates the performance comparison of ProgA and ProgB on different datasets, where "enwiki\_8g" consists of the leftmost 8 GiB extracted from "enwiki".
+As depicted, ProgB runs slower than ProgA by around 20\%.
+The speed gap is mainly due to the difference in I/O performance.
+Specifically, the I/O volume of ProgA keeps at $155n$ for all the three datasets, while that of ProgB rises up to nearly $200n$ on average.
 Besides, the peak disk use of ProgB is about $26/40=0.65$ as ProgA.
-This can be explained as following.
 Recall that Algorithm~\ref{alg:2} invokes Algorithm~\ref{alg:1} to check the suffix and LCP arrays for the S*-type suffixes.
 Because at most one out of every two successive characters in the input string is S*-type, the consumption for checking the suffix and LCP arrays of S*-type suffixes in ProgB is expected to be half as that for checking the given arrays in ProgA.
-To make a deep insight, we collect in Table~\ref{tbl:2} the performance overhead of ProgB and ProgA when checking the suffix and LCP arrays of S*-type and all the suffixes, respectively.
+For a better insight, we collect in Table~\ref{tbl:2} the performance overhead of ProgB and ProgA when checking the suffix and LCP arrays of S*-type suffixes and all, respectively.
 As can be observed, the mean ratio of the number of S*-type suffixes to the number of all the suffixes is around 0.30 for the datasets under investigation, while the mean ratios of time, space and I/O volume for checking $sa^*$ and $lcp^*$ to that for checking $sa$ and $lcp$ are 0.38, 0.57 and 0.60, respectively.
 
-The above phenomenon indicates that ProgB reaches its peak disk use when checking the final suffix and LCP arrays during the inducing process.
+The above observations indicate that ProgB reaches its peak disk use when checking the final suffix and LCP arrays during the inducing process, i.e., the inducing process constitutes the performance bottleneck of the whole algorithm.
 By adopting the space optimization scheme introduced in Section~\ref{sec:method2:algorithm}, we adapt Algorithm~\ref{alg:2} and evaluate the tuned version of ProgB, called ProgB+, in comparison with ProgA and ProgB.
 Fig.~\ref{fig:performance_analysis} shows that the maximum space requirement for ProgB+ is about $21n$, which is much less than that of ProgB and even only half as that of ProgA.
-In addition, progB+ outperforms its prototype with respect to time and I/O efficiency and it achieves a higher speed against ProgA when handling "proteins".
+In addition, progB+ outperforms its prototype with respect to time and I/O efficiency and is faster than ProgA when handling "proteins".
 We also investigate the performance trend of the three programs on the prefix of "enwiki" with the length varying in $\{1, 2, 4, 8\}$ GiB.
-In Figure~\ref{fig:performance_analysis2}, the peak disk use for each program remains unchanged, but their speed become slower as the prefix length increases due to the performance degradation of the external memory sorter exploited in our programs.
-As we can see from Table~\ref{tbl:2}, ProgB+ keeps the I/O volume around $90n$ with the prefix length of "enwiki" varying from $1$ to $8$ GiB, while its running time rises from $1.05$ to $1.33$.
+In Figure~\ref{fig:performance_analysis2}, the peak disk use for each program remains unchanged, but their speed become slower as the prefix length increases due to the performance degradation of the external memory sorter used in our programs.
+This can be also observed from Table~\ref{tbl:2}, where ProgB+ keeps the I/O volume around $90n$ with the prefix length of "enwiki" varying from $1$ to $8$ GiB but its running time rises from $1.05$ to $1.33$.
 
@@
 		\hline
-		\multirow{2}{*}{dataset} & \multicolumn{3}{|c|}{number of suffixes} & \multicolumn{3}{|c|}{PDU} & \multicolumn{3}{|c|}{IOV} & \multicolumn{3}{|c|}{RT} \\\cline{2-13}
+		\multirow{2}{*}{Dataset} & \multicolumn{3}{|c|}{\# of suffixes} & \multicolumn{3}{|c|}{PDU} & \multicolumn{3}{|c|}{IOV} & \multicolumn{3}{|c|}{RT} \\\cline{2-13}
 						 & S*-type & all & ratio & S*-type & all & ratio & S*-type & all & ratio & S*-type & all & ratio \\\hline
@@
 
-The next experiment is to compare our programs with that of two solutions for building the suffix and LCP arrays as below, where either of them combines an existing suffix sorter with an LCP builder.
+In the next experiment, we compare our programs with two solutions for building the suffix and LCP arrays as below, where each of them combines an existing suffix sorter with an LCP builder:
 
-\begin{enumerate} [solut{i}on 1]
-	\item Use eSAIS for building SA and the sequential version of Sparse-$\phi$~\cite{Karkkainen2016} for building LCP array.
+\begin{itemize}
+	\item Solution 1: Use eSAIS for building SA and the sequential version of Sparse-$\phi$~\cite{Karkkainen2016} for building LCP array.
 
-	\item Use pSAscan~\cite{Karkkainen2015} for building SA and the parallel version of Sparse-$\phi$ for building LCP array.
-\end{enumerate}
+	\item Solution 2: Use pSAscan~\cite{Karkkainen2015} for building SA and the parallel version of Sparse-$\phi$ for building LCP array.
+\end{itemize}
 
- We select eSAIS and pSAscan because they are currently the fastest sequential and parallel algorithms for SA construction.
-Also, Sparse-$\phi$ is the fastest algorithm for LCP array construction ever reported.
+We select these programs because they are currently the fastest suffix and LCP arrays builders available to us.
 A runtime breakdown of the programs for these solutions on the prefixes of "enwiki" is given in Table~\ref{tbl:3}.
-As can be seen, solution 2 is about two times faster than solution 1 and twice as fast as ProgA, which is mainly owing to the high speed of pSAscan.
-Notice that both eSAIS and the proposed checking algorithms can achieve optimal time and I/O complexity in external memory, but pSAscan and Sparse-$\phi$ are not theoretically optimal and thus have a limitation to their scalability.
-As reported in~\cite{Karkkainen2015}, when the length of input string is considerably greater than the size of internal memory, eSAIS is more quickly and I/O efficient than pSAScan.
-We can see from the same table that an increase in the time overhead occurs to pSAscan when handling the prefix containing 8 Gi characters.
+The program for Solution 2 is about two times faster than that for Solution 1 and twice as fast as ProgA, which is mainly due to the high speed of pSAscan in this experiment.
+However, it is worthy of pointing out that both pSAscan and Sparse-$\phi$ are of the time and I/O complexities proportional to $n^2/M$.
+This is much higher than eSAIS and our checking algorithms when $n$ increases, and thus poses a strict limitation to the scalability of Solution 2.
+As reported in~\cite{Karkkainen2015}, when $n$ is considerably greater than $M$, eSAIS is much more time and I/O efficient than pSAscan.
+In this experiment, pSAscan builds the SA for "enwiki\_8g" in time double as that for "enwiki\_1g".
+{\bf For big $n$, it is more reasonable to compare the results of our programs with that of Solution 1.}
 
@@
 \begin{table*}[h]
-	\caption{A runtime comparison between the programs for the two solutions and the proposed algorithms.}
+	\caption{A runtime comparison for the programs of two construction solutions and ours.}
 	\label{tbl:3}
@@
 		\hline
-		\multirow{2}{*}{dataset} & \multicolumn{3}{|c|}{solution 1} & \multicolumn{3}{c|}{solution 2} & \multirow{2}{*}{ProgA} & \multirow{2}{*}{ProgB+} \\\cline{2-7}
+		\multirow{2}{*}{Dataset} & \multicolumn{3}{|c|}{Solution 1} & \multicolumn{3}{c|}{Solution 2} & \multirow{2}{*}{ProgA} & \multirow{2}{*}{ProgB+} \\\cline{2-7}
 		 & eSAIS & sequential sparse-$\phi$ & total & pSAscan & parallel sparse-$\phi$ & total & & \\\hline
@@
 Firstly, it was observed that our programs suffer from a bottleneck when sorting massive data in external memory.
-For implementation simplicity, we currently use the container provided by the STXXL library to perform the sorting task without designing a specific sorter.
-It is possible to speed up the sorting process by means of the high-performance radix-sort algorithms proposed on GPU-based computation platforms.
+For implementation simplicity, we currently use the container provided by the STXXL library to execute the sorting task without designing a specific sorter optimized for our purpose.
+It is possible to speed up the sorting process by high-performance radix-sort GPU algorithms.
 Secondly, Method B checks the suffix and LCP arrays using the induced sorting principle.
-Unfortunately, the existing IS-based suffix/LCP array construction algorithms are not capable of fully using the available computation resources.
-At the time of writing this paper, the authors are making research on designing IS-based algorithms for running in the context of parallel environments.
-This work may also improve the implementation design of Algorithm~\ref{alg:2}.
+At the time of writing this paper, the existing IS-based suffix/LCP array construction algorithms are naturally sequential.
+We have been conducting a study to design IS-based parallel algorithms, this work may also improve the implementation design of Algorithm~\ref{alg:2}.
 
-Method A has a higher versatility compared to the existing construction algorithms, it can be employed to check any set containing one or multiple pairs of lexicographically neighboring or non-neighboring suffixes.
+Method A is able to check any set containing one or multiple pairs of lexicographically neighboring or non-neighboring suffixes.
 This feature can be applied to various scenarios.
-For example, sometimes the consistency of a suffix/LCP array may be broken due to hardware malfunctions or human errors.
-If the backup of the corrupted data is not available and it is too time-consuming to rebuild the whole array, then we can locate the bad areas quickly by using a generalized version of Algorithm~\ref{alg:1} and restore the partial SA for each area by calling a sparse SA construction algorithm.
+For example, a suffix/LCP array may be broken due to software or hardware malfunctions.
+If a backup is not available and it is too time-consuming to rebuild the whole array, then we can locate the bad areas quickly using Algorithm~\ref{alg:1} and restore the partial SA for each area by calling a sparse SA construction algorithm.
 Another example is to check the correctness of a sparse SA.
-Because the number of suffixes in the sparse SA is commonly much smaller than the number of suffixes in the SA, it is expected that a substantial improvement in time, space and I/O volume can be achieved when performing verification using the proposed algorithms.
+Because the number of suffixes in a sparse SA is commonly much smaller than that in the full SA, Algorithm~\ref{alg:1} could become an efficient verification solution.
+
+%In this paper, both methods A and B assume a constant or integer alphabet.
+However, in practice, an input string is commonly of a constant alphabet, e.g.
+4 and 256 characters for genome and text, respectively.
+In this case, Method B can be improved for better time and space performance as follows.Given the alphabet is constant, we can first scan the input string once to get the statistics for buckets in the suffix array.
+Without loss of generality, suppose that the S-type characters are less.
+Then, we scan the input suffix array once to get ${\sf SA_S/LCP_S}$ consisting of all the sorted S-type suffixes with their LCP-values, by using the bucket statistics to on-the-fly determine a scanned suffix is S-type or not.
+From ${\sf SA_S/LCP_S}$, we can further induce the final suffix and LCP arrays from ${\sf SA_S/LCP_S}$ for checking.
+In this way, we can avoid the time and space required for the two sort($n$) in the current fashion of Method B, resulting in significant expected performance improvement.
+
+In this paper, both methods A and B assume a constant or integer alphabet.
+However, in practice, an input string is commonly of a constant alphabet, e.g.
+4 and 256 characters for genome and text, respectively.
+In this case, Method B can be improved for better time and space performance by inducing the final suffix and LCP arrays directly from $sa_S/lcp_S$ or $sa_L/lcp_L$, which consist of all the sorted S-type or L-type suffixes with their LCP-values and can be obtained as follows.
+Given the alphabet is constant, we first scan the input string once to get the statistics for buckets in the input suffix array.
+Without loss of generality, suppose that the S-type characters are less, then we scan the suffix array once to get $sa_S/lcp_S$ by using the bucket statistics to on-the-fly determine a scanned suffix is S-type or not.
+Afterward, we check $sa_S/lcp_S$ by using Algorithm~\ref{alg:1} and induce $sa'/lcp'$ from them.
+In this way, we avoid the two integer sorts in the current fashion of Method B for retrieving $sa^*/lcp^*$ and speed up the inducing process by nearly half as well.
+
+It should be noticed that our programs are coded for experimental study only.
+From engineering aspects, there is still a big margin for better implementation.
+For example, several algorithms for induced sorting a suffix and/or LCP arrays were proposed these years \cite{Nong15,Nong14,Bingmann12}, with different methods for solving the key problem of retrieving the preceding character of a sorted suffix in the inducing process.
+A recent work \cite{Karkkainen2017} for engineering these induced sorting methods with some implementation optimizing techniques achieves a significant improvement over the previous results.
+As reported, the peak disk use is $7n$ for 32-bit integers.
+Because the induced sorting process is the performance bottleneck for Method B, it is reasonable to expect that a better engineering implementation of the method will yield a remarkable performance improvement.
+{\bf An optimized engineering of our methods is out of the scope of this paper and will be addressed elsewhere.}
 
@@
 In this paper, we propose two methods for probabilistically checking the given suffix and LCP arrays.
-Theoretically, the external-memory algorithms designed by these methods can achieve better time and I/O complexities compared to the existing fastest construction algorithms.
-Our experimental results indicate that the programs for Algorithm~\ref{alg:2} designed by Method B run slower than that for Algorithm~\ref{alg:1} designed by Method A, but they are more efficient than the latter in terms of time and I/O volume.
-As discussed in Section~\ref{sec:experiment}, there are still several ways of enhancing the performance of our programs.
-For future work, we attempt to redesign the sorting and inducing process in our implementations to make them competitive with the state-of-the-art parallel construction algorithms.
+Theoretically, the external-memory algorithms designed by these methods have better time and I/O complexities compared to the existing fastest construction algorithms.
+Our experimental results indicate that the current programs for Algorithm~\ref{alg:2} designed by Method B run slower than that for Algorithm~\ref{alg:1} designed by Method A, but they are much more space-efficient than the latter.
+As discussed in Section~\ref{sec:experiment}, there still remains much room for improving the implementations of the proposed algorithms.
+Our experimental programs can be further optimized to achieve higher performance, in particular for checking arrays of constant alphabets that are most common in practice.
+The optimized programs will run much faster and use at most $n$ integers as the working space in addition to the input arrays.
 
-From our perspective, a checker should be not only fast but also versatile.
-As a common practice, we usually check an array derived from a builder by literally comparing it with the one produced by another builder.
-However, this is not feasible in all the cases, because, for example, an algorithm for constructing infinite-order array can not be directly used to check a finite-order array and vise versa.
-On the contrary, our first method can be generalized to check the correctness of the lexical order and the LCP values of one or multiple pairs of suffixes starting at any positions of input string.
-This makes it possible to trivially adapt Algorithm~\ref{alg:1} for verifying a sparse or finite-order SA together with the corresponding LCP array.
+From our perspective, a checker should be not only fast but also general.
+For program debugging, we usually check the output of a builder by comparing it with that of another builder.
+But this is not feasible in all the cases, for example, an algorithm for constructing infinite-order\footnote{A suffix array is infinite-order if the suffixes are sorted up to their ends, or else finite-order.} array can not be directly used to check a finite-order array and vise versa.
+On the contrary, our first method can be generalized to check the correctness of the lexical order and the LCP values of any pairs of suffixes.
+This makes it possible for verifying any full or sparse suffix/LCP array of any order.
+
+The IS method has been applied to successfully design a number of suffix and LCP arrays construction algorithms.
+A recent work \cite{Karkkainen2017} reports that a careful engineering of the IS in external memory can build a suffix array using only $7n$ bytes for $n\le 2^{32}$, which is approaching the optimal in respect to $5n$ bytes for the IS in internal memory.
+Besides, it runs fastest in most cases of the experiments therein.
+This convinces that the IS method could serve as a basis for developing potentially optimal solutions for building suffix/LCP arrays.
+We design here the algorithms for checking given suffix and LCP arrays.
+In another paper, we will come up with a solution for building and checking a suffix/LCP array simultaneously using the IS method.
+By this way, no additional checker is needed to be distributed with a suffix/LCP array builder using the IS method.
 
@@
 	\item 
-	Clear S-type sub-buckets in $sa$. Scan $sa^*$ leftward and insert each element into current rightmost empty position in the corresponding S-type sub-bucket.
+	Clear S-type sub-buckets in $sa$. Scan $sa^*$ leftward and insert each element into the current rightmost empty position in the corresponding S-type sub-bucket.
 
@@
 Scan $sa$ rightward with $i$ increasing from $0$ to $n - 1$.
-For each scanned non-empty $sa[i]$ with $t[sa[i] - 1] = 0$, insert $sa[i] - 1$ into current leftmost empty position in ${\sf sa\_bkt_L}(x[sa[i] - 1])$.
+For each scanned non-empty $sa[i]$ with $t[sa[i] - 1] = 0$, insert $sa[i] - 1$ into the current leftmost empty position in ${\sf sa\_bkt_L}(x[sa[i] - 1])$.
 
@@
 Scan $sa$ leftward with $i$ decreasing from $n - 1$ to $0$.
-For each scanned non-empty $sa[i]$ with $t[sa[i] - 1] = 1$, insert $sa[i] - 1$ into current rightmost empty position in ${\sf sa\_bkt_S}(x[sa[i] - 1])$.
+For each scanned non-empty $sa[i]$ with $t[sa[i] - 1] = 1$, insert $sa[i] - 1$ into the current rightmost empty position in ${\sf sa\_bkt_S}(x[sa[i] - 1])$.
 
@@
 
-In brief, assume $sa^*$ is already known, S1 inserts all the S*-type suffixes into $sa$ in their lexical order.
-Then, S2-S3 induce the order of L-type and S-type suffixes from those already sorted in $sa$, respectively, where the relative order of two suffixes induced into the same sub-bucket matches their insertion order according to the rule stated above.
+In brief, given $sa^*$, S1 inserts all the S*-type suffixes into $sa$ in their lexical order.
+Then, S2-S3 induce the order of L- and S-type suffixes from those already sorted in $sa$, respectively, where the relative order of two suffixes induced into the same sub-bucket matches their insertion order according to the rule stated above.
 To be more specific, we show in Fig.~\ref{fig:example2} a running example of the induction phase.
@@
 Then, we scan $sa$ from left to right for inducing the order of all the L-type suffixes.
-In lines 10-11, when visiting $sa[0] = 13$ (marked by the symbol $@$), we check the type array $t$ to find $x[12] = 2$ is L-type and hence insert ${\sf suf}(12)$ into current leftmost empty position in ${\sf sa\_bkt_L}(2)$.
+In lines 10-11, when visiting $sa[0] = 13$ (marked by the symbol $@$), we check the type array $t$ to find $x[12] = 2$ is L-type and hence insert ${\sf suf}(12)$ into the current leftmost empty position in ${\sf sa\_bkt_L}(2)$.
 Similarly, in lines 12-13, we visit the next scanned item $sa[1] = 11$ and see that $t[10] = 0$, thus we place ${\sf suf}(10)$ into the current head of ${\sf sa\_bkt_L}(3)$.
@@
 After that, we first find the end of each S-type sub-bucket in lines 25-26 and scan $sa$ leftward for inducing the order of all the S-type suffixes in lines 27-40.
-When visiting $sa[13] = 2$, we see $x[1]$ is S-type and thus put ${\sf suf}(1)$ into current rightmost empty position in ${\sf sa\_bkt_S}(1)$.
-Then, at $sa[12] = 8$, we see $x[7] = 1$ is S-type and thus put ${\sf suf}(7)$ into current rightmost empty position in ${\sf sa\_bkt_S}(1)$.
+When visiting $sa[13] = 2$, we see $x[1]$ is S-type and thus put ${\sf suf}(1)$ into the current rightmost empty position in ${\sf sa\_bkt_S}(1)$.
+Then, at $sa[12] = 8$, we see $x[7] = 1$ is S-type and thus put ${\sf suf}(7)$ into the current rightmost empty position in ${\sf sa\_bkt_S}(1)$.
 To repeat scanning $sa$ in this way, we get all the S-type suffixes sorted in $sa$.
@@
 The work presented in~\cite{Fischer11} describes how to compute the LCP array during the execution of S2-S3.
-Given two suffixes placed at the neighboring positions in $sa$, their LCP-value can be computed according to one of the following two cases with regard to whether or not they are inserted into the same sub-bucket: if yes, then the LCP-value of them is one greater than that of the two suffixes from which inducing them; otherwise, the LCP-value of them is equal to zero.
+Given two suffixes placed at the neighboring positions in $sa$, their LCP-value can be computed according to one of the following two cases in respect to whether or not they are inserted into the same sub-bucket: if yes, then their LCP-value is one greater than that of the two suffixes from which inducing them; otherwise, their LCP-value equals to zero.
 In this way, we can determine $lcp[i]$ immediately after the computation of $sa[i]$.
-The problem here is how to obtain the LCP-value of these inducing suffixes, which is modeled as a range minimum query in~\cite{Fischer11} and can be easily answered within $\mathcal{O}(1)$ time using $\mathcal{O}(\|\Sigma\|)$ space.
-To be specific, when scanning from $sa[0]$ to $sa[5]$ in lines 10-21 of Fig.~\ref{fig:example2}, we induce ${\sf suf}(12)$ and ${\sf suf}(6)$ into the neighboring positions in ${\sf sa\_bkt_L(2)}$.
-During the scan, if we keep recording the minimal of $lcp(0, 5]$ in a variable, then we can obtain the LCP-value of the inducing suffixes ${\sf suf}(13)$ and ${\sf suf}(5)$ from this variable when putting ${\sf suf}(6)$ into $sa$.
+The problem here is how to obtain the LCP-values of these inducing suffixes starting at the next positions in $x$, which is modeled as a range minimum query in~\cite{Fischer11} and can be answered within amortized $\mathcal{O}(1)$ time.
+For example, when scanning from $sa[0]$ to $sa[5]$ in lines 10-21 of Fig.~\ref{fig:example2}, we induce ${\sf suf}(12)$ and ${\sf suf}(6)$ into the neighboring positions in ${\sf sa\_bkt_L(2)}$.
+During the scan, if we keep recording the minimal of $lcp(0, 5]$ in a variable, then we can obtain the LCP-value of the suffixes ${\sf suf}(13)$ and ${\sf suf}(5)$ from this variable when putting ${\sf suf}(6)$ into $sa$.
 
@@
 
-	\caption{An Example for Computing the suffix and LCP arrays during the Induction Phase. \label{fig:example2}}	
+	\caption{An Example for inducing the suffix and LCP arrays. \label{fig:example2}}	
 \end{figure}

### 2017-03-17 draft/draft.tex
2017/03/17

@@
 This method is rather general in terms of that it can verify any full or sparse suffix/LCP array of any order.
-The second method is more space efficient, it first employs the fingerprinting technique to verify a subset of the given suffix and LCP arrays, from which then a copy of the suffix and LCP arrays is produced using the induced sorting principle and compared with the given arrays for verification, where the copy of the induced suffix and LCP arrays can be removed for constant alphabets.
+The second method is more space efficient, it first employs the fingerprinting technique to verify a subset of the given suffix and LCP arrays, from which then a copy of the suffix and LCP arrays is produced by using the induced sorting method and compared with the given arrays for verification.
+In particular, for constant alphabets, the copy of the induced suffix and LCP arrays can be removed to make a further improvement on the space efficiency.
 
@@
 The first algorithm for building suffix array~(SA) in internal memory was presented in~\cite{Manber1993}.
-From then on, much more effort has been put on designing efficient constructors for suffix array on different computation models~\cite{Karkkainen2003, Ko2003, Kim2003, Nong11, Dementiev2008, Ferragina2012, Manzini2004, Bingmann12, Karkkainen2014, Nong14, Nong15}.
+From then on, much more effort has been put on designing efficient SA constructors on different computation models~\cite{Karkkainen2003, Ko2003, Kim2003, Nong11, Dementiev2008, Ferragina2012, Manzini2004, Bingmann12, Karkkainen2014, Nong14, Nong15}.
 In respect of the research on LCP array construction algorithms, the existing works can be classified into two categories with regard to their input requirements, where the algorithms from the first category compute both suffix and LCP arrays at the same time with the original text only~\cite{Fischer11, Bingmann12, Flick2015}, and those from the second category carry out the computation by taking SA and/or Burrows-Wheeler transform (BWT) as additional inputs~\cite{Kasai2001,Karkkainen2009, Fischer11, Puglisi2008, Deo2013}.
-So far, the algorithms designed by the induced sorting~(IS) principle take linear time and space to run and get the best results on both internal and external memory~\cite{Nong11, Karkkainen2014, Karkkainen2017}.
-In addition to the sequential algorithms, there are also parallel algorithms proposed to achieve high performance by fully using the available multi-core CPUs and/or GPUs~\cite{Osipov2012, Deo2013, Wang2015, Karkkainen2015, Karkkainen2016}.
+So far, the algorithms designed by the induced sorting~(IS) method take linear time and space to run and get the best results on both internal and external memory models~\cite{Nong11, Karkkainen2014, Karkkainen2017}.
+In addition to these sequential algorithms, there are also some parallel alternatives proposed to achieve high performance by fully using the available multi-core CPUs and/or GPUs~\cite{Osipov2012, Deo2013, Wang2015, Karkkainen2015, Karkkainen2016}.
 
 While the research on efficient construction of suffix and LCP arrays keeps evolving, the algorithms proposed recently are becoming more complicated than before.
-Currently, the open source programs for the state-of-the-art algorithms are provided "as-is" for demonstration and experiment purpose only, giving no guarantee that they have correctly implemented the algorithms.
+Currently, the open source programs for the state-of-the-art algorithms are provided "as-is" for demonstration and experiment purposes only, giving no guarantee that they have correctly implemented the algorithms.
 As a common practice, a suffix or LCP checker is provided to check the correctness of a constructed array.
-For example, such a checker can be found in some software packages for DC3~\cite{Dementiev08}, SA-IS~\cite{Nong11}, eSAIS~\cite{Bingmann12} and so forth.
+For example, such a checker can be found in some widespread software packages for DC3~\cite{Dementiev08}, SA-IS~\cite{Nong11}, eSAIS~\cite{Bingmann12} and so forth.
 In addition to help avoid implementation bugs, a checker is also demanded for an array constructed by a probabilistic algorithm~(e.g.~\cite{Bille2013}).
-In this case, the array is correctly constructed with a probability and hence must be verified by a checker to ensure its correctness.
+In this case, the array is correctly constructed with a probability and hence must be verified to ensure its correctness.
 As far as we know, the work in~\cite{Burkhardt2003} describes the only SA checking method that can be found in the existing literature, and no efficient checking method for LCP array has been reported yet.
 Particularly, there is currently no reported solution that can check both the suffix and the LCP arrays in external memory.
-This motivates our work here to design efficient checkers for big suffix and LCP arrays in external memory.
+This motivates our work here to design efficient checkers for big suffix and LCP arrays.
 
@@
 Our contribution comprises two methods to probabilistically verify any given suffix and LCP arrays.
-In principle, Method A checks the lexical order and the LCP-value of two neighboring suffixes in the suffix array by literally comparing the characters of their LCPs.
+In principle, Method A checks the lexical order and the LCP-value of two neighboring suffixes in the given SA by literally comparing the characters of their LCPs.
 For reducing the time complexity of a comparison between two sequences of characters, we use a Karp-Rabin fingerprinting technique to convert each sequence into a single integer, called fingerprint, and compare the fingerprints instead to check the equality of two sequences.
@@
 Its implementation in external memory suffers from a space bottleneck due to the large disk volume taken by each sort.
-To overcome this drawback, Method B first employs the fingerprinting technique to check a subset selected from the given suffix and LCP arrays, then it reuses the inducing process of the IS-based construction algorithm SA-IS \cite{Nong11} to produce the final suffix and LCP arrays from the verified subset and literally compares them with the input arrays to ensure the correctness of the latter.
-Our experiments indicate that the peak disk use of the programs for Algorithm~\ref{alg:2} designed by Method B is only about half as that of the program for Algorithm~\ref{alg:1} designed by Method A.
+To overcome this drawback, Method B first employs the fingerprinting technique to check a subset selected from the given suffix and LCP arrays, then it utilizes the IS method to induce the final suffix and LCP arrays from the verified subset and literally compares them with the input arrays to ensure the correctness of the latter.
+Our experimental results indicate that the programs for Algorithm~\ref{alg:2} designed by Method B only take around half as much disk space as the program for Algorithm~\ref{alg:1} designed by Method A.
 
@@
 An alternative is to exploit a perfect hash function to convert each substring into a single integer such that any two substrings have a common hash value if and only if they are literally equal to each other, hence we can compare the hash values of two substrings instead to check their equality.
-Taking into account the high difficulty of finding such a perfect hash function to meet this requirement, we prefer using a Karp-Rabin fingerprinting function~\cite{Karp1987} to transform a substring into an integer called fingerprint.
+Taking into account the high difficulty of finding such a perfect hash function, we prefer using a Karp-Rabin fingerprinting function~\cite{Karp1987} to transform a substring into an integer called fingerprint.
 To be specific, suppose $L$ is a prime and $\delta$ is a number randomly chosen from $[1, L)$, the fingerprint ${\sf fp}(i, j)$ for a substring $x[i, j]$ can be iteratively calculated according to the formulas below as follows: scan $x$ rightward to iteratively compute ${\sf fp}(0, k)$ for all $k \in [0, n)$ using Formulas~\ref{formula:1}-\ref{formula:2}, record ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ during the calculation and subtract the former from the latter to obtain ${\sf fp}(i, j)$ using Formula~\ref{formula:3}.
@@
 Given that $L = 197$ and $\delta = 101$, lines 4-8 compute ${\sf fp}(0, p)$ iteratively according to Formulas~\ref{formula:1}-\ref{formula:2}.
-Then, lines 10-16 use these values to compute the fingerprints for all the target substrings.
+Then, lines 10-20 use these values to compute the fingerprints for all the target substrings.
 In more detail, consider the leftmost pair of neighboring suffixes in $sa$, that is ${\sf suf}(sa[0])$ and ${\sf suf}(sa[1])$, the substrings indicated by their LCP-value are $x[sa[0], sa[0] + lcp[1] - 1]$ and $x[sa[1], sa[1] + lcp[1] - 1]$, respectively.
@@
 Following the same way, ${\sf fp}(sa[1], sa[1] + lcp[1] - 1)$ is computed by reducing ${\sf fp}(0, sa[1] - 1)$ from ${\sf fp}(0, sa[1] + lcp[1] - 1)$.
-Hence, we obtain the fingerprints for these two substrings in lines 10-12 and see that they are equal to each other.
+Hence, we obtain the fingerprints for these two substrings in lines 10-14 and see that they are equal to each other.
 
@@
 	\includegraphics[width = 0.9\columnwidth]{example}
-	\caption{An example for computing and comparing fingerprints for substrings specifed by the LCP-Values of neighboring suffixes in the suffix array. \label{fig:example}}	
+	\caption{An example for computing and comparing fingerprints for substrings specifed by the LCP-values of neighboring suffixes in the suffix array. \label{fig:example}}	
 \end{figure}
@@
 It is clear that the above algorithm consumes $\mathcal{O}(n)$ time and space when implemented in internal memory.
-However, if the two auxiliary arrays cannot be wholly accommodated into RAM during the execution of S2, it suffers from a performance degradation caused by frequent random accesses to disks.
+However, if the two auxiliary arrays cannot fit entirely in RAM during the execution of S2, it suffers from a performance degradation caused by frequent random accesses to disks.
 Assume that $x$, $sa$ and $lcp$ are stored in external memory, we design Algorithm~\ref{alg:1} for conducting these I/O operations in a disk-friendly way.
-The main idea is to first sort data in their access order and then visit them by sequential reads.
-For the purpose, Algorithm~\ref{alg:1} first scans $sa$ and $lcp$ to produce $ST_1, ST_2, ST_3$ and sorts their tuples by 1st component in ascending order at the very beginning (lines~\ref{alg:1:a}-\ref{alg:1:b}).
+The main idea is to first sort data in their access order and then visit them sequentially.
+To the end, Algorithm~\ref{alg:1} first scans $sa$ and $lcp$ to produce $ST_1, ST_2, ST_3$ and sorts their tuples by 1st component in ascending order at the very beginning (lines~\ref{alg:1:a}-\ref{alg:1:b}).
 Afterward, it iteratively computes the fingerprints of all the prefixes according to Formulas~\ref{formula:1}-\ref{formula:2} and assigns them to the sorted tuples as following (lines~\ref{alg:1:c}-\ref{alg:1:d}): when figuring out ${\sf fp}(0, i - 1)$, extract each tuple $e$ with $e.1st = i$ from $ST_1/ST_2/ST_3$, update $e$  with ${\sf fp}(0, i - 1)$, and then forward $e$ to $ST_1'/ST_2'/ST_3'$.
@@
 One method is to keep a lookup table in internal memory to store $\delta^{lcp[i]}$ for all $i \in [0, n)$.
-This can answer the question in constant time, but it is impractical if the table is larger than the available memory size.
-Notice that the LCP of any two suffixes is smaller than $n$, thus we can return the answer in $\mathcal{O}(\lceil \log_2{n} \rceil)$ time using $\mathcal{O}(\lceil \log_2{n} \rceil)$ internal memory space based on the following idea.
-Suppose $e$ is an integer from $[0, n)$, it can be broken down into the form of $\Sigma_{i = 0}^{\lceil \log_2{n} \rceil}{k_i \cdot 2^i}$ by performing at most $\lceil \log_2{n} \rceil$ divisions, where $k_0, k_1, ..., k_{\lceil \log_2{n} \rceil}$ are integers from $\{0, 1\}$ .
+This can answer the question in constant time, but it is impractical if the lookup table exceeds the available memory capacity.
+Notice that the LCP of any two suffixes is smaller than $n$, thus we can return the answer in $\mathcal{O}(\lceil \log_2{n} \rceil)$ time using $\mathcal{O}(\lceil \log_2{n} \rceil)$ RAM space based on the following idea.
+Suppose $e$ is an integer from $[0, n)$, it can be broken down into the form of $\Sigma_{i = 0}^{\lceil \log_2{n} \rceil}{k_i \cdot 2^i}$ by performing at most $\lceil \log_2{n} \rceil$ divisions, where $k_0, k_1, ..., k_{\lceil \log_2{n} \rceil}$ are also integers from $\{0, 1\}$.
 Thereby, we have $\delta^e = \Pi_{i = 0}^{\lceil \log_2{n} \rceil}{\delta}^{k_i \cdot 2^i}$ by replacing $e$ with its decomposition, where the expression on the right side of the equation can be easily computed with $\{{\delta}^{1}, {\delta}^{2}, \dots, {\delta}^{2^{\lceil \log_2{n} \rceil}} \}$ already known.
@@
 Given an external memory model with RAM size $M$, disk size $D$ and block size $B$, all are in words, the time and I/O complexities for each scan are $\mathcal{O}(n)$ and $\mathcal{O}(n / B)$, respectively, while those for each sort are $\mathcal{O}(n\log_{M/ B}(n / B))$ and $\mathcal{O}((n / B)\log_{M / B}(n / B))$, respectively~\cite{Arge2013}.
-Algorithm~\ref{alg:1} reaches its peak disk use when sorting tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}.
-Suppose the input string and the suffix/LCP array are encoded using $\alpha$- and $\beta$-byte integers, respectively, and each fingerprint is represented by a $\gamma$-byte integer, it takes $(2 \cdot (2 \cdot \alpha + \beta)) \cdot n$ space for sorting $ST_1/ST_1'$ and $(2 \cdot (2 \cdot \alpha + \beta + \gamma)) \cdot n$ for sorting $ST_2/ST_2'$ and $ST_3/ST_3'$.
-To save disk space, our program implementing the algorithm sorts $ST_1/ST_1'$, $ST_2/ST_2'$ and $ST_3/ST_3'$ separately and performs a single scan over $x$ for each of them to obtain the target fingerprints, resulting in smaller space requirement but larger running time.
-The experimental study in Section~\ref{sec:experiment} indicates that this program is still space consuming, its peak disk use is 40 bytes per input character.
+This algorithm reaches its peak disk use when sorting tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}.
+Assume we represent each fingerprint by an $\alpha$-byte integer, and encode the input string and the suffix/LCP array by $\beta$- and $\gamma$-byte integers, respectively, then it takes $(2 \cdot (\alpha + 2 \cdot \gamma)) \cdot n$ space for sorting $ST_1/ST_1'$ and $(2 \cdot (\alpha + \beta + 2 \cdot \gamma)) \cdot n$ for sorting $ST_2/ST_2'$ and $ST_3/ST_3'$.
+To improve space efficiency, our program implementing Algorithm~\ref{alg:1} sorts $ST_1/ST_1'$, $ST_2/ST_2'$ and $ST_3/ST_3'$ separately and performs a single scan over $x$ for each of them to obtain the target fingerprints, resulting in smaller space consumption but larger running time.
+However, from our experiments in Section~\ref{sec:experiment}, this program is still rather space consuming, its peak disk use is $40$ times the size of $x$.
 
@@
 
-In this part, we describe an alternative checking method based on the induced sorting principle.
-Compared with Algorithm~\ref{alg:1}, our programs for Algorithm~\ref{alg:2} designed by this method take around half disk space on real-world datasets.
+In this part, we design another checking method using the fingerprinting and the induced sorting techniques.
 Before the presentation, we introduce some symbols and notations used in the following paragraphs.
@@
 
-The induced sorting principle has been extensively used to design efficient algorithms for constructing the suffix and LCP arrays on internal and external memory models.
-An IS-based construction algorithm mainly consists of a reduction phase for computing $sa^*$ and $lcp^*$, followed by an induction phase for inducing $sa$ and $lcp$ from $sa^*$ and $lcp^*$~\footnote{In the interest of completeness, we give an overview of the induction phase in Appendix~\ref{sec:appendix}.}.
-Given that $sa^*$ and $lcp^*$ are already known, we can produce the final suffix and LCP arrays by calling the inducing process of an existing IS-based construction algorithm.
-This enlightens us to design a checker based on Lemma~\ref{lemma:2}.
+An IS suffix and LCP arrays construction algorithm mainly consists of a reduction phase for computing $sa^*$ and $lcp^*$, followed by an induction phase for inducing $sa$ and $lcp$ from $sa^*$ and $lcp^*$~\footnote{In the interest of completeness, we give an overview of the induction phase in Appendix~\ref{sec:appendix}.}.
+This enlightens us to design a checker based on Lemma~\ref{lemma:2}, provided that $sa^*$ and $lcp^*$ are already known.
 
@@
 \begin{Corollary} \label{corollary:2}
-Both $sa[0, n)$ and $lcp[0, n)$ are correct with a high probability given the following conditions, for all $i \in [1, n_1)$ and $j \in [0, n)$:
+Both $sa[0, n)$ and $lcp[0, n)$ are correct with a high probability given the following conditions:
 \begin{enumerate}[(1)]
 	\item
-	$x[sa^*[i]]$ is S*-type, and $sa^*[i] \ne sa^*[k]$ for all $k \in [0, n_1)$ and $k \ne i$.
+	$x[sa^*[i]]$ is S*-type and $sa^*[j] \ne sa^*[i]$ for $i, j \in [0, n_1)$ and $i \ne j$.
 	\item
-	${\sf fp}(sa^*[i], sa^*[i] + lcp^*[i] - 1) = {\sf fp}(sa^*[i - 1], sa^*[i - 1] + lcp^*[i] - 1)$.
+	${\sf fp}(sa^*[i], sa^*[i] + lcp^*[i] - 1) = {\sf fp}(sa^*[i - 1], sa^*[i - 1] + lcp^*[i] - 1)$ for $i \in [1,n_1)$.
 	\item
-	$x[sa^*[i] + lcp^*[i]] > x[sa^*[i - 1] + lcp^*[i]]$.
+	$x[sa^*[i] + lcp^*[i]] > x[sa^*[i - 1] + lcp^*[i]]$ for $i \in [1, n_1)$.
 	\item
-	$sa[j] = sa'[j]$ and $lcp[j] = lcp'[j]$ for $j \in [0, n)$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by the IS method.
+	$sa[i] = sa'[i]$ and $lcp[i] = lcp'[i]$ for $i \in [0, n)$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by the IS method.
 \end{enumerate}
@@
 The first step of Algorithm~\ref{alg:2} is to compute and verify $sa^*$ and $lcp^*$.
-According to their definitions, $sa^*$ can be produced by sequentially retrieving the S*-type suffixes from $sa$ and the LCP-value of two successive S*-type suffixes in $sa$, say ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$, is equal to the minimal of $\{lcp[i + 1], ..., lcp[j - 1], lcp[j]\}$.
+According to their definitions, $sa^*$ can be produced by sequentially retrieving the S*-type suffixes from $sa$, while the LCP-value of two successive S*-type suffixes in $sa$, say ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$, is equal to the minimal of $\{lcp[i + 1], ..., lcp[j - 1], lcp[j]\}$.
 Hence, the proposed algorithm first sorts all the suffixes in $sa$ by their starting positions~(lines~\ref{alg:2:a}-\ref{alg:2:b}) and then scans $x$ only once to pick out the S*-type suffixes~(lines~\ref{alg:2:c}-\ref{alg:2:d}).
@@
 Meanwhile, it calculates the LCP-value for each pair of the neighboring suffixes in $sa^*$ by tracing the minimal over the $lcp$ interval indicated by the two suffixes.
-Notice that, we check condition (1) in Corollary~\ref{corollary:2} during the time when visiting the suffixes in position order (lines~\ref{alg:2:e}-\ref{alg:2:f}) and conditions (2)-(3) by calling Algorithm~\ref{alg:1} with $sa^*$ and $lcp^*$ as input.
-Suppose $sa^*$ and $lcp^*$ are both correct, then Algorithm~\ref{alg:2} invokes the inducing process of an existing IS-based construction algorithm to induce $sa'$ and $lcp'$, which are a copy of the final suffix and LCP arrays, from the two verified arrays~(line~\ref{alg:2:k}) and literally compares them with $sa$ and $lcp$ to complete the whole checking process~(lines~\ref{alg:2:l}-\ref{alg:2:m}).
+Notice that, we check condition (1) in Corollary~\ref{corollary:2} during the time when visiting the suffixes in position order (lines~\ref{alg:2:e}-\ref{alg:2:f}) and conditions (2)-(3) by calling Algorithm~\ref{alg:1} with $sa^*$ and $lcp^*$ as inputs.
+If $sa^*$ and $lcp^*$ are both correct, then Algorithm~\ref{alg:2} invokes an inducing process to employ IS method for inducing $sa'$ and $lcp'$ from the two verified arrays~(line~\ref{alg:2:k}) and literally compares them with $sa$ and $lcp$ to complete the whole checking process~(lines~\ref{alg:2:l}-\ref{alg:2:m}).
 
@@
 If $v_1 = v_2$, then $v_2$ is correct and we further use this value to induce the remaining suffix/LCP items.
-The key point here is to retrieve items of $sa/lcp$ from external storage as fast as possible.
-This can be done by conducting sequential I/O operations if we provide a read pointer together with a buffer for each suffix/LCP sub-bucket.
-We describe below more details of the adapted inducing process, where $lp_1/lp_2$ and $sp_1/sp_2$ are file pointer arrays for reading items from the sub-buckets of $sa$ and $lcp$.
+We describe more details of the adapted inducing process as below, where $lp_1/lp_2$ and $sp_1/sp_2$ point to the next items to be visited in the L-type and S-type sub-buckets, respectively.
 
@@
 
-Algorithm~\ref{alg:2} mainly consists of two parts, where the first part for checking $sa^*$ and $lcp^*$ can be done within sorting time and the second part for checking $sa$ and $lcp$ can be done in linear time.
-Clearly, the space complexity of part one is dependent upon the number of S*-type suffixes.
-As will be seen from Section~\ref{sec:experiment}, the programs for Algorithm~\ref{alg:2} take around $15n$ to check $sa^*$ and $lcp^*$, which is about one-third as that for Algorithm~\ref{alg:1} to check $sa$ and $lcp$.
-This corresponds to the ratio of S*-type suffixes to all in the real-world datasets.
-From our experiments, these programs take more disk space during the execution of inducing process, their peak disk use is about half as that for Algorithm~\ref{alg:1}.
+Algorithm~\ref{alg:2} consists of two steps.
+The first step for checking $sa^*$ and $lcp^*$ can be done in sorting complexity, while the second step for checking $sa$ and $lcp$ can also be done in sorting complexity for inducing the copy of suffix and LCP arrays by using external-memory priority queues.
+The experimental results in Section~\ref{sec:experiment} indicate that the disk use of the programs for this algorithm and its tuned version are around $21n$ and $26n$, respectively, where the peak values are achieved when executing the second step.
 
@@
 
-For implementation simplicity, our programs for the algorithms proposed in the previous sections use the external-memory containers provided by the STXXL library~\cite{Dementiev2007} to manage read/write operations on disks.
-We make a performance evaluation by running them on the real-world corpora listed in Table~\ref{tbl:1}, where three measures normalized by the size of input string are investigated:
+For engineering simplicity, the algorithms proposed in the previous sections are implemented using the external-memory containers from the STXXL library~\cite{Dementiev2007}.
+We make a performance evaluation by running programs on the real-world corpora listed in Table~\ref{tbl:1}, where three measures normalized by the size of the input string are investigated:
 
@@
 The experimental platform is a server equipped with an Intel Core i3-550 CPU, 4 GiB RAM and 2 TiB HD.
-All the programs are compiled by gcc/g++ 4.8.4 with -O3 options on ubuntu 14.04 64-bit operating system and each program is allowed to use 3 GiB RAM.
+All the programs are compiled by gcc/g++ 4.8.4 with -O3 options on ubuntu 14.04 64-bit operating system, and each program is allowed to use 3 GiB RAM.
 For denotation convenience, we use "ProgA" and "ProgB" to represent the programs for Algorithms~\ref{alg:1} and~\ref{alg:2}, respectively.
@@
 Specifically, the I/O volume of ProgA keeps at $155n$ for all the three datasets, while that of ProgB rises up to nearly $200n$ on average.
-Besides, the peak disk use of ProgB is about $26/40=0.65$ as ProgA.
+Besides, the PDU of ProgB is about $26/40=0.65$ as ProgA.
 Recall that Algorithm~\ref{alg:2} invokes Algorithm~\ref{alg:1} to check the suffix and LCP arrays for the S*-type suffixes.
@@
 For a better insight, we collect in Table~\ref{tbl:2} the performance overhead of ProgB and ProgA when checking the suffix and LCP arrays of S*-type suffixes and all, respectively.
-As can be observed, the mean ratio of the number of S*-type suffixes to the number of all the suffixes is around 0.30 for the datasets under investigation, while the mean ratios of time, space and I/O volume for checking $sa^*$ and $lcp^*$ to that for checking $sa$ and $lcp$ are 0.38, 0.57 and 0.60, respectively.
+As shown in the table, the mean ratio of the number of S*-type suffixes to the number of all the suffixes is around 0.30 for the datasets under investigation, while the mean ratios of time, space and I/O volume for checking $sa^*$ and $lcp^*$ to that for checking $sa$ and $lcp$ are 0.38, 0.57 and 0.60, respectively.
 
@@
 By adopting the space optimization scheme introduced in Section~\ref{sec:method2:algorithm}, we adapt Algorithm~\ref{alg:2} and evaluate the tuned version of ProgB, called ProgB+, in comparison with ProgA and ProgB.
-Fig.~\ref{fig:performance_analysis} shows that the maximum space requirement for ProgB+ is about $21n$, which is much less than that of ProgB and even only half as that of ProgA.
-In addition, progB+ outperforms its prototype with respect to time and I/O efficiency and is faster than ProgA when handling "proteins".
+Fig.~\ref{fig:performance_analysis} shows that the maximum space requirement for ProgB+ is about $21n$, which is much less than that of ProgB and only half as that of ProgA.
+In addition, progB+ outperforms its prototype with respect to time and I/O efficiencies and is even faster than ProgA when handling "uniprot".
 We also investigate the performance trend of the three programs on the prefix of "enwiki" with the length varying in $\{1, 2, 4, 8\}$ GiB.
-In Figure~\ref{fig:performance_analysis2}, the peak disk use for each program remains unchanged, but their speed become slower as the prefix length increases due to the performance degradation of the external memory sorter used in our programs.
+In Figure~\ref{fig:performance_analysis2}, the peak disk use for each program remains unchanged, but their speed become slower as the prefix length increases due to the performance degradation of the external memory sorter exploited in our programs.
 This can be also observed from Table~\ref{tbl:2}, where ProgB+ keeps the I/O volume around $90n$ with the prefix length of "enwiki" varying from $1$ to $8$ GiB but its running time rises from $1.05$ to $1.33$.
@@
 
-We select these programs because they are currently the fastest suffix and LCP arrays builders available to us.
-A runtime breakdown of the programs for these solutions on the prefixes of "enwiki" is given in Table~\ref{tbl:3}.
-The program for Solution 2 is about two times faster than that for Solution 1 and twice as fast as ProgA, which is mainly due to the high speed of pSAscan in this experiment.
+We select these solutions because they are the current fastest available to us.
+A runtime breakdown of these solutions on the prefixes of "enwiki" is given in Table~\ref{tbl:3}, from which we see that Solution 2 is about two times faster than Solution 1 and twice as fast as ProgA.
+This phenomenon is mainly due to the high speed of pSAscan in the experiment.
 However, it is worthy of pointing out that both pSAscan and Sparse-$\phi$ are of the time and I/O complexities proportional to $n^2/M$.
@@
 		\multirow{2}{*}{Dataset} & \multicolumn{3}{|c|}{Solution 1} & \multicolumn{3}{c|}{Solution 2} & \multirow{2}{*}{ProgA} & \multirow{2}{*}{ProgB+} \\\cline{2-7}
-		 & eSAIS & sequential sparse-$\phi$ & total & pSAscan & parallel sparse-$\phi$ & total & & \\\hline
+		 & eSAIS & sequential Sparse-$\phi$ & total & pSAscan & parallel Sparse-$\phi$ & total & & \\\hline
 		enwiki\_1g & 2.21 & 0.61 & 2.82 & 0.39 & 0.59 & 0.98 & 1.70 & 2.54 \\\hline
@@
 It is possible to speed up the sorting process by high-performance radix-sort GPU algorithms.
-Secondly, Method B checks the suffix and LCP arrays using the induced sorting principle.
-At the time of writing this paper, the existing IS-based suffix/LCP array construction algorithms are naturally sequential.
-We have been conducting a study to design IS-based parallel algorithms, this work may also improve the implementation design of Algorithm~\ref{alg:2}.
-
-Method A is able to check any set containing one or multiple pairs of lexicographically neighboring or non-neighboring suffixes.
-This feature can be applied to various scenarios.
-For example, a suffix/LCP array may be broken due to software or hardware malfunctions.
-If a backup is not available and it is too time-consuming to rebuild the whole array, then we can locate the bad areas quickly using Algorithm~\ref{alg:1} and restore the partial SA for each area by calling a sparse SA construction algorithm.
-Another example is to check the correctness of a sparse SA.
-Because the number of suffixes in a sparse SA is commonly much smaller than that in the full SA, Algorithm~\ref{alg:1} could become an efficient verification solution.
+Secondly, Method B checks the suffix and LCP arrays using the IS method.
+At the time of writing this paper, the existing IS suffix/LCP array construction algorithms are naturally sequential.
+We have been conducting a study to design IS parallel algorithms, this work may also improve the implementation design of Algorithm~\ref{alg:2}.
 
@@
 For example, several algorithms for induced sorting a suffix and/or LCP arrays were proposed these years \cite{Nong15,Nong14,Bingmann12}, with different methods for solving the key problem of retrieving the preceding character of a sorted suffix in the inducing process.
-A recent work \cite{Karkkainen2017} for engineering these induced sorting methods with some implementation optimizing techniques achieves a significant improvement over the previous results.
+A recent work \cite{Karkkainen2017} for engineering these IS methods with some implementation optimizing techniques achieves a significant improvement over the previous results.
 As reported, the peak disk use is $7n$ for 32-bit integers.
-Because the induced sorting process is the performance bottleneck for Method B, it is reasonable to expect that a better engineering implementation of the method will yield a remarkable performance improvement.
+Because the inducing process is the performance bottleneck for Method B, it is reasonable to expect that a better engineering implementation of the method will yield a remarkable performance improvement.
 {\bf An optimized engineering of our methods is out of the scope of this paper and will be addressed elsewhere.}
+
+Finally, we emphasize that Method A is able to check any set containing one or multiple pairs of lexicographically neighboring or non-neighboring suffixes.
+This feature can be applied to various scenarios.
+For example, a suffix/LCP array may be broken due to software or hardware malfunctions.
+If a backup is not available and it is too time-consuming to rebuild the whole array, then we can locate the bad areas quickly using Algorithm~\ref{alg:1} and restore the partial SA for each area by calling a sparse SA construction algorithm.
+Another example is to check the correctness of a sparse SA.
+Because the number of suffixes in a sparse SA is commonly much smaller than that in the full SA, Algorithm~\ref{alg:1} could become an efficient verification solution in this case.
 
@@
 Theoretically, the external-memory algorithms designed by these methods have better time and I/O complexities compared to the existing fastest construction algorithms.
-Our experimental results indicate that the current programs for Algorithm~\ref{alg:2} designed by Method B run slower than that for Algorithm~\ref{alg:1} designed by Method A, but they are much more space-efficient than the latter.
-As discussed in Section~\ref{sec:experiment}, there still remains much room for improving the implementations of the proposed algorithms.
-Our experimental programs can be further optimized to achieve higher performance, in particular for checking arrays of constant alphabets that are most common in practice.
-The optimized programs will run much faster and use at most $n$ integers as the working space in addition to the input arrays.
+From our experiments, the current program for Algorithm~\ref{alg:2} runs slower than that for Algorithm~\ref{alg:1}, but the former is more space efficient than the latter.
+As discussed in Section~\ref{sec:experiment}, our experimental programs can be further optimized to achieve better performance, especially when checking arrays of constant alphabets that are most common in practice.
+%In this particular case, the optimized programs will run much faster and use at most $n$ integers as the working space in addition to the input arrays.
 
 From our perspective, a checker should be not only fast but also general.
-For program debugging, we usually check the output of a builder by comparing it with that of another builder.
+In practice, we usually check a constructed array from a builder by comparing it with that from another builder.
 But this is not feasible in all the cases, for example, an algorithm for constructing infinite-order\footnote{A suffix array is infinite-order if the suffixes are sorted up to their ends, or else finite-order.} array can not be directly used to check a finite-order array and vise versa.
-On the contrary, our first method can be generalized to check the correctness of the lexical order and the LCP values of any pairs of suffixes.
+On the contrary, Method A can be generalized to check the correctness of the lexical order and the LCP-values of any pairs of suffixes.
 This makes it possible for verifying any full or sparse suffix/LCP array of any order.
 
-The IS method has been applied to successfully design a number of suffix and LCP arrays construction algorithms.
+The IS method has been employed to successfully design a number of suffix and LCP arrays construction algorithms.
 A recent work \cite{Karkkainen2017} reports that a careful engineering of the IS in external memory can build a suffix array using only $7n$ bytes for $n\le 2^{32}$, which is approaching the optimal in respect to $5n$ bytes for the IS in internal memory.
@@
 
-Recall that the lexical order of two suffixes starting with $x[i]$ and $x[j]$ can be determined by sequentially comparing their characters until finding a position $k$ such that $x[i, i + k) = x[j, j + k)$ and $x[i + k] \ne x[j + k]$.
-In other words, we have ${\sf suf}(i) < {\sf suf}(j)$ if (1) $x[i] < x[j]$~$(k = 0)$ or (2) $x[i] = x[j]$ and ${\sf suf}(i + 1) < {\sf suf}(j + 1)$~$(k > 0)$; otherwise, ${\sf suf}(i) > {\sf suf}(j)$.
-This rule is used by the IS-based SA construction algorithms to sort suffixes during the induction phase:
+Notice that ${\sf suf}(i)$ is lexicographically smaller than ${\sf suf}(j)$ if and only if (1) $x[i] < x[j]$ or (2) $x[i] = x[j]$ and ${\sf suf}(i + 1) < {\sf suf}(j + 1)$.
+This property constitutes the core part of the IS method and has been utilized by SA-IS and other IS variants to derive the order of unsorted suffixes from the order of sorted ones following the 3-step induction phase below.
 
@@
 In brief, given $sa^*$, S1 inserts all the S*-type suffixes into $sa$ in their lexical order.
-Then, S2-S3 induce the order of L- and S-type suffixes from those already sorted in $sa$, respectively, where the relative order of two suffixes induced into the same sub-bucket matches their insertion order according to the rule stated above.
-To be more specific, we show in Fig.~\ref{fig:example2} a running example of the induction phase.
+Then, S2-S3 induce the order of L- and S-type suffixes from those already sorted in $sa$, respectively, where the relative order of two suffixes induced into the same sub-bucket matches their insertion order according to the previously stated property.
 
+We show in Fig.~\ref{fig:example2} a running example with more details.
 As depicted, the input string $x$ contains 6 S*-type suffixes sorted in line 3.
 When finished inserting the S*-type suffixes in lines 5-6, we first find the head of each L-type sub-bucket (marked by the symbol $\wedge$) and insert ${\sf suf}(13)$ into $sa$.
-Notice that ${\sf suf}(13)$ consists of only one character, it must be the smallest L-type suffixes starting with $1$.
+Notice that ${\sf suf}(13)$ is a single character, it must be the smallest L-type suffixes starting with $1$.
 Thus, we put ${\sf suf}(13)$ into the leftmost position in ${\sf sa\_bkt_L}(1)$ in line 8.
@@
 
-The work presented in~\cite{Fischer11} describes how to compute the LCP array during the execution of S2-S3.
-Given two suffixes placed at the neighboring positions in $sa$, their LCP-value can be computed according to one of the following two cases in respect to whether or not they are inserted into the same sub-bucket: if yes, then their LCP-value is one greater than that of the two suffixes from which inducing them; otherwise, their LCP-value equals to zero.
-In this way, we can determine $lcp[i]$ immediately after the computation of $sa[i]$.
-The problem here is how to obtain the LCP-values of these inducing suffixes starting at the next positions in $x$, which is modeled as a range minimum query in~\cite{Fischer11} and can be answered within amortized $\mathcal{O}(1)$ time.
-For example, when scanning from $sa[0]$ to $sa[5]$ in lines 10-21 of Fig.~\ref{fig:example2}, we induce ${\sf suf}(12)$ and ${\sf suf}(6)$ into the neighboring positions in ${\sf sa\_bkt_L(2)}$.
-During the scan, if we keep recording the minimal of $lcp(0, 5]$ in a variable, then we can obtain the LCP-value of the suffixes ${\sf suf}(13)$ and ${\sf suf}(5)$ from this variable when putting ${\sf suf}(6)$ into $sa$.
+The work presented in~\cite{Fischer11} describes how to compute the LCP array during S2-S3 of the induction phase.
+Specifically, for any two suffixes placed at the neighboring positions in $sa$, their LCP-value can be computed according to one of the following two cases in respect to whether or not they are inserted into the same sub-bucket: if yes, then the LCP-value is one greater than that of the two suffixes from which inducing them; otherwise, the LCP-value is zero.
+The key operation herein is to compute the LCP-value of the inducing suffixes at the same time when inserting the induced suffixes into $sa$.
+For example, in lines 10-21 of Fig.~\ref{fig:example2}, we induce ${\sf suf}(12)$ and ${\sf suf}(6)$ into the neighboring positions of ${\sf sa\_bkt_L(2)}$, respectively.
+If we keep recording the minimal over $lcp(0, 5]$, then we can obtain the LCP-value of the inducing suffixes ${\sf suf}(13)$ and ${\sf suf}(5)$ immediately after putting ${\sf suf}(6)$ into $sa$.
+This problem is modeled as a range minimum query in~\cite{Fischer11} and can be answered within amortized $\mathcal{O}(1)$ time.
 

### 2017-03-18 draft-alternative/draft.tex
2017/03/18

--- 2017-03-14 draft/draft.tex
@@
 program debugging and verifying the arrays constructed by probabilistic algorithms.
-In this paper, we propose two probabilistic methods to check the suffix and LCP arrays of constant or integer alphabets in external memory by using a Karp-Rabin fingerprinting technique, where the checking result is wrong only with a negligible error probability.
+Two probabilistic methods are proposed to check the suffix and LCP arrays of constant or integer alphabets in external memory using a Karp-Rabin fingerprinting technique, where the checking  is wrong only with a negligible error probability.
 The first method checks the lexicographical order and the LCP-value of two suffixes by computing and comparing the fingerprints of their LCPs.
-This method is rather general in terms of that it can verify any full or sparse suffix/LCP array of any order.
-The second method is more space efficient, it first employs the fingerprinting technique to verify a subset of the given suffix and LCP arrays, from which then a copy of the suffix and LCP arrays is produced using the induced sorting principle and compared with the given arrays for verification, where the copy of the induced suffix and LCP arrays can be removed for constant alphabets.
+This method is general in terms of that it can verify any full or sparse suffix/LCP array of any order.
+The second method uses less space, it first employs the fingerprinting technique to verify a subset of the given suffix and LCP arrays, from which two new suffix and LCP arrays are induced and compared with the given arrays for verification, where the induced suffix and LCP arrays can be removed for constant alphabets to save space.
 
@@
 
+{\color{blue} 
+Abstract changed. \\
+Many changes, not to mark. \\
+Some marked in blue for your check. \\
+The figures and tables should be near to the content talking about them. \\
+Do not use too many: we, based, following, clearly...  \\
+}
+
 \section{Introduction}\label{sec:introduction}
@@
 In respect of the research on LCP array construction algorithms, the existing works can be classified into two categories with regard to their input requirements, where the algorithms from the first category compute both suffix and LCP arrays at the same time with the original text only~\cite{Fischer11, Bingmann12, Flick2015}, and those from the second category carry out the computation by taking SA and/or Burrows-Wheeler transform (BWT) as additional inputs~\cite{Kasai2001,Karkkainen2009, Fischer11, Puglisi2008, Deo2013}.
-So far, the algorithms designed by the induced sorting~(IS) principle take linear time and space to run and get the best results on both internal and external memory~\cite{Nong11, Karkkainen2014, Karkkainen2017}.
+So far, the algorithms designed by the induced sorting~(IS) principle take linear time and space to run and get the best results on both internal and external memory~\cite{Nong11, esais}.
 In addition to the sequential algorithms, there are also parallel algorithms proposed to achieve high performance by fully using the available multi-core CPUs and/or GPUs~\cite{Osipov2012, Deo2013, Wang2015, Karkkainen2015, Karkkainen2016}.
@@
 
-Given a string $x[0, n-1]$ drawn from a constant or integer alphabet $\Sigma$ of size $O(1)$ or $O(n)$, respectively, the suffix array of $x$, denoted by $sa$, is a permutation of $\{0, 1, ..., n - 1\}$ such that ${\sf suf}(sa[i]) < {\sf suf}(sa[j])$ for $i, j \in [0, n)$ and $i < j$, where ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$ are two suffixes starting with $x[sa[i]]$ and $x[sa[j]]$, respectively.
+Given a string $x[0, n-1]$ drawn from a constant or integer alphabet $\Sigma$ of size $\mathcal{O}(1)$ or $\mathcal{O}(n)$, respectively, the suffix array of $x$, denoted by $sa$, is a permutation of $\{0, 1, ..., n - 1\}$ such that ${\sf suf}(sa[i]) < {\sf suf}(sa[j])$ for $i, j \in [0, n)$ and $i < j$, where ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$ are two suffixes starting with $x[sa[i]]$ and $x[sa[j]]$, respectively.
 Particularly, we say ${\sf suf}(sa[j])$ is a lexical neighbor of ${\sf suf}(sa[i])$ if $|i - j| = 1$.
 The LCP array of $x$, denoted by $lcp$, consists of $n$ integers, where $lcp[0]=0$ and $lcp[i]$ records the LCP-value of ${\sf suf}(sa[i])$ and ${\sf suf}(sa[i - 1])$ for $i \in [1, n)$.
+A suffix/LCP array is infinite-order if the suffixes/LCPs are sorted/counted up to their ends, respectively, or else finite-order.
 
@@
 
-According to the above definitions, we give in Lemma~\ref{lemma:1} the sufficient and necessary conditions for checking suffix and LCP arrays.
-Notice that the lexical order and the LCP-value of any two suffixes in $x$ can be computed by literally comparing their characters rightward.
-For convenience, we append a virtual character to $x$ and assume it to be lexicographically smaller than any characters in $\Sigma$.
-Because all the suffixes differ in length and end with the virtual character, any two suffixes are different.
+According to the above definitions, we give in Lemma~\ref{lemma:1} the sufficient and necessary conditions for checking both suffix and LCP arrays.
+Notice that the lexical order and the LCP-value of any two suffixes in $x$ can be computed by literally comparing their characters.
+For convenience, we append a virtual character to $x$ and assume it to be lexicographically smaller than any characters in $\Sigma$, hence any two suffixes are different.
 
@@
 \begin{IEEEproof}
-	Both the sufficiency and necessity are immediately seen from the definition of suffix and LCP arrays.
-Specifically, condition (1) demonstrates that all the suffixes in $x$ are sorted in $sa$, while conditions (2)-(3) indicate that the lexical order and the LCP-value of any two neighboring suffixes in $sa$ are both correct.
+	Both the sufficiency and necessity are immediately from the definitions of suffix and LCP arrays.
+Condition 1 guarantees that each suffix is in $sa$, conditions 2 and 3 guarantees that the lexical order and the LCP-value of any two neighboring suffixes in $sa$ are both correct.
 \end{IEEEproof}
 
-If we directly compare the characters of two suffixes, the worst case time is $O(n)$.
-An alternative is to exploit a perfect hash function to convert each substring into a single integer such that any two substrings have a common hash value if and only if they are literally equal to each other, hence we can compare the hash values of two substrings instead to check their equality.
-Taking into account the high difficulty of finding such a perfect hash function to meet this requirement, we prefer using a Karp-Rabin fingerprinting function~\cite{Karp1987} to transform a substring into an integer called fingerprint.
-To be specific, suppose $L$ is a prime and $\delta$ is a number randomly chosen from $[1, L)$, the fingerprint ${\sf fp}(i, j)$ for a substring $x[i, j]$ can be iteratively calculated according to the formulas below as follows: scan $x$ rightward to iteratively compute ${\sf fp}(0, k)$ for all $k \in [0, n)$ using Formulas~\ref{formula:1}-\ref{formula:2}, record ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ during the calculation and subtract the former from the latter to obtain ${\sf fp}(i, j)$ using Formula~\ref{formula:3}.
+Directly comparing the characters of two suffixes to determine their LCP has the worst case time of $O(n)$.
+An alternative is to exploit a perfect hash function to convert each substring into a single integer such that any two substrings have a common hash value if and only if they are literally equal to each other, hence the hash values of two substrings can be compared instead to check the equality of two substrings.
+Taking into account the high difficulty of finding a perfect hash function to meet this requirement, we prefer using a Karp-Rabin fingerprinting function~\cite{Karp1987} to transform a substring into an integer called fingerprint.
+To be specific, suppose $L$ is a prime and $\delta$ is a number randomly chosen from $[1, L)$, the fingerprint ${\sf fp}(i, j)$ for a substring $x[i, j]$ can be iteratively calculated according to the formulas below: scan $x$ rightward to iteratively compute ${\sf fp}(0, k)$ for all $k \in [0, n)$ using Formulas~\ref{formula:1}-\ref{formula:2}, record ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ during the calculation and subtract the former from the latter to obtain ${\sf fp}(i, j)$ using Formula~\ref{formula:3}.
 
@@
 Notice that two equal substrings always share a common fingerprint, but the inverse is not true.
-It has been proved in~\cite{Karp1987} that the probability of a false match can be reduced to a negligible level by setting $L$ to a large value\footnote{This property is utilized in~\cite{Bille2013} to design a probabilistic algorithm for computing a sparse suffix array.}.
+It has been proven in~\cite{Karp1987} that the probability of a false match can be reduced to a negligible level by setting $L$ to a large value\footnote{This property is utilized in~\cite{Bille2013} to design a probabilistic algorithm for computing a sparse suffix array.}.
 Hence, we have:
@@
 \begin{Corollary} \label{corollary:1}
-	Both $sa[0, n)$ and $lcp[0, n)$ are correct with a high probability given the following conditions, for all $i \in [1, n)$:
+	Both $sa[0, n)$ and $lcp[0, n)$ are correct with a high probability given these conditions, for all $i \in [1, n)$:
 
@@
 Then, lines 10-16 use these values to compute the fingerprints for all the target substrings.
-In more detail, consider the leftmost pair of neighboring suffixes in $sa$, that is ${\sf suf}(sa[0])$ and ${\sf suf}(sa[1])$, the substrings indicated by their LCP-value are $x[sa[0], sa[0] + lcp[1] - 1]$ and $x[sa[1], sa[1] + lcp[1] - 1]$, respectively.
-According to Formula~\ref{formula:3}, ${\sf fp}(sa[0], sa[0] + lcp[1] - 1)$ is equal to the difference between ${\sf fp}(0, sa[0] - 1)$ and ${\sf fp}(0, sa[0] + lcp[1] - 1)$, both of which have been calculated beforehand.
+In more detail, consider the leftmost pair of neighboring suffixes in $sa$, i.e.
+${\sf suf}(sa[0])$ and ${\sf suf}(sa[1])$, the substrings given by their LCP-value are $x[sa[0], sa[0] + lcp[1] - 1]$ and $x[sa[1], sa[1] + lcp[1] - 1]$, respectively.
+According to Formula~\ref{formula:3}, ${\sf fp}(sa[0], sa[0] + lcp[1] - 1)$ is equal to the difference between ${\sf fp}(0, sa[0] - 1)$ and ${\sf fp}(0, sa[0] + lcp[1] - 1)$, both have been calculated.
 Following the same way, ${\sf fp}(sa[1], sa[1] + lcp[1] - 1)$ is computed by reducing ${\sf fp}(0, sa[1] - 1)$ from ${\sf fp}(0, sa[1] + lcp[1] - 1)$.
@@
 	\includegraphics[width = 0.9\columnwidth]{example}
-	\caption{An example for computing and comparing fingerprints for substrings specifed by the LCP-Values of neighboring suffixes in the suffix array. \label{fig:example}}	
+	\caption{An example for computing and comparing fingerprints for substrings specified by the LCP-values of neighboring suffixes in $sa$. \label{fig:example}}	
 \end{figure}
@@
 
-We describe an algorithm for checking the conditions in Corollary~\ref{corollary:1} on random access models, of which the core part is to check the lexical order and the LCP-value for each pair of neighboring suffixes in $sa$ on-the-fly during the scan of $sa$ and $lcp$.
-This is done by using Formulas~\ref{formula:1}-\ref{formula:3} following our discussion in the previous subsection.
-Two zero-initialized array, namely $fp$ and $mk$, are introduced to facilitate the checking process, where $fp$ is for storing the fingerprints of all the prefixes in $x$ and $mk$ is for checking whether or not each number of $\{0, 1, ..., n - 1\}$ is present in $sa$.
+We describe an approach for checking the conditions in Corollary~\ref{corollary:1} on random access models, of which the core part is to check the lexical order and the LCP-value for each pair of neighboring suffixes in $sa$ during the scan of $sa$ and $lcp$.
+This is done by using Formulas~\ref{formula:1}-\ref{formula:3}.
+Two zero-initialized arrays $fp$ and $mk$ are introduced to facilitate the checking process, where $fp$ is for storing the fingerprints of all the prefixes in $x$ and $mk$ is for checking whether $sa$ stores a permutation of $\{0, 1, ..., n - 1\}$.
 
@@
 	\item [S1]
-	Scan $x$ rightward with $i$ increasing from $0$ to $n - 1$. For each scanned $x[i]$, compute ${\sf fp}(0, i)$ and assign the value to $fp[i]$.
+	Scan $x$ with $i$ increasing from $0$ to $n - 1$, for each scanned $x[i]$, compute ${\sf fp}(0, i)$ and assign to $fp[i]$.
 
 	\item [S2]
-	Scan $sa$ and $lcp$ rightward with $i$ increasing from $1$ to $n - 1$. For each scanned $sa[i]$ and $lcp[i]$, let $u = sa[i], v = lcp[i], w = sa[i - 1]$ and perform substeps (a)-(c) in sequence:
+	Scan $sa$ and $lcp$ with $i$ increasing from $1$ to $n - 1$, for each scanned $sa[i]$ and $lcp[i]$, let $u = sa[i], v = lcp[i]$ and $w = sa[i - 1]$, perform:
 
@@
 		\item
-		Retrieve $fp[u - 1]$ and $fp[u + v - 1]$ from $fp$ to compute ${\sf fp}(u, u + v - 1)$. Set $mk[u]$ to $1$.
+		Retrieve $fp[u - 1]$ and $fp[u + v - 1]$ from $fp$ to compute ${\sf fp}(u, u + v - 1)$, set $mk[u]=1$;
 
 		\item
-		Retrieve $fp[w - 1]$ and $fp[w + v - 1]$ from $fp$ to compute ${\sf fp}(w, w + v - 1)$.
+		Retrieve $fp[w - 1]$ and $fp[w + v - 1]$ from $fp$ to compute ${\sf fp}(w, w + v - 1)$;
 
 		\item
-		Check if ${\sf fp}(u, u + v - 1) = {\sf fp}(w, w + v - 1)$ and $x[u + v] > x[w + v]$.
+		Check if ${\sf fp}(u, u + v - 1) = {\sf fp}(w, w + v - 1)$ and $x[u + v] > x[w + v]$;
 
@@
 
-It is clear that the above algorithm consumes $\mathcal{O}(n)$ time and space when implemented in internal memory.
-However, if the two auxiliary arrays cannot be wholly accommodated into RAM during the execution of S2, it suffers from a performance degradation caused by frequent random accesses to disks.
+The above approach takes $\mathcal{O}(n)$ time and space in internal memory.
+The difficulty for applying it in external memory is step S2, it suffers from a performance degradation caused by frequent random accesses to disks.
 Assume that $x$, $sa$ and $lcp$ are stored in external memory, we design Algorithm~\ref{alg:1} for conducting these I/O operations in a disk-friendly way.
-The main idea is to first sort data in their access order and then visit them by sequential reads.
-For the purpose, Algorithm~\ref{alg:1} first scans $sa$ and $lcp$ to produce $ST_1, ST_2, ST_3$ and sorts their tuples by 1st component in ascending order at the very beginning (lines~\ref{alg:1:a}-\ref{alg:1:b}).
-Afterward, it iteratively computes the fingerprints of all the prefixes according to Formulas~\ref{formula:1}-\ref{formula:2} and assigns them to the sorted tuples as following (lines~\ref{alg:1:c}-\ref{alg:1:d}): when figuring out ${\sf fp}(0, i - 1)$, extract each tuple $e$ with $e.1st = i$ from $ST_1/ST_2/ST_3$, update $e$  with ${\sf fp}(0, i - 1)$, and then forward $e$ to $ST_1'/ST_2'/ST_3'$.
-Because the 1st components of the tuples in $ST_1$ constitute a copy of $sa$, the algorithm checks condition (1) when scanning these tuples in their sorted order.
-Finally, it sorts the updated tuples back to their original order~(line~\ref{alg:1:e}) and visits them  sequentially to check conditions (2)-(3) following the same way of S2~(lines~\ref{alg:1:f}-\ref{alg:1:g}).
+The idea is to first sort data in the order that they are to be visited and then access them sequentially.
+For this purpose, Algorithm~\ref{alg:1} first scans $sa$ and $lcp$ to produce $ST_1, ST_2, ST_3$, and sorts their tuples by the first components in ascending order at the beginning (lines~\ref{alg:1:a}-\ref{alg:1:b}).
+Afterward, it iteratively computes the fingerprints of all the prefixes of $x$ according to Formulas~\ref{formula:1}-\ref{formula:2} and assigns them to the sorted tuples as follows (lines~\ref{alg:1:c}-\ref{alg:1:d}): when figuring out ${\sf fp}(0, i - 1)$, extract each tuple $e$ with $e.1st = i$ from $ST_1/ST_2/ST_3$, update $e$  with ${\sf fp}(0, i - 1)$, and then forward $e$ to $ST_1'/ST_2'/ST_3'$.
+Because the first components of the tuples in $ST_1$ constitute a copy of $sa$, the algorithm checks condition 1 when scanning these tuples in their sorted order.
+Finally, it sorts the updated tuples back to their original order~(line~\ref{alg:1:e}) and visits them sequentially to check conditions 2 and 3 following the same way of step S2~(lines~\ref{alg:1:f}-\ref{alg:1:g}).
 
@@
 
-		sort tuples in $ST_1$, $ST_2$ and $ST_3$ by 1st component \label{alg:1:b}
+		{\color{blue} sort the tuples in $ST_1$, $ST_2$ and $ST_3$ by the 1st components, respectively;} \label{alg:1:b}
 
@@
 
-		sort tuples in $ST_1'$, $ST_2'$ and $ST_3'$ by 2nd component.  \label{alg:1:e}
+		{\color{blue} sort the tuples in $ST_1'$, $ST_2'$ and $ST_3'$ by the 2nd component, respectively;} \label{alg:1:e}
 
@@
 
-The last point to be mentioned here is how to obtain the value of $\delta^{lcp[i]}$ quickly when computing $\hat{fp_1}$ and $\hat{fp_2}$ in lines~\ref{alg:1:j} and~\ref{alg:1:k}.
-One method is to keep a lookup table in internal memory to store $\delta^{lcp[i]}$ for all $i \in [0, n)$.
-This can answer the question in constant time, but it is impractical if the table is larger than the available memory size.
-Notice that the LCP of any two suffixes is smaller than $n$, thus we can return the answer in $\mathcal{O}(\lceil \log_2{n} \rceil)$ time using $\mathcal{O}(\lceil \log_2{n} \rceil)$ internal memory space based on the following idea.
-Suppose $e$ is an integer from $[0, n)$, it can be broken down into the form of $\Sigma_{i = 0}^{\lceil \log_2{n} \rceil}{k_i \cdot 2^i}$ by performing at most $\lceil \log_2{n} \rceil$ divisions, where $k_0, k_1, ..., k_{\lceil \log_2{n} \rceil}$ are integers from $\{0, 1\}$ .
-Thereby, we have $\delta^e = \Pi_{i = 0}^{\lceil \log_2{n} \rceil}{\delta}^{k_i \cdot 2^i}$ by replacing $e$ with its decomposition, where the expression on the right side of the equation can be easily computed with $\{{\delta}^{1}, {\delta}^{2}, \dots, {\delta}^{2^{\lceil \log_2{n} \rceil}} \}$ already known.
+The last point is how to obtain $\delta^{lcp[i]}$ quickly when computing $\hat{fp_1}$ and $\hat{fp_2}$ in lines~\ref{alg:1:j} and~\ref{alg:1:k}.
+One way is to keep a lookup table in internal memory to store all $\delta^{lcp[i]}$.
+This can answer the question in constant time, but it is space-consuming and impractical to be used in external memory.
+Notice that the LCP of any two suffixes is shorter than $n$, we can return the answer in $\mathcal{O}(\lceil \log_2{n} \rceil)$ time using $\mathcal{O}(\lceil \log_2{n} \rceil)$ internal memory.
+Let $e$ be an integer from $[0, n)$, its binary form is $k_{\lceil \log_2{n} \rceil}...k_1k_0$.
+We have $\delta^e = \Pi_{i = 0}^{\lceil \log_2{n} \rceil}{\delta}^{k_i \cdot 2^i}$, which can be computed with $\{{\delta}^{1}, {\delta}^{2}, \dots, {\delta}^{2^{\lceil \log_2{n} \rceil}} \}$ already known.
 
@@
 
-Algorithm~\ref{alg:1} performs multiple scans and sorts on the arrays of $\mathcal{O}(n)$ fixed-size tuples residing on disks.
-Given an external memory model with RAM size $M$, disk size $D$ and block size $B$, all are in words, the time and I/O complexities for each scan are $\mathcal{O}(n)$ and $\mathcal{O}(n / B)$, respectively, while those for each sort are $\mathcal{O}(n\log_{M/ B}(n / B))$ and $\mathcal{O}((n / B)\log_{M / B}(n / B))$, respectively~\cite{Arge2013}.
-Algorithm~\ref{alg:1} reaches its peak disk use when sorting tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}.
-Suppose the input string and the suffix/LCP array are encoded using $\alpha$- and $\beta$-byte integers, respectively, and each fingerprint is represented by a $\gamma$-byte integer, it takes $(2 \cdot (2 \cdot \alpha + \beta)) \cdot n$ space for sorting $ST_1/ST_1'$ and $(2 \cdot (2 \cdot \alpha + \beta + \gamma)) \cdot n$ for sorting $ST_2/ST_2'$ and $ST_3/ST_3'$.
-To save disk space, our program implementing the algorithm sorts $ST_1/ST_1'$, $ST_2/ST_2'$ and $ST_3/ST_3'$ separately and performs a single scan over $x$ for each of them to obtain the target fingerprints, resulting in smaller space requirement but larger running time.
-The experimental study in Section~\ref{sec:experiment} indicates that this program is still space consuming, its peak disk use is 40 bytes per input character.
+Algorithm~\ref{alg:1} performs multiple scans and sorts on the arrays of $\mathcal{O}(n)$ fixed-size tuples in disks.
+Given RAM size $M$, disk size $D$ and block size $B$, all are in words, the time and I/O complexities for each scan are $\mathcal{O}(n)$ and $\mathcal{O}(n / B)$, respectively, while those for each sort are $\mathcal{O}(n\log_{M/ B}(n / B))$ and $\mathcal{O}((n / B)\log_{M / B}(n / B))$, respectively~\cite{Arge2013}.
+Algorithm~\ref{alg:1} reaches its peak disk use when sorting the tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}.
+Suppose the input string and the suffix/LCP array are encoded as $\alpha$- and $\beta$-byte integers, respectively, and each fingerprint is a $\gamma$-byte integer, it takes $(2 \cdot (2 \cdot \alpha + \beta))$ space for sorting the tuples of $ST_1/ST_1'$ and $(2 \cdot (2 \cdot \alpha + \beta + \gamma))$ for sorting the tuples of $ST_2/ST_2'$ and $ST_3/ST_3'$.
+For saving space, our program implementing the algorithm tackles $ST_1/ST_1'$, $ST_2/ST_2'$ and $ST_3/ST_3'$ separately and performs a single scan over $x$ for each of them to obtain the fingerprints, using less space but more time.
+The experiment in Section~\ref{sec:experiment} indicates that the peak disk use is 40 bytes per input character.
 
@@
 
-In this part, we describe an alternative checking method based on the induced sorting principle.
-Compared with Algorithm~\ref{alg:1}, our programs for Algorithm~\ref{alg:2} designed by this method take around half disk space on real-world datasets.
-Before the presentation, we introduce some symbols and notations used in the following paragraphs.
+We further to give another checking method using the induced sorting principle {\color{blue} \cite{sais,ka}}, , which requires much less space than Method A.
+For presentation convenience, we introduce some symbols and notations as below.
 
@@
 In detail, $x[i]$ is L-type if (1) $i = n - 1$ or (2) $x[i] > x[i + 1]$ or (3) $x[i] = x[i + 1]$ and $x[i + 1]$ is L-type; otherwise, $x[i]$ is S-type.
-Further, if $x[i]$ and $x[i + 1]$ are separately L-type and S-type, then $x[i + 1]$ is also an S*-type character.
+Further, if $x[i]$ and $x[i + 1]$ are separately L-type and S-type, then $x[i + 1]$ is also S*-type.
 Moreover, a suffix is L-, S- or S*-type if its heading character is L-, S-, or S*-type, respectively.
 
-{\em Suffix and LCP buckets.} Suppose $sa$ is correct, all the suffixes in $sa$ are naturally partitioned into multiple buckets and those of a common heading character are grouped into a single bucket that occupies a contiguous interval in $sa$.
-Each bucket can be further divided into two sub-buckets, where the left and the right parts only contain L- and S-type suffixes, respectively.
-For short, we use ${\sf sa\_bkt}(c)$ to denote the bucket storing suffixes starting with character $c$ and ${\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$ to denote its left/right sub-bucket.
-Accordingly, $lcp$ can be also split into multiple buckets, where ${\sf lcp\_bkt}(c)/{\sf lcp\_bkt_L}(c)/{\sf lcp\_bkt_S}(c)$ stores the LCP-values of suffixes in ${\sf sa\_bkt}(c)/{\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$.
+{\em Suffix and LCP buckets.} All the suffixes in $sa$ are partitioned into multiple buckets and those of a common heading character are grouped into a single bucket that occupies a contiguous interval in $sa$.
+Each bucket can be further divided into two sub-buckets, where the left and the right parts  contain L- and S-type suffixes only, respectively.
+For short, we use ${\sf sa\_bkt}(c)$ to denote the bucket storing the suffixes starting with character $c$ and ${\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$ to denote its left/right sub-bucket.
+Accordingly, $lcp$ can be also split into multiple buckets, where ${\sf lcp\_bkt}(c)/{\sf lcp\_bkt_L}(c)/{\sf lcp\_bkt_S}(c)$ stores the LCP-values of suffixes in ${\sf sa\_bkt}(c)/{\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$, respectively.
 
@@
 
-{\em Type Array.} The array $t$ records in $t[i]$ the type information of $x[i]$, where $t[i] = 1$ or $0$ if $x[i]$ is S-type or L-type, respectively.
+{\em Type Array.} The array $t$ records in $t[i]$ the type information of $x[i]$, where $t[i] = 1$ or $0$ if $x[i]$ is S- or L-type, respectively.
 
@@
 
-The induced sorting principle has been extensively used to design efficient algorithms for constructing the suffix and LCP arrays on internal and external memory models.
-An IS-based construction algorithm mainly consists of a reduction phase for computing $sa^*$ and $lcp^*$, followed by an induction phase for inducing $sa$ and $lcp$ from $sa^*$ and $lcp^*$~\footnote{In the interest of completeness, we give an overview of the induction phase in Appendix~\ref{sec:appendix}.}.
-Given that $sa^*$ and $lcp^*$ are already known, we can produce the final suffix and LCP arrays by calling the inducing process of an existing IS-based construction algorithm.
-This enlightens us to design a checker based on Lemma~\ref{lemma:2}.
+The induced sorting principle has been extensively used to design efficient algorithms for constructing the suffix and LCP arrays in internal or external memory {\color{blue} \cite{sais,dsais,emsads,esais,inducelcp}}.
+Such a construction algorithm mainly consists of a reduction phase for computing $sa^*$ and $lcp^*$, followed by an induction phase for inducing $sa$ and $lcp$ from $sa^*$ and $lcp^*$~\footnote{An overview of the induction phase is given in Appendix~\ref{sec:appendix}.}.
+Given that $sa^*$ and $lcp^*$ are already known, we can induce the final suffix and LCP arrays from them.
+This suggests a checking method based on Lemma~\ref{lemma:2}.
 
@@
 	\item
-	$sa^*$ and $lcp^*$ are both correct.
+	Both $sa^*$ and $lcp^*$ are correct.
 	\item
@@
 
-Similar to Method A, the fingerprinting technique can be employed to probabilistically check the correctness of $sa^*$ and $lcp^*$.
-An external-memory algorithm for checking the conditions in Corollary~\ref{corollary:2} is given in the next subsection.
+We have Corollary~\ref{corollary:2} for probabilistically checking the conditions of Lemma \ref{lemma:2}.
 
@@
 
-The first step of Algorithm~\ref{alg:2} is to compute and verify $sa^*$ and $lcp^*$.
-According to their definitions, $sa^*$ can be produced by sequentially retrieving the S*-type suffixes from $sa$ and the LCP-value of two successive S*-type suffixes in $sa$, say ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$, is equal to the minimal of $\{lcp[i + 1], ..., lcp[j - 1], lcp[j]\}$.
-Hence, the proposed algorithm first sorts all the suffixes in $sa$ by their starting positions~(lines~\ref{alg:2:a}-\ref{alg:2:b}) and then scans $x$ only once to pick out the S*-type suffixes~(lines~\ref{alg:2:c}-\ref{alg:2:d}).
+We further to design Algorithm~\ref{alg:2} for checking the conditions of Corollary~\ref{corollary:2}.
+The first step is to compute and verify $sa^*$ and $lcp^*$.
+Similar to Method A, the fingerprinting technique is employed to probabilistically check the correctness of $sa^*$ and $lcp^*$.
+The array $sa^*$ can be produced by sequentially retrieving the S*-type suffixes from $sa$ and the LCP-value of two successive S*-type suffixes in $sa$, say ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$, is equal to the minimal of $\{lcp[i + 1], ..., lcp[j - 1], lcp[j]\}$.
+The algorithm first sorts all the suffixes in $sa$ by their starting positions~(lines~\ref{alg:2:a}-\ref{alg:2:b}) and then scans $x$ once to get the S*-type suffixes~(lines~\ref{alg:2:c}-\ref{alg:2:d}).
 After that, it puts these S*-type suffixes back in their lexical order and outputs them one by one to generate $sa^*$~(lines~\ref{alg:2:g}-\ref{alg:2:h}).
-Meanwhile, it calculates the LCP-value for each pair of the neighboring suffixes in $sa^*$ by tracing the minimal over the $lcp$ interval indicated by the two suffixes.
-Notice that, we check condition (1) in Corollary~\ref{corollary:2} during the time when visiting the suffixes in position order (lines~\ref{alg:2:e}-\ref{alg:2:f}) and conditions (2)-(3) by calling Algorithm~\ref{alg:1} with $sa^*$ and $lcp^*$ as input.
-Suppose $sa^*$ and $lcp^*$ are both correct, then Algorithm~\ref{alg:2} invokes the inducing process of an existing IS-based construction algorithm to induce $sa'$ and $lcp'$, which are a copy of the final suffix and LCP arrays, from the two verified arrays~(line~\ref{alg:2:k}) and literally compares them with $sa$ and $lcp$ to complete the whole checking process~(lines~\ref{alg:2:l}-\ref{alg:2:m}).
+Meanwhile, it calculates the LCP-value for each pair of the neighboring suffixes in $sa^*$ by tracing the minimum in the $lcp$ interval between these two suffixes.
+Notice that, we check condition 1 when visiting the suffixes in their position order (lines~\ref{alg:2:e}-\ref{alg:2:f}), and check conditions 2 and 3 by Algorithm~\ref{alg:1} with $sa^*$ and $lcp^*$ as input.
+Suppose $sa^*$ and $lcp^*$ are both correct, then Algorithm~\ref{alg:2} invokes the inducing process of an existing IS-based construction algorithm to induce $sa'$ and $lcp'$ from the two verified arrays $sa^*$ and $lcp^*$~(line~\ref{alg:2:k}) and compares them with $sa$ and $lcp$ to complete the whole checking process~(lines~\ref{alg:2:l}-\ref{alg:2:m}).
 
@@
 
-	sort tuples in $ST_1$ by 1st component \label{alg:2:b}
+	sort the tuples in $ST_1$ by the 1st component; \label{alg:2:b}
 
@@
 
-	sort tuples in $ST_2$ by the 2nd component \label{alg:2:g}
+	sort the tuples in $ST_2$ by the 2nd component; \label{alg:2:g}
 
@@
 
-{\bf Assume that the alphabet $\Sigma$ is of a constant size, we can check $sa$ and $lcp$ without producing a copy of the final suffix and LCP arrays in Algorithm~\ref{alg:2}.} The idea is to compare the induced suffix/LCP items with their corresponding items in $sa/lcp$ during the inducing process.
+{\bf Assume that the alphabet $\Sigma$ is of size $\mathcal{O}(1)$, we can check $sa$ and $lcp$ without storing the induced suffix and LCP arrays in Algorithm~\ref{alg:2}.} The idea is to compare the induced suffix/LCP items with their corresponding items in $sa/lcp$ during the inducing process.
 Specifically, when a suffix/LCP item $v_1$ is induced into a bucket, we check if it is equal to the corresponding item $v_2$ in $sa/lcp$.
 If $v_1 = v_2$, then $v_2$ is correct and we further use this value to induce the remaining suffix/LCP items.
-The key point here is to retrieve items of $sa/lcp$ from external storage as fast as possible.
+The key point is to quickly retrieve the items of $sa/lcp$ in external memory.
 This can be done by conducting sequential I/O operations if we provide a read pointer together with a buffer for each suffix/LCP sub-bucket.
-We describe below more details of the adapted inducing process, where $lp_1/lp_2$ and $sp_1/sp_2$ are file pointer arrays for reading items from the sub-buckets of $sa$ and $lcp$.
+We describe below more details of the modified inducing process, where $lp_1/lp_2$ and $sp_1/sp_2$ are file pointer arrays for reading items from the sub-buckets of $sa$ and $lcp$.
 
@@
 		\item 
-		Scan $sa$ and $lcp$ rightward to induce L-type suffixes and their LCP-values.
+		Scan $sa$ and $lcp$ rightward to induce the L-type suffixes and their LCP-values.
 For each induced suffix $p$ (with a heading character $c_0$) and its LCP-value $q$: (1) check if $p = lp_1[c_0]$ and $q = lp_2[c_0]$; (2) move $lp_1[c_0]$ and $lp_2[c_0]$ to the next items on the right.
@@
 		\item 	
-		Scan $sa$ and $lcp$ leftward to induce S-type suffixes and their LCP-values.
+		Scan $sa$ and $lcp$ leftward to induce the S-type suffixes and their LCP-values.
 For each induced suffix $p$ (with a heading character $c_0$) and its LCP-value $q$: (1) check if $p = sp_1[c_0]$ and $q = sp_2[c_0]$; (2) move $sp_1[c_0]$ and $sp_2[c_0]$ to the next items on the left.
@@
 
-Algorithm~\ref{alg:2} mainly consists of two parts, where the first part for checking $sa^*$ and $lcp^*$ can be done within sorting time and the second part for checking $sa$ and $lcp$ can be done in linear time.
-Clearly, the space complexity of part one is dependent upon the number of S*-type suffixes.
-As will be seen from Section~\ref{sec:experiment}, the programs for Algorithm~\ref{alg:2} take around $15n$ to check $sa^*$ and $lcp^*$, which is about one-third as that for Algorithm~\ref{alg:1} to check $sa$ and $lcp$.
-This corresponds to the ratio of S*-type suffixes to all in the real-world datasets.
-From our experiments, these programs take more disk space during the execution of inducing process, their peak disk use is about half as that for Algorithm~\ref{alg:1}.
+Algorithm~\ref{alg:2} mainly consists of two parts, where the first part for checking $sa^*$ and $lcp^*$ can be done within sorting complexity and the second part for checking $sa$ and $lcp$ can be done in linear time.
+In our current program for this algorithm, the peak disk use is reached in part two, specifically, when computing the BWT from $sa$ and $x$ for use in the inducing process.
 
@@
 
-	\item IOV: amount of data read from and write to external memory, in bytes. Each element of the suffix and LCP arrays takes 5 bytes.
+	\item IOV: amount of data read from and write to external memory, in bytes, where each integer is 40-bit.
 
@@
 All the programs are compiled by gcc/g++ 4.8.4 with -O3 options on ubuntu 14.04 64-bit operating system and each program is allowed to use 3 GiB RAM.
-For denotation convenience, we use "ProgA" and "ProgB" to represent the programs for Algorithms~\ref{alg:1} and~\ref{alg:2}, respectively.
+For simplicity, we use "ProgA" and "ProgB" to represent the programs for Algorithms~\ref{alg:1} and~\ref{alg:2}, respectively.
 
@@
 For example, a suffix/LCP array may be broken due to software or hardware malfunctions.
-If a backup is not available and it is too time-consuming to rebuild the whole array, then we can locate the bad areas quickly using Algorithm~\ref{alg:1} and restore the partial SA for each area by calling a sparse SA construction algorithm.
+If a backup is not available and it is  time-consuming to rebuild the whole array, then we can locate the bad areas quickly using Algorithm~\ref{alg:1} and restore the partial SA for each area by calling a sparse SA construction algorithm.
 Another example is to check the correctness of a sparse SA.
-Because the number of suffixes in a sparse SA is commonly much smaller than that in the full SA, Algorithm~\ref{alg:1} could become an efficient verification solution.
+Because the number of suffixes in a sparse SA is commonly much smaller than that in the full SA, Algorithm~\ref{alg:1} could be an efficient verification solution.
 
@@
 For example, several algorithms for induced sorting a suffix and/or LCP arrays were proposed these years \cite{Nong15,Nong14,Bingmann12}, with different methods for solving the key problem of retrieving the preceding character of a sorted suffix in the inducing process.
-A recent work \cite{Karkkainen2017} for engineering these induced sorting methods with some implementation optimizing techniques achieves a significant improvement over the previous results.
-As reported, the peak disk use is $7n$ for 32-bit integers.
-Because the induced sorting process is the performance bottleneck for Method B, it is reasonable to expect that a better engineering implementation of the method will yield a remarkable performance improvement.
+A recent work \cite{Karkkainen2017} engineering these induced sorting methods with some implementation optimizing techniques achieves a significant improvement over the previous results.
+As reported, the peak disk use is around $8n$ for 40-bit integers.
+Because the induced sorting process is the performance bottleneck for Method B, it is reasonable to expect that a better engineering implementation of the method will yield a remarkable improvement in both time and space.
 {\bf An optimized engineering of our methods is out of the scope of this paper and will be addressed elsewhere.}
@@
 For program debugging, we usually check the output of a builder by comparing it with that of another builder.
-But this is not feasible in all the cases, for example, an algorithm for constructing infinite-order\footnote{A suffix array is infinite-order if the suffixes are sorted up to their ends, or else finite-order.} array can not be directly used to check a finite-order array and vise versa.
+But this is not feasible in all the cases, for example, an algorithm for constructing infinite-order array can not be directly used to check a finite-order array and vise versa.
 On the contrary, our first method can be generalized to check the correctness of the lexical order and the LCP values of any pairs of suffixes.
@@
 The IS method has been applied to successfully design a number of suffix and LCP arrays construction algorithms.
-A recent work \cite{Karkkainen2017} reports that a careful engineering of the IS in external memory can build a suffix array using only $7n$ bytes for $n\le 2^{32}$, which is approaching the optimal in respect to $5n$ bytes for the IS in internal memory.
-Besides, it runs fastest in most cases of the experiments therein.
+A recent work \cite{Karkkainen2017} reports that a careful engineering of the IS in external memory can build a suffix array using around $8n$ bytes for $n\le 2^{40}$, which is approaching $6n$ bytes for the IS in internal memory.
+Besides, it runs the fastest for large $n$ in the experiments therein.
 This convinces that the IS method could serve as a basis for developing potentially optimal solutions for building suffix/LCP arrays.
@@
 
-Recall that the lexical order of two suffixes starting with $x[i]$ and $x[j]$ can be determined by sequentially comparing their characters until finding a position $k$ such that $x[i, i + k) = x[j, j + k)$ and $x[i + k] \ne x[j + k]$.
-In other words, we have ${\sf suf}(i) < {\sf suf}(j)$ if (1) $x[i] < x[j]$~$(k = 0)$ or (2) $x[i] = x[j]$ and ${\sf suf}(i + 1) < {\sf suf}(j + 1)$~$(k > 0)$; otherwise, ${\sf suf}(i) > {\sf suf}(j)$.
-This rule is used by the IS-based SA construction algorithms to sort suffixes during the induction phase:
+Notice that ${\sf suf}(i) < {\sf suf}(j)$ if (1) $x[i] < x[j]$ or (2) $x[i] = x[j]$ and ${\sf suf}(i + 1) < {\sf suf}(j + 1)$; otherwise, ${\sf suf}(i) > {\sf suf}(j)$.
+This observation is utilized by the IS-based SA construction algorithms to sort suffixes as follows:
 
@@
 For example, when scanning from $sa[0]$ to $sa[5]$ in lines 10-21 of Fig.~\ref{fig:example2}, we induce ${\sf suf}(12)$ and ${\sf suf}(6)$ into the neighboring positions in ${\sf sa\_bkt_L(2)}$.
-During the scan, if we keep recording the minimal of $lcp(0, 5]$ in a variable, then we can obtain the LCP-value of the suffixes ${\sf suf}(13)$ and ${\sf suf}(5)$ from this variable when putting ${\sf suf}(6)$ into $sa$.
+During the scan, if we keep recording the minimum of $lcp(0, 5]$ in a variable, then we can obtain the LCP-value of the suffixes ${\sf suf}(13)$ and ${\sf suf}(5)$ from this variable when putting ${\sf suf}(6)$ into $sa$.
 

### 2017-03-20 draft-abandon/draft.tex
2017/03/20

--- 2017-03-01 draft/draft.tex
@@
 In this paper, we propose two methods to check the suffix and LCP arrays in external memory by using a Karp-Rabin fingerprinting technique, where the checking result is wrong only with a negligible error probability.
-The first method checks the lexicographical order and the LCP-value of two neighboring suffixes in the given suffix array by computing and comparing the fingerprints of their LCPs.
-This idea is also employed in the second method to verify a subset of the given suffix and LCP arrays, from which then a copy of the final suffix and LCP arrays is produced following the induced sorting principle and compared with the given arrays for verification.
+The first method checks the lexicographical order and the LCP-value of two suffixes by computing and comparing the fingerprints of their LCPs.
+This method is of high versatility that it can verify any (sparse) suffix/LCP arrays of finite or infinite order.
+The second method is more space efficient, it first employs the same technique to verify a subset of the given suffix and LCP arrays, from which then a copy of the final suffix and LCP arrays is produced following the induced sorting principle and compared with the given arrays for verification.
 
@@
 In many applications, these two data structures make up the core part of a powerful full-text index, called enhanced suffix array~\cite{Abouelhodaa2004}, which is more space efficient than a suffix tree and applicable to emulating any searching functionalities provided by the latter in the same time complexity.
-The first algorithm for building suffix array in internal memory was presented in~\cite{Manber1993}.
-From then on, much more effort has been put on designing efficient constructors for suffix array~(SA) on different memory models~\cite{Karkkainen2003, Ko2003, Kim2003, Nong11, Dementiev2008, Ferragina2012, Manzini2004, Bingmann12, Karkkainen2014, Nong14, Nong15}.
+The first algorithm for building suffix array~(SA) in internal memory was presented in~\cite{Manber1993}.
+From then on, much more effort has been put on designing efficient constructors for suffix array on different memory models~\cite{Karkkainen2003, Ko2003, Kim2003, Nong11, Dementiev2008, Ferragina2012, Manzini2004, Bingmann12, Karkkainen2014, Nong14, Nong15}.
 In respect of the research on LCP array construction algorithms, the existing works can be classified into two categories with regard to their input requirements, where the algorithms from the first category compute both suffix and LCP arrays at the same time with the original text only~\cite{Fischer11, Bingmann12, Flick2015} and those from the second category carry out the computation by taking SA and/or Burrows-Wheeler transform (BWT) as additional input~\cite{Kasai2001,Karkkainen2009, Fischer11, Puglisi2008, Deo2013}.
@@
 To overcome the drawback, Method B first employs the fingerprinting technique to check a subset selected from the given suffix and LCP arrays, then it reuses the inducing process of an IS-based construction algorithm to produce the final suffix and LCP arrays from the verified subset and literally compares them with the input arrays to ensure the correctness of the latter.
-Our experiments indicate that the peak disk use of the program for the algorithm designed by Method B is only half as that of the program for the algorithm designed by Method A.
+Our experiments indicate that the peak disk use of the programs for Algorithm~\ref{alg:2} designed by Method B is only about half as that of the program for Algorithm~\ref{alg:1} designed by Method A.
 
@@
 According to the above definitions, we show in Lemma~\ref{lemma:1} the sufficient and necessary conditions for checking suffix and LCP arrays.
-Notice that the lexical order and the LCP-value of any two suffixes in $x$ can be computed by literally comparing their characters from left to right.
-Because all the suffixes differ in length and end with a common character, there must exist $k \in [0, n)$ such that $x[i, i + k) = x[j, j + k)$ and $x[i + k] \ne x[j + k]$ for any $i, j \in [0, n)$ and $i \ne j$.
-This approach can be also applied to verifying the last two conditions in Lemma~\ref{lemma:1}, but it takes at worst $\mathcal{O}(n)$ character-wise comparisons for each pair of neighboring suffixes in $sa$ to compare the two underlying substrings indicated by their LCP-value.
+Notice that the lexical order and the LCP-value of any two suffixes in $x$ can be computed by literally comparing their characters rightward.
+To do this, we assume $x[n]$ to be an empty character lexicographically smaller than any characters of $\Sigma$.
+Because all the suffixes differ in length and end with the empty character, there must exist $k \in [0, n)$ such that $x[i, i + k) = x[j, j + k)$ and $x[i + k] \ne x[j + k]$ for $i, j \in [0, n)$ and $i \ne j$.
+This approach can be also applied to verifying the last two conditions in Lemma~\ref{lemma:1}, but it takes at worst $\mathcal{O}(n)$ character-wise comparisons for each pair of neighboring suffixes in $sa$ to compare the underlying substrings indicated by their LCP-value.
 
@@
 An alternative is to exploit a perfect hash function~(PHF) to convert each substring into a single integer such that any two substrings have a common hash value if and only if they are literally equal to each other.
-This implies that we can compare the hash values instead to check equality of their corresponding substrings.
+This implies that we can compare the hash values of substrings instead to check their equality.
 The key point here is how to quickly calculate the hash values of $x[sa[i], sa[i] + lcp[i] - 1]$ and $x[sa[i - 1], sa[i - 1] + lcp[i] - 1]$ for all $i \in [1, n)$.
-Taking into consideration the high difficulty of finding a PHF to meet this requirement, we prefer using a Karp-Rabin fingerprinting function~\cite{Karp1987} to transform a substring into its integer form, called fingerprint.
+Taking into account the high difficulty of finding a PHF to meet this requirement, we prefer using a Karp-Rabin fingerprinting function~\cite{Karp1987} to transform a substring into its integer form, called fingerprint.
 To be specific, suppose $L$ is a prime and $\delta$ is a number randomly chosen from $[1, L)$, the fingerprint ${\sf fp}(i, j)$ for a substring $x[i, j]$ can be calculated according to the formulas below as following: scan $x$ rightward to iteratively compute ${\sf fp}(0, k)$ for all $k \in [0, n)$ using Formulas~\ref{formula:1}-\ref{formula:2}, record ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ during the calculation and subtract the former from the latter to obtain ${\sf fp}(i, j)$ using Formula~\ref{formula:3}.
@@
 
-We close this part with an example in Fig.~\ref{fig:example} for a better understanding of computing and comparing the fingerprints of the substrings specified the LCP-values of lexical neighbors.
+We close this part with an example in Fig.~\ref{fig:example} for a better understanding.
 Given that $L = 197$ and $\delta = 101$, lines 4-8 compute ${\sf fp}(0, p)$ iteratively according to Formulas~\ref{formula:1}-\ref{formula:2}.
-Then, lines 10-16 use these values to compute the fingerprints for target substrings.
+Then, lines 10-16 use these values to compute the fingerprints for all the target substrings.
 Consider the leftmost pair of neighboring suffixes in $sa$, that is ${\sf suf}(sa[0])$ and ${\sf suf}(sa[1])$, the substrings indicated by their LCP-value are $x[sa[0], sa[0] + lcp[1] - 1]$ and $x[sa[1], sa[1] + lcp[1] - 1]$, respectively.
 According to Formula~\ref{formula:3}, ${\sf fp}(sa[0], sa[0] + lcp[1] - 1)$ is equal to the difference between ${\sf fp}(0, sa[0] - 1)$ and ${\sf fp}(0, sa[0] + lcp[1] - 1)$, both of which have been calculated beforehand.
+Following the same way, ${\sf fp}(sa[1], sa[1] + lcp[1] - 1)$ is computed by deducting ${\sf fp}(0, sa[1] - 1)$ from ${\sf fp}(0, sa[1] + lcp[1] - 1)$.
 Hence, we obtain the fingerprints for these two substrings in lines 10-12 and see that they are equal to each other.
@@
 Assume that $x$, $sa$ and $lcp$ are stored in external memory, we design Algorithm~\ref{alg:1} for conducting these I/O operations in a disk-friendly way.
-The main idea is to sort data in the order that they are visited and then access them by sequential reads.
+The main idea is to first sort data in the order that they are to be visited and then access them by sequential reads.
 For the purpose, Algorithm~\ref{alg:1} first scans $sa$ and $lcp$ to produce $ST_1, ST_2, ST_3$ and sorts their tuples by 1st component in ascending order at the very beginning (lines~\ref{alg:1:a}-\ref{alg:1:b}).
 Afterward, it iteratively computes the fingerprints of all the prefixes according to Formulas~\ref{formula:1}-\ref{formula:2} and assigns them to the sorted tuples as following (lines~\ref{alg:1:c}-\ref{alg:1:d}): when figuring out ${\sf fp}(0, i - 1)$, extract each tuple $e$ with $e.1st = i$ from $ST_1/ST_2/ST_3$, update $e$  with ${\sf fp}(0, i - 1)$, and then forward $e$ to $ST_1'/ST_2'/ST_3'$.
-Because the 1st components of the tuples in $ST_1$ constitute a copy of $sa$, the algorithm can check condition (1) when scanning these tuples in their sorted order.
+Because the 1st components of the tuples in $ST_1$ constitute a copy of $sa$, the algorithm checks condition (1) when scanning these tuples in their sorted order.
 Finally, it sorts the updated tuples back to their original order~(line~\ref{alg:1:e}) and visits them  sequentially to check conditions (2)-(3) following the same way of S2~(lines~\ref{alg:1:f}-\ref{alg:1:g}).
@@
 	\item
-	$sa = sa'$ and $lcp = lcp'$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by calling the inducing process of any existing IS-based construction algorithm.
+	$sa = sa'$ and $lcp = lcp'$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by calling the inducing process of an existing IS-based construction algorithm.
 \end{enumerate}
@@
 \begin{Corollary} \label{corollary:2}
-Both $sa[0, n)$ and $lcp[0, n)$ are correct with a high probability given the following conditions, for $i \in [0, n)$, $\{j, k\} \in [1, n_1)$ and $j \ne k$:
+Both $sa[0, n)$ and $lcp[0, n)$ are correct with a high probability given the following conditions:
 
@@
 	\item
-	$sa^*[j] \ne sa^*[k]$.
+	$x[sa^*[i]]$ is S*-type and $sa^*[i] \ne sa^*[j]$ for $i, j \in [0,n_1)$ and $i \ne j$.
 	\item
-	${\sf fp}(sa^*[j], sa^*[j] + lcp^*[j] - 1) = {\sf fp}(sa^*[j - 1], sa^*[j - 1] + lcp^*[j] - 1)$.
+	${\sf fp}(sa^*[i], sa^*[i] + lcp^*[i] - 1) = {\sf fp}(sa^*[i - 1], sa^*[i - 1] + lcp^*[i] - 1)$ for $i \in [1, n_1)$.
 	\item
-	$x[sa^*[j] + lcp^*[j]] > x[sa^*[j - 1] + lcp^*[j]]$.
+	$x[sa^*[i] + lcp^*[i]] > x[sa^*[i - 1] + lcp^*[i]]$ for $i \in [1, n_1)$.
 	\item
-	$sa[i] = sa'[i]$ and $lcp[i] = lcp'[i]$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by calling the inducing process of an existing IS-based construction algorithm.
+	$sa[i] = sa'[i]$ and $lcp[i] = lcp'[i]$ for $i \in [0, n)$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by calling the inducing process of an existing IS-based construction algorithm.
 \end{enumerate}
@@
 If $v_1 = v_2$, then $v_2$ is correct and we further use this value to induce the remaining suffix/LCP items.
-The key point here is to retrieve items from $sa/lcp$ quickly.
+The key point here is to retrieve items of $sa/lcp$ from external storage as fast as possible.
 This can be done by conducting sequential I/O operations if we provide a read pointer together with a buffer for each suffix/LCP sub-bucket.
@@
 
-Algorithm~\ref{alg:2} mainly consists of two parts, where the first part for checking $sa^*$ and $lcp^*$ can be implemented within sorting complexity and the second part for checking $sa$ and $lcp$ can be implemented in linear time under the condition that $\|\Sigma\| = \mathcal{O}(1)$.
-As will be seen from Section~\ref{sec:experiment}, the peak disk use of our program for Algorithm~\ref{alg:2} is around $21n$, while it has a better performance than that for Algorithm~\ref{alg:1} in terms of time and I/O volume.
+Algorithm~\ref{alg:2} mainly consists of two parts, where the first part for checking $sa^*$ and $lcp^*$ can be implemented within sorting complexity and the second part for checking $sa$ and $lcp$ can be implemented in linear time.
+As will be seen from Section~\ref{sec:experiment}, the peak disk use of our program for the optimized version of Algorithm~\ref{alg:2} is around $21n$ under the condition of $\|\Sigma\| = \mathcal{O}(1)$, and it even runs faster than the program for Algorithm~\ref{alg:1} in some cases.
 
@@
 
-The experimental platform is a work station equipped with an Intel Xeon E3-1220 V2 CPU, 4 GiB RAM and 2 TiB HD.
+The experimental platform is a work station equipped with an Intel Core i3-550 CPU, 4 GiB RAM and 2 TiB HD.
 All the programs are compiled by gcc/g++ 4.8.4 with -O3 options under ubuntu 14.04 64-bit operating system.
@@
 	\centering
-	\begin{tabular}{|l|c|c|p{5cm}|}
+	\begin{tabular}{|l|c|p{5cm}|}
 		\hline
-		Corpora & \multicolumn{1}{c|}{$n$} & \multicolumn{1}{c|}{$\|\Sigma\|$} & Description \\\hline
-		enwiki & 8 & 256 & The 8-GiB prefix of an XML dump of English Wikipedia, available at \url{https://dumps.wikimedia.org/enwiki}, dated as 16/05/01. \\\hline	
-		uniprot & 2.5 & 96 & UniProt Knowledgebase, available at \url{ftp://ftp.expasy.org/databases/.../complete}, dated as 16/05/11. \\\hline
-		proteins & 1.1 & 27 & Swissprot database, available at \url{http://pizzachili.dcc.uchile.cl/texts/protein}, dated as 06/12/15. \\\hline
+		Corpora & \multicolumn{1}{c|}{$\|\Sigma\|$} & Description \\\hline
+		enwiki & 256 & An XML dump of English Wikipedia, available at \url{https://dumps.wikimedia.org/enwiki}, dated as 16/05/01. \\\hline	
+		uniprot & 96 & UniProt Knowledgebase, available at \url{ftp://ftp.expasy.org/databases/.../complete}, dated as 16/05/11. \\\hline
+		proteins & 27 & Swissprot database, available at \url{http://pizzachili.dcc.uchile.cl/texts/protein}, dated as 06/12/15. \\\hline
 	\end{tabular}
@@
 The speed gap between them is mainly due to the difference in their I/O performances.
-Specifically, the I/O volume of ProgB keeps at $155n$ for all the three datasets, while that of ProgA rises up to nearly $200n$ on average.
+Specifically, the I/O volume of ProgA keeps at $155n$ for all the three datasets, while that of ProgB rises up to nearly $200n$ on average.
 Besides, the peak disk use of ProgB is about $26/40=0.65$ as ProgA.
@@
 Because at most one out of every two successive characters in the input string is S*-type, the consumption for checking the suffix and LCP arrays of S*-type suffixes in ProgB is expected to be half as that for checking the given arrays in ProgA.
-To make a deep insight, we collect in Table~\ref{tbl:2} the performance overhead of ProgB and ProgA when checking the suffix and LCP arrays of S*-type and all the suffixes, respectively.
+To make a deep insight, we collect in Table~\ref{tbl:2} the performance overhead of ProgB and ProgA when checking the suffix and LCP arrays of S*-type suffixes and all, respectively.
 As can be observed, the mean ratio of the number of S*-type suffixes to the number of all the suffixes is around 0.30 for the datasets under investigation, while the mean ratios of time, space and I/O volume for checking $sa^*$ and $lcp^*$ to that for checking $sa$ and $lcp$ are 0.38, 0.57 and 0.60, respectively.
@@
 In Figure~\ref{fig:performance_analysis2}, the peak disk use for each program remains unchanged, but their speed become slower as the prefix length increases due to the performance degradation of the external memory sorter exploited in our programs.
-As we can see from Table~\ref{tbl:2}, ProgB+ keeps the I/O volume around $90n$ with the prefix length of "enwiki" varying from $1$ to $8$ GiB, while its running time rises from $1.05$ to $1.33$.
+This can be also observed from Table~\ref{tbl:2}, where ProgB+ keeps the I/O volume around $90n$ with the prefix length of "enwiki" varying from $1$ to $8$ GiB but its running time rises from $1.05$ to $1.33$.
 
@@
 		\hline
-		\multirow{2}{*}{dataset} & \multicolumn{3}{|c|}{number of suffixes} & \multicolumn{3}{|c|}{PDU} & \multicolumn{3}{|c|}{IOV} & \multicolumn{3}{|c|}{RT} \\\cline{2-13}
+		\multirow{2}{*}{dataset} & \multicolumn{3}{|c|}{\# of suffixes} & \multicolumn{3}{|c|}{PDU} & \multicolumn{3}{|c|}{IOV} & \multicolumn{3}{|c|}{RT} \\\cline{2-13}
 						 & S*-type & all & ratio & S*-type & all & ratio & S*-type & all & ratio & S*-type & all & ratio \\\hline
@@
 
- We select eSAIS and pSAscan because they are currently the fastest sequential and parallel algorithms for SA construction.
-Also, Sparse-$\phi$ is the fastest algorithm for LCP array construction ever reported.
+ We select eSAIS and pSAscan because they are currently the fastest sequential and parallel SA construction algorithms available to us.
+Also, Sparse-$\phi$ is the fastest LCP array construction algorithm among those ever reported.
 A runtime breakdown of the programs for these solutions on the prefixes of "enwiki" is given in Table~\ref{tbl:3}.
-As can be seen, solution 2 is about two times faster than solution 1 and twice as fast as ProgA, which is mainly owing to the high speed of pSAscan.
-Notice that both eSAIS and the proposed checking algorithms can achieve optimal time and I/O complexity in external memory, but pSAscan and Sparse-$\phi$ are not theoretically optimal and thus have a limitation to their scalability.
-As reported in~\cite{Karkkainen2015}, when the length of input string is considerably greater than the size of internal memory, eSAIS is more quickly and I/O efficient than pSAScan.
-We can see from the same table that an increase in the time overhead occurs to pSAscan when handling the prefix containing 8 Gi characters.
+As can be seen, the program for solution 2 is about two times faster than that for solution 1 and twice as fast as ProgA, which is mainly owing to the high speed of pSAscan.
+However, it is worthy of pointing out that both pSAscan and Sparse-$\phi$ are of the time and I/O complexity proportional to $n^2/M$.
+This is much higher than eSAIS and our checking algorithms, and thus poses a limitation to their scalability.
+As reported in~\cite{Karkkainen2015}, when the input string length is considerably greater than the internal memory size, eSAIS is more quickly and I/O efficient than pSAscan.
+We can see from Table~\ref{tbl:3} that, the time consumption of constructing the SA for "enwiki\_8g" is doubled as that of constructing the SA for "enwiki\_1g" by means of pSAscan.
 
@@
 \begin{table*}[h]
-	\caption{A runtime comparison between the programs for the two solutions and the proposed algorithms.}
+	\caption{A runtime comparison between the programs for two construction solutions and the proposed algorithms.}
 	\label{tbl:3}
@@
 Secondly, Method B checks the suffix and LCP arrays using the induced sorting principle.
-Unfortunately, the existing IS-based suffix/LCP array construction algorithms are not capable of fully using the available computation resources.
-At the time of writing this paper, the authors are making research on designing IS-based algorithms for running in the context of parallel environments.
+At the time of writing this paper, the existing IS-based suffix/LCP array construction algorithms are not capable of fully using the available computation resources.
+We are now devoted to designing IS-based construction algorithms scalable for running in parallel environments.
 This work may also improve the implementation design of Algorithm~\ref{alg:2}.
@@
 For example, sometimes the consistency of a suffix/LCP array may be broken due to hardware malfunctions or human errors.
-If the backup of the corrupted data is not available and it is too time-consuming to rebuild the whole array, then we can locate the bad areas quickly by using a generalized version of Algorithm~\ref{alg:1} and restore the partial SA for each area by calling a sparse SA construction algorithm.
+If the backup of the corrupted data is not available and it is too time-consuming to rebuild the whole array, then we can locate the bad areas quickly using Algorithm~\ref{alg:1} and restore the partial SA for each area by calling a sparse SA construction algorithm.
 Another example is to check the correctness of a sparse SA.
-Because the number of suffixes in the sparse SA is commonly much smaller than the number of suffixes in the SA, it is expected that a substantial improvement in time, space and I/O volume can be achieved when performing verification using the proposed algorithms.
+Because the number of suffixes in a sparse SA is commonly much smaller than the number of suffixes in the corresponding SA, it is expected that a substantial improvement in time, space and I/O volume can be achieved when performing verification using Algorithm~\ref{alg:1}.
 
@@
 In this paper, we propose two methods for probabilistically checking the given suffix and LCP arrays.
-Theoretically, the external-memory algorithms designed by these methods can achieve better time and I/O complexities compared to the existing fastest construction algorithms.
-Our experimental results indicate that the programs for Algorithm~\ref{alg:2} designed by Method B run slower than that for Algorithm~\ref{alg:1} designed by Method A, but they are more efficient than the latter in terms of time and I/O volume.
-As discussed in Section~\ref{sec:experiment}, there are still several ways of enhancing the performance of our programs.
-For future work, we attempt to redesign the sorting and inducing process in our implementations to make them competitive with the state-of-the-art parallel construction algorithms.
+Theoretically, the external-memory algorithms designed by these methods have better time and I/O complexities compared to the existing fastest construction algorithms.
+Our experimental results indicate that the programs for Algorithm~\ref{alg:2} designed by Method B run slower than that for Algorithm~\ref{alg:1} designed by Method A, but they are much more space-efficient than the latter.
+As discussed in Section~\ref{sec:experiment}, there is still a great potential for enhancing the performance of our programs.
+For future work, we are now attempting to redesign the sorting and inducing process in our implementations to make them competitive with the state-of-the-art parallel construction algorithms.
 
@@
 The problem here is how to obtain the LCP-value of these inducing suffixes, which is modeled as a range minimum query in~\cite{Fischer11} and can be easily answered within $\mathcal{O}(1)$ time using $\mathcal{O}(\|\Sigma\|)$ space.
-To be specific, when scanning from $sa[0]$ to $sa[5]$ in lines 10-21 of Fig.~\ref{fig:example2}, we induce ${\sf suf}(12)$ and ${\sf suf}(6)$ into the neighboring positions in ${\sf sa\_bkt_L(2)}$.
-During the scan, if we keep recording the minimal of $lcp(0, 5]$ in a variable, then we can obtain the LCP-value of the inducing suffixes ${\sf suf}(13)$ and ${\sf suf}(5)$ from this variable when putting ${\sf suf}(6)$ into $sa$.
+For example, when scanning from $sa[0]$ to $sa[5]$ in lines 10-21 of Fig.~\ref{fig:example2}, we induce ${\sf suf}(12)$ and ${\sf suf}(6)$ into the neighboring positions in ${\sf sa\_bkt_L(2)}$.
+During the scan of $sa[0, 5]$, if we keep recording the minimal of $lcp(0, 5]$ in a variable, then we can obtain the LCP-value of the inducing suffixes ${\sf suf}(13)$ and ${\sf suf}(5)$ from this variable when putting ${\sf suf}(6)$ into $sa$.
 
@@
 
-	\caption{An Example for Computing the suffix and LCP arrays during the Induction Phase. \label{fig:example2}}	
+	\caption{An Example for computing the suffix and LCP arrays during the induction phase. \label{fig:example2}}	
 \end{figure}

### 2017-03-20 draft-new/draft.tex
2017/03/20

--- 2017-03-18 draft-alternative/draft.tex
@@
 
-{\color{blue} 
-Abstract changed. \\
-Many changes, not to mark. \\
-Some marked in blue for your check. \\
-The figures and tables should be near to the content talking about them. \\
-Do not use too many: we, based, following, clearly...  \\
-}
-
 \section{Introduction}\label{sec:introduction}
@@
 In respect of the research on LCP array construction algorithms, the existing works can be classified into two categories with regard to their input requirements, where the algorithms from the first category compute both suffix and LCP arrays at the same time with the original text only~\cite{Fischer11, Bingmann12, Flick2015}, and those from the second category carry out the computation by taking SA and/or Burrows-Wheeler transform (BWT) as additional inputs~\cite{Kasai2001,Karkkainen2009, Fischer11, Puglisi2008, Deo2013}.
-So far, the algorithms designed by the induced sorting~(IS) principle take linear time and space to run and get the best results on both internal and external memory~\cite{Nong11, esais}.
+So far, the algorithms designed by the induced sorting~(IS) principle take linear time and space to run and get the best results on both internal and external memory~\cite{Nong11, Bingmann12}.
 In addition to the sequential algorithms, there are also parallel algorithms proposed to achieve high performance by fully using the available multi-core CPUs and/or GPUs~\cite{Osipov2012, Deo2013, Wang2015, Karkkainen2015, Karkkainen2016}.
@@
 Its implementation in external memory suffers from a space bottleneck due to the large disk volume taken by each sort.
-To overcome this drawback, Method B first employs the fingerprinting technique to check a subset selected from the given suffix and LCP arrays, then it reuses the inducing process of the IS-based construction algorithm SA-IS \cite{Nong11} to produce the final suffix and LCP arrays from the verified subset and literally compares them with the input arrays to ensure the correctness of the latter.
+To overcome this drawback, Method B first employs the fingerprinting technique to check a subset selected from the given suffix and LCP arrays, 
+%then it reuses the inducing process of the IS-based construction algorithm SA-IS \cite{Nong11} to produce the final suffix and LCP arrays from the verified subset and literally compares them with the input arrays to ensure the correctness of the latter.
 Our experiments indicate that the peak disk use of the programs for Algorithm~\ref{alg:2} designed by Method B is only about half as that of the program for Algorithm~\ref{alg:1} designed by Method A.
+{\color{red}{then it utilizes the IS method to produce the final suffix and LCP arrays from the verified subset and literally compares them with the input arrays to ensure the correctness of the latter.
+Our experiments indicate that the program for Algorithm~\ref{alg:2} designed by Method B only takes around half as much disk space as the program for Algorithm~\ref{alg:1} designed by Method A.}}
 
@@
 Section~\ref{sec:experiment} conducts an experimental study for performance evaluation of our programs for these algorithms.
-Section~\ref{sec:conclusion} gives some concluding remarks.
+{\color{red}{Finally}}, Section~\ref{sec:conclusion} gives some concluding remarks.
 
@@
 
-Notice that two equal substrings always share a common fingerprint, but the inverse is not true.
-It has been proven in~\cite{Karp1987} that the probability of a false match can be reduced to a negligible level by setting $L$ to a large value\footnote{This property is utilized in~\cite{Bille2013} to design a probabilistic algorithm for computing a sparse suffix array.}.
+Notice that two equal substrings always share a common fingerprint, but the inverse is not true. It has been %proven
+{\color{red}{proved}} in~\cite{Karp1987} that the probability of a false match can be reduced to a negligible level by setting $L$ to a large value\footnote{This property is utilized in~\cite{Bille2013} to design a probabilistic algorithm for computing a sparse suffix array.}.
 Hence, we have:
@@
 Given that $L = 197$ and $\delta = 101$, lines 4-8 compute ${\sf fp}(0, p)$ iteratively according to Formulas~\ref{formula:1}-\ref{formula:2}.
-Then, lines 10-16 use these values to compute the fingerprints for all the target substrings.
+Then, {\color{red}{lines 10-20}} use these values to compute the fingerprints for all the target substrings.
 In more detail, consider the leftmost pair of neighboring suffixes in $sa$, i.e.
@@
 Following the same way, ${\sf fp}(sa[1], sa[1] + lcp[1] - 1)$ is computed by reducing ${\sf fp}(0, sa[1] - 1)$ from ${\sf fp}(0, sa[1] + lcp[1] - 1)$.
-Hence, we obtain the fingerprints for these two substrings in lines 10-12 and see that they are equal to each other.
+Hence, we obtain the fingerprints for these two substrings in {\color{red}{lines 10-14}} and see that they are equal to each other.
 
@@
 
-		{\color{blue} sort the tuples in $ST_1$, $ST_2$ and $ST_3$ by the 1st components, respectively;} \label{alg:1:b}
+		sort the tuples in $ST_1$, $ST_2$ and $ST_3$ by the 1st components, respectively; \label{alg:1:b}
 
@@
 			\Else{
-				\Return false \hspace{5cm} // condition (1) is violated
+				\Return false \hspace{5cm} // condition 1 is violated
 			}~\label{alg:1:i}
@@
 
-		{\color{blue} sort the tuples in $ST_1'$, $ST_2'$ and $ST_3'$ by the 2nd component, respectively;} \label{alg:1:e}
+		sort the tuples in $ST_1'$, $ST_2'$ and $ST_3'$ by the 2nd component, respectively; \label{alg:1:e}
 
@@
 
-				\Return false \hspace{5cm} // condition (2) or (3) is violated
+				\Return false \hspace{5cm} // condition 2 or 3 is violated
 			}	
@@
 Algorithm~\ref{alg:1} reaches its peak disk use when sorting the tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}.
-Suppose the input string and the suffix/LCP array are encoded as $\alpha$- and $\beta$-byte integers, respectively, and each fingerprint is a $\gamma$-byte integer, it takes $(2 \cdot (2 \cdot \alpha + \beta))$ space for sorting the tuples of $ST_1/ST_1'$ and $(2 \cdot (2 \cdot \alpha + \beta + \gamma))$ for sorting the tuples of $ST_2/ST_2'$ and $ST_3/ST_3'$.
+Suppose the input string and the suffix/LCP array are encoded as $\alpha$- and $\beta$-byte integers, respectively, and each fingerprint is a $\gamma$-byte integer, it takes $(2 \cdot (\alpha +2 \cdot \beta))$ space for sorting the tuples of $ST_1/ST_1'$ and $(2 \cdot (\alpha + 2 \cdot \beta + \gamma))$ for sorting the tuples of $ST_2/ST_2'$ and $ST_3/ST_3'$.
 For saving space, our program implementing the algorithm tackles $ST_1/ST_1'$, $ST_2/ST_2'$ and $ST_3/ST_3'$ separately and performs a single scan over $x$ for each of them to obtain the fingerprints, using less space but more time.
-The experiment in Section~\ref{sec:experiment} indicates that the peak disk use is 40 bytes per input character.
+The experiment in Section~\ref{sec:experiment} indicates that {\color{red}{the disk use is 40 times the size of $x$.}}
 
@@
 
-We further to give another checking method using the induced sorting principle {\color{blue} \cite{sais,ka}}, , which requires much less space than Method A.
+We further to give another checking method using the induced sorting principle \cite{Nong11,Dementiev08}, which requires much less space than Method A.
 For presentation convenience, we introduce some symbols and notations as below.
 
-{\em Character and suffix classification.} All the characters in $x$ are classified into three types, namely L-, S- and S*-type.
+Character and suffix classification.
+All the characters in $x$ are classified into three types, namely L-, S- and S*-type.
 In detail, $x[i]$ is L-type if (1) $i = n - 1$ or (2) $x[i] > x[i + 1]$ or (3) $x[i] = x[i + 1]$ and $x[i + 1]$ is L-type; otherwise, $x[i]$ is S-type.
@@
 
-{\em Suffix and LCP buckets.} All the suffixes in $sa$ are partitioned into multiple buckets and those of a common heading character are grouped into a single bucket that occupies a contiguous interval in $sa$.
+Suffix and LCP buckets.
+All the suffixes in $sa$ are partitioned into multiple buckets and those of a common heading character are grouped into a single bucket that occupies a contiguous interval in $sa$.
 Each bucket can be further divided into two sub-buckets, where the left and the right parts  contain L- and S-type suffixes only, respectively.
@@
 
-{\em Suffix and LCP arrays for S*-type suffixes.} Given that the number of S*-type suffixes is $n_1$, $sa^*[0, n_1)$ stores all the S*-type suffixes arranged in lexical order, while $lcp^*[0] = 0$ and $lcp^*[i]$ records the LCP-value of ${\sf suf}(sa^*[i])$ and ${\sf suf}(sa^*[i - 1])$ for $i \in [1, n_1)$.
+Suffix and LCP arrays for S*-type suffixes.
+Given that the number of S*-type suffixes is $n_1$, $sa^*[0, n_1)$ stores all the S*-type suffixes arranged in lexical order, while $lcp^*[0] = 0$ and $lcp^*[i]$ records the LCP-value of ${\sf suf}(sa^*[i])$ and ${\sf suf}(sa^*[i - 1])$ for $i \in [1, n_1)$.
 
-{\em Type Array.} The array $t$ records in $t[i]$ the type information of $x[i]$, where $t[i] = 1$ or $0$ if $x[i]$ is S- or L-type, respectively.
+Type Array. The array $t$ records in $t[i]$ the type information of $x[i]$, where $t[i] = 1$ or $0$ if $x[i]$ is S- or L-type, respectively.
 
@@
 
-The induced sorting principle has been extensively used to design efficient algorithms for constructing the suffix and LCP arrays in internal or external memory {\color{blue} \cite{sais,dsais,emsads,esais,inducelcp}}.
+The induced sorting principle has been extensively used to design efficient algorithms for constructing the suffix and LCP arrays in internal or external memory \cite{Nong11,Nong14, Nong15, Bingmann12,Fischer11}.
 Such a construction algorithm mainly consists of a reduction phase for computing $sa^*$ and $lcp^*$, followed by an induction phase for inducing $sa$ and $lcp$ from $sa^*$ and $lcp^*$~\footnote{An overview of the induction phase is given in Appendix~\ref{sec:appendix}.}.
@@
 Notice that, we check condition 1 when visiting the suffixes in their position order (lines~\ref{alg:2:e}-\ref{alg:2:f}), and check conditions 2 and 3 by Algorithm~\ref{alg:1} with $sa^*$ and $lcp^*$ as input.
-Suppose $sa^*$ and $lcp^*$ are both correct, then Algorithm~\ref{alg:2} invokes the inducing process of an existing IS-based construction algorithm to induce $sa'$ and $lcp'$ from the two verified arrays $sa^*$ and $lcp^*$~(line~\ref{alg:2:k}) and compares them with $sa$ and $lcp$ to complete the whole checking process~(lines~\ref{alg:2:l}-\ref{alg:2:m}).
+Suppose $sa^*$ and $lcp^*$ are both correct, %then Algorithm~\ref{alg:2} invokes the inducing process of an existing IS-based construction algorithm
+{\color{red}{then Algorithm~\ref{alg:2} invokes an inducing process for employing the IS method}} to induce $sa'$ and $lcp'$ from the two verified arrays $sa^*$ and $lcp^*$~(line~\ref{alg:2:k}) and compares them with $sa$ and $lcp$ to complete the whole checking process~(lines~\ref{alg:2:l}-\ref{alg:2:m}).
 
@@
 
-				\Return false  \hspace{1cm} // condition (1) is violated
+				\Return false  \hspace{1cm} // condition 1 is violated
 			}
@@
 
-		\Return false \hspace{1cm} // conditions (2) or (3) is violated
+		\Return false \hspace{1cm} // conditions 2 or 3 is violated
 	}\label{alg:2:j}
@@
 
-			\Return false \hspace{1cm}	// condition (4) is violated
+			\Return false \hspace{1cm}	// condition 4 is violated
 		}	
@@
 
-{\bf Assume that the alphabet $\Sigma$ is of size $\mathcal{O}(1)$, we can check $sa$ and $lcp$ without storing the induced suffix and LCP arrays in Algorithm~\ref{alg:2}.} The idea is to compare the induced suffix/LCP items with their corresponding items in $sa/lcp$ during the inducing process.
+Assume that the alphabet $\Sigma$ is of size $\mathcal{O}(1)$, we can check $sa$ and $lcp$ without storing the induced suffix and LCP arrays in Algorithm~\ref{alg:2}.
+The idea is to compare the induced suffix/LCP items with their corresponding items in $sa/lcp$ during the inducing process.
 Specifically, when a suffix/LCP item $v_1$ is induced into a bucket, we check if it is equal to the corresponding item $v_2$ in $sa/lcp$.
@@
 This can be done by conducting sequential I/O operations if we provide a read pointer together with a buffer for each suffix/LCP sub-bucket.
-We describe below more details of the modified inducing process, where $lp_1/lp_2$ and $sp_1/sp_2$ are file pointer arrays for reading items from the sub-buckets of $sa$ and $lcp$.
+We describe below more details of the modified inducing process, %where $lp_1/lp_2$ and $sp_1/sp_2$ are file pointer arrays for reading items from the sub-buckets of $sa$ and $lcp$.
+{\color{red}{where $lp_1/lp_2$ and $sp_1/sp_2$ indicate the next items to be visited in the L-type and S-type sub-buckets, respectively.}}
 
@@
 
-Algorithm~\ref{alg:2} mainly consists of two parts, where the first part for checking $sa^*$ and $lcp^*$ can be done within sorting complexity and the second part for checking $sa$ and $lcp$ can be done in linear time.
-In our current program for this algorithm, the peak disk use is reached in part two, specifically, when computing the BWT from $sa$ and $x$ for use in the inducing process.
+{\color{red}{Algorithm~\ref{alg:2} mainly consists of two steps, where the first step for checking $sa^*$ and $lcp^*$ can be done within sorting complexity and the second step for checking $sa$ and $lcp$ can also be done in sorting complexity for using external-memory sorters and priority queues.
+In our current program for this algorithm, the peak disk use is reached in step two, specifically, when computing the BWT from $sa$ and $x$ for use in the inducing process.
+}}
 
@@
 Fig.~\ref{fig:performance_analysis} shows that the maximum space requirement for ProgB+ is about $21n$, which is much less than that of ProgB and even only half as that of ProgA.
-In addition, progB+ outperforms its prototype with respect to time and I/O efficiency and is faster than ProgA when handling "proteins".
+In addition, progB+ outperforms its prototype with respect to time and I/O efficiency and is faster than ProgA when handling "uniprot".
 We also investigate the performance trend of the three programs on the prefix of "enwiki" with the length varying in $\{1, 2, 4, 8\}$ GiB.
@@
 In this experiment, pSAscan builds the SA for "enwiki\_8g" in time double as that for "enwiki\_1g".
-{\bf For big $n$, it is more reasonable to compare the results of our programs with that of Solution 1.}
+For big $n$, it is more reasonable to compare the results of our programs with that of Solution 1.
 
@@
 Because the induced sorting process is the performance bottleneck for Method B, it is reasonable to expect that a better engineering implementation of the method will yield a remarkable improvement in both time and space.
-{\bf An optimized engineering of our methods is out of the scope of this paper and will be addressed elsewhere.}
+An optimized engineering of our methods is out of the scope of this paper and will be addressed elsewhere.
 
@@
 Our experimental programs can be further optimized to achieve higher performance, in particular for checking arrays of constant alphabets that are most common in practice.
-The optimized programs will run much faster and use at most $n$ integers as the working space in addition to the input arrays.
+{\color{red}{The optimized programs will run much faster and use at most $n$ integers as the working space in addition to the input arrays.}  \color{blue}{Should be deleted.
+This may not be correct, because it takes more space to verify $sa_L/sa_S$ and $lcp_L/lcp_S$ by Algorithm~\ref{alg:1}.}}
 
@@
 
+% Bibliography
+\bibliographystyle{IEEEtran}
+\bibliography{IEEEabrv,bibfile}
+
+\newpage
 \appendices
@@
 The problem here is how to obtain the LCP-values of these inducing suffixes starting at the next positions in $x$, which is modeled as a range minimum query in~\cite{Fischer11} and can be answered within amortized $\mathcal{O}(1)$ time.
-For example, when scanning from $sa[0]$ to $sa[5]$ in lines 10-21 of Fig.~\ref{fig:example2}, we induce ${\sf suf}(12)$ and ${\sf suf}(6)$ into the neighboring positions in ${\sf sa\_bkt_L(2)}$.
-During the scan, if we keep recording the minimum of $lcp(0, 5]$ in a variable, then we can obtain the LCP-value of the suffixes ${\sf suf}(13)$ and ${\sf suf}(5)$ from this variable when putting ${\sf suf}(6)$ into $sa$.
+{\color{red}{For example, when scanning $sa[0]$ and $sa[5]$ in lines 10-11 and 20-21 of Fig.~\ref{fig:example2}, we sequentially induce ${\sf suf}(12)$ and ${\sf suf}(6)$ into the neighboring positions in ${\sf sa\_bkt_L(2)}$.
+In the meantime, if we keep recording the minimum over $lcp(0, 5]$, then we can obtain the LCP-value of the inducing suffixes ${\sf suf}(13)$ and ${\sf suf}(7)$ when putting the induced suffix ${\sf suf}(6)$ into $sa$}}.
 
@@
 \end{figure}
-
-% Bibliography
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,bibfile}
 

### 2017-03-20 draft-old/draft.tex
2017/03/20

--- 2017-03-17 draft/draft.tex
@@
 This method is rather general in terms of that it can verify any full or sparse suffix/LCP array of any order.
-The second method is more space efficient, it first employs the fingerprinting technique to verify a subset of the given suffix and LCP arrays, from which then a copy of the suffix and LCP arrays is produced by using the induced sorting method and compared with the given arrays for verification.
-In particular, for constant alphabets, the copy of the induced suffix and LCP arrays can be removed to make a further improvement on the space efficiency.
+The second method is more space efficient, it first employs the fingerprinting technique to verify a subset of the given suffix and LCP arrays, from which then a copy of the suffix and LCP arrays is produced by using the induced sorting method and compared with the given arrays for verification, where the copy of the induced suffix and LCP arrays can be removed for constant alphabets.
 
@@
 To overcome this drawback, Method B first employs the fingerprinting technique to check a subset selected from the given suffix and LCP arrays, then it utilizes the IS method to induce the final suffix and LCP arrays from the verified subset and literally compares them with the input arrays to ensure the correctness of the latter.
-Our experimental results indicate that the programs for Algorithm~\ref{alg:2} designed by Method B only take around half as much disk space as the program for Algorithm~\ref{alg:1} designed by Method A.
+Our experimental results indicate that the program for Algorithm~\ref{alg:2} designed by Method B only takes around half as much disk space as the program for Algorithm~\ref{alg:1} designed by Method A.
 
@@
 Section~\ref{sec:experiment} conducts an experimental study for performance evaluation of our programs for these algorithms.
-Section~\ref{sec:conclusion} gives some concluding remarks.
+Finally, Section~\ref{sec:conclusion} gives some concluding remarks.
 
@@
 
-{\bf Assume that the alphabet $\Sigma$ is of a constant size, we can check $sa$ and $lcp$ without producing a copy of the final suffix and LCP arrays in Algorithm~\ref{alg:2}.} The idea is to compare the induced suffix/LCP items with their corresponding items in $sa/lcp$ during the inducing process.
+Assume that the alphabet $\Sigma$ is of a constant size, we can check $sa$ and $lcp$ without producing a copy of the final suffix and LCP arrays in Algorithm~\ref{alg:2}.
+The idea is to compare the induced suffix/LCP items with their corresponding items in $sa/lcp$ during the inducing process.
 Specifically, when a suffix/LCP item $v_1$ is induced into a bucket, we check if it is equal to the corresponding item $v_2$ in $sa/lcp$.
@@
 Because the inducing process is the performance bottleneck for Method B, it is reasonable to expect that a better engineering implementation of the method will yield a remarkable performance improvement.
-{\bf An optimized engineering of our methods is out of the scope of this paper and will be addressed elsewhere.}
+An optimized engineering of our methods is out of the scope of this paper and will be addressed elsewhere.
 
@@
 For example, in lines 10-21 of Fig.~\ref{fig:example2}, we induce ${\sf suf}(12)$ and ${\sf suf}(6)$ into the neighboring positions of ${\sf sa\_bkt_L(2)}$, respectively.
-If we keep recording the minimal over $lcp(0, 5]$, then we can obtain the LCP-value of the inducing suffixes ${\sf suf}(13)$ and ${\sf suf}(5)$ immediately after putting ${\sf suf}(6)$ into $sa$.
+If we keep recording the minimal over $lcp(0, 5]$, then we can obtain the LCP-value of the inducing suffixes ${\sf suf}(13)$ and ${\sf suf}(7)$ immediately after putting ${\sf suf}(6)$ into $sa$.
 This problem is modeled as a range minimum query in~\cite{Fischer11} and can be answered within amortized $\mathcal{O}(1)$ time.
@@
 
-% Bibliography
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,bibfile}
-
 \end{document}
-
-We are intended for ....
-
-put emphasis on
-
-with the same ease as when
-
-The biggest difference between two is that ...
-
-Toward the end, ...
-
-they are designed to be both easy to interpret on ... and easily traslated into ... (they are designed to be easily implemented in classic external memory models)
-
-Having a ... eliminates .... (random accesses), access ordering
-
-Not only are ..., but
-
-The fingerprints are calculated on the fly during the scan of x ...
-
-become so good that they are competitive with ...., and in some cases, even outperform them ...
-
-concurrent programming is needed to make sure ....
-
-designed to adapt to an evolving environment
-
-most importantly
-
-exchanges data between the computer presenting the applet and the computer serving it.
-
-carries out sophisticated calculations
-
-Presumably because
-
-make ... capable of ...
-
-greatly improve ... , it was still rather limited, though.
-
-additional performance improvements
-
-close the chapter with ...
-
-gain
-
-which pose ...
-
-integrate with
-
-In this chapter, we will ... how to ... and how to ...
-
-we prefer the comfort of an integrated development environment, ( prefer the low cost of fingerprinting techinques)
-
-space-hungry
-
-begin exploring ... by ...
-
-commnuicate the monmentous advances
-
-extremely simple
-
-check each number is present in the suffix array.
-
-go into much more greater details
-
-stand-alone algorithms for computing suffix arrays only and has been reused to
-
-invoke/call
-
-the mechanics of ...
-
-If you have done sth, then when you do sth, you end up with ...
-
-depend on the machine on which you will be running the java code ...
-
-alleviate
-
-The second method is invented to overcome the drawback of
-
-in place of
-
-as to/about
-
-as far as
-
-assign to a variable
-
-stated goals
-
-intermediate steps
-
-tied to the behavior of
-
-an assortment of
-
-following the footsteps of
-
-characters in the input string are processed from left to right
-
-in greater detail
-
-in the  order received
-
-build up a whole new thing from scratch
-
-In the interest of completeness, we briefly discuss the date and time formatting options of the printf method
-
-immediately follow
-
-preceding statement
-
-tuned version
-
-hang on to the object
-
-track down
-
-invisible to the remainder of the program
-
-put it another way

### 2017-03-30 draft-new/draft.tex
2017/03/30

@@
 Algorithm~\ref{alg:1} reaches its peak disk use when sorting the tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}.
-Suppose the input string and the suffix/LCP array are encoded as $\alpha$- and $\beta$-byte integers, respectively, and each fingerprint is a $\gamma$-byte integer, it takes $(2 \cdot (\alpha +2 \cdot \beta))$ space for sorting the tuples of $ST_1/ST_1'$ and $(2 \cdot (\alpha + 2 \cdot \beta + \gamma))$ for sorting the tuples of $ST_2/ST_2'$ and $ST_3/ST_3'$.
+Suppose the input string and the suffix/LCP array are encoded as $\alpha$- and $\beta$-byte integers, respectively, and each fingerprint is a $\gamma$-byte integer, it takes $(\alpha +2 \cdot \beta)$ space for sorting the tuples of $ST_1/ST_1'$ and $(\alpha + 2 \cdot \beta + \gamma)$ for sorting the tuples of $ST_2/ST_2'$ and $ST_3/ST_3'$.
 For saving space, our program implementing the algorithm tackles $ST_1/ST_1'$, $ST_2/ST_2'$ and $ST_3/ST_3'$ separately and performs a single scan over $x$ for each of them to obtain the fingerprints, using less space but more time.
@@
 
-From our perspective, a checker should be not only fast but also general.
-For program debugging, we usually check the output of a builder by comparing it with that of another builder.
-But this is not feasible in all the cases, for example, an algorithm for constructing infinite-order array can not be directly used to check a finite-order array and vise versa.
+From our perspective, a checker should be not only fast but also general. %For program debugging,
+{\color{red}{In practice,} \color{blue}{not only for program debugging but also for checking results from probabilistic builders}} we usually check the output of a builder by comparing it with that of another builder.
+But this is not feasible in all the cases, for example, an algorithm for constructing {\color{red}{an}} infinite-order array can not be directly used to check a finite-order array and vise versa.
 On the contrary, our first method can be generalized to check the correctness of the lexical order and the LCP values of any pairs of suffixes.

### 2017-04-25 draft/draft.tex
2017/04/25

--- 2017-03-14 draft/draft.tex
@@
 Wu, G.
-Nong (corresponding author) and L.~B.~Han are with the Department of Computer Science, Sun Yat-sen University, Guangzhou 510275, China.
+Nong (corresponding author) and L.~B.~Han are with the Department of Computer Science, Sun Yat-sen University, Guangzhou, and the SYSU-CMU Shunde International Joint Research Institute, Shunde, China.
 E-mails: wu.yi.christian@gmail.com, issng@mail.sysu.edu.cn, hanlb@mail2.sysu.edu.cn.
@@
 In respect of the research on LCP array construction algorithms, the existing works can be classified into two categories with regard to their input requirements, where the algorithms from the first category compute both suffix and LCP arrays at the same time with the original text only~\cite{Fischer11, Bingmann12, Flick2015}, and those from the second category carry out the computation by taking SA and/or Burrows-Wheeler transform (BWT) as additional inputs~\cite{Kasai2001,Karkkainen2009, Fischer11, Puglisi2008, Deo2013}.
-So far, the algorithms designed by the induced sorting~(IS) principle take linear time and space to run and get the best results on both internal and external memory~\cite{Nong11, Karkkainen2014, Karkkainen2017}.
+So far, the algorithms designed by the induced sorting~(IS) principle take linear time and space to run and get the best results on both internal and external memory~\cite{Nong11, Bingmann12}.
 In addition to the sequential algorithms, there are also parallel algorithms proposed to achieve high performance by fully using the available multi-core CPUs and/or GPUs~\cite{Osipov2012, Deo2013, Wang2015, Karkkainen2015, Karkkainen2016}.
@@
 Its implementation in external memory suffers from a space bottleneck due to the large disk volume taken by each sort.
-To overcome this drawback, Method B first employs the fingerprinting technique to check a subset selected from the given suffix and LCP arrays, then it reuses the inducing process of the IS-based construction algorithm SA-IS \cite{Nong11} to produce the final suffix and LCP arrays from the verified subset and literally compares them with the input arrays to ensure the correctness of the latter.
+To overcome this drawback, Method B first employs the fingerprinting technique to check a subset selected from the given suffix and LCP arrays, 
+%then it reuses the inducing process of the IS-based construction algorithm SA-IS \cite{Nong11} to produce the final suffix and LCP arrays from the verified subset and literally compares them with the input arrays to ensure the correctness of the latter.
 Our experiments indicate that the peak disk use of the programs for Algorithm~\ref{alg:2} designed by Method B is only about half as that of the program for Algorithm~\ref{alg:1} designed by Method A.
+then it utilizes the IS method to produce the final suffix and LCP arrays from the verified subset and literally compares them with the input arrays to ensure the correctness of the latter.
+Our experiments indicate that the program for Algorithm~\ref{alg:2} designed by Method B only takes around half as much disk space as the program for Algorithm~\ref{alg:1} designed by Method A.
 
@@
 Notice that two equal substrings always share a common fingerprint, but the inverse is not true.
-It has been proved in~\cite{Karp1987} that the probability of a false match can be reduced to a negligible level by setting $L$ to a large value\footnote{This property is utilized in~\cite{Bille2013} to design a probabilistic algorithm for computing a sparse suffix array.}.
-Hence, we have:
+The probability of a false match can be reduced to a negligible level by setting $L$ to a large value~\cite{Karp1987}, this property is utilized in~\cite{Bille2013} to design a probabilistic algorithm for computing a sparse suffix array.
+Hence we have:
 
 \begin{Corollary} \label{corollary:1}
-	Both $sa[0, n)$ and $lcp[0, n)$ are correct with a high probability given the following conditions, for all $i \in [1, n)$:
+	Both $sa[0, n)$ and $lcp[0, n)$ are correct with a high probability given these conditions, for all $i \in [1, n)$:
 
@@
 Given that $L = 197$ and $\delta = 101$, lines 4-8 compute ${\sf fp}(0, p)$ iteratively according to Formulas~\ref{formula:1}-\ref{formula:2}.
-Then, lines 10-16 use these values to compute the fingerprints for all the target substrings.
-In more detail, consider the leftmost pair of neighboring suffixes in $sa$, that is ${\sf suf}(sa[0])$ and ${\sf suf}(sa[1])$, the substrings indicated by their LCP-value are $x[sa[0], sa[0] + lcp[1] - 1]$ and $x[sa[1], sa[1] + lcp[1] - 1]$, respectively.
-According to Formula~\ref{formula:3}, ${\sf fp}(sa[0], sa[0] + lcp[1] - 1)$ is equal to the difference between ${\sf fp}(0, sa[0] - 1)$ and ${\sf fp}(0, sa[0] + lcp[1] - 1)$, both of which have been calculated beforehand.
+Lines 10-20 use these values to compute the fingerprints for all the target substrings.
+In more detail, consider the leftmost pair of neighboring suffixes in $sa$, i.e.
+${\sf suf}(sa[0])$ and ${\sf suf}(sa[1])$, the substrings given by their LCP-value are $x[sa[0], sa[0] + lcp[1] - 1]$ and $x[sa[1], sa[1] + lcp[1] - 1]$, respectively.
+According to Formula~\ref{formula:3}, ${\sf fp}(sa[0], sa[0] + lcp[1] - 1)$ is equal to the difference between ${\sf fp}(0, sa[0] - 1)$ and ${\sf fp}(0, sa[0] + lcp[1] - 1)$, both have been calculated.
 Following the same way, ${\sf fp}(sa[1], sa[1] + lcp[1] - 1)$ is computed by reducing ${\sf fp}(0, sa[1] - 1)$ from ${\sf fp}(0, sa[1] + lcp[1] - 1)$.
-Hence, we obtain the fingerprints for these two substrings in lines 10-12 and see that they are equal to each other.
+Hence, we obtain the fingerprints for these two substrings in lines 10-14 and see that they are equal to each other.
 
@@
 
-		sort tuples in $ST_1$, $ST_2$ and $ST_3$ by 1st component \label{alg:1:b}
+		sort the tuples in $ST_1$, $ST_2$ and $ST_3$ by the 1st components, respectively; \label{alg:1:b}
 
@@
 			\Else{
-				\Return false \hspace{5cm} // condition (1) is violated
+				\Return false \hspace{1cm} // condition 1 is violated
 			}~\label{alg:1:i}
@@
 
-			$fp := fp \cdot \delta + x[i] \! \mod \! P$ \hspace{5cm} // $x[n]$ is the virtual character
+			$fp := fp \cdot \delta + x[i] \! \mod \! P$ \hspace{1cm} // $x[n]$ is the virtual character
 		} \label{alg:1:d}
 
-		sort tuples in $ST_1'$, $ST_2'$ and $ST_3'$ by 2nd component.  \label{alg:1:e}
+		sort the tuples in $ST_1'$, $ST_2'$ and $ST_3'$ by the 2nd component, respectively; \label{alg:1:e}
 
@@
 
-				\Return false \hspace{5cm} // condition (2) or (3) is violated
+				\Return false \hspace{1cm} // condition 2 or 3 is violated
 			}	
@@
 
-Algorithm~\ref{alg:1} performs multiple scans and sorts on the arrays of $\mathcal{O}(n)$ fixed-size tuples residing on disks.
-Given an external memory model with RAM size $M$, disk size $D$ and block size $B$, all are in words, the time and I/O complexities for each scan are $\mathcal{O}(n)$ and $\mathcal{O}(n / B)$, respectively, while those for each sort are $\mathcal{O}(n\log_{M/ B}(n / B))$ and $\mathcal{O}((n / B)\log_{M / B}(n / B))$, respectively~\cite{Arge2013}.
-Algorithm~\ref{alg:1} reaches its peak disk use when sorting tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}.
-Suppose the input string and the suffix/LCP array are encoded using $\alpha$- and $\beta$-byte integers, respectively, and each fingerprint is represented by a $\gamma$-byte integer, it takes $(2 \cdot (2 \cdot \alpha + \beta)) \cdot n$ space for sorting $ST_1/ST_1'$ and $(2 \cdot (2 \cdot \alpha + \beta + \gamma)) \cdot n$ for sorting $ST_2/ST_2'$ and $ST_3/ST_3'$.
-To save disk space, our program implementing the algorithm sorts $ST_1/ST_1'$, $ST_2/ST_2'$ and $ST_3/ST_3'$ separately and performs a single scan over $x$ for each of them to obtain the target fingerprints, resulting in smaller space requirement but larger running time.
-The experimental study in Section~\ref{sec:experiment} indicates that this program is still space consuming, its peak disk use is 40 bytes per input character.
+Algorithm~\ref{alg:1} performs multiple scans and sorts on the arrays of $\mathcal{O}(n)$ fixed-size tuples in disks.
+Given RAM size $M$, disk size $D$ and block size $B$, all are in words, the time and I/O complexities for each scan are $\mathcal{O}(n)$ and $\mathcal{O}(n / B)$, respectively, while those for each sort are $\mathcal{O}(n\log_{M/ B}(n / B))$ and $\mathcal{O}((n / B)\log_{M / B}(n / B))$, respectively~\cite{Arge2013}.
+Algorithm~\ref{alg:1} reaches its peak disk use when sorting the tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}.
+Suppose the input string and the suffix/LCP array are encoded as $\alpha$- and $\beta$-byte integers, respectively, and each fingerprint is a $\gamma$-byte integer, it takes $(2 \cdot \beta + \gamma)$ space for sorting the tuples of $ST_1/ST_1'$ and $(\alpha + 2 \cdot \beta + \gamma)$ for sorting the tuples of $ST_2/ST_2'$ and $ST_3/ST_3'$.
+For saving space, our program implementing the algorithm tackles $ST_1/ST_1'$, $ST_2/ST_2'$ and $ST_3/ST_3'$ separately and performs a single scan over $x$ for each of them to obtain the fingerprints, using less space but more time.
+The experiment in Section~\ref{sec:experiment} indicates that the disk use is 40 times of $x$.
 
@@
 
-In this part, we describe an alternative checking method based on the induced sorting principle.
-Compared with Algorithm~\ref{alg:1}, our programs for Algorithm~\ref{alg:2} designed by this method take around half disk space on real-world datasets.
-Before the presentation, we introduce some symbols and notations used in the following paragraphs.
+We further to give another checking method using the induced sorting principle \cite{Nong11,Dementiev08}, which requires much less space than Method A.
+For presentation convenience, we introduce some symbols and notations as below.
 
-{\em Character and suffix classification.} All the characters in $x$ are classified into three types, namely L-, S- and S*-type.
+Character and suffix classification.
+All the characters in $x$ are classified into three types, namely L-, S- and S*-type.
 In detail, $x[i]$ is L-type if (1) $i = n - 1$ or (2) $x[i] > x[i + 1]$ or (3) $x[i] = x[i + 1]$ and $x[i + 1]$ is L-type; otherwise, $x[i]$ is S-type.
-Further, if $x[i]$ and $x[i + 1]$ are separately L-type and S-type, then $x[i + 1]$ is also an S*-type character.
+Further, if $x[i]$ and $x[i + 1]$ are separately L-type and S-type, then $x[i + 1]$ is also S*-type.
 Moreover, a suffix is L-, S- or S*-type if its heading character is L-, S-, or S*-type, respectively.
 
-{\em Suffix and LCP buckets.} Suppose $sa$ is correct, all the suffixes in $sa$ are naturally partitioned into multiple buckets and those of a common heading character are grouped into a single bucket that occupies a contiguous interval in $sa$.
-Each bucket can be further divided into two sub-buckets, where the left and the right parts only contain L- and S-type suffixes, respectively.
-For short, we use ${\sf sa\_bkt}(c)$ to denote the bucket storing suffixes starting with character $c$ and ${\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$ to denote its left/right sub-bucket.
-Accordingly, $lcp$ can be also split into multiple buckets, where ${\sf lcp\_bkt}(c)/{\sf lcp\_bkt_L}(c)/{\sf lcp\_bkt_S}(c)$ stores the LCP-values of suffixes in ${\sf sa\_bkt}(c)/{\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$.
+Suffix and LCP buckets.
+All the suffixes in $sa$ are partitioned into multiple buckets and those of a common heading character are grouped into a single bucket that occupies a contiguous interval in $sa$.
+Each bucket can be further divided into two sub-buckets, where the left and the right parts  contain L- and S-type suffixes only, respectively.
+For short, we use ${\sf sa\_bkt}(c)$ to denote the bucket storing the suffixes starting with character $c$ and ${\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$ to denote its left/right sub-bucket.
+Accordingly, $lcp$ can be also split into multiple buckets, where ${\sf lcp\_bkt}(c)/{\sf lcp\_bkt_L}(c)/{\sf lcp\_bkt_S}(c)$ stores the LCP-values of suffixes in ${\sf sa\_bkt}(c)/{\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$, respectively.
 
-{\em Suffix and LCP arrays for S*-type suffixes.} Given that the number of S*-type suffixes is $n_1$, $sa^*[0, n_1)$ stores all the S*-type suffixes arranged in lexical order, while $lcp^*[0] = 0$ and $lcp^*[i]$ records the LCP-value of ${\sf suf}(sa^*[i])$ and ${\sf suf}(sa^*[i - 1])$ for $i \in [1, n_1)$.
+Suffix and LCP arrays for S*-type suffixes.
+Given that the number of S*-type suffixes is $n_1$, $sa^*[0, n_1)$ stores all the S*-type suffixes arranged in lexical order, while $lcp^*[0] = 0$ and $lcp^*[i]$ records the LCP-value of ${\sf suf}(sa^*[i])$ and ${\sf suf}(sa^*[i - 1])$ for $i \in [1, n_1)$.
 
-{\em Type Array.} The array $t$ records in $t[i]$ the type information of $x[i]$, where $t[i] = 1$ or $0$ if $x[i]$ is S-type or L-type, respectively.
+Type Array. The array $t$ records in $t[i]$ the type information of $x[i]$, where $t[i] = 1$ or $0$ if $x[i]$ is S- or L-type, respectively.
 
@@
 
-The induced sorting principle has been extensively used to design efficient algorithms for constructing the suffix and LCP arrays on internal and external memory models.
-An IS-based construction algorithm mainly consists of a reduction phase for computing $sa^*$ and $lcp^*$, followed by an induction phase for inducing $sa$ and $lcp$ from $sa^*$ and $lcp^*$~\footnote{In the interest of completeness, we give an overview of the induction phase in Appendix~\ref{sec:appendix}.}.
-Given that $sa^*$ and $lcp^*$ are already known, we can produce the final suffix and LCP arrays by calling the inducing process of an existing IS-based construction algorithm.
-This enlightens us to design a checker based on Lemma~\ref{lemma:2}.
+The induced sorting principle has been extensively used to design efficient algorithms for constructing the suffix and LCP arrays in internal or external memory \cite{Nong11,Nong14, Nong15, Bingmann12,Fischer11}.
+Such a construction algorithm mainly consists of a reduction phase for computing $sa^*$ and $lcp^*$, followed by an induction phase for inducing $sa$ and $lcp$ from $sa^*$ and $lcp^*$~\footnote{An overview of the induction phase is given in Appendix~\ref{sec:appendix}.}.
+Given that $sa^*$ and $lcp^*$ are already known, we can induce the final suffix and LCP arrays from them.
+This suggests a checking method based on Lemma~\ref{lemma:2}.
 
@@
 
-The first step of Algorithm~\ref{alg:2} is to compute and verify $sa^*$ and $lcp^*$.
-According to their definitions, $sa^*$ can be produced by sequentially retrieving the S*-type suffixes from $sa$ and the LCP-value of two successive S*-type suffixes in $sa$, say ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$, is equal to the minimal of $\{lcp[i + 1], ..., lcp[j - 1], lcp[j]\}$.
-Hence, the proposed algorithm first sorts all the suffixes in $sa$ by their starting positions~(lines~\ref{alg:2:a}-\ref{alg:2:b}) and then scans $x$ only once to pick out the S*-type suffixes~(lines~\ref{alg:2:c}-\ref{alg:2:d}).
+We further to design Algorithm~\ref{alg:2} for checking the conditions of Corollary~\ref{corollary:2}.
+The first step is to compute and verify $sa^*$ and $lcp^*$.
+Similar to Method A, the fingerprinting technique is employed to probabilistically check the correctness of $sa^*$ and $lcp^*$.
+The array $sa^*$ can be produced by sequentially retrieving the S*-type suffixes from $sa$ and the LCP-value of two successive S*-type suffixes in $sa$, say ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$, is equal to the minimal of $\{lcp[i + 1], ..., lcp[j - 1], lcp[j]\}$.
+The algorithm first sorts all the suffixes in $sa$ by their starting positions~(lines~\ref{alg:2:a}-\ref{alg:2:b}) and then scans $x$ once to get the S*-type suffixes~(lines~\ref{alg:2:c}-\ref{alg:2:d}).
 After that, it puts these S*-type suffixes back in their lexical order and outputs them one by one to generate $sa^*$~(lines~\ref{alg:2:g}-\ref{alg:2:h}).
-Meanwhile, it calculates the LCP-value for each pair of the neighboring suffixes in $sa^*$ by tracing the minimal over the $lcp$ interval indicated by the two suffixes.
-Notice that, we check condition (1) in Corollary~\ref{corollary:2} during the time when visiting the suffixes in position order (lines~\ref{alg:2:e}-\ref{alg:2:f}) and conditions (2)-(3) by calling Algorithm~\ref{alg:1} with $sa^*$ and $lcp^*$ as input.
-Suppose $sa^*$ and $lcp^*$ are both correct, then Algorithm~\ref{alg:2} invokes the inducing process of an existing IS-based construction algorithm to induce $sa'$ and $lcp'$, which are a copy of the final suffix and LCP arrays, from the two verified arrays~(line~\ref{alg:2:k}) and literally compares them with $sa$ and $lcp$ to complete the whole checking process~(lines~\ref{alg:2:l}-\ref{alg:2:m}).
+Meanwhile, it calculates the LCP-value for each pair of the neighboring suffixes in $sa^*$ by tracing the minimum in the $lcp$ interval between these two suffixes.
+Notice that, we check condition 1 when visiting the suffixes in their position order (lines~\ref{alg:2:e}-\ref{alg:2:f}), and check conditions 2 and 3 by Algorithm~\ref{alg:1} with $sa^*$ and $lcp^*$ as input.
+Given $sa^*$ and $lcp^*$ are correct,
+Algorithm~\ref{alg:2} invokes an inducing process by employing the IS method to induce $sa'$ and $lcp'$ from $sa^*$ and $lcp^*$~(line~\ref{alg:2:k}) and compares them with $sa$ and $lcp$ to complete the whole checking process~(lines~\ref{alg:2:l}-\ref{alg:2:m}).
 
@@
 
-{\bf Assume that the alphabet $\Sigma$ is of a constant size, we can check $sa$ and $lcp$ without producing a copy of the final suffix and LCP arrays in Algorithm~\ref{alg:2}.} The idea is to compare the induced suffix/LCP items with their corresponding items in $sa/lcp$ during the inducing process.
+Assume that the alphabet $\Sigma$ is of size $\mathcal{O}(1)$, we can check $sa$ and $lcp$ without storing the induced suffix and LCP arrays in Algorithm~\ref{alg:2}.
+The idea is to compare the induced suffix/LCP items with their corresponding items in $sa/lcp$ during the inducing process.
 Specifically, when a suffix/LCP item $v_1$ is induced into a bucket, we check if it is equal to the corresponding item $v_2$ in $sa/lcp$.
 If $v_1 = v_2$, then $v_2$ is correct and we further use this value to induce the remaining suffix/LCP items.
-The key point here is to retrieve items of $sa/lcp$ from external storage as fast as possible.
+The key point is to quickly retrieve the items of $sa/lcp$ in external memory.
 This can be done by conducting sequential I/O operations if we provide a read pointer together with a buffer for each suffix/LCP sub-bucket.
-We describe below more details of the adapted inducing process, where $lp_1/lp_2$ and $sp_1/sp_2$ are file pointer arrays for reading items from the sub-buckets of $sa$ and $lcp$.
+We describe below more details of the modified inducing process, where $lp_1/lp_2$ and $sp_1/sp_2$ indicate the next items to be visited in the L-type and S-type sub-buckets, respectively.
 
@@
 
-Algorithm~\ref{alg:2} mainly consists of two parts, where the first part for checking $sa^*$ and $lcp^*$ can be done within sorting time and the second part for checking $sa$ and $lcp$ can be done in linear time.
-Clearly, the space complexity of part one is dependent upon the number of S*-type suffixes.
-As will be seen from Section~\ref{sec:experiment}, the programs for Algorithm~\ref{alg:2} take around $15n$ to check $sa^*$ and $lcp^*$, which is about one-third as that for Algorithm~\ref{alg:1} to check $sa$ and $lcp$.
-This corresponds to the ratio of S*-type suffixes to all in the real-world datasets.
-From our experiments, these programs take more disk space during the execution of inducing process, their peak disk use is about half as that for Algorithm~\ref{alg:1}.
+Algorithm~\ref{alg:2} mainly consists of two steps, where the first step for checking $sa^*$ and $lcp^*$ can be done within sorting complexity and the second step for checking $sa$ and $lcp$ can also be done in sorting complexity for using external-memory sorters and priority queues.
+In our current program for this algorithm, the peak disk use is reached in the second step, specifically, when computing the BWT from $sa$ and $x$ for use in the inducing process.
 
@@
 
-The experimental platform is a server equipped with an Intel Core i3-550 CPU, 4 GiB RAM and 2 TiB HD.
+The experimental platform is a server with an Intel Core i3-550 CPU, 4 GiB RAM and 2 TiB HD.
 All the programs are compiled by gcc/g++ 4.8.4 with -O3 options on ubuntu 14.04 64-bit operating system and each program is allowed to use 3 GiB RAM.
-For denotation convenience, we use "ProgA" and "ProgB" to represent the programs for Algorithms~\ref{alg:1} and~\ref{alg:2}, respectively.
+For simplicity, "ProgA" and "ProgB" represent the programs for Algorithms~\ref{alg:1} and~\ref{alg:2}, respectively.
 
@@
 	}
-	\caption{Performance of ProgA, ProgB and ProgB+ for different corpora.}
+	\caption{Performance of ProgA, ProgB, ProgB+ and ProgC for different corpora.}
 	\label{fig:performance_analysis}
@@
 	}
-	\caption{Performance of ProgA, ProgB and ProgB+ for prefixes of "enwiki".}
+	\caption{Performance of ProgA, ProgB, ProgB+ and ProgC for prefixes of "enwiki".}
 	\label{fig:performance_analysis2}
@@
 
-In the next experiment, we compare our programs with two solutions for building the suffix and LCP arrays as below, where each of them combines an existing suffix sorter with an LCP builder:
+Because there is no solution for checking both suffix and LCP arrays in the existing literature,  comparing the outputs of two builders could be a way for checking (even though it is not checking in the strict sense, for both outputs may be incorrect).
+In the next experiment, we compare our programs with two builders for suffix and LCP arrays as follows, where each of them combines an existing suffix sorter with an LCP builder:
 
@@
 In this experiment, pSAscan builds the SA for "enwiki\_8g" in time double as that for "enwiki\_1g".
-{\bf For big $n$, it is more reasonable to compare the results of our programs with that of Solution 1.}
+For big $n$, it is reasonable to compare the results of our programs with that of Solution 1.
 
@@
 
-\subsection{Discussion}
+Currently, the method described in~\cite{Burkhardt2003} is the only known in the literature for checking SA.
+Despite that it can check SA only, in order to give a rough image for the performance of our methods, we implement it by STXXL and compare our implementation with ProgA and ProgB/ProgB+ in Fig.~\ref{fig:performance_analysis} and \ref{fig:performance_analysis2}.
+This method and its program are denoted by "Method C" and "ProgC", respectively.
+ProgC is about two times faster than ProgA and three times faster than ProgB+, where the runtime is consistent with the I/O volume.
+This performance gap can be significantly narrowed by improving the algorithm and program designs of Methods A and B, using the techniques discussed below.
 
-There are still several ways to enhance the performance of our programs.
-Firstly, it was observed that our programs suffer from a bottleneck when sorting massive data in external memory.
-For implementation simplicity, we currently use the container provided by the STXXL library to execute the sorting task without designing a specific sorter optimized for our purpose.
-It is possible to speed up the sorting process by high-performance radix-sort GPU algorithms.
-Secondly, Method B checks the suffix and LCP arrays using the induced sorting principle.
-At the time of writing this paper, the existing IS-based suffix/LCP array construction algorithms are naturally sequential.
-We have been conducting a study to design IS-based parallel algorithms, this work may also improve the implementation design of Algorithm~\ref{alg:2}.
+\subsection{Discussion} \label{sec:experiments:discussion}
 
-Method A is able to check any set containing one or multiple pairs of lexicographically neighboring or non-neighboring suffixes.
-This feature can be applied to various scenarios.
-For example, a suffix/LCP array may be broken due to software or hardware malfunctions.
-If a backup is not available and it is too time-consuming to rebuild the whole array, then we can locate the bad areas quickly using Algorithm~\ref{alg:1} and restore the partial SA for each area by calling a sparse SA construction algorithm.
-Another example is to check the correctness of a sparse SA.
-Because the number of suffixes in a sparse SA is commonly much smaller than that in the full SA, Algorithm~\ref{alg:1} could become an efficient verification solution.
+\subsubsection{Improvement in Algorithm Design} \label{sec:experiments:discussion:improve_algorithm_design}
 
-%In this paper, both methods A and B assume a constant or integer alphabet.
-However, in practice, an input string is commonly of a constant alphabet, e.g.
-4 and 256 characters for genome and text, respectively.
-In this case, Method B can be improved for better time and space performance as follows.Given the alphabet is constant, we can first scan the input string once to get the statistics for buckets in the suffix array.
-Without loss of generality, suppose that the S-type characters are less.
-Then, we scan the input suffix array once to get ${\sf SA_S/LCP_S}$ consisting of all the sorted S-type suffixes with their LCP-values, by using the bucket statistics to on-the-fly determine a scanned suffix is S-type or not.
-From ${\sf SA_S/LCP_S}$, we can further induce the final suffix and LCP arrays from ${\sf SA_S/LCP_S}$ for checking.
-In this way, we can avoid the time and space required for the two sort($n$) in the current fashion of Method B, resulting in significant expected performance improvement.
-
-In this paper, both methods A and B assume a constant or integer alphabet.
+There are several ways to improve the algorithm designs of the proposed checking methods.
+First, Algorithm~\ref{alg:1} sorts the tuples of $ST_1/ST_1', ST_2/ST_2', ST_3/ST_3'$ in sequence.
+These sorting processes are independent and can be parallelized on computation platforms with multiple disks supporting parallel reads and writes.
+Second, Method B verifies the suffix and LCP arrays using the induced sorting principle.
+At the time of writing this paper, the existing IS algorithms are naturally sequential.
+Recently, we have been conducting a study to design parallel IS algorithms, this work will also help improve the design of Algorithm~\ref{alg:2}.
+Third, both methods A and B assume a constant or integer alphabet in this paper.
 However, in practice, an input string is commonly of a constant alphabet, e.g.
@@
 Given the alphabet is constant, we first scan the input string once to get the statistics for buckets in the input suffix array.
-Without loss of generality, suppose that the S-type characters are less, then we scan the suffix array once to get $sa_S/lcp_S$ by using the bucket statistics to on-the-fly determine a scanned suffix is S-type or not.
-Afterward, we check $sa_S/lcp_S$ by using Algorithm~\ref{alg:1} and induce $sa'/lcp'$ from them.
+Without loss of generality, suppose that the S-type characters are less, we scan the suffix array once to get $sa_S/lcp_S$ by using the bucket statistics to on-the-fly determine a scanned suffix is S-type or not.
+Then we check $sa_S/lcp_S$ by using Algorithm~\ref{alg:1} and induce $sa'/lcp'$ from them.
 In this way, we avoid the two integer sorts in the current fashion of Method B for retrieving $sa^*/lcp^*$ and speed up the inducing process by nearly half as well.
 
-It should be noticed that our programs are coded for experimental study only.
-From engineering aspects, there is still a big margin for better implementation.
-For example, several algorithms for induced sorting a suffix and/or LCP arrays were proposed these years \cite{Nong15,Nong14,Bingmann12}, with different methods for solving the key problem of retrieving the preceding character of a sorted suffix in the inducing process.
-A recent work \cite{Karkkainen2017} for engineering these induced sorting methods with some implementation optimizing techniques achieves a significant improvement over the previous results.
-As reported, the peak disk use is $7n$ for 32-bit integers.
-Because the induced sorting process is the performance bottleneck for Method B, it is reasonable to expect that a better engineering implementation of the method will yield a remarkable performance improvement.
-{\bf An optimized engineering of our methods is out of the scope of this paper and will be addressed elsewhere.}
+\subsubsection{Improvement in Program Design} \label{sec:experiments:discussion:improve_program_design}
+
+Our programs are coded for experimental study only, from engineering aspects, there is still a big margin for better implementation.
+For example, both ProgA and ProgB/ProgB+ consume long CPU time and large I/O volume for sorting data in external memory.
+We currently use the containers provided by STXXL to execute the sorting processes without designing a specific sorter optimized for our purpose.
+It is possible to speed up each sorting process by high-performance radix-sort GPU algorithms.
+Secondly, all our programs require a disk space significant more than what it is really needed.
+The main reason is the disk space for saving temporary data is not freed in time even if the data is not needed any more.
+This is an implementation issue due to STXXL in use, can be solved by storing the temporary data using multiple files and deleting each file immediately when it is obsolete.
+
+Several algorithms for induced sorting a suffix and/or LCP arrays were proposed these recent years \cite{Nong15,Nong14,Bingmann12}, with different methods for solving the key problem of retrieving the preceding character of a sorted suffix in the inducing process.
+A recent work \cite{Karkkainen2017} engineering these induced sorting methods with some implementation optimizing techniques achieves a significant improvement over the previous results.
+As reported, the peak disk use is around $8n$ for 40-bit integers.
+Because the induced sorting process is the performance bottleneck for Method B, it is reasonable to expect that a better engineering implementation of the method will yield a remarkable improvement in both time and space.
+An optimized engineering of our methods is out of the scope of this paper and will be addressed elsewhere.
+
+\subsubsection{Miscellaneous}
+
+Method A is more general than the other alternatives, it can be generalized to check the correctness of the lexical order and LCP values of any pairs of suffixes, this makes it possible for verifying any full or sparse suffix/LCP array of any order.
+On the other hand, Method B can only check suffix and LCP arrays, while Method C is specific for checking SA only.
+This feature of Method A makes it applicable to various scenarios.
+For example, a suffix/LCP array may be broken due to software or hardware malfunctions.
+If a backup is not available and it is time-consuming to rebuild the whole array, then we can locate the bad areas using Algorithm~\ref{alg:1} and restore the partial SA for each area by calling a sparse SA construction algorithm.
+Another example is to check the correctness of a sparse SA, in this case, the number of suffixes in a sparse SA is commonly much smaller than that in the full SA, Algorithm~\ref{alg:1} could be an efficient verification solution.
 
@@
 
-In this paper, we propose two methods for probabilistically checking the given suffix and LCP arrays.
+Two methods are proposed here for probabilistically checking a pair of given suffix and LCP arrays.
 Theoretically, the external-memory algorithms designed by these methods have better time and I/O complexities compared to the existing fastest construction algorithms.
-Our experimental results indicate that the current programs for Algorithm~\ref{alg:2} designed by Method B run slower than that for Algorithm~\ref{alg:1} designed by Method A, but they are much more space-efficient than the latter.
-As discussed in Section~\ref{sec:experiment}, there still remains much room for improving the implementations of the proposed algorithms.
-Our experimental programs can be further optimized to achieve higher performance, in particular for checking arrays of constant alphabets that are most common in practice.
-The optimized programs will run much faster and use at most $n$ integers as the working space in addition to the input arrays.
-
-From our perspective, a checker should be not only fast but also general.
-For program debugging, we usually check the output of a builder by comparing it with that of another builder.
-But this is not feasible in all the cases, for example, an algorithm for constructing infinite-order\footnote{A suffix array is infinite-order if the suffixes are sorted up to their ends, or else finite-order.} array can not be directly used to check a finite-order array and vise versa.
-On the contrary, our first method can be generalized to check the correctness of the lexical order and the LCP values of any pairs of suffixes.
-This makes it possible for verifying any full or sparse suffix/LCP array of any order.
+Our experimental results indicate that the current programs for Algorithm~\ref{alg:2} designed by Method B run slower than that for Algorithm~\ref{alg:1} designed by Method A, but they are much more space efficient than the latter.
+We also show in Section~\ref{sec:experiment} that there still remains much room for improving the algorithm and program designs of the proposed methods.
+Particularly, our experimental program for Method A can be parallelized to achieve higher time performance, while that for method B can be further optimized for checking arrays of constant alphabets that are most common in practice.
 
 The IS method has been applied to successfully design a number of suffix and LCP arrays construction algorithms.
-A recent work \cite{Karkkainen2017} reports that a careful engineering of the IS in external memory can build a suffix array using only $7n$ bytes for $n\le 2^{32}$, which is approaching the optimal in respect to $5n$ bytes for the IS in internal memory.
-Besides, it runs fastest in most cases of the experiments therein.
-This convinces that the IS method could serve as a basis for developing potentially optimal solutions for building suffix/LCP arrays.
-We design here the algorithms for checking given suffix and LCP arrays.
+A recent work \cite{Karkkainen2017} reports that a careful engineering of the IS in external memory can build a suffix array using around $8n$ bytes for $n\le 2^{40}$, which is approaching $6n$ bytes for the IS in internal memory.
+Besides, it runs the fastest for large $n$ in the experiments therein.
+This convinces that the IS method could be a stand for developing potentially optimal solutions for building suffix/LCP arrays.
+We design here the algorithms for checking a pair of given suffix and LCP arrays.
 In another paper, we will come up with a solution for building and checking a suffix/LCP array simultaneously using the IS method.
@@
 
+%\section*{Acknowledgment}
+%The work of Y.
+Wu, G.
+Nong and L.
+B.
+Han were supported by the Guangzhou Science and Technology Program grant 201707010165 and the Project of DEGP grant 2014KTSCX007.
+{\color{red} %The work of W.
+H.
+Chan was supported by...}
+
+% Bibliography
+\bibliographystyle{IEEEtran}
+\bibliography{IEEEabrv,bibfile}
+
+\clearpage
 \appendices
@@
 
-Recall that the lexical order of two suffixes starting with $x[i]$ and $x[j]$ can be determined by sequentially comparing their characters until finding a position $k$ such that $x[i, i + k) = x[j, j + k)$ and $x[i + k] \ne x[j + k]$.
-In other words, we have ${\sf suf}(i) < {\sf suf}(j)$ if (1) $x[i] < x[j]$~$(k = 0)$ or (2) $x[i] = x[j]$ and ${\sf suf}(i + 1) < {\sf suf}(j + 1)$~$(k > 0)$; otherwise, ${\sf suf}(i) > {\sf suf}(j)$.
-This rule is used by the IS-based SA construction algorithms to sort suffixes during the induction phase:
+Notice that ${\sf suf}(i) < {\sf suf}(j)$ if (1) $x[i] < x[j]$ or (2) $x[i] = x[j]$ and ${\sf suf}(i + 1) < {\sf suf}(j + 1)$; otherwise, ${\sf suf}(i) > {\sf suf}(j)$.
+This observation is utilized by the IS algorithms to sort suffixes as follows:
 
@@
 
-The work presented in~\cite{Fischer11} describes how to compute the LCP array during the execution of S2-S3.
+The work in~\cite{Fischer11} describes how to compute the LCP array during the execution of S2-S3.
 Given two suffixes placed at the neighboring positions in $sa$, their LCP-value can be computed according to one of the following two cases in respect to whether or not they are inserted into the same sub-bucket: if yes, then their LCP-value is one greater than that of the two suffixes from which inducing them; otherwise, their LCP-value equals to zero.
@@
 The problem here is how to obtain the LCP-values of these inducing suffixes starting at the next positions in $x$, which is modeled as a range minimum query in~\cite{Fischer11} and can be answered within amortized $\mathcal{O}(1)$ time.
-For example, when scanning from $sa[0]$ to $sa[5]$ in lines 10-21 of Fig.~\ref{fig:example2}, we induce ${\sf suf}(12)$ and ${\sf suf}(6)$ into the neighboring positions in ${\sf sa\_bkt_L(2)}$.
-During the scan, if we keep recording the minimal of $lcp(0, 5]$ in a variable, then we can obtain the LCP-value of the suffixes ${\sf suf}(13)$ and ${\sf suf}(5)$ from this variable when putting ${\sf suf}(6)$ into $sa$.
+For example, when scanning $sa[0]$ and $sa[5]$ in lines 10-11 and 20-21 of Fig.~\ref{fig:example2}, ${\sf suf}(12)$ and ${\sf suf}(6)$ are sequentially induced into the neighboring positions in ${\sf sa\_bkt_L(2)}$.
+In the meantime, if we keep recording the minimum over $lcp(0, 5]$, then we can obtain the LCP-value of the inducing suffixes ${\sf suf}(13)$ and ${\sf suf}(7)$ when putting the induced suffix ${\sf suf}(6)$ into $sa$.
 

### 2017-06-06 camera-ready/TC-2016-10-0714.tex
2017/06/06

--- 2017-04-25 draft/draft.tex
@@
 	Yi~Wu,
-	Ge~Nong,
+	Ge~Nong,~\IEEEmembership{Senior~Member,~IEEE},
 	Wai~Hong~Chan,
@@
 		\IEEEcompsocthanksitem Y.
-Wu, G.
-Nong (corresponding author) and L.~B.~Han are with the Department of Computer Science, Sun Yat-sen University, Guangzhou, and the SYSU-CMU Shunde International Joint Research Institute, Shunde, China.
-E-mails: wu.yi.christian@gmail.com, issng@mail.sysu.edu.cn, hanlb@mail2.sysu.edu.cn.
+Wu and G.
+Nong (corresponding author) are with the Department of Computer Science, Sun Yat-sen University, Guangzhou, and the SYSU-CMU Shunde International Joint Research Institute, Shunde, China.
+E-mails: wu.yi.christian@gmail.com, issng@mail.sysu.edu.cn.
 
@@
 E-mail: waihchan@ied.edu.hk.
+
+		\IEEEcompsocthanksitem L.~B.~Han is with the Key Laboratory of Machine Intelligence and Advanced Computing (Sun Yat-sen University), Ministry of Education, China, E-mail: hanlb@mail2.sysu.edu.cn.		
 }}% <-this % stops a space
@@
 
-	\includegraphics[width = 0.9\columnwidth]{example}
+	\includegraphics[width = 0.9\columnwidth]{example.eps}
 	\caption{An example for computing and comparing fingerprints for substrings specified by the LCP-values of neighboring suffixes in $sa$. \label{fig:example}}	
@@
 
-%\section*{Acknowledgment}
-%The work of Y.
-Wu, G.
-Nong and L.
-B.
-Han were supported by the Guangzhou Science and Technology Program grant 201707010165 and the Project of DEGP grant 2014KTSCX007.
-{\color{red} %The work of W.
+\section*{Acknowledgment}
+The work of G.
+Nong was supported by the Guangzhou Science and Technology Program grant 201707010165 and the Project of DEGP grant 2014KTSCX007.
+The work of W.
 H.
-Chan was supported by...}
+Chan was supported by GRF (810012), Research Grant Council, Hong Kong SAR.
 
@@
 \bibliography{IEEEabrv,bibfile}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{ywu_avator.eps}}]{Yi Wu}
+received his BSc and MSc degrees in computer science from the Central-South University in 2009 and the Sun Yat-sen University in 2012, both in China, respectively.
+He is now pursuing a Ph.D.
+degree in computer science at the Sun Yat-sen University, China.
+His current research interests are switching and routing, and string processing for massive data.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gnong_avatar.eps}}]{Ge Nong}
+received his B.E.
+and M.E.
+degrees, both in Computer Engineering, from the NanJing University of Aeronautics and Astronautics in 1992 and the South China University of Science and Technology in 1995, respectively.
+He received the Ph.D.
+in Computer Science from the Hong Kong University of Science and Technology in 1999.
+Then, he joined STMicroelectronics as a senior researcher with R\&D on IC and system technologies for high-speed switches and routers.
+He is now a Professor in the Department of Computer Science of Sun Yat-sen University in Guangzhou, China.
+His current research interests include algorithms, computer and communication networks, switching theory and performance evaluation.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{chan_avatar.eps}}]{Wai Hong Chan}
+received the BSc, MPhil and Ph.D.
+in Mathematical Science from the Hong Kong Baptist University, Hong Kong Special Administrative Region, China, in 1994, 1996 and 2003 respectively.
+He joined the Department of Mathematics and Information Technology of the Education University of Hong Kong in 2011, and now the Head of Department.
+His current research interests include algorithm design, quantum information, graph theory and combinatorics.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{lbhan_avatar.eps}}]{Ling Bo Han}
+received his B.S.
+degree in Computer Science from the Taiyuan Normal University in 2006 and the M.S.
+degree in Computer Science from the Guangxi Normal University in 2009, both in China.
+He is now pursuing a Ph.D.
+degree in the School of Data and Computer Science at the Sun Yat-sen University, China.
+His current research interests are data mining, and string processing for massive data.
+\end{IEEEbiography}
 

### 2017-06-06 draft/appendix.tex
2017/06/06

--- 2017-04-25 draft/draft.tex
@@
 
-\title{Checking Big Suffix and LCP Arrays by Probabilistic Methods}
-
-\author{
-	Yi~Wu,
-	Ge~Nong,
-	Wai~Hong~Chan,
-	Ling~Bo~Han% <-this % stops a space
-	\IEEEcompsocitemizethanks{
-		\IEEEcompsocthanksitem Y.
-Wu, G.
-Nong (corresponding author) and L.~B.~Han are with the Department of Computer Science, Sun Yat-sen University, Guangzhou, and the SYSU-CMU Shunde International Joint Research Institute, Shunde, China.
-E-mails: wu.yi.christian@gmail.com, issng@mail.sysu.edu.cn, hanlb@mail2.sysu.edu.cn.
-
-		\IEEEcompsocthanksitem Wai Hong Chan (corresponding author) is with the Department of Mathematics and Information Technology, The Education University of Hong Kong, Hong Kong.
-E-mail: waihchan@ied.edu.hk.
-}}% <-this % stops a space
-
-\IEEEtitleabstractindextext{%
-\begin{abstract}
-
-For full-text indexing of massive data, the suffix and LCP (longest common prefix) arrays have been recognized as fundamental data structures, and there are at least two needs in practice for checking their correctness, i.e.
-program debugging and verifying the arrays constructed by probabilistic algorithms.
-Two probabilistic methods are proposed to check the suffix and LCP arrays of constant or integer alphabets in external memory using a Karp-Rabin fingerprinting technique, where the checking  is wrong only with a negligible error probability.
-The first method checks the lexicographical order and the LCP-value of two suffixes by computing and comparing the fingerprints of their LCPs.
-This method is general in terms of that it can verify any full or sparse suffix/LCP array of any order.
-The second method uses less space, it first employs the fingerprinting technique to verify a subset of the given suffix and LCP arrays, from which two new suffix and LCP arrays are induced and compared with the given arrays for verification, where the induced suffix and LCP arrays can be removed for constant alphabets to save space.
-
-\end{abstract}
-
-% Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-	Suffix and LCP arrays, verification, Karp-Rabin fingerprinting, external memory.
-\end{IEEEkeywords}}
-
-% make the title area
-\maketitle
-
-\IEEEdisplaynontitleabstractindextext
-
-\IEEEpeerreviewmaketitle
-
-\section{Introduction}\label{sec:introduction}
-
-\subsection{Background} \label{sec:introduction:background}
-
-Suffix and longest common prefix (LCP) arrays play an important role in various string processing tasks, such as data compression, pattern matching and genome assembly.
-In many applications, these two data structures make up the core part of a powerful full-text index, called enhanced suffix array~\cite{Abouelhodaa2004}, which is more space efficient than a suffix tree and applicable to emulating most searching functionalities provided by the latter in the same time complexity.
-The first algorithm for building suffix array~(SA) in internal memory was presented in~\cite{Manber1993}.
-From then on, much more effort has been put on designing efficient constructors for suffix array on different computation models~\cite{Karkkainen2003, Ko2003, Kim2003, Nong11, Dementiev2008, Ferragina2012, Manzini2004, Bingmann12, Karkkainen2014, Nong14, Nong15}.
-In respect of the research on LCP array construction algorithms, the existing works can be classified into two categories with regard to their input requirements, where the algorithms from the first category compute both suffix and LCP arrays at the same time with the original text only~\cite{Fischer11, Bingmann12, Flick2015}, and those from the second category carry out the computation by taking SA and/or Burrows-Wheeler transform (BWT) as additional inputs~\cite{Kasai2001,Karkkainen2009, Fischer11, Puglisi2008, Deo2013}.
-So far, the algorithms designed by the induced sorting~(IS) principle take linear time and space to run and get the best results on both internal and external memory~\cite{Nong11, Bingmann12}.
-In addition to the sequential algorithms, there are also parallel algorithms proposed to achieve high performance by fully using the available multi-core CPUs and/or GPUs~\cite{Osipov2012, Deo2013, Wang2015, Karkkainen2015, Karkkainen2016}.
-
-While the research on efficient construction of suffix and LCP arrays keeps evolving, the algorithms proposed recently are becoming more complicated than before.
-Currently, the open source programs for the state-of-the-art algorithms are provided "as-is" for demonstration and experiment purpose only, giving no guarantee that they have correctly implemented the algorithms.
-As a common practice, a suffix or LCP checker is provided to check the correctness of a constructed array.
-For example, such a checker can be found in some software packages for DC3~\cite{Dementiev08}, SA-IS~\cite{Nong11}, eSAIS~\cite{Bingmann12} and so forth.
-In addition to help avoid implementation bugs, a checker is also demanded for an array constructed by a probabilistic algorithm~(e.g.~\cite{Bille2013}).
-In this case, the array is correctly constructed with a probability and hence must be verified by a checker to ensure its correctness.
-As far as we know, the work in~\cite{Burkhardt2003} describes the only SA checking method that can be found in the existing literature, and no efficient checking method for LCP array has been reported yet.
-Particularly, there is currently no reported solution that can check both the suffix and the LCP arrays in external memory.
-This motivates our work here to design efficient checkers for big suffix and LCP arrays in external memory.
-
-\subsection{Contribution}\label{sec:introduction:contribution}
-
-Our contribution comprises two methods to probabilistically verify any given suffix and LCP arrays.
-In principle, Method A checks the lexical order and the LCP-value of two neighboring suffixes in the suffix array by literally comparing the characters of their LCPs.
-For reducing the time complexity of a comparison between two sequences of characters, we use a Karp-Rabin fingerprinting technique to convert each sequence into a single integer, called fingerprint, and compare the fingerprints instead to check the equality of two sequences.
-The algorithm for Method A involves multiple scans and sorts on sets of $\mathcal{O}(n)$ fixed-size items.
-Its implementation in external memory suffers from a space bottleneck due to the large disk volume taken by each sort.
-To overcome this drawback, Method B first employs the fingerprinting technique to check a subset selected from the given suffix and LCP arrays, 
-%then it reuses the inducing process of the IS-based construction algorithm SA-IS \cite{Nong11} to produce the final suffix and LCP arrays from the verified subset and literally compares them with the input arrays to ensure the correctness of the latter.
-Our experiments indicate that the peak disk use of the programs for Algorithm~\ref{alg:2} designed by Method B is only about half as that of the program for Algorithm~\ref{alg:1} designed by Method A.
-then it utilizes the IS method to produce the final suffix and LCP arrays from the verified subset and literally compares them with the input arrays to ensure the correctness of the latter.
-Our experiments indicate that the program for Algorithm~\ref{alg:2} designed by Method B only takes around half as much disk space as the program for Algorithm~\ref{alg:1} designed by Method A.
-
-The remainder of this paper is organized as follows.
-Sections~\ref{sec:method1} and~\ref{sec:method2} describe the two methods and their algorithmic designs.
-Section~\ref{sec:experiment} conducts an experimental study for performance evaluation of our programs for these algorithms.
-Finally, Section~\ref{sec:conclusion} gives some concluding remarks.
-
-\section{Method A} \label{sec:method1}
-
-\subsection{Preliminaries} \label{sec:method1:notations}
-
-Given a string $x[0, n-1]$ drawn from a constant or integer alphabet $\Sigma$ of size $\mathcal{O}(1)$ or $\mathcal{O}(n)$, respectively, the suffix array of $x$, denoted by $sa$, is a permutation of $\{0, 1, ..., n - 1\}$ such that ${\sf suf}(sa[i]) < {\sf suf}(sa[j])$ for $i, j \in [0, n)$ and $i < j$, where ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$ are two suffixes starting with $x[sa[i]]$ and $x[sa[j]]$, respectively.
-Particularly, we say ${\sf suf}(sa[j])$ is a lexical neighbor of ${\sf suf}(sa[i])$ if $|i - j| = 1$.
-The LCP array of $x$, denoted by $lcp$, consists of $n$ integers, where $lcp[0]=0$ and $lcp[i]$ records the LCP-value of ${\sf suf}(sa[i])$ and ${\sf suf}(sa[i - 1])$ for $i \in [1, n)$.
-A suffix/LCP array is infinite-order if the suffixes/LCPs are sorted/counted up to their ends, respectively, or else finite-order.
-
-\subsection{Idea} \label{sec:method1:idea}
-
-According to the above definitions, we give in Lemma~\ref{lemma:1} the sufficient and necessary conditions for checking both suffix and LCP arrays.
-Notice that the lexical order and the LCP-value of any two suffixes in $x$ can be computed by literally comparing their characters.
-For convenience, we append a virtual character to $x$ and assume it to be lexicographically smaller than any characters in $\Sigma$, hence any two suffixes are different.
-
-\begin{Lemma} \label{lemma:1}
-	Both $sa[0, n)$ and $lcp[0, n)$ are correct if and only if the following conditions are satisfied, for all $i \in [1, n)$:
-	\begin{enumerate}[(1)]
-		\item
-		$sa$ is a permutation of $\{0, 1, \dots, n - 1\}$.
-		\item
-		$x[sa[i], sa[i] + lcp[i] - 1] = x[sa[i - 1], sa[i - 1] + lcp[i] - 1]$.
-		\item
-		$x[sa[i] + lcp[i]] > x[sa[i - 1] + lcp[i]]$. 	
-	\end{enumerate}
-\end{Lemma}
-
-\begin{IEEEproof}
-	Both the sufficiency and necessity are immediately from the definitions of suffix and LCP arrays.
-Condition 1 guarantees that each suffix is in $sa$, conditions 2 and 3 guarantees that the lexical order and the LCP-value of any two neighboring suffixes in $sa$ are both correct.
-\end{IEEEproof}
-
-Directly comparing the characters of two suffixes to determine their LCP has the worst case time of $O(n)$.
-An alternative is to exploit a perfect hash function to convert each substring into a single integer such that any two substrings have a common hash value if and only if they are literally equal to each other, hence the hash values of two substrings can be compared instead to check the equality of two substrings.
-Taking into account the high difficulty of finding a perfect hash function to meet this requirement, we prefer using a Karp-Rabin fingerprinting function~\cite{Karp1987} to transform a substring into an integer called fingerprint.
-To be specific, suppose $L$ is a prime and $\delta$ is a number randomly chosen from $[1, L)$, the fingerprint ${\sf fp}(i, j)$ for a substring $x[i, j]$ can be iteratively calculated according to the formulas below: scan $x$ rightward to iteratively compute ${\sf fp}(0, k)$ for all $k \in [0, n)$ using Formulas~\ref{formula:1}-\ref{formula:2}, record ${\sf fp}(0, i - 1)$ and ${\sf fp}(0, j)$ during the calculation and subtract the former from the latter to obtain ${\sf fp}(i, j)$ using Formula~\ref{formula:3}.
-
-\begin{Formula} \label{formula:1}
-	${\sf fp}(0, -1) = 0$.
-
-\end{Formula}
-
-\begin{Formula} \label{formula:2}	
-	${\sf fp}(0, i) = {\sf fp}(0, i - 1) \cdot {\delta} + x[i]\mod L$ for $i \ge 0$.
-
-\end{Formula}
-
-\begin{Formula} \label{formula:3}
-	${\sf fp}(i, j) = {\sf fp}(0, j) - {\sf fp}(0 ,i - 1) \cdot {\delta}^{j - i + 1}\mod L$.
-
-\end{Formula}
-
-Notice that two equal substrings always share a common fingerprint, but the inverse is not true.
-The probability of a false match can be reduced to a negligible level by setting $L$ to a large value~\cite{Karp1987}, this property is utilized in~\cite{Bille2013} to design a probabilistic algorithm for computing a sparse suffix array.
-Hence we have:
-
-\begin{Corollary} \label{corollary:1}
-	Both $sa[0, n)$ and $lcp[0, n)$ are correct with a high probability given these conditions, for all $i \in [1, n)$:
-
-	\begin{enumerate}[(1)]
-		\item
-		$sa$ is a permutation of $\{0, 1, \dots, n - 1\}$.
-
-		\item
-		${\sf fp}(sa[i], sa[i] + lcp[i] - 1) = {\sf fp}(sa[i - 1], sa[i - 1] + lcp[i] - 1)$.
-
-		\item
-		$x[sa[i] + lcp[i]] > x[sa[i - 1] + lcp[i]]$.
-	\end{enumerate}
-\end{Corollary}
-
-Fig.~\ref{fig:example} gives an illustrating example for utilizing Corollary~\ref{corollary:1} to check the input suffix and LCP arrays.
-Given that $L = 197$ and $\delta = 101$, lines 4-8 compute ${\sf fp}(0, p)$ iteratively according to Formulas~\ref{formula:1}-\ref{formula:2}.
-Lines 10-20 use these values to compute the fingerprints for all the target substrings.
-In more detail, consider the leftmost pair of neighboring suffixes in $sa$, i.e.
-${\sf suf}(sa[0])$ and ${\sf suf}(sa[1])$, the substrings given by their LCP-value are $x[sa[0], sa[0] + lcp[1] - 1]$ and $x[sa[1], sa[1] + lcp[1] - 1]$, respectively.
-According to Formula~\ref{formula:3}, ${\sf fp}(sa[0], sa[0] + lcp[1] - 1)$ is equal to the difference between ${\sf fp}(0, sa[0] - 1)$ and ${\sf fp}(0, sa[0] + lcp[1] - 1)$, both have been calculated.
-Following the same way, ${\sf fp}(sa[1], sa[1] + lcp[1] - 1)$ is computed by reducing ${\sf fp}(0, sa[1] - 1)$ from ${\sf fp}(0, sa[1] + lcp[1] - 1)$.
-Hence, we obtain the fingerprints for these two substrings in lines 10-14 and see that they are equal to each other.
-
-\begin{figure}
-	\centering
-
-	\includegraphics[width = 0.9\columnwidth]{example}
-	\caption{An example for computing and comparing fingerprints for substrings specified by the LCP-values of neighboring suffixes in $sa$. \label{fig:example}}	
-\end{figure}
-
-\subsection{Algorithm} \label{sec:method1:algorithm}
-
-We describe an approach for checking the conditions in Corollary~\ref{corollary:1} on random access models, of which the core part is to check the lexical order and the LCP-value for each pair of neighboring suffixes in $sa$ during the scan of $sa$ and $lcp$.
-This is done by using Formulas~\ref{formula:1}-\ref{formula:3}.
-Two zero-initialized arrays $fp$ and $mk$ are introduced to facilitate the checking process, where $fp$ is for storing the fingerprints of all the prefixes in $x$ and $mk$ is for checking whether $sa$ stores a permutation of $\{0, 1, ..., n - 1\}$.
-
-\begin{enumerate}
-	\item [S1]
-	Scan $x$ with $i$ increasing from $0$ to $n - 1$, for each scanned $x[i]$, compute ${\sf fp}(0, i)$ and assign to $fp[i]$.
-
-	\item [S2]
-	Scan $sa$ and $lcp$ with $i$ increasing from $1$ to $n - 1$, for each scanned $sa[i]$ and $lcp[i]$, let $u = sa[i], v = lcp[i]$ and $w = sa[i - 1]$, perform:
-
-	\begin{enumerate}[(a)]
-		\item
-		Retrieve $fp[u - 1]$ and $fp[u + v - 1]$ from $fp$ to compute ${\sf fp}(u, u + v - 1)$, set $mk[u]=1$;
-
-		\item
-		Retrieve $fp[w - 1]$ and $fp[w + v - 1]$ from $fp$ to compute ${\sf fp}(w, w + v - 1)$;
-
-		\item
-		Check if ${\sf fp}(u, u + v - 1) = {\sf fp}(w, w + v - 1)$ and $x[u + v] > x[w + v]$;
-
-		\item
-		Set $mk[sa[0]] = 1$.
-	\end{enumerate}
-
-	\item [S3] Check if $mk[i] = 1$ for all $i \in [0, n)$.
-
-\end{enumerate}
-
-The above approach takes $\mathcal{O}(n)$ time and space in internal memory.
-The difficulty for applying it in external memory is step S2, it suffers from a performance degradation caused by frequent random accesses to disks.
-Assume that $x$, $sa$ and $lcp$ are stored in external memory, we design Algorithm~\ref{alg:1} for conducting these I/O operations in a disk-friendly way.
-The idea is to first sort data in the order that they are to be visited and then access them sequentially.
-For this purpose, Algorithm~\ref{alg:1} first scans $sa$ and $lcp$ to produce $ST_1, ST_2, ST_3$, and sorts their tuples by the first components in ascending order at the beginning (lines~\ref{alg:1:a}-\ref{alg:1:b}).
-Afterward, it iteratively computes the fingerprints of all the prefixes of $x$ according to Formulas~\ref{formula:1}-\ref{formula:2} and assigns them to the sorted tuples as follows (lines~\ref{alg:1:c}-\ref{alg:1:d}): when figuring out ${\sf fp}(0, i - 1)$, extract each tuple $e$ with $e.1st = i$ from $ST_1/ST_2/ST_3$, update $e$  with ${\sf fp}(0, i - 1)$, and then forward $e$ to $ST_1'/ST_2'/ST_3'$.
-Because the first components of the tuples in $ST_1$ constitute a copy of $sa$, the algorithm checks condition 1 when scanning these tuples in their sorted order.
-Finally, it sorts the updated tuples back to their original order~(line~\ref{alg:1:e}) and visits them sequentially to check conditions 2 and 3 following the same way of step S2~(lines~\ref{alg:1:f}-\ref{alg:1:g}).
-
-\SetKwProg{Fn}{Function}{}{}
-
-\begin{algorithm*}
-
-	\caption{The Algorithm Based on Corollary~\ref{corollary:1}.}
-
-	\label{alg:1}
-
-	%\SetAlgoNoLine
-	\Fn{{\sf CheckByFP}($x$, $sa$, $lcp$, $n$)}{
-
-		$ST_1$ := $[(sa[i], i, null) | i \in [0, n)]$ \label{alg:1:a}
-
-		$ST_2$ := $[(sa[i] + lcp[i + 1], i, null, null) | i \in [0, n - 1)]$
-
-		$ST_3$ := $[(sa[i] + lcp[i], i, null, null) | i \in [1, n)]$
-
-		sort the tuples in $ST_1$, $ST_2$ and $ST_3$ by the 1st components, respectively; \label{alg:1:b}
-
-		$fp := 0$  \label{alg:1:c}
-
-		\For{$i \in [0, n]$}{
-
-			\If{$ST_1.{\sf notEmpty}()$ {\sf and} $ST_1.{\sf top}().1st = i$}{~\label{alg:1:h}
-				$e := ST_1.{\sf top}()$, $ST_1.{\sf pop}()$, $e.3rd := fp$, $ST_1'.{\sf push}(e)$
-			}
-			\Else{
-				\Return false \hspace{1cm} // condition 1 is violated
-			}~\label{alg:1:i}
-			\While{$ST_2.{\sf notEmpty}()$ {\sf and} $ST_2.{\sf top}().1st = i$}{
-
-				$e := ST_2.{\sf top}()$, $ST_2.{\sf pop}()$, $e.3rd := fp$, $e.4th := x[i]$, $ST_2'.{\sf push}(e)$
-			}
-
-			\While{$ST_3.{\sf notEmpty}()$ {\sf and} $ST_3.{\sf top}().1st = i$}{
-
-				$e := ST_3.{\sf top}()$, $ST_3.{\sf pop}()$, $e.3rd := fp$, $e.4th := x[i]$, $ST_3'.{\sf push}(e)$
-			}
-
-			$fp := fp \cdot \delta + x[i] \! \mod \! P$ \hspace{1cm} // $x[n]$ is the virtual character
-		} \label{alg:1:d}
-
-		sort the tuples in $ST_1'$, $ST_2'$ and $ST_3'$ by the 2nd component, respectively; \label{alg:1:e}
-
-		\For {$i \in [1, n)$}{  \label{alg:1:f}
-
-			$fp_1 := ST_1'.{\sf top}().3rd$, $ST_1'.{\sf pop}()$, $fp_2 := ST_2'.{\sf top}().3rd$, $ch_1 := ST_2'.{\sf top}().4th$, $ST_2'.{\sf pop}()$
-
-			$\hat{fp_1} = fp_2 - fp_1 \cdot \delta^{lcp[i]} \! \mod \! P$ \label{alg:1:j}
-
-		 	$fp_1 := ST_1'.{\sf top}().3rd$, $fp_3 := ST_3'.{\sf top}().3rd$, $ch_2 := ST_3'.{\sf top}().4th$, $ST_3'.{\sf pop}()$
-
-			$\hat{fp_2} = fp_3 - fp_1 \cdot \delta^{lcp[i]} \! \mod \! P$	\label{alg:1:k}
-
-			\If{$\hat{fp_1} \ne \hat{fp_2}$ {\sf or} $ch_1 \ge ch_2$}{
-
-				\Return false \hspace{1cm} // condition 2 or 3 is violated
-			}	
-		} \label{alg:1:g}
-
-		\Return true
-	}
-\end{algorithm*}
-
-The last point is how to obtain $\delta^{lcp[i]}$ quickly when computing $\hat{fp_1}$ and $\hat{fp_2}$ in lines~\ref{alg:1:j} and~\ref{alg:1:k}.
-One way is to keep a lookup table in internal memory to store all $\delta^{lcp[i]}$.
-This can answer the question in constant time, but it is space-consuming and impractical to be used in external memory.
-Notice that the LCP of any two suffixes is shorter than $n$, we can return the answer in $\mathcal{O}(\lceil \log_2{n} \rceil)$ time using $\mathcal{O}(\lceil \log_2{n} \rceil)$ internal memory.
-Let $e$ be an integer from $[0, n)$, its binary form is $k_{\lceil \log_2{n} \rceil}...k_1k_0$.
-We have $\delta^e = \Pi_{i = 0}^{\lceil \log_2{n} \rceil}{\delta}^{k_i \cdot 2^i}$, which can be computed with $\{{\delta}^{1}, {\delta}^{2}, \dots, {\delta}^{2^{\lceil \log_2{n} \rceil}} \}$ already known.
-
-\subsection{Analysis} \label{sec:method1:analysis}
-
-Algorithm~\ref{alg:1} performs multiple scans and sorts on the arrays of $\mathcal{O}(n)$ fixed-size tuples in disks.
-Given RAM size $M$, disk size $D$ and block size $B$, all are in words, the time and I/O complexities for each scan are $\mathcal{O}(n)$ and $\mathcal{O}(n / B)$, respectively, while those for each sort are $\mathcal{O}(n\log_{M/ B}(n / B))$ and $\mathcal{O}((n / B)\log_{M / B}(n / B))$, respectively~\cite{Arge2013}.
-Algorithm~\ref{alg:1} reaches its peak disk use when sorting the tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}.
-Suppose the input string and the suffix/LCP array are encoded as $\alpha$- and $\beta$-byte integers, respectively, and each fingerprint is a $\gamma$-byte integer, it takes $(2 \cdot \beta + \gamma)$ space for sorting the tuples of $ST_1/ST_1'$ and $(\alpha + 2 \cdot \beta + \gamma)$ for sorting the tuples of $ST_2/ST_2'$ and $ST_3/ST_3'$.
-For saving space, our program implementing the algorithm tackles $ST_1/ST_1'$, $ST_2/ST_2'$ and $ST_3/ST_3'$ separately and performs a single scan over $x$ for each of them to obtain the fingerprints, using less space but more time.
-The experiment in Section~\ref{sec:experiment} indicates that the disk use is 40 times of $x$.
-
-\section{Method B} \label{sec:method2}
-
-\subsection{Preliminaries} \label{sec:method2:preliminaries}
-
-We further to give another checking method using the induced sorting principle \cite{Nong11,Dementiev08}, which requires much less space than Method A.
-For presentation convenience, we introduce some symbols and notations as below.
-
-Character and suffix classification.
-All the characters in $x$ are classified into three types, namely L-, S- and S*-type.
-In detail, $x[i]$ is L-type if (1) $i = n - 1$ or (2) $x[i] > x[i + 1]$ or (3) $x[i] = x[i + 1]$ and $x[i + 1]$ is L-type; otherwise, $x[i]$ is S-type.
-Further, if $x[i]$ and $x[i + 1]$ are separately L-type and S-type, then $x[i + 1]$ is also S*-type.
-Moreover, a suffix is L-, S- or S*-type if its heading character is L-, S-, or S*-type, respectively.
-
-Suffix and LCP buckets.
-All the suffixes in $sa$ are partitioned into multiple buckets and those of a common heading character are grouped into a single bucket that occupies a contiguous interval in $sa$.
-Each bucket can be further divided into two sub-buckets, where the left and the right parts  contain L- and S-type suffixes only, respectively.
-For short, we use ${\sf sa\_bkt}(c)$ to denote the bucket storing the suffixes starting with character $c$ and ${\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$ to denote its left/right sub-bucket.
-Accordingly, $lcp$ can be also split into multiple buckets, where ${\sf lcp\_bkt}(c)/{\sf lcp\_bkt_L}(c)/{\sf lcp\_bkt_S}(c)$ stores the LCP-values of suffixes in ${\sf sa\_bkt}(c)/{\sf sa\_bkt_L}(c)/{\sf sa\_bkt_S}(c)$, respectively.
-
-Suffix and LCP arrays for S*-type suffixes.
-Given that the number of S*-type suffixes is $n_1$, $sa^*[0, n_1)$ stores all the S*-type suffixes arranged in lexical order, while $lcp^*[0] = 0$ and $lcp^*[i]$ records the LCP-value of ${\sf suf}(sa^*[i])$ and ${\sf suf}(sa^*[i - 1])$ for $i \in [1, n_1)$.
-
-Type Array. The array $t$ records in $t[i]$ the type information of $x[i]$, where $t[i] = 1$ or $0$ if $x[i]$ is S- or L-type, respectively.
-
-\subsection{Idea} \label{sec:method2:idea}
-
-The induced sorting principle has been extensively used to design efficient algorithms for constructing the suffix and LCP arrays in internal or external memory \cite{Nong11,Nong14, Nong15, Bingmann12,Fischer11}.
-Such a construction algorithm mainly consists of a reduction phase for computing $sa^*$ and $lcp^*$, followed by an induction phase for inducing $sa$ and $lcp$ from $sa^*$ and $lcp^*$~\footnote{An overview of the induction phase is given in Appendix~\ref{sec:appendix}.}.
-Given that $sa^*$ and $lcp^*$ are already known, we can induce the final suffix and LCP arrays from them.
-This suggests a checking method based on Lemma~\ref{lemma:2}.
-
-\begin{Lemma} \label{lemma:2}
-Both $sa[0, n)$ and $lcp[0, n)$ are correct if and only if the conditions below are satisfied:
-
-\begin{enumerate}[(1)]
-	\item
-	Both $sa^*$ and $lcp^*$ are correct.
-	\item
-	$sa = sa'$ and $lcp = lcp'$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by the IS method.
-\end{enumerate}
-\end{Lemma}
-
-We have Corollary~\ref{corollary:2} for probabilistically checking the conditions of Lemma \ref{lemma:2}.
-
-\begin{Corollary} \label{corollary:2}
-Both $sa[0, n)$ and $lcp[0, n)$ are correct with a high probability given the following conditions, for all $i \in [1, n_1)$ and $j \in [0, n)$:
-\begin{enumerate}[(1)]
-	\item
-	$x[sa^*[i]]$ is S*-type, and $sa^*[i] \ne sa^*[k]$ for all $k \in [0, n_1)$ and $k \ne i$.
-	\item
-	${\sf fp}(sa^*[i], sa^*[i] + lcp^*[i] - 1) = {\sf fp}(sa^*[i - 1], sa^*[i - 1] + lcp^*[i] - 1)$.
-	\item
-	$x[sa^*[i] + lcp^*[i]] > x[sa^*[i - 1] + lcp^*[i]]$.
-	\item
-	$sa[j] = sa'[j]$ and $lcp[j] = lcp'[j]$ for $j \in [0, n)$, where $sa'$ and $lcp'$ are induced from $sa^*$ and $lcp^*$ by the IS method.
-\end{enumerate}
-\end{Corollary}
-
-\subsection{Algorithm} \label{sec:method2:algorithm}
-
-We further to design Algorithm~\ref{alg:2} for checking the conditions of Corollary~\ref{corollary:2}.
-The first step is to compute and verify $sa^*$ and $lcp^*$.
-Similar to Method A, the fingerprinting technique is employed to probabilistically check the correctness of $sa^*$ and $lcp^*$.
-The array $sa^*$ can be produced by sequentially retrieving the S*-type suffixes from $sa$ and the LCP-value of two successive S*-type suffixes in $sa$, say ${\sf suf}(sa[i])$ and ${\sf suf}(sa[j])$, is equal to the minimal of $\{lcp[i + 1], ..., lcp[j - 1], lcp[j]\}$.
-The algorithm first sorts all the suffixes in $sa$ by their starting positions~(lines~\ref{alg:2:a}-\ref{alg:2:b}) and then scans $x$ once to get the S*-type suffixes~(lines~\ref{alg:2:c}-\ref{alg:2:d}).
-After that, it puts these S*-type suffixes back in their lexical order and outputs them one by one to generate $sa^*$~(lines~\ref{alg:2:g}-\ref{alg:2:h}).
-Meanwhile, it calculates the LCP-value for each pair of the neighboring suffixes in $sa^*$ by tracing the minimum in the $lcp$ interval between these two suffixes.
-Notice that, we check condition 1 when visiting the suffixes in their position order (lines~\ref{alg:2:e}-\ref{alg:2:f}), and check conditions 2 and 3 by Algorithm~\ref{alg:1} with $sa^*$ and $lcp^*$ as input.
-Given $sa^*$ and $lcp^*$ are correct,
-Algorithm~\ref{alg:2} invokes an inducing process by employing the IS method to induce $sa'$ and $lcp'$ from $sa^*$ and $lcp^*$~(line~\ref{alg:2:k}) and compares them with $sa$ and $lcp$ to complete the whole checking process~(lines~\ref{alg:2:l}-\ref{alg:2:m}).
-
-\begin{algorithm*}[!htbp]
-
-	\caption{The Algorithm Based on Corollary~\ref{corollary:2}.}
-
-	\label{alg:2}
-
-	%\SetAlgoNoLine
-	\Fn{{\sf CheckByIS}($x$, $sa$, $lcp$, $n$)}{
-
-	$ST_1$ := $[(sa[i], i, null) | i \in [0, n)]$ \label{alg:2:a}
-
-	sort the tuples in $ST_1$ by the 1st component; \label{alg:2:b}
-
-	$pos := -1$ \label{alg:2:c}
-
-	\For{$i \in (n, 0]$}{
-
-		$e := ST_1.{\sf top}()$, $ST_1.{\sf pop}()$
-
-		\If{$x[i]$ is S*-type}{ \label{alg:2:e}
-
-			\If{$pos \ge e.1st$}{
-
-				\Return false  \hspace{1cm} // condition 1 is violated
-			}
-
-			$ST_2.{\sf push}(e)$, $pos := e.1st$
-		}\label{alg:2:f}
-	} \label{alg:2:d}
-
-	sort the tuples in $ST_2$ by the 2nd component; \label{alg:2:g}
-
-	$i := 0$, $j := 0$, $lcp_{min} := max\_val$
-
-	\While{$ST_2.{\sf NotEmpty()}$}{
-
-		$e := ST_2.{\sf top}()$, $ST_2.{\sf pop}()$
-
-		\While {true} {
-
-			$lcp_{min} := {\sf min}(lcp_{min}, lcp[i])$
-
-			\If {$e.2nd = i$} {
-
-				$sa^*[j] := e.1st$, $lcp^*[j] := lcp_{min}$, $j := j + 1$, $i:= i + 1$
-
-				\textbf{break}
-			}
-
-			$i:= i + 1$
-		}
-
-		$lcp_{min} := max\_val$
-	} \label{alg:2:h}
-
-	\If{${\sf CheckByFP}(x, sa^*, lcp^*, n_1) = false$}{  \label{alg:2:i}
-
-		\Return false \hspace{1cm} // conditions 2 or 3 is violated
-	}\label{alg:2:j}
-
-	$(sa', lcp') := {\sf InducingProcess}(x, sa^*, lcp^*)$ \label{alg:2:k}
-
-	\For{$i \in [0, n)$}{\label{alg:2:l}
-
-		\If{$sa[i] \ne sa'[i] \parallel lcp[i] \ne lcp'[i]$}{
-
-			\Return false \hspace{1cm}	// condition 4 is violated
-		}	
-	}\label{alg:2:m}
-
-	\Return true
-}
-\end{algorithm*}
-
-Assume that the alphabet $\Sigma$ is of size $\mathcal{O}(1)$, we can check $sa$ and $lcp$ without storing the induced suffix and LCP arrays in Algorithm~\ref{alg:2}.
-The idea is to compare the induced suffix/LCP items with their corresponding items in $sa/lcp$ during the inducing process.
-Specifically, when a suffix/LCP item $v_1$ is induced into a bucket, we check if it is equal to the corresponding item $v_2$ in $sa/lcp$.
-If $v_1 = v_2$, then $v_2$ is correct and we further use this value to induce the remaining suffix/LCP items.
-The key point is to quickly retrieve the items of $sa/lcp$ in external memory.
-This can be done by conducting sequential I/O operations if we provide a read pointer together with a buffer for each suffix/LCP sub-bucket.
-We describe below more details of the modified inducing process, where $lp_1/lp_2$ and $sp_1/sp_2$ indicate the next items to be visited in the L-type and S-type sub-buckets, respectively.
-
-\begin{enumerate}
-	\item [S1]
-	\begin{enumerate}[(a)]
-		\item 
-		Let $lp_1[c]$ and $lp_2[c]$ point to the leftmost items of ${\sf sa\_bkt_L}(c)$ and ${\sf lcp\_bkt_L}(c)$, for $c \in [0, \Sigma)$.
-		\item 
-		Scan $sa$ and $lcp$ rightward to induce the L-type suffixes and their LCP-values.
-For each induced suffix $p$ (with a heading character $c_0$) and its LCP-value $q$: (1) check if $p = lp_1[c_0]$ and $q = lp_2[c_0]$; (2) move $lp_1[c_0]$ and $lp_2[c_0]$ to the next items on the right.
-	\end{enumerate}
-	\item [S2]
-	\begin{enumerate}[(a)]
-		\item 	
-		Let $sp_1[c]$ and $sp_2[c]$ point to the rightmost items of ${\sf sa\_bkt_S}(c)$ and ${\sf lcp\_bkt_S}(c)$, for $c \in [0, \Sigma)$.
-		\item 	
-		Scan $sa$ and $lcp$ leftward to induce the S-type suffixes and their LCP-values.
-For each induced suffix $p$ (with a heading character $c_0$) and its LCP-value $q$: (1) check if $p = sp_1[c_0]$ and $q = sp_2[c_0]$; (2) move $sp_1[c_0]$ and $sp_2[c_0]$ to the next items on the left.
-	\end{enumerate}
-\end{enumerate}
-
-\subsection{Analysis} \label{sec:method2:analysis}
-
-Algorithm~\ref{alg:2} mainly consists of two steps, where the first step for checking $sa^*$ and $lcp^*$ can be done within sorting complexity and the second step for checking $sa$ and $lcp$ can also be done in sorting complexity for using external-memory sorters and priority queues.
-In our current program for this algorithm, the peak disk use is reached in the second step, specifically, when computing the BWT from $sa$ and $x$ for use in the inducing process.
-
-\section{Experiments} \label{sec:experiment}
-
-\subsection{Setup} \label{sec:experiment:setup}
-
-For implementation simplicity, our programs for the algorithms proposed in the previous sections use the external-memory containers provided by the STXXL library~\cite{Dementiev2007} to manage read/write operations on disks.
-We make a performance evaluation by running them on the real-world corpora listed in Table~\ref{tbl:1}, where three measures normalized by the size of input string are investigated:
-
-\begin{itemize}
-
-	\item RT: running time, in microseconds.
-
-	\item PDU: peak disk use of external memory, in bytes.
-
-	\item IOV: amount of data read from and write to external memory, in bytes, where each integer is 40-bit.
-
-\end{itemize}
-
-The experimental platform is a server with an Intel Core i3-550 CPU, 4 GiB RAM and 2 TiB HD.
-All the programs are compiled by gcc/g++ 4.8.4 with -O3 options on ubuntu 14.04 64-bit operating system and each program is allowed to use 3 GiB RAM.
-For simplicity, "ProgA" and "ProgB" represent the programs for Algorithms~\ref{alg:1} and~\ref{alg:2}, respectively.
-
-%Table
-\renewcommand\arraystretch{1.3}
-\begin{table}[!htbp]
-	\caption{Corpus, $n$ in Gi, 1 byte per character.}
-	\label{tbl:1}
-	\centering
-	\begin{tabular}{|l|c|c|p{5.2cm}|}
-		\hline
-		Corpora & \multicolumn{1}{c|}{$\|\Sigma\|$} & $n$ & Description \\\hline
-		enwiki & 256 & 74.7 & An XML dump of English Wikipedia, available at \url{https://dumps.wikimedia.org/enwiki}, dated as 16/05/01. \\\hline	
-		uniprot & 96 & 2.5 & UniProt Knowledgebase, available at \url{ftp://ftp.expasy.org/databases/uniprot/current_release/knowledgebase/complete/}, dated as 16/05/11. \\\hline
-		proteins & 27 & 1.1 & Swissprot database, available at \url{http://pizzachili.dcc.uchile.cl/texts/protein}, dated as 06/12/15. \\\hline
-	\end{tabular}
-\end{table}
-
-\subsection{Results} \label{sec:experiments:results}
-
-Fig.~\ref{fig:performance_analysis} illustrates the performance comparison of ProgA and ProgB on different datasets, where "enwiki\_8g" consists of the leftmost 8 GiB extracted from "enwiki".
-As depicted, ProgB runs slower than ProgA by around 20\%.
-The speed gap is mainly due to the difference in I/O performance.
-Specifically, the I/O volume of ProgA keeps at $155n$ for all the three datasets, while that of ProgB rises up to nearly $200n$ on average.
-Besides, the peak disk use of ProgB is about $26/40=0.65$ as ProgA.
-Recall that Algorithm~\ref{alg:2} invokes Algorithm~\ref{alg:1} to check the suffix and LCP arrays for the S*-type suffixes.
-Because at most one out of every two successive characters in the input string is S*-type, the consumption for checking the suffix and LCP arrays of S*-type suffixes in ProgB is expected to be half as that for checking the given arrays in ProgA.
-For a better insight, we collect in Table~\ref{tbl:2} the performance overhead of ProgB and ProgA when checking the suffix and LCP arrays of S*-type suffixes and all, respectively.
-As can be observed, the mean ratio of the number of S*-type suffixes to the number of all the suffixes is around 0.30 for the datasets under investigation, while the mean ratios of time, space and I/O volume for checking $sa^*$ and $lcp^*$ to that for checking $sa$ and $lcp$ are 0.38, 0.57 and 0.60, respectively.
-
-The above observations indicate that ProgB reaches its peak disk use when checking the final suffix and LCP arrays during the inducing process, i.e., the inducing process constitutes the performance bottleneck of the whole algorithm.
-By adopting the space optimization scheme introduced in Section~\ref{sec:method2:algorithm}, we adapt Algorithm~\ref{alg:2} and evaluate the tuned version of ProgB, called ProgB+, in comparison with ProgA and ProgB.
-Fig.~\ref{fig:performance_analysis} shows that the maximum space requirement for ProgB+ is about $21n$, which is much less than that of ProgB and even only half as that of ProgA.
-In addition, progB+ outperforms its prototype with respect to time and I/O efficiency and is faster than ProgA when handling "uniprot".
-We also investigate the performance trend of the three programs on the prefix of "enwiki" with the length varying in $\{1, 2, 4, 8\}$ GiB.
-In Figure~\ref{fig:performance_analysis2}, the peak disk use for each program remains unchanged, but their speed become slower as the prefix length increases due to the performance degradation of the external memory sorter used in our programs.
-This can be also observed from Table~\ref{tbl:2}, where ProgB+ keeps the I/O volume around $90n$ with the prefix length of "enwiki" varying from $1$ to $8$ GiB but its running time rises from $1.05$ to $1.33$.
-
-%figure
-\begin{figure}
-	\centering
-	\subfigure{
-		\label{subfig:pdu_cmp}
-		\includegraphics[width = 0.9\columnwidth]{pdu_cmp}
-	}
-	\hfil
-	\subfigure{
-		\label{subfig:iov_cmp}
-		\includegraphics[width = 0.9\columnwidth]{io_cmp}
-	}
-	\hfil
-	\subfigure{
-		\label{subfig:ct_cmp}
-		\includegraphics[width = 0.9\columnwidth]{ct_cmp}
-	}
-	\caption{Performance of ProgA, ProgB, ProgB+ and ProgC for different corpora.}
-	\label{fig:performance_analysis}
-\end{figure}
-
-%figure
-\begin{figure}[htbp!]
-	\centering
-	\subfigure{
-		\label{subfig:pdu_cmp2}
-		\includegraphics[width = 0.9\columnwidth]{pdu_cmp2}
-	}
-	\hfil
-	\subfigure{
-		\label{subfig:iov_cmp2}
-		\includegraphics[width = 0.9\columnwidth]{io_cmp2}
-	}
-	\hfil
-	\subfigure{
-		\label{subfig:ct_cmp2}
-		\includegraphics[width = 0.9\columnwidth]{ct_cmp2}
-	}
-	\caption{Performance of ProgA, ProgB, ProgB+ and ProgC for prefixes of "enwiki".}
-	\label{fig:performance_analysis2}
-\end{figure}
-
-%Table
-\renewcommand\arraystretch{1.3}
-\begin{table*}
-	\caption{A performance comparison of checking the suffix and LCP arrays of S*-type suffixes to checking that of all the suffixes.}
-	\label{tbl:2}
-	\centering
-	\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|}
-		\hline
-		\multirow{2}{*}{Dataset} & \multicolumn{3}{|c|}{\# of suffixes} & \multicolumn{3}{|c|}{PDU} & \multicolumn{3}{|c|}{IOV} & \multicolumn{3}{|c|}{RT} \\\cline{2-13}
-						 & S*-type & all & ratio & S*-type & all & ratio & S*-type & all & ratio & S*-type & all & ratio \\\hline
-		enwiki\_1g & 329810376 & 1073741824 & 0.31 & 15.67 & 40 & 0.39 & 89.94 & 155 & 0.58 & 1.05 & 1.70 & 0.62 \\\hline
-		enwiki\_2g & 650901939 & 2147483648 & 0.30 & 15.41 & 40 & 0.39 & 89.18 & 155 & 0.58 & 1.22 & 1.85 & 0.66 \\\hline
-		enwiki\_4g & 1301327878 & 4294967296 & 0.30 & 15.45 & 40 & 0.39 & 89.14 & 155 & 0.58 & 1.19 & 1.89 & 0.63 \\\hline
-		enwiki\_8g & 2586471839 & 8589934592 & 0.30 & 15.35 & 40 & 0.38 & 88.80 & 155 & 0.57 & 1.33 & 2.14 & 0.62 \\\hline	
-		uniprot & 829262945 & 3028811776 & 0.27 & 13.94 & 40 & 0.35 & 83.80 & 155 & 0.54 & 1.04 & 2.26 & 0.46 \\\hline
-		proteins & 379092002 & 1184366592 & 0.32 & 16.21 & 40 & 0.41 & 92.29 & 155 & 0.60 & 1.14 & 1.85 & 0.62	\\\hline
-		mean & 1012811163 & 3189156522 & 0.30 & 15.34 & 40 & 0.38 & 88.86 & 155 & 0.57 & 1.16 & 1.95 & 0.60 \\\hline
-	\end{tabular}
-\end{table*}
-
-%It is identified that both programs heavily rely on the performance of the external memory sorter in use.
-A potential candidate for improving their speed is to adapt a GPU-based multi-way sorter~(e.g.,~\cite{Leischner2010, Davidson2012}) for sorting massive data using external memory.
-By the aid of these fast sorting algorithms, the throughputs of the programs are expected to nearly approach the I/O bandwidth.
-Besides, the first two steps of Algorithm~\ref{alg:1} are independent of each other and thus can be executed in parallel for acceleration.
-This technique can be also applied to check the suffix and LCP arrays of the LMS suffixes in Algorithm~\ref{alg:3}.
-
-%Currently, for Algorithm~\ref{alg:3}, step 2 constitutes the space bottleneck.
-It is worthy of mentioning that this step produces a copy of the suffix and LCP array during the inducing and checking processes.
-Actually, given that $\Sigma$ is of a constant size and $sa/lcp$ are known already, we can simply scan the input $sa/lcp$ to perform the inducing process and compare each induced suffix/LCP value with that in the given $sa/lcp$ to perform the checking process, resulting in less space consumption.
-To the end, we must maintain a read pointer for each suffix/LCP bucket in $sa/lcp$ to scan elements in sequence.
-
-Because there is no solution for checking both suffix and LCP arrays in the existing literature,  comparing the outputs of two builders could be a way for checking (even though it is not checking in the strict sense, for both outputs may be incorrect).
-In the next experiment, we compare our programs with two builders for suffix and LCP arrays as follows, where each of them combines an existing suffix sorter with an LCP builder:
-
-\begin{itemize}
-	\item Solution 1: Use eSAIS for building SA and the sequential version of Sparse-$\phi$~\cite{Karkkainen2016} for building LCP array.
-
-	\item Solution 2: Use pSAscan~\cite{Karkkainen2015} for building SA and the parallel version of Sparse-$\phi$ for building LCP array.
-\end{itemize}
-
-We select these programs because they are currently the fastest suffix and LCP arrays builders available to us.
-A runtime breakdown of the programs for these solutions on the prefixes of "enwiki" is given in Table~\ref{tbl:3}.
-The program for Solution 2 is about two times faster than that for Solution 1 and twice as fast as ProgA, which is mainly due to the high speed of pSAscan in this experiment.
-However, it is worthy of pointing out that both pSAscan and Sparse-$\phi$ are of the time and I/O complexities proportional to $n^2/M$.
-This is much higher than eSAIS and our checking algorithms when $n$ increases, and thus poses a strict limitation to the scalability of Solution 2.
-As reported in~\cite{Karkkainen2015}, when $n$ is considerably greater than $M$, eSAIS is much more time and I/O efficient than pSAscan.
-In this experiment, pSAscan builds the SA for "enwiki\_8g" in time double as that for "enwiki\_1g".
-For big $n$, it is reasonable to compare the results of our programs with that of Solution 1.
-
-%Table
-\renewcommand\arraystretch{1.3}
-\begin{table*}[h]
-	\caption{A runtime comparison for the programs of two construction solutions and ours.}
-	\label{tbl:3}
-	\centering
-	\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
-		\hline
-		\multirow{2}{*}{Dataset} & \multicolumn{3}{|c|}{Solution 1} & \multicolumn{3}{c|}{Solution 2} & \multirow{2}{*}{ProgA} & \multirow{2}{*}{ProgB+} \\\cline{2-7}
-		 & eSAIS & sequential sparse-$\phi$ & total & pSAscan & parallel sparse-$\phi$ & total & & \\\hline
-		enwiki\_1g & 2.21 & 0.61 & 2.82 & 0.39 & 0.59 & 0.98 & 1.70 & 2.54 \\\hline
-		enwiki\_2g & 2.63 & 0.53 & 3.16 & 0.47 & 0.53 & 1.00 & 1.84 & 2.51 \\\hline
-		enwiki\_4g & 2.90 & 0.63 & 3.53 & 0.59 & 0.40 & 0.99 & 1.89 & 2.56 \\\hline
-		enwiki\_8g & 3.02 & 0.63 & 3.65 & 0.83 & 0.45 & 1.28 & 2.13 & 2.79 \\\hline
-	\end{tabular}
-\end{table*}
-
-Currently, the method described in~\cite{Burkhardt2003} is the only known in the literature for checking SA.
-Despite that it can check SA only, in order to give a rough image for the performance of our methods, we implement it by STXXL and compare our implementation with ProgA and ProgB/ProgB+ in Fig.~\ref{fig:performance_analysis} and \ref{fig:performance_analysis2}.
-This method and its program are denoted by "Method C" and "ProgC", respectively.
-ProgC is about two times faster than ProgA and three times faster than ProgB+, where the runtime is consistent with the I/O volume.
-This performance gap can be significantly narrowed by improving the algorithm and program designs of Methods A and B, using the techniques discussed below.
-
-\subsection{Discussion} \label{sec:experiments:discussion}
-
-\subsubsection{Improvement in Algorithm Design} \label{sec:experiments:discussion:improve_algorithm_design}
-
-There are several ways to improve the algorithm designs of the proposed checking methods.
-First, Algorithm~\ref{alg:1} sorts the tuples of $ST_1/ST_1', ST_2/ST_2', ST_3/ST_3'$ in sequence.
-These sorting processes are independent and can be parallelized on computation platforms with multiple disks supporting parallel reads and writes.
-Second, Method B verifies the suffix and LCP arrays using the induced sorting principle.
-At the time of writing this paper, the existing IS algorithms are naturally sequential.
-Recently, we have been conducting a study to design parallel IS algorithms, this work will also help improve the design of Algorithm~\ref{alg:2}.
-Third, both methods A and B assume a constant or integer alphabet in this paper.
-However, in practice, an input string is commonly of a constant alphabet, e.g.
-4 and 256 characters for genome and text, respectively.
-In this case, Method B can be improved for better time and space performance by inducing the final suffix and LCP arrays directly from $sa_S/lcp_S$ or $sa_L/lcp_L$, which consist of all the sorted S-type or L-type suffixes with their LCP-values and can be obtained as follows.
-Given the alphabet is constant, we first scan the input string once to get the statistics for buckets in the input suffix array.
-Without loss of generality, suppose that the S-type characters are less, we scan the suffix array once to get $sa_S/lcp_S$ by using the bucket statistics to on-the-fly determine a scanned suffix is S-type or not.
-Then we check $sa_S/lcp_S$ by using Algorithm~\ref{alg:1} and induce $sa'/lcp'$ from them.
-In this way, we avoid the two integer sorts in the current fashion of Method B for retrieving $sa^*/lcp^*$ and speed up the inducing process by nearly half as well.
-
-\subsubsection{Improvement in Program Design} \label{sec:experiments:discussion:improve_program_design}
-
-Our programs are coded for experimental study only, from engineering aspects, there is still a big margin for better implementation.
-For example, both ProgA and ProgB/ProgB+ consume long CPU time and large I/O volume for sorting data in external memory.
-We currently use the containers provided by STXXL to execute the sorting processes without designing a specific sorter optimized for our purpose.
-It is possible to speed up each sorting process by high-performance radix-sort GPU algorithms.
-Secondly, all our programs require a disk space significant more than what it is really needed.
-The main reason is the disk space for saving temporary data is not freed in time even if the data is not needed any more.
-This is an implementation issue due to STXXL in use, can be solved by storing the temporary data using multiple files and deleting each file immediately when it is obsolete.
-
-Several algorithms for induced sorting a suffix and/or LCP arrays were proposed these recent years \cite{Nong15,Nong14,Bingmann12}, with different methods for solving the key problem of retrieving the preceding character of a sorted suffix in the inducing process.
-A recent work \cite{Karkkainen2017} engineering these induced sorting methods with some implementation optimizing techniques achieves a significant improvement over the previous results.
-As reported, the peak disk use is around $8n$ for 40-bit integers.
-Because the induced sorting process is the performance bottleneck for Method B, it is reasonable to expect that a better engineering implementation of the method will yield a remarkable improvement in both time and space.
-An optimized engineering of our methods is out of the scope of this paper and will be addressed elsewhere.
-
-\subsubsection{Miscellaneous}
-
-Method A is more general than the other alternatives, it can be generalized to check the correctness of the lexical order and LCP values of any pairs of suffixes, this makes it possible for verifying any full or sparse suffix/LCP array of any order.
-On the other hand, Method B can only check suffix and LCP arrays, while Method C is specific for checking SA only.
-This feature of Method A makes it applicable to various scenarios.
-For example, a suffix/LCP array may be broken due to software or hardware malfunctions.
-If a backup is not available and it is time-consuming to rebuild the whole array, then we can locate the bad areas using Algorithm~\ref{alg:1} and restore the partial SA for each area by calling a sparse SA construction algorithm.
-Another example is to check the correctness of a sparse SA, in this case, the number of suffixes in a sparse SA is commonly much smaller than that in the full SA, Algorithm~\ref{alg:1} could be an efficient verification solution.
-
-\section{Conclusions} \label{sec:conclusion}
-
-Two methods are proposed here for probabilistically checking a pair of given suffix and LCP arrays.
-Theoretically, the external-memory algorithms designed by these methods have better time and I/O complexities compared to the existing fastest construction algorithms.
-Our experimental results indicate that the current programs for Algorithm~\ref{alg:2} designed by Method B run slower than that for Algorithm~\ref{alg:1} designed by Method A, but they are much more space efficient than the latter.
-We also show in Section~\ref{sec:experiment} that there still remains much room for improving the algorithm and program designs of the proposed methods.
-Particularly, our experimental program for Method A can be parallelized to achieve higher time performance, while that for method B can be further optimized for checking arrays of constant alphabets that are most common in practice.
-
-The IS method has been applied to successfully design a number of suffix and LCP arrays construction algorithms.
-A recent work \cite{Karkkainen2017} reports that a careful engineering of the IS in external memory can build a suffix array using around $8n$ bytes for $n\le 2^{40}$, which is approaching $6n$ bytes for the IS in internal memory.
-Besides, it runs the fastest for large $n$ in the experiments therein.
-This convinces that the IS method could be a stand for developing potentially optimal solutions for building suffix/LCP arrays.
-We design here the algorithms for checking a pair of given suffix and LCP arrays.
-In another paper, we will come up with a solution for building and checking a suffix/LCP array simultaneously using the IS method.
-By this way, no additional checker is needed to be distributed with a suffix/LCP array builder using the IS method.
-
-%\section*{Acknowledgment}
-%The work of Y.
-Wu, G.
-Nong and L.
-B.
-Han were supported by the Guangzhou Science and Technology Program grant 201707010165 and the Project of DEGP grant 2014KTSCX007.
-{\color{red} %The work of W.
-H.
-Chan was supported by...}
-
-% Bibliography
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,bibfile}
-
-\clearpage
 \appendices
